### 2020-05-22 manuscript.Rmd
Add finalized code scripts and RMD for manuscript

---
title             : "Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring"
shorttitle        : "Arab Spring"

author: 
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidg Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Lead C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action"
  - id            : "2"
    institution   : "University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

abstract: |

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

# clear the workspace
rm(list=ls())

# install and load required packages
source('./scripts/required_packages.r')
source('./scripts/libraries_and_functions.r')

# references file
r_refs("references.bib")

# create subdirectories
# dir.create("./data/raw") # load three data files here
# dir.create("./data/formatted/primary")
# dir.create("./data/formatted/secondary")
# dir.create("./results/primary/crqa")
# dir.create("./results/primary/windowed-crqa")
# dir.create("./results/secondary/icews/crqa/source_target")
# dir.create("./results/secondary/icews/crqa/target")
# dir.create("./results/secondary/icews/windowed-crqa/source_target")
# dir.create("./results/secondary/icews/windowed-crqa/target")
# dir.create("./results/secondary/pheonix/crqa/source_target")
# dir.create("./results/secondary/pheonix/crqa/target")
# dir.create("./results/secondary/pheonix/windowed-crqa/source_target")
# dir.create("./results/secondary/pheonix/windowed-crqa/target")

```

```{r data-prep, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# format the data
source('./scripts/primary-analyses/01_formatting_data.R')
source('./scripts/secondary-analyses/icews/01_formatting_data.R')
source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')

```

# Introduction

# Method

## Data Collection

## Data Preparation

## Procedure

## Data analysis

# Results

```{r analyses, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# primary analyses
source('./scripts/primary-analyses/02_crqa.R')
source('./scripts/primary-analyses/03_windowed_crqa.R')

# secondary analyses
source('./scripts/secondary-analyses/icews/02_crqa.R')
source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
source('./scripts/secondary-analyses/pheonix/02_crqa.R')
source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')

```

```{r images}
# code block to insert an image

```

# Discussion

### Acknowledgements

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-05-22 manuscript.tex
Add finalized code scripts and RMD for manuscript

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Arab Spring}
\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Lead C. Windsor\textsuperscript{3,*}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Center for the Ecological Study of Perception and Action\\\textsuperscript{2} University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidg Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

\title{Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring}

\date{}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{data-collection}{%
\subsection{Data Collection}\label{data-collection}}

\hypertarget{data-preparation}{%
\subsection{Data Preparation}\label{data-preparation}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{acknowledgements}{%
\subsubsection{Acknowledgements}\label{acknowledgements}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\endgroup

\end{document}

### 2020-05-22 scripts/01_formatting_data.R

@@ -1,603 +1,0 @@
-##### Formatting Arab Spring Data #####
-# Code by: M. Chiovaro
-# University of Connecticut
-
-# clear environment
-rm(list=ls())
-
-# set working directory
-setwd("./arab-spring/")
-
-# load the required packages
-library(dplyr)
-library(readxl)
-
-# read in Syria data 
-cohesion <- read_excel("./data/raw/SyriaDataByDay-1.xlsx")  
-event_data <- read.csv("./data/raw/ICEWS.Syria.3_2012-7_2012.csv")
-
-#=============================
-# Prep the event time series #
-#=============================
-
-# create new cleaned dataframe
-processed_event <- event_data %>% 
-  
-  # group by date
-  group_by(Event.Date) %>%
-  
-  # count total number of events
-  mutate(count = n()) %>%
-  
-  # count positive events
-  mutate(pos_event = sum(Intensity > 0)) %>%
-  
-  # count negative events
-  mutate(neg_event = sum(Intensity < 0)) %>%
-  
-  # keep one unique row per day
-  distinct(Event.Date, count, pos_event, neg_event) %>%
-  
-  rename(Date = Event.Date) %>%
-  
-  # ungroup data
-  ungroup()
-  
-##### Quartiles #####
-
-### count of events ###
-
-# create the quartiles
-processed_event$count_quart <- with(processed_event, cut(count, 
-                                breaks=quantile(count, probs=seq(0, 1, by=0.25), na.rm=TRUE), 
-                                include.lowest=TRUE))
-# check that we have 4 levels
-unique(processed_event$count_quart)
-
-# re-label with intuitive quartile levels
-levels(processed_event$count_quart) <- factor(c("1","2","3","4"))
-
-### positive events ###
-
-# create the quartiles
-processed_event$pos_quart <- with(processed_event, cut(pos_event, 
-                                  breaks=quantile(pos_event, probs=seq(0, 1, by=0.25), na.rm=TRUE), 
-                                  include.lowest=TRUE))
-# check that we have 4 levels
-unique(processed_event$pos_quart)
-
-# re-label with intuitive quartile levels
-levels(processed_event$pos_quart) <- factor(c("1","2","3","4"))
-
-### negative events ###
-
-# create the quartiles
-processed_event$neg_quart <- with(processed_event, cut(neg_event, 
[…]

### 2020-05-22 scripts/libraries_and_functions.r

@@ -1,0 +1,18 @@
+#### Load necessary packages ####
+#
+#
+#
+# Last updated:
+
+# list of required packages
+required_packages = c(
+  'dplyr',
+  'ggplot2',
+  'crqa',
+  'tidyr',
+  'modeest',
+  'papaja'
+)
+
+# load required packages
+invisible(lapply(required_packages, require, character.only = TRUE))

### 2020-05-22 scripts/primary-analyses/01_formatting_data.R

@@ -1,0 +1,585 @@
+######## Formatting Arab Spring Data (ICEWS) ########
+#
+# This script formats data related to the Arab Spring.
+# Daily Twitter social cohesion and event data are processed 
+# and transformed into deciles for CRQA and windowed CRQA
+# analyses.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in the data 
+cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab", header = TRUE, sep = "\t", quote = "")
+
+#### 2. Filter and format the time series ####
+
+### filter for source and target ###
+
+# filter full 2012 ICEWS data for correct dates and parameters
+ICEWS_filtered <- ICEWS_df %>% 
+  
+  # fill blanks with NAs
+  na_if("") %>%
+
+  # turn factor to character for using grepl
+  mutate(Event.Date = as.character(Event.Date)) %>%
+  
+  # filter out unusable dates
+  filter(grepl("^(2012)[-](0[1-9]|1[012])[-](0[1-9]|[12][0-9]|3[01])$", 
+               Event.Date)) %>%
+  
+  # turn to date format to use select for date range
+  mutate_at(vars(Event.Date), as.Date, format = "%Y-%m-%d") %>%
+  
+  # grab the dates that align with old data
+  filter(Event.Date >= as.Date("2012-03-30") 
+         & Event.Date <= as.Date("2012-06-15")) %>%
+  
+  # change search params to characters for searching
+  mutate_if(is.factor, as.character)  %>%
+  
+  # grab observations where either source or target is Syria
+  filter(grepl("Syria", Source.Country) |
+           grepl("Syria", Target.Country)) %>%
+  
+  # filter out invalid intensity formats
+  filter(grepl("\\-*\\d+\\.*\\d*", Intensity)) %>%
+  
+  # convert intensity to numeric
+  mutate(Intensity = as.numeric(Intensity)) %>%
+  
+  # filter out invalid intensity values
+  filter(Intensity >= -10 & Intensity <= 10)
+
+### prep the event count time series ###
+
+# create new dataframe with counts of different events
+ICEWS_formatted_source_target <- ICEWS_filtered %>% 
+  
+  # group by date
[…]

### 2020-05-22 scripts/primary-analyses/02_crqa.R

@@ -1,0 +1,501 @@
+######## Cross-Recurrence Quantification Analysis ########
+#
+# This script runs cross-recurrence quantification analysis
+# the real-world events and Twitter social cohesion of 
+# Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/primary/formatted_data.csv")
+shuffled_full <- read.csv("./data/formatted/primary/shuffled_data_full.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_full[,c(1:1000)]
+shuffled_all_source_target <- shuffled_full[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_full[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_full[,c(3001:4000)]
+shuffled_all_target <- shuffled_full[,c(4001:5000)]
+shuffled_pos_target <- shuffled_full[,c(5001:6000)]
+shuffled_neg_target <- shuffled_full[,c(6001:7000)]
+
+#### 2. Run CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# run cross recurrence
+cross_recurrence_analysis = crqa(ts1=data$coh_deciles,
+                                 ts2=data$all_deciles_source_target,
+                                 delay=0,
+                                 embed=1,
+                                 rescale=0,
+                                 radius=.001,
+                                 normalize=0,
+                                 mindiagline=2,
+                                 minvertline=2,
+                                 tw=0) 
+
+# save the crqa results
+rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
+write.table(rqa_results_all_source_target,'./results/primary/crqa/source_target/crqa_results-all_events.csv',
+            sep=",", row.names=FALSE)
+
+# build the CRP using 'crqa' package function: plotRP
+png("./results/primary/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+par = list(unit = 2, 
+           labelx = "Social cohesion", 
+           labely = "Count of all events", 
+           cols = "blue", 
+           pcex = .5)
+plotRP(cross_recurrence_analysis$RP, par)
+dev.off()
+
[…]

### 2020-05-22 scripts/primary-analyses/03_windowed_crqa.R

@@ -1,0 +1,733 @@
+######## Windowed Cross-Recurrence Quantification Analysis ########
+#
+# This script runs windowed cross-recurrence quantification 
+# analysis the real-world events and Twitter social cohesion 
+# of Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21 
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/primary/formatted_data.csv")
+shuffled_windowed <- read.csv("./data/formatted/primary/shuffled_data_windowed.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_windowed[,c(1:1000)]
+shuffled_all_source_target <- shuffled_windowed[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_windowed[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_windowed[,c(3001:4000)]
+shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
+shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
+shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
+
+#### 2. Run Windowed CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# calculate windowed rqa
+windowed_all_source_target = wincrqa(ts1 = data$coh_deciles, 
+                                       ts2 = data$all_deciles_source_target, 
+                                       windowstep = 1, 
+                                       windowsize = 14,
+                                       radius = .001,  
+                                       delay = 1,       
+                                       embed = 1, 
+                                       rescale = 0, 
+                                       normalize = 0,  
+                                       mindiagline = 2, 
+                                       minvertline = 2, 
+                                       tw = 0,
+                                       whiteline = FALSE,
+                                       trend = TRUE) 
+
+# tranform into a dataframe for easier plotting 
+wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+
+## count of positive events and social cohesion ##
+
+# calculate windowed rqa
[…]

### 2020-05-22 scripts/primary-analyses/04_cross_wavelet.R

@@ -1,0 +1,71 @@
+######## Cross Wavelet Analysis (ICEWS) ########
+#
+# This script runs cross wavelet analysis on the
+# real-world events and Twitter social cohesion of 
+# Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_15
+
+# clear environment
+rm(list=ls())
+
+# set working directory
+setwd("./arab-spring/")
+
+# load the required packages
+library(dplyr)
+library(biwavelet)
+
+# read in truncated data 
+data <- read.csv("./data/formatted/formatted_data.csv")
+
+# make date into a number for the analysis
+data$date_num <- seq(from =1, to = nrow(data))
+
+t1 <- data[,c("date_num", "coh_dec")]
+t2 <- data[,c("date_num", "all_dec")]
+
+##### Coherence #####
+
+# Specify the number of iterations. The more, the better (>1000)
+nrands = 1000
+
+# compute coherence
+wtc.AB = wtc(t1, t2, nrands = nrands)
+
+# make room for the color bar on the right
+par(oma = c(0, 0, 0, 1), mar = c(5, 4, 5, 5) + 0.1)
+
+# plot the graph
+plot(wtc.AB, 
+     plot.phase = TRUE, 
+     lty.coi = 1, 
+     col.coi = "grey", 
+     lwd.coi = 2, 
+     lwd.sig = 2, 
+     arrow.lwd = 0.03, 
+     arrow.len = 0.12, 
+     ylab = "Scale", 
+     xlab = "Period (days)", 
+     plot.cb = TRUE, 
+     main = "Wavelet Coherence\nMean social coherence and Count of events (deciles)")
+
+# Adding grid lines
+n = length(t1[, 1])
+abline(v = seq(5, n, 5), h = 1:16, col = "brown", lty = 1, lwd = 1)
+
+# Defining x labels
+#axis(side = 3, at = c(seq(5, n, 5)), labels = c(seq(5, 75, 5)))
+
+##### Cross Wavelet #####
+
+# Compute cross-wavelet
+xwt <- xwt(t1, t2)
+
+# make room for the color bar on the right
+par(oma=c(0, 0, 0, 1), mar=c(5, 4, 4, 5) + 0.1) 
+
+# Plot cross wavelet power and phase difference (arrows)
+plot(xwt, plot.cb=TRUE)

### 2020-05-22 scripts/required_packages.r

@@ -1,0 +1,21 @@
+#### Install missing packages ####
+#
+#
+#
+# Last updated:
+
+# list of required packages as strings
+required_packages = c(
+  'dplyr',
+  'ggplot2',
+  'crqa',
+  'tidyr',
+  'modeest',
+  'papaja'
+)
+
+# install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)
+missing_packages = required_packages[!(required_packages %in% installed.packages()[,"Package"])]
+if (length(missing_packages) > 0) {
+  install.packages(missing_packages)
+}

### 2020-05-22 scripts/secondary-analyses/icews/01_formatting_data.R

@@ -1,0 +1,588 @@
+######## Formatting Arab Spring Data (ICEWS) ########
+#
+# This script formats data related to the Arab Spring.
+# Daily Twitter social cohesion and event data are processed 
+# and transformed into *sextiles* for CRQA and windowed CRQA
+# analyses.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in the data 
+cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab", header = TRUE, sep = "\t", quote = "")
+
+#### 2. Filter and format the time series ####
+
+### filter for source and target ###
+
+# filter full 2012 ICEWS data for correct dates and parameters
+ICEWS_filtered <- ICEWS_df %>% 
+  
+  # fill blanks with NAs
+  na_if("") %>%
+
+  # turn factor to character for using grepl
+  mutate(Event.Date = as.character(Event.Date)) %>%
+  
+  # filter out unusable dates
+  filter(grepl("^(2012)[-](0[1-9]|1[012])[-](0[1-9]|[12][0-9]|3[01])$", 
+               Event.Date)) %>%
+  
+  # turn to date format to use select for date range
+  mutate_at(vars(Event.Date), as.Date, format = "%Y-%m-%d") %>%
+  
+  # grab the dates that align with old data
+  filter(Event.Date >= as.Date("2012-03-30") 
+         & Event.Date <= as.Date("2012-06-15")) %>%
+  
+  # change search params to characters for searching
+  mutate_if(is.factor, as.character)  %>%
+  
+  # grab observations where either source or target is Syria
+  filter(grepl("Syria", Source.Country) |
+           grepl("Syria", Target.Country)) %>%
+  
+  # filter out invalid intensity formats
+  filter(grepl("\\-*\\d+\\.*\\d*", Intensity)) %>%
+  
+  # convert intensity to numeric
+  mutate(Intensity = as.numeric(Intensity)) %>%
+  
+  # filter out invalid intensity values
+  filter(Intensity >= -10 & Intensity <= 10)
+
+### prep the event count time series ###
+
+# create new dataframe with counts of different events
+ICEWS_formatted_source_target <- ICEWS_filtered %>% 
+  
+  # group by date
[…]

### 2020-05-22 scripts/secondary-analyses/icews/02_crqa.R

@@ -1,0 +1,501 @@
+######## Cross-Recurrence Quantification Analysis ########
+#
+# This script runs cross-recurrence quantification analysis
+# the real-world events and Twitter social cohesion of 
+# Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/icews/formatted_data.csv")
+shuffled_full <- read.csv("./data/formatted/secondary/icews/shuffled_data_full.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_full[,c(1:1000)]
+shuffled_all_source_target <- shuffled_full[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_full[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_full[,c(3001:4000)]
+shuffled_all_target <- shuffled_full[,c(4001:5000)]
+shuffled_pos_target <- shuffled_full[,c(5001:6000)]
+shuffled_neg_target <- shuffled_full[,c(6001:7000)]
+
+#### 2. Run CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# run cross recurrence
+cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
+                                 ts2=data$all_sextiles_source_target,
+                                 delay=0,
+                                 embed=1,
+                                 rescale=0,
+                                 radius=.001,
+                                 normalize=0,
+                                 mindiagline=2,
+                                 minvertline=2,
+                                 tw=0) 
+
+# save the crqa results
+rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
+write.table(rqa_results_all_source_target,'./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv',
+            sep=",", row.names=FALSE)
+
+# build the CRP using 'crqa' package function: plotRP
+png("./results/secondary/icews/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+par = list(unit = 2, 
+           labelx = "Social cohesion", 
+           labely = "Count of all events", 
+           cols = "blue", 
+           pcex = .5)
[…]

### 2020-05-22 scripts/secondary-analyses/icews/03_windowed_crqa.R

@@ -1,0 +1,733 @@
+######## Windowed Cross-Recurrence Quantification Analysis ########
+#
+# This script runs windowed cross-recurrence quantification 
+# analysis the real-world events and Twitter social cohesion 
+# of Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21 
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/icews/formatted_data.csv")
+shuffled_windowed <- read.csv("./data/formatted/secondary/icews/shuffled_data_windowed.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_windowed[,c(1:1000)]
+shuffled_all_source_target <- shuffled_windowed[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_windowed[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_windowed[,c(3001:4000)]
+shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
+shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
+shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
+
+#### 2. Run Windowed CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# calculate windowed rqa
+windowed_all_source_target = wincrqa(ts1 = data$coh_sextiles, 
+                                       ts2 = data$all_sextiles_source_target, 
+                                       windowstep = 1, 
+                                       windowsize = 14,
+                                       radius = .001,  
+                                       delay = 1,       
+                                       embed = 1, 
+                                       rescale = 0, 
+                                       normalize = 0,  
+                                       mindiagline = 2, 
+                                       minvertline = 2, 
+                                       tw = 0,
+                                       whiteline = FALSE,
+                                       trend = TRUE) 
+
+# tranform into a dataframe for easier plotting 
+wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+
+## count of positive events and social cohesion ##
+
+# calculate windowed rqa
[…]

### 2020-05-22 scripts/secondary-analyses/pheonix/01_formatting_data.R

@@ -1,0 +1,594 @@
+######## Formatting Arab Spring Data (Pheonix) ########
+#
+# Pheonix event data from the Cline center: 
+# https://databank.illinois.edu/datasets/IDB-2796521
+# "PhoenixBLN-SWB_1979-2019.csv" pulled on 2020_05_13
+#
+# This script formats data related to the Arab Spring.
+# Daily Twitter social cohesion and event data are processed 
+# and transformed into sextiles for CRQA and windowed CRQA
+# analyses.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data
+cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+pheonix_df <- read.csv("./data/raw/PhoenixBLN-SWB_1979-2019.csv", header = TRUE)
+
+#### 2. Filter and format the time series ####
+
+### filter for source and target ###
+
+# filter full 2012 ICEWS data for correct dates and parameters
+pheonix_df_filtered <- pheonix_df %>% 
+  
+  # fill blanks with NAs
+  na_if("") %>%
+  
+  # drop observations without dates
+  drop_na(story_date) %>%
+  
+  # turn factor to character for using grepl
+  mutate(story_date = as.character(story_date)) %>%
+  
+  # turn to date format to use select for date range
+  mutate_at(vars(story_date), as.Date, format = "%m/%d/%Y") %>%
+  
+  # grab the dates that align with old data
+  filter(story_date >= as.Date("2012-03-30") 
+         & story_date <= as.Date("2012-06-15")) %>%
+  
+  # change search params to characters for searching
+  mutate_if(is.factor, as.character)  %>%
+  
+  # grab observations where either source or target is Syria
+  filter(grepl("SYR", source) |
+           grepl("SYR", target)) %>%
+  
+  # convert intensity to numeric
+  mutate(goldstein = as.numeric(goldstein))
+
+### prep the event count time series ###
+
+# create new dataframe with counts of different events
+pheonix_formatted_source_target <- pheonix_df_filtered %>% 
+  
+  # group by date
+  group_by(story_date) %>%
+  
+  # count total number of events
+  mutate(all_events_source_target = n()) %>%
+  
+  # count positive events
+  mutate(pos_events_source_target = sum(goldstein > 0)) %>%
+  
[…]

### 2020-05-22 scripts/secondary-analyses/pheonix/02_crqa.R

@@ -1,0 +1,501 @@
+######## Cross-Recurrence Quantification Analysis (Pheonix) ########
+#
+# This script runs cross-recurrence quantification analysis
+# the real-world events and Twitter social cohesion of 
+# Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/pheonix/formatted_data.csv")
+shuffled_full <- read.csv("./data/formatted/secondary/pheonix/shuffled_data_full.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_full[,c(1:1000)]
+shuffled_all_source_target <- shuffled_full[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_full[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_full[,c(3001:4000)]
+shuffled_all_target <- shuffled_full[,c(4001:5000)]
+shuffled_pos_target <- shuffled_full[,c(5001:6000)]
+shuffled_neg_target <- shuffled_full[,c(6001:7000)]
+
+#### 2. Run CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# run cross recurrence
+cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
+                                 ts2=data$all_sextiles_source_target,
+                                 delay=0,
+                                 embed=1,
+                                 rescale=0,
+                                 radius=.001,
+                                 normalize=0,
+                                 mindiagline=2,
+                                 minvertline=2,
+                                 tw=0) 
+
+# save the crqa results
+rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
+write.table(rqa_results_all_source_target,'./results/secondary/pheonix/crqa/source_target/crqa_results-all_events.csv',
+            sep=",", row.names=FALSE)
+
+# build the CRP using 'crqa' package function: plotRP
+png("./results/secondary/pheonix/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+par = list(unit = 2, 
+           labelx = "Social cohesion", 
+           labely = "Count of all events", 
+           cols = "blue", 
+           pcex = .5)
[…]

### 2020-05-22 scripts/secondary-analyses/pheonix/03_windowed_crqa.R

@@ -1,0 +1,731 @@
+######## Windowed Cross-Recurrence Quantification Analysis (Pheonix) ########
+#
+# This script runs windowed cross-recurrence quantification 
+# analysis the real-world events and Twitter social cohesion 
+# of Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_05_21
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/pheonix/formatted_data.csv")
+shuffled_windowed <- read.csv("./data/formatted/secondary/pheonix/shuffled_data_windowed.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_windowed[,c(1:1000)]
+shuffled_all_source_target <- shuffled_windowed[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_windowed[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_windowed[,c(3001:4000)]
+shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
+shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
+shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
+
+#### 2. Run Windowed CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# calculate windowed rqa
+windowed_count = wincrqa(ts1 = data$coh_sextiles, 
+                         ts2 = data$all_sextiles_source_target, 
+                         windowstep = 1, 
+                         windowsize = 14,
+                         radius = .001,  
+                         delay = 1,       
+                         embed = 1, 
+                         rescale = 0, 
+                         normalize = 0,  
+                         mindiagline = 2, 
+                         minvertline = 2, 
+                         tw = 0,
+                         whiteline = FALSE,
+                         trend = TRUE) 
+
+# tranform into a dataframe for easier plotting 
+wincrqa_all_df_source_target <- as.data.frame(windowed_count$crqwin)
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+
+## count of positive events and social cohesion ##
+
+# calculate windowed rqa
[…]

### 2020-05-25 manuscript.Rmd
Add intro, methods, and references

@@
     corresponding : yes    # Define only one corresponding author
-    address       : "406 Babbidg Road, Unit 1020, Storrs, CT 06269"
+    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
     email         : "megan.chiovaro@uconn.edu"
@@
 abstract: |
-
+  Social mobilization requires effective collective coordination.
+In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
+Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
+Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
+Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
+This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
+We conclude with a discussion of implications and applications of nonlinear methods in political science research.
   <!-- https://tinyurl.com/ybremelq -->
 
-keywords          : "keywords"
+keywords          : "Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring"
 wordcount         : "X"
@@
 # clear the workspace
-rm(list=ls())
+#rm(list=ls())
 
@@
 # references file
-r_refs("references.bib")
+#r_refs("references.bib")
 
@@
 # format the data
-source('./scripts/primary-analyses/01_formatting_data.R')
-source('./scripts/secondary-analyses/icews/01_formatting_data.R')
-source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')
+#source('./scripts/primary-analyses/01_formatting_data.R')
+#source('./scripts/secondary-analyses/icews/01_formatting_data.R')
+#source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')
 
@@
 
-# Introduction
+Social coordination has long been used both physically and virtually to start and carry out collective actions.
+These collective events bring individuals together and create emergent patterns of communication and action.
+Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
+From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another [@mahner1997foundations].
+Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
+The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
+
+## Arab Spring
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
+His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
+His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
+The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
+These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
+The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab, @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+
+## Social Cohesion
+Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary].
+This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
+Being overcome with this feeling is known to lead to violence [@collins2009violence, @spaaij2014sports].
+While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
+Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
+Just as real-world social cohesion can be quantified, the same is true for online cohesion.
+Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
+Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
+
+## Social Media as a Platform for Mobilization
+Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
+Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
+During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests [@vicari2013public].
+Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
+As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
+
+## Use of Nonlinear Methods in Naturally Occurring Data
+Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
+Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
+This notion has been increasingly replaced by ideas from dynamical systems theory.
+Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts [@turvey2018lectures].
+When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
+Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
+Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
+The primary methods used in the current work is cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and it’s off-shoot, windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
+CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions [for a review, see @fusaroli2014analyzing] and interpersonal synchrony [@paxton2017interpersonal].
+We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
+
+## The Present Work
+Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
+We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
+Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
+This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
+Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence], we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
+We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
+Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
+As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
+The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
 
 # Method
+## Materials
+### Tweet Corpus
+The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
+A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
+For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
+The tweet corpus was scraped from Twitter by [insert search parameters here].
 
-## Data Collection
+### Event Data
+Event data were obtained from the 2012 Integrated Crisis Early Warning System [ICEWS; @DVN/28075_2015].
+The event data were first filtered to remove incomplete and incorrectly formatted data.
+They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
 
 ## Data Preparation
+### Social Cohesion Metric
+The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
+If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
+The tweets were first sorted into ascending order by timestamp.
+They were then grouped into successive sets of five tweets.
+Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
+1-3).
+This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
+Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
 
-## Procedure
+(insert social cohesion equations here)
 
-## Data analysis
+The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
+All hashtags and URLs were included in the analysis.
+This method is similar to that of inverse document frequency (IDF).
+For more information on IDF, see Sparck Jones (1972) and Robertson (2004).
+
+### ICEWS Event Time Series
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
+Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
+This well-validated coding scheme allows for numerical quantification of different event types.
+For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score (M = , SD = ).
+Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero (M = , SD = ).
+Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero (M = , SD = ).
+
+## Analyses
+### Cross-Recurrence Quantification Analysis
+We first used cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
+As an extension of RQA, which captures the patterns of revisited states of a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
+Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
+In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.
+Nyquist frequency in signal processing; @grenander1959probability).
+We converted each time series (e.g., Figure #) into deciles (e.g., Figure #) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+In CRQA, a recurrent point is when two signals share the same state.
+These shared states can be at the same time or at later points in the time series.
+A recurrence plot (RP) is the visual representation of CRQA.
+To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
+Visually analyzing these plots can help reveal patterns of structure and recurrence.
+The line y = x is known as the line of identity.
+This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
+See Figures #-# for examples of RPs.
+
+#### Metrics
+The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
+This metrics gives a general description of how frequently the time series are sharing the same states.
+In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
+Recurrent points that occur in successive moments form line structures.
+These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
+The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
+For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
+The average length of the line structures is called mean line (L).
+This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
+The longest line length is called max line (maxL).
+maxL indicates the longest instance of being “stuck” in a particular state together.
+The total number of lines is called NRLINE.
+The more lines there are, the more coordinated the system may be.
+The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
+These entropy metrics help indicate the stability and predictability of the system.
+When one of the signals gets “stuck” in a state and the other moves on to other states, this results in vertical line structures.
+The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
+For more detail on CRQA metrics, see Coco and Dale (2014).
+
+#### Parameters
+To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
+Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
+No normalization was done, and lines were considered two or more consecutive recurrent points.
+The Theiler window was set to zero to include points along the line of identity.
+For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2014).
+
+#### Permutation Test
+Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
+Using the sample function in base R [@R-base], 1000 permuted time series were created for each of the real time series.
+A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
+CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
+This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
+Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
+Thus, RR is not included in the inferential tests.
+For more information on permutation tests, see Good (2013).
+
+### Windowed Cross-Recurrence Quantification Analysis
+We used windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence] to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
+In this analysis, a smaller “window” of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
+The window remains the same size and “slides” diagonally up the line of identity.
+The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+#### Metrics
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
+These metrics can then be plotted as a time series to visualize their evolution over time.
+For these analyses, we decided to visualize recurrence rate and determinism.
+#### Parameters
+In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
+First, a window size must be decided on.
+The window size will determine how many observations are used in each CRQA analysis.
+We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
+The second parameter to be chosen is a step size.
+Window step size is how far the window moves up the line of identity before conducting CRQA again.
+We chose 1 for the step size to understand how the metrics evolve from day to day.
+All other CRQA metrics remained the same as previously noted.
+#### Visualization
+To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
+This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
+These dynamics can then be linked to other external events.
+See Figures ##-## for examples.
+#### Permutation Test
+To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
+Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
+The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 # primary analyses
-source('./scripts/primary-analyses/02_crqa.R')
-source('./scripts/primary-analyses/03_windowed_crqa.R')
+#source('./scripts/primary-analyses/02_crqa.R')
+#source('./scripts/primary-analyses/03_windowed_crqa.R')
 
 # secondary analyses
-source('./scripts/secondary-analyses/icews/02_crqa.R')
-source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
-source('./scripts/secondary-analyses/pheonix/02_crqa.R')
-source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
+#source('./scripts/secondary-analyses/icews/02_crqa.R')
+#source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
+#source('./scripts/secondary-analyses/pheonix/02_crqa.R')
+#source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
 

### 2020-05-25 manuscript.tex
Add intro, methods, and references

@@
             pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
-            pdfkeywords={keywords},
+            pdfkeywords={Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring},
             pdfborder={0 0 0},
@@
 \textsuperscript{1} Center for the Ecological Study of Perception and Action\\\textsuperscript{2} University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\authornote{
 
-Enter author note here.
-
-Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidg Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
-\keywords{keywords\newline\indent Word count: X}
+Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidge Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
+\keywords{Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+Social mobilization requires effective collective coordination.
+In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
+Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
+Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
+Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
+This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
+We conclude with a discussion of implications and applications of nonlinear methods in political science research.
 }
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+Social coordination has long been used both physically and virtually to start and carry out collective actions.
+These collective events bring individuals together and create emergent patterns of communication and action.
+Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
+From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another (Mahner \& Bunge, 1997).
+Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
+The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
+
+\hypertarget{arab-spring}{%
+\subsection{Arab Spring}\label{arab-spring}}
+
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
+His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
+His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
+The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
+These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
+The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013, @koehler2017political) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+
+\hypertarget{social-cohesion}{%
+\subsection{Social Cohesion}\label{social-cohesion}}
+
+Real-world collective action is known to bring about a sense of togetherness, also known as \enquote{collective effervescence} (Durkheim, 1995).
+This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
+Being overcome with this feeling is known to lead to violence (Collins, 2009, @spaaij2014sports).
+While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
+Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
+Just as real-world social cohesion can be quantified, the same is true for online cohesion.
+Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
+Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
+
+\hypertarget{social-media-as-a-platform-for-mobilization}{%
+\subsection{Social Media as a Platform for Mobilization}\label{social-media-as-a-platform-for-mobilization}}
+
+Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
+Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
+During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests (Vicari, 2013).
+Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
+As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
+
+\hypertarget{use-of-nonlinear-methods-in-naturally-occurring-data}{%
+\subsection{Use of Nonlinear Methods in Naturally Occurring Data}\label{use-of-nonlinear-methods-in-naturally-occurring-data}}
+
+Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
+Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
+This notion has been increasingly replaced by ideas from dynamical systems theory.
+Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts (Turvey, 2018).
+When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
+Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
+Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
+The primary methods used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and it's off-shoot, windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
+CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions (for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony (Paxton \& Dale, 2017).
+We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
+
+\hypertarget{the-present-work}{%
+\subsection{The Present Work}\label{the-present-work}}
+
+Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
+We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
+Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
+This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
+Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) and windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
+We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
+Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
+As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
+The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
 
@@
 
-\hypertarget{data-collection}{%
-\subsection{Data Collection}\label{data-collection}}
+\hypertarget{materials}{%
+\subsection{Materials}\label{materials}}
+
+\hypertarget{tweet-corpus}{%
+\subsubsection{Tweet Corpus}\label{tweet-corpus}}
+
+The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
+A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
+For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
+The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
+
+\hypertarget{event-data}{%
+\subsubsection{Event Data}\label{event-data}}
+
+Event data were obtained from the 2012 Integrated Crisis Early Warning System (ICEWS; Boschee et al., 2015).
+The event data were first filtered to remove incomplete and incorrectly formatted data.
+They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
 
@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
+\hypertarget{social-cohesion-metric}{%
+\subsubsection{Social Cohesion Metric}\label{social-cohesion-metric}}
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words' frequencies in the entire tweet corpus.
+If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
+The tweets were first sorted into ascending order by timestamp.
+They were then grouped into successive sets of five tweets.
+Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
+1-3).
+This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
+Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
 
-We used R (Version 3.6.1; R Core Team, 2019) and the R-package \emph{papaja} (Version 0.1.0.9942; Aust \& Barth, 2020) for all our analyses.
+(insert social cohesion equations here)
+
+The social cohesion calculation was performed on a subset of the corpus containing 3,855,743 English and 1,731,700 Arabic tweets.
+All hashtags and URLs were included in the analysis.
+This method is similar to that of inverse document frequency (IDF).
+For more information on IDF, see Sparck Jones (1972) and Robertson (2004).
+
+\hypertarget{icews-event-time-series}{%
+\subsubsection{ICEWS Event Time Series}\label{icews-event-time-series}}
+
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
+Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
+This well-validated coding scheme allows for numerical quantification of different event types.
+For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score (M = , SD = ).
+Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero (M = , SD = ).
+Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero (M = , SD = ).
+
+\hypertarget{analyses}{%
+\subsection{Analyses}\label{analyses}}
+
+\hypertarget{cross-recurrence-quantification-analysis}{%
+\subsubsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis}}
+
+We first used cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
+As an extension of RQA, which captures the patterns of revisited states of a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992), CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
+Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
+In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander (1959)).
+We converted each time series (e.g., Figure \#) into deciles (e.g., Figure \#) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+In CRQA, a recurrent point is when two signals share the same state.
+These shared states can be at the same time or at later points in the time series.
+A recurrence plot (RP) is the visual representation of CRQA.
+To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
+Visually analyzing these plots can help reveal patterns of structure and recurrence.
+The line y = x is known as the line of identity.
+This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
+See Figures \#-\# for examples of RPs.
+
+\hypertarget{metrics}{%
+\paragraph{Metrics}\label{metrics}}
+
+The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
+This metrics gives a general description of how frequently the time series are sharing the same states.
+In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
+Recurrent points that occur in successive moments form line structures.
+These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
+The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
+For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
+The average length of the line structures is called mean line (L).
+This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
+The longest line length is called max line (maxL).
+maxL indicates the longest instance of being \enquote{stuck} in a particular state together.
+The total number of lines is called NRLINE.
+The more lines there are, the more coordinated the system may be.
+The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
+These entropy metrics help indicate the stability and predictability of the system.
+When one of the signals gets \enquote{stuck} in a state and the other moves on to other states, this results in vertical line structures.
+The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
+For more detail on CRQA metrics, see Coco and Dale (2014).
+
+\hypertarget{parameters}{%
+\paragraph{Parameters}\label{parameters}}
+
+To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
+Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
+No normalization was done, and lines were considered two or more consecutive recurrent points.
+The Theiler window was set to zero to include points along the line of identity.
+For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2014).
+
+\hypertarget{permutation-test}{%
+\paragraph{Permutation Test}\label{permutation-test}}
+
+Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
+Using the sample function in base R (R Core Team, 2019), 1000 permuted time series were created for each of the real time series.
+A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
+CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
+This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
+Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
+Thus, RR is not included in the inferential tests.
+For more information on permutation tests, see Good (2013).
+
+\hypertarget{windowed-cross-recurrence-quantification-analysis}{%
+\subsubsection{Windowed Cross-Recurrence Quantification Analysis}\label{windowed-cross-recurrence-quantification-analysis}}
+
+We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
+In this analysis, a smaller \enquote{window} of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
+The window remains the same size and \enquote{slides} diagonally up the line of identity.
+The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+\#\#\#\# Metrics
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
+These metrics can then be plotted as a time series to visualize their evolution over time.
+For these analyses, we decided to visualize recurrence rate and determinism.
+\#\#\#\# Parameters
+In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
+First, a window size must be decided on.
+The window size will determine how many observations are used in each CRQA analysis.
+We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
+The second parameter to be chosen is a step size.
+Window step size is how far the window moves up the line of identity before conducting CRQA again.
+We chose 1 for the step size to understand how the metrics evolve from day to day.
+All other CRQA metrics remained the same as previously noted.
+\#\#\#\# Visualization
+To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
+This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
+These dynamics can then be linked to other external events.
+See Figures \#\#-\#\# for examples.
+\#\#\#\# Permutation Test
+To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
+Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
+The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+\leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
+Boschee, E., Lautenschlager, J., O'Brien, S., Shellman, S., Starz, J., \& Ward, M.
+(2015).
+\emph{ICEWS Coded Event Data} (Version V27) {[}Data set{]}.
+Harvard Dataverse.
+\url{https://doi.org/10.7910/DVN/28075}
+
+\leavevmode\hypertarget{ref-collins2009violence}{}%
+Collins, R. (2009). \emph{Violence: A micro-sociological theory}. Princeton University Press.
+
+\leavevmode\hypertarget{ref-durkheim1995elementary}{}%
+Durkheim, E.
+(1995).
+The elementary forms of religious life, terj.
+Karen e.
+Fields.
+\emph{New York: Free Press.
+East, ML, \& Hofer, H.(1991).
+Loud Calling in a Female Dominated Mammalian Society, II: Behavioural Contexts and Functions of Whooping of Spotted Hyenas, Crocuta Crocuta.
+Animal Behaviour}, \emph{42}, 651669.
+
+\leavevmode\hypertarget{ref-fusaroli2014analyzing}{}%
+Fusaroli, R., Konvalinka, I., \& Wallot, S.
+(2014).
+Analyzing social interactions: The promises and challenges of using cross recurrence quantification analysis.
+In \emph{Translational recurrences} (pp.
+137--155).
+Springer.
+
+\leavevmode\hypertarget{ref-grenander1959probability}{}%
+Grenander, U. (1959). \emph{Probability and statistics: The harald cramer volume}. Alqvist \& Wiksell.
+
+\leavevmode\hypertarget{ref-koehler2017political}{}%
+Koehler, K. (2017). Political militaries in popular uprisings: A comparative perspective on the arab spring. \emph{International Political Science Review}, \emph{38}(3), 363--377.
+
+\leavevmode\hypertarget{ref-lutterbeck2013arab}{}%
+Lutterbeck, D. (2013). Arab uprisings, armed forces, and civil--military relations. \emph{Armed Forces \& Society}, \emph{39}(1), 28--52.
+
+\leavevmode\hypertarget{ref-mahner1997foundations}{}%
+Mahner, M., \& Bunge, M. (1997). \emph{Foundations of biophilosophy}. Springer Science \& Business Media.
+
+\leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
+Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.
 
@@
 
+\leavevmode\hypertarget{ref-spaaij2014sports}{}%
+Spaaij, R. (2014). Sports crowd violence: An interdisciplinary synthesis. \emph{Aggression and Violent Behavior}, \emph{19}(2), 146--155.
+
+\leavevmode\hypertarget{ref-turvey2018lectures}{}%
+Turvey, M. T. (2018). \emph{Lectures on perception: An ecological perspective}. Routledge.
+
+\leavevmode\hypertarget{ref-vicari2013public}{}%
+Vicari, S. (2013). Public reasoning around social contention: A case study of twitter use in the italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
+
+\leavevmode\hypertarget{ref-webber1994dynamical}{}%
+Webber Jr, C. L., \& Zbilut, J. P. (1994). Dynamical assessment of physiological systems and states using recurrence plot strategies. \emph{Journal of Applied Physiology}, \emph{76}(2), 965--973.
+
+\leavevmode\hypertarget{ref-webber2005recurrence}{}%
+Webber Jr, C.
+L., \& Zbilut, J.
+P.
+(2005).
+Recurrence quantification analysis of nonlinear dynamical systems.
+\emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences}, \emph{94}(2005), 26--94.
+
+\leavevmode\hypertarget{ref-zbilut1998detecting}{}%
+Zbilut, J.
+P., Giuliani, A., \& Webber Jr, C.
+L.
+(1998).
+Detecting deterministic signals in exceptionally noisy environments using cross-recurrence quantification.
+\emph{Physics Letters A}, \emph{246}(1-2), 122--128.
+
+\leavevmode\hypertarget{ref-zbilut1992embeddings}{}%
+Zbilut, J. P., \& Webber Jr, C. L. (1992). Embeddings and delays as derived from quantification of recurrence plots. \emph{Physics Letters A}, \emph{171}(3-4), 199--203.
+
 \endgroup

### 2020-05-25 manuscript.Rmd
Tweaks to authorship info

@@
     affiliation   : "1,2,*"
-  - name          : "Lead C. Windsor"
+  - name          : "Leah C. Windsor"
     affiliation   : "3,*"
@@
   - id            : "1"
-    institution   : "Center for the Ecological Study of Perception and Action"
+    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
   - id            : "2"
-    institution   : "University of Connecticut"
+    institution   : "Department of Psychological Sciences, University of Connecticut"
   - id            : "3"

### 2020-05-25 manuscript.tex
Update tex to match Rmd

@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[english,man]{apa6}
+\documentclass[
+  english,
+  man]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
   \IfFileExists{parskip.sty}{%
@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
+  pdflang={en-EN},
   pdfkeywords={Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 % Manuscript styling
@@
 \shorttitle{Arab Spring}
-\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Lead C. Windsor\textsuperscript{3,*}}
+\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Leah C. Windsor\textsuperscript{3,*}}
 \affiliation{
 \vspace{0.5cm}
-\textsuperscript{1} Center for the Ecological Study of Perception and Action\\\textsuperscript{2} University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
+\textsuperscript{1} Center for the Ecological Study of Perception and Action, University of Connecticut\\\textsuperscript{2} Department of Psychological Sciences, University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
 \authornote{
@@
 \usepackage{csquotes}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
 \fi
@@
 These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013, @koehler2017political) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013, p.
+@koehler2017political) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
 
@@
 This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence (Collins, 2009, @spaaij2014sports).
+Being overcome with this feeling is known to lead to violence (Collins, 2009, p.
+@spaaij2014sports).
 While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
@@
 
-The social cohesion calculation was performed on a subset of the corpus containing 3,855,743 English and 1,731,700 Arabic tweets.
+The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
 All hashtags and URLs were included in the analysis.

### 2020-05-25 manuscript.tex
Minor header typo fix

@@
 The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
-\#\#\#\# Metrics
+
+\hypertarget{metrics-1}{%
+\paragraph{Metrics}\label{metrics-1}}
+
 Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
@@
 For these analyses, we decided to visualize recurrence rate and determinism.
-\#\#\#\# Parameters
+
+\hypertarget{parameters-1}{%
+\paragraph{Parameters}\label{parameters-1}}
+
 In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
@@
 All other CRQA metrics remained the same as previously noted.
-\#\#\#\# Visualization
+
+\hypertarget{visualization}{%
+\paragraph{Visualization}\label{visualization}}
+
 To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
@@
 See Figures \#\#-\#\# for examples.
-\#\#\#\# Permutation Test
+
+\hypertarget{permutation-test-1}{%
+\paragraph{Permutation Test}\label{permutation-test-1}}
+
 To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.

### 2020-05-26 manuscript.Rmd
Turn on caching
Minor header typo fix
Add primary CRQA code and results

@@
 # clear the workspace
-#rm(list=ls())
+rm(list=ls())
 
@@
 
-# references file
-#r_refs("references.bib")
+# turn on caching
+knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
 
 # create subdirectories
-# dir.create("./data/raw") # load three data files here
-# dir.create("./data/formatted/primary")
-# dir.create("./data/formatted/secondary")
-# dir.create("./results/primary/crqa")
-# dir.create("./results/primary/windowed-crqa")
-# dir.create("./results/secondary/icews/crqa/source_target")
-# dir.create("./results/secondary/icews/crqa/target")
-# dir.create("./results/secondary/icews/windowed-crqa/source_target")
-# dir.create("./results/secondary/icews/windowed-crqa/target")
-# dir.create("./results/secondary/pheonix/crqa/source_target")
-# dir.create("./results/secondary/pheonix/crqa/target")
-# dir.create("./results/secondary/pheonix/windowed-crqa/source_target")
-# dir.create("./results/secondary/pheonix/windowed-crqa/target")
+dir.create("./data/raw") # load three data files here
+dir.create("./data/formatted/primary")
+dir.create("./data/formatted/secondary")
+dir.create("./results/primary/crqa")
+dir.create("./results/primary/windowed-crqa")
+dir.create("./results/secondary/icews/crqa/source_target")
+dir.create("./results/secondary/icews/crqa/target")
+dir.create("./results/secondary/icews/windowed-crqa/source_target")
+dir.create("./results/secondary/icews/windowed-crqa/target")
+dir.create("./results/secondary/pheonix/crqa/source_target")
+dir.create("./results/secondary/pheonix/crqa/target")
+dir.create("./results/secondary/pheonix/windowed-crqa/source_target")
+dir.create("./results/secondary/pheonix/windowed-crqa/target")
 
@@
 # format the data
-#source('./scripts/primary-analyses/01_formatting_data.R')
-#source('./scripts/secondary-analyses/icews/01_formatting_data.R')
-#source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')
+source('./scripts/primary-analyses/01_formatting_data.R')
+source('./scripts/secondary-analyses/icews/01_formatting_data.R')
+source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')
 
@@
 These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab, @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
 
@@
 This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence [@collins2009violence, @spaaij2014sports].
+Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
 While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
@@
 This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see Sparck Jones (1972) and Robertson (2004).
+For more information on IDF, see @jones1972statistical and @robertson2004understanding.
 
@@
 This well-validated coding scheme allows for numerical quantification of different event types.
-For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score (M = , SD = ).
-Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero (M = , SD = ).
-Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero (M = , SD = ).
+For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
+Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
+Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
 
@@
 Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.
-Nyquist frequency in signal processing; @grenander1959probability).
-We converted each time series (e.g., Figure #) into deciles (e.g., Figure #) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system [cf.
+Nyquist frequency in signal processing; @grenander1959probability].
+We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
 In CRQA, a recurrent point is when two signals share the same state.
 These shared states can be at the same time or at later points in the time series.
+
+#### Visualization
 A recurrence plot (RP) is the visual representation of CRQA.
@@
 This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures #-# for examples of RPs.
+See Figures 3-5 for examples of RPs.
 
@@
 The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see Coco and Dale (2014).
+For more detail on CRQA metrics, see @R-crqa.
 
@@
 The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2014).
+For more details on the CRQA parameters and how they impact the analysis, see @R-crqa.
 
@@
 Thus, RR is not included in the inferential tests.
-For more information on permutation tests, see Good (2013).
+For more information on permutation tests, see @good2013permutation.
 
@@
 The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+
 #### Metrics
@@
 For these analyses, we decided to visualize recurrence rate and determinism.
+
 #### Parameters
@@
 All other CRQA metrics remained the same as previously noted.
+
 #### Visualization
@@
 See Figures ##-## for examples.
+
 #### Permutation Test
@@
 # Results
+```{r primary-crqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
 
-```{r analyses, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+# run primary crq analysis
+source('./scripts/primary-analyses/02_crqa.R')
 
-# primary analyses
-#source('./scripts/primary-analyses/02_crqa.R')
-#source('./scripts/primary-analyses/03_windowed_crqa.R')
+# read in metric names
+metrics <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
-# secondary analyses
-#source('./scripts/secondary-analyses/icews/02_crqa.R')
-#source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
-#source('./scripts/secondary-analyses/pheonix/02_crqa.R')
-#source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
+# read in metrics from crq analyses (target filtered)
+metrics_all_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (target filtered)
+sig_all_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+
+# read in metrics from crq analyses (source and target filtered)
+metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (source and target filtered)
+sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 
-```{r images}
-# code block to insert an image
+```{r raw-ts, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Example of pre-processed data.'}
+
+# read in processed data
+data <- read.csv("./data/formatted/primary/formatted_data.csv", header = TRUE)
+
+raw_ts_example <- ggplot(data, aes(x= as.Date(Date), y=all_events_target)) +
+  geom_point() +
+  geom_line() +
+  xlab("Date") +
+  ylab("Count of events")
+ggsave("./results/primary/tally_ts_example.png")
+
+# call the image
+knitr::include_graphics("./results/primary/tally_ts_example.png")
 
@@
 
+```{r deciled-ts, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Example of deciled data.'}
+
+# plot the deciles time series and save
+deciled_ts_example <- ggplot(data, aes(x= as.Date(Date), y=all_deciles_target)) +
+  geom_point() +
+  geom_line() +
+  xlab("Date") +
+  ylab("Count of events (deciles)")
+ggsave("./results/primary/deciled_ts_example.png")
+
+# call the image
+knitr::include_graphics("./results/primary/deciled_ts_example.png")
+
+```
+
+## Cross-Recurrence Quantification Analysis
+CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+
+### Syria as Target
+A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
+All other metrics were non-significant (Figure 3; Table 1).
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
+All other metrics were non-significant (Figure 5; Table 1).
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+
+```{r primary-crqa-table-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+target_results <- as.data.frame(cbind(metrics,
+                                      metrics_all_targ, 
+                                      sig_all_targ, 
+                                      metrics_pos_targ, 
+                                      sig_pos_targ, 
+                                      metrics_neg_targ, 
+                                      sig_neg_targ), stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+target_results[,numerics] <- sapply(target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(target_results[,7]))
+
+target_results <- cbind(target_results, stars_all, stars_pos, stars_neg)
+target_results <- target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(target_results, caption = "CRQA results for target only data.")
+
+```
+
+```{r plot-rp-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/target/rp-all_events.png")
+
+```
+
+```{r plot-rp-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/target/rp-pos_events.png")
+
+```
+
+```{r plot-rp-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/target/rp-neg_events.png")
+
+```
+
+### Syria as Source and Target
+A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
+All other metrics were non-significant (Figure 6; Table 2).
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
+All other metrics were non-significant (Figure 8; Table 2).
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+
+```{r primary-table-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+source_target_results <- as.data.frame(cbind(metrics,
+                                      metrics_all_source_targ, 
+                                      sig_all_source_targ, 
+                                      metrics_pos_source_targ, 
+                                      sig_pos_source_targ, 
+                                      metrics_neg_source_targ, 
+                                      sig_neg_source_targ), stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+source_target_results[,numerics] <- sapply(source_target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(source_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(source_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(source_target_results[,7]))
+
+source_target_results <- cbind(source_target_results, stars_all, stars_pos, stars_neg)
+source_target_results <- source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(source_target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(source_target_results, caption = "CRQA results for source and target data.")
+
+```
+
+```{r plot-rp-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/source_target/rp-all_events.png")
+
+```
+
+```{r plot-rp-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/source_target/rp-pos_events.png")
+
+```
+
+```{r plot-rp-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/crqa/source_target/rp-neg_events.png")
+
+```
+
+## Windowed Cross-Recurrence Quantification Analysis
+WCRQA was performed using the crqa package [@R-crqa] for R [@R-base].
+Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
+In the plots (see Figures #-#), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+For social cohesion and counts of all and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 36th through 46th windows.
+These windows span from May 4th, 2012 to May 28th, 2012.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure #).
+
 # Discussion
+In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
+We examined how social mobilization both virtually and physically evolve over time in tandem.
+Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
+
+## Cross-Recurrence Quantification Analysis
+The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
+The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
+The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
+The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
+By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 36, or May 4th, 2012.
+To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
+
+## Windowed-Recurrence Quantification Analysis
+The time period of differing dynamics, from observation 36 through 46, appears to be captured by WCRQA of social cohesion and count of negative events with window size 14 for both RR (Figure 8) and DET (Figure 11).
+The amount of recurrence and determinism for these periods consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
+During this time period, Syria underwent the “Siege of Homs” on May 5th, where fleets of tanks were sent into Homs and over 300 individuals were arrested.
+On May 6th, demonstrators began protesting after Friday prayers, leading to retaliation violence by the Syrian army, leaving sixteen civilians and eleven Syrian army men dead.
+That day, tens of thousands of individuals marched in an attempt to meet the army peacefully and bring supplies to Deraa, but were refused entrance.
+This day became known as the “Day of Defiance” or the “Friday of Challenge.” Syria also faced the “Siege of Baniyas” on May 7th, “Siege of Tafas” on May 8th, “Friday of Free Women” on May 13th, “Siege of Talkalakh” on May 14th, the “Israel border demonstrations” on May 15th, “Friday of Azady (freedom)” on May 20th, “Home Protectors’ Friday” on May 27th, and the “Siege of Rastan and Talbiseh” on May 28th.
+The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
+The frequency of negative events is also captured by the mode ICEWS rating for each day.
+In Figure 12, observed days from 33 to 47, or from May 1st, 2012 to May 15th, 2012, are largely overcome by extreme negative events of ICEWS rating -10.
+These directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, RR (Figure 7) and DET (Figure 10) were both within chance.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter.
+
+## Conclusion
+Given the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
+If consistent across other civil wars, these results have serious implications for monitoring global movements.
+While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
+By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
+Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
 
@@
 
+# Appendix
+Results for CRQA and Windowed CRQA on Pheonix data.
+```{r secondary-crqa}
+
+# run crqa on sextiled icews data
+# source('./scripts/secondary-analyses/icews/02_crqa.R')
+
+# run crqa on sextiled pheonix data
+# source('./scripts/secondary-analyses/pheonix/02_crqa.R')
+
+```
+
+```{r secondary-windowed-crqa}
+
+# run windowed crqa on sextiled icews data
+# source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
+
+# run windowed crqa on sextiled pheonix data
+# source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
+
+```
+
 \begingroup

### 2020-05-26 manuscript.tex
Add primary CRQA code and results

--- 2020-05-25 manuscript.tex
@@
 \urlstyle{same}  % don't use monospace font for urls
+\usepackage{longtable,booktabs}
+% Fix footnotes in tables (requires footnote package)
+\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
 \usepackage{graphicx,grffile}
@@
 These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013, @koehler2017political) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
 
@@
 This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence (Collins, 2009, @spaaij2014sports).
+Being overcome with this feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
 While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
@@
 
-The social cohesion calculation was performed on a subset of the corpus containing 3,855,743 English and 1,731,700 Arabic tweets.
+The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
 All hashtags and URLs were included in the analysis.
 This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see Sparck Jones (1972) and Robertson (2004).
+For more information on IDF, see Jones (1972) and Robertson (2004).
 
@@
 Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander (1959)).
-We converted each time series (e.g., Figure \#) into deciles (e.g., Figure \#) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
+We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
 In CRQA, a recurrent point is when two signals share the same state.
 These shared states can be at the same time or at later points in the time series.
+
+\hypertarget{visualization}{%
+\paragraph{Visualization}\label{visualization}}
+
 A recurrence plot (RP) is the visual representation of CRQA.
@@
 This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures \#-\# for examples of RPs.
+See Figures 3-5 for examples of RPs.
 
@@
 The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see Coco and Dale (2014).
+For more detail on CRQA metrics, see Coco and Dale (2018).
 
@@
 The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2014).
+For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2018).
 
@@
 All other CRQA metrics remained the same as previously noted.
-\#\#\#\# Visualization
+
+\hypertarget{visualization-1}{%
+\paragraph{Visualization}\label{visualization-1}}
+
 To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
@@
 
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/tally_ts_example} \caption{Example of pre-processed data.}\label{fig:raw-ts}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/deciled_ts_example} \caption{Example of deciled data.}\label{fig:deciled-ts}
+\end{figure}
+
+\hypertarget{cross-recurrence-quantification-analysis-1}{%
+\subsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis-1}}
+
+CRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+
+\hypertarget{syria-as-target}{%
+\subsubsection{Syria as Target}\label{syria-as-target}}
+
+A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
+All other metrics were non-significant (Figure 3; Table 1).
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
+All other metrics were non-significant (Figure 5; Table 1).
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 30.130 & 0.000 & *** & 21.266 & 0.124 & & 25.081 & 0.002 & **\tabularnewline
+NRLINE & 85.000 & 0.000 & *** & 61.000 & 0.162 & & 70.000 & 0.008 & **\tabularnewline
+maxL & 4.000 & 0.046 & * & 4.000 & 0.057 & . & 5.000 & 0.004 & **\tabularnewline
+L & 2.176 & 0.073 & . & 2.148 & 0.193 & & 2.214 & 0.024 & *\tabularnewline
+ENTR & 0.493 & 0.058 & . & 0.438 & 0.154 & & 0.538 & 0.036 & *\tabularnewline
+rENTR & 0.449 & 0.326 & & 0.399 & 0.444 & & 0.388 & 0.527 &\tabularnewline
+LAM & 32.410 & 0.016 & * & 21.591 & 0.252 & & 26.052 & 0.102 &\tabularnewline
+TT & 2.187 & 0.186 & & 2.293 & 0.091 & . & 2.368 & 0.036 & *\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.}\label{fig:plot-rp-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.}\label{fig:plot-rp-targ-neg}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target}}
+
+A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
+All other metrics were non-significant (Figure 6; Table 2).
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
+All other metrics were non-significant (Figure 8; Table 2).
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 28.222 & 0.000 & *** & 23.328 & 0.013 & * & 23.443 & 0.011 & *\tabularnewline
+NRLINE & 83.000 & 0.000 & *** & 66.000 & 0.021 & * & 65.000 & 0.023 & *\tabularnewline
+maxL & 3.000 & 0.429 & & 4.000 & 0.049 & * & 4.000 & 0.048 & *\tabularnewline
+L & 2.084 & 0.708 & & 2.167 & 0.127 & & 2.200 & 0.037 & *\tabularnewline
+ENTR & 0.289 & 0.700 & & 0.475 & 0.108 & & 0.523 & 0.033 & *\tabularnewline
+rENTR & 0.417 & 0.433 & & 0.432 & 0.381 & & 0.476 & 0.225 &\tabularnewline
+LAM & 32.790 & 0.008 & ** & 28.548 & 0.023 & * & 21.639 & 0.201 &\tabularnewline
+TT & 2.284 & 0.085 & . & 2.333 & 0.051 & . & 2.129 & 0.298 &\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-rp-source-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-rp-source-targ-neg}
+\end{figure}
+
+\hypertarget{windowed-cross-recurrence-quantification-analysis-1}{%
+\subsection{Windowed Cross-Recurrence Quantification Analysis}\label{windowed-cross-recurrence-quantification-analysis-1}}
+
+WCRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019).
+Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
+In the plots (see Figures \#-\#), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+For social cohesion and counts of all and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 36th through 46th windows.
+These windows span from May 4th, 2012 to May 28th, 2012.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \#).
+
 \hypertarget{discussion}{%
 \section{Discussion}\label{discussion}}
+
+In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
+We examined how social mobilization both virtually and physically evolve over time in tandem.
+Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
+
+\hypertarget{cross-recurrence-quantification-analysis-2}{%
+\subsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis-2}}
+
+The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
+The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
+The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
+The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
+By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 36, or May 4th, 2012.
+To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
+
+\hypertarget{windowed-recurrence-quantification-analysis}{%
+\subsection{Windowed-Recurrence Quantification Analysis}\label{windowed-recurrence-quantification-analysis}}
+
+The time period of differing dynamics, from observation 36 through 46, appears to be captured by WCRQA of social cohesion and count of negative events with window size 14 for both RR (Figure 8) and DET (Figure 11).
+The amount of recurrence and determinism for these periods consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
+During this time period, Syria underwent the \enquote{Siege of Homs} on May 5th, where fleets of tanks were sent into Homs and over 300 individuals were arrested.
+On May 6th, demonstrators began protesting after Friday prayers, leading to retaliation violence by the Syrian army, leaving sixteen civilians and eleven Syrian army men dead.
+That day, tens of thousands of individuals marched in an attempt to meet the army peacefully and bring supplies to Deraa, but were refused entrance.
+This day became known as the \enquote{Day of Defiance} or the \enquote{Friday of Challenge.} Syria also faced the \enquote{Siege of Baniyas} on May 7th, \enquote{Siege of Tafas} on May 8th, \enquote{Friday of Free Women} on May 13th, \enquote{Siege of Talkalakh} on May 14th, the \enquote{Israel border demonstrations} on May 15th, \enquote{Friday of Azady (freedom)} on May 20th, \enquote{Home Protectors' Friday} on May 27th, and the \enquote{Siege of Rastan and Talbiseh} on May 28th.
+The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
+The frequency of negative events is also captured by the mode ICEWS rating for each day.
+In Figure 12, observed days from 33 to 47, or from May 1st, 2012 to May 15th, 2012, are largely overcome by extreme negative events of ICEWS rating -10.
+These directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, RR (Figure 7) and DET (Figure 10) were both within chance.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter.
+
+\hypertarget{conclusion}{%
+\subsection{Conclusion}\label{conclusion}}
+
+Given the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
+If consistent across other civil wars, these results have serious implications for monitoring global movements.
+While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
+By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
+Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
 
@@
 \section{References}\label{references}}
+
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
+Results for CRQA and Windowed CRQA on Pheonix data.
 
@@
 
+\leavevmode\hypertarget{ref-R-crqa}{}%
+Coco, M. I., \& Dale, R. (2018). \emph{Crqa: Cross-recurrence quantification analysis for categorical and continuous time-series}. Retrieved from \url{https://CRAN.R-project.org/package=crqa}
+
 \leavevmode\hypertarget{ref-collins2009violence}{}%
@@
 \leavevmode\hypertarget{ref-durkheim1995elementary}{}%
-Durkheim, E.
-(1995).
-The elementary forms of religious life, terj.
-Karen e.
-Fields.
-\emph{New York: Free Press.
-East, ML, \& Hofer, H.(1991).
-Loud Calling in a Female Dominated Mammalian Society, II: Behavioural Contexts and Functions of Whooping of Spotted Hyenas, Crocuta Crocuta.
-Animal Behaviour}, \emph{42}, 651669.
+Durkheim, E. (1995). The elementary forms of religious life, terj. Karen e. Fields. \emph{New York: Free Press.}, \emph{42}, 651669.
 
@@
 
+\leavevmode\hypertarget{ref-good2013permutation}{}%
+Good, P. (2013). \emph{Permutation tests: A practical guide to resampling methods for testing hypotheses}. Springer Science \& Business Media.
+
 \leavevmode\hypertarget{ref-grenander1959probability}{}%
 Grenander, U. (1959). \emph{Probability and statistics: The harald cramer volume}. Alqvist \& Wiksell.
+
+\leavevmode\hypertarget{ref-jones1972statistical}{}%
+Jones, K. S. (1972). A statistical interpretation of term specificity and its application in retrieval. \emph{Journal of Documentation}.
 
@@
 R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-robertson2004understanding}{}%
+Robertson, S. (2004). Understanding inverse document frequency: On theoretical arguments for idf. \emph{Journal of Documentation}.
 

### 2020-05-26 scripts/libraries_and_functions.r

@@ -11,7 +11,10 @@ required_packages = c(
   'crqa',
   'tidyr',
   'modeest',
-  'papaja'
+  'papaja',
+  'pander',
+  'gtools',
+  'knitr'
 )
 
 # load required packages

### 2020-05-26 scripts/required_packages.r

@@ -11,7 +11,10 @@ required_packages = c(
   'crqa',
   'tidyr',
   'modeest',
-  'papaja'
+  'papaja',
+  'pander',
+  'gtools',
+  'knitr'
 )
 
 # install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)

### 2020-05-26 manuscript.Rmd
Add primary windowed CRQA code and results

@@
 These dynamics can then be linked to other external events.
-See Figures ##-## for examples.
+See Figures 9-14 and 16-21 for examples.
 
@@
 ## Windowed Cross-Recurrence Quantification Analysis
+```{r primary-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run primary crq analysis
+source('./scripts/primary-analyses/03_windowed_crqa.R')
+
+```
+
 WCRQA was performed using the crqa package [@R-crqa] for R [@R-base].
 Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures #-#), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-For social cohesion and counts of all and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 36th through 46th windows.
-These windows span from May 4th, 2012 to May 28th, 2012.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure #).
+In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+The trend lines are plotted in blue.
+
+### Syria as Target
+
+```{r plot-RR-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Mode ICEWS event per day.'}
+
+mode_plot <- ggplot(data, aes(x= as.Date(Date), y=mode_source_target)) +
+                    geom_point() +
+                    geom_line() +
+                    xlab("Date") +
+                    ylab("Mode ICEWS event")
+ggsave("./results/primary/mode_ts_plot.png")
+
+# call the image
+knitr::include_graphics("./results/primary/mode_ts_plot.png")
+
+```
+
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
+Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
+For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```
+
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th thorugh 46th window (Figure 16).
+Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
+For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
+These windows span from May 3rd, 2012 to May 14th, 2012.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 9), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
 
@@
 The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
-By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 36, or May 4th, 2012.
+By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
 To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).

### 2020-05-26 manuscript.tex
Add primary windowed CRQA code and results

@@
 Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures \#-\#), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-For social cohesion and counts of all and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 36th through 46th windows.
-These windows span from May 4th, 2012 to May 28th, 2012.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \#).
+In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+The trend lines are plotted in blue.
+
+\hypertarget{syria-as-target-1}{%
+\subsubsection{Syria as Target}\label{syria-as-target-1}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/mode_ts_plot} \caption{Mode ICEWS event per day.}\label{fig:plot-mode-event}
+\end{figure}
+
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
+Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
+For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
+
+\hypertarget{syria-as-source-and-target-1}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-1}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
+\end{figure}
+
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th thorugh 46th window (Figure 16).
+Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
+For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
+These windows span from May 3rd, 2012 to May 14th, 2012.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 9), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
 

### 2020-05-27 manuscript.Rmd
Add last of primary analyses, interpretations, and secondary CRQ analyses

@@
 These windows span from May 3rd, 2012 to May 14th, 2012.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 9), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
 
@@
 ## Cross-Recurrence Quantification Analysis
+### Syria as Target
 The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
@@
 The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
-By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
+
+### Syria as Source and Target
+By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
+These additional observations are times where Syria initiated an event with another country.
+Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
+The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
+Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
+Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on.
+We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
+The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
+By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
 To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
@@
 ## Windowed-Recurrence Quantification Analysis
-The time period of differing dynamics, from observation 36 through 46, appears to be captured by WCRQA of social cohesion and count of negative events with window size 14 for both RR (Figure 8) and DET (Figure 11).
-The amount of recurrence and determinism for these periods consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-During this time period, Syria underwent the “Siege of Homs” on May 5th, where fleets of tanks were sent into Homs and over 300 individuals were arrested.
-On May 6th, demonstrators began protesting after Friday prayers, leading to retaliation violence by the Syrian army, leaving sixteen civilians and eleven Syrian army men dead.
-That day, tens of thousands of individuals marched in an attempt to meet the army peacefully and bring supplies to Deraa, but were refused entrance.
-This day became known as the “Day of Defiance” or the “Friday of Challenge.” Syria also faced the “Siege of Baniyas” on May 7th, “Siege of Tafas” on May 8th, “Friday of Free Women” on May 13th, “Siege of Talkalakh” on May 14th, the “Israel border demonstrations” on May 15th, “Friday of Azady (freedom)” on May 20th, “Home Protectors’ Friday” on May 27th, and the “Siege of Rastan and Talbiseh” on May 28th.
+### Syria as Target
+The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
+The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
 The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-The frequency of negative events is also captured by the mode ICEWS rating for each day.
-In Figure 12, observed days from 33 to 47, or from May 1st, 2012 to May 15th, 2012, are largely overcome by extreme negative events of ICEWS rating -10.
-These directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, RR (Figure 7) and DET (Figure 10) were both within chance.
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
+These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.
+
+### Syria as Source and Target
+WCRQ analyses of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
+Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
+WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
+This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
+Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
 
@@
 
-# Appendix
-Results for CRQA and Windowed CRQA on Pheonix data.
-```{r secondary-crqa}
-
-# run crqa on sextiled icews data
-# source('./scripts/secondary-analyses/icews/02_crqa.R')
-
-# run crqa on sextiled pheonix data
-# source('./scripts/secondary-analyses/pheonix/02_crqa.R')
-
-```
-
-```{r secondary-windowed-crqa}
-
-# run windowed crqa on sextiled icews data
-# source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
-
-# run windowed crqa on sextiled pheonix data
-# source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
-
-```
-
 \begingroup
@@
 \endgroup
+
+\newpage
+
+# Appendix A
+
+Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Pheonix Event Data [@illinoisdatabankIDB-2796521].
+After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Pheonix data.
+As a results, sextiles were used for these analyses.
+For comparison, the filtered ICEWS data was also transformed into sextiles.
+
+## CRQA for Pheonix data in sextiles
+```{r secondary-crqa-phoenix, , echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run crqa on sextiled pheonix data
+source('./scripts/secondary-analyses/pheonix/02_crqa.R')
+
+# read in metric names
+pheonix_metrics <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+
+# read in metrics from crq analyses (target filtered)
+pheonix_metrics_all_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+pheonix_metrics_pos_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+pheonix_metrics_neg_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (target filtered)
+pheonix_sig_all_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
+pheonix_sig_pos_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+pheonix_sig_neg_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+
+# read in metrics from crq analyses (source and target filtered)
+pheonix_metrics_all_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+pheonix_metrics_pos_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+pheonix_metrics_neg_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (source and target filtered)
+pheonix_sig_all_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
+pheonix_sig_pos_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+pheonix_sig_neg_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+
+```
+
+```{r secondary-crqa-table-pheonix-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+pheonix_target_results <- as.data.frame(cbind(pheonix_metrics,
+                                      pheonix_metrics_all_targ, 
+                                      pheonix_sig_all_targ, 
+                                      pheonix_metrics_pos_targ, 
+                                      pheonix_sig_pos_targ, 
+                                      pheonix_metrics_neg_targ, 
+                                      pheonix_sig_neg_targ), 
+                                      stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+pheonix_target_results[,numerics] <- sapply(pheonix_target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(pheonix_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(pheonix_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(pheonix_target_results[,7]))
+
+pheonix_target_results <- cbind(pheonix_target_results, stars_all, stars_pos, stars_neg)
+pheonix_target_results <- pheonix_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(pheonix_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(pheonix_target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(pheonix_target_results, caption = "CRQA results for target only Pheonix data.")
+
+```
+
+```{r primary-table-pheonix-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+pheonix_source_target_results <- as.data.frame(cbind(pheonix_metrics,
+                                      pheonix_metrics_all_source_targ, 
+                                      pheonix_sig_all_source_targ, 
+                                      pheonix_metrics_pos_source_targ, 
+                                      pheonix_sig_pos_source_targ, 
+                                      pheonix_metrics_neg_source_targ, 
+                                      pheonix_sig_neg_source_targ), 
+                                      stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+pheonix_source_target_results[,numerics] <- sapply(pheonix_source_target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(pheonix_source_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(pheonix_source_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(pheonix_source_target_results[,7]))
+
+pheonix_source_target_results <- cbind(pheonix_source_target_results, stars_all, stars_pos, stars_neg)
+pheonix_source_target_results <- pheonix_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(pheonix_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(pheonix_source_target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(pheonix_source_target_results, caption = "CRQA results for source and target Pheonix data.")
+
+```
+CRQ analyses for sextiled Pheonix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
+Negative events were not coupled with social cohesion irrepective of filtering.
+
+## CRQA for ICEWS data in sextiles
+```{r secondary-crqa-icews, , echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run crqa on sextiled icews data
+source('./scripts/secondary-analyses/icews/02_crqa.R')
+
+# read in metric names
+icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+
+# read in metrics from crq analyses (target filtered)
+icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (target filtered)
+icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
+icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+
+# read in metrics from crq analyses (source and target filtered)
+icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+
+# read in signficiance from permutation tests (source and target filtered)
+icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
+icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+
+```
+
+```{r secondary-crqa-table-icews-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+icews_target_results <- as.data.frame(cbind(icews_metrics,
+                                      icews_metrics_all_targ, 
+                                      icews_sig_all_targ, 
+                                      icews_metrics_pos_targ, 
+                                      icews_sig_pos_targ, 
+                                      icews_metrics_neg_targ, 
+                                      icews_sig_neg_targ), 
+                                      stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+icews_target_results[,numerics] <- sapply(icews_target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(icews_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(icews_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(icews_target_results[,7]))
+
+icews_target_results <- cbind(icews_target_results, stars_all, stars_pos, stars_neg)
+icews_target_results <- icews_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(icews_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(icews_target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(icews_target_results, caption = "CRQA results for target only ICEWS data.")
+
+```
+
+```{r primary-table-icews-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+# bind metrics and significance results
+icews_source_target_results <- as.data.frame(cbind(icews_metrics,
+                                      icews_metrics_all_source_targ, 
+                                      icews_sig_all_source_targ, 
+                                      icews_metrics_pos_source_targ, 
+                                      icews_sig_pos_source_targ, 
+                                      icews_metrics_neg_source_targ, 
+                                      icews_sig_neg_source_targ), 
+                                      stringsAsFactors = FALSE)
+
+# covert to numerics for rounding
+numerics <- c(2:7)
+icews_source_target_results[,numerics] <- sapply(icews_source_target_results[,numerics],as.numeric)
+
+# add significance stars
+stars_all <- as.data.frame(stars.pval(icews_source_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(icews_source_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(icews_source_target_results[,7]))
+
+icews_source_target_results <- cbind(icews_source_target_results, stars_all, stars_pos, stars_neg)
+icews_source_target_results <- icews_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+
+# give intuitive names
+colnames(icews_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+
+# exclude row names
+rownames(icews_source_target_results) <- NULL
+
+# set to not split table and round to two decimal places
+panderOptions("table.split.table", Inf) 
+panderOptions('round', 3)
+panderOptions('keep.trailing.zeros', TRUE)
+
+# style for Rmd
+panderOptions("table.style", "rmarkdown")
+
+# build table
+pander(icews_source_target_results, caption = "CRQA results for source and target ICEWS data.")
+
+```
+CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
+Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
+The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.

### 2020-05-27 manuscript.tex
Add last of primary analyses, interpretations, and secondary CRQ analyses

@@
 These dynamics can then be linked to other external events.
-See Figures \#\#-\#\# for examples.
+See Figures 9-14 and 16-21 for examples.
 
@@
 
+\hypertarget{syria-as-target-2}{%
+\subsubsection{Syria as Target}\label{syria-as-target-2}}
+
 The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
@@
 The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
-By visual inspection of the recurrence plots (RPs; Figures 3-5), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
+
+\hypertarget{syria-as-source-and-target-2}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-2}}
+
+By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
 To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
@@
 \subsection{Windowed-Recurrence Quantification Analysis}\label{windowed-recurrence-quantification-analysis}}
+
+\hypertarget{syria-as-target-3}{%
+\subsubsection{Syria as Target}\label{syria-as-target-3}}
 
@@
 This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter.
+
+\hypertarget{syria-as-source-and-target-3}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-3}}
 
@@
 
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-Results for CRQA and Windowed CRQA on Pheonix data.
-
 \begingroup
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
+Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
+(2020).
+\emph{Cline center historical phoenix event data.
+Cline center for advanced social research.
+V1.3.0.
+May 4} {[}Data set{]}.
+University of Illinois at Urbana-Champaign.
+\url{https://doi.org/10.13012/B2IDB-0647142_V3}
+
 \leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
@@
 
+\leavevmode\hypertarget{ref-wang2016growing}{}%
+Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing pains for global monitoring of societal events. \emph{Science}, \emph{353}(6307), 1502--1503.
+
 \leavevmode\hypertarget{ref-webber1994dynamical}{}%
@@
 
+\newpage
+
+\hypertarget{appendix-a}{%
+\section{Appendix A}\label{appendix-a}}
+
+Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Pheonix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
+After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
+As a results, sextiles were used for these analyses.
+For comparison, the filtered ICEWS data was also transformed into sextiles.
+
+\hypertarget{crqa-for-pheonix-data-in-sextiles}{%
+\subsection{CRQA for Pheonix data in sextiles}\label{crqa-for-pheonix-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only Pheonix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 29.441 & 0.617 & & 38.232 & 0.000 & *** & 30.792 & 0.332 &\tabularnewline
+NRLINE & 140.000 & 0.457 & & 168.000 & 0.000 & *** & 141.000 & 0.450 &\tabularnewline
+maxL & 4.000 & 0.443 & & 5.000 & 0.088 & . & 4.000 & 0.454 &\tabularnewline
+L & 2.143 & 0.894 & & 2.292 & 0.014 & * & 2.234 & 0.165 &\tabularnewline
+ENTR & 0.420 & 0.904 & & 0.683 & 0.012 & * & 0.569 & 0.239 &\tabularnewline
+rENTR & 0.382 & 0.750 & & 0.492 & 0.171 & & 0.518 & 0.096 & .\tabularnewline
+LAM & 31.600 & 0.350 & & 42.105 & 0.042 & * & 29.619 & 0.625 &\tabularnewline
+TT & 2.252 & 0.247 & & 2.356 & 0.142 & & 2.295 & 0.314 &\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target Pheonix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 32.677 & 0.069 & . & 37.313 & 0.000 & *** & 31.610 & 0.130 &\tabularnewline
+NRLINE & 152.000 & 0.047 & * & 160.000 & 0.000 & *** & 145.000 & 0.133 &\tabularnewline
+maxL & 4.000 & 0.465 & & 7.000 & 0.001 & *** & 4.000 & 0.448 &\tabularnewline
+L & 2.184 & 0.577 & & 2.344 & 0.000 & *** & 2.193 & 0.476 &\tabularnewline
+ENTR & 0.507 & 0.550 & & 0.751 & 0.000 & *** & 0.523 & 0.446 &\tabularnewline
+rENTR & 0.462 & 0.289 & & 0.466 & 0.247 & & 0.476 & 0.214 &\tabularnewline
+LAM & 40.453 & 0.051 & . & 50.746 & 0.001 & *** & 32.008 & 0.453 &\tabularnewline
+TT & 2.446 & 0.044 & * & 2.217 & 0.376 & & 2.284 & 0.327 &\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{crqa-for-icews-data-in-sextiles}{%
+\subsection{CRQA for ICEWS data in sextiles}\label{crqa-for-icews-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 38.636 & 0.000 & *** & 36.759 & 0.001 & *** & 36.858 & 0.000 & ***\tabularnewline
+NRLINE & 175.000 & 0.000 & *** & 165.000 & 0.001 & *** & 161.000 & 0.002 & **\tabularnewline
+maxL & 5.000 & 0.079 & . & 4.000 & 0.438 & & 6.000 & 0.013 & *\tabularnewline
+L & 2.234 & 0.148 & & 2.255 & 0.086 & . & 2.317 & 0.003 & **\tabularnewline
+ENTR & 0.596 & 0.131 & & 0.623 & 0.088 & . & 0.723 & 0.002 & **\tabularnewline
+rENTR & 0.430 & 0.450 & & 0.567 & 0.047 & * & 0.449 & 0.394 &\tabularnewline
+LAM & 42.984 & 0.035 & * & 37.846 & 0.096 & . & 39.625 & 0.062 & .\tabularnewline
+TT & 2.254 & 0.228 & & 2.471 & 0.036 & * & 2.373 & 0.081 & .\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target Pheonix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 32.840 & 0.061 & . & 37.451 & 0.000 & *** & 38.741 & 0.000 & ***\tabularnewline
+NRLINE & 145.000 & 0.208 & & 166.000 & 0.001 & *** & 173.000 & 0.000 & ***\tabularnewline
+maxL & 5.000 & 0.084 & . & 5.000 & 0.093 & . & 7.000 & 0.002 & **\tabularnewline
+L & 2.297 & 0.007 & ** & 2.283 & 0.017 & * & 2.277 & 0.026 & *\tabularnewline
+ENTR & 0.693 & 0.005 & ** & 0.667 & 0.016 & * & 0.632 & 0.058 & .\tabularnewline
+rENTR & 0.500 & 0.128 & & 0.481 & 0.180 & & 0.393 & 0.724 &\tabularnewline
+LAM & 34.221 & 0.208 & & 41.996 & 0.034 & * & 41.003 & 0.037 & *\tabularnewline
+TT & 2.239 & 0.276 & & 2.348 & 0.107 & & 2.279 & 0.231 &\tabularnewline
+\bottomrule
+\end{longtable}
+
+\hypertarget{windowed-crqa-for-pheonix-data-in-sextiles}{%
+\subsection{Windowed CRQA for Pheonix data in sextiles}\label{windowed-crqa-for-pheonix-data-in-sextiles}}
+
+\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
+\subsection{Windowed CRQA for ICEWS data in sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
+
 \end{document}

### 2020-05-27 manuscript.Rmd
Fix typos

@@
 dir.create("./results/secondary/icews/windowed-crqa/target")
-dir.create("./results/secondary/pheonix/crqa/source_target")
-dir.create("./results/secondary/pheonix/crqa/target")
-dir.create("./results/secondary/pheonix/windowed-crqa/source_target")
-dir.create("./results/secondary/pheonix/windowed-crqa/target")
+dir.create("./results/secondary/phoenix/crqa/source_target")
+dir.create("./results/secondary/phoenix/crqa/target")
+dir.create("./results/secondary/phoenix/windowed-crqa/source_target")
+dir.create("./results/secondary/phoenix/windowed-crqa/target")
 
@@
 source('./scripts/secondary-analyses/icews/01_formatting_data.R')
-source('./scripts/secondary-analyses/pheonix/01_formatting_data.R')
+source('./scripts/secondary-analyses/phoenix/01_formatting_data.R')
 
@@
 
-Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Pheonix Event Data [@illinoisdatabankIDB-2796521].
-After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Pheonix data.
+Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Phoenix Event Data [@illinoisdatabankIDB-2796521].
+After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data.
 As a results, sextiles were used for these analyses.
@@
 
-## CRQA for Pheonix data in sextiles
+## CRQA for Phoenix data in sextiles
 ```{r secondary-crqa-phoenix, , echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
 
-# run crqa on sextiled pheonix data
-source('./scripts/secondary-analyses/pheonix/02_crqa.R')
+# run crqa on sextiled phoenix data
+source('./scripts/secondary-analyses/phoenix/02_crqa.R')
 
 # read in metric names
-pheonix_metrics <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-pheonix_metrics_all_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-pheonix_metrics_pos_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-pheonix_metrics_neg_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (target filtered)
-pheonix_sig_all_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-pheonix_sig_pos_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-pheonix_sig_neg_targ <- t(read.csv("./results/secondary/pheonix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
+phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
 
 # read in metrics from crq analyses (source and target filtered)
-pheonix_metrics_all_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-pheonix_metrics_pos_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-pheonix_metrics_neg_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (source and target filtered)
-pheonix_sig_all_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-pheonix_sig_pos_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-pheonix_sig_neg_source_targ <- t(read.csv("./results/secondary/pheonix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
+phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
+phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 
-```{r secondary-crqa-table-pheonix-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+```{r secondary-crqa-table-phoenix-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
 
 # bind metrics and significance results
-pheonix_target_results <- as.data.frame(cbind(pheonix_metrics,
-                                      pheonix_metrics_all_targ, 
-                                      pheonix_sig_all_targ, 
-                                      pheonix_metrics_pos_targ, 
-                                      pheonix_sig_pos_targ, 
-                                      pheonix_metrics_neg_targ, 
-                                      pheonix_sig_neg_targ), 
+phoenix_target_results <- as.data.frame(cbind(phoenix_metrics,
+                                      phoenix_metrics_all_targ, 
+                                      phoenix_sig_all_targ, 
+                                      phoenix_metrics_pos_targ, 
+                                      phoenix_sig_pos_targ, 
+                                      phoenix_metrics_neg_targ, 
+                                      phoenix_sig_neg_targ), 
                                       stringsAsFactors = FALSE)
@@
 numerics <- c(2:7)
-pheonix_target_results[,numerics] <- sapply(pheonix_target_results[,numerics],as.numeric)
+phoenix_target_results[,numerics] <- sapply(phoenix_target_results[,numerics],as.numeric)
 
 # add significance stars
-stars_all <- as.data.frame(stars.pval(pheonix_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(pheonix_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(pheonix_target_results[,7]))
+stars_all <- as.data.frame(stars.pval(phoenix_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(phoenix_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(phoenix_target_results[,7]))
 
-pheonix_target_results <- cbind(pheonix_target_results, stars_all, stars_pos, stars_neg)
-pheonix_target_results <- pheonix_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+phoenix_target_results <- cbind(phoenix_target_results, stars_all, stars_pos, stars_neg)
+phoenix_target_results <- phoenix_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
 
 # give intuitive names
-colnames(pheonix_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+colnames(phoenix_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
 
 # exclude row names
-rownames(pheonix_target_results) <- NULL
+rownames(phoenix_target_results) <- NULL
 
@@
 # build table
-pander(pheonix_target_results, caption = "CRQA results for target only Pheonix data.")
+pander(phoenix_target_results, caption = "CRQA results for target only Phoenix data.")
 
@@
 
-```{r primary-table-pheonix-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+```{r primary-table-phoenix-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
 
 # bind metrics and significance results
-pheonix_source_target_results <- as.data.frame(cbind(pheonix_metrics,
-                                      pheonix_metrics_all_source_targ, 
-                                      pheonix_sig_all_source_targ, 
-                                      pheonix_metrics_pos_source_targ, 
-                                      pheonix_sig_pos_source_targ, 
-                                      pheonix_metrics_neg_source_targ, 
-                                      pheonix_sig_neg_source_targ), 
+phoenix_source_target_results <- as.data.frame(cbind(phoenix_metrics,
+                                      phoenix_metrics_all_source_targ, 
+                                      phoenix_sig_all_source_targ, 
+                                      phoenix_metrics_pos_source_targ, 
+                                      phoenix_sig_pos_source_targ, 
+                                      phoenix_metrics_neg_source_targ, 
+                                      phoenix_sig_neg_source_targ), 
                                       stringsAsFactors = FALSE)
@@
 numerics <- c(2:7)
-pheonix_source_target_results[,numerics] <- sapply(pheonix_source_target_results[,numerics],as.numeric)
+phoenix_source_target_results[,numerics] <- sapply(phoenix_source_target_results[,numerics],as.numeric)
 
 # add significance stars
-stars_all <- as.data.frame(stars.pval(pheonix_source_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(pheonix_source_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(pheonix_source_target_results[,7]))
+stars_all <- as.data.frame(stars.pval(phoenix_source_target_results[,3]))
+stars_pos <- as.data.frame(stars.pval(phoenix_source_target_results[,5]))
+stars_neg <- as.data.frame(stars.pval(phoenix_source_target_results[,7]))
 
-pheonix_source_target_results <- cbind(pheonix_source_target_results, stars_all, stars_pos, stars_neg)
-pheonix_source_target_results <- pheonix_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
+phoenix_source_target_results <- cbind(phoenix_source_target_results, stars_all, stars_pos, stars_neg)
+phoenix_source_target_results <- phoenix_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
 
 # give intuitive names
-colnames(pheonix_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+colnames(phoenix_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
 
 # exclude row names
-rownames(pheonix_source_target_results) <- NULL
+rownames(phoenix_source_target_results) <- NULL
 
@@
 # build table
-pander(pheonix_source_target_results, caption = "CRQA results for source and target Pheonix data.")
+pander(phoenix_source_target_results, caption = "CRQA results for source and target Phoenix data.")
 
 ```
-CRQ analyses for sextiled Pheonix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
+CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
 Negative events were not coupled with social cohesion irrepective of filtering.
@@
 Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.

### 2020-05-27 manuscript.tex
Fix typos

@@
 
-Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Pheonix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
+Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
 After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
@@
 
-\hypertarget{crqa-for-pheonix-data-in-sextiles}{%
-\subsection{CRQA for Pheonix data in sextiles}\label{crqa-for-pheonix-data-in-sextiles}}
+\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
+\subsection{CRQA for Phoenix data in sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
 
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only Pheonix data.}\tabularnewline
+\caption{CRQA results for target only Phoenix data.}\tabularnewline
 \toprule
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Pheonix data.}\tabularnewline
+\caption{CRQA results for source and target Phoenix data.}\tabularnewline
 \toprule
@@
 
-\hypertarget{windowed-crqa-for-pheonix-data-in-sextiles}{%
-\subsection{Windowed CRQA for Pheonix data in sextiles}\label{windowed-crqa-for-pheonix-data-in-sextiles}}
+\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
+\subsection{Windowed CRQA for Phoenix data in sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
 

### 2020-05-27 manuscript.Rmd
Make all directory creation recursive

@@
 dir.create("./data/raw") # load three data files here
-dir.create("./data/formatted/primary")
-dir.create("./data/formatted/secondary")
-dir.create("./results/primary/crqa")
-dir.create("./results/primary/windowed-crqa")
-dir.create("./results/secondary/icews/crqa/source_target")
-dir.create("./results/secondary/icews/crqa/target")
-dir.create("./results/secondary/icews/windowed-crqa/source_target")
-dir.create("./results/secondary/icews/windowed-crqa/target")
-dir.create("./results/secondary/phoenix/crqa/source_target")
-dir.create("./results/secondary/phoenix/crqa/target")
-dir.create("./results/secondary/phoenix/windowed-crqa/source_target")
-dir.create("./results/secondary/phoenix/windowed-crqa/target")
+dir.create("./data/formatted/primary", recursive = TRUE)
+dir.create("./data/formatted/secondary/icews", recursive = TRUE)
+dir.create("./data/formatted/secondary/phoenix", recursive = TRUE)
+dir.create("./results/primary/crqa", recursive = TRUE)
+dir.create("./results/primary/windowed-crqa", recursive = TRUE)
+dir.create("./results/secondary/icews/crqa/source_target", recursive = TRUE)
+dir.create("./results/secondary/icews/crqa/target", recursive = TRUE)
+dir.create("./results/secondary/icews/windowed-crqa/source_target", recursive = TRUE)
+dir.create("./results/secondary/icews/windowed-crqa/target", recursive = TRUE)
+dir.create("./results/secondary/phoenix/crqa/source_target", recursive = TRUE)
+dir.create("./results/secondary/phoenix/crqa/target", recursive = TRUE)
+dir.create("./results/secondary/phoenix/windowed-crqa/source_target", recursive = TRUE)
+dir.create("./results/secondary/phoenix/windowed-crqa/target", recursive = TRUE)
 

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R
Formatting and typos

@@ -1,11 +1,11 @@
-######## Formatting Arab Spring Data (ICEWS) ########
+######## Secondary Analysis: Formatting ICEWS Arab Spring Data ########
 #
 # This script formats data related to the Arab Spring.
-# Daily Twitter social cohesion and event data are processed 
+# Daily Twitter social cohesion and event data are processed
 # and transformed into *sextiles* for CRQA and windowed CRQA
 # analyses.
 #
-# Code by: M. Chiovaro (@mchiovaro)
+# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
 # Last updated: 2020_05_21
 
@@ -14,32 +14,33 @@
 # clear environment
 rm(list=ls())
 
-# read in the data 
+# read in the data
 cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
-ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab", header = TRUE, sep = "\t", quote = "")
+ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab",
+                       header = TRUE, sep = "\t", quote = "")
 
 #### 2. Filter and format the time series ####
 
 ### filter for source and target ###
 
 # filter full 2012 ICEWS data for correct dates and parameters
-ICEWS_filtered <- ICEWS_df %>% 
+ICEWS_filtered <- ICEWS_df %>%
   
   # fill blanks with NAs
   na_if("") %>%
-
+  
   # turn factor to character for using grepl
   mutate(Event.Date = as.character(Event.Date)) %>%
   
   # filter out unusable dates
-  filter(grepl("^(2012)[-](0[1-9]|1[012])[-](0[1-9]|[12][0-9]|3[01])$", 
+  filter(grepl("^(2012)[-](0[1-9]|1[012])[-](0[1-9]|[12][0-9]|3[01])$",
                Event.Date)) %>%
   
   # turn to date format to use select for date range
   mutate_at(vars(Event.Date), as.Date, format = "%Y-%m-%d") %>%
   
   # grab the dates that align with old data
-  filter(Event.Date >= as.Date("2012-03-30") 
+  filter(Event.Date >= as.Date("2012-03-30")
          & Event.Date <= as.Date("2012-06-15")) %>%
   
   # change search params to characters for searching
@@ -61,7 +62,7 @@ ICEWS_filtered <- ICEWS_df %>%
[…]

### 2020-05-27 scripts/required_packages.r
Specify package for mode computation

@@ -14,7 +14,8 @@ required_packages = c(
   'papaja',
   'pander',
   'gtools',
-  'knitr'
+  'knitr',
+  'statip'
 )
 
 # install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R

@@ -80,7 +80,7 @@ ICEWS_formatted_source_target <- ICEWS_filtered %>%
   mutate(Intensity = sort(Intensity, decreasing = TRUE)) %>%
   
   # calculate mode
-  mutate(mode_source_target = mfv1(Intensity, method = "mfv")) %>%
+  mutate(mode_source_target = statip::mfv1(Intensity, method = "mfv")) %>%
   
   # keep one unique row per day
   distinct(Event.Date,
@@ -119,7 +119,7 @@ ICEWS_formatted_target <- ICEWS_filtered %>%
   mutate(Intensity = sort(Intensity, decreasing = TRUE)) %>%
   
   # calculate mode
-  mutate(mode_target = mfv1(Intensity, method = "mfv")) %>%
+  mutate(mode_target = statip::mfv1(Intensity, method = "mfv")) %>%
   
   # keep one unique row per day
   distinct(Event.Date,

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R
Streamline sextile calculation

@@ -134,96 +134,49 @@ ICEWS_formatted_target <- ICEWS_filtered %>%
   # undo grouping by date
   ungroup()
 
-# bind the event and social cohesion data frames
-ICEWS_df_formatted <- cbind(ICEWS_formatted_source_target, ICEWS_formatted_target, cohesion_df)
+### prepare cohesion dataframe for merging ###
 
-# keep only what we need
-ICEWS_df_formatted <- ICEWS_df_formatted[c("Date", 
-                                           "all_events_source_target", 
-                                           "pos_events_source_target", 
-                                           "neg_events_source_target", 
-                                           "mode_source_target", 
-                                           "all_events_target", 
-                                           "pos_events_target", 
-                                           "neg_events_target", 
-                                           "mode_target", 
-                                           "MeanCohesion")]
+cohesion_df <- cohesion_df %>%
+  
+  # format dates
+  mutate(Date = as.Date(Date)) %>%
+  
+  # only keep variables we need
+  select(Date, MeanCohesion)
+
+### combine all dataframes ###
+
+# bind the event and social cohesion data frames
+ICEWS_df_formatted <- dplyr::full_join(ICEWS_formatted_source_target,
+                                       ICEWS_formatted_target,
+                                       by=c("Date")) %>%
+  dplyr::full_join(., cohesion_df,
+                   by=c("Date"))
 
 #### 3. Create the sextiles for analyses ####
 
-## social cohesion ##
-
-# create the sextiles
-ICEWS_df_formatted$coh_sextiles <- with(ICEWS_df_formatted, cut(MeanCohesion, 
-                                                               breaks=quantile(MeanCohesion, probs=seq(0, 1, by=1/6), na.rm=TRUE), 
-                                                               include.lowest=TRUE))
-
-# re-label with intuitive decile levels
-levels(ICEWS_df_formatted$coh_sextiles) <- factor(c("1","2","3","4", "5", "6", "7", "8", "9", "10"))
-
-### source and target variable sextiles ###
-
-## count of events ##
-
-# create the sextiles
-ICEWS_df_formatted$all_sextiles_source_target <- with(ICEWS_df_formatted, cut(all_events_source_target, 
[…]

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R
Make warning messages more informative

@@ -210,7 +210,11 @@ original <- as.data.frame(t(original))
 shuffled_coh <- rbind(shuffled_coh, original)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_coh))
+print(paste0("Total distinct shuffled social cohesion time series for CRQA: ",
+             nrow(distinct(shuffled_coh))))
+if(nrow(distinct(shuffled_coh)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_coh <- as.data.frame(t(shuffled_coh))
@@ -238,7 +242,11 @@ original_all <- as.data.frame(t(original_all))
 shuffled_all_source_target <- rbind(shuffled_all_source_target, original_all)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_all_source_target))
+print(paste0("Total distinct shuffled all-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_all_source_target))))
+if(nrow(distinct(shuffled_all_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_all_source_target <- as.data.frame(t(shuffled_all_source_target))
@@ -264,7 +272,11 @@ original_pos <- as.data.frame(t(original_pos))
 shuffled_pos_source_target <- rbind(shuffled_pos_source_target, original_pos)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_pos_source_target))
+print(paste0("Total distinct shuffled positive-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_pos_source_target))))
+if(nrow(distinct(shuffled_pos_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_pos_source_target <- as.data.frame(t(shuffled_pos_source_target))
@@ -290,7 +302,11 @@ original_neg <- as.data.frame(t(original_neg))
 shuffled_neg_source_target <- rbind(shuffled_neg_source_target, original_neg)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_neg_source_target))
+print(paste0("Total distinct shuffled negative-event time series (source and target) for CRQA: ",
[…]

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R
Update code modification date

@@ -7,7 +7,7 @@
 #
 # Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_05_21
+# Last updated: 2020_05_27
 
 #### 1. Set up ####
 

### 2020-05-27 scripts/secondary-analyses/icews/01_formatting_data.R
Fix surrogate checks for windowed CRQA

@@ -444,7 +444,7 @@ for (i in 1:1000){
 # check to see if we have 1000 distinct time series
 print(paste0("Total distinct shuffled social cohesion time series for windowed CRQA: ",
              nrow(distinct(shuffled_coh))))
-if(nrow(distinct(shuffled_coh)) != 1001){
+if(nrow(distinct(shuffled_coh)) != 1000){
   print("WARNING: Duplicates in surrogate time series.")
 }
 
@@ -465,10 +465,10 @@ for (i in 1:1000){
   shuffled_all_source_target <- rbind(shuffled_all_source_target, sample)
 }
 
-# check to see if we have 1001 distinct time series
+# check to see if we have 1000 distinct time series
 print(paste0("Total distinct shuffled all-event time series (source and target) for windowed CRQA: ",
              nrow(distinct(shuffled_all_source_target))))
-if(nrow(distinct(shuffled_all_source_target)) != 1001){
+if(nrow(distinct(shuffled_all_source_target)) != 1000){
   print("WARNING: Duplicates in surrogate time series.")
 }
 
@@ -487,10 +487,10 @@ for (i in 1:1000){
   shuffled_pos_source_target <- rbind(shuffled_pos_source_target, sample)
 }
 
-# check to see if we have 1001 distinct time series
-print(paste0("Total distinct shuffled positive-event time series (source and target): ",
+# check to see if we have 1000 distinct time series
+print(paste0("Total distinct shuffled positive-event time series (source and target) for windowed CRQA: ",
              nrow(distinct(shuffled_pos_source_target))))
-if(nrow(distinct(shuffled_pos_source_target)) != 1001){
+if(nrow(distinct(shuffled_pos_source_target)) != 1000){
   print("WARNING: Duplicates in surrogate time series.")
 }
 # transform rows to columns for binding
@@ -508,10 +508,10 @@ for (i in 1:1000){
   shuffled_neg_source_target <- rbind(shuffled_neg_source_target, sample)
 }
 
-# check to see if we have 1001 distinct time series
-print(paste0("Total distinct shuffled negative-event time series (source and target): ",
+# check to see if we have 1000 distinct time series
+print(paste0("Total distinct shuffled negative-event time series (source and target) for windowed CRQA: ",
              nrow(distinct(shuffled_neg_source_target))))
-if(nrow(distinct(shuffled_neg_source_target)) != 1001){
+if(nrow(distinct(shuffled_neg_source_target)) != 1000){
[…]

### 2020-05-27 manuscript.Rmd
Add secondary windowed CRQA code

--- 2020-05-27 manuscript.Rmd
@@
 The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+
+## Windowed CRQA for Pheonix data in sextiles
+```{r secondary-windowed-crqa-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled pheonix data
+source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```
+
+## Windowed CRQA for ICEWS data in sextiles
+```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled icews data
+source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```

### 2020-05-27 manuscript.tex
Add secondary windowed CRQA code

--- 2020-05-27 manuscript.tex
@@
 
+By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
+These additional observations are times where Syria initiated an event with another country.
+Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
+The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
+Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
+Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on.
+We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
+The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
 By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
@@
 
-The time period of differing dynamics, from observation 36 through 46, appears to be captured by WCRQA of social cohesion and count of negative events with window size 14 for both RR (Figure 8) and DET (Figure 11).
-The amount of recurrence and determinism for these periods consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-During this time period, Syria underwent the \enquote{Siege of Homs} on May 5th, where fleets of tanks were sent into Homs and over 300 individuals were arrested.
-On May 6th, demonstrators began protesting after Friday prayers, leading to retaliation violence by the Syrian army, leaving sixteen civilians and eleven Syrian army men dead.
-That day, tens of thousands of individuals marched in an attempt to meet the army peacefully and bring supplies to Deraa, but were refused entrance.
-This day became known as the \enquote{Day of Defiance} or the \enquote{Friday of Challenge.} Syria also faced the \enquote{Siege of Baniyas} on May 7th, \enquote{Siege of Tafas} on May 8th, \enquote{Friday of Free Women} on May 13th, \enquote{Siege of Talkalakh} on May 14th, the \enquote{Israel border demonstrations} on May 15th, \enquote{Friday of Azady (freedom)} on May 20th, \enquote{Home Protectors' Friday} on May 27th, and the \enquote{Siege of Rastan and Talbiseh} on May 28th.
+The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
+The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
 The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-The frequency of negative events is also captured by the mode ICEWS rating for each day.
-In Figure 12, observed days from 33 to 47, or from May 1st, 2012 to May 15th, 2012, are largely overcome by extreme negative events of ICEWS rating -10.
-These directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, RR (Figure 7) and DET (Figure 10) were both within chance.
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
+These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.
 
@@
 \subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-3}}
+
+WCRQ analyses of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
+Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
+WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
+This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
+Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
 
@@
 Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Pheonix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
-After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
+After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Pheonix data.
 As a results, sextiles were used for these analyses.
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Pheonix data.}\tabularnewline
+\caption{CRQA results for source and target Pheonix data.
+CRQ analyses for sextiled Pheonix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
+Negative events were not coupled with social cohesion irrepective of filtering.}\tabularnewline
 \toprule
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Pheonix data.}\tabularnewline
+\caption{CRQA results for source and target ICEWS data.
+CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
+Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
+The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.}\tabularnewline
 \toprule
@@
 
+\hypertarget{syria-as-target-4}{%
+\subsubsection{Syria as Target}\label{syria-as-target-4}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-pheonix}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target-4}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-4}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-pheonix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-pheonix}
+\end{figure}
+
 \hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
@@
 
+\hypertarget{syria-as-target-5}{%
+\subsubsection{Syria as Target}\label{syria-as-target-5}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target-5}{%
+\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-5}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\end{figure}
+
 \end{document}

### 2020-05-27 manuscript.Rmd

--- 2020-05-27 manuscript.Rmd
@@
 Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+
+## Windowed CRQA for Pheonix data in sextiles
+```{r secondary-windowed-crqa-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled pheonix data
+source('./scripts/secondary-analyses/pheonix/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-pheonix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```
+
+## Windowed CRQA for ICEWS data in sextiles
+```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled icews data
+source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```

### 2020-05-27 manuscript.tex

@@
 
-Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Pheonix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
-After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Pheonix data.
+Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
+After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
 As a results, sextiles were used for these analyses.
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Pheonix data.
-CRQ analyses for sextiled Pheonix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrepective of filtering.}\tabularnewline
+\caption{CRQA results for source and target Phoenix data.}\tabularnewline
+CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
+Negative events were not coupled with social cohesion irrespective of filtering.
 \toprule
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target ICEWS data.
+\caption{CRQA results for source and target ICEWS data.}\tabularnewline
 CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Pheonix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.}\tabularnewline
+Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
+The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
 \toprule

### 2020-05-27 manuscript.Rmd
Fixed typos

--- 2020-05-27 manuscript.Rmd
@@
 The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+
+## Windowed CRQA for Phoenix data in sextiles
+```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled Phoenix data
+source('./scripts/secondary-analyses/Phoenix/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```
+
+## Windowed CRQA for ICEWS data in sextiles
+```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# run windowed crqa on sextiled icews data
+source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
+
+```
+
+### Syria as Target
+
+```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")
+
+```
+
+### Syria as Source and Target
+
+```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")
+
+```
+
+```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")
+
+```

### 2020-05-27 manuscript.tex
Fixed typos

@@
 Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
-After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
+After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data.
 As a results, sextiles were used for these analyses.
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Phoenix data.}\tabularnewline
+\caption{CRQA results for source and target Phoenix data.
 CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrespective of filtering.
+Negative events were not coupled with social cohesion irrepective of filtering.}\tabularnewline
 \toprule
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target ICEWS data.}\tabularnewline
+\caption{CRQA results for source and target ICEWS data.
 CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
+The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.}\tabularnewline
 \toprule
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-pheonix}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
 \end{figure}

### 2020-05-27 manuscript.Rmd

@@
 \newpage
-
-# Appendix A
-
-Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Phoenix Event Data [@illinoisdatabankIDB-2796521].
-After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data.
-As a results, sextiles were used for these analyses.
-For comparison, the filtered ICEWS data was also transformed into sextiles.
-
-## CRQA for Phoenix data in sextiles
-```{r secondary-crqa-phoenix, , echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# run crqa on sextiled phoenix data
-source('./scripts/secondary-analyses/phoenix/02_crqa.R')
-
-# read in metric names
-phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
-
-# read in metrics from crq analyses (target filtered)
-phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
-
-# read in signficiance from permutation tests (target filtered)
-phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
-
-# read in metrics from crq analyses (source and target filtered)
-phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
-
-# read in signficiance from permutation tests (source and target filtered)
-phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
-
-```
-
-```{r secondary-crqa-table-phoenix-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
-
-# bind metrics and significance results
-phoenix_target_results <- as.data.frame(cbind(phoenix_metrics,
-                                      phoenix_metrics_all_targ,
-                                      phoenix_sig_all_targ,
-                                      phoenix_metrics_pos_targ,
-                                      phoenix_sig_pos_targ,
-                                      phoenix_metrics_neg_targ,
-                                      phoenix_sig_neg_targ),
-                                      stringsAsFactors = FALSE)
-
-# covert to numerics for rounding
-numerics <- c(2:7)
-phoenix_target_results[,numerics] <- sapply(phoenix_target_results[,numerics],as.numeric)
-
-# add significance stars
-stars_all <- as.data.frame(stars.pval(phoenix_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(phoenix_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(phoenix_target_results[,7]))
-
-phoenix_target_results <- cbind(phoenix_target_results, stars_all, stars_pos, stars_neg)
-phoenix_target_results <- phoenix_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
-
-# give intuitive names
-colnames(phoenix_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
-
-# exclude row names
-rownames(phoenix_target_results) <- NULL
-
-# set to not split table and round to two decimal places
-panderOptions("table.split.table", Inf)
-panderOptions('round', 3)
-panderOptions('keep.trailing.zeros', TRUE)
-
-# style for Rmd
-panderOptions("table.style", "rmarkdown")
-
-# build table
-pander(phoenix_target_results, caption = "CRQA results for target only Phoenix data.")
-
-```
-
-```{r primary-table-phoenix-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
-
-# bind metrics and significance results
-phoenix_source_target_results <- as.data.frame(cbind(phoenix_metrics,
-                                      phoenix_metrics_all_source_targ,
-                                      phoenix_sig_all_source_targ,
-                                      phoenix_metrics_pos_source_targ,
-                                      phoenix_sig_pos_source_targ,
-                                      phoenix_metrics_neg_source_targ,
-                                      phoenix_sig_neg_source_targ),
-                                      stringsAsFactors = FALSE)
-
-# covert to numerics for rounding
-numerics <- c(2:7)
-phoenix_source_target_results[,numerics] <- sapply(phoenix_source_target_results[,numerics],as.numeric)
-
-# add significance stars
-stars_all <- as.data.frame(stars.pval(phoenix_source_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(phoenix_source_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(phoenix_source_target_results[,7]))
-
-phoenix_source_target_results <- cbind(phoenix_source_target_results, stars_all, stars_pos, stars_neg)
-phoenix_source_target_results <- phoenix_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
-
-# give intuitive names
-colnames(phoenix_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
-
-# exclude row names
-rownames(phoenix_source_target_results) <- NULL
-
-# set to not split table and round to two decimal places
-panderOptions("table.split.table", Inf)
-panderOptions('round', 3)
-panderOptions('keep.trailing.zeros', TRUE)
-
-# style for Rmd
-panderOptions("table.style", "rmarkdown")
-
-# build table
-pander(phoenix_source_target_results, caption = "CRQA results for source and target Phoenix data.")
-
-```
-CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrepective of filtering.
-
-## CRQA for ICEWS data in sextiles
-```{r secondary-crqa-icews, , echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# run crqa on sextiled icews data
-source('./scripts/secondary-analyses/icews/02_crqa.R')
-
-# read in metric names
-icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
-
-# read in metrics from crq analyses (target filtered)
-icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
-
-# read in signficiance from permutation tests (target filtered)
-icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
-
-# read in metrics from crq analyses (source and target filtered)
-icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
-
-# read in signficiance from permutation tests (source and target filtered)
-icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
-
-```
-
-```{r secondary-crqa-table-icews-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
-
-# bind metrics and significance results
-icews_target_results <- as.data.frame(cbind(icews_metrics,
-                                      icews_metrics_all_targ,
-                                      icews_sig_all_targ,
-                                      icews_metrics_pos_targ,
-                                      icews_sig_pos_targ,
-                                      icews_metrics_neg_targ,
-                                      icews_sig_neg_targ),
-                                      stringsAsFactors = FALSE)
-
-# covert to numerics for rounding
-numerics <- c(2:7)
-icews_target_results[,numerics] <- sapply(icews_target_results[,numerics],as.numeric)
-
-# add significance stars
-stars_all <- as.data.frame(stars.pval(icews_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(icews_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(icews_target_results[,7]))
-
-icews_target_results <- cbind(icews_target_results, stars_all, stars_pos, stars_neg)
-icews_target_results <- icews_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
-
-# give intuitive names
-colnames(icews_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
-
-# exclude row names
-rownames(icews_target_results) <- NULL
-
-# set to not split table and round to two decimal places
-panderOptions("table.split.table", Inf)
-panderOptions('round', 3)
-panderOptions('keep.trailing.zeros', TRUE)
-
-# style for Rmd
-panderOptions("table.style", "rmarkdown")
-
-# build table
-pander(icews_target_results, caption = "CRQA results for target only ICEWS data.")
-
-```
-
-```{r primary-table-icews-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
-
-# bind metrics and significance results
-icews_source_target_results <- as.data.frame(cbind(icews_metrics,
-                                      icews_metrics_all_source_targ,
-                                      icews_sig_all_source_targ,
-                                      icews_metrics_pos_source_targ,
-                                      icews_sig_pos_source_targ,
-                                      icews_metrics_neg_source_targ,
-                                      icews_sig_neg_source_targ),
-                                      stringsAsFactors = FALSE)
-
-# covert to numerics for rounding
-numerics <- c(2:7)
-icews_source_target_results[,numerics] <- sapply(icews_source_target_results[,numerics],as.numeric)
-
-# add significance stars
-stars_all <- as.data.frame(stars.pval(icews_source_target_results[,3]))
-stars_pos <- as.data.frame(stars.pval(icews_source_target_results[,5]))
-stars_neg <- as.data.frame(stars.pval(icews_source_target_results[,7]))
-
-icews_source_target_results <- cbind(icews_source_target_results, stars_all, stars_pos, stars_neg)
-icews_source_target_results <- icews_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]
-
-# give intuitive names
-colnames(icews_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
-
-# exclude row names
-rownames(icews_source_target_results) <- NULL
-
-# set to not split table and round to two decimal places
-panderOptions("table.split.table", Inf)
-panderOptions('round', 3)
-panderOptions('keep.trailing.zeros', TRUE)
-
-# style for Rmd
-panderOptions("table.style", "rmarkdown")
-
-# build table
-pander(icews_source_target_results, caption = "CRQA results for source and target ICEWS data.")
-
-```
-CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
-
-## Windowed CRQA for Phoenix data in sextiles
-```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# run windowed crqa on sextiled Phoenix data
-source('./scripts/secondary-analyses/Phoenix/03_windowed_crqa.R')
-
-```
-
-### Syria as Target
-
-```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR.png")
-
-```
-
-```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET.png")
-
-```
-
-```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET.png")
-
-```
-
-### Syria as Source and Target
-
-```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR.png")
-
-```
-
-```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET.png")
-
-```
-
-```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET.png")
-
-```
-
-## Windowed CRQA for ICEWS data in sextiles
-```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# run windowed crqa on sextiled icews data
-source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')
-
-```
-
-### Syria as Target
-
-```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")
-
-```
-
-```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")
-
-```
-
-```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")
-
-```
-
-### Syria as Source and Target
-
-```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")
-
-```
-
-```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")
-
-```
-
-```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")
-
-```

### 2020-05-27 manuscript.tex

--- 2020-05-27 manuscript.tex
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
-Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
-(2020).
-\emph{Cline center historical phoenix event data.
-Cline center for advanced social research.
-V1.3.0.
-May 4} {[}Data set{]}.
-University of Illinois at Urbana-Champaign.
-\url{https://doi.org/10.13012/B2IDB-0647142_V3}
-
 \leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
@@
 
-\leavevmode\hypertarget{ref-wang2016growing}{}%
-Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing pains for global monitoring of societal events. \emph{Science}, \emph{353}(6307), 1502--1503.
-
 \leavevmode\hypertarget{ref-webber1994dynamical}{}%
@@
 
-\hypertarget{appendix-a}{%
-\section{Appendix A}\label{appendix-a}}
-
-Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
-After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles.
-As a results, sextiles were used for these analyses.
-For comparison, the filtered ICEWS data was also transformed into sextiles.
-
-\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
-\subsection{CRQA for Phoenix data in sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only Phoenix data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 29.441 & 0.617 & & 38.232 & 0.000 & *** & 30.792 & 0.332 &\tabularnewline
-NRLINE & 140.000 & 0.457 & & 168.000 & 0.000 & *** & 141.000 & 0.450 &\tabularnewline
-maxL & 4.000 & 0.443 & & 5.000 & 0.088 & . & 4.000 & 0.454 &\tabularnewline
-L & 2.143 & 0.894 & & 2.292 & 0.014 & * & 2.234 & 0.165 &\tabularnewline
-ENTR & 0.420 & 0.904 & & 0.683 & 0.012 & * & 0.569 & 0.239 &\tabularnewline
-rENTR & 0.382 & 0.750 & & 0.492 & 0.171 & & 0.518 & 0.096 & .\tabularnewline
-LAM & 31.600 & 0.350 & & 42.105 & 0.042 & * & 29.619 & 0.625 &\tabularnewline
-TT & 2.252 & 0.247 & & 2.356 & 0.142 & & 2.295 & 0.314 &\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Phoenix data.}\tabularnewline
-CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrespective of filtering.
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 32.677 & 0.069 & . & 37.313 & 0.000 & *** & 31.610 & 0.130 &\tabularnewline
-NRLINE & 152.000 & 0.047 & * & 160.000 & 0.000 & *** & 145.000 & 0.133 &\tabularnewline
-maxL & 4.000 & 0.465 & & 7.000 & 0.001 & *** & 4.000 & 0.448 &\tabularnewline
-L & 2.184 & 0.577 & & 2.344 & 0.000 & *** & 2.193 & 0.476 &\tabularnewline
-ENTR & 0.507 & 0.550 & & 0.751 & 0.000 & *** & 0.523 & 0.446 &\tabularnewline
-rENTR & 0.462 & 0.289 & & 0.466 & 0.247 & & 0.476 & 0.214 &\tabularnewline
-LAM & 40.453 & 0.051 & . & 50.746 & 0.001 & *** & 32.008 & 0.453 &\tabularnewline
-TT & 2.446 & 0.044 & * & 2.217 & 0.376 & & 2.284 & 0.327 &\tabularnewline
-\bottomrule
-\end{longtable}
-
-\hypertarget{crqa-for-icews-data-in-sextiles}{%
-\subsection{CRQA for ICEWS data in sextiles}\label{crqa-for-icews-data-in-sextiles}}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only ICEWS data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 38.636 & 0.000 & *** & 36.759 & 0.001 & *** & 36.858 & 0.000 & ***\tabularnewline
-NRLINE & 175.000 & 0.000 & *** & 165.000 & 0.001 & *** & 161.000 & 0.002 & **\tabularnewline
-maxL & 5.000 & 0.079 & . & 4.000 & 0.438 & & 6.000 & 0.013 & *\tabularnewline
-L & 2.234 & 0.148 & & 2.255 & 0.086 & . & 2.317 & 0.003 & **\tabularnewline
-ENTR & 0.596 & 0.131 & & 0.623 & 0.088 & . & 0.723 & 0.002 & **\tabularnewline
-rENTR & 0.430 & 0.450 & & 0.567 & 0.047 & * & 0.449 & 0.394 &\tabularnewline
-LAM & 42.984 & 0.035 & * & 37.846 & 0.096 & . & 39.625 & 0.062 & .\tabularnewline
-TT & 2.254 & 0.228 & & 2.471 & 0.036 & * & 2.373 & 0.081 & .\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target ICEWS data.}\tabularnewline
-CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 32.840 & 0.061 & . & 37.451 & 0.000 & *** & 38.741 & 0.000 & ***\tabularnewline
-NRLINE & 145.000 & 0.208 & & 166.000 & 0.001 & *** & 173.000 & 0.000 & ***\tabularnewline
-maxL & 5.000 & 0.084 & . & 5.000 & 0.093 & . & 7.000 & 0.002 & **\tabularnewline
-L & 2.297 & 0.007 & ** & 2.283 & 0.017 & * & 2.277 & 0.026 & *\tabularnewline
-ENTR & 0.693 & 0.005 & ** & 0.667 & 0.016 & * & 0.632 & 0.058 & .\tabularnewline
-rENTR & 0.500 & 0.128 & & 0.481 & 0.180 & & 0.393 & 0.724 &\tabularnewline
-LAM & 34.221 & 0.208 & & 41.996 & 0.034 & * & 41.003 & 0.037 & *\tabularnewline
-TT & 2.239 & 0.276 & & 2.348 & 0.107 & & 2.279 & 0.231 &\tabularnewline
-\bottomrule
-\end{longtable}
-
-\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
-\subsection{Windowed CRQA for Phoenix data in sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
-
-\hypertarget{syria-as-target-4}{%
-\subsubsection{Syria as Target}\label{syria-as-target-4}}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-pheonix}
-\end{figure}
-
-\hypertarget{syria-as-source-and-target-4}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-4}}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-pheonix}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-pheonix}
-\end{figure}
-
-\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
-\subsection{Windowed CRQA for ICEWS data in sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
-
-\hypertarget{syria-as-target-5}{%
-\subsubsection{Syria as Target}\label{syria-as-target-5}}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
-\end{figure}
-
-\hypertarget{syria-as-source-and-target-5}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-5}}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
-\end{figure}
-
 \end{document}

### 2020-05-27 scripts/primary-analyses/02_crqa.R
Update directory and file structure

@@ -4,9 +4,9 @@
 # the real-world events and Twitter social cohesion of 
 # Arab Spring.
 #
-# Code by: M. Chiovaro (@mchiovaro)
+# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_05_21
+# Last updated: 2020_05_27
 
 #### 1. Set up ####
 
@@ -46,11 +46,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_deciles,
 
 # save the crqa results
 rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_all_source_target,'./results/primary/crqa/source_target/crqa_results-all_events.csv',
+write.table(rqa_results_all_source_target,'./results/primary/crqa/source_target-crqa_results-all_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/primary/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/primary/crqa/source_target-rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of all events", 
@@ -75,11 +75,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_deciles,
 
 # save the crqa results
 rqa_results_pos_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_pos_source_target,'./results/primary/crqa/source_target/crqa_results-pos_events.csv',
+write.table(rqa_results_pos_source_target,'./results/primary/crqa/source_target-crqa_results-pos_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/primary/crqa/source_target/rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/primary/crqa/source_target-rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of positive events", 
@@ -104,11 +104,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_deciles,
 
 # save the crqa results
[…]

### 2020-05-27 manuscript.Rmd
Update file and directory structure in Rmd

@@
 # read in metric names
-metrics <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-metrics_all_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-metrics_pos_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-metrics_neg_targ <- t(read.csv("./results/primary/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (target filtered)
-sig_all_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-sig_pos_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-sig_neg_targ <- t(read.csv("./results/primary/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/target/rp-all_events.png")
+knitr::include_graphics("./results/primary/crqa/target-rp-all_events.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/target/rp-pos_events.png")
+knitr::include_graphics("./results/primary/crqa/target-rp-pos_events.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/target/rp-neg_events.png")
+knitr::include_graphics("./results/primary/crqa/target-rp-neg_events.png")
 

### 2020-05-27 scripts/secondary-analyses/phoenix/01_formatting_data.R
Formatting and typos

@@ -1,4 +1,4 @@
-######## Formatting Arab Spring Data (Phoenix) ########
+######## Secondary Analysis: Formatting Phoenix Arab Spring Data ########
 #
 # Phoenix event data from the Cline center: 
 # https://databank.illinois.edu/datasets/IDB-2796521
@@ -9,9 +9,9 @@
 # and transformed into sextiles for CRQA and windowed CRQA
 # analyses.
 #
-# Code by: M. Chiovaro (@mchiovaro)
+# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_05_21
+# Last updated: 2020_05_27
 
 #### 1. Set up ####
 
@@ -79,9 +79,13 @@ phoenix_formatted_source_target <- phoenix_df_filtered %>%
   mutate(mode_source_target = mfv1(goldstein, method = "mfv")) %>%
   
   # keep one unique row per day
-  distinct(story_date, all_events_source_target, pos_events_source_target, neg_events_source_target, mode_source_target) %>%
+  distinct(story_date, 
+           all_events_source_target, 
+           pos_events_source_target, 
+           neg_events_source_target, 
+           mode_source_target) %>%
   
-  # make date varible name match cohesion_df
+  # make date variable name match cohesion_df
   rename(Date = story_date) %>%
   
   # ungroup data
@@ -97,10 +101,10 @@ phoenix_formatted_source_target <- phoenix_df_filtered %>%
 
 # grab observations where target is Syria
 phoenix_formatted_target <- phoenix_df_filtered %>%
-
+  
   # grab observations where target is Syria
   filter(grepl("SYR", target)) %>%
-
+  
   # group by date
   group_by(story_date) %>%
   
@@ -113,16 +117,20 @@ phoenix_formatted_target <- phoenix_df_filtered %>%
   # count negative events
   mutate(neg_events_target = sum(goldstein < 0)) %>%
   
-  # sort descending so the mode will the be the more positive event
+  # sort descending so the mode will be the more positive event
   mutate(Intensity = sort(goldstein, decreasing = TRUE)) %>%
   
   # calculate mode
   mutate(mode_target = mfv1(goldstein, method = "mfv")) %>%
   
   # keep one unique row per day
-  distinct(story_date, all_events_target, pos_events_target, neg_events_target, mode_target) %>%
+  distinct(story_date, 
+           all_events_target, 
+           pos_events_target, 
[…]

### 2020-05-27 scripts/secondary-analyses/phoenix/01_formatting_data.R
Specify packages for variables where R gets confused

@@ -76,7 +76,7 @@ phoenix_formatted_source_target <- phoenix_df_filtered %>%
   mutate(Intensity = sort(goldstein, decreasing = TRUE)) %>%
   
   # calculate mode
-  mutate(mode_source_target = mfv1(goldstein, method = "mfv")) %>%
+  mutate(mode_source_target = statip::mfv1(goldstein, method = "mfv")) %>%
   
   # keep one unique row per day
   distinct(story_date, 
@@ -92,7 +92,8 @@ phoenix_formatted_source_target <- phoenix_df_filtered %>%
   ungroup() %>%
   
   # fill in dates that turned up no observations
-  complete(Date = seq.Date(min(as.Date(Date)), max(as.Date(Date)), by="day")) %>%
+  tidyr::complete(Date = seq.Date(min(as.Date(Date)), max(as.Date(Date)), 
+                                  by="day")) %>%
   
   # fill NAs with zeros
   replace(is.na(.), 0)
@@ -121,7 +122,7 @@ phoenix_formatted_target <- phoenix_df_filtered %>%
   mutate(Intensity = sort(goldstein, decreasing = TRUE)) %>%
   
   # calculate mode
-  mutate(mode_target = mfv1(goldstein, method = "mfv")) %>%
+  mutate(mode_target = statip::mfv1(goldstein, method = "mfv")) %>%
   
   # keep one unique row per day
   distinct(story_date, 
@@ -137,7 +138,8 @@ phoenix_formatted_target <- phoenix_df_filtered %>%
   ungroup() %>%
   
   # fill in dates that turned up no observations
-  complete(Date = seq.Date(min(as.Date(Date)), max(as.Date(Date)), by="day")) %>%
+  tidyr::complete(Date = seq.Date(min(as.Date(Date)), max(as.Date(Date)), 
+                                  by="day")) %>%
   
   # fill NAs with zeros
   replace(is.na(.), 0)

### 2020-05-27 scripts/secondary-analyses/phoenix/01_formatting_data.R
Simplify sextile procedure

@@ -144,96 +144,49 @@ phoenix_formatted_target <- phoenix_df_filtered %>%
   # fill NAs with zeros
   replace(is.na(.), 0)
 
-# bind the event and social cohesion data frames
-phoenix_df_formatted <- cbind(phoenix_formatted_source_target, phoenix_formatted_target, cohesion_df)
+### prepare cohesion dataframe for merging ###
 
-# keep only what we need
-phoenix_df_formatted <- phoenix_df_formatted[c("Date", 
-                                           "all_events_source_target", 
-                                           "pos_events_source_target", 
-                                           "neg_events_source_target", 
-                                           "mode_source_target", 
-                                           "all_events_target", 
-                                           "pos_events_target", 
-                                           "neg_events_target", 
-                                           "mode_target", 
-                                           "MeanCohesion")]
+cohesion_df <- cohesion_df %>%
+  
+  # format dates
+  mutate(Date = as.Date(Date)) %>%
+  
+  # only keep variables we need
+  select(Date, MeanCohesion)
+
+### combine all dataframes ###
+
+# bind the event and social cohesion data frames
+phoenix_df_formatted <- dplyr::full_join(phoenix_formatted_source_target,
+                                         phoenix_formatted_target,
+                                         by = c("Date")) %>%
+  dplyr::full_join(., cohesion_df,
+                   by = c("Date"))
 
 #### 3. Create the sextiles for analyses ####
 
-## social cohesion ##
-
-# create the sextiles
-phoenix_df_formatted$coh_sextiles <- with(phoenix_df_formatted, cut(MeanCohesion, 
-                                                                    breaks=quantile(MeanCohesion, probs=seq(0, 1, by=1/6), na.rm=TRUE), 
-                                                                    include.lowest=TRUE))
-
-# re-label with intuitive sextile levels
-levels(phoenix_df_formatted$coh_sextiles) <- factor(c("1","2","3","4", "5", "6"))
-
-### source and target variable sextiles ###
-
-## count of events ##
-
-# create the sextiles
-phoenix_df_formatted$all_sextiles_source_target <- with(phoenix_df_formatted, cut(all_events_source_target, 
-                                                                    breaks=quantile(all_events_source_target, probs=seq(0, 1, by=1/6), na.rm=TRUE), 
[…]

### 2020-05-27 scripts/secondary-analyses/phoenix/01_formatting_data.R
Help us out with some informative output along the way

@@ -220,7 +220,11 @@ original_ts <- as.data.frame(t(original_ts))
 shuffled_coh <- rbind(shuffled_coh, original_ts)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_coh))
+print(paste0("Total distinct shuffled social cohesion time series for CRQA: ",
+             nrow(distinct(shuffled_coh))))
+if(nrow(distinct(shuffled_coh)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_coh <- as.data.frame(t(shuffled_coh))
@@ -248,7 +252,11 @@ original_ts_all <- as.data.frame(t(original_ts_all))
 shuffled_all_source_target <- rbind(shuffled_all_source_target, original_ts_all)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_all_source_target))
+print(paste0("Total distinct shuffled all-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_all_source_target))))
+if(nrow(distinct(shuffled_all_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_all_source_target <- as.data.frame(t(shuffled_all_source_target))
@@ -274,7 +282,11 @@ original_ts_pos <- as.data.frame(t(original_ts_pos))
 shuffled_pos_source_target <- rbind(shuffled_pos_source_target, original_ts_pos)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_pos_source_target))
+print(paste0("Total distinct shuffled positive-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_pos_source_target))))
+if(nrow(distinct(shuffled_pos_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_pos_source_target <- as.data.frame(t(shuffled_pos_source_target))
@@ -300,7 +312,11 @@ original_ts_neg <- as.data.frame(t(original_ts_neg))
 shuffled_neg_source_target <- rbind(shuffled_neg_source_target, original_ts_neg)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_neg_source_target))
[…]

### 2020-05-27 manuscript.Rmd
Add appendix to YAML

--- 2020-05-27 manuscript.Rmd
@@
 draft             : no
+appendix          : "appendix.Rmd"
 
@@
 knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
+knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
 
@@
 \newpage
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix.Rmd')
+```

### 2020-05-27 manuscript.tex
Add appendix to YAML

--- 2020-05-27 manuscript.tex
@@
 
-\hypertarget{appendix-a}{%
-\section{Appendix A}\label{appendix-a}}
+\begin{verbatim}
+## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
+## 'appendix.Rmd'
+\end{verbatim}
 
-Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020).
-After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data.
-As a results, sextiles were used for these analyses.
-For comparison, the filtered ICEWS data was also transformed into sextiles.
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+Given the inherent issues found in event data sets (Wang, Kennedy,
+Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
+Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
+Peyton, \& Shalmon, 2020). After filtering the data and creating the
+count variables for all, positive, and negative events each day, there
+was not enough variability to transform the data into deciles for the
+target only Phoenix data. As a results, sextiles were used for these
+analyses. For comparison, the filtered ICEWS data was also transformed
+into sextiles.
 
 \hypertarget{crqa-for-phoenix-data-in-sextiles}{%
-\subsection{CRQA for Phoenix data in sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
+\subsection{CRQA for Phoenix data in
+sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
 
@@
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
@@
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
 \endhead
-DET & 29.441 & 0.617 & & 38.232 & 0.000 & *** & 30.792 & 0.332 &\tabularnewline
-NRLINE & 140.000 & 0.457 & & 168.000 & 0.000 & *** & 141.000 & 0.450 &\tabularnewline
-maxL & 4.000 & 0.443 & & 5.000 & 0.088 & . & 4.000 & 0.454 &\tabularnewline
+DET & 29.441 & 0.617 & & 38.232 & 0.000 & *** & 30.792 & 0.332
+&\tabularnewline
+NRLINE & 140.000 & 0.457 & & 168.000 & 0.000 & *** & 141.000 & 0.450
+&\tabularnewline
+maxL & 4.000 & 0.443 & & 5.000 & 0.088 & . & 4.000 & 0.454
+&\tabularnewline
 L & 2.143 & 0.894 & & 2.292 & 0.014 & * & 2.234 & 0.165 &\tabularnewline
-ENTR & 0.420 & 0.904 & & 0.683 & 0.012 & * & 0.569 & 0.239 &\tabularnewline
-rENTR & 0.382 & 0.750 & & 0.492 & 0.171 & & 0.518 & 0.096 & .\tabularnewline
-LAM & 31.600 & 0.350 & & 42.105 & 0.042 & * & 29.619 & 0.625 &\tabularnewline
+ENTR & 0.420 & 0.904 & & 0.683 & 0.012 & * & 0.569 & 0.239
+&\tabularnewline
+rENTR & 0.382 & 0.750 & & 0.492 & 0.171 & & 0.518 & 0.096 &
+.\tabularnewline
+LAM & 31.600 & 0.350 & & 42.105 & 0.042 & * & 29.619 & 0.625
+&\tabularnewline
 TT & 2.252 & 0.247 & & 2.356 & 0.142 & & 2.295 & 0.314 &\tabularnewline
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Phoenix data.
-CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrepective of filtering.}\tabularnewline
+\caption{CRQA results for source and target Phoenix
+data.}\tabularnewline
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
@@
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
 \endhead
-DET & 32.677 & 0.069 & . & 37.313 & 0.000 & *** & 31.610 & 0.130 &\tabularnewline
-NRLINE & 152.000 & 0.047 & * & 160.000 & 0.000 & *** & 145.000 & 0.133 &\tabularnewline
-maxL & 4.000 & 0.465 & & 7.000 & 0.001 & *** & 4.000 & 0.448 &\tabularnewline
-L & 2.184 & 0.577 & & 2.344 & 0.000 & *** & 2.193 & 0.476 &\tabularnewline
-ENTR & 0.507 & 0.550 & & 0.751 & 0.000 & *** & 0.523 & 0.446 &\tabularnewline
-rENTR & 0.462 & 0.289 & & 0.466 & 0.247 & & 0.476 & 0.214 &\tabularnewline
-LAM & 40.453 & 0.051 & . & 50.746 & 0.001 & *** & 32.008 & 0.453 &\tabularnewline
-TT & 2.446 & 0.044 & * & 2.217 & 0.376 & & 2.284 & 0.327 &\tabularnewline
+DET & 32.677 & 0.069 & . & 37.313 & 0.000 & *** & 31.610 & 0.130
+&\tabularnewline
+NRLINE & 152.000 & 0.047 & * & 160.000 & 0.000 & *** & 145.000 & 0.133
+&\tabularnewline
+maxL & 4.000 & 0.465 & & 7.000 & 0.001 & *** & 4.000 & 0.448
+&\tabularnewline
+L & 2.184 & 0.577 & & 2.344 & 0.000 & *** & 2.193 & 0.476
+&\tabularnewline
+ENTR & 0.507 & 0.550 & & 0.751 & 0.000 & *** & 0.523 & 0.446
+&\tabularnewline
+rENTR & 0.462 & 0.289 & & 0.466 & 0.247 & & 0.476 & 0.214
+&\tabularnewline
+LAM & 40.453 & 0.051 & . & 50.746 & 0.001 & *** & 32.008 & 0.453
+&\tabularnewline
+TT & 2.446 & 0.044 & * & 2.217 & 0.376 & & 2.284 & 0.327
+&\tabularnewline
 \bottomrule
@@
 
+CRQ analyses for sextiled Phoenix event data found increased levels of
+coupling between positive events and social cohesion, irrespective of
+target or source and target filtering. Negative events were not coupled
+with social cohesion irrepective of filtering.
+
 \hypertarget{crqa-for-icews-data-in-sextiles}{%
-\subsection{CRQA for ICEWS data in sextiles}\label{crqa-for-icews-data-in-sextiles}}
+\subsection{CRQA for ICEWS data in
+sextiles}\label{crqa-for-icews-data-in-sextiles}}
 
@@
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
 \endhead
-DET & 38.636 & 0.000 & *** & 36.759 & 0.001 & *** & 36.858 & 0.000 & ***\tabularnewline
-NRLINE & 175.000 & 0.000 & *** & 165.000 & 0.001 & *** & 161.000 & 0.002 & **\tabularnewline
-maxL & 5.000 & 0.079 & . & 4.000 & 0.438 & & 6.000 & 0.013 & *\tabularnewline
-L & 2.234 & 0.148 & & 2.255 & 0.086 & . & 2.317 & 0.003 & **\tabularnewline
-ENTR & 0.596 & 0.131 & & 0.623 & 0.088 & . & 0.723 & 0.002 & **\tabularnewline
-rENTR & 0.430 & 0.450 & & 0.567 & 0.047 & * & 0.449 & 0.394 &\tabularnewline
-LAM & 42.984 & 0.035 & * & 37.846 & 0.096 & . & 39.625 & 0.062 & .\tabularnewline
-TT & 2.254 & 0.228 & & 2.471 & 0.036 & * & 2.373 & 0.081 & .\tabularnewline
+DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
+***\tabularnewline
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
+& ***\tabularnewline
+maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
+.\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
+**\tabularnewline
+ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
+**\tabularnewline
+rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
+&\tabularnewline
+LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
+*\tabularnewline
+TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
+.\tabularnewline
 \bottomrule
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target ICEWS data.
-CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.}\tabularnewline
+\caption{CRQA results for source and target ICEWS data.}\tabularnewline
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
@@
 \toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
 \midrule
 \endhead
-DET & 32.840 & 0.061 & . & 37.451 & 0.000 & *** & 38.741 & 0.000 & ***\tabularnewline
-NRLINE & 145.000 & 0.208 & & 166.000 & 0.001 & *** & 173.000 & 0.000 & ***\tabularnewline
-maxL & 5.000 & 0.084 & . & 5.000 & 0.093 & . & 7.000 & 0.002 & **\tabularnewline
-L & 2.297 & 0.007 & ** & 2.283 & 0.017 & * & 2.277 & 0.026 & *\tabularnewline
-ENTR & 0.693 & 0.005 & ** & 0.667 & 0.016 & * & 0.632 & 0.058 & .\tabularnewline
-rENTR & 0.500 & 0.128 & & 0.481 & 0.180 & & 0.393 & 0.724 &\tabularnewline
-LAM & 34.221 & 0.208 & & 41.996 & 0.034 & * & 41.003 & 0.037 & *\tabularnewline
-TT & 2.239 & 0.276 & & 2.348 & 0.107 & & 2.279 & 0.231 &\tabularnewline
+DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+***\tabularnewline
+NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+***\tabularnewline
+maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
+**\tabularnewline
+L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
+**\tabularnewline
+ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
+**\tabularnewline
+rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
+&\tabularnewline
+LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
+**\tabularnewline
+TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
+&\tabularnewline
 \bottomrule
@@
 
+CRQ analyses for sextiled ICEWS event data found coupling between both
+positive and negative events with social cohesion, irrespective of
+target or source and target filtering. Negative events were more stongly
+coupled with social cohesion than positive events for the target only
+analyses. The abscence of coupling between negative events and social
+cohesion in the Phoenix CRQ analyses speaks to the unreliability of
+event data, and that nonlinear analyses in general are only as valuable
+as the quality of the data being used.
+
 \hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
-\subsection{Windowed CRQA for Phoenix data in sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
+\subsection{Windowed CRQA for Phoenix data in
+sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
 
-\hypertarget{syria-as-target-4}{%
-\subsubsection{Syria as Target}\label{syria-as-target-4}}
+\hypertarget{syria-as-target}{%
+\subsubsection{Syria as Target}\label{syria-as-target}}
 
@@
 
-\hypertarget{syria-as-source-and-target-4}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-4}}
+\hypertarget{syria-as-source-and-target}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target}}
 
@@
 \hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
-\subsection{Windowed CRQA for ICEWS data in sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
+\subsection{Windowed CRQA for ICEWS data in
+sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
 
-\hypertarget{syria-as-target-5}{%
-\subsubsection{Syria as Target}\label{syria-as-target-5}}
+\hypertarget{syria-as-target-1}{%
+\subsubsection{Syria as Target}\label{syria-as-target-1}}
 
@@
 
-\hypertarget{syria-as-source-and-target-5}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-5}}
+\hypertarget{syria-as-source-and-target-1}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target-1}}
 
@@
 
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
+Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
+(2020). \emph{Cline center historical phoenix event data. Cline center
+for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
+of Illinois at Urbana-Champaign.
+\url{https://doi.org/10.13012/B2IDB-0647142_V3}
+
+\leavevmode\hypertarget{ref-wang2016growing}{}%
+Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
+pains for global monitoring of societal events. \emph{Science},
+\emph{353}(6307), 1502--1503.
+\end{appendix}
+
 \end{document}

### 2020-05-27 scripts/primary-analyses/01_formatting_data.R
Streamline decile creation

@@ -134,96 +134,49 @@ ICEWS_formatted_target <- ICEWS_filtered %>%
   # undo grouping by date
   ungroup()
 
-# bind the event and social cohesion data frames
-ICEWS_df_formatted <- cbind(ICEWS_formatted_source_target, ICEWS_formatted_target, cohesion_df)
+### prepare cohesion dataframe for merging ###
 
-# keep only what we need
-ICEWS_df_formatted <- ICEWS_df_formatted[c("Date", 
-                                           "all_events_source_target", 
-                                           "pos_events_source_target", 
-                                           "neg_events_source_target", 
-                                           "mode_source_target", 
-                                           "all_events_target", 
-                                           "pos_events_target", 
-                                           "neg_events_target", 
-                                           "mode_target", 
-                                           "MeanCohesion")]
+cohesion_df <- cohesion_df %>%
+  
+  # format dates
+  mutate(Date = as.Date(Date)) %>%
+  
+  # only keep variables we need
+  select(Date, MeanCohesion)
+
+### combine all dataframes ###
+
+# bind the event and social cohesion data frames
+ICEWS_df_formatted <- dplyr::full_join(ICEWS_formatted_source_target,
+                                       ICEWS_formatted_target,
+                                       by=c("Date")) %>%
+  dplyr::full_join(., cohesion_df,
+                   by=c("Date"))
 
 #### 3. Create the deciles for analyses ####
 
-## social cohesion ##
-
-# create the deciles
-ICEWS_df_formatted$coh_deciles <- with(ICEWS_df_formatted, cut(MeanCohesion, 
-                                                               breaks=quantile(MeanCohesion, probs=seq(0, 1, by=0.1), na.rm=TRUE), 
-                                                               include.lowest=TRUE))
-
-# re-label with intuitive decile levels
-levels(ICEWS_df_formatted$coh_deciles) <- factor(c("1","2","3","4", "5", "6", "7", "8", "9", "10"))
-
-### source and target variable deciles ###
-
-## count of events ##
-
-# create the deciles
-ICEWS_df_formatted$all_deciles_source_target <- with(ICEWS_df_formatted, cut(all_events_source_target, 
-                                  breaks=quantile(all_events_source_target, probs=seq(0, 1, by=0.1), na.rm=TRUE), 
[…]

### 2020-05-27 scripts/primary-analyses/01_formatting_data.R
Help us out with informative messages during surrogate creation

@@ -187,7 +187,7 @@ write.table(x = ICEWS_df_formatted,
             col.names=TRUE,
             row.names=FALSE)
 
-#### 4. Create randomized time series for permutation testing for crqa ####
+#### 4. Create randomized time series for permutation testing for CRQA ####
 
 # set seed for reproducibility
 set.seed(123)
@@ -210,8 +210,11 @@ original <- as.data.frame(t(original))
 shuffled_coh <- rbind(shuffled_coh, original)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_coh))
-
+print(paste0("Total distinct shuffled social cohesion time series for CRQA: ",
+             nrow(distinct(shuffled_coh))))
+if(nrow(distinct(shuffled_coh)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 # transform rows to columns for binding
 shuffled_coh <- as.data.frame(t(shuffled_coh))
 
@@ -238,7 +241,11 @@ original_all <- as.data.frame(t(original_all))
 shuffled_all_source_target <- rbind(shuffled_all_source_target, original_all)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_all_source_target))
+print(paste0("Total distinct shuffled all-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_all_source_target))))
+if(nrow(distinct(shuffled_all_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_all_source_target <- as.data.frame(t(shuffled_all_source_target))
@@ -264,7 +271,11 @@ original_pos <- as.data.frame(t(original_pos))
 shuffled_pos_source_target <- rbind(shuffled_pos_source_target, original_pos)
 
 # check to see if we have 1001 distinct time series
-nrow(distinct(shuffled_pos_source_target))
+print(paste0("Total distinct shuffled positive-event time series (source and target) for CRQA: ",
+             nrow(distinct(shuffled_pos_source_target))))
+if(nrow(distinct(shuffled_pos_source_target)) != 1001){
+  print("WARNING: Duplicates in surrogate time series.")
+}
 
 # transform rows to columns for binding
 shuffled_pos_source_target <- as.data.frame(t(shuffled_pos_source_target))
[…]

### 2020-05-27 manuscript.Rmd
Add appendix to YAML

--- 2020-05-27 manuscript.Rmd
@@
 knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
-knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
+#knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
 
@@
 \newpage
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('appendix.Rmd')
-```

### 2020-05-27 manuscript.tex
Add appendix to YAML

--- 2020-05-27 manuscript.tex
@@
 
+\begin{verbatim}
+## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
+## 'appendix.Rmd'
+\end{verbatim}
+
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+Given the inherent issues found in event data sets (Wang, Kennedy,
+Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
+Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
+Peyton, \& Shalmon, 2020). After filtering the data and creating the
+count variables for all, positive, and negative events each day, there
+was not enough variability to transform the data into deciles for the
+target only Phoenix data. As a results, sextiles were used for these
+analyses. For comparison, the filtered ICEWS data was also transformed
+into sextiles.
+
+\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
+\subsection{CRQA for Phoenix data in
+sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only Phoenix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
+&\tabularnewline
+NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
+&\tabularnewline
+maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
+&\tabularnewline
+L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
+ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
+&\tabularnewline
+rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
+&\tabularnewline
+LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
+&\tabularnewline
+TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
+.\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target Phoenix
+data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
+&\tabularnewline
+NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
+&\tabularnewline
+maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
+&\tabularnewline
+L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
+ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
+&\tabularnewline
+rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
+&\tabularnewline
+LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
+&\tabularnewline
+TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
+*\tabularnewline
+\bottomrule
+\end{longtable}
+
+CRQ analyses for sextiled Phoenix event data found increased levels of
+coupling between positive events and social cohesion, irrespective of
+target or source and target filtering. Negative events were not coupled
+with social cohesion irrepective of filtering.
+
+\hypertarget{crqa-for-icews-data-in-sextiles}{%
+\subsection{CRQA for ICEWS data in
+sextiles}\label{crqa-for-icews-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
+***\tabularnewline
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
+& ***\tabularnewline
+maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
+.\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
+**\tabularnewline
+ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
+**\tabularnewline
+rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
+&\tabularnewline
+LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
+*\tabularnewline
+TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
+.\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+***\tabularnewline
+NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+***\tabularnewline
+maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
+**\tabularnewline
+L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
+**\tabularnewline
+ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
+**\tabularnewline
+rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
+&\tabularnewline
+LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
+**\tabularnewline
+TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
+&\tabularnewline
+\bottomrule
+\end{longtable}
+
+CRQ analyses for sextiled ICEWS event data found coupling between both
+positive and negative events with social cohesion, irrespective of
+target or source and target filtering. Negative events were more stongly
+coupled with social cohesion than positive events for the target only
+analyses. The abscence of coupling between negative events and social
+cohesion in the Phoenix CRQ analyses speaks to the unreliability of
+event data, and that nonlinear analyses in general are only as valuable
+as the quality of the data being used.
+
+\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
+\subsection{Windowed CRQA for Phoenix data in
+sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
+
+\hypertarget{syria-as-target}{%
+\subsubsection{Syria as Target}\label{syria-as-target}}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target}}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
+\subsection{Windowed CRQA for ICEWS data in
+sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
+
+\hypertarget{syria-as-target-1}{%
+\subsubsection{Syria as Target}\label{syria-as-target-1}}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target-1}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target-1}}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\end{figure}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
+Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
+(2020). \emph{Cline center historical phoenix event data. Cline center
+for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
+of Illinois at Urbana-Champaign.
+\url{https://doi.org/10.13012/B2IDB-0647142_V3}
+
+\leavevmode\hypertarget{ref-wang2016growing}{}%
+Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
+pains for global monitoring of societal events. \emph{Science},
+\emph{353}(6307), 1502--1503.
+\end{appendix}
+
 \end{document}

### 2020-05-27 appendix.Rmd
Add appendix Rmd

```{r setup-appendix, include = FALSE}

# clear the workspace
rm(list=ls())

# install and load required packages
source('./scripts/required_packages.r')
source('./scripts/libraries_and_functions.r')

# turn on caching
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

# restrict floating
knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")

```
Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Phoenix Event Data [@illinoisdatabankIDB-2796521]. After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data. As a results, sextiles were used for these analyses. For comparison, the filtered ICEWS data was also transformed into sextiles.

## CRQA for Phoenix data in sextiles
```{r secondary-crqa-phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run crqa on sextiled phoenix data
source('./scripts/secondary-analyses/phoenix/02_crqa.R')

# read in metric names
phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])

```

```{r secondary-crqa-table-phoenix-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
phoenix_target_results <- as.data.frame(cbind(phoenix_metrics,
                                      phoenix_metrics_all_targ,
                                      phoenix_sig_all_targ,
                                      phoenix_metrics_pos_targ,
                                      phoenix_sig_pos_targ,
                                      phoenix_metrics_neg_targ,
                                      phoenix_sig_neg_targ),
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
phoenix_target_results[,numerics] <- sapply(phoenix_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(phoenix_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(phoenix_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(phoenix_target_results[,7]))

phoenix_target_results <- cbind(phoenix_target_results, stars_all, stars_pos, stars_neg)
phoenix_target_results <- phoenix_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(phoenix_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")

# exclude row names
rownames(phoenix_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(phoenix_target_results, caption = "CRQA results for target only Phoenix data.")

```

```{r secondary-crqa-table-phoenix-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
phoenix_source_target_results <- as.data.frame(cbind(phoenix_metrics,
                                      phoenix_metrics_all_source_targ,
                                      phoenix_sig_all_source_targ,
                                      phoenix_metrics_pos_source_targ,
                                      phoenix_sig_pos_source_targ,
                                      phoenix_metrics_neg_source_targ,
                                      phoenix_sig_neg_source_targ),
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
phoenix_source_target_results[,numerics] <- sapply(phoenix_source_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(phoenix_source_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(phoenix_source_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(phoenix_source_target_results[,7]))

phoenix_source_target_results <- cbind(phoenix_source_target_results, stars_all, stars_pos, stars_neg)
phoenix_source_target_results <- phoenix_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(phoenix_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")

# exclude row names
rownames(phoenix_source_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(phoenix_source_target_results, caption = "CRQA results for source and target Phoenix data.")

```

CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering. Negative events were not coupled with social cohesion irrepective of filtering.

## CRQA for ICEWS data in sextiles
```{r secondary-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run crqa on sextiled icews data
source('./scripts/secondary-analyses/icews/02_crqa.R')

# read in metric names
icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (target filtered)
icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])

# read in signficiance from permutation tests (source and target filtered)
icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])

```

```{r secondary-crqa-table-icews-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
icews_target_results <- as.data.frame(cbind(icews_metrics,
                                      icews_metrics_all_targ,
                                      icews_sig_all_targ,
                                      icews_metrics_pos_targ,
                                      icews_sig_pos_targ,
                                      icews_metrics_neg_targ,
                                      icews_sig_neg_targ),
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
icews_target_results[,numerics] <- sapply(icews_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(icews_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(icews_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(icews_target_results[,7]))

icews_target_results <- cbind(icews_target_results, stars_all, stars_pos, stars_neg)
icews_target_results <- icews_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(icews_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")

# exclude row names
rownames(icews_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(icews_target_results, caption = "CRQA results for target only ICEWS data.")

```

```{r secondary-crqa-table-icews-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
icews_source_target_results <- as.data.frame(cbind(icews_metrics,
                                      icews_metrics_all_source_targ,
                                      icews_sig_all_source_targ,
                                      icews_metrics_pos_source_targ,
                                      icews_sig_pos_source_targ,
                                      icews_metrics_neg_source_targ,
                                      icews_sig_neg_source_targ),
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
icews_source_target_results[,numerics] <- sapply(icews_source_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(icews_source_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(icews_source_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(icews_source_target_results[,7]))

icews_source_target_results <- cbind(icews_source_target_results, stars_all, stars_pos, stars_neg)
icews_source_target_results <- icews_source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(icews_source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")

# exclude row names
rownames(icews_source_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(icews_source_target_results, caption = "CRQA results for source and target ICEWS data.")

```

CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering. Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.

## Windowed CRQA for Phoenix data in sextiles
```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run windowed crqa on sextiled Phoenix data
source('./scripts/secondary-analyses/Phoenix/03_windowed_crqa.R')

```

### Syria as Target
```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR.png")

```

```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET.png")

```

```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR.png")

```

```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET.png")

```

```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR.png")

```

```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET.png")

```

### Syria as Source and Target
```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR.png")

```

```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET.png")

```

```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR.png")

```

```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET.png")

```

```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR.png")

```

```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET.png")

```

## Windowed CRQA for ICEWS data in sextiles
```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run windowed crqa on sextiled icews data
source('./scripts/secondary-analyses/icews/03_windowed_crqa.R')

```

### Syria as Target
```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")

```

```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")

```

```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")

```

```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")

```

```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")

```

```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")

```

### Syria as Source and Target

```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")

```

```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")

```

```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")

```

```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")

```

```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")

```

```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}

# call image
knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")

```

### 2020-05-27 appendix.tex
Add appendix Rmd

--- 2020-05-27 manuscript.tex
@@
-\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[english,man]{apa6}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provides euro and other symbols
-\else % if luatex or xelatex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage[]{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
-\hypersetup{
-            pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
-            pdfkeywords={Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
-\usepackage{graphicx,grffile}
+\clearpage
 \makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
+\efloat@restorefloats
 \makeatother
 
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
+\begin{appendix}
+\section{}
+Given the inherent issues found in event data sets (Wang, Kennedy,
+Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
+Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
+Peyton, \& Shalmon, 2020). After filtering the data and creating the
+count variables for all, positive, and negative events each day, there
+was not enough variability to transform the data into deciles for the
+target only Phoenix data. As a results, sextiles were used for these
+analyses. For comparison, the filtered ICEWS data was also transformed
+into sextiles.
 
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
+\subsection{CRQA for Phoenix data in
+sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only Phoenix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
+&\tabularnewline
+NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
+&\tabularnewline
+maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
+&\tabularnewline
+L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
+ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
+&\tabularnewline
+rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
+&\tabularnewline
+LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
+&\tabularnewline
+TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
+.\tabularnewline
+\bottomrule
+\end{longtable}
 
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target Phoenix
+data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
+&\tabularnewline
+NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
+&\tabularnewline
+maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
+&\tabularnewline
+L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
+ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
+&\tabularnewline
+rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
+&\tabularnewline
+LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
+&\tabularnewline
+TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
+*\tabularnewline
+\bottomrule
+\end{longtable}
 
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+CRQ analyses for sextiled Phoenix event data found increased levels of
+coupling between positive events and social cohesion, irrespective of
+target or source and target filtering. Negative events were not coupled
+with social cohesion irrepective of filtering.
 
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\makeatother
-\shorttitle{Arab Spring}
-\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Leah C. Windsor\textsuperscript{3,*}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Center for the Ecological Study of Perception and Action, University of Connecticut\\\textsuperscript{2} Department of Psychological Sciences, University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
-\authornote{
+\hypertarget{crqa-for-icews-data-in-sextiles}{%
+\subsection{CRQA for ICEWS data in
+sextiles}\label{crqa-for-icews-data-in-sextiles}}
 
-Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidge Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
-\keywords{Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
+***\tabularnewline
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
+& ***\tabularnewline
+maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
+.\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
+**\tabularnewline
+ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
+**\tabularnewline
+rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
+&\tabularnewline
+LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
+*\tabularnewline
+TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
+.\tabularnewline
+\bottomrule
+\end{longtable}
 
-\linenumbers
-\usepackage{csquotes}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\fi
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+***\tabularnewline
+NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+***\tabularnewline
+maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
+**\tabularnewline
+L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
+**\tabularnewline
+ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
+**\tabularnewline
+rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
+&\tabularnewline
+LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
+**\tabularnewline
+TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
+&\tabularnewline
+\bottomrule
+\end{longtable}
 
-\title{Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring}
+CRQ analyses for sextiled ICEWS event data found coupling between both
+positive and negative events with social cohesion, irrespective of
+target or source and target filtering. Negative events were more stongly
+coupled with social cohesion than positive events for the target only
+analyses. The abscence of coupling between negative events and social
+cohesion in the Phoenix CRQ analyses speaks to the unreliability of
+event data, and that nonlinear analyses in general are only as valuable
+as the quality of the data being used.
 
-\date{}
-
-\abstract{
-Social mobilization requires effective collective coordination.
-In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
-Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
-Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
-Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
-This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
-We conclude with a discussion of implications and applications of nonlinear methods in political science research.
-}
-
-\begin{document}
-\maketitle
-
-Social coordination has long been used both physically and virtually to start and carry out collective actions.
-These collective events bring individuals together and create emergent patterns of communication and action.
-Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
-From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another (Mahner \& Bunge, 1997).
-Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
-The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
-
-\hypertarget{arab-spring}{%
-\subsection{Arab Spring}\label{arab-spring}}
-
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
-His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
-His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
-The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
-These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
-
-\hypertarget{social-cohesion}{%
-\subsection{Social Cohesion}\label{social-cohesion}}
-
-Real-world collective action is known to bring about a sense of togetherness, also known as \enquote{collective effervescence} (Durkheim, 1995).
-This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
-While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
-Just as real-world social cohesion can be quantified, the same is true for online cohesion.
-Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
-Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
-
-\hypertarget{social-media-as-a-platform-for-mobilization}{%
-\subsection{Social Media as a Platform for Mobilization}\label{social-media-as-a-platform-for-mobilization}}
-
-Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
-Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests (Vicari, 2013).
-Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
-As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
-
-\hypertarget{use-of-nonlinear-methods-in-naturally-occurring-data}{%
-\subsection{Use of Nonlinear Methods in Naturally Occurring Data}\label{use-of-nonlinear-methods-in-naturally-occurring-data}}
-
-Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
-Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
-This notion has been increasingly replaced by ideas from dynamical systems theory.
-Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts (Turvey, 2018).
-When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
-Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
-Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
-The primary methods used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and it's off-shoot, windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
-CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions (for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony (Paxton \& Dale, 2017).
-We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
-
-\hypertarget{the-present-work}{%
-\subsection{The Present Work}\label{the-present-work}}
-
-Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
-We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
-Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
-This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
-Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) and windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
-We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
-We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
-Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
-As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
-
-\hypertarget{method}{%
-\section{Method}\label{method}}
-
-\hypertarget{materials}{%
-\subsection{Materials}\label{materials}}
-
-\hypertarget{tweet-corpus}{%
-\subsubsection{Tweet Corpus}\label{tweet-corpus}}
-
-The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
-A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
-For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
-The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
-
-\hypertarget{event-data}{%
-\subsubsection{Event Data}\label{event-data}}
-
-Event data were obtained from the 2012 Integrated Crisis Early Warning System (ICEWS; Boschee et al., 2015).
-The event data were first filtered to remove incomplete and incorrectly formatted data.
-They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
-To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
-
-\hypertarget{data-preparation}{%
-\subsection{Data Preparation}\label{data-preparation}}
-
-\hypertarget{social-cohesion-metric}{%
-\subsubsection{Social Cohesion Metric}\label{social-cohesion-metric}}
-
-The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words' frequencies in the entire tweet corpus.
-If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
-The tweets were first sorted into ascending order by timestamp.
-They were then grouped into successive sets of five tweets.
-Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
-1-3).
-This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
-Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
-
-(insert social cohesion equations here)
-
-The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
-All hashtags and URLs were included in the analysis.
-This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see Jones (1972) and Robertson (2004).
-
-\hypertarget{icews-event-time-series}{%
-\subsubsection{ICEWS Event Time Series}\label{icews-event-time-series}}
-
-Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
-Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
-This well-validated coding scheme allows for numerical quantification of different event types.
-For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
-Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
-Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
-
-\hypertarget{analyses}{%
-\subsection{Analyses}\label{analyses}}
-
-\hypertarget{cross-recurrence-quantification-analysis}{%
-\subsubsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis}}
-
-We first used cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
-As an extension of RQA, which captures the patterns of revisited states of a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992), CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
-Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
-We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
-In CRQA, a recurrent point is when two signals share the same state.
-These shared states can be at the same time or at later points in the time series.
-
-\hypertarget{visualization}{%
-\paragraph{Visualization}\label{visualization}}
-
-A recurrence plot (RP) is the visual representation of CRQA.
-To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
-Visually analyzing these plots can help reveal patterns of structure and recurrence.
-The line y = x is known as the line of identity.
-This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures 3-5 for examples of RPs.
-
-\hypertarget{metrics}{%
-\paragraph{Metrics}\label{metrics}}
-
-The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
-This metrics gives a general description of how frequently the time series are sharing the same states.
-In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
-Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
-The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
-For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
-The average length of the line structures is called mean line (L).
-This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
-The longest line length is called max line (maxL).
-maxL indicates the longest instance of being \enquote{stuck} in a particular state together.
-The total number of lines is called NRLINE.
-The more lines there are, the more coordinated the system may be.
-The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
-These entropy metrics help indicate the stability and predictability of the system.
-When one of the signals gets \enquote{stuck} in a state and the other moves on to other states, this results in vertical line structures.
-The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see Coco and Dale (2018).
-
-\hypertarget{parameters}{%
-\paragraph{Parameters}\label{parameters}}
-
-To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
-Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
-No normalization was done, and lines were considered two or more consecutive recurrent points.
-The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2018).
-
-\hypertarget{permutation-test}{%
-\paragraph{Permutation Test}\label{permutation-test}}
-
-Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R (R Core Team, 2019), 1000 permuted time series were created for each of the real time series.
-A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
-CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
-This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
-Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
-Thus, RR is not included in the inferential tests.
-For more information on permutation tests, see Good (2013).
-
-\hypertarget{windowed-cross-recurrence-quantification-analysis}{%
-\subsubsection{Windowed Cross-Recurrence Quantification Analysis}\label{windowed-cross-recurrence-quantification-analysis}}
-
-We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
-In this analysis, a smaller \enquote{window} of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
-The window remains the same size and \enquote{slides} diagonally up the line of identity.
-The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
-
-\hypertarget{metrics-1}{%
-\paragraph{Metrics}\label{metrics-1}}
-
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
-These metrics can then be plotted as a time series to visualize their evolution over time.
-For these analyses, we decided to visualize recurrence rate and determinism.
-
-\hypertarget{parameters-1}{%
-\paragraph{Parameters}\label{parameters-1}}
-
-In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
-First, a window size must be decided on.
-The window size will determine how many observations are used in each CRQA analysis.
-We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
-The second parameter to be chosen is a step size.
-Window step size is how far the window moves up the line of identity before conducting CRQA again.
-We chose 1 for the step size to understand how the metrics evolve from day to day.
-All other CRQA metrics remained the same as previously noted.
-
-\hypertarget{visualization-1}{%
-\paragraph{Visualization}\label{visualization-1}}
-
-To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
-This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
-These dynamics can then be linked to other external events.
-See Figures 9-14 and 16-21 for examples.
-
-\hypertarget{permutation-test-1}{%
-\paragraph{Permutation Test}\label{permutation-test-1}}
-
-To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
-Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
-The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\begin{figure}
-\includegraphics[width=6.5in]{./results/primary/tally_ts_example} \caption{Example of pre-processed data.}\label{fig:raw-ts}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=6.5in]{./results/primary/deciled_ts_example} \caption{Example of deciled data.}\label{fig:deciled-ts}
-\end{figure}
-
-\hypertarget{cross-recurrence-quantification-analysis-1}{%
-\subsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis-1}}
-
-CRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
+\subsection{Windowed CRQA for Phoenix data in
+sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
 
@@
 
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure 3; Table 1).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
-All other metrics were non-significant (Figure 5; Table 1).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 30.130 & 0.000 & *** & 21.266 & 0.124 & & 25.081 & 0.002 & **\tabularnewline
-NRLINE & 85.000 & 0.000 & *** & 61.000 & 0.162 & & 70.000 & 0.008 & **\tabularnewline
-maxL & 4.000 & 0.046 & * & 4.000 & 0.057 & . & 5.000 & 0.004 & **\tabularnewline
-L & 2.176 & 0.073 & . & 2.148 & 0.193 & & 2.214 & 0.024 & *\tabularnewline
-ENTR & 0.493 & 0.058 & . & 0.438 & 0.154 & & 0.538 & 0.036 & *\tabularnewline
-rENTR & 0.449 & 0.326 & & 0.399 & 0.444 & & 0.388 & 0.527 &\tabularnewline
-LAM & 32.410 & 0.016 & * & 21.591 & 0.252 & & 26.052 & 0.102 &\tabularnewline
-TT & 2.187 & 0.186 & & 2.293 & 0.091 & . & 2.368 & 0.036 & *\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.}\label{fig:plot-rp-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.}\label{fig:plot-rp-targ-neg}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
 \end{figure}
@@
 \hypertarget{syria-as-source-and-target}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target}}
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target}}
 
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure 6; Table 2).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
-All other metrics were non-significant (Figure 8; Table 2).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 28.222 & 0.000 & *** & 23.328 & 0.013 & * & 23.443 & 0.011 & *\tabularnewline
-NRLINE & 83.000 & 0.000 & *** & 66.000 & 0.021 & * & 65.000 & 0.023 & *\tabularnewline
-maxL & 3.000 & 0.429 & & 4.000 & 0.049 & * & 4.000 & 0.048 & *\tabularnewline
-L & 2.084 & 0.708 & & 2.167 & 0.127 & & 2.200 & 0.037 & *\tabularnewline
-ENTR & 0.289 & 0.700 & & 0.475 & 0.108 & & 0.523 & 0.033 & *\tabularnewline
-rENTR & 0.417 & 0.433 & & 0.432 & 0.381 & & 0.476 & 0.225 &\tabularnewline
-LAM & 32.790 & 0.008 & ** & 28.548 & 0.023 & * & 21.639 & 0.201 &\tabularnewline
-TT & 2.284 & 0.085 & . & 2.333 & 0.051 & . & 2.129 & 0.298 &\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-rp-source-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-rp-source-targ-neg}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
 \end{figure}
 
-\hypertarget{windowed-cross-recurrence-quantification-analysis-1}{%
-\subsection{Windowed Cross-Recurrence Quantification Analysis}\label{windowed-cross-recurrence-quantification-analysis-1}}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
+\end{figure}
 
-WCRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019).
-Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-The trend lines are plotted in blue.
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
+\end{figure}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
+\end{figure}
+
+\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
+\subsection{Windowed CRQA for ICEWS data in
+sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
 
@@
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=6.5in]{./results/primary/mode_ts_plot} \caption{Mode ICEWS event per day.}\label{fig:plot-mode-event}
+\hypertarget{syria-as-source-and-target-1}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target-1}}
+
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
 \end{figure}
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
-
-\hypertarget{syria-as-source-and-target-1}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-1}}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
+\begin{figure}[!h]
+\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
-\end{figure}
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
+Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
+(2020). \emph{Cline center historical phoenix event data. Cline center
+for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
+of Illinois at Urbana-Champaign.
+\url{https://doi.org/10.13012/B2IDB-0647142_V3}
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th thorugh 46th window (Figure 16).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
-For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
-These windows span from May 3rd, 2012 to May 14th, 2012.
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
-We examined how social mobilization both virtually and physically evolve over time in tandem.
-Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
-
-\hypertarget{cross-recurrence-quantification-analysis-2}{%
-\subsection{Cross-Recurrence Quantification Analysis}\label{cross-recurrence-quantification-analysis-2}}
-
-\hypertarget{syria-as-target-2}{%
-\subsubsection{Syria as Target}\label{syria-as-target-2}}
-
-The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
-The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
-The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
-The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
-
-\hypertarget{syria-as-source-and-target-2}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-2}}
-
-By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
-These additional observations are times where Syria initiated an event with another country.
-Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
-The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
-Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
-Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on.
-We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
-The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
-By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
-To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
-
-\hypertarget{windowed-recurrence-quantification-analysis}{%
-\subsection{Windowed-Recurrence Quantification Analysis}\label{windowed-recurrence-quantification-analysis}}
-
-\hypertarget{syria-as-target-3}{%
-\subsubsection{Syria as Target}\label{syria-as-target-3}}
-
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
-The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
-These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.
-
-\hypertarget{syria-as-source-and-target-3}{%
-\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-3}}
-
-WCRQ analyses of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
-Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
-WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
-This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
-Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
-
-\hypertarget{conclusion}{%
-\subsection{Conclusion}\label{conclusion}}
-
-Given the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
-If consistent across other civil wars, these results have serious implications for monitoring global movements.
-While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
-By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
-Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
-
-\hypertarget{acknowledgements}{%
-\subsubsection{Acknowledgements}\label{acknowledgements}}
-
-\newpage
-
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
-Boschee, E., Lautenschlager, J., O'Brien, S., Shellman, S., Starz, J., \& Ward, M.
-(2015).
-\emph{ICEWS Coded Event Data} (Version V27) {[}Data set{]}.
-Harvard Dataverse.
-\url{https://doi.org/10.7910/DVN/28075}
-
-\leavevmode\hypertarget{ref-R-crqa}{}%
-Coco, M. I., \& Dale, R. (2018). \emph{Crqa: Cross-recurrence quantification analysis for categorical and continuous time-series}. Retrieved from \url{https://CRAN.R-project.org/package=crqa}
-
-\leavevmode\hypertarget{ref-collins2009violence}{}%
-Collins, R. (2009). \emph{Violence: A micro-sociological theory}. Princeton University Press.
-
-\leavevmode\hypertarget{ref-durkheim1995elementary}{}%
-Durkheim, E. (1995). The elementary forms of religious life, terj. Karen e. Fields. \emph{New York: Free Press.}, \emph{42}, 651669.
-
-\leavevmode\hypertarget{ref-fusaroli2014analyzing}{}%
-Fusaroli, R., Konvalinka, I., \& Wallot, S.
-(2014).
-Analyzing social interactions: The promises and challenges of using cross recurrence quantification analysis.
-In \emph{Translational recurrences} (pp.
-137--155).
-Springer.
-
-\leavevmode\hypertarget{ref-good2013permutation}{}%
-Good, P. (2013). \emph{Permutation tests: A practical guide to resampling methods for testing hypotheses}. Springer Science \& Business Media.
-
-\leavevmode\hypertarget{ref-grenander1959probability}{}%
-Grenander, U. (1959). \emph{Probability and statistics: The harald cramer volume}. Alqvist \& Wiksell.
-
-\leavevmode\hypertarget{ref-jones1972statistical}{}%
-Jones, K. S. (1972). A statistical interpretation of term specificity and its application in retrieval. \emph{Journal of Documentation}.
-
-\leavevmode\hypertarget{ref-koehler2017political}{}%
-Koehler, K. (2017). Political militaries in popular uprisings: A comparative perspective on the arab spring. \emph{International Political Science Review}, \emph{38}(3), 363--377.
-
-\leavevmode\hypertarget{ref-lutterbeck2013arab}{}%
-Lutterbeck, D. (2013). Arab uprisings, armed forces, and civil--military relations. \emph{Armed Forces \& Society}, \emph{39}(1), 28--52.
-
-\leavevmode\hypertarget{ref-mahner1997foundations}{}%
-Mahner, M., \& Bunge, M. (1997). \emph{Foundations of biophilosophy}. Springer Science \& Business Media.
-
-\leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
-Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-robertson2004understanding}{}%
-Robertson, S. (2004). Understanding inverse document frequency: On theoretical arguments for idf. \emph{Journal of Documentation}.
-
-\leavevmode\hypertarget{ref-spaaij2014sports}{}%
-Spaaij, R. (2014). Sports crowd violence: An interdisciplinary synthesis. \emph{Aggression and Violent Behavior}, \emph{19}(2), 146--155.
-
-\leavevmode\hypertarget{ref-turvey2018lectures}{}%
-Turvey, M. T. (2018). \emph{Lectures on perception: An ecological perspective}. Routledge.
-
-\leavevmode\hypertarget{ref-vicari2013public}{}%
-Vicari, S. (2013). Public reasoning around social contention: A case study of twitter use in the italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
-
-\leavevmode\hypertarget{ref-webber1994dynamical}{}%
-Webber Jr, C. L., \& Zbilut, J. P. (1994). Dynamical assessment of physiological systems and states using recurrence plot strategies. \emph{Journal of Applied Physiology}, \emph{76}(2), 965--973.
-
-\leavevmode\hypertarget{ref-webber2005recurrence}{}%
-Webber Jr, C.
-L., \& Zbilut, J.
-P.
-(2005).
-Recurrence quantification analysis of nonlinear dynamical systems.
-\emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences}, \emph{94}(2005), 26--94.
-
-\leavevmode\hypertarget{ref-zbilut1998detecting}{}%
-Zbilut, J.
-P., Giuliani, A., \& Webber Jr, C.
-L.
-(1998).
-Detecting deterministic signals in exceptionally noisy environments using cross-recurrence quantification.
-\emph{Physics Letters A}, \emph{246}(1-2), 122--128.
-
-\leavevmode\hypertarget{ref-zbilut1992embeddings}{}%
-Zbilut, J. P., \& Webber Jr, C. L. (1992). Embeddings and delays as derived from quantification of recurrence plots. \emph{Physics Letters A}, \emph{171}(3-4), 199--203.
-
-\endgroup
-
-\newpage
-
-\end{document}
+\leavevmode\hypertarget{ref-wang2016growing}{}%
+Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
+pains for global monitoring of societal events. \emph{Science},
+\emph{353}(6307), 1502--1503.
+\end{appendix}

### 2020-05-27 scripts/primary-analyses/03_windowed_crqa.R
Fix paths for image saving in primary WCRQA script

@@ -455,7 +455,7 @@ names(significance_neg_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", 
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/primary/windowed-crqa/source_target/windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/primary/windowed-crqa/source_target-windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(4, 24),
      main = "Windowed CRQA for Social\nCohesion and Event Count")
 
@@ -479,7 +479,7 @@ dev.off()
 wincrqa_all_df_source_target$DET[is.na(wincrqa_all_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/primary/windowed-crqa/source_target/windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/primary/windowed-crqa/source_target-windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$DET,xlab='Window',ylab='DET',type='b', ylim = c(0, 53), 
      main = "Windowed CRQA for Social\nCohesion and Event Count")
 
@@ -502,7 +502,7 @@ dev.off()
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/primary/windowed-crqa/source_target/windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/primary/windowed-crqa/source_target-windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_pos_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(6, 23),
      main = "Windowed CRQA for Social\nCohesion and Positive Event Count")
 
@@ -526,7 +526,7 @@ dev.off()
 wincrqa_pos_df_source_target$DET[is.na(wincrqa_pos_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/primary/windowed-crqa/source_target/windowed_pos_DET.png", width = 4, height = 4, units = 'in', res = 300)
[…]

### 2020-05-27 scripts/secondary-analyses/icews/02_crqa.R
Fix paths for image saving in secondary icews scripts

@@ -46,11 +46,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_all_source_target,'./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv',
+write.table(rqa_results_all_source_target,'./results/secondary/icews/crqa/source_target-crqa_results-all_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/secondary/icews/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/icews/crqa/source_target-rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of all events", 
@@ -75,11 +75,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_pos_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_pos_source_target,'./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv',
+write.table(rqa_results_pos_source_target,'./results/secondary/icews/crqa/source_target-crqa_results-pos_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/secondary/icews/crqa/source_target/rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/icews/crqa/source_target-rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of positive events", 
@@ -104,11 +104,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_neg_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_neg_source_target,'./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv',
[…]

### 2020-05-27 scripts/secondary-analyses/icews/03_windowed_crqa.R

@@ -455,7 +455,7 @@ names(significance_neg_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", 
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(4, 30),
      main = "Windowed CRQA for Social\nCohesion and Event Count")
 
@@ -479,7 +479,7 @@ dev.off()
 wincrqa_all_df_source_target$DET[is.na(wincrqa_all_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$DET,xlab='Window',ylab='DET',type='b', ylim = c(0, 55), 
      main = "Windowed CRQA for Social\nCohesion and Event Count")
 
@@ -502,7 +502,7 @@ dev.off()
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_pos_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(8, 33),
      main = "Windowed CRQA for Social\nCohesion and Positive Event Count")
 
@@ -526,7 +526,7 @@ dev.off()
 wincrqa_pos_df_source_target$DET[is.na(wincrqa_pos_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png", width = 4, height = 4, units = 'in', res = 300)
[…]

### 2020-05-27 scripts/secondary-analyses/phoenix/02_crqa.R
Fix paths for image saving in secondary phoenix scripts

@@ -46,11 +46,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_all_source_target,'./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv',
+write.table(rqa_results_all_source_target,'./results/secondary/phoenix/crqa/source_target-crqa_results-all_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/secondary/phoenix/crqa/source_target/rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/phoenix/crqa/source_target-rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of all events", 
@@ -75,11 +75,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_pos_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_pos_source_target,'./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv',
+write.table(rqa_results_pos_source_target,'./results/secondary/phoenix/crqa/source_target-crqa_results-pos_events.csv',
             sep=",", row.names=FALSE)
 
 # build the CRP using 'crqa' package function: plotRP
-png("./results/secondary/phoenix/crqa/source_target/rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/phoenix/crqa/source_target-rp-pos_events.png", width = 4, height = 4, units = 'in', res = 300)
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of positive events", 
@@ -104,11 +104,11 @@ cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
 
 # save the crqa results
 rqa_results_neg_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_neg_source_target,'./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv',
[…]

### 2020-05-27 scripts/secondary-analyses/phoenix/03_windowed_crqa.R

@@ -455,7 +455,7 @@ names(significance_neg_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", 
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/secondary/phoenix/windowed-crqa/source_target/windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(12, 27),
      main = "Windowed RQA for Social\nCohesion and Event Count")
 
@@ -479,7 +479,7 @@ dev.off()
 wincrqa_all_df_source_target$DET[is.na(wincrqa_all_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/secondary/phoenix/windowed-crqa/source_target/windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all_DET.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_all_df_source_target$DET,xlab='Window',ylab='DET',type='b', ylim = c(8,62), 
      main = "Windowed RQA for Social\nCohesion and Event Count")
 
@@ -502,7 +502,7 @@ dev.off()
 # RR plot #
 
 # plot the windows and RRs 
-png("./results/secondary/phoenix/windowed-crqa/source_target/windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
+png("./results/secondary/phoenix/windowed-crqa/source_target-windowed_pos_RR.png", width = 4, height = 4, units = 'in', res = 300)
 plot(wincrqa_pos_df_source_target$RR,xlab='Window',ylab='RR',type='b', ylim = c(10, 28),
      main = "Windowed RQA for Social\nCohesion and Positive Event Count")
 
@@ -526,7 +526,7 @@ dev.off()
 wincrqa_pos_df_source_target$DET[is.na(wincrqa_pos_df_source_target$DET)] <- 0
 
 # plot the windows and RRs 
-png("./results/secondary/phoenix/windowed-crqa/source_target/windowed_pos_DET.png", width = 4, height = 4, units = 'in', res = 300)
[…]

### 2020-05-27 appendix.Rmd
Fix paths for calling images in appendix

@@
 # read in metric names
-phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+phoenix_metrics <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (target filtered)
-phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+phoenix_sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
+phoenix_sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+phoenix_sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
 # read in metrics from crq analyses (source and target filtered)
-phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+phoenix_metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (source and target filtered)
-phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+phoenix_sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
+phoenix_sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+phoenix_sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 # read in metric names
-icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-2,-1])
+icews_metrics <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+icews_metrics_all_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+icews_metrics_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+icews_metrics_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (target filtered)
-icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_all.csv", header = FALSE)[-1,-1])
-icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+icews_sig_all_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
+icews_sig_pos_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+icews_sig_neg_targ <- t(read.csv("./results/secondary/icews/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
 # read in metrics from crq analyses (source and target filtered)
-icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+icews_metrics_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+icews_metrics_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+icews_metrics_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (source and target filtered)
-icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+icews_sig_all_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
+icews_sig_pos_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET.png")
+knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_all_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_pos_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target/windowed_neg_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET.png")
 

### 2020-05-27 appendix.tex
Fix paths for calling images in appendix

@@
 \endhead
-DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
+DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
 &\tabularnewline
-NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
+NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
 &\tabularnewline
-maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
+maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
 &\tabularnewline
-L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
-ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
+L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
+ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
 &\tabularnewline
-rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
+rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
 &\tabularnewline
-LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
+LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
 &\tabularnewline
-TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
+TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
 .\tabularnewline
@@
 \endhead
-DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
+DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
 &\tabularnewline
-NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
+NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
 &\tabularnewline
-maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
+maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
 &\tabularnewline
-L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
-ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
+L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
+ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
 &\tabularnewline
-rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
+rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
 &\tabularnewline
-LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
+LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
 &\tabularnewline
-TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
+TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
 *\tabularnewline
@@
 ***\tabularnewline
-NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
 & ***\tabularnewline
-maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
-.\tabularnewline
-L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
+maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
+&\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
 **\tabularnewline
-ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
+ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
 **\tabularnewline
-rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
+rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
 &\tabularnewline
-LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
+LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
 *\tabularnewline
-TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
-.\tabularnewline
+TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
+&\tabularnewline
 \bottomrule
@@
 \endhead
-DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
 ***\tabularnewline
-NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
 ***\tabularnewline
-maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
+maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
 **\tabularnewline
-L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
+L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
 **\tabularnewline
-ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
+ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
 **\tabularnewline
-rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
+rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
 &\tabularnewline
-LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
+LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
 **\tabularnewline
-TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
+TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
 &\tabularnewline
@@
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
 \end{figure}
@@
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/Phoenix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
 \end{figure}
@@
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
 \end{figure}
@@
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
 \end{figure}
 
-\begin{figure}[!h]
-\includegraphics[width=4in,]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
 \end{figure}

### 2020-05-27 manuscript.Rmd
Fix paths in manuscript Rmd

--- 2020-05-27 manuscript.Rmd
@@
 # read in metrics from crq analyses (source and target filtered)
-metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-all_events.csv", header = FALSE)[-1,-1])
-metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target/crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
 # read in signficiance from permutation tests (source and target filtered)
-sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_all.csv", header = FALSE)[-1,-1])
-sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_pos.csv", header = FALSE)[-1,-1])
-sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target/metric_signif_neg.csv", header = FALSE)[-1,-1])
+sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/source_target/rp-all_events.png")
+knitr::include_graphics("./results/primary/crqa/source_target-rp-all_events.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/source_target/rp-pos_events.png")
+knitr::include_graphics("./results/primary/crqa/source_target-rp-pos_events.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/crqa/source_target/rp-neg_events.png")
+knitr::include_graphics("./results/primary/crqa/source_target-rp-neg_events.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_all_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_all_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_pos_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_pos_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_neg_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target/windowed_neg_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_all_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_all_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_pos_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_pos_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_DET.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_neg_RR.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_RR.png")
 
@@
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target/windowed_neg_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_DET.png")
 

### 2020-05-27 manuscript.tex
Fix paths in manuscript Rmd

--- 2020-05-27 manuscript.tex
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ-all}
+\includegraphics[width=4in]{./results/primary/crqa/target-rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.}\label{fig:plot-rp-targ-pos}
+\includegraphics[width=4in]{./results/primary/crqa/target-rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.}\label{fig:plot-rp-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.}\label{fig:plot-rp-targ-neg}
+\includegraphics[width=4in]{./results/primary/crqa/target-rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.}\label{fig:plot-rp-targ-neg}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ-all}
+\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-rp-source-targ-pos}
+\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-rp-source-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target/rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-rp-source-targ-neg}
+\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-rp-source-targ-neg}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
+\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
 \end{figure}
@@
 
+\begin{verbatim}
+## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
+## 'appendix.Rmd'
+\end{verbatim}
+
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+Given the inherent issues found in event data sets (Wang, Kennedy,
+Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
+Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
+Peyton, \& Shalmon, 2020). After filtering the data and creating the
+count variables for all, positive, and negative events each day, there
+was not enough variability to transform the data into deciles for the
+target only Phoenix data. As a results, sextiles were used for these
+analyses. For comparison, the filtered ICEWS data was also transformed
+into sextiles.
+
+\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
+\subsection{CRQA for Phoenix data in
+sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only Phoenix data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
+&\tabularnewline
+NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
+&\tabularnewline
+maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
+&\tabularnewline
+L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
+ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
+&\tabularnewline
+rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
+&\tabularnewline
+LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
+&\tabularnewline
+TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
+.\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target Phoenix
+data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
+&\tabularnewline
+NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
+&\tabularnewline
+maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
+&\tabularnewline
+L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
+ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
+&\tabularnewline
+rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
+&\tabularnewline
+LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
+&\tabularnewline
+TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
+*\tabularnewline
+\bottomrule
+\end{longtable}
+
+CRQ analyses for sextiled Phoenix event data found increased levels of
+coupling between positive events and social cohesion, irrespective of
+target or source and target filtering. Negative events were not coupled
+with social cohesion irrepective of filtering.
+
+\hypertarget{crqa-for-icews-data-in-sextiles}{%
+\subsection{CRQA for ICEWS data in
+sextiles}\label{crqa-for-icews-data-in-sextiles}}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for target only ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
+***\tabularnewline
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
+& ***\tabularnewline
+maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
+&\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
+**\tabularnewline
+ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
+**\tabularnewline
+rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
+&\tabularnewline
+LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
+*\tabularnewline
+TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
+&\tabularnewline
+\bottomrule
+\end{longtable}
+
+\begin{longtable}[]{@{}cccccccccc@{}}
+\caption{CRQA results for source and target ICEWS data.}\tabularnewline
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+metric & all events & p & sig. & positive events & p & sig. & negative
+events & p & sig.\tabularnewline
+\midrule
+\endhead
+DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+***\tabularnewline
+NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+***\tabularnewline
+maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
+**\tabularnewline
+L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
+**\tabularnewline
+ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
+**\tabularnewline
+rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
+&\tabularnewline
+LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
+**\tabularnewline
+TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
+&\tabularnewline
+\bottomrule
+\end{longtable}
+
+CRQ analyses for sextiled ICEWS event data found coupling between both
+positive and negative events with social cohesion, irrespective of
+target or source and target filtering. Negative events were more stongly
+coupled with social cohesion than positive events for the target only
+analyses. The abscence of coupling between negative events and social
+cohesion in the Phoenix CRQ analyses speaks to the unreliability of
+event data, and that nonlinear analyses in general are only as valuable
+as the quality of the data being used.
+
+\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
+\subsection{Windowed CRQA for Phoenix data in
+sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
+
+\hypertarget{syria-as-target}{%
+\subsubsection{Syria as Target}\label{syria-as-target}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
+\end{figure}
+
+\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
+\subsection{Windowed CRQA for ICEWS data in
+sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
+
+\hypertarget{syria-as-target-1}{%
+\subsubsection{Syria as Target}\label{syria-as-target-1}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
+\end{figure}
+
+\hypertarget{syria-as-source-and-target-1}{%
+\subsubsection{Syria as Source and
+Target}\label{syria-as-source-and-target-1}}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\end{figure}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
+Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
+(2020). \emph{Cline center historical phoenix event data. Cline center
+for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
+of Illinois at Urbana-Champaign.
+\url{https://doi.org/10.13012/B2IDB-0647142_V3}
+
+\leavevmode\hypertarget{ref-wang2016growing}{}%
+Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
+pains for global monitoring of societal events. \emph{Science},
+\emph{353}(6307), 1502--1503.
+\end{appendix}
+
 \end{document}

### 2020-05-27 appendix.Rmd
Fix syntax

@@
 icews_sig_neg_source_targ <- t(read.csv("./results/secondary/icews/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
-
 ```

### 2020-05-27 manuscript.Rmd
Fix syntax

@@
 dir.create("./results/primary/windowed-crqa", recursive = TRUE)
-dir.create("./results/secondary/icews/crqa/source_target", recursive = TRUE)
-dir.create("./results/secondary/icews/crqa/target", recursive = TRUE)
-dir.create("./results/secondary/icews/windowed-crqa/source_target", recursive = TRUE)
-dir.create("./results/secondary/icews/windowed-crqa/target", recursive = TRUE)
-dir.create("./results/secondary/phoenix/crqa/source_target", recursive = TRUE)
-dir.create("./results/secondary/phoenix/crqa/target", recursive = TRUE)
-dir.create("./results/secondary/phoenix/windowed-crqa/source_target", recursive = TRUE)
-dir.create("./results/secondary/phoenix/windowed-crqa/target", recursive = TRUE)
+dir.create("./results/secondary/icews/crqa", recursive = TRUE)
+dir.create("./results/secondary/icews/windowed-crqa", recursive = TRUE)
+dir.create("./results/secondary/phoenix/crqa", recursive = TRUE)
+dir.create("./results/secondary/phoenix/windowed-crqa", recursive = TRUE)
 
@@
 \endgroup
-
-\newpage

### 2020-05-27 manuscript.tex
Fix syntax

@@
 \endhead
-DET & 30.130 & 0.000 & *** & 21.266 & 0.124 & & 25.081 & 0.002 & **\tabularnewline
-NRLINE & 85.000 & 0.000 & *** & 61.000 & 0.162 & & 70.000 & 0.008 & **\tabularnewline
-maxL & 4.000 & 0.046 & * & 4.000 & 0.057 & . & 5.000 & 0.004 & **\tabularnewline
-L & 2.176 & 0.073 & . & 2.148 & 0.193 & & 2.214 & 0.024 & *\tabularnewline
-ENTR & 0.493 & 0.058 & . & 0.438 & 0.154 & & 0.538 & 0.036 & *\tabularnewline
-rENTR & 0.449 & 0.326 & & 0.399 & 0.444 & & 0.388 & 0.527 &\tabularnewline
-LAM & 32.410 & 0.016 & * & 21.591 & 0.252 & & 26.052 & 0.102 &\tabularnewline
-TT & 2.187 & 0.186 & & 2.293 & 0.091 & . & 2.368 & 0.036 & *\tabularnewline
+DET & 28.525 & 0.000 & *** & 19.672 & 0.288 & & 25.902 & 0.001 & ***\tabularnewline
+NRLINE & 80.000 & 0.000 & *** & 57.000 & 0.274 & & 71.000 & 0.005 & **\tabularnewline
+maxL & 4.000 & 0.045 & * & 4.000 & 0.053 & . & 4.000 & 0.053 & .\tabularnewline
+L & 2.175 & 0.082 & . & 2.105 & 0.474 & & 2.225 & 0.021 & *\tabularnewline
+ENTR & 0.481 & 0.079 & . & 0.341 & 0.455 & & 0.575 & 0.015 & *\tabularnewline
+rENTR & 0.438 & 0.352 & & 0.311 & 0.749 & & 0.523 & 0.135 &\tabularnewline
+LAM & 35.902 & 0.002 & ** & 25.738 & 0.062 & . & 29.344 & 0.021 & *\tabularnewline
+TT & 2.147 & 0.238 & & 2.492 & 0.012 & * & 2.295 & 0.049 & *\tabularnewline
 \bottomrule
@@
 \endhead
-DET & 28.222 & 0.000 & *** & 23.328 & 0.013 & * & 23.443 & 0.011 & *\tabularnewline
-NRLINE & 83.000 & 0.000 & *** & 66.000 & 0.021 & * & 65.000 & 0.023 & *\tabularnewline
-maxL & 3.000 & 0.429 & & 4.000 & 0.049 & * & 4.000 & 0.048 & *\tabularnewline
-L & 2.084 & 0.708 & & 2.167 & 0.127 & & 2.200 & 0.037 & *\tabularnewline
-ENTR & 0.289 & 0.700 & & 0.475 & 0.108 & & 0.523 & 0.033 & *\tabularnewline
-rENTR & 0.417 & 0.433 & & 0.432 & 0.381 & & 0.476 & 0.225 &\tabularnewline
-LAM & 32.790 & 0.008 & ** & 28.548 & 0.023 & * & 21.639 & 0.201 &\tabularnewline
-TT & 2.284 & 0.085 & . & 2.333 & 0.051 & . & 2.129 & 0.298 &\tabularnewline
+DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
+NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
+maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
+L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
+ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
+rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
+LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
+TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
 \bottomrule
@@
 \endgroup
-
-\newpage
-
-\begin{verbatim}
-## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
-## 'appendix.Rmd'
-\end{verbatim}
 
@@
 \endhead
-DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
-&\tabularnewline
-NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
-&\tabularnewline
-maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
-&\tabularnewline
-L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
-ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
-&\tabularnewline
-rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
-&\tabularnewline
-LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
-&\tabularnewline
-TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
+DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
+&\tabularnewline
+NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
+&\tabularnewline
+maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
+&\tabularnewline
+L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
+ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
+&\tabularnewline
+rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
+&\tabularnewline
+LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
+&\tabularnewline
+TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
 .\tabularnewline
@@
 \endhead
-DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
-&\tabularnewline
-NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
-&\tabularnewline
-maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
-&\tabularnewline
-L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
-ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
-&\tabularnewline
-rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
-&\tabularnewline
-LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
-&\tabularnewline
-TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
+DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
+&\tabularnewline
+NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
+&\tabularnewline
+maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
+&\tabularnewline
+L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
+ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
+&\tabularnewline
+rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
+&\tabularnewline
+LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
+&\tabularnewline
+TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
 *\tabularnewline
@@
 ***\tabularnewline
-NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
 & ***\tabularnewline
-maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
-&\tabularnewline
-L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
+maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
+.\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
 **\tabularnewline
-ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
+ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
 **\tabularnewline
-rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
-&\tabularnewline
-LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
+rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
+&\tabularnewline
+LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
 *\tabularnewline
-TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
-&\tabularnewline
+TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
+.\tabularnewline
 \bottomrule
@@
 \endhead
-DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
 ***\tabularnewline
-NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
 ***\tabularnewline
-maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
+maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
 **\tabularnewline
-L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
+L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
 **\tabularnewline
-ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
+ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
 **\tabularnewline
-rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
-&\tabularnewline
-LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
+rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
+&\tabularnewline
+LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
 **\tabularnewline
-TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
+TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
 &\tabularnewline

### 2020-05-27 appendix.Rmd
Fix typos in appendix

@@
 CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering.
-Negative events were not coupled with social cohesion irrepective of filtering.
+Negative events were not coupled with social cohesion irrespective of filtering.
 
@@
 CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering.
-Negative events were more stongly coupled with social cohesion than positive events for the target only analyses.
-The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
+Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
+The absence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
 

### 2020-05-27 appendix.tex
Fix syntax
Fix typos in appendix

@@
 \endhead
-DET & 31.065 & 0.246 & & 38.955 & 0.000 & *** & 31.854 & 0.130
+DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
 &\tabularnewline
-NRLINE & 144.000 & 0.220 & & 174.000 & 0.000 & *** & 148.000 & 0.106
+NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
 &\tabularnewline
-maxL & 4.000 & 0.456 & & 5.000 & 0.082 & . & 4.000 & 0.461
+maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
 &\tabularnewline
-L & 2.188 & 0.555 & & 2.270 & 0.030 & * & 2.182 & 0.637 &\tabularnewline
-ENTR & 0.513 & 0.527 & & 0.650 & 0.027 & * & 0.504 & 0.615
+L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
+ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
 &\tabularnewline
-rENTR & 0.467 & 0.273 & & 0.469 & 0.264 & & 0.459 & 0.344
+rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
 &\tabularnewline
-LAM & 32.051 & 0.290 & & 46.154 & 0.007 & ** & 30.769 & 0.333
+LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
 &\tabularnewline
-TT & 2.273 & 0.211 & & 2.400 & 0.071 & . & 2.400 & 0.073 &
+TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
 .\tabularnewline
@@
 \endhead
-DET & 31.558 & 0.168 & & 37.377 & 0.000 & *** & 25.740 & 0.984
+DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
 &\tabularnewline
-NRLINE & 145.000 & 0.172 & & 169.000 & 0.000 & *** & 119.000 & 0.983
+NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
 &\tabularnewline
-maxL & 4.000 & 0.437 & & 5.000 & 0.088 & . & 4.000 & 0.440
+maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
 &\tabularnewline
-L & 2.207 & 0.355 & & 2.243 & 0.125 & & 2.193 & 0.500 &\tabularnewline
-ENTR & 0.547 & 0.334 & & 0.610 & 0.100 & . & 0.521 & 0.494
+L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
+ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
 &\tabularnewline
-rENTR & 0.498 & 0.164 & & 0.440 & 0.411 & & 0.474 & 0.261
+rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
 &\tabularnewline
-LAM & 38.462 & 0.079 & . & 48.718 & 0.001 & *** & 21.795 & 0.798
+LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
 &\tabularnewline
-TT & 2.500 & 0.021 & * & 2.235 & 0.294 & & 2.429 & 0.042 &
+TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
 *\tabularnewline
@@
 target or source and target filtering. Negative events were not coupled
-with social cohesion irrepective of filtering.
+with social cohesion irrespective of filtering.
 
@@
 ***\tabularnewline
-NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.001 & *** & 170.000 & 0.001
+NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
 & ***\tabularnewline
-maxL & 5.000 & 0.074 & . & 5.000 & 0.099 & . & 5.000 & 0.101
+maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
+.\tabularnewline
+L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
+**\tabularnewline
+ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
+**\tabularnewline
+rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
 &\tabularnewline
-L & 2.249 & 0.089 & . & 2.272 & 0.045 & * & 2.306 & 0.009 &
-**\tabularnewline
-ENTR & 0.619 & 0.080 & . & 0.653 & 0.040 & * & 0.705 & 0.007 &
-**\tabularnewline
-rENTR & 0.447 & 0.362 & & 0.471 & 0.246 & & 0.509 & 0.125
-&\tabularnewline
-LAM & 43.590 & 0.017 & * & 39.744 & 0.051 & . & 42.308 & 0.028 &
+LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
 *\tabularnewline
-TT & 2.267 & 0.222 & & 2.385 & 0.093 & . & 2.357 & 0.111
-&\tabularnewline
+TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
+.\tabularnewline
 \bottomrule
@@
 \endhead
-DET & 34.122 & 0.011 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
+DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
 ***\tabularnewline
-NRLINE & 152.000 & 0.037 & * & 168.000 & 0.000 & *** & 173.000 & 0.000 &
+NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
 ***\tabularnewline
-maxL & 5.000 & 0.090 & . & 5.000 & 0.081 & . & 7.000 & 0.005 &
+maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
 **\tabularnewline
-L & 2.276 & 0.026 & * & 2.280 & 0.024 & * & 2.312 & 0.002 &
+L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
 **\tabularnewline
-ENTR & 0.663 & 0.021 & * & 0.661 & 0.021 & * & 0.698 & 0.005 &
+ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
 **\tabularnewline
-rENTR & 0.478 & 0.236 & & 0.477 & 0.233 & & 0.434 & 0.459
+rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
 &\tabularnewline
-LAM & 34.615 & 0.186 & & 39.744 & 0.045 & * & 48.718 & 0.003 &
+LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
 **\tabularnewline
-TT & 2.250 & 0.236 & & 2.385 & 0.077 & . & 2.235 & 0.267
+TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
 &\tabularnewline
@@
 positive and negative events with social cohesion, irrespective of
-target or source and target filtering. Negative events were more stongly
-coupled with social cohesion than positive events for the target only
-analyses. The abscence of coupling between negative events and social
-cohesion in the Phoenix CRQ analyses speaks to the unreliability of
-event data, and that nonlinear analyses in general are only as valuable
-as the quality of the data being used.
+target or source and target filtering. Negative events were more
+strongly coupled with social cohesion than positive events for the
+target only analyses. The absence of coupling between negative events
+and social cohesion in the Phoenix CRQ analyses speaks to the
+unreliability of event data, and that nonlinear analyses in general are
+only as valuable as the quality of the data being used.
 

### 2020-05-27 manuscript.Rmd
Fix typos in manuscript

@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th thorugh 46th window (Figure 16).
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure 16).
 Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
@@
 We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
-The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their saftey.
+The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
 By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
@@
 The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequntly occuring event was almost consistently -10, the most violent event in the coding system.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
 These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
 Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings durig the Arab Spring.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
 

### 2020-05-27 manuscript.Rmd
Fix reference format

@@
 While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
+@gilligan2014civil found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
 Just as real-world social cohesion can be quantified, the same is true for online cohesion.

### 2020-05-27 manuscript.tex
Fix reference format

@@
 While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-Gilligan, Pasquale, and Samii (2013) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
+Gilligan, Pasquale, and Samii (2014) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
 Just as real-world social cohesion can be quantified, the same is true for online cohesion.
@@
 
+\leavevmode\hypertarget{ref-gilligan2014civil}{}%
+Gilligan, M. J., Pasquale, B. J., \& Samii, C. (2014). Civil war and social cohesion: Lab-in-the-field evidence from nepal. \emph{American Journal of Political Science}, \emph{58}(3), 604--619.
+
 \leavevmode\hypertarget{ref-good2013permutation}{}%

### 2020-05-28 appendix.Rmd
Fix formatting for appendix

@@
 # restrict floating
-knitr::opts_chunk$set(fig.pos = "!h", out.extra = "")
+knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
 
 ```
-Given the inherent issues found in event data sets [@wang2016growing], we conducted the same analyses on the Cline Center Historical Phoenix Event Data [@illinoisdatabankIDB-2796521].
-After filtering the data and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles for the target only Phoenix data.
-As a results, sextiles were used for these analyses.
-For comparison, the filtered ICEWS data was also transformed into sextiles.
 
-## CRQA for Phoenix data in sextiles
+# CRQA for Phoenix data in sextiles
 ```{r secondary-crqa-phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
@@
 
-## CRQA for ICEWS data in sextiles
+# CRQA for ICEWS data in sextiles
 ```{r secondary-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
@@
 
-## Windowed CRQA for Phoenix data in sextiles
+# Windowed CRQA for Phoenix data in sextiles
 ```{r secondary-windowed-crqa-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
@@
 ```
-
-### Syria as Target
-```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-### Syria as Source and Target
-```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
 
@@
 
-## Windowed CRQA for ICEWS data in sextiles
+# Windowed CRQA for ICEWS data in sextiles
 ```{r secondary-windowed-crqa-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
@@
 ```
-
-### Syria as Target
-```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
 
@@
 ```
-
-### Syria as Source and Target
-
-```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
 
@@
 ```
-
-```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
 

### 2020-05-28 appendix.tex
Fix formatting for appendix

@@
 \begin{appendix}
-\section{}
-Given the inherent issues found in event data sets (Wang, Kennedy,
-Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the
-Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter,
-Peyton, \& Shalmon, 2020). After filtering the data and creating the
-count variables for all, positive, and negative events each day, there
-was not enough variability to transform the data into deciles for the
-target only Phoenix data. As a results, sextiles were used for these
-analyses. For comparison, the filtered ICEWS data was also transformed
-into sextiles.
-
 \hypertarget{crqa-for-phoenix-data-in-sextiles}{%
-\subsection{CRQA for Phoenix data in
+\section{CRQA for Phoenix data in
 sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
@@
 \hypertarget{crqa-for-icews-data-in-sextiles}{%
-\subsection{CRQA for ICEWS data in
+\section{CRQA for ICEWS data in
 sextiles}\label{crqa-for-icews-data-in-sextiles}}
@@
 \hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
-\subsection{Windowed CRQA for Phoenix data in
+\section{Windowed CRQA for Phoenix data in
 sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
 
-\hypertarget{syria-as-target}{%
-\subsubsection{Syria as Target}\label{syria-as-target}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
 \end{figure}
-
-\hypertarget{syria-as-source-and-target}{%
-\subsubsection{Syria as Source and
-Target}\label{syria-as-source-and-target}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
 \end{figure}
@@
 \hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
-\subsection{Windowed CRQA for ICEWS data in
+\section{Windowed CRQA for ICEWS data in
 sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
 
-\hypertarget{syria-as-target-1}{%
-\subsubsection{Syria as Target}\label{syria-as-target-1}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
 \end{figure}
-
-\hypertarget{syria-as-source-and-target-1}{%
-\subsubsection{Syria as Source and
-Target}\label{syria-as-source-and-target-1}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
 \end{figure}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
-Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
-(2020). \emph{Cline center historical phoenix event data. Cline center
-for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
-of Illinois at Urbana-Champaign.
-\url{https://doi.org/10.13012/B2IDB-0647142_V3}
-
-\leavevmode\hypertarget{ref-wang2016growing}{}%
-Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
-pains for global monitoring of societal events. \emph{Science},
-\emph{353}(6307), 1502--1503.
 \end{appendix}

### 2020-05-28 manuscript.Rmd
Add float package for appendix formatting

@@
 classoption       : "man"
+header-includes   : 
+  - "\\usepackage{float}"
 output            : papaja::apa6_pdf
@@
 Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
-Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was going on.
+Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was happening internally.
 We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
 The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
+Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
 By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
@@
 ### Syria as Source and Target
-WCRQ analyses of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
+WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
 Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
@@
 ## Conclusion
-Given the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
+Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
 If consistent across other civil wars, these results have serious implications for monitoring global movements.

### 2020-05-28 manuscript.tex
Add float package for appendix formatting

@@
 \usepackage{csquotes}
+\usepackage{float}
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
 
-WCRQ analyses of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
+WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
 Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
@@
 
-Given the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
+Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
 If consistent across other civil wars, these results have serious implications for monitoring global movements.
@@
 \hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
-\subsection{Windowed CRQA for Phoenix data in
+\section{Windowed CRQA for Phoenix data in
 sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
 
-\hypertarget{syria-as-target}{%
-\subsubsection{Syria as Target}\label{syria-as-target}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
 \end{figure}
-
-\hypertarget{syria-as-source-and-target}{%
-\subsubsection{Syria as Source and
-Target}\label{syria-as-source-and-target}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
+\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
 \end{figure}
@@
 \hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
-\subsection{Windowed CRQA for ICEWS data in
+\section{Windowed CRQA for ICEWS data in
 sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
 
-\hypertarget{syria-as-target-1}{%
-\subsubsection{Syria as Target}\label{syria-as-target-1}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
 \end{figure}
-
-\hypertarget{syria-as-source-and-target-1}{%
-\subsubsection{Syria as Source and
-Target}\label{syria-as-source-and-target-1}}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
 \end{figure}
-
 \begin{figure}
-\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
 \end{figure}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
-Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D.
-(2020). \emph{Cline center historical phoenix event data. Cline center
-for advanced social research. V1.3.0. May 4} {[}Data set{]}. University
-of Illinois at Urbana-Champaign.
-\url{https://doi.org/10.13012/B2IDB-0647142_V3}
-
-\leavevmode\hypertarget{ref-wang2016growing}{}%
-Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing
-pains for global monitoring of societal events. \emph{Science},
-\emph{353}(6307), 1502--1503.
 \end{appendix}

### 2020-05-28 manuscript.Rmd
Update tweet count

@@
 ### Tweet Corpus
-The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
-A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
-For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
+
+```{r tweet-count, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+
+# read in social cohesion data
+cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+
+```
+
+The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets occurring between March 30, 2012 and June 15, 2012.
 The tweet corpus was scraped from Twitter by [insert search parameters here].

### 2020-05-28 manuscript.tex
Update tweet count

@@
 
-The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
-A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
-For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
-The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
+The corpus of tweets used included 697428 Syrian tweets occurring between March 30, 2012 and June 15, 2012. The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
 

### 2020-05-28 scripts/primary-analyses/02_crqa.R
Setting seed for reproducibility in each subscript (for maximal reproducibility)

@@ -208,6 +208,9 @@ dev.off()
 
 #### 3. Conduct permutation tests ####
 
+# set seed for reproducibility
+set.seed(123)
+
 ### source and target filtered data ###
 
 ## count of all events and social cohesion ##

### 2020-05-28 scripts/primary-analyses/03_windowed_crqa.R

@@ -166,6 +166,9 @@ colnames(wincrqa_neg_df_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR",
 
 #### 3. Conduct permutation tests ####
 
+# set seed for reproducibility
+set.seed(123)
+
 ### source and target filtered data ###
 
 ## count of all events and social cohesion ##

### 2020-05-28 scripts/primary-analyses/03_windowed_crqa.R
Typos and formatting

@@ -4,9 +4,9 @@
 # analysis the real-world events and Twitter social cohesion 
 # of Arab Spring.
 #
-# Code by: M. Chiovaro (@mchiovaro)
+# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_05_21 
+# Last updated: 2020_05_28
 
 #### 1. Set up ####
 
@@ -26,13 +26,13 @@ shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
 shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
 shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
 
-#### 2. Run Windowed CRQA ####
+#### 2. Run windowed CRQA ####
 
 ### source and target filtered data ###
 
 ## count of all events and social cohesion ##
 
-# calculate windowed rqa
+# calculate windowed CRQA
 windowed_all_source_target = wincrqa(ts1 = data$coh_deciles, 
                                        ts2 = data$all_deciles_source_target, 
                                        windowstep = 1, 
@@ -48,13 +48,17 @@ windowed_all_source_target = wincrqa(ts1 = data$coh_deciles,
                                        whiteline = FALSE,
                                        trend = TRUE) 
 
-# tranform into a dataframe for easier plotting 
+# transform into a dataframe for easier plotting 
 wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
-colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
+                                            "ENTR", "rENTR", 
+                                            "LAM", "TT", 
+                                            "window")
 
 ## count of positive events and social cohesion ##
 
-# calculate windowed rqa
+# calculate windowed CRQA
 windowed_pos_source_target = wincrqa(ts1 = data$coh_deciles, 
                                      ts2 = data$pos_deciles_source_target, 
                                      windowstep = 1, 
@@ -70,13 +74,17 @@ windowed_pos_source_target = wincrqa(ts1 = data$coh_deciles,
                                      whiteline = FALSE,
                                      trend = TRUE)
 
[…]

### 2020-05-28 manuscript.Rmd
Add equations

@@
 
-(insert social cohesion equations here)
+\begin{align}
+\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\end{align}
+
+\begin{align}
+\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\end{align}
+
+\begin{align}
+\text{Two tweets similarity =}\frac{\text{inverse frequency weighting of overlap words}}{\text{inverse frequency weighting of all words}}
+\end{align}
 

### 2020-05-28 scripts/primary-analyses/03_windowed_crqa.R
Combine plots into a single multipaneled plot

@@ -34,19 +34,19 @@ shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
 
 # calculate windowed CRQA
 windowed_all_source_target = wincrqa(ts1 = data$coh_deciles, 
-                                       ts2 = data$all_deciles_source_target, 
-                                       windowstep = 1, 
-                                       windowsize = 14,
-                                       radius = .001,  
-                                       delay = 1,       
-                                       embed = 1, 
-                                       rescale = 0, 
-                                       normalize = 0,  
-                                       mindiagline = 2, 
-                                       minvertline = 2, 
-                                       tw = 0,
-                                       whiteline = FALSE,
-                                       trend = TRUE) 
+                                     ts2 = data$all_deciles_source_target, 
+                                     windowstep = 1, 
+                                     windowsize = 14,
+                                     radius = .001,  
+                                     delay = 1,       
+                                     embed = 1, 
+                                     rescale = 0, 
+                                     normalize = 0,  
+                                     mindiagline = 2, 
+                                     minvertline = 2, 
+                                     tw = 0,
+                                     whiteline = FALSE,
+                                     trend = TRUE) 
 
 # transform into a dataframe for easier plotting 
 wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
@@ -114,19 +114,19 @@ colnames(wincrqa_neg_df_source_target) <- c("RR", "DET",
 
 # calculate windowed CRQA
 windowed_all_target = wincrqa(ts1 = data$coh_deciles, 
-                               ts2 = data$all_deciles_target, 
-                               windowstep = 1, 
-                               windowsize = 14,
-                               radius = .001,  
-                               delay = 1,       
-                               embed = 1, 
-                               rescale = 0, 
-                               normalize = 0,  
-                               mindiagline = 2, 
-                               minvertline = 2, 
-                               tw = 0,
-                               whiteline = FALSE,
-                               trend = TRUE) 
[…]

### 2020-05-28 appendix.tex

@@
 
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
 \end{figure}
@@
 
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
 \end{figure}

### 2020-05-28 manuscript.tex

@@
 
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
 \end{figure}
@@
 
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
 \end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\begin{figure}[H]
+\includegraphics[width=0.4\linewidth,]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
 \end{figure}

### 2020-05-28 scripts/libraries_and_functions.r
Be sure we specify new plotting packages

@@ -15,7 +15,8 @@ required_packages = c(
   'pander',
   'gtools',
   'knitr',
-  'statip'
+  'statip',
+  'gridExtra'
 )
 
 # load required packages

### 2020-05-28 scripts/required_packages.r

@@ -15,7 +15,8 @@ required_packages = c(
   'pander',
   'gtools',
   'knitr',
-  'statip'
+  'statip',
+  'gridExtra'
 )
 
 # install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)

### 2020-05-28 manuscript.Rmd
Add tweet scraping description

@@
 knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
-#knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
 
@@
 The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets occurring between March 30, 2012 and June 15, 2012.
-The tweet corpus was scraped from Twitter by [insert search parameters here].
+Using the Twitter streaming API, servers at the University of Texas at Austin collected the tweets.
+The servers were run on a stable (LTS) version of Ubuntu Linus, 10.04, and were connected directly to the high-bandwidth UT network maintained by IT services.
+Tweets collected contained one or more of the following keywords: “syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These keywords were chosen based on the most distinctive terms used in news articles covering the Arab Spring in Syria at the time.
+A node.js script was used to reinitialize the connection to Twitter's servers whenever the script timed out due to a period of silence.
+The script requested data from the API endpoint using basic HTTP authentication (OAuth was optional, at the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored the data directly to the local hard disk.
+The tweets were then post-processed with a Python script to convert the JSON-formatted tweets to tab-separated files and were then compressed to maximize storage efficiency.
+All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.
 

### 2020-05-28 manuscript.tex
Add tweet scraping description

--- 2020-05-28 manuscript.tex
@@
 
-The corpus of tweets used included 697428 Syrian tweets occurring between March 30, 2012 and June 15, 2012. The tweet corpus was scraped from Twitter by {[}insert search parameters here{]}.
+The corpus of tweets used included 697428 Syrian tweets occurring between March 30, 2012 and June 15, 2012.
+Using the Twitter streaming API, servers at the University of Texas at Austin collected the tweets.
+The servers were run on a stable (LTS) version of Ubuntu Linus, 10.04, and were connected directly to the high-bandwidth UT network maintained by IT services.
+Tweets collected contained one or more of the following keywords: \enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These keywords were chosen based on the most distinctive terms used in news articles covering the Arab Spring in Syria at the time.
+A node.js script was used to reinitialize the connection to Twitter's servers whenever the script timed out due to a period of silence.
+The script requested data from the API endpoint using basic HTTP authentication (OAuth was optional, at the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored the data directly to the local hard disk.
+The tweets were then post-processed with a Python script to convert the JSON-formatted tweets to tab-separated files and were then compressed to maximize storage efficiency.
+All scripts used for scrapping tweets and compressing data can be found at \url{https://github.com/chbrown/twilight}.
 

### 2020-05-28 scripts/primary-analyses/03_windowed_crqa.R
Update plotting in primary windowed crqa

@@ -767,153 +767,251 @@ ggsave(filename = "./results/primary/windowed-crqa/source_target-windowed_all.pn
 
 ### target filtered data ###
 
+## count of all events and social cohesion ##
+
 # RR plot #
 
-# plot the windows and RRs 
-png("./results/primary/windowed-crqa/target-windowed_all_RR.png", 
-    width = 4, height = 4, units = 'in', res = 300)
-plot(wincrqa_all_df_target$RR,
-     xlab='Window',ylab='RR',type='b', ylim = c(4, 24),
-     main = "Windowed CRQA for Social\nCohesion and Event Count")
-
-# add trend line
+# identify trend line
 fit <- lm(RR ~ window, data = wincrqa_all_df_target)
-summary(fit)
-abline(fit, col="blue")
+fit_intercept = fit$coefficients[1]
+fit_slope = fit$coefficients[2]
 
-# add upper and lower 95th and 99th percentile lines 
-abline(h = significance_all_target[1,1], col="orange")
-abline(h = significance_all_target[2,1], col="red")
-abline(h = significance_all_target[3,1], col="red")
-abline(h = significance_all_target[4,1], col="orange")
-
-# finish image processing
-dev.off()
+# construct and save the plot
+plot_target_windowed_all_RR = ggplot(data = wincrqa_all_df_target,
+                                            aes(y = RR,
+                                                x = window)) +
+  
+  # add both points and lines for each observation
+  geom_line() +
+  geom_point() +
+  
+  # add upper and lower 95th and 99th percentile lines for significance tests
+  geom_hline(yintercept = significance_all_target[1,1], color = "orange") +
+  geom_hline(yintercept = significance_all_target[2,1], color = "red") +
+  geom_hline(yintercept = significance_all_target[3,1], color = "red") +
+  geom_hline(yintercept = significance_all_target[4,1], color = "orange") +
+  
+  # add abline
+  geom_abline(intercept = fit_intercept,
+              slope = fit_slope,
+              color="blue") +
+  
+  # make uniform boundaries
+  coord_cartesian(ylim = c(plot_rr_ymin, plot_rr_ymax)) +
+  
+  # add labels
+  ggtitle('RR: All event count') +
+  ylab("RR") +
+  xlab("")
 
 # DET plot #
 
 # fill in NA determinism values with 0
 wincrqa_all_df_target$DET[is.na(wincrqa_all_df_target$DET)] <- 0
 
-# plot the windows and RRs 
[…]

### 2020-05-28 scripts/secondary-analyses/icews/03_windowed_crqa.R
Update secondary ICEWS windowed crqa image formats

@@ -1,4 +1,4 @@
-######## Windowed Cross-Recurrence Quantification Analysis ########
+######## Windowed Cross-Recurrence Quantification Analysis (ICEWS) ########
 #
 # This script runs windowed cross-recurrence quantification 
 # analysis the real-world events and Twitter social cohesion 
@@ -50,7 +50,11 @@ windowed_all_source_target = wincrqa(ts1 = data$coh_sextiles,
 
 # tranform into a dataframe for easier plotting 
 wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
-colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
+                                            "ENTR", "rENTR", 
+                                            "LAM", "TT", 
+                                            "window")
 
 ## count of positive events and social cohesion ##
 
@@ -72,7 +76,11 @@ windowed_pos_source_target = wincrqa(ts1 = data$coh_sextiles,
 
 # tranform into a dataframe for easier plotting 
 wincrqa_pos_df_source_target <- as.data.frame(windowed_pos_source_target$crqwin)
-colnames(wincrqa_pos_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+colnames(wincrqa_pos_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
+                                            "ENTR", "rENTR", 
+                                            "LAM", "TT", 
+                                            "window")
 
 ## count of negative events and social cohesion ##
 
@@ -94,7 +102,11 @@ windowed_neg_source_target = wincrqa(ts1 = data$coh_sextiles,
 
 # tranform into a dataframe for easier plotting 
 wincrqa_neg_df_source_target <- as.data.frame(windowed_neg_source_target$crqwin)
-colnames(wincrqa_neg_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+colnames(wincrqa_neg_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
[…]

### 2020-05-28 scripts/secondary-analyses/phoenix/03_windowed_crqa.R
Update secondary Phoenix windowed crqa image formats

@@ -33,138 +33,165 @@ shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
 ## count of all events and social cohesion ##
 
 # calculate windowed rqa
-windowed_count = wincrqa(ts1 = data$coh_sextiles, 
-                         ts2 = data$all_sextiles_source_target, 
-                         windowstep = 1, 
-                         windowsize = 14,
-                         radius = .001,  
-                         delay = 1,       
-                         embed = 1, 
-                         rescale = 0, 
-                         normalize = 0,  
-                         mindiagline = 2, 
-                         minvertline = 2, 
-                         tw = 0,
-                         whiteline = FALSE,
-                         trend = TRUE) 
+windowed_all_source_target = wincrqa(ts1 = data$coh_sextiles, 
+                                     ts2 = data$all_sextiles_source_target, 
+                                     windowstep = 1, 
+                                     windowsize = 14,
+                                     radius = .001,  
+                                     delay = 1,       
+                                     embed = 1, 
+                                     rescale = 0, 
+                                     normalize = 0,  
+                                     mindiagline = 2, 
+                                     minvertline = 2, 
+                                     tw = 0,
+                                     whiteline = FALSE,
+                                     trend = TRUE) 
 
 # tranform into a dataframe for easier plotting 
-wincrqa_all_df_source_target <- as.data.frame(windowed_count$crqwin)
-colnames(wincrqa_all_df_source_target) <- c("RR", "DET", "NRLINE", "maxL", "L", "ENTR", "rENTR", "LAM", "TT", "window")
+wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
+                                            "ENTR", "rENTR", 
+                                            "LAM", "TT", 
+                                            "window")
 
 ## count of positive events and social cohesion ##
 
 # calculate windowed rqa
-windowed_pos = wincrqa(ts1 = data$coh_sextiles, 
-                       ts2 = data$pos_sextiles_source_target, 
-                       windowstep = 1, 
-                       windowsize = 14,
-                       radius = .001,  
-                       delay = 1,        
-                       embed = 1, 
-                       rescale = 0, 
-                       normalize = 0, 
-                       mindiagline = 2,  
-                       minvertline = 2,  
[…]

### 2020-05-28 manuscript.Rmd
Update primary figure paths

@@
 
-```{r plot-RR-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
+```{r plot-wcrqa-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90'}
 
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_RR.png")
-
-```
-
-```{r plot-DET-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_DET.png")
-
-```
-
-```{r plot-RR-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all.png")
 
@@
 
-```{r plot-RR-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
 
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_RR.png")
-
-```
-
-```{r plot-DET-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_DET.png")
-
-```
-
-```{r plot-RR-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_RR.png")
-
-```
-
-```{r plot-DET-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_DET.png")
-
-```
-
-```{r plot-RR-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_RR.png")
-
-```
-
-```{r plot-DET-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_DET.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
 

### 2020-05-28 manuscript.tex
Update primary figure paths

@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg}
+\includegraphics[width=9in,angle=90]{./results/primary/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-wcrqa-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg}
+\includegraphics[width=9in,angle=90]{./results/primary/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from source and target filtered data.}\label{fig:plot-wcrqa-source-targ-all}
 \end{figure}
@@
 
+\begin{verbatim}
+## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
+## 'appendix.Rmd'
+\end{verbatim}
+
 \clearpage
@@
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-Phoenix}
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-targ-all}
 \end{figure}
+
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-Phoenix}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-Phoenix}
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-source-targ-all}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-targ-all}
 \end{figure}
+
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-source-targ-all}
 \end{figure}

### 2020-05-28 appendix.Rmd
Remove unused setup code
Update secondary plot paths

@@
 rm(list=ls())
-
-# install and load required packages
-source('./scripts/required_packages.r')
-source('./scripts/libraries_and_functions.r')
-
-# turn on caching
-knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
 
@@
 ```
-```{r plot-RR-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}
+
+```{r plot-secondary-phoenix-wcrqa-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90', out.width = "90%"}
 
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/target-windowed_all.png")
 
 ```
-```{r plot-DET-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}
+
+```{r plot-secondary-phoenix-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90', out.width = "90%"}
 
 # call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET.png")
-
-```
-```{r plot-RR-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR.png")
-
-```
-```{r plot-DET-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET.png")
-
-```
-```{r plot-RR-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR.png")
-
-```
-```{r plot-DET-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET.png")
-
-```
-```{r plot-RR-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR.png")
-
-```
-```{r plot-DET-source-targ-all-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET.png")
-
-```
-```{r plot-RR-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR.png")
-
-```
-```{r plot-DET-source-targ-pos-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET.png")
-
-```
-```{r plot-RR-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR.png")
-
-```
-```{r plot-DET-source-targ-neg-secondary-Phoenix, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET.png")
+knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all.png")
 
@@
 ```
-```{r plot-RR-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.', out.width = "40%"}
+
+```{r plot-secondary-icews-wcrqa-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90', out.width = "90%"}
 
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_RR.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all.png")
 
 ```
-```{r plot-DET-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.', out.width = "40%"}
+
+```{r plot-secondary-icews-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90', out.width = "90%"}
 
 # call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_all_DET.png")
+knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all.png")
 
 ```
-```{r plot-RR-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_RR.png")
-
-```
-```{r plot-DET-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_pos_DET.png")
-
-```
-```{r plot-RR-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_RR.png")
-
-```
-```{r plot-DET-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/target-windowed_neg_DET.png")
-
-```
-```{r plot-RR-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR.png")
-
-```
-```{r plot-DET-source-targ-all-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET.png")
-
-```
-```{r plot-RR-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR.png")
-
-```
-```{r plot-DET-source-targ-pos-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET.png")
-
-```
-```{r plot-RR-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR.png")
-
-```
-```{r plot-DET-source-targ-neg-secondary-icews, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.', out.width = "40%"}
-
-# call image
-knitr::include_graphics("./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET.png")
-
-```

### 2020-05-28 appendix.tex
Update secondary plot paths

--- 2020-05-28 appendix.tex
@@
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-Phoenix)
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}(\#fig:plot-secondary-phoenix-wcrqa-targ-all)
 \end{figure}
+
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-Phoenix)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/Phoenix/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-Phoenix)
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}(\#fig:plot-secondary-phoenix-wcrqa-source-targ-all)
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}(\#fig:plot-RR-targ-all-secondary-icews)
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}(\#fig:plot-secondary-icews-wcrqa-targ-all)
 \end{figure}
+
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}(\#fig:plot-DET-targ-all-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}(\#fig:plot-RR-targ-pos-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}(\#fig:plot-DET-targ-pos-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}(\#fig:plot-RR-targ-neg-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}(\#fig:plot-DET-targ-neg-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-RR-source-targ-all-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}(\#fig:plot-DET-source-targ-all-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-RR-source-targ-pos-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}(\#fig:plot-DET-source-targ-pos-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-RR-source-targ-neg-secondary-icews)
-\end{figure}
-\begin{figure}
-\includegraphics[width=0.4\linewidth]{./results/secondary/icews/windowed-crqa/source_target-windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}(\#fig:plot-DET-source-targ-neg-secondary-icews)
+\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}(\#fig:plot-secondary-icews-wcrqa-source-targ-all)
 \end{figure}

### 2020-05-29 manuscript.Rmd
Figure and table cross-references

@@
 Nyquist frequency in signal processing; @grenander1959probability].
-We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
 In CRQA, a recurrent point is when two signals share the same state.
@@
 This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures 3-5 for examples of RPs.
+See Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) for examples of RPs.
 
@@
 These dynamics can then be linked to other external events.
-See Figures 9-14 and 16-21 for examples.
+See Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all) for examples.
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure 3; Table 1).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
+All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all); \autoref{table-1}).
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
 A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
-All other metrics were non-significant (Figure 5; Table 1).
+All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
 Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
@@
 # build table
-pander(target_results, caption = "CRQA results for target only data.")
+pander(target_results, caption = "\\label{table-1}CRQA results for target only data.")
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure 6; Table 2).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
+All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
 A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
-All other metrics were non-significant (Figure 8; Table 2).
+All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
 Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
@@
 # build table
-pander(source_target_results, caption = "CRQA results for source and target data.")
+pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.")
 
@@
 Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
 The trend lines are plotted in blue.
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+Determinism is also almost consistently above chance from the 39th window onwards (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves and determinism stays almost entirely within chance across windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window and determinism is also above or nearly above chance from the 38th through 43rd window (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure 16).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
-For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves and determinism stays largely within chance with the exception of windows 13-19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+For social cohesion and negative events, there appears to be an extended time period where RR  and DET were greater than chance, from the 35th through 46th windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
 These windows span from May 3rd, 2012 to May 14th, 2012.
@@
 Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
+By visual inspection of the recurrence plots (RPs; Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
 To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
@@
 ### Syria as Target
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
+The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)).
 The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
 The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
 These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET was entirely within chance (Figure \@ref(fig:plot-wcrqa-targ-all)).
 This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.

### 2020-05-29 manuscript.tex
Figure and table cross-references

@@
 In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
-We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+We converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles (e.g., Figure \ref{fig:deciled-ts}) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
 In CRQA, a recurrent point is when two signals share the same state.
@@
 This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures 3-5 for examples of RPs.
+See Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg} for examples of RPs.
 
@@
 These dynamics can then be linked to other external events.
-See Figures 9-14 and 16-21 for examples.
+See Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all} for examples.
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure 3; Table 1).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
+All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-all}; \autoref{table-1}).
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
 A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
-All other metrics were non-significant (Figure 5; Table 1).
+All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
 Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only data.}\tabularnewline
+\caption{\label{table-1}CRQA results for target only data.}\tabularnewline
 \toprule
@@
 A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure 6; Table 2).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
+All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-all}; \autoref{table-2}).
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
 A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
-All other metrics were non-significant (Figure 8; Table 2).
+All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-neg}; \autoref{table-2}).
 Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target data.}\tabularnewline
+\caption{\label{table-2}CRQA results for source and target data.}\tabularnewline
 \toprule
@@
 Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+In the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all}), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
 The trend lines are plotted in blue.
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+Determinism is also almost consistently above chance from the 39th window onwards (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves and determinism stays almost entirely within chance across windows (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window and determinism is also above or nearly above chance from the 38th through 43rd window (Figure \ref{fig:plot-wcrqa-targ-all}).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure 16).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
-For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves and determinism stays largely within chance with the exception of windows 13-19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+For social cohesion and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 35th through 46th windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
 These windows span from May 3rd, 2012 to May 14th, 2012.
@@
 Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
+By visual inspection of the recurrence plots (RPs; Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
 To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
@@
 
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
+The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR and DET (Figure \ref{fig:plot-wcrqa-targ-all}).
 The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
 The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \ref{fig:plot-mode-event}), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
 These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET was entirely within chance (Figure \ref{fig:plot-wcrqa-targ-all}).
 This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.

### 2020-05-29 manuscript.Rmd
Updates to keywords and abstract

@@
   Social mobilization requires effective collective coordination.
-In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
-Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
+In recent years, individuals involved in social movements have taken to social media platforms to reach broader audiences at rapid speeds.
+Effective virtual mobilization similarly requires social cohesion and coordination, yet the degree to which virtual mobilization reflects or drives real-world movements is unclear.
 Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
 Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
-Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
-This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
+Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day but not with counts of positive events.
+This suggests that virtual mobilization does reflect real-world movements but only for salient, frequent, and negative events.
 We conclude with a discussion of implications and applications of nonlinear methods in political science research.
@@
 
-keywords          : "Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring"
+keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
 wordcount         : "X"

### 2020-05-29 manuscript.Rmd
Update results section

--- 2020-05-29 manuscript.Rmd
@@
 All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, L, ENTR, LAM, and TT.
 All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
@@
 All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR.
 All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves and determinism stays almost entirely within chance across windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window and determinism is also above or nearly above chance from the 38th through 43rd window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 7th-12th and 36th-47th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+Determinism is largely above chance from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves with largly above chance RR from the 1st-18th and 32nd-45th windows.
+Determinism was at or above chance for the 8th-17th, 32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of negative events, recurrence rate stays above or almost above chance from the 4th-7th and 43rd-47th windows, and determinism is above or nearly above chance in the 1st and 2nd windows, with short intermittent peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves and determinism stays largely within chance with the exception of windows 13-19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and negative events, there appears to be an extended time period where RR  and DET were greater than chance, from the 35th through 46th windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 7th-13th and 26th-47th windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+Determinism also shows above or nearly above chance values in windows 7th-17th and short, intermittent peaks between the 34th and 61st windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves with largely above chance values in the first 20 windows and the 32nd-45th windows.
+Determinism stays largely within chance with the exception of windows 13 through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+For social cohesion and negative events, there appears to be an extended time period where RR (32nd-47th windows) and DET (35th-39th windows) were above of nearly above chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
 These windows span from May 3rd, 2012 to May 14th, 2012.

### 2020-05-29 manuscript.Rmd
Impose hard wrapping to improve versioning informativeness

--- 2020-05-29 manuscript.Rmd
@@
 Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day but not with counts of positive events.
-This suggests that virtual mobilization does reflect real-world movements but only for salient, frequent, and negative events.
+This suggests that virtual mobilization does reflect real-world movements but only for salient, frequent and negative events.
 We conclude with a discussion of implications and applications of nonlinear methods in political science research.
@@
 
-Social coordination has long been used both physically and virtually to start and carry out collective actions.
-These collective events bring individuals together and create emergent patterns of communication and action.
-Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
-From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another [@mahner1997foundations].
-Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
-The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
+Social coordination has long been used both physically and virtually 
+to start and carry out collective actions. These collective events 
+bring individuals together and create emergent patterns of communication 
+and action. Online communication has historically been used to document 
+and communicate archival information about events, but it has been 
+increasingly used to bring about social change. From a dynamical 
+systems perspective, these different means of social coordination during 
+times of turmoil can be considered two complementary components of a 
+single system, mutually constrained and constantly interacting and 
+influencing one another [@mahner1997foundations]. Investigation of the 
+coupling of real-world mobilization and social cohesion could provide 
+new insight into the power of social media during mobilization and the 
+ways in which individuals utilize it to bring about, or respond to, social 
+change. Increasingly, social media platforms are being utilized during 
+social mobilization, but the relationship between virtual and real-world 
+mobilization is still largely unknown. The present work aims to understand 
+how physical and virtual movements coexist and interact from a dynamical 
+systems perspective.
 
 ## Arab Spring
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
-His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
-His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
-The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
-These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and 
+unjustifiably stripped of his vendor cart by municipal officials. His 
+humiliation led him to set himself on fire in protest to the authoritarian 
+rule, ultimately leading to his death several days later. His actions served 
+as a catalyst for the Tunisian Revolution, and one week after his death, the 
+long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the 
+country. The events of Tunisia rapidly spread to surrounding countries that 
+were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, 
+and Syria. These mass movements would not have been possible without 
+efficient interpersonal coordination, both physically and virtually on social
+media platforms, such as Twitter. The events of Arab Spring have been
+thoroughly discussed within the political science literature 
+[e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge, 
+the use of Twitter by Syrian citizens has not been investigated.
 
 ## Social Cohesion
-Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary].
-This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
-While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-@gilligan2014civil found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
-Just as real-world social cohesion can be quantified, the same is true for online cohesion.
-Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
-Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
+Real-world collective action is known to bring about a sense of togetherness, 
+also known as “collective effervescence” [@durkheim1995elementary]. This 
+feeling of being a part of something larger than oneself leads individuals 
+to act in ways that would not have on their own. Being overcome with this 
+feeling is known to lead to violence [@collins2009violence; @spaaij2014sports]. 
+While feelings of social connection may lead to violence, increased exposure 
+to violence can result in feelings of social cohesion. @gilligan2014civil 
+found that exposure to fatal wartime violence resulted in increased prosocial 
+motivations, including cooperative behaviors, feelings of trust, and overall 
+community-level social cohesion. Just as real-world social cohesion can be 
+quantified, the same is true for online cohesion. Strategic communication on 
+social media in the form of social cohesion of language can lead to real-world 
+social change, and exposure to real-world violence could result in social 
+cohesion in the virtual world. Increased social cohesion is thus potentially 
+an indicator of increased social organization and mobilization on the ground.
 
 ## Social Media as a Platform for Mobilization
-Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
-Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests [@vicari2013public].
-Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
-As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
+Social media platforms, such as Twitter, offer rapid real-time dissemination
+of information. Given its accessibility and proficiency as an information 
+exchange tool, individuals involved in social movements have taken to them 
+in conjunction, or in replacement, of real-world social mobilization. 
+During the 2012 Italian protests for global economic change, the riots in 
+Rome were mirrored by Twitter activity both on the same day and in the 
+following days after the protests [@vicari2013public]. Tweeting was 
+determined to be more effective locally in discussing real-world, real-time 
+events than traditional mainstream media platforms. As more and more 
+individuals rely on social media to obtain local news and information, it 
+becomes increasingly important to understand just how these micro-blogs 
+reflect real-world action.
 
 ## Use of Nonlinear Methods in Naturally Occurring Data
-Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
-Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
-This notion has been increasingly replaced by ideas from dynamical systems theory.
-Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts [@turvey2018lectures].
-When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
-Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
-Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
-The primary methods used in the current work is cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and it’s off-shoot, windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
-CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions [for a review, see @fusaroli2014analyzing] and interpersonal synchrony [@paxton2017interpersonal].
-We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
+Traditional linear analyses have led to many notable discoveries in the 
+domains of psychology and political science, but continuous data pose 
+problems that are not easily overcome with these methods. Events have
+historically been conceptualized as linear chains of smaller, sequential 
+events with one occurrence leading to the next. This notion has been 
+increasingly replaced by ideas from dynamical systems theory. Rather than 
+a chain of events, continuous data can be thought of as nested occurrences, 
+where mutually constrained parts (e.g., citizens, governments, real-world 
+events, social media platforms) are constantly interacting, leading to 
+more global behaviors that are larger than the sum of the parts 
+[@turvey2018lectures]. When analyzed as dynamical systems, many phenomena 
+exhibit new nonlinear patterns that were formerly overlooked. Continuous 
+data subject to linear analyses becomes flattened, and the variability 
+that is fundamental to these systems and their evolution over time is 
+ignored. Nonlinear methods provide means for capturing the rich temporal 
+dynamics and variability that unfold in continuous data.
+
+The primary methods used in the current work is cross-recurrence 
+quantification analysis [CRQA; @zbilut1998detecting] and its offshoot, 
+windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence]. 
+CRQA has successfully been used to gain a better understanding of many 
+complex human phenomena, such as human social interactions 
+[for a review, see @fusaroli2014analyzing] and interpersonal synchrony 
+[@paxton2017interpersonal]. We argue that the use of nonlinear methods in 
+the investigation of political science phenomena will lead to new insights 
+and development of more robust theories.
 
 ## The Present Work
-Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
-We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
-Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
-This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
-Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence], we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
-We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
-We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
-Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
-As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
+Social media has become a primary platform for social movements and 
+activism across the world, but the extent to which virtual activism 
+reflects real-world mobilization is still largely unknown. We 
+conceptualize the physical and virtual movements as a dynamical system, 
+both constantly interacting and influencing the other. Both real- and 
+virtual-world collective coordination were powerful tools in the events 
+of Arab Spring, and are undeniably linked. This study aims to explore 
+the dynamics of Syrian individuals who took to Twitter to raise 
+awareness about the events of Arab Spring and bring about mass mobilization. 
+Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] 
+and windowed cross-recurrence quantification analysis 
+[WCRQA; @webber2005recurrence], we analyzed the dynamics of social 
+cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts 
+of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative 
+events would show high levels of determinism, as this time period was 
+marked by daily violence which often leads to increased salience. We also 
+hypothesized that the count of positive events would not show patterns of 
+determinism, as these events were likely overshadowed by the salient 
+negative daily occurrences. Using WCRQA, we hoped to identify shifts in the 
+dynamics of the systems that could then be linked to real world shifts in 
+conflict frequency. As social cohesion has never been analyzed using 
+nonlinear methods, the analyses contained herein are largely exploratory. 
+The goal of this endeavor is to gain a better understanding of how events 
+of different intensities during times of turmoil may enhance or deter 
+social cohesion in social media communication, and how social mobilization 
+may be evident in the dynamic coupling of cohesion and real-world events.
 
@@
 
-The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets occurring between March 30, 2012 and June 15, 2012.
-Using the Twitter streaming API, servers at the University of Texas at Austin collected the tweets.
-The servers were run on a stable (LTS) version of Ubuntu Linus, 10.04, and were connected directly to the high-bandwidth UT network maintained by IT services.
-Tweets collected contained one or more of the following keywords: “syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These keywords were chosen based on the most distinctive terms used in news articles covering the Arab Spring in Syria at the time.
-A node.js script was used to reinitialize the connection to Twitter's servers whenever the script timed out due to a period of silence.
-The script requested data from the API endpoint using basic HTTP authentication (OAuth was optional, at the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored the data directly to the local hard disk.
-The tweets were then post-processed with a Python script to convert the JSON-formatted tweets to tab-separated files and were then compressed to maximize storage efficiency.
+The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets 
+occurring between March 30, 2012 and June 15, 2012. Using the Twitter 
+streaming API, servers at the University of Texas at Austin collected 
+the tweets. The servers were run on a stable (LTS) version of Ubuntu 
+Linus, 10.04, and were connected directly to the high-bandwidth UT network 
+maintained by IT services.
+
+Tweets collected contained one or more of the following keywords:
+“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These 
+keywords were chosen based on the most distinctive terms used in news 
+articles covering the Arab Spring in Syria at the time. A node.js script 
+was used to reinitialize the connection to Twitter's servers whenever the 
+script timed out due to a period of silence. The script requested data from 
+the API endpoint using basic HTTP authentication (OAuth was optional, at 
+the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored 
+the data directly to the local hard disk. The tweets were then post-processed
+with a Python script to convert the JSON-formatted tweets to tab-separated 
+files and were then compressed to maximize storage efficiency.
+
 All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.
@@
 ### Event Data
-Event data were obtained from the 2012 Integrated Crisis Early Warning System [ICEWS; @DVN/28075_2015].
-The event data were first filtered to remove incomplete and incorrectly formatted data.
-They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
-To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
+Event data were obtained from the 2012 Integrated Crisis Early Warning 
+System [ICEWS; @DVN/28075_2015]. The event data were first filtered to 
+remove incomplete and incorrectly formatted data. They were then filtered 
+to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were 
+filtered again to include events that were both directed at (i.e., target) 
+or directed by (i.e., source) Syria (n = 7990).
 
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
-If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
-The tweets were first sorted into ascending order by timestamp.
-They were then grouped into successive sets of five tweets.
-Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
-1-3).
-This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
-Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
+The social cohesion or linguistic similarity of daily tweets was calculated
+by quantifying the frequency of shared content words with respect to those 
+words’ frequencies in the entire tweet corpus. If a linguistic term has a 
+high frequency in one tweet but has a low frequency in the whole tweet 
+corpus, then it is more likely a content word and is this given more weight
+in calculating social cohesion.
+
+The tweets were first sorted into ascending order by timestamp. They were 
+then grouped into successive sets of five tweets. Inverse frequency 
+weighting for the overlap words and all words was conducted for each pair 
+of two tweets in the group of five, then divided to get the social cohesion 
+score for that pair (see Eq. 1-3). This resulted in ten social cohesion 
+values for each group of five tweets, which were then averaged. Finally, 
+the mean of all average cohesion values for all groups was taken to get 
+a social cohesion score for each day.
 
@@
 
-The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
-All hashtags and URLs were included in the analysis.
-This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see @jones1972statistical and @robertson2004understanding.
+The social cohesion calculation was performed on a subset of the corpus 
+containing (recalculate with new date span) English and (recalculate with 
+new date span) Arabic tweets. All hashtags and URLs were included in the 
+analysis. This method is similar to that of inverse document frequency (IDF). 
+For more information on IDF, see @jones1972statistical and
+@robertson2004understanding.
 
 ### ICEWS Event Time Series
-Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
-Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
-This well-validated coding scheme allows for numerical quantification of different event types.
-For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
-Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
-Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the 
+Defense Advanced Research Project Agency, the daily events in Syria were 
+scored with an intensity rating ranging from -10 to 10. Negative events, 
+such as riots and attacks, are coded with low negative numbers while 
+positive, peaceful events are coded with high positive numbers. This 
+well-validated coding scheme allows for numerical quantification of 
+different event types.
+
+For both the target only and the target and source data, time series of 
+the count of all events were generated by summing the total number of events 
+on each day, irrespective of ICEWS score. Similarly, time series of count 
+of positive events were generated by summing the number of ICEWS events 
+for each day that had an intensity rating greater than zero. Lastly, 
+time series of count of negative events were generated by summing the number 
+of ICEWS events for each day that had an intensity rating less than zero.
 
@@
 ### Cross-Recurrence Quantification Analysis
-We first used cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
-As an extension of RQA, which captures the patterns of revisited states of a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
-Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system [cf.
-Nyquist frequency in signal processing; @grenander1959probability].
-We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
-In CRQA, a recurrent point is when two signals share the same state.
-These shared states can be at the same time or at later points in the time series.
+We first used cross-recurrence quantification analysis 
+[CRQA; @zbilut1998detecting] to investigate the temporal patterns of 
+social cohesion and real-world events in Syria during Arab Spring. As 
+an extension of RQA, which captures the patterns of revisited states of 
+a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA 
+allows for two time series to be projected onto one another to investigate 
+shared states and trajectories. Nonlinear analyses such as CRQA can reveal
+dynamics that are not captured by traditional linear methods.
+
+In order to perform CRQA, the time series need to be converted to the same 
+scale, while still preserving a sampling rate that respects the native 
+timescale of the system 
+[cf. Nyquist frequency in signal processing; @grenander1959probability]. 
+We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
+(e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different 
+levels of social cohesion and counts of all, positive, and negative events 
+on each day. In CRQA, a recurrent point is when two signals share the same 
+state. These shared states can be at the same time or at later points in 
+the time series.
 
 #### Visualization
-A recurrence plot (RP) is the visual representation of CRQA.
-To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
-Visually analyzing these plots can help reveal patterns of structure and recurrence.
-The line y = x is known as the line of identity.
-This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) for examples of RPs.
+A recurrence plot (RP) is the visual representation of CRQA. To construct 
+a recurrence plot, two time series are plotted against each other on the 
+X and Y axes, and at every point where they share the same state, and point 
+in placed on the plot to indicate recurrence. Visually analyzing these plots 
+can help reveal patterns of structure and recurrence. The line y = x is known 
+as the line of identity. This line falls where the time series match 
+temporally, and a filled line would indicate perfect synchrony between the 
+two time series. See 
+Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) 
+for examples of RPs.
 
 #### Metrics
-The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
-This metrics gives a general description of how frequently the time series are sharing the same states.
-In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
+The percentage of recurrent points to total possible points is a metric 
+called recurrence rate (RR). This metrics gives a general description of 
+how frequently the time series are sharing the same states. In the current 
+study, a recurrent point would indicate that the level of social cohesion 
+and frequency of events were at the same intensity.
+
 Recurrent points that occur in successive moments form line structures. 
-These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
-The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
-For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
-The average length of the line structures is called mean line (L).
-This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
-The longest line length is called max line (maxL).
-maxL indicates the longest instance of being “stuck” in a particular state together.
-The total number of lines is called NRLINE.
-The more lines there are, the more coordinated the system may be.
-The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
-These entropy metrics help indicate the stability and predictability of the system.
-When one of the signals gets “stuck” in a state and the other moves on to other states, this results in vertical line structures.
-The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see @R-crqa.
+These are conceptualized as shared trajectories, where the two time series 
+are moving together across time in a shared state. The percentage of 
+recurrent points that make up diagonal line structures (i.e., two or more 
+consecutive points) is a metric called percent determinism (DET). For the 
+current project, a high DET would indicate that not only are the levels of 
+social cohesion and frequency of events occurring at similar intensities, 
+but they are doing so across consecutive days.
+
+The average length of the line structures is called mean line (L). This can 
+be conceptualized as the average amount of time that the two time series move
+together before one or both shift states. The longest line length is called 
+max line (maxL). maxL indicates the longest instance of being “stuck” in a
+particular state together. The total number of lines is called NRLINE. The 
+more lines there are, the more coordinated the system may be. The 
+complexity or variability of line lengths is captured by a metric called 
+entropy (ENTR) and entropy while accounting for the total number of lines in 
+the plot is normalized entropy (rENTR). These entropy metrics help indicate 
+the stability and predictability of the system. When one of the signals gets
+“stuck” in a state and the other moves on to other states, this results in
+vertical line structures. The proportion of points forming vertical line 
+structures is a metric called laminarity (LAM) and the average length of the
+vertical trajectories is called trapping time (TT). For more detail on CRQA 
+metrics, see @R-crqa.
 
 #### Parameters
-To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
-Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
-No normalization was done, and lines were considered two or more consecutive recurrent points.
-The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see @R-crqa.
+To conduct the analyses on the decile data, the parameters were set to those 
+typically used in categorical CRQA. Delay was set to zero, embedding dimension 
+was set to 1, and radius was set to .001 to allow for only exact recurrent 
+matches. No normalization was done, and lines were considered two or more 
+consecutive recurrent points. The Theiler window was set to zero to include 
+points along the line of identity. For more details on the CRQA parameters and 
+how they impact the analysis, see @R-crqa.
 
 #### Permutation Test
-Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R [@R-base], 1000 permuted time series were created for each of the real time series.
-A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
-CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
-This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
-Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
-Thus, RR is not included in the inferential tests.
-For more information on permutation tests, see @good2013permutation.
+Using the deciled, real time series of social cohesion, count of all events, 
+count of positive events, and count of negative events, a permutation test was 
+done to determine statistical difference from chance for each CRQA metric. 
+Using the sample function in base R [@R-base], 1000 permuted time series were 
+created for each of the real time series. A permutation test is similar to
+bootstrapping, except that the sampling of observations is done without 
+replacement. CRQA was then run 1000 times for social cohesion and count of all 
+events, social cohesion and count of positive events, and social cohesion and 
+count of negative events using the permuted time series. This resulted in 
+1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles 
+of the metrics from the permuted CRQ analyses. Given that a permutation test 
+is similar to bootstrapping but does not include replacement, all points were
+included in each CRQA analysis, leaving RR the same across all analyses. Thus, 
+RR is not included in the inferential tests. For more information on permutation 
+tests, see @good2013permutation.
 
 ### Windowed Cross-Recurrence Quantification Analysis
-We used windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence] to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
-In this analysis, a smaller “window” of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
-The window remains the same size and “slides” diagonally up the line of identity.
-The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+We used windowed cross-recurrence quantification analysis
+[WCRQA; @webber2005recurrence] to further investigate the evolution of the
+temporal dynamics of social cohesion and real-world events. In this analysis, 
+a smaller “window” of time points is used to calculate CRQA and capture more 
+fine-grain dynamics of two time series. The window remains the same size and 
+“slides” diagonally up the line of identity. The changes in the CRQA metrics 
+across the windows can reveal changes in dynamics that can then be linked to 
+external, real-world events.
 
 #### Metrics
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
-These metrics can then be plotted as a time series to visualize their evolution over time.
-For these analyses, we decided to visualize recurrence rate and determinism.
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each 
+respective window. These metrics can then be plotted as a time series to 
+visualize their evolution over time. For these analyses, we decided to 
+visualize recurrence rate and determinism.
 
 #### Parameters
-In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
-First, a window size must be decided on.
-The window size will determine how many observations are used in each CRQA analysis.
-We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
-The second parameter to be chosen is a step size.
-Window step size is how far the window moves up the line of identity before conducting CRQA again.
-We chose 1 for the step size to understand how the metrics evolve from day to day.
-All other CRQA metrics remained the same as previously noted.
+In addition to the CRQA parameters, two other parameters are required when 
+conducting WCRQA. First, a window size must be decided on. The window size 
+will determine how many observations are used in each CRQA analysis. We 
+conducted WCRQA with a window size of 14 to investigate the dynamics over 
+two weeks and allow for the capture of more structure and thus a more 
+meaningful interpretation of DET. The second parameter to be chosen is a 
+step size. Window step size is how far the window moves up the line of identity 
+before conducting CRQA again. We chose 1 for the step size to understand 
+how the metrics evolve from day to day. All other CRQA metrics remained the 
+same as previously noted.
 
 #### Visualization
-To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
-This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
-These dynamics can then be linked to other external events.
-See Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all) for examples.
+To visualize WCRQA, the resulting metrics from each window can be plotted 
+as a time series. This allows for visual interpretation of the pattern or 
+fluctuation of the metrics across time. These dynamics can then be linked 
+to other external events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
+\@ref(fig:plot-wcrqa-source-targ-all) for examples.
 
 #### Permutation Test
-To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
-Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
-The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
+To visualize the differences in the WCRQA metrics from those obtained by 
+chance, a permutation test was done to set upper and lower bounds for the 
+95th and 99th percentiles. Using a sample size of 14, one-thousand permuted 
+time series were generated without replacement for each real time series. The 
+upper and lower 95th and 99th percentiles were set based on the distribution 
+of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 ## Cross-Recurrence Quantification Analysis
-CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a 
+permutation test to check for statistical difference from chance for all analyses and 
+metrics.
 
 ### Syria as Target
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all events found a 
+statistical difference from chance for DET, NRLINE, maxL, and LAM. All other metrics 
+were non-significant (Figure \@ref(fig:plot-rp-targ-all); \autoref{table-1}). A permutation 
+test for the CRQA of social cohesion and count of positive events found no statistical 
+difference from chance for any of the metrics (Figure \@ref(fig:plot-rp-targ-pos); 
+\autoref{table-1}). A permutation test for the CRQA of social cohesion and count of 
+negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, 
+and TT. All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-neg); 
+\autoref{table-1}). Looking at the recurrence plots there appears, to be a shift in dynamics 
+around the 36th observation which corresponds to May 4th, 2012.
 
@@
 ### Syria as Source and Target
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all events found a 
+statistical difference from chance for DET, NRLINE, and LAM. All other metrics were 
+non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}). A permutation 
+test for the CRQA of social cohesion and count of positive events found a statistical 
+difference from chance for DET, NRLINE, maxL, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos);
+\autoref{table-2}). A permutation test for the CRQA of social cohesion and count of negative
+events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR. All other 
+metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}). 
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th 
+observation which corresponds to May 4th, 2012.
 
@@
 
-WCRQA was performed using the crqa package [@R-crqa] for R [@R-base].
-Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-The trend lines are plotted in blue.
+WCRQA was performed using the crqa package [@R-crqa] for R [@R-base]. Permutation tests 
+were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In 
+the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)),
+the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
+represented by horizontal orange lines. The trend lines are plotted in blue.
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves and determinism stays almost entirely within chance across windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window and determinism is also above or nearly above chance from the 38th through 43rd window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of all events, there is a consistent period of 
+above chance recurrence rate from the 31st through 48th window 
+(Figure \@ref(fig:plot-wcrqa-targ-all)). Determinism is also almost consistently 
+above chance from the 39th window onwards (Figure \@ref(fig:plot-wcrqa-targ-all)). 
+For social cohesion and count of positive events there is a downward trend in RR 
+as the window moves and determinism stays almost entirely within chance across 
+windows (Figure \@ref(fig:plot-wcrqa-targ-all)). For social cohesion and count of 
+negative events, recurrence rate stay above or almost above chance from the 36th 
+through the 48th window and determinism is also above or nearly above chance from 
+the 38th through 43rd window (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves and determinism stays largely within chance with the exception of windows 13-19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and negative events, there appears to be an extended time period where RR  and DET were greater than chance, from the 35th through 46th windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-These windows span from May 3rd, 2012 to May 14th, 2012.
+For social cohesion and count of all events, there is a consistent period 
+of above or nearly above chance determinism from the 26th through 46th window 
+(Figure \@ref(fig:plot-wcrqa-source-targ-all)). Determinism also shows above 
+or nearly above chance values in window spans 11-16 and 35-37 
+(Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and count 
+of positive events, there is a downward trend in RR as the window moves and 
+determinism stays largely within chance with the exception of windows 13-19 
+(Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and 
+negative events, there appears to be an extended time period where RR and 
+DET were greater than chance, from the 35th through 46th windows 
+(Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from 
+May 3rd, 2012 to May 14th, 2012.
 
 # Discussion
-In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
-We examined how social mobilization both virtually and physically evolve over time in tandem.
-Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
+In the present study, we investigated the dynamics of real-world events 
+and online communication on Twitter in Syria during Arab Spring. We examined 
+how social mobilization both virtually and physically evolve over time in 
+tandem. Prior to now, the extent to which virtual mobilization on social 
+media platforms such as Twitter has been largely unexplored. Using the 
+nonlinear methods cross-recurrence quantification analysis and windowed 
+cross-recurrence quantification analysis, we investigated the theory that 
+virtual mobilization is increasingly reflective of real-world events 
+during times of strife.
 
@@
 ### Syria as Target
-The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
-The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
-The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
-The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
+The significant result of DET for social cohesion and both the all events 
+and negative events time series confirms our hypothesis, that increased 
+salience of events is reflected in social cohesion on Twitter. The frequency 
+of all events and of negative events thus result in a significant number 
+of shared trajectories that are statistically different from chance. The 
+non-significant results for all metrics for positive event count also 
+confirm our hypothesis, and gives support to the theory that positive events 
+are less coupled to social cohesion than the more salient, negative events 
+during times of turmoil. The inevitable increased salience of event 
+frequency and event violence thus leads to increased coupling with Twitter 
+social cohesion.
 
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
-These additional observations are times where Syria initiated an event with another country.
-Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
-The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
-Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
-Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
-The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs; Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
-To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
+By adding Syria as a source in the data filtering, the dataset increased 
+in size by 1,690 samples. These additional observations are times where 
+Syria initiated an event with another country. Events initiated by Syria
+but directed internally within the country were already captured by the 
+target only filtering. The increase in coupling between positive events 
+and social cohesion is thus due to the inclusion of these externally 
+directed events. Though CRQA metrics for count of all and count of 
+negative events with social cohesion were largely unaffected, count of 
+positive events and social cohesion showed significant levels of 
+determinism, number of lines, max line length, and laminarity that were 
+not present in the target filtered data. Given that the Syria during 
+this time was still under Authoritarian rule, the government may have
+been initiating more positive external events to prevent intervention
+by other countries or try to cover up what was happening internally. 
+We believe that the increased coupling of positive events is thus not
+reflective of actual social cohesion, but happened by chance. The 
+inflation of the number of positive events when including source 
+observations is causing increased coupling, but it is more likely that 
+the Twitter users were using the platform to raise awareness of the 
+violent, internal events that were being inflicted on them by their 
+government officials and armies and not reporting on the positive 
+external events that did not directly affect them or their safety. 
+Further research should explore the semantic content of this tweet 
+corpus to determine what the socially cohered language was focused on.
+By visual inspection of the recurrence plots (RPs; 
+Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)), 
+there appears to be a shift in the dynamics of these systems around 
+observation 35, or May 3rd, 2012. To further investigate these local 
+dynamics, we performed a sliding window technique known as windowed 
+cross-recurrence quantification analysis (WCRQA).
 
@@
 ### Syria as Target
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)).
-The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
-These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET was entirely within chance (Figure \@ref(fig:plot-wcrqa-targ-all)).
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
+The time period of differing dynamics, from observation 38 through 43, 
+appears to be captured by WCRQA of social cohesion and count of negative 
+events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)). The 
+amount of recurrence and determinism for these periods almost consistently 
+lie above chance, suggesting that the intensity of negative events coincide
+with the degree of social cohesion found on Twitter, and that these states 
+carry across multiple days in a way that is different from that of chance.
+
+The above-chance levels of determinism and recurrence rate are demonstrating
+the coupling of social cohesion and counts of all and negative events during
+times of strife. We can see this string of highly violent events reflected 
+in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)), 
+where from May 1st, 2020 to May 15th, 2020, the most frequently occurring 
+event was almost consistently -10, the most violent event in the coding 
+system. These dates directly correlate with the above chance RR and DET 
+metrics for the WCRQA of social cohesion and count of negative events. 
+Furthermore, for WCRQA of social cohesion and positive event count during 
+this time period, DET was entirely within chance (Figure 
+\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the 
+positive events are seemingly not coupled with the social cohesion on Twitter 
+during civil uprisings during the Arab Spring.
 
 ### Syria as Source and Target
-WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
-Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
-WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
-This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
-Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
+WCRQA of recurrence rate on the source and target filtered data remained
+largely the same for count of all events and social cohesion, suggesting
+that large numbers on a given day will be reflective of increased levels
+of social cohesion. Determinism showed more frequent above-chance metrics
+for windows 39 and up, suggesting that the inclusion of externally 
+directed events lead to higher event counts during these days and then 
+was more reflective of the level of social cohesion on Twitter. WCRQA for 
+count of positive events and social cohesion remained largely the same for
+RR and DET as the source only data. This again seems to support the idea 
+that these two aren't actually coupled, but rather that the inflation of 
+the positive counts lead to a spurious relationship. Count of negative 
+events and social cohesion also showed similar trends for RR and DET, 
+again attesting to the theory that negative events were coupled to social 
+cohesion on Twitter while positive events happened by chance.
 
 ## Conclusion
-Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
-If consistent across other civil wars, these results have serious implications for monitoring global movements.
-While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
-By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
-Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
+Considering the invasiveness of social media in our everyday lives, it is 
+inevitable that individuals involved in real-world social mobilization have
+utilized these platforms to their advantage. If consistent across other civil
+wars, these results have serious implications for monitoring global 
+movements. While traditional media in regions of authoritarian rule are 
+often biased, the self-organized nature of Twitter poses a new avenue to gain 
+insight into truths about up-risings and social mobilization. By 
+conceptualizing Twitter and real-world events as two components of an 
+inextricably linked dynamical system, the levels of social cohesion within the 
+virtual platform could be monitored for fluctuations indicating global shifts 
+in power and peace. Social media mobilization can thus help alert us to 
+real-world mobilization not communicated in mainstream media and allow for faster intervention.
 

### 2020-05-29 manuscript.Rmd

--- 2020-05-29 manuscript.Rmd
@@
 
-Social coordination has long been used both physically and virtually to start and carry out collective actions.
-These collective events bring individuals together and create emergent patterns of communication and action.
-Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
-From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another [@mahner1997foundations].
-Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
-The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
+Social coordination has long been used both physically and virtually
+to start and carry out collective actions. These collective events
+bring individuals together and create emergent patterns of communication
+and action. Online communication has historically been used to document
+and communicate archival information about events, but it has been
+increasingly used to bring about social change. From a dynamical
+systems perspective, these different means of social coordination during
+times of turmoil can be considered two complementary components of a
+single system, mutually constrained and constantly interacting and
+influencing one another [@mahner1997foundations]. Investigation of the
+coupling of real-world mobilization and social cohesion could provide
+new insight into the power of social media during mobilization and the
+ways in which individuals utilize it to bring about, or respond to, social
+change. Increasingly, social media platforms are being utilized during
+social mobilization, but the relationship between virtual and real-world
+mobilization is still largely unknown. The present work aims to understand
+how physical and virtual movements coexist and interact from a dynamical
+systems perspective.
 
 ## Arab Spring
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
-His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
-His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
-The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
-These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
+unjustifiably stripped of his vendor cart by municipal officials. His
+humiliation led him to set himself on fire in protest to the authoritarian
+rule, ultimately leading to his death several days later. His actions served
+as a catalyst for the Tunisian Revolution, and one week after his death, the
+long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
+country. The events of Tunisia rapidly spread to surrounding countries that
+were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
+and Syria. These mass movements would not have been possible without
+efficient interpersonal coordination, both physically and virtually on social
+media platforms, such as Twitter. The events of Arab Spring have been
+thoroughly discussed within the political science literature
+[e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge,
+the use of Twitter by Syrian citizens has not been investigated.
 
 ## Social Cohesion
-Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary].
-This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
-While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-@gilligan2014civil found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
-Just as real-world social cohesion can be quantified, the same is true for online cohesion.
-Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
-Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
+Real-world collective action is known to bring about a sense of togetherness,
+also known as “collective effervescence” [@durkheim1995elementary]. This
+feeling of being a part of something larger than oneself leads individuals
+to act in ways that would not have on their own. Being overcome with this
+feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
+While feelings of social connection may lead to violence, increased exposure
+to violence can result in feelings of social cohesion. @gilligan2014civil
+found that exposure to fatal wartime violence resulted in increased prosocial
+motivations, including cooperative behaviors, feelings of trust, and overall
+community-level social cohesion. Just as real-world social cohesion can be
+quantified, the same is true for online cohesion. Strategic communication on
+social media in the form of social cohesion of language can lead to real-world
+social change, and exposure to real-world violence could result in social
+cohesion in the virtual world. Increased social cohesion is thus potentially
+an indicator of increased social organization and mobilization on the ground.
 
 ## Social Media as a Platform for Mobilization
-Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
-Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests [@vicari2013public].
-Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
-As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
+Social media platforms, such as Twitter, offer rapid real-time dissemination
+of information. Given its accessibility and proficiency as an information
+exchange tool, individuals involved in social movements have taken to them
+in conjunction, or in replacement, of real-world social mobilization.
+During the 2012 Italian protests for global economic change, the riots in
+Rome were mirrored by Twitter activity both on the same day and in the
+following days after the protests [@vicari2013public]. Tweeting was
+determined to be more effective locally in discussing real-world, real-time
+events than traditional mainstream media platforms. As more and more
+individuals rely on social media to obtain local news and information, it
+becomes increasingly important to understand just how these micro-blogs
+reflect real-world action.
 
 ## Use of Nonlinear Methods in Naturally Occurring Data
-Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
-Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
-This notion has been increasingly replaced by ideas from dynamical systems theory.
-Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts [@turvey2018lectures].
-When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
-Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
-Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
-The primary methods used in the current work is cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and it’s off-shoot, windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
-CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions [for a review, see @fusaroli2014analyzing] and interpersonal synchrony [@paxton2017interpersonal].
-We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
+Traditional linear analyses have led to many notable discoveries in the
+domains of psychology and political science, but continuous data pose
+problems that are not easily overcome with these methods. Events have
+historically been conceptualized as linear chains of smaller, sequential
+events with one occurrence leading to the next. This notion has been
+increasingly replaced by ideas from dynamical systems theory. Rather than
+a chain of events, continuous data can be thought of as nested occurrences,
+where mutually constrained parts (e.g., citizens, governments, real-world
+events, social media platforms) are constantly interacting, leading to
+more global behaviors that are larger than the sum of the parts
+[@turvey2018lectures]. When analyzed as dynamical systems, many phenomena
+exhibit new nonlinear patterns that were formerly overlooked. Continuous
+data subject to linear analyses becomes flattened, and the variability
+that is fundamental to these systems and their evolution over time is
+ignored. Nonlinear methods provide means for capturing the rich temporal
+dynamics and variability that unfold in continuous data.
+
+The primary methods used in the current work is cross-recurrence
+quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
+windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
+CRQA has successfully been used to gain a better understanding of many
+complex human phenomena, such as human social interactions
+[for a review, see @fusaroli2014analyzing] and interpersonal synchrony
+[@paxton2017interpersonal]. We argue that the use of nonlinear methods in
+the investigation of political science phenomena will lead to new insights
+and development of more robust theories.
 
 ## The Present Work
-Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
-We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
-Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
-This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
-Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence], we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
-We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
-We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
-Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
-As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
+Social media has become a primary platform for social movements and
+activism across the world, but the extent to which virtual activism
+reflects real-world mobilization is still largely unknown. We
+conceptualize the physical and virtual movements as a dynamical system,
+both constantly interacting and influencing the other. Both real- and
+virtual-world collective coordination were powerful tools in the events
+of Arab Spring, and are undeniably linked. This study aims to explore
+the dynamics of Syrian individuals who took to Twitter to raise
+awareness about the events of Arab Spring and bring about mass mobilization.
+Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
+and windowed cross-recurrence quantification analysis
+[WCRQA; @webber2005recurrence], we analyzed the dynamics of social
+cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts
+of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative
+events would show high levels of determinism, as this time period was
+marked by daily violence which often leads to increased salience. We also
+hypothesized that the count of positive events would not show patterns of
+determinism, as these events were likely overshadowed by the salient
+negative daily occurrences. Using WCRQA, we hoped to identify shifts in the
+dynamics of the systems that could then be linked to real world shifts in
+conflict frequency. As social cohesion has never been analyzed using
+nonlinear methods, the analyses contained herein are largely exploratory.
+The goal of this endeavor is to gain a better understanding of how events
+of different intensities during times of turmoil may enhance or deter
+social cohesion in social media communication, and how social mobilization
+may be evident in the dynamic coupling of cohesion and real-world events.
 
@@
 
-The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets occurring between March 30, 2012 and June 15, 2012.
-Using the Twitter streaming API, servers at the University of Texas at Austin collected the tweets.
-The servers were run on a stable (LTS) version of Ubuntu Linus, 10.04, and were connected directly to the high-bandwidth UT network maintained by IT services.
-Tweets collected contained one or more of the following keywords: “syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These keywords were chosen based on the most distinctive terms used in news articles covering the Arab Spring in Syria at the time.
-A node.js script was used to reinitialize the connection to Twitter's servers whenever the script timed out due to a period of silence.
-The script requested data from the API endpoint using basic HTTP authentication (OAuth was optional, at the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored the data directly to the local hard disk.
-The tweets were then post-processed with a Python script to convert the JSON-formatted tweets to tab-separated files and were then compressed to maximize storage efficiency.
+The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
+occurring between March 30, 2012 and June 15, 2012. Using the Twitter
+streaming API, servers at the University of Texas at Austin collected
+the tweets. The servers were run on a stable (LTS) version of Ubuntu
+Linus, 10.04, and were connected directly to the high-bandwidth UT network
+maintained by IT services.
+
+Tweets collected contained one or more of the following keywords:
+“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These
+keywords were chosen based on the most distinctive terms used in news
+articles covering the Arab Spring in Syria at the time. A node.js script
+was used to reinitialize the connection to Twitter's servers whenever the
+script timed out due to a period of silence. The script requested data from
+the API endpoint using basic HTTP authentication (OAuth was optional, at
+the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored
+the data directly to the local hard disk. The tweets were then post-processed
+with a Python script to convert the JSON-formatted tweets to tab-separated
+files and were then compressed to maximize storage efficiency.
+
 All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.
@@
 ### Event Data
-Event data were obtained from the 2012 Integrated Crisis Early Warning System [ICEWS; @DVN/28075_2015].
-The event data were first filtered to remove incomplete and incorrectly formatted data.
-They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
-To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
+Event data were obtained from the 2012 Integrated Crisis Early Warning
+System [ICEWS; @DVN/28075_2015]. The event data were first filtered to
+remove incomplete and incorrectly formatted data. They were then filtered
+to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were
+filtered again to include events that were both directed at (i.e., target)
+or directed by (i.e., source) Syria (n = 7990).
 
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
-If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
-The tweets were first sorted into ascending order by timestamp.
-They were then grouped into successive sets of five tweets.
-Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
-1-3).
-This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
-Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
+The social cohesion or linguistic similarity of daily tweets was calculated
+by quantifying the frequency of shared content words with respect to those
+words’ frequencies in the entire tweet corpus. If a linguistic term has a
+high frequency in one tweet but has a low frequency in the whole tweet
+corpus, then it is more likely a content word and is this given more weight
+in calculating social cohesion.
+
+The tweets were first sorted into ascending order by timestamp. They were
+then grouped into successive sets of five tweets. Inverse frequency
+weighting for the overlap words and all words was conducted for each pair
+of two tweets in the group of five, then divided to get the social cohesion
+score for that pair (see Eq. 1-3). This resulted in ten social cohesion
+values for each group of five tweets, which were then averaged. Finally,
+the mean of all average cohesion values for all groups was taken to get
+a social cohesion score for each day.
 
@@
 
-The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
-All hashtags and URLs were included in the analysis.
-This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see @jones1972statistical and @robertson2004understanding.
+The social cohesion calculation was performed on a subset of the corpus
+containing (recalculate with new date span) English and (recalculate with
+new date span) Arabic tweets. All hashtags and URLs were included in the
+analysis. This method is similar to that of inverse document frequency (IDF).
+For more information on IDF, see @jones1972statistical and
+@robertson2004understanding.
 
 ### ICEWS Event Time Series
-Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
-Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
-This well-validated coding scheme allows for numerical quantification of different event types.
-For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
-Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
-Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the
+Defense Advanced Research Project Agency, the daily events in Syria were
+scored with an intensity rating ranging from -10 to 10. Negative events,
+such as riots and attacks, are coded with low negative numbers while
+positive, peaceful events are coded with high positive numbers. This
+well-validated coding scheme allows for numerical quantification of
+different event types.
+
+For both the target only and the target and source data, time series of
+the count of all events were generated by summing the total number of events
+on each day, irrespective of ICEWS score. Similarly, time series of count
+of positive events were generated by summing the number of ICEWS events
+for each day that had an intensity rating greater than zero. Lastly,
+time series of count of negative events were generated by summing the number
+of ICEWS events for each day that had an intensity rating less than zero.
 
@@
 ### Cross-Recurrence Quantification Analysis
-We first used cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
-As an extension of RQA, which captures the patterns of revisited states of a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
-Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system [cf.
-Nyquist frequency in signal processing; @grenander1959probability].
-We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
-In CRQA, a recurrent point is when two signals share the same state.
-These shared states can be at the same time or at later points in the time series.
+We first used cross-recurrence quantification analysis
+[CRQA; @zbilut1998detecting] to investigate the temporal patterns of
+social cohesion and real-world events in Syria during Arab Spring. As
+an extension of RQA, which captures the patterns of revisited states of
+a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA
+allows for two time series to be projected onto one another to investigate
+shared states and trajectories. Nonlinear analyses such as CRQA can reveal
+dynamics that are not captured by traditional linear methods.
+
+In order to perform CRQA, the time series need to be converted to the same
+scale, while still preserving a sampling rate that respects the native
+timescale of the system
+[cf. Nyquist frequency in signal processing; @grenander1959probability].
+We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
+(e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different
+levels of social cohesion and counts of all, positive, and negative events
+on each day. In CRQA, a recurrent point is when two signals share the same
+state. These shared states can be at the same time or at later points in
+the time series.
 
 #### Visualization
-A recurrence plot (RP) is the visual representation of CRQA.
-To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
-Visually analyzing these plots can help reveal patterns of structure and recurrence.
-The line y = x is known as the line of identity.
-This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) for examples of RPs.
+A recurrence plot (RP) is the visual representation of CRQA. To construct
+a recurrence plot, two time series are plotted against each other on the
+X and Y axes, and at every point where they share the same state, and point
+in placed on the plot to indicate recurrence. Visually analyzing these plots
+can help reveal patterns of structure and recurrence. The line y = x is known
+as the line of identity. This line falls where the time series match
+temporally, and a filled line would indicate perfect synchrony between the
+two time series. See
+Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)
+for examples of RPs.
 
 #### Metrics
-The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
-This metrics gives a general description of how frequently the time series are sharing the same states.
-In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
+The percentage of recurrent points to total possible points is a metric
+called recurrence rate (RR). This metrics gives a general description of
+how frequently the time series are sharing the same states. In the current
+study, a recurrent point would indicate that the level of social cohesion
+and frequency of events were at the same intensity.
+
 Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
-The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
-For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
-The average length of the line structures is called mean line (L).
-This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
-The longest line length is called max line (maxL).
-maxL indicates the longest instance of being “stuck” in a particular state together.
-The total number of lines is called NRLINE.
-The more lines there are, the more coordinated the system may be.
-The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
-These entropy metrics help indicate the stability and predictability of the system.
-When one of the signals gets “stuck” in a state and the other moves on to other states, this results in vertical line structures.
-The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see @R-crqa.
+These are conceptualized as shared trajectories, where the two time series
+are moving together across time in a shared state. The percentage of
+recurrent points that make up diagonal line structures (i.e., two or more
+consecutive points) is a metric called percent determinism (DET). For the
+current project, a high DET would indicate that not only are the levels of
+social cohesion and frequency of events occurring at similar intensities,
+but they are doing so across consecutive days.
+
+The average length of the line structures is called mean line (L). This can
+be conceptualized as the average amount of time that the two time series move
+together before one or both shift states. The longest line length is called
+max line (maxL). maxL indicates the longest instance of being “stuck” in a
+particular state together. The total number of lines is called NRLINE. The
+more lines there are, the more coordinated the system may be. The
+complexity or variability of line lengths is captured by a metric called
+entropy (ENTR) and entropy while accounting for the total number of lines in
+the plot is normalized entropy (rENTR). These entropy metrics help indicate
+the stability and predictability of the system. When one of the signals gets
+“stuck” in a state and the other moves on to other states, this results in
+vertical line structures. The proportion of points forming vertical line
+structures is a metric called laminarity (LAM) and the average length of the
+vertical trajectories is called trapping time (TT). For more detail on CRQA
+metrics, see @R-crqa.
 
 #### Parameters
-To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
-Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
-No normalization was done, and lines were considered two or more consecutive recurrent points.
-The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see @R-crqa.
+To conduct the analyses on the decile data, the parameters were set to those
+typically used in categorical CRQA. Delay was set to zero, embedding dimension
+was set to 1, and radius was set to .001 to allow for only exact recurrent
+matches. No normalization was done, and lines were considered two or more
+consecutive recurrent points. The Theiler window was set to zero to include
+points along the line of identity. For more details on the CRQA parameters and
+how they impact the analysis, see @R-crqa.
 
 #### Permutation Test
-Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R [@R-base], 1000 permuted time series were created for each of the real time series.
-A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
-CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
-This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
-Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
-Thus, RR is not included in the inferential tests.
-For more information on permutation tests, see @good2013permutation.
+Using the deciled, real time series of social cohesion, count of all events,
+count of positive events, and count of negative events, a permutation test was
+done to determine statistical difference from chance for each CRQA metric.
+Using the sample function in base R [@R-base], 1000 permuted time series were
+created for each of the real time series. A permutation test is similar to
+bootstrapping, except that the sampling of observations is done without
+replacement. CRQA was then run 1000 times for social cohesion and count of all
+events, social cohesion and count of positive events, and social cohesion and
+count of negative events using the permuted time series. This resulted in
+1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles
+of the metrics from the permuted CRQ analyses. Given that a permutation test
+is similar to bootstrapping but does not include replacement, all points were
+included in each CRQA analysis, leaving RR the same across all analyses. Thus,
+RR is not included in the inferential tests. For more information on permutation
+tests, see @good2013permutation.
 
 ### Windowed Cross-Recurrence Quantification Analysis
-We used windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence] to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
-In this analysis, a smaller “window” of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
-The window remains the same size and “slides” diagonally up the line of identity.
-The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+We used windowed cross-recurrence quantification analysis
+[WCRQA; @webber2005recurrence] to further investigate the evolution of the
+temporal dynamics of social cohesion and real-world events. In this analysis,
+a smaller “window” of time points is used to calculate CRQA and capture more
+fine-grain dynamics of two time series. The window remains the same size and
+“slides” diagonally up the line of identity. The changes in the CRQA metrics
+across the windows can reveal changes in dynamics that can then be linked to
+external, real-world events.
 
 #### Metrics
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
-These metrics can then be plotted as a time series to visualize their evolution over time.
-For these analyses, we decided to visualize recurrence rate and determinism.
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
+respective window. These metrics can then be plotted as a time series to
+visualize their evolution over time. For these analyses, we decided to
+visualize recurrence rate and determinism.
 
 #### Parameters
-In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
-First, a window size must be decided on.
-The window size will determine how many observations are used in each CRQA analysis.
-We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
-The second parameter to be chosen is a step size.
-Window step size is how far the window moves up the line of identity before conducting CRQA again.
-We chose 1 for the step size to understand how the metrics evolve from day to day.
-All other CRQA metrics remained the same as previously noted.
+In addition to the CRQA parameters, two other parameters are required when
+conducting WCRQA. First, a window size must be decided on. The window size
+will determine how many observations are used in each CRQA analysis. We
+conducted WCRQA with a window size of 14 to investigate the dynamics over
+two weeks and allow for the capture of more structure and thus a more
+meaningful interpretation of DET. The second parameter to be chosen is a
+step size. Window step size is how far the window moves up the line of identity
+before conducting CRQA again. We chose 1 for the step size to understand
+how the metrics evolve from day to day. All other CRQA metrics remained the
+same as previously noted.
 
 #### Visualization
-To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
-This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
-These dynamics can then be linked to other external events.
-See Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all) for examples.
+To visualize WCRQA, the resulting metrics from each window can be plotted
+as a time series. This allows for visual interpretation of the pattern or
+fluctuation of the metrics across time. These dynamics can then be linked
+to other external events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
+\@ref(fig:plot-wcrqa-source-targ-all) for examples.
 
 #### Permutation Test
-To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
-Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
-The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
+To visualize the differences in the WCRQA metrics from those obtained by
+chance, a permutation test was done to set upper and lower bounds for the
+95th and 99th percentiles. Using a sample size of 14, one-thousand permuted
+time series were generated without replacement for each real time series. The
+upper and lower 95th and 99th percentiles were set based on the distribution
+of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 ## Cross-Recurrence Quantification Analysis
-CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a
+permutation test to check for statistical difference from chance for all analyses and
+metrics.
 
@@
 
-WCRQA was performed using the crqa package [@R-crqa] for R [@R-base].
-Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-The trend lines are plotted in blue.
+WCRQA was performed using the crqa package [@R-crqa] for R [@R-base]. Permutation tests
+were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
+the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)),
+the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
+represented by horizontal orange lines. The trend lines are plotted in blue.
 
@@
 # Discussion
-In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
-We examined how social mobilization both virtually and physically evolve over time in tandem.
-Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
+In the present study, we investigated the dynamics of real-world events
+and online communication on Twitter in Syria during Arab Spring. We examined
+how social mobilization both virtually and physically evolve over time in
+tandem. Prior to now, the extent to which virtual mobilization on social
+media platforms such as Twitter has been largely unexplored. Using the
+nonlinear methods cross-recurrence quantification analysis and windowed
+cross-recurrence quantification analysis, we investigated the theory that
+virtual mobilization is increasingly reflective of real-world events
+during times of strife.
 
@@
 ### Syria as Target
-The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
-The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
-The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
-The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
+The significant result of DET for social cohesion and both the all events
+and negative events time series confirms our hypothesis, that increased
+salience of events is reflected in social cohesion on Twitter. The frequency
+of all events and of negative events thus result in a significant number
+of shared trajectories that are statistically different from chance. The
+non-significant results for all metrics for positive event count also
+confirm our hypothesis, and gives support to the theory that positive events
+are less coupled to social cohesion than the more salient, negative events
+during times of turmoil. The inevitable increased salience of event
+frequency and event violence thus leads to increased coupling with Twitter
+social cohesion.
 
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
-These additional observations are times where Syria initiated an event with another country.
-Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
-The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
-Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
-Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
-The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs; Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
-To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
+By adding Syria as a source in the data filtering, the dataset increased
+in size by 1,690 samples. These additional observations are times where
+Syria initiated an event with another country. Events initiated by Syria
+but directed internally within the country were already captured by the
+target only filtering. The increase in coupling between positive events
+and social cohesion is thus due to the inclusion of these externally
+directed events. Though CRQA metrics for count of all and count of
+negative events with social cohesion were largely unaffected, count of
+positive events and social cohesion showed significant levels of
+determinism, number of lines, max line length, and laminarity that were
+not present in the target filtered data. Given that the Syria during
+this time was still under Authoritarian rule, the government may have
+been initiating more positive external events to prevent intervention
+by other countries or try to cover up what was happening internally.
+We believe that the increased coupling of positive events is thus not
+reflective of actual social cohesion, but happened by chance. The
+inflation of the number of positive events when including source
+observations is causing increased coupling, but it is more likely that
+the Twitter users were using the platform to raise awareness of the
+violent, internal events that were being inflicted on them by their
+government officials and armies and not reporting on the positive
+external events that did not directly affect them or their safety.
+Further research should explore the semantic content of this tweet
+corpus to determine what the socially cohered language was focused on.
+By visual inspection of the recurrence plots (RPs;
+Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)),
+there appears to be a shift in the dynamics of these systems around
+observation 35, or May 3rd, 2012. To further investigate these local
+dynamics, we performed a sliding window technique known as windowed
+cross-recurrence quantification analysis (WCRQA).
 
@@
 ### Syria as Target
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)).
-The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
-These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET was entirely within chance (Figure \@ref(fig:plot-wcrqa-targ-all)).
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
+The time period of differing dynamics, from observation 38 through 43,
+appears to be captured by WCRQA of social cohesion and count of negative
+events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)). The
+amount of recurrence and determinism for these periods almost consistently
+lie above chance, suggesting that the intensity of negative events coincide
+with the degree of social cohesion found on Twitter, and that these states
+carry across multiple days in a way that is different from that of chance.
+
+The above-chance levels of determinism and recurrence rate are demonstrating
+the coupling of social cohesion and counts of all and negative events during
+times of strife. We can see this string of highly violent events reflected
+in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)),
+where from May 1st, 2020 to May 15th, 2020, the most frequently occurring
+event was almost consistently -10, the most violent event in the coding
+system. These dates directly correlate with the above chance RR and DET
+metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during
+this time period, DET was entirely within chance (Figure
+\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
+positive events are seemingly not coupled with the social cohesion on Twitter
+during civil uprisings during the Arab Spring.
 
 ### Syria as Source and Target
-WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
-Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
-WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
-This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
-Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
+WCRQA of recurrence rate on the source and target filtered data remained
+largely the same for count of all events and social cohesion, suggesting
+that large numbers on a given day will be reflective of increased levels
+of social cohesion. Determinism showed more frequent above-chance metrics
+for windows 39 and up, suggesting that the inclusion of externally
+directed events lead to higher event counts during these days and then
+was more reflective of the level of social cohesion on Twitter. WCRQA for
+count of positive events and social cohesion remained largely the same for
+RR and DET as the source only data. This again seems to support the idea
+that these two aren't actually coupled, but rather that the inflation of
+the positive counts lead to a spurious relationship. Count of negative
+events and social cohesion also showed similar trends for RR and DET,
+again attesting to the theory that negative events were coupled to social
+cohesion on Twitter while positive events happened by chance.
 
 ## Conclusion
-Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
-If consistent across other civil wars, these results have serious implications for monitoring global movements.
-While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
-By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
-Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
+Considering the invasiveness of social media in our everyday lives, it is
+inevitable that individuals involved in real-world social mobilization have
+utilized these platforms to their advantage. If consistent across other civil
+wars, these results have serious implications for monitoring global
+movements. While traditional media in regions of authoritarian rule are
+often biased, the self-organized nature of Twitter poses a new avenue to gain
+insight into truths about up-risings and social mobilization. By
+conceptualizing Twitter and real-world events as two components of an
+inextricably linked dynamical system, the levels of social cohesion within the
+virtual platform could be monitored for fluctuations indicating global shifts
+in power and peace. Social media mobilization can thus help alert us to
+real-world mobilization not communicated in mainstream media and allow for faster intervention.
 

### 2020-05-29 manuscript.tex

@@
 All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-all}; \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics other than TT (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, L, ENTR, LAM, and TT.
 All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
@@
 All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-all}; \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR.
 All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-neg}; \autoref{table-2}).
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure \ref{fig:plot-wcrqa-targ-all}).
-Determinism is also almost consistently above chance from the 39th window onwards (Figure \ref{fig:plot-wcrqa-targ-all}).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves and determinism stays almost entirely within chance across windows (Figure \ref{fig:plot-wcrqa-targ-all}).
-For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window and determinism is also above or nearly above chance from the 38th through 43rd window (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 7th-12th and 36th-47th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+Determinism is largely above chance from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves with largly above chance RR from the 1st-18th and 32nd-45th windows.
+Determinism was at or above chance for the 8th-17th, 32nd-34th, and the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of negative events, recurrence rate stays above or almost above chance from the 4th-7th and 43rd-47th windows, and determinism is above or nearly above chance in the 1st and 2nd windows, with short intermittent peaks in later windows (Figure \ref{fig:plot-wcrqa-targ-all}).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves and determinism stays largely within chance with the exception of windows 13-19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-For social cohesion and negative events, there appears to be an extended time period where RR and DET were greater than chance, from the 35th through 46th windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 7th-13th and 26th-47th windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+Determinism also shows above or nearly above chance values in windows 7th-17th and short, intermittent peaks between the 34th and 61st windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves with largely above chance values in the first 20 windows and the 32nd-45th windows.
+Determinism stays largely within chance with the exception of windows 13 through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+For social cohesion and negative events, there appears to be an extended time period where RR (32nd-47th windows) and DET (35th-39th windows) were above of nearly above chance (Figure \ref{fig:plot-wcrqa-source-targ-all}).
 These windows span from May 3rd, 2012 to May 14th, 2012.

### 2020-05-29 manuscript.Rmd
Finish hard wrapping

@@
 ## Cross-Recurrence Quantification Analysis
-CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a
-permutation test to check for statistical difference from chance for all analyses and
-metrics.
+CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We 
+conducted a permutation test to check for statistical difference from chance 
+for all analyses and metrics.
 
 ### Syria as Target
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, L, ENTR, LAM, and TT.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all events 
+found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
+All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all);
+\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
+count of positive events found no statistical difference from chance for any 
+of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
+\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
+count of negative events found a statistical difference from chance for DET, 
+NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
+\@ref(fig:plot-rp-targ-neg); \autoref{table-1}). Looking at the recurrence 
+plots there appears, to be a shift in dynamics around the 36th observation 
+which corresponds to May 4th, 2012.
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 7th-12th and 36th-47th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
-Determinism is largely above chance from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves with largly above chance RR from the 1st-18th and 32nd-45th windows.
-Determinism was at or above chance for the 8th-17th, 32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
-For social cohesion and count of negative events, recurrence rate stays above or almost above chance from the 4th-7th and 43rd-47th windows, and determinism is above or nearly above chance in the 1st and 2nd windows, with short intermittent peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of all events, there is a consistent period 
+of above chance recurrence rate from the 7th-12th and 36th-47th window 
+(Figure \@ref(fig:plot-wcrqa-targ-all)). Determinism is largely above chance 
+from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)). For
+social cohesion and count of positive events there is a downward trend in RR 
+as the window moves with largly above chance RR from the 1st-18th and 
+32nd-45th windows. Determinism was at or above chance for the 8th-17th, 
+32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)). 
+For social cohesion and count of negative events, recurrence rate stays above
+or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
+is above or nearly above chance in the 1st and 2nd windows, with short intermittent 
+peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 7th-13th and 26th-47th windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-Determinism also shows above or nearly above chance values in windows 7th-17th and short, intermittent peaks between the 34th and 61st windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves with largely above chance values in the first 20 windows and the 32nd-45th windows.
-Determinism stays largely within chance with the exception of windows 13 through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-For social cohesion and negative events, there appears to be an extended time period where RR (32nd-47th windows) and DET (35th-39th windows) were above of nearly above chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-These windows span from May 3rd, 2012 to May 14th, 2012.
+For social cohesion and count of all events, there is a consistent period of
+above or nearly above chance determinism from the 7th-13th and 26th-47th 
+windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). Determinism also 
+shows above or nearly above chance values in windows 7th-17th and short, 
+intermittent peaks between the 34th and 61st windows (Figure 
+\@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and count of 
+positive events, there is a downward trend in RR as the window moves with 
+largely above chance values in the first 20 windows and the 32nd-45th windows. 
+Determinism stays largely within chance with the exception of windows 13 
+through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion
+and negative events, there appears to be an extended time period where RR 
+(32nd-47th windows) and DET (35th-39th windows) were above of nearly above 
+chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
+May 3rd, 2012 to May 14th, 2012.
 
@@
 in power and peace. Social media mobilization can thus help alert us to
-real-world mobilization not communicated in mainstream media and allow for faster intervention.
+real-world mobilization not communicated in mainstream media and allow for 
+faster intervention.
 

### 2020-05-29 scripts/primary-analyses/03_windowed_crqa.R
Give WCRQA figures more informative main titles

@@ -746,7 +746,8 @@ plot_source_target_windowed_neg_DET = ggplot(data = wincrqa_neg_df_source_target
 plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
-                       "with event count data",
+                       "\nwith event count data",
+                       "with source and target filtering",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -997,7 +998,8 @@ plot_target_windowed_neg_DET = ggplot(data = wincrqa_neg_df_target,
 plot_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
-                       "with event count data",
+                       "\nwith event count data",
+                       "with target-only filtering",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_target_windowed_all_RR,

### 2020-05-29 manuscript.Rmd
Impose hard wrapping on abstract
Ensure appendix doesn't render
Edits to intro

@@
 abstract: |
-  Social mobilization requires effective collective coordination.
-In recent years, individuals involved in social movements have taken to social media platforms to reach broader audiences at rapid speeds.
-Effective virtual mobilization similarly requires social cohesion and coordination, yet the degree to which virtual mobilization reflects or drives real-world movements is unclear.
-Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
-Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day but not with counts of positive events.
-This suggests that virtual mobilization does reflect real-world movements but only for salient, frequent and negative events.
-We conclude with a discussion of implications and applications of nonlinear methods in political science research.
+  Social mobilization requires effective collective coordination. In recent 
+  years, individuals involved in social movements have taken to social media
+  platforms to reach broader audiences at rapid speeds. Effective virtual 
+  mobilization similarly requires social cohesion and coordination, yet the 
+  degree to which virtual mobilization reflects or drives real-world movements
+  is unclear. Here, we explore the dynamics of real-world events and social 
+  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear 
+  methods cross-recurrence quantification analysis and windowed cross-recurrence
+  quantification analysis, we investigate if counts of all daily events, daily 
+  positive events, and daily negative events are coupled with social cohesion 
+  found in Syrian tweets. Results indicate that virtual social cohesion is 
+  coupled with the counts of all and negative events each day but not with 
+  counts of positive events. This suggests that virtual mobilization does reflect 
+  real-world movements but only for salient, frequent and negative events. We 
+  conclude with a discussion of implications and applications of nonlinear 
+  methods in political science research.
   <!-- https://tinyurl.com/ybremelq -->
@@
 draft             : no
-appendix          : "appendix.Rmd"
+appendix          :
 
@@
 bring individuals together and create emergent patterns of communication
-and action. Online communication has historically been used to document
-and communicate archival information about events, but it has been
-increasingly used to bring about social change. From a dynamical
+and action. From a dynamical
 systems perspective, these different means of social coordination during
@@
 single system, mutually constrained and constantly interacting and
-influencing one another [@mahner1997foundations]. Investigation of the
+influencing one another [@mahner1997foundations]. 
+Increasingly, social media platforms are being utilized during
+social mobilization, but the relationship between virtual and real-world
+mobilization is still largely unknown. Investigation of the
 coupling of real-world mobilization and social cohesion could provide
-new insight into the power of social media during mobilization and the
-ways in which individuals utilize it to bring about, or respond to, social
-change. Increasingly, social media platforms are being utilized during
-social mobilization, but the relationship between virtual and real-world
-mobilization is still largely unknown. The present work aims to understand
-how physical and virtual movements coexist and interact from a dynamical
-systems perspective.
+new insights into the power of social media during mobilization and 
+it can be used to respond to or create social change. The present work 
+aims to understand how physical and virtual movements coexist and interact 
+from a dynamical systems perspective.
 

### 2020-05-29 manuscript.Rmd
More edits to introduction

@@
 rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death, the
-long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
-country. The events of Tunisia rapidly spread to surrounding countries that
-were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
-and Syria. These mass movements would not have been possible without
-efficient interpersonal coordination, both physically and virtually on social
-media platforms, such as Twitter. The events of Arab Spring have been
+as a catalyst for the Tunisian Revolution, and one week after his death,
+Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
+country. The events of Tunisia rapidly spread to surrounding countries 
+also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
+and Syria.
+
+These mass movements would not have been possible without
+efficient large-scale coordination, both physically and virtually on social
+media platforms. Along with Facebook, Twitter has been credited as essential 
+to the Arab Spring---both for protesters (as a means to coordinate with one 
+another and to communicate with the world) and for the government response
+(to monitor and track protestors to crack down on dissent) [@comninos2011twitter]. 
+The events of Arab Spring have been
 thoroughly discussed within the political science literature
-[e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge,
-the use of Twitter by Syrian citizens has not been investigated.
+[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
+the direct coupling between Syrian Twitter use and international action
+has not been investigated.
 

### 2020-05-29 manuscript.Rmd
Edits to social cohesion and mobilization subsections

@@
 
-## Social Cohesion
+## Social Cohesion and Social Mobilization
 Real-world collective action is known to bring about a sense of togetherness,
@@
 to act in ways that would not have on their own. Being overcome with this
-feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
-While feelings of social connection may lead to violence, increased exposure
-to violence can result in feelings of social cohesion. @gilligan2014civil
+feeling can lead to violence [@collins2009violence; @spaaij2014sports].
+Conversely, increased exposure
+to violence can result in positive social cohesion. @gilligan2014civil
 found that exposure to fatal wartime violence resulted in increased prosocial
 motivations, including cooperative behaviors, feelings of trust, and overall
-community-level social cohesion. Just as real-world social cohesion can be
-quantified, the same is true for online cohesion. Strategic communication on
-social media in the form of social cohesion of language can lead to real-world
-social change, and exposure to real-world violence could result in social
+community-level social cohesion.
+
+Just as real-world social cohesion can be
+quantified, so can online cohesion. While this can be quantified in many ways,
+one kind of cohesion can be found in the similarity in language use on social media.
+This implicit or explicit similarity in language use can indicate shared
+beliefs, thoughts, and feelings, as has been studied in research on language style
+in psycholinguistics and social psychology 
+[@gonzales2010language, @tausczik2010psychological, @brennan1996conceptual]; 
+although previous work on language style
+has often focused on individuals and small groups, this can be scaled up to examine
+massive social-level changes [@michel2011quantitative, @fusaroli2015timescales]. 
+This kind of massive online social cohesion can lead to real-world
+social change.
+
+Combining these separate threads, it is reasonable to expect that real-world actions 
+and online social interactions would be enmeshed, driving and being driven by 
+one another. Rather than expecting that only real-world social cohesion would be
+driven by real-world action, we would expect interaction between real-world and
+virtual dynamics: In this case, exposure to real-world violence could result in social
 cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator of increased social organization and mobilization on the ground.
+an indicator and a result of increased social organization and mobilization 
+on the ground.
 
-## Social Media as a Platform for Mobilization
-Social media platforms, such as Twitter, offer rapid real-time dissemination
-of information. Given its accessibility and proficiency as an information
-exchange tool, individuals involved in social movements have taken to them
-in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in
-Rome were mirrored by Twitter activity both on the same day and in the
-following days after the protests [@vicari2013public]. Tweeting was
+Social media platforms provide one way of enabling this kind of online social
+cohesion by offering distributed information-gathering and real-time information
+dissemination. Given its accessibility and proficiency as an information
+exchange tool, Twitter has provided individuals involved in social movements
+an opportunity to complement or even replace real-world social mobilization.
+For example, during the 2012 Italian protests for global economic change, the riots in
+Rome were mirrored by Twitter activity both on the day of the protests and in the
+days following them [@vicari2013public]. Tweeting was
 determined to be more effective locally in discussing real-world, real-time

### 2020-05-29 manuscript.Rmd
Fix syntax for multiple parenthetical citations

@@
 in psycholinguistics and social psychology 
-[@gonzales2010language, @tausczik2010psychological, @brennan1996conceptual]; 
+[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
 although previous work on language style
 has often focused on individuals and small groups, this can be scaled up to examine
-massive social-level changes [@michel2011quantitative, @fusaroli2015timescales]. 
+massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
 This kind of massive online social cohesion can lead to real-world

### 2020-05-29 manuscript.Rmd
Edits to nonlinear methods section

@@
 
-## Use of Nonlinear Methods in Naturally Occurring Data
+## Using Nonlinear Methods to Capture Complex Relationships
+Given the hypothesized interrelationship between the real-world
+and online actions---and the notorious messiness of naturally occurring
+data---it is critical to find appropriate analysis tools that can
+identify the complex interconnections.
 Traditional linear analyses have led to many notable discoveries in the
-domains of psychology and political science, but continuous data pose
+domains of psychology and political science, but time series data pose
 problems that are not easily overcome with these methods. Events have
 historically been conceptualized as linear chains of smaller, sequential
-events with one occurrence leading to the next. This notion has been
+events with one occurrence leading to the next. 
+Certain kinds of data are relatively well-suited to these analyses,
+but messy, complex, variable data from real-world events can pose
+challenges from overpowered samples to violation of underlying
+statistical assumptions [@paxton2017finding].
+
+At the same time, the foundational theoretical assumptions of a 
+linear world has been
 increasingly replaced by ideas from dynamical systems theory. Rather than
-a chain of events, continuous data can be thought of as nested occurrences,
+a chain of events, time series data can be thought of as nested occurrences,
 where mutually constrained parts (e.g., citizens, governments, real-world
@@
 more global behaviors that are larger than the sum of the parts
-[@turvey2018lectures]. When analyzed as dynamical systems, many phenomena
-exhibit new nonlinear patterns that were formerly overlooked. Continuous
-data subject to linear analyses becomes flattened, and the variability
-that is fundamental to these systems and their evolution over time is
-ignored. Nonlinear methods provide means for capturing the rich temporal
-dynamics and variability that unfold in continuous data.
+[@turvey2018lectures]. Linear analyses flatten these nonlinear patterns in 
+time series data and ignore the variability
+that is fundamental to these systems and their evolution over time. 
+However, when analyzed as dynamical systems, many phenomena
+exhibit new nonlinear patterns that were formerly overlooked. 
+Nonlinear methods provide means for capturing the rich temporal
+dynamics and variability that unfold in time series data.
 
-The primary methods used in the current work is cross-recurrence
+Although a number of other nonlinear methods exist, 
+the primary nonlinear method used in the current work is cross-recurrence
 quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
@@
 CRQA has successfully been used to gain a better understanding of many
-complex human phenomena, such as human social interactions
-[for a review, see @fusaroli2014analyzing] and interpersonal synchrony
-[@paxton2017interpersonal]. We argue that the use of nonlinear methods in
+complex human phenomena, including a variety of human social interactions
+[for a review, see @fusaroli2014analyzing]. 
+Much as it has for psychology, we argue that the use of nonlinear methods in
 the investigation of political science phenomena will lead to new insights
-and development of more robust theories.
+and the development of more robust theories.
 

### 2020-05-29 manuscript.Rmd
Edit: Present study section

@@
 activism across the world, but the extent to which virtual activism
-reflects real-world mobilization is still largely unknown. We
+reflects and drives real-world mobilization is still largely unknown. 
+In the current work, we
 conceptualize the physical and virtual movements as a dynamical system,
-both constantly interacting and influencing the other. Both real- and
+both constantly interacting and influencing the other. We aim to study
+this by analyzing the real-world events and online social cohesion
+during nearly three months of the Arab Spring. Both real- and
 virtual-world collective coordination were powerful tools in the events
-of Arab Spring, and are undeniably linked. This study aims to explore
-the dynamics of Syrian individuals who took to Twitter to raise
-awareness about the events of Arab Spring and bring about mass mobilization.
+of the Arab Spring and are undeniably linked. This study aims to explore
+the dynamics of Syrian Twitter users, who used the social media platform to raise
+awareness about the Arab Spring and bring about mass mobilization.
+
 Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
 and windowed cross-recurrence quantification analysis
-[WCRQA; @webber2005recurrence], we analyzed the dynamics of social
-cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts
-of all, positive, and negative real-world events on those respective days.
+[WCRQA; @webber2005recurrence], we analyzed the co-evolution of social
+cohesion online and real-world events. Specifically, using heterogeneous
+data from March 30, 2012, to June 15, 2012, we compared the social cohesion
+of Syrian tweets with the counts
+of all, positive, and negative real-world events.
+
 We hypothesized that the count of all events and the count of negative
@@
 determinism, as these events were likely overshadowed by the salient
-negative daily occurrences. Using WCRQA, we hoped to identify shifts in the
-dynamics of the systems that could then be linked to real world shifts in
-conflict frequency. As social cohesion has never been analyzed using
-nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events
-of different intensities during times of turmoil may enhance or deter
-social cohesion in social media communication, and how social mobilization
+negative daily occurrences. 
+After testing these hypotheses, we then conducted exploratory analyses 
+to further examine the patterns identified with CRQA. Using WCRQA,
+we sought to identify shifts in the
+dynamics of the systems that could then be linked to real-world shifts in
+conflict frequency.
+Through these analyses, our primary goal in the current work was to uncover
+(1) how different intensities during times of turmoil may enhance or deter
+social cohesion in social media communication and (2) how social mobilization
 may be evident in the dynamic coupling of cohesion and real-world events.
+
+An additional focus of the current work is to introduce cross-recurrence
+quantification analysis---a longstanding method from physics that has 
+since become influential in a variety of other fields---to political 
+science. We do so by providing detailed descriptions of the methods and
+providing clear directions about interpretation and significance testing
+even with relatively small-*n* or case studies. After demonstrating these
+methods' utility with this dataset, we close the paper with specific
+suggestions to political scientists interested in incorporating these
+methods into their work.
 

### 2020-05-29 manuscript.Rmd
Fix in-line image issue

@@
 bring individuals together and create emergent patterns of communication
-and action. From a dynamical
+and action. Online communication has historically been used to document
+and communicate archival information about events, but it has been
+increasingly used to bring about social change. From a dynamical
 systems perspective, these different means of social coordination during
@@
 single system, mutually constrained and constantly interacting and
-influencing one another [@mahner1997foundations]. 
-Increasingly, social media platforms are being utilized during
+influencing one another [@mahner1997foundations]. Investigation of the
+coupling of real-world mobilization and social cohesion could provide
+new insight into the power of social media during mobilization and the
+ways in which individuals utilize it to bring about, or respond to, social
+change. Increasingly, social media platforms are being utilized during
 social mobilization, but the relationship between virtual and real-world
-mobilization is still largely unknown. Investigation of the
-coupling of real-world mobilization and social cohesion could provide
-new insights into the power of social media during mobilization and 
-it can be used to respond to or create social change. The present work 
-aims to understand how physical and virtual movements coexist and interact 
-from a dynamical systems perspective.
+mobilization is still largely unknown. The present work aims to understand
+how physical and virtual movements coexist and interact from a dynamical
+systems perspective.
 
@@
 ## Windowed Cross-Recurrence Quantification Analysis
-```{r primary-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
+```{r primary-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide', include = FALSE}
 

### 2020-05-29 manuscript.tex
Fix in-line image issue

@@
             pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
-            pdfkeywords={Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring},
+            pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
             pdfborder={0 0 0},
@@
 Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidge Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
-\keywords{Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring\newline\indent Word count: X}
+\keywords{social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring\newline\indent Word count: X}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \abstract{
-Social mobilization requires effective collective coordination.
-In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
-Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
-Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
-Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
-This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
-We conclude with a discussion of implications and applications of nonlinear methods in political science research.
+Social mobilization requires effective collective coordination. In recent
+years, individuals involved in social movements have taken to social media
+platforms to reach broader audiences at rapid speeds. Effective virtual
+mobilization similarly requires social cohesion and coordination, yet the
+degree to which virtual mobilization reflects or drives real-world movements
+is unclear. Here, we explore the dynamics of real-world events and social
+cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear
+methods cross-recurrence quantification analysis and windowed cross-recurrence
+quantification analysis, we investigate if counts of all daily events, daily
+positive events, and daily negative events are coupled with social cohesion
+found in Syrian tweets. Results indicate that virtual social cohesion is
+coupled with the counts of all and negative events each day but not with
+counts of positive events. This suggests that virtual mobilization does reflect
+real-world movements but only for salient, frequent and negative events. We
+conclude with a discussion of implications and applications of nonlinear
+methods in political science research.
 }
@@
 
-Social coordination has long been used both physically and virtually to start and carry out collective actions.
-These collective events bring individuals together and create emergent patterns of communication and action.
-Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
-From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another (Mahner \& Bunge, 1997).
-Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
-The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
+Social coordination has long been used both physically and virtually
+to start and carry out collective actions. These collective events
+bring individuals together and create emergent patterns of communication
+and action. Online communication has historically been used to document
+and communicate archival information about events, but it has been
+increasingly used to bring about social change. From a dynamical
+systems perspective, these different means of social coordination during
+times of turmoil can be considered two complementary components of a
+single system, mutually constrained and constantly interacting and
+influencing one another (Mahner \& Bunge, 1997). Investigation of the
+coupling of real-world mobilization and social cohesion could provide
+new insight into the power of social media during mobilization and the
+ways in which individuals utilize it to bring about, or respond to, social
+change. Increasingly, social media platforms are being utilized during
+social mobilization, but the relationship between virtual and real-world
+mobilization is still largely unknown. The present work aims to understand
+how physical and virtual movements coexist and interact from a dynamical
+systems perspective.
 
@@
 
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
-His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
-His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
-The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
-These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
-The events of Arab Spring have been thoroughly discussed within the political science literature (e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
+unjustifiably stripped of his vendor cart by municipal officials. His
+humiliation led him to set himself on fire in protest to the authoritarian
+rule, ultimately leading to his death several days later. His actions served
+as a catalyst for the Tunisian Revolution, and one week after his death, the
+long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
+country. The events of Tunisia rapidly spread to surrounding countries that
+were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
+and Syria. These mass movements would not have been possible without
+efficient interpersonal coordination, both physically and virtually on social
+media platforms, such as Twitter. The events of Arab Spring have been
+thoroughly discussed within the political science literature
+(e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge,
+the use of Twitter by Syrian citizens has not been investigated.
 
@@
 
-Real-world collective action is known to bring about a sense of togetherness, also known as \enquote{collective effervescence} (Durkheim, 1995).
-This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
-Being overcome with this feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
-While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
-Gilligan, Pasquale, and Samii (2014) found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
-Just as real-world social cohesion can be quantified, the same is true for online cohesion.
-Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
-Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
+Real-world collective action is known to bring about a sense of togetherness,
+also known as \enquote{collective effervescence} (Durkheim, 1995). This
+feeling of being a part of something larger than oneself leads individuals
+to act in ways that would not have on their own. Being overcome with this
+feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
+While feelings of social connection may lead to violence, increased exposure
+to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2014)
+found that exposure to fatal wartime violence resulted in increased prosocial
+motivations, including cooperative behaviors, feelings of trust, and overall
+community-level social cohesion. Just as real-world social cohesion can be
+quantified, the same is true for online cohesion. Strategic communication on
+social media in the form of social cohesion of language can lead to real-world
+social change, and exposure to real-world violence could result in social
+cohesion in the virtual world. Increased social cohesion is thus potentially
+an indicator of increased social organization and mobilization on the ground.
 
@@
 
-Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
-Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests (Vicari, 2013).
-Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
-As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
+Social media platforms, such as Twitter, offer rapid real-time dissemination
+of information. Given its accessibility and proficiency as an information
+exchange tool, individuals involved in social movements have taken to them
+in conjunction, or in replacement, of real-world social mobilization.
+During the 2012 Italian protests for global economic change, the riots in
+Rome were mirrored by Twitter activity both on the same day and in the
+following days after the protests (Vicari, 2013). Tweeting was
+determined to be more effective locally in discussing real-world, real-time
+events than traditional mainstream media platforms. As more and more
+individuals rely on social media to obtain local news and information, it
+becomes increasingly important to understand just how these micro-blogs
+reflect real-world action.
 
@@
 
-Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
-Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
-This notion has been increasingly replaced by ideas from dynamical systems theory.
-Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts (Turvey, 2018).
-When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
-Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
-Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
-The primary methods used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and it's off-shoot, windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
-CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions (for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony (Paxton \& Dale, 2017).
-We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
+Traditional linear analyses have led to many notable discoveries in the
+domains of psychology and political science, but continuous data pose
+problems that are not easily overcome with these methods. Events have
+historically been conceptualized as linear chains of smaller, sequential
+events with one occurrence leading to the next. This notion has been
+increasingly replaced by ideas from dynamical systems theory. Rather than
+a chain of events, continuous data can be thought of as nested occurrences,
+where mutually constrained parts (e.g., citizens, governments, real-world
+events, social media platforms) are constantly interacting, leading to
+more global behaviors that are larger than the sum of the parts
+(Turvey, 2018). When analyzed as dynamical systems, many phenomena
+exhibit new nonlinear patterns that were formerly overlooked. Continuous
+data subject to linear analyses becomes flattened, and the variability
+that is fundamental to these systems and their evolution over time is
+ignored. Nonlinear methods provide means for capturing the rich temporal
+dynamics and variability that unfold in continuous data.
+
+The primary methods used in the current work is cross-recurrence
+quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot,
+windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
+CRQA has successfully been used to gain a better understanding of many
+complex human phenomena, such as human social interactions
+(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony
+(Paxton \& Dale, 2017). We argue that the use of nonlinear methods in
+the investigation of political science phenomena will lead to new insights
+and development of more robust theories.
 
@@
 
-Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
-We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
-Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
-This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
-Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) and windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
-We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
-We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
-Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
-As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
+Social media has become a primary platform for social movements and
+activism across the world, but the extent to which virtual activism
+reflects real-world mobilization is still largely unknown. We
+conceptualize the physical and virtual movements as a dynamical system,
+both constantly interacting and influencing the other. Both real- and
+virtual-world collective coordination were powerful tools in the events
+of Arab Spring, and are undeniably linked. This study aims to explore
+the dynamics of Syrian individuals who took to Twitter to raise
+awareness about the events of Arab Spring and bring about mass mobilization.
+Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998)
+and windowed cross-recurrence quantification analysis
+(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social
+cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts
+of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative
+events would show high levels of determinism, as this time period was
+marked by daily violence which often leads to increased salience. We also
+hypothesized that the count of positive events would not show patterns of
+determinism, as these events were likely overshadowed by the salient
+negative daily occurrences. Using WCRQA, we hoped to identify shifts in the
+dynamics of the systems that could then be linked to real world shifts in
+conflict frequency. As social cohesion has never been analyzed using
+nonlinear methods, the analyses contained herein are largely exploratory.
+The goal of this endeavor is to gain a better understanding of how events
+of different intensities during times of turmoil may enhance or deter
+social cohesion in social media communication, and how social mobilization
+may be evident in the dynamic coupling of cohesion and real-world events.
 
@@
 
-The corpus of tweets used included 697428 Syrian tweets occurring between March 30, 2012 and June 15, 2012.
-Using the Twitter streaming API, servers at the University of Texas at Austin collected the tweets.
-The servers were run on a stable (LTS) version of Ubuntu Linus, 10.04, and were connected directly to the high-bandwidth UT network maintained by IT services.
-Tweets collected contained one or more of the following keywords: \enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These keywords were chosen based on the most distinctive terms used in news articles covering the Arab Spring in Syria at the time.
-A node.js script was used to reinitialize the connection to Twitter's servers whenever the script timed out due to a period of silence.
-The script requested data from the API endpoint using basic HTTP authentication (OAuth was optional, at the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored the data directly to the local hard disk.
-The tweets were then post-processed with a Python script to convert the JSON-formatted tweets to tab-separated files and were then compressed to maximize storage efficiency.
+The corpus of tweets used included 697428 Syrian tweets
+occurring between March 30, 2012 and June 15, 2012. Using the Twitter
+streaming API, servers at the University of Texas at Austin collected
+the tweets. The servers were run on a stable (LTS) version of Ubuntu
+Linus, 10.04, and were connected directly to the high-bandwidth UT network
+maintained by IT services.
+
+Tweets collected contained one or more of the following keywords:
+\enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These
+keywords were chosen based on the most distinctive terms used in news
+articles covering the Arab Spring in Syria at the time. A node.js script
+was used to reinitialize the connection to Twitter's servers whenever the
+script timed out due to a period of silence. The script requested data from
+the API endpoint using basic HTTP authentication (OAuth was optional, at
+the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored
+the data directly to the local hard disk. The tweets were then post-processed
+with a Python script to convert the JSON-formatted tweets to tab-separated
+files and were then compressed to maximize storage efficiency.
+
 All scripts used for scrapping tweets and compressing data can be found at \url{https://github.com/chbrown/twilight}.
@@
 
-Event data were obtained from the 2012 Integrated Crisis Early Warning System (ICEWS; Boschee et al., 2015).
-The event data were first filtered to remove incomplete and incorrectly formatted data.
-They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
-To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
+Event data were obtained from the 2012 Integrated Crisis Early Warning
+System (ICEWS; Boschee et al., 2015). The event data were first filtered to
+remove incomplete and incorrectly formatted data. They were then filtered
+to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were
+filtered again to include events that were both directed at (i.e., target)
+or directed by (i.e., source) Syria (n = 7990).
 
@@
 
-The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words' frequencies in the entire tweet corpus.
-If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
-The tweets were first sorted into ascending order by timestamp.
-They were then grouped into successive sets of five tweets.
-Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
-1-3).
-This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
-Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
+The social cohesion or linguistic similarity of daily tweets was calculated
+by quantifying the frequency of shared content words with respect to those
+words' frequencies in the entire tweet corpus. If a linguistic term has a
+high frequency in one tweet but has a low frequency in the whole tweet
+corpus, then it is more likely a content word and is this given more weight
+in calculating social cohesion.
+
+The tweets were first sorted into ascending order by timestamp. They were
+then grouped into successive sets of five tweets. Inverse frequency
+weighting for the overlap words and all words was conducted for each pair
+of two tweets in the group of five, then divided to get the social cohesion
+score for that pair (see Eq. 1-3). This resulted in ten social cohesion
+values for each group of five tweets, which were then averaged. Finally,
+the mean of all average cohesion values for all groups was taken to get
+a social cohesion score for each day.
 
@@
 
-The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
-All hashtags and URLs were included in the analysis.
-This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see Jones (1972) and Robertson (2004).
+The social cohesion calculation was performed on a subset of the corpus
+containing (recalculate with new date span) English and (recalculate with
+new date span) Arabic tweets. All hashtags and URLs were included in the
+analysis. This method is similar to that of inverse document frequency (IDF).
+For more information on IDF, see Jones (1972) and
+Robertson (2004).
 
@@
 
-Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
-Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
-This well-validated coding scheme allows for numerical quantification of different event types.
-For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
-Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
-Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the
+Defense Advanced Research Project Agency, the daily events in Syria were
+scored with an intensity rating ranging from -10 to 10. Negative events,
+such as riots and attacks, are coded with low negative numbers while
+positive, peaceful events are coded with high positive numbers. This
+well-validated coding scheme allows for numerical quantification of
+different event types.
+
+For both the target only and the target and source data, time series of
+the count of all events were generated by summing the total number of events
+on each day, irrespective of ICEWS score. Similarly, time series of count
+of positive events were generated by summing the number of ICEWS events
+for each day that had an intensity rating greater than zero. Lastly,
+time series of count of negative events were generated by summing the number
+of ICEWS events for each day that had an intensity rating less than zero.
 
@@
 
-We first used cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
-As an extension of RQA, which captures the patterns of revisited states of a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992), CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
-Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
-In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
-We converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles (e.g., Figure \ref{fig:deciled-ts}) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
-In CRQA, a recurrent point is when two signals share the same state.
-These shared states can be at the same time or at later points in the time series.
+We first used cross-recurrence quantification analysis
+(CRQA; Zbilut et al., 1998) to investigate the temporal patterns of
+social cohesion and real-world events in Syria during Arab Spring. As
+an extension of RQA, which captures the patterns of revisited states of
+a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992), CRQA
+allows for two time series to be projected onto one another to investigate
+shared states and trajectories. Nonlinear analyses such as CRQA can reveal
+dynamics that are not captured by traditional linear methods.
+
+In order to perform CRQA, the time series need to be converted to the same
+scale, while still preserving a sampling rate that respects the native
+timescale of the system
+(cf.~Nyquist frequency in signal processing; Grenander, 1959).
+We converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles
+(e.g., Figure \ref{fig:deciled-ts}) to analyze the dynamics of different
+levels of social cohesion and counts of all, positive, and negative events
+on each day. In CRQA, a recurrent point is when two signals share the same
+state. These shared states can be at the same time or at later points in
+the time series.
 
@@
 
-A recurrence plot (RP) is the visual representation of CRQA.
-To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
-Visually analyzing these plots can help reveal patterns of structure and recurrence.
-The line y = x is known as the line of identity.
-This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
-See Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg} for examples of RPs.
+A recurrence plot (RP) is the visual representation of CRQA. To construct
+a recurrence plot, two time series are plotted against each other on the
+X and Y axes, and at every point where they share the same state, and point
+in placed on the plot to indicate recurrence. Visually analyzing these plots
+can help reveal patterns of structure and recurrence. The line y = x is known
+as the line of identity. This line falls where the time series match
+temporally, and a filled line would indicate perfect synchrony between the
+two time series. See
+Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}
+for examples of RPs.
 
@@
 
-The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
-This metrics gives a general description of how frequently the time series are sharing the same states.
-In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
+The percentage of recurrent points to total possible points is a metric
+called recurrence rate (RR). This metrics gives a general description of
+how frequently the time series are sharing the same states. In the current
+study, a recurrent point would indicate that the level of social cohesion
+and frequency of events were at the same intensity.
+
 Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
-The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
-For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
-The average length of the line structures is called mean line (L).
-This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
-The longest line length is called max line (maxL).
-maxL indicates the longest instance of being \enquote{stuck} in a particular state together.
-The total number of lines is called NRLINE.
-The more lines there are, the more coordinated the system may be.
-The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
-These entropy metrics help indicate the stability and predictability of the system.
-When one of the signals gets \enquote{stuck} in a state and the other moves on to other states, this results in vertical line structures.
-The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
-For more detail on CRQA metrics, see Coco and Dale (2018).
+These are conceptualized as shared trajectories, where the two time series
+are moving together across time in a shared state. The percentage of
+recurrent points that make up diagonal line structures (i.e., two or more
+consecutive points) is a metric called percent determinism (DET). For the
+current project, a high DET would indicate that not only are the levels of
+social cohesion and frequency of events occurring at similar intensities,
+but they are doing so across consecutive days.
+
+The average length of the line structures is called mean line (L). This can
+be conceptualized as the average amount of time that the two time series move
+together before one or both shift states. The longest line length is called
+max line (maxL). maxL indicates the longest instance of being \enquote{stuck} in a
+particular state together. The total number of lines is called NRLINE. The
+more lines there are, the more coordinated the system may be. The
+complexity or variability of line lengths is captured by a metric called
+entropy (ENTR) and entropy while accounting for the total number of lines in
+the plot is normalized entropy (rENTR). These entropy metrics help indicate
+the stability and predictability of the system. When one of the signals gets
+\enquote{stuck} in a state and the other moves on to other states, this results in
+vertical line structures. The proportion of points forming vertical line
+structures is a metric called laminarity (LAM) and the average length of the
+vertical trajectories is called trapping time (TT). For more detail on CRQA
+metrics, see Coco and Dale (2018).
 
@@
 
-To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
-Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
-No normalization was done, and lines were considered two or more consecutive recurrent points.
-The Theiler window was set to zero to include points along the line of identity.
-For more details on the CRQA parameters and how they impact the analysis, see Coco and Dale (2018).
+To conduct the analyses on the decile data, the parameters were set to those
+typically used in categorical CRQA. Delay was set to zero, embedding dimension
+was set to 1, and radius was set to .001 to allow for only exact recurrent
+matches. No normalization was done, and lines were considered two or more
+consecutive recurrent points. The Theiler window was set to zero to include
+points along the line of identity. For more details on the CRQA parameters and
+how they impact the analysis, see Coco and Dale (2018).
 
@@
 
-Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R (R Core Team, 2019), 1000 permuted time series were created for each of the real time series.
-A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
-CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
-This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
-Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
-Thus, RR is not included in the inferential tests.
-For more information on permutation tests, see Good (2013).
+Using the deciled, real time series of social cohesion, count of all events,
+count of positive events, and count of negative events, a permutation test was
+done to determine statistical difference from chance for each CRQA metric.
+Using the sample function in base R (R Core Team, 2019), 1000 permuted time series were
+created for each of the real time series. A permutation test is similar to
+bootstrapping, except that the sampling of observations is done without
+replacement. CRQA was then run 1000 times for social cohesion and count of all
+events, social cohesion and count of positive events, and social cohesion and
+count of negative events using the permuted time series. This resulted in
+1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles
+of the metrics from the permuted CRQ analyses. Given that a permutation test
+is similar to bootstrapping but does not include replacement, all points were
+included in each CRQA analysis, leaving RR the same across all analyses. Thus,
+RR is not included in the inferential tests. For more information on permutation
+tests, see Good (2013).
 
@@
 
-We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
-In this analysis, a smaller \enquote{window} of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
-The window remains the same size and \enquote{slides} diagonally up the line of identity.
-The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
+We used windowed cross-recurrence quantification analysis
+(WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the
+temporal dynamics of social cohesion and real-world events. In this analysis,
+a smaller \enquote{window} of time points is used to calculate CRQA and capture more
+fine-grain dynamics of two time series. The window remains the same size and
+\enquote{slides} diagonally up the line of identity. The changes in the CRQA metrics
+across the windows can reveal changes in dynamics that can then be linked to
+external, real-world events.
 
@@
 
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
-These metrics can then be plotted as a time series to visualize their evolution over time.
-For these analyses, we decided to visualize recurrence rate and determinism.
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
+respective window. These metrics can then be plotted as a time series to
+visualize their evolution over time. For these analyses, we decided to
+visualize recurrence rate and determinism.
 
@@
 
-In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
-First, a window size must be decided on.
-The window size will determine how many observations are used in each CRQA analysis.
-We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
-The second parameter to be chosen is a step size.
-Window step size is how far the window moves up the line of identity before conducting CRQA again.
-We chose 1 for the step size to understand how the metrics evolve from day to day.
-All other CRQA metrics remained the same as previously noted.
+In addition to the CRQA parameters, two other parameters are required when
+conducting WCRQA. First, a window size must be decided on. The window size
+will determine how many observations are used in each CRQA analysis. We
+conducted WCRQA with a window size of 14 to investigate the dynamics over
+two weeks and allow for the capture of more structure and thus a more
+meaningful interpretation of DET. The second parameter to be chosen is a
+step size. Window step size is how far the window moves up the line of identity
+before conducting CRQA again. We chose 1 for the step size to understand
+how the metrics evolve from day to day. All other CRQA metrics remained the
+same as previously noted.
 
@@
 
-To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
-This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
-These dynamics can then be linked to other external events.
-See Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all} for examples.
+To visualize WCRQA, the resulting metrics from each window can be plotted
+as a time series. This allows for visual interpretation of the pattern or
+fluctuation of the metrics across time. These dynamics can then be linked
+to other external events. See Figures \ref{fig:plot-wcrqa-targ-all} and
+\ref{fig:plot-wcrqa-source-targ-all} for examples.
 
@@
 
-To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
-Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
-The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
+To visualize the differences in the WCRQA metrics from those obtained by
+chance, a permutation test was done to set upper and lower bounds for the
+95th and 99th percentiles. Using a sample size of 14, one-thousand permuted
+time series were generated without replacement for each real time series. The
+upper and lower 95th and 99th percentiles were set based on the distribution
+of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 
-CRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
+CRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). We
+conducted a permutation test to check for statistical difference from chance
+for all analyses and metrics.
 
@@
 
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-all}; \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics other than TT (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, L, ENTR, LAM, and TT.
-All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all events
+found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
+All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-all};
+\autoref{table-1}). A permutation test for the CRQA of social cohesion and
+count of positive events found no statistical difference from chance for any
+of the metrics other than TT (Figure \ref{fig:plot-rp-targ-pos};
+\autoref{table-1}). A permutation test for the CRQA of social cohesion and
+count of negative events found a statistical difference from chance for DET,
+NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
+\ref{fig:plot-rp-targ-neg}; \autoref{table-1}). Looking at the recurrence
+plots there appears, to be a shift in dynamics around the 36th observation
+which corresponds to May 4th, 2012.
 
@@
 
-WCRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019).
-Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
-In the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all}), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
-The trend lines are plotted in blue.
+WCRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). Permutation tests
+were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
+the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all}),
+the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
+represented by horizontal orange lines. The trend lines are plotted in blue.
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 7th-12th and 36th-47th window (Figure \ref{fig:plot-wcrqa-targ-all}).
-Determinism is largely above chance from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}).
-For social cohesion and count of positive events there is a downward trend in RR as the window moves with largly above chance RR from the 1st-18th and 32nd-45th windows.
-Determinism was at or above chance for the 8th-17th, 32nd-34th, and the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
-For social cohesion and count of negative events, recurrence rate stays above or almost above chance from the 4th-7th and 43rd-47th windows, and determinism is above or nearly above chance in the 1st and 2nd windows, with short intermittent peaks in later windows (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of all events, there is a consistent period
+of above chance recurrence rate from the 7th-12th and 36th-47th window
+(Figure \ref{fig:plot-wcrqa-targ-all}). Determinism is largely above chance
+from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}). For
+social cohesion and count of positive events there is a downward trend in RR
+as the window moves with largly above chance RR from the 1st-18th and
+32nd-45th windows. Determinism was at or above chance for the 8th-17th,
+32nd-34th, and the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of negative events, recurrence rate stays above
+or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
+is above or nearly above chance in the 1st and 2nd windows, with short intermittent
+peaks in later windows (Figure \ref{fig:plot-wcrqa-targ-all}).
 
@@
 
-For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 7th-13th and 26th-47th windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-Determinism also shows above or nearly above chance values in windows 7th-17th and short, intermittent peaks between the 34th and 61st windows (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-For social cohesion and count of positive events, there is a downward trend in RR as the window moves with largely above chance values in the first 20 windows and the 32nd-45th windows.
-Determinism stays largely within chance with the exception of windows 13 through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-For social cohesion and negative events, there appears to be an extended time period where RR (32nd-47th windows) and DET (35th-39th windows) were above of nearly above chance (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-These windows span from May 3rd, 2012 to May 14th, 2012.
+For social cohesion and count of all events, there is a consistent period of
+above or nearly above chance determinism from the 7th-13th and 26th-47th
+windows (Figure \ref{fig:plot-wcrqa-source-targ-all}). Determinism also
+shows above or nearly above chance values in windows 7th-17th and short,
+intermittent peaks between the 34th and 61st windows (Figure
+\ref{fig:plot-wcrqa-source-targ-all}). For social cohesion and count of
+positive events, there is a downward trend in RR as the window moves with
+largely above chance values in the first 20 windows and the 32nd-45th windows.
+Determinism stays largely within chance with the exception of windows 13
+through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}). For social cohesion
+and negative events, there appears to be an extended time period where RR
+(32nd-47th windows) and DET (35th-39th windows) were above of nearly above
+chance (Figure \ref{fig:plot-wcrqa-source-targ-all}). These windows span from
+May 3rd, 2012 to May 14th, 2012.
 
@@
 
-In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
-We examined how social mobilization both virtually and physically evolve over time in tandem.
-Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
-Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
+In the present study, we investigated the dynamics of real-world events
+and online communication on Twitter in Syria during Arab Spring. We examined
+how social mobilization both virtually and physically evolve over time in
+tandem. Prior to now, the extent to which virtual mobilization on social
+media platforms such as Twitter has been largely unexplored. Using the
+nonlinear methods cross-recurrence quantification analysis and windowed
+cross-recurrence quantification analysis, we investigated the theory that
+virtual mobilization is increasingly reflective of real-world events
+during times of strife.
 
@@
 
-The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
-The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
-The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
-The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
+The significant result of DET for social cohesion and both the all events
+and negative events time series confirms our hypothesis, that increased
+salience of events is reflected in social cohesion on Twitter. The frequency
+of all events and of negative events thus result in a significant number
+of shared trajectories that are statistically different from chance. The
+non-significant results for all metrics for positive event count also
+confirm our hypothesis, and gives support to the theory that positive events
+are less coupled to social cohesion than the more salient, negative events
+during times of turmoil. The inevitable increased salience of event
+frequency and event violence thus leads to increased coupling with Twitter
+social cohesion.
 
@@
 
-By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
-These additional observations are times where Syria initiated an event with another country.
-Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
-The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
-Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
-Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
-The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs; Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
-To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
+By adding Syria as a source in the data filtering, the dataset increased
+in size by 1,690 samples. These additional observations are times where
+Syria initiated an event with another country. Events initiated by Syria
+but directed internally within the country were already captured by the
+target only filtering. The increase in coupling between positive events
+and social cohesion is thus due to the inclusion of these externally
+directed events. Though CRQA metrics for count of all and count of
+negative events with social cohesion were largely unaffected, count of
+positive events and social cohesion showed significant levels of
+determinism, number of lines, max line length, and laminarity that were
+not present in the target filtered data. Given that the Syria during
+this time was still under Authoritarian rule, the government may have
+been initiating more positive external events to prevent intervention
+by other countries or try to cover up what was happening internally.
+We believe that the increased coupling of positive events is thus not
+reflective of actual social cohesion, but happened by chance. The
+inflation of the number of positive events when including source
+observations is causing increased coupling, but it is more likely that
+the Twitter users were using the platform to raise awareness of the
+violent, internal events that were being inflicted on them by their
+government officials and armies and not reporting on the positive
+external events that did not directly affect them or their safety.
+Further research should explore the semantic content of this tweet
+corpus to determine what the socially cohered language was focused on.
+By visual inspection of the recurrence plots (RPs;
+Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}),
+there appears to be a shift in the dynamics of these systems around
+observation 35, or May 3rd, 2012. To further investigate these local
+dynamics, we performed a sliding window technique known as windowed
+cross-recurrence quantification analysis (WCRQA).
 
@@
 
-The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR and DET (Figure \ref{fig:plot-wcrqa-targ-all}).
-The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
-The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
-We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure \ref{fig:plot-mode-event}), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
-These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET was entirely within chance (Figure \ref{fig:plot-wcrqa-targ-all}).
-This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
+The time period of differing dynamics, from observation 38 through 43,
+appears to be captured by WCRQA of social cohesion and count of negative
+events for both RR and DET (Figure \ref{fig:plot-wcrqa-targ-all}). The
+amount of recurrence and determinism for these periods almost consistently
+lie above chance, suggesting that the intensity of negative events coincide
+with the degree of social cohesion found on Twitter, and that these states
+carry across multiple days in a way that is different from that of chance.
+
+The above-chance levels of determinism and recurrence rate are demonstrating
+the coupling of social cohesion and counts of all and negative events during
+times of strife. We can see this string of highly violent events reflected
+in the mode ICEWS event for each day (Figure \ref{fig:plot-mode-event}),
+where from May 1st, 2020 to May 15th, 2020, the most frequently occurring
+event was almost consistently -10, the most violent event in the coding
+system. These dates directly correlate with the above chance RR and DET
+metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during
+this time period, DET was entirely within chance (Figure
+\ref{fig:plot-wcrqa-targ-all}). This supports our hypothesis, as the
+positive events are seemingly not coupled with the social cohesion on Twitter
+during civil uprisings during the Arab Spring.
 
@@
 
-WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
-Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
-WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
-This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
-Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
+WCRQA of recurrence rate on the source and target filtered data remained
+largely the same for count of all events and social cohesion, suggesting
+that large numbers on a given day will be reflective of increased levels
+of social cohesion. Determinism showed more frequent above-chance metrics
+for windows 39 and up, suggesting that the inclusion of externally
+directed events lead to higher event counts during these days and then
+was more reflective of the level of social cohesion on Twitter. WCRQA for
+count of positive events and social cohesion remained largely the same for
+RR and DET as the source only data. This again seems to support the idea
+that these two aren't actually coupled, but rather that the inflation of
+the positive counts lead to a spurious relationship. Count of negative
+events and social cohesion also showed similar trends for RR and DET,
+again attesting to the theory that negative events were coupled to social
+cohesion on Twitter while positive events happened by chance.
 
@@
 
-Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
-If consistent across other civil wars, these results have serious implications for monitoring global movements.
-While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
-By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
-Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
+Considering the invasiveness of social media in our everyday lives, it is
+inevitable that individuals involved in real-world social mobilization have
+utilized these platforms to their advantage. If consistent across other civil
+wars, these results have serious implications for monitoring global
+movements. While traditional media in regions of authoritarian rule are
+often biased, the self-organized nature of Twitter poses a new avenue to gain
+insight into truths about up-risings and social mobilization. By
+conceptualizing Twitter and real-world events as two components of an
+inextricably linked dynamical system, the levels of social cohesion within the
+virtual platform could be monitored for fluctuations indicating global shifts
+in power and peace. Social media mobilization can thus help alert us to
+real-world mobilization not communicated in mainstream media and allow for
+faster intervention.
 
@@
 
-\begin{verbatim}
-## Warning in readLines(x, encoding = "UTF-8"): incomplete final line found on
-## 'appendix.Rmd'
-\end{verbatim}
-
-\clearpage
-\makeatletter
-\efloat@restorefloats
-\makeatother
-
-\begin{appendix}
-\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
-\section{CRQA for Phoenix data in
-sextiles}\label{crqa-for-phoenix-data-in-sextiles}}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only Phoenix data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 31.065 & 0.241 & & 38.955 & 0.000 & *** & 31.854 & 0.139
-&\tabularnewline
-NRLINE & 144.000 & 0.229 & & 174.000 & 0.000 & *** & 148.000 & 0.105
-&\tabularnewline
-maxL & 4.000 & 0.421 & & 5.000 & 0.087 & . & 4.000 & 0.452
-&\tabularnewline
-L & 2.188 & 0.544 & & 2.270 & 0.039 & * & 2.182 & 0.580 &\tabularnewline
-ENTR & 0.513 & 0.526 & & 0.650 & 0.033 & * & 0.504 & 0.550
-&\tabularnewline
-rENTR & 0.467 & 0.290 & & 0.469 & 0.276 & & 0.459 & 0.310
-&\tabularnewline
-LAM & 32.051 & 0.284 & & 46.154 & 0.008 & ** & 30.769 & 0.314
-&\tabularnewline
-TT & 2.273 & 0.196 & & 2.400 & 0.072 & . & 2.400 & 0.063 &
-.\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target Phoenix
-data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 31.558 & 0.178 & & 37.377 & 0.000 & *** & 25.740 & 0.988
-&\tabularnewline
-NRLINE & 145.000 & 0.189 & & 169.000 & 0.000 & *** & 119.000 & 0.989
-&\tabularnewline
-maxL & 4.000 & 0.467 & & 5.000 & 0.084 & . & 4.000 & 0.454
-&\tabularnewline
-L & 2.207 & 0.368 & & 2.243 & 0.123 & & 2.193 & 0.509 &\tabularnewline
-ENTR & 0.547 & 0.343 & & 0.610 & 0.104 & & 0.521 & 0.492
-&\tabularnewline
-rENTR & 0.498 & 0.135 & & 0.440 & 0.432 & & 0.474 & 0.244
-&\tabularnewline
-LAM & 38.462 & 0.073 & . & 48.718 & 0.000 & *** & 21.795 & 0.790
-&\tabularnewline
-TT & 2.500 & 0.017 & * & 2.235 & 0.280 & & 2.429 & 0.048 &
-*\tabularnewline
-\bottomrule
-\end{longtable}
-
-CRQ analyses for sextiled Phoenix event data found increased levels of
-coupling between positive events and social cohesion, irrespective of
-target or source and target filtering. Negative events were not coupled
-with social cohesion irrespective of filtering.
-
-\hypertarget{crqa-for-icews-data-in-sextiles}{%
-\section{CRQA for ICEWS data in
-sextiles}\label{crqa-for-icews-data-in-sextiles}}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for target only ICEWS data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 39.250 & 0.000 & *** & 37.870 & 0.000 & *** & 38.659 & 0.000 &
-***\tabularnewline
-NRLINE & 177.000 & 0.000 & *** & 169.000 & 0.000 & *** & 170.000 & 0.000
-& ***\tabularnewline
-maxL & 5.000 & 0.093 & . & 5.000 & 0.081 & . & 5.000 & 0.087 &
-.\tabularnewline
-L & 2.249 & 0.089 & . & 2.272 & 0.033 & * & 2.306 & 0.009 &
-**\tabularnewline
-ENTR & 0.619 & 0.074 & . & 0.653 & 0.030 & * & 0.705 & 0.008 &
-**\tabularnewline
-rENTR & 0.447 & 0.368 & & 0.471 & 0.261 & & 0.509 & 0.118
-&\tabularnewline
-LAM & 43.590 & 0.013 & * & 39.744 & 0.047 & * & 42.308 & 0.030 &
-*\tabularnewline
-TT & 2.267 & 0.208 & & 2.385 & 0.065 & . & 2.357 & 0.092 &
-.\tabularnewline
-\bottomrule
-\end{longtable}
-
-\begin{longtable}[]{@{}cccccccccc@{}}
-\caption{CRQA results for source and target ICEWS data.}\tabularnewline
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endfirsthead
-\toprule
-metric & all events & p & sig. & positive events & p & sig. & negative
-events & p & sig.\tabularnewline
-\midrule
-\endhead
-DET & 34.122 & 0.014 & * & 37.771 & 0.000 & *** & 39.448 & 0.000 &
-***\tabularnewline
-NRLINE & 152.000 & 0.064 & . & 168.000 & 0.000 & *** & 173.000 & 0.000 &
-***\tabularnewline
-maxL & 5.000 & 0.092 & . & 5.000 & 0.093 & . & 7.000 & 0.002 &
-**\tabularnewline
-L & 2.276 & 0.030 & * & 2.280 & 0.024 & * & 2.312 & 0.003 &
-**\tabularnewline
-ENTR & 0.663 & 0.022 & * & 0.661 & 0.022 & * & 0.698 & 0.005 &
-**\tabularnewline
-rENTR & 0.478 & 0.211 & & 0.477 & 0.242 & & 0.434 & 0.475
-&\tabularnewline
-LAM & 34.615 & 0.178 & & 39.744 & 0.047 & * & 48.718 & 0.002 &
-**\tabularnewline
-TT & 2.250 & 0.233 & & 2.385 & 0.067 & . & 2.235 & 0.295
-&\tabularnewline
-\bottomrule
-\end{longtable}
-
-CRQ analyses for sextiled ICEWS event data found coupling between both
-positive and negative events with social cohesion, irrespective of
-target or source and target filtering. Negative events were more
-strongly coupled with social cohesion than positive events for the
-target only analyses. The absence of coupling between negative events
-and social cohesion in the Phoenix CRQ analyses speaks to the
-unreliability of event data, and that nonlinear analyses in general are
-only as valuable as the quality of the data being used.
-
-\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
-\section{Windowed CRQA for Phoenix data in
-sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/phoenix/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-phoenix-wcrqa-source-targ-all}
-\end{figure}
-
-\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
-\section{Windowed CRQA for ICEWS data in
-sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth,angle=90]{./results/secondary/icews/windowed-crqa/source_target-windowed_all} \caption{Windowed CRQA for social cohesion and event counts from target filtered data.}\label{fig:plot-secondary-icews-wcrqa-source-targ-all}
-\end{figure}
-\end{appendix}
-
 \end{document}

### 2020-05-29 manuscript.Rmd
Edits to Method and added references

@@
 The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
-occurring between March 30, 2012 and June 15, 2012. Using the Twitter
+occurring between March 30--June 15, 2012. Using the Twitter
 streaming API, servers at the University of Texas at Austin collected
 the tweets. The servers were run on a stable (LTS) version of Ubuntu
-Linus, 10.04, and were connected directly to the high-bandwidth UT network
+Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
 maintained by IT services.
@@
 with a Python script to convert the JSON-formatted tweets to tab-separated
-files and were then compressed to maximize storage efficiency.
+files, which were then compressed to maximize storage efficiency.
 
@@
 remove incomplete and incorrectly formatted data. They were then filtered
-to include only events that were directed (i.e., target) at Syria (n = 6300).
+to include only events that were directed at (i.e., `target`) Syria ($n = 6300$).
 To explore the impact of outwardly directed Syrian events, the data were
-filtered again to include events that were both directed at (i.e., target)
-or directed by (i.e., source) Syria (n = 7990).
+filtered again to include events that were both directed at (i.e., `target`)
+or directed by (i.e., `source`) Syria ($n = 7990$).
 

### 2020-05-29 manuscript.tex
Bring tex file up to date

@@
     \setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\usepackage{hyperref}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
   pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
+  pdflang={en-EN},
   pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage{longtable,booktabs}
-% Fix footnotes in tables (requires footnote package)
-\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx,grffile}
@@
 \usepackage{float}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[shorthands=off,main=english]{babel}
-\else
-  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
+\ifxetex
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
+\else
+  \usepackage[shorthands=off,main=english]{babel}
 \fi
@@
 rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death, the
-long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the
-country. The events of Tunisia rapidly spread to surrounding countries that
-were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya,
-and Syria. These mass movements would not have been possible without
-efficient interpersonal coordination, both physically and virtually on social
-media platforms, such as Twitter. The events of Arab Spring have been
+as a catalyst for the Tunisian Revolution, and one week after his death,
+Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
+country. The events of Tunisia rapidly spread to surrounding countries
+also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
+and Syria.
+
+These mass movements would not have been possible without
+efficient large-scale coordination, both physically and virtually on social
+media platforms. Along with Facebook, Twitter has been credited as essential
+to the Arab Spring---both for protesters (as a means to coordinate with one
+another and to communicate with the world) and for the government response
+(to monitor and track protestors to crack down on dissent) (Comninos, 2011).
+The events of Arab Spring have been
 thoroughly discussed within the political science literature
-(e.g., Lutterbeck, 2013; Koehler, 2017) but to our knowledge,
-the use of Twitter by Syrian citizens has not been investigated.
+(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
+the direct coupling between Syrian Twitter use and international action
+has not been investigated.
 
-\hypertarget{social-cohesion}{%
-\subsection{Social Cohesion}\label{social-cohesion}}
+\hypertarget{social-cohesion-and-social-mobilization}{%
+\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}
 
@@
 to act in ways that would not have on their own. Being overcome with this
-feeling is known to lead to violence (Collins, 2009; Spaaij, 2014).
-While feelings of social connection may lead to violence, increased exposure
-to violence can result in feelings of social cohesion. Gilligan, Pasquale, and Samii (2014)
+feeling can lead to violence (Collins, 2009; Spaaij, 2014).
+Conversely, increased exposure
+to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
 found that exposure to fatal wartime violence resulted in increased prosocial
 motivations, including cooperative behaviors, feelings of trust, and overall
-community-level social cohesion. Just as real-world social cohesion can be
-quantified, the same is true for online cohesion. Strategic communication on
-social media in the form of social cohesion of language can lead to real-world
-social change, and exposure to real-world violence could result in social
+community-level social cohesion.
+
+Just as real-world social cohesion can be
+quantified, so can online cohesion. While this can be quantified in many ways,
+one kind of cohesion can be found in the similarity in language use on social media.
+This implicit or explicit similarity in language use can indicate shared
+beliefs, thoughts, and feelings, as has been studied in research on language style
+in psycholinguistics and social psychology
+(Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010);
+although previous work on language style
+has often focused on individuals and small groups, this can be scaled up to examine
+massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
+This kind of massive online social cohesion can lead to real-world
+social change.
+
+Combining these separate threads, it is reasonable to expect that real-world actions
+and online social interactions would be enmeshed, driving and being driven by
+one another. Rather than expecting that only real-world social cohesion would be
+driven by real-world action, we would expect interaction between real-world and
+virtual dynamics: In this case, exposure to real-world violence could result in social
 cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator of increased social organization and mobilization on the ground.
+an indicator and a result of increased social organization and mobilization
+on the ground.
 
-\hypertarget{social-media-as-a-platform-for-mobilization}{%
-\subsection{Social Media as a Platform for Mobilization}\label{social-media-as-a-platform-for-mobilization}}
-
-Social media platforms, such as Twitter, offer rapid real-time dissemination
-of information. Given its accessibility and proficiency as an information
-exchange tool, individuals involved in social movements have taken to them
-in conjunction, or in replacement, of real-world social mobilization.
-During the 2012 Italian protests for global economic change, the riots in
-Rome were mirrored by Twitter activity both on the same day and in the
-following days after the protests (Vicari, 2013). Tweeting was
+Social media platforms provide one way of enabling this kind of online social
+cohesion by offering distributed information-gathering and real-time information
+dissemination. Given its accessibility and proficiency as an information
+exchange tool, Twitter has provided individuals involved in social movements
+an opportunity to complement or even replace real-world social mobilization.
+For example, during the 2012 Italian protests for global economic change, the riots in
+Rome were mirrored by Twitter activity both on the day of the protests and in the
+days following them (Vicari, 2013). Tweeting was
 determined to be more effective locally in discussing real-world, real-time
@@
 
-\hypertarget{use-of-nonlinear-methods-in-naturally-occurring-data}{%
-\subsection{Use of Nonlinear Methods in Naturally Occurring Data}\label{use-of-nonlinear-methods-in-naturally-occurring-data}}
+\hypertarget{using-nonlinear-methods-to-capture-complex-relationships}{%
+\subsection{Using Nonlinear Methods to Capture Complex Relationships}\label{using-nonlinear-methods-to-capture-complex-relationships}}
 
+Given the hypothesized interrelationship between the real-world
+and online actions---and the notorious messiness of naturally occurring
+data---it is critical to find appropriate analysis tools that can
+identify the complex interconnections.
 Traditional linear analyses have led to many notable discoveries in the
-domains of psychology and political science, but continuous data pose
+domains of psychology and political science, but time series data pose
 problems that are not easily overcome with these methods. Events have
 historically been conceptualized as linear chains of smaller, sequential
-events with one occurrence leading to the next. This notion has been
+events with one occurrence leading to the next.
+Certain kinds of data are relatively well-suited to these analyses,
+but messy, complex, variable data from real-world events can pose
+challenges from overpowered samples to violation of underlying
+statistical assumptions (Paxton \& Griffiths, 2017).
+
+At the same time, the foundational theoretical assumptions of a
+linear world has been
 increasingly replaced by ideas from dynamical systems theory. Rather than
-a chain of events, continuous data can be thought of as nested occurrences,
+a chain of events, time series data can be thought of as nested occurrences,
 where mutually constrained parts (e.g., citizens, governments, real-world
@@
 more global behaviors that are larger than the sum of the parts
-(Turvey, 2018). When analyzed as dynamical systems, many phenomena
-exhibit new nonlinear patterns that were formerly overlooked. Continuous
-data subject to linear analyses becomes flattened, and the variability
-that is fundamental to these systems and their evolution over time is
-ignored. Nonlinear methods provide means for capturing the rich temporal
-dynamics and variability that unfold in continuous data.
+(Turvey, 2018). Linear analyses flatten these nonlinear patterns in
+time series data and ignore the variability
+that is fundamental to these systems and their evolution over time.
+However, when analyzed as dynamical systems, many phenomena
+exhibit new nonlinear patterns that were formerly overlooked.
+Nonlinear methods provide means for capturing the rich temporal
+dynamics and variability that unfold in time series data.
 
-The primary methods used in the current work is cross-recurrence
+Although a number of other nonlinear methods exist,
+the primary nonlinear method used in the current work is cross-recurrence
 quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot,
@@
 CRQA has successfully been used to gain a better understanding of many
-complex human phenomena, such as human social interactions
-(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014) and interpersonal synchrony
-(Paxton \& Dale, 2017). We argue that the use of nonlinear methods in
+complex human phenomena, including a variety of human social interactions
+(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014).
+Much as it has for psychology, we argue that the use of nonlinear methods in
 the investigation of political science phenomena will lead to new insights
-and development of more robust theories.
+and the development of more robust theories.
 
@@
 activism across the world, but the extent to which virtual activism
-reflects real-world mobilization is still largely unknown. We
+reflects and drives real-world mobilization is still largely unknown.
+In the current work, we
 conceptualize the physical and virtual movements as a dynamical system,
-both constantly interacting and influencing the other. Both real- and
+both constantly interacting and influencing the other. We aim to study
+this by analyzing the real-world events and online social cohesion
+during nearly three months of the Arab Spring. Both real- and
 virtual-world collective coordination were powerful tools in the events
-of Arab Spring, and are undeniably linked. This study aims to explore
-the dynamics of Syrian individuals who took to Twitter to raise
-awareness about the events of Arab Spring and bring about mass mobilization.
+of the Arab Spring and are undeniably linked. This study aims to explore
+the dynamics of Syrian Twitter users, who used the social media platform to raise
+awareness about the Arab Spring and bring about mass mobilization.
+
 Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998)
 and windowed cross-recurrence quantification analysis
-(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the dynamics of social
-cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts
-of all, positive, and negative real-world events on those respective days.
+(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the co-evolution of social
+cohesion online and real-world events. Specifically, using heterogeneous
+data from March 30, 2012, to June 15, 2012, we compared the social cohesion
+of Syrian tweets with the counts
+of all, positive, and negative real-world events.
+
 We hypothesized that the count of all events and the count of negative
@@
 determinism, as these events were likely overshadowed by the salient
-negative daily occurrences. Using WCRQA, we hoped to identify shifts in the
-dynamics of the systems that could then be linked to real world shifts in
-conflict frequency. As social cohesion has never been analyzed using
-nonlinear methods, the analyses contained herein are largely exploratory.
-The goal of this endeavor is to gain a better understanding of how events
-of different intensities during times of turmoil may enhance or deter
-social cohesion in social media communication, and how social mobilization
+negative daily occurrences.
+After testing these hypotheses, we then conducted exploratory analyses
+to further examine the patterns identified with CRQA. Using WCRQA,
+we sought to identify shifts in the
+dynamics of the systems that could then be linked to real-world shifts in
+conflict frequency.
+Through these analyses, our primary goal in the current work was to uncover
+(1) how different intensities during times of turmoil may enhance or deter
+social cohesion in social media communication and (2) how social mobilization
 may be evident in the dynamic coupling of cohesion and real-world events.
+
+An additional focus of the current work is to introduce cross-recurrence
+quantification analysis---a longstanding method from physics that has
+since become influential in a variety of other fields---to political
+science. We do so by providing detailed descriptions of the methods and
+providing clear directions about interpretation and significance testing
+even with relatively small-\emph{n} or case studies. After demonstrating these
+methods' utility with this dataset, we close the paper with specific
+suggestions to political scientists interested in incorporating these
+methods into their work.
 
@@
 The corpus of tweets used included 697428 Syrian tweets
-occurring between March 30, 2012 and June 15, 2012. Using the Twitter
+occurring between March 30--June 15, 2012. Using the Twitter
 streaming API, servers at the University of Texas at Austin collected
 the tweets. The servers were run on a stable (LTS) version of Ubuntu
-Linus, 10.04, and were connected directly to the high-bandwidth UT network
+Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
 maintained by IT services.
@@
 remove incomplete and incorrectly formatted data. They were then filtered
-to include only events that were directed (i.e., target) at Syria (n = 6300).
+to include only events that were directed at (i.e., \texttt{target}) Syria (\(n = 6300\)).
 To explore the impact of outwardly directed Syrian events, the data were
-filtered again to include events that were both directed at (i.e., target)
-or directed by (i.e., source) Syria (n = 7990).
+filtered again to include events that were both directed at (i.e., \texttt{target})
+or directed by (i.e., \texttt{source}) Syria (\(n = 7990\)).
 
@@
 \endhead
-DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
-NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
-maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
-L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
-ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
-rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
-LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
-TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
+DET & 25.246 & 0.001 & *** & 21.803 & 0.074 & . & 22.623 & 0.023 & *\tabularnewline
+NRLINE & 75.000 & 0.000 & *** & 61.000 & 0.121 & & 64.000 & 0.038 & *\tabularnewline
+maxL & 3.000 & 0.423 & & 4.000 & 0.037 & * & 3.000 & 0.370 &\tabularnewline
+L & 2.053 & 0.911 & & 2.180 & 0.079 & . & 2.156 & 0.155 &\tabularnewline
+ENTR & 0.208 & 0.901 & & 0.499 & 0.064 & . & 0.433 & 0.165 &\tabularnewline
+rENTR & 0.300 & 0.802 & & 0.455 & 0.305 & & 0.625 & 0.032 & *\tabularnewline
+LAM & 34.262 & 0.003 & ** & 30.328 & 0.016 & * & 24.098 & 0.113 &\tabularnewline
+TT & 2.247 & 0.107 & & 2.176 & 0.165 & & 2.100 & 0.360 &\tabularnewline
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-brennan1996conceptual}{}%
+Brennan, S. E., \& Clark, H. H. (1996). Conceptual pacts and lexical choice in conversation. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}(6), 1482.
+
 \leavevmode\hypertarget{ref-R-crqa}{}%
@@
 Collins, R. (2009). \emph{Violence: A micro-sociological theory}. Princeton University Press.
+
+\leavevmode\hypertarget{ref-comninos2011twitter}{}%
+Comninos, A. (2011). \emph{Twitter revolutions and cyber crackdowns}. Association for Progressive Communications.
 
@@
 
+\leavevmode\hypertarget{ref-fusaroli2015timescales}{}%
+Fusaroli, R., Perlman, M., Mislove, A., Paxton, A., Matlock, T., \& Dale, R. (2015). Timescales of massive human entrainment. \emph{PloS ONE}, \emph{10}(4).
+
 \leavevmode\hypertarget{ref-gilligan2014civil}{}%
 Gilligan, M. J., Pasquale, B. J., \& Samii, C. (2014). Civil war and social cohesion: Lab-in-the-field evidence from nepal. \emph{American Journal of Political Science}, \emph{58}(3), 604--619.
+
+\leavevmode\hypertarget{ref-gonzales2010language}{}%
+Gonzales, A. L., Hancock, J. T., \& Pennebaker, J. W. (2010). Language style matching as a predictor of social dynamics in small groups. \emph{Communication Research}, \emph{37}(1), 3--19.
 
@@
 
-\leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
-Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.
+\leavevmode\hypertarget{ref-michel2011quantitative}{}%
+Michel, J.-B., Shen, Y.
+K., Aiden, A.
+P., Veres, A., Gray, M.
+K., Pickett, J.
+P., \ldots{} others.
+(2011).
+Quantitative analysis of culture using millions of digitized books.
+\emph{Science}, \emph{331}(6014), 176--182.
+
+\leavevmode\hypertarget{ref-paxton2017finding}{}%
+Paxton, A., \& Griffiths, T.
+L.
+(2017).
+Finding the traces of behavioral and cognitive processes in big data and naturally occurring datasets.
+\emph{Behavior Research Methods}, \emph{49}(5), 1630--1638.
 
@@
 Spaaij, R. (2014). Sports crowd violence: An interdisciplinary synthesis. \emph{Aggression and Violent Behavior}, \emph{19}(2), 146--155.
+
+\leavevmode\hypertarget{ref-tausczik2010psychological}{}%
+Tausczik, Y. R., \& Pennebaker, J. W. (2010). The psychological meaning of words: LIWC and computerized text analysis methods. \emph{Journal of Language and Social Psychology}, \emph{29}(1), 24--54.
 

### 2020-05-29 manuscript.Rmd
Edits to Method section

@@
 high frequency in one tweet but has a low frequency in the whole tweet
-corpus, then it is more likely a content word and is this given more weight
+corpus, then it is more likely a content word and is thus given more weight
 in calculating social cohesion. 
+This method is similar to inverse document frequency (IDF).
+For more information on IDF, see @jones1972statistical and
+@robertson2004understanding.
 
@@
 score for that pair (see Eq. 1-3). This resulted in ten social cohesion
-values for each group of five tweets, which were then averaged. Finally,
+values for each group of five tweets; these values were then averaged to get
+a social cohesion score for the entire set of five tweets. Finally,
 the mean of all average cohesion values for all groups was taken to get
@@
 
-The social cohesion calculation was performed on a subset of the corpus
+The social cohesion calculation was performed on the tweet corpus
 containing (recalculate with new date span) English and (recalculate with
 new date span) Arabic tweets. All hashtags and URLs were included in the
-analysis. This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see @jones1972statistical and
-@robertson2004understanding.
+analysis.
 
@@
 Using the Integrated Crisis Early Warning System (ICEWS) developed at the
-Defense Advanced Research Project Agency, the daily events in Syria were
-scored with an intensity rating ranging from -10 to 10. Negative events,
-such as riots and attacks, are coded with low negative numbers while
-positive, peaceful events are coded with high positive numbers. This
+Defense Advanced Research Project Agency, the daily events were
+scored with an intensity rating ranging from -10 to 10. Negative 
+events---such as riots and attacks---are coded with low negative numbers, while
+positive or peaceful events are coded with high positive numbers. This
 well-validated coding scheme allows for numerical quantification of
@@
 
-For both the target only and the target and source data, time series of
+For both the target only and the target and source data described above, time series of
 the count of all events were generated by summing the total number of events
@@
 [CRQA; @zbilut1998detecting] to investigate the temporal patterns of
-social cohesion and real-world events in Syria during Arab Spring. As
-an extension of RQA, which captures the patterns of revisited states of
-a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA
+social cohesion and real-world events in Syria during Arab Spring. CRQA
+is an extension of RQA, which captures the patterns of revisited states of
+a single time series [@zbilut1992embeddings; @webber1994dynamical]. CRQA
 allows for two time series to be projected onto one another to investigate
-shared states and trajectories. Nonlinear analyses such as CRQA can reveal
-dynamics that are not captured by traditional linear methods.
+shared states and trajectories.
+In CRQA, we track these shared states by identifying *recurrent points*,
+or intersections of time during which two signals shared or revisited the same
+state. These shared states can be at the same time or at later points in
+the time series. We can further chart shared trajectories by examining
+the occurrences and patterns of multiple sequential recurrent points.
 
-In order to perform CRQA, the time series need to be converted to the same
+To perform CRQA, the time series must be converted to the same
 scale, while still preserving a sampling rate that respects the native
@@
 [cf. Nyquist frequency in signal processing; @grenander1959probability].
-We converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
-(e.g., Figure \@ref(fig:deciled-ts)) to analyze the dynamics of different
+Because the social cohesion and event data have different scales and values,
+we converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
+(e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
 levels of social cohesion and counts of all, positive, and negative events
-on each day. In CRQA, a recurrent point is when two signals share the same
-state. These shared states can be at the same time or at later points in
-the time series.
+on each day.
 
 #### Visualization
-A recurrence plot (RP) is the visual representation of CRQA. To construct
-a recurrence plot, two time series are plotted against each other on the
-X and Y axes, and at every point where they share the same state, and point
-in placed on the plot to indicate recurrence. Visually analyzing these plots
-can help reveal patterns of structure and recurrence. The line y = x is known
-as the line of identity. This line falls where the time series match
-temporally, and a filled line would indicate perfect synchrony between the
+A cross-recurrence plot (CRP) is the visual representation of CRQA. To construct
+a cross-recurrence plot, two time series are plotted against each other on the
+$x$ and $y$ axes. At every point where they share the same state, a point
+in placed on the plot to indicate recurrence. (For categorical CRQA, this process
+is similar to the Cartesian product.)
+
+We can visually analyze these plots
+to reveal patterns of structure and recurrence. The line $y = x$ is known
+as the *line of identity*. This line falls where the time series match
+temporally. A filled line would indicate perfect in-phase synchrony between the
 two time series. See
@@
 #### Metrics
+While visual inspections can be informative, we can derive a variety of 
+quantitative metrics from the cross-recurrence plot. Each of these metrics
+provides information into the pattern and dynamics of the new shared system
+between the original time series. These metrics are also critical for inferential
+statistics. We will focus most directly on two of these metrics: 
+*recurrence rate* and *determinism*.
+
 The percentage of recurrent points to total possible points is a metric
-called recurrence rate (RR). This metrics gives a general description of
+called the *recurrence rate* (*RR*). This metrics gives a general description of
 how frequently the time series are sharing the same states. In the current
@@
 are moving together across time in a shared state. The percentage of
-recurrent points that make up diagonal line structures (i.e., two or more
-consecutive points) is a metric called percent determinism (DET). For the
+recurrent points on the plot that fall along diagonal line structures 
+(i.e., two or more
+consecutive points) is a metric called *percent determinism* 
+(or simply *determinism*; *DET*). For the
 current project, a high DET would indicate that not only are the levels of
@@
 
-The average length of the line structures is called mean line (L). This can
+A number of other metrics provide insight not only into the amount of structure
+between the systems but about the nature of this shared structure.
+The average length of the line structures is called *mean line* (L), which can
 be conceptualized as the average amount of time that the two time series move
 together before one or both shift states. The longest line length is called
-max line (maxL). maxL indicates the longest instance of being “stuck” in a
-particular state together. The total number of lines is called NRLINE. The
-more lines there are, the more coordinated the system may be. The
+*max line* (*maxL*); it indicates the longest instance of being “stuck” in a
+particular state together. The total *number of lines* on the plot (*NRLINE*) 
+scales with structure: The more lines that exist, the more coupled the systems are. The
 complexity or variability of line lengths is captured by a metric called
-entropy (ENTR) and entropy while accounting for the total number of lines in
-the plot is normalized entropy (rENTR). These entropy metrics help indicate
+*entropy* (*ENTR*)---which may also be normalized by the total number of lines
+(i.e., *normalized entropy*; *rENTR*)---and indicates
 the stability and predictability of the system. When one of the signals gets
 “stuck” in a state and the other moves on to other states, this results in
-vertical line structures. The proportion of points forming vertical line
-structures is a metric called laminarity (LAM) and the average length of the
-vertical trajectories is called trapping time (TT). For more detail on CRQA
-metrics, see @R-crqa.
+vertical line structures, which are quantified in *laminarity* (*LAM*;
+i.e., the proportion of points forming vertical line structures) 
+and trapping time (*TT*; i.e., the average length of the
+vertical trajectories). For more detail on CRQA metrics, see @R-crqa.
 
@@
 To conduct the analyses on the decile data, the parameters were set to those
-typically used in categorical CRQA. Delay was set to zero, embedding dimension
-was set to 1, and radius was set to .001 to allow for only exact recurrent
+typically used in categorical CRQA: Delay was set to $0$, embedding dimension
+was set to $1$, and radius was set to $.001$ to allow for only exact recurrent
 matches. No normalization was done, and lines were considered two or more
-consecutive recurrent points. The Theiler window was set to zero to include
+consecutive recurrent points. The Theiler window was set to $0$ to include
 points along the line of identity. For more details on the CRQA parameters and
@@
 #### Permutation Test
-Using the deciled, real time series of social cohesion, count of all events,
-count of positive events, and count of negative events, a permutation test was
-done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R [@R-base], 1000 permuted time series were
-created for each of the real time series. A permutation test is similar to
+Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not have
+inherently meaningful values. As a result, CRQA is best used as a relative
+metric---that is, comparing the CRQA values across conditions or subsets
+of the data. Typically, meaningful differences between values are determined with
+traditional inferential statistics. While this may not be a problem for 
+experimentally derived datasets, it can pose a barrier to researchers using
+small-$n$ data or conducting data-informed case studies.
+
+For CRQA, this can be addressed using *permutation tests*.
+Similar to more established methods of statistical significance in CRQA research
+[which create surrogate time series; e.g., @paxton2017interpersonal],
+the permutation test approach to significance testing allows the researcher
+to use a time series as its own baseline by testing whether the *structure*
+of the unfolding events of the time series---rather than the *raw frequency* of the 
+events within the time series---cohere together more than would be expected
+by chance. A permutation test is similar to
 bootstrapping, except that the sampling of observations is done without
-replacement. CRQA was then run 1000 times for social cohesion and count of all
+replacement. In this approach, we simply create a large number of permutations
+of the original time series (i.e., breaking up the dependency across time points but
+preserving the frequencies of the events), conduct CRQA for each of those
+permutations, and then examine whether the real time series' CRQA metrics
+exceed those that we would expect to see by chance. The proportion of times that
+the real time series' values exceeds the surrogate time series' values can
+be interpreted as the alpha criterion to determine significance. 
+For more information on permutation
+tests, see @good2013permutation.
+
+Using the real deciles of social cohesion, count of all events,
+count of positive events, and count of negative events, we conducted a series
+of permutation tests 
+(one for the comparison between social cohesion and each type of event count)
+to determine statistical difference from chance for each CRQA metric.
+Using the `sample` function in base R [@R-base], $1000$ permuted time series were
+created for each of the real time series.  
+CRQA was then run $1000$ times for social cohesion and count of all
 events, social cohesion and count of positive events, and social cohesion and
 count of negative events using the permuted time series. This resulted in
-1000 results for each of the CRQA metrics for each combination of time series.
+$1000$ results for each of the CRQA metrics for each combination of time series.
 Statistical significance from chance was set at the 95th and 99th percentiles
@@
 is similar to bootstrapping but does not include replacement, all points were
-included in each CRQA analysis, leaving RR the same across all analyses. Thus,
-RR is not included in the inferential tests. For more information on permutation
-tests, see @good2013permutation.
+included in each CRQA analysis, leaving RR constant across all permutations. Thus,
+RR is not included in the inferential tests.
 
@@
 a smaller “window” of time points is used to calculate CRQA and capture more
-fine-grain dynamics of two time series. The window remains the same size and
+fine-grained dynamics of two time series. The window remains the same size and
 “slides” diagonally up the line of identity. The changes in the CRQA metrics
@@
 visualize their evolution over time. For these analyses, we decided to
-visualize recurrence rate and determinism.
+focus on recurrence rate and determinism.
 
@@
 In addition to the CRQA parameters, two other parameters are required when
-conducting WCRQA. First, a window size must be decided on. The window size
+conducting WCRQA. First, the *window size*
 will determine how many observations are used in each CRQA analysis. We
-conducted WCRQA with a window size of 14 to investigate the dynamics over
+conducted WCRQA with a window size of $14$ to investigate the dynamics over
 two weeks and allow for the capture of more structure and thus a more
-meaningful interpretation of DET. The second parameter to be chosen is a
-step size. Window step size is how far the window moves up the line of identity
-before conducting CRQA again. We chose 1 for the step size to understand
-how the metrics evolve from day to day. All other CRQA metrics remained the
-same as previously noted.
+meaningful interpretation of DET.
+
+The second parameter to be chosen is a *window step size*. 
+Window step size is how far the window moves up the line of identity
+before conducting CRQA again. We chose $1$ for the step size to understand
+how the metrics evolve from day to day.
+
+All other CRQA metrics remained the same as those previously noted.
 
@@
 chance, a permutation test was done to set upper and lower bounds for the
-95th and 99th percentiles. Using a sample size of 14, one-thousand permuted
+95th and 99th percentiles. Using a sample size of 14, $1000$ permuted
 time series were generated without replacement for each real time series. The
 upper and lower 95th and 99th percentiles were set based on the distribution
-of CRQA metrics from these one-thousand CRQ analyses.
+of the permuted WCRQA metrics.
 

### 2020-05-29 manuscript.Rmd
More edits to Present Study section

@@
 of Syrian tweets with the counts
-of all, positive, and negative real-world events.
+of all, positive, and negative real-world events derived from gold-standard
+international event data [i.e., the Integrated Crisis Early Warning
+System; @DVN/28075_2015].
 
@@
 conflict frequency.
-Through these analyses, our primary goal in the current work was to uncover
+Through these analyses, our two primary goals in the current work were to uncover
 (1) how different intensities during times of turmoil may enhance or deter
@@
 
-# run primary crq analysis
+# run primary crqa analysis
 source('./scripts/primary-analyses/02_crqa.R')
@@
 # read in metric names
-metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])
+metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", 
+                      header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
-metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", 
+                               header = FALSE)[-1,-1])
+metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", 
+                               header = FALSE)[-1,-1])
+metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", 
+                               header = FALSE)[-1,-1])
 
-# read in signficiance from permutation tests (target filtered)
-sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
-sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
-sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])
+# read in significance from permutation tests (target filtered)
+sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", 
+                           header = FALSE)[-1,-1])
+sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", 
+                           header = FALSE)[-1,-1])
+sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", 
+                           header = FALSE)[-1,-1])
 
 # read in metrics from crq analyses (source and target filtered)
-metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
-metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
-metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
+metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv",
+                                      header = FALSE)[-1,-1])
+metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv",
+                                      header = FALSE)[-1,-1])
+metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv",
+                                      header = FALSE)[-1,-1])
 
-# read in signficiance from permutation tests (source and target filtered)
-sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
-sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
-sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
+# read in significance from permutation tests (source and target filtered)
+sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", 
+                                  header = FALSE)[-1,-1])
+sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", 
+                                  header = FALSE)[-1,-1])
+sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", 
+                                  header = FALSE)[-1,-1])
 
@@
 ## Cross-Recurrence Quantification Analysis
-CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We 
+CRQA was performed using the `crqa` package [@R-crqa] for R [@R-base]. We 
 conducted a permutation test to check for statistical difference from chance 

### 2020-05-29 manuscript.Rmd
Shift crqa package citation

@@
 on each day. 
+We implemented CRQA using the `crqa` package [@R-crqa] for R [@R-base].
 
@@
 external, real-world events. 
+We implemented WCRQA using the `crqa` package [@R-crqa] for R [@R-base].
 
@@
 ## Cross-Recurrence Quantification Analysis
-CRQA was performed using the `crqa` package [@R-crqa] for R [@R-base]. We 
-conducted a permutation test to check for statistical difference from chance 
-for all analyses and metrics.
 

### 2020-05-29 manuscript.Rmd
Edits to Results

@@
 ### Syria as Target
+
 A permutation test for the CRQA of social cohesion and count of all events 
 found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all);
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
-count of positive events found no statistical difference from chance for any 
+All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ-all);
+\autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and 
+count of positive events found no statistically significant difference for any 
 of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
-count of negative events found a statistical difference from chance for DET, 
-NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
-\@ref(fig:plot-rp-targ-neg); \autoref{table-1}). Looking at the recurrence 
-plots there appears, to be a shift in dynamics around the 36th observation 
+\autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and 
+count of negative events found a statistically significant difference for DET, 
+NRLINE, L, ENTR, LAM, and TT. All other metrics did not reach significance 
+(Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
+
+A qualitative investigation of the recurrence plots suggests
+a shift in dynamics around the 36th observation, 
 which corresponds to May 4th, 2012.
@@
 # give intuitive names
-colnames(target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+colnames(target_results) <- c("metric", 
+                              "all events", "p", "sig.", 
+                              "positive events", "p", "sig.", 
+                              "negative events", "p", "sig.")
 
@@
 ### Syria as Source and Target
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all 
+events found a statistical difference from chance for DET, NRLINE, and 
+LAM. All other metrics were non-significant (Figure 
+\@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of positive 
+events found a statistical difference from chance for maxL, ENTR, and LAM 
+(Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative 
+events found a statistical difference from chance for DET, NRLINE, and rENTR. 
+All other metrics were non-significant (Figure 
+\@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
+
+Looking qualitatively at the recurrence plots, there again appeared 
+to be a shift in dynamics around the 36th observation (May 4th, 2012).
 
@@
 # give intuitive names
-colnames(source_target_results) <- c("metric", "all events", "p", "sig.", "positive events", "p", "sig.", "negative events", "p", "sig.")
+colnames(source_target_results) <- c("metric", 
+                                     "all events", "p", "sig.", 
+                                     "positive events", "p", "sig.", 
+                                     "negative events", "p", "sig.")
 
@@
 
-WCRQA was performed using the crqa package [@R-crqa] for R [@R-base]. Permutation tests
-were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
-the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)),
-the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
+In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and 
+\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented
+by horizontal red lines, and the 99th percentiles are
 represented by horizontal orange lines. The trend lines are plotted in blue.
@@
 
-For social cohesion and count of all events, there is a consistent period 
-of above chance recurrence rate from the 7th-12th and 36th-47th window 
-(Figure \@ref(fig:plot-wcrqa-targ-all)). Determinism is largely above chance 
-from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)). For
-social cohesion and count of positive events there is a downward trend in RR 
-as the window moves with largly above chance RR from the 1st-18th and 
-32nd-45th windows. Determinism was at or above chance for the 8th-17th, 
-32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)). 
-For social cohesion and count of negative events, recurrence rate stays above
-or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
-is above or nearly above chance in the 1st and 2nd windows, with short intermittent 
+For social cohesion and count of all events, there was a consistent period 
+of above-chance RR from the 7th-12th and 36th-47th window 
+(Figure \@ref(fig:plot-wcrqa-targ-all)). DET was largely above chance 
+from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of positive events, there was a downward trend in RR 
+as the window moves with largely above-chance RR from the 1st-18th and 
+32nd-45th windows. DET was at or above chance for the 8th-17th, 
+32nd-34th and at the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of negative events, RR stayed above
+or almost above chance from the 4th-7th and 43rd-47th windows. DET
+was above or nearly above chance in the 1st and 2nd windows, with intermittent 
 peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
@@
 
-For social cohesion and count of all events, there is a consistent period of
-above or nearly above chance determinism from the 7th-13th and 26th-47th 
-windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). Determinism also 
-shows above or nearly above chance values in windows 7th-17th and short, 
+For social cohesion and count of all events, there was a consistent period of
+above- or nearly above-chance DET from the 7th-13th and 26th-47th 
+windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). DET also 
+showed above- or nearly above-chance values in windows 7th-17th and 
 intermittent peaks between the 34th and 61st windows (Figure 
-\@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and count of 
-positive events, there is a downward trend in RR as the window moves with 
-largely above chance values in the first 20 windows and the 32nd-45th windows. 
-Determinism stays largely within chance with the exception of windows 13 
-through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion
-and negative events, there appears to be an extended time period where RR 
-(32nd-47th windows) and DET (35th-39th windows) were above of nearly above 
+\@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and count of 
+positive events, there was a downward trend in RR as the window moved, with 
+largely above-chance values in the first 20 windows and the 32nd-45th windows. 
+DET stayed largely within chance, with the exception of windows 13 
+through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion
+and negative events, there was an extended period of time during which RR 
+(32nd-47th windows) and DET (35th-39th windows) were above or nearly above 
 chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
-May 3rd, 2012 to May 14th, 2012.
+May 3rd--14th, 2012.
 

### 2020-05-29 manuscript.Rmd
Edit Discussion

@@
 *max line* (*maxL*); it indicates the longest instance of being “stuck” in a
-particular state together. The total *number of lines* on the plot (*NRLINE*) 
+particular state together and is a measure of the stability of the system. 
+The total *number of lines* on the plot (*NRLINE*) 
 scales with structure: The more lines that exist, the more coupled the systems are. The
@@
 how social mobilization both virtually and physically evolve over time in
-tandem. Prior to now, the extent to which virtual mobilization on social
-media platforms such as Twitter has been largely unexplored. Using the
-nonlinear methods cross-recurrence quantification analysis and windowed
-cross-recurrence quantification analysis, we investigated the theory that
+tandem. Using the
+nonlinear dynamical time series analyses, we investigated the theory that
 virtual mobilization is increasingly reflective of real-world events
@@
 ### Syria as Target
-The significant result of DET for social cohesion and both the all events
-and negative events time series confirms our hypothesis, that increased
-salience of events is reflected in social cohesion on Twitter. The frequency
-of all events and of negative events thus result in a significant number
-of shared trajectories that are statistically different from chance. The
-non-significant results for all metrics for positive event count also
-confirm our hypothesis, and gives support to the theory that positive events
-are less coupled to social cohesion than the more salient, negative events
-during times of turmoil. The inevitable increased salience of event
-frequency and event violence thus leads to increased coupling with Twitter
-social cohesion.
+The significant result of DET for social cohesion with all and negative 
+events supports our hypothesis that
+event salience is coupled with online social cohesion The frequency
+of all and negative events are thus associated with greater
+shared trajectories with social cohesion that would be expected by chance. 
+However, when we specifically target positive events, the connection
+to social cohesion fades, providing further
+support for our hypothesis. Positive events
+may be less coupled to social cohesion than more salient negative events
+during times of turmoil; by contrast, overall event frequency and
+negative event frequency are coupled with Twitter social cohesion.
 
@@
 but directed internally within the country were already captured by the
-target only filtering. The increase in coupling between positive events
-and social cohesion is thus due to the inclusion of these externally
-directed events. Though CRQA metrics for count of all and count of
-negative events with social cohesion were largely unaffected, count of
-positive events and social cohesion showed significant levels of
-determinism, number of lines, max line length, and laminarity that were
-not present in the target filtered data. Given that the Syria during
-this time was still under Authoritarian rule, the government may have
-been initiating more positive external events to prevent intervention
-by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not
-reflective of actual social cohesion, but happened by chance. The
-inflation of the number of positive events when including source
-observations is causing increased coupling, but it is more likely that
-the Twitter users were using the platform to raise awareness of the
-violent, internal events that were being inflicted on them by their
-government officials and armies and not reporting on the positive
-external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet
-corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs;
-Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)),
-there appears to be a shift in the dynamics of these systems around
-observation 35, or May 3rd, 2012. To further investigate these local
-dynamics, we performed a sliding window technique known as windowed
-cross-recurrence quantification analysis (WCRQA).
+target-only filtering. The increase in coupling between positive events
+and social cohesion can thus only be due to the externally
+directed events. Though the coupling between social cohesion with
+negative and all events were largely unchanged, 
+positive events and social cohesion showed greater stability
+in their coupling (reflected in maxL); while TT was no longer
+significant in these analyses, LAM (related to TT) did
+reach statistical significance.
+
+While interesting, the underlying meaning or drivers of this change
+in results requires further investigation that incorporates the
+actual content of the tweets themselves. One possible reason (among
+many) may be that the finding was spurious. The positive external 
+events from Syria may have been self-serving, aiming to prevent intervention
+by other countries or to cover up what was happening internally.
+During these moments, the increased cohesion may reflect a surge from 
+the Syrian people trying to raise awareness of the situation or
+to decry the Syrian government's attempts to improve their international
+standing. In this case, the increased coupling of positive events would
+coupled not with shared positive affect in social media but instead
+to shared negative affect in social media in response. However, we
+cannot test this hypothesis with the current data; future  
+research should explore the semantic content of this tweet
+corpus to determine the nature of the socially cohered language.
 
 ## Windowed-Recurrence Quantification Analysis
+
 ### Syria as Target
-The time period of differing dynamics, from observation 38 through 43,
-appears to be captured by WCRQA of social cohesion and count of negative
-events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)). The
+The time period of differing dynamics---from observation 38 through 
+43---appears to be captured by the RR and DET values in
+WCRQA of social cohesion and count of negative
+events (Figure \@ref(fig:plot-wcrqa-targ-all)). The
 amount of recurrence and determinism for these periods almost consistently
 lie above chance, suggesting that the intensity of negative events coincide
-with the degree of social cohesion found on Twitter, and that these states
-carry across multiple days in a way that is different from that of chance.
-
-The above-chance levels of determinism and recurrence rate are demonstrating
-the coupling of social cohesion and counts of all and negative events during
-times of strife. We can see this string of highly violent events reflected
-in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)),
-where from May 1st, 2020 to May 15th, 2020, the most frequently occurring
-event was almost consistently -10, the most violent event in the coding
-system. These dates directly correlate with the above chance RR and DET
+with the degree of social cohesion found on Twitter and that these 
+shared trajectories extend across multiple days.
+
+The above-chance levels of determinism and recurrence rate demonstrate
+the coupling of social cohesion to both total and negative events during
+times of strife. During this period, 
+the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
+during May 1st---15th was almost consistently -10, the most violent 
+event category. These dates directly correlate with the above-chance RR and DET
 metrics for the WCRQA of social cohesion and count of negative events.
@@
 that large numbers on a given day will be reflective of increased levels
-of social cohesion. Determinism showed more frequent above-chance metrics
+of social cohesion. DET showed more frequent above-chance metrics
 for windows 39 and up, suggesting that the inclusion of externally
 directed events lead to higher event counts during these days and then
-was more reflective of the level of social cohesion on Twitter. WCRQA for
-count of positive events and social cohesion remained largely the same for
-RR and DET as the source only data. This again seems to support the idea
-that these two aren't actually coupled, but rather that the inflation of
-the positive counts lead to a spurious relationship. Count of negative
-events and social cohesion also showed similar trends for RR and DET,
-again attesting to the theory that negative events were coupled to social
-cohesion on Twitter while positive events happened by chance.
+was more reflective of the level of social cohesion on Twitter.
+
+WCRQA metrics for positive-only and negative-only event counts with 
+social cohesion remained largely the same for
+RR and DET as the source-only data. This may support the ideas suggested
+in the CRQA section, but again, only future work including the *content*
+of those tweets can directly speak to that explanation.
 
 ## Conclusion
-Considering the invasiveness of social media in our everyday lives, it is
-inevitable that individuals involved in real-world social mobilization have
-utilized these platforms to their advantage. If consistent across other civil
-wars, these results have serious implications for monitoring global
+Given the pervasiveness of social media, it is unsurprising
+that social activists and protesters have
+utilized these platforms to support real-world mobilization. 
+Here, we quantitatively explored the connection
+between online social cohesion and real-world events. In addition
+to introducing political scientists to a family of powerful nonlinear 
+dynamics analyses, our results have serious implications for monitoring global
 movements. While traditional media in regions of authoritarian rule are
 often biased, the self-organized nature of Twitter poses a new avenue to gain
-insight into truths about up-risings and social mobilization. By
-conceptualizing Twitter and real-world events as two components of an
-inextricably linked dynamical system, the levels of social cohesion within the
-virtual platform could be monitored for fluctuations indicating global shifts
-in power and peace. Social media mobilization can thus help alert us to
-real-world mobilization not communicated in mainstream media and allow for 
-faster intervention.
+insight into truths about uprisings and social mobilization. By
+conceptualizing Twitter and real-world events as two elements of an
+inextricably linked dynamical system, the levels of social cohesion within 
+social media platforms could be monitored for fluctuations indicating shifts
+in power and peace. Social media mobilization may thus help alert the world to
+citizens' actions and reactions that are suppressed by government regimes,
+providing insight into events that may not otherwise be broadcast.
 

### 2020-05-29 manuscript.tex
Bring tex up to speed

@@
 of Syrian tweets with the counts
-of all, positive, and negative real-world events.
+of all, positive, and negative real-world events derived from gold-standard
+international event data (i.e., the Integrated Crisis Early Warning
+System; Boschee et al., 2015).
 
@@
 high frequency in one tweet but has a low frequency in the whole tweet
-corpus, then it is more likely a content word and is this given more weight
+corpus, then it is more likely a content word and is thus given more weight
 in calculating social cohesion.
+This method is similar to inverse document frequency (IDF).
+For more information on IDF, see Jones (1972) and
+Robertson (2004).
 
@@
 
-The social cohesion calculation was performed on a subset of the corpus
+The social cohesion calculation was performed on the tweet corpus
 containing (recalculate with new date span) English and (recalculate with
 new date span) Arabic tweets. All hashtags and URLs were included in the
-analysis. This method is similar to that of inverse document frequency (IDF).
-For more information on IDF, see Jones (1972) and
-Robertson (2004).
+analysis.
 
@@
 Using the Integrated Crisis Early Warning System (ICEWS) developed at the
-Defense Advanced Research Project Agency, the daily events in Syria were
-scored with an intensity rating ranging from -10 to 10. Negative events,
-such as riots and attacks, are coded with low negative numbers while
-positive, peaceful events are coded with high positive numbers. This
+Defense Advanced Research Project Agency, the daily events were
+scored with an intensity rating ranging from -10 to 10. Negative
+events---such as riots and attacks---are coded with low negative numbers, while
+positive or peaceful events are coded with high positive numbers. This
 well-validated coding scheme allows for numerical quantification of
@@
 (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of
-social cohesion and real-world events in Syria during Arab Spring. As
-an extension of RQA, which captures the patterns of revisited states of
-a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992), CRQA
+social cohesion and real-world events in Syria during Arab Spring. CRQA
+is an extension of RQA, which captures the patterns of revisited states of
+a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992). CRQA
 allows for two time series to be projected onto one another to investigate
-shared states and trajectories. Nonlinear analyses such as CRQA can reveal
-dynamics that are not captured by traditional linear methods.
-
-In order to perform CRQA, the time series need to be converted to the same
+shared states and trajectories.
+In CRQA, we track these shared states by identifying \emph{recurrent points},
+or intersections of time during which two signals shared or revisited the same
+state. These shared states can be at the same time or at later points in
+the time series. We can further chart shared trajectories by examining
+the occurrences and patterns of multiple sequential recurrent points.
+
+To perform CRQA, the time series must be converted to the same
 scale, while still preserving a sampling rate that respects the native
@@
 (cf.~Nyquist frequency in signal processing; Grenander, 1959).
-We converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles
-(e.g., Figure \ref{fig:deciled-ts}) to analyze the dynamics of different
+Because the social cohesion and event data have different scales and values,
+we converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles
+(e.g., Figure \ref{fig:deciled-ts}) to analyze the relative dynamics of different
 levels of social cohesion and counts of all, positive, and negative events
-on each day. In CRQA, a recurrent point is when two signals share the same
-state. These shared states can be at the same time or at later points in
-the time series.
+on each day.
+We implemented CRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R (R Core Team, 2019).
 
@@
 
-A recurrence plot (RP) is the visual representation of CRQA. To construct
-a recurrence plot, two time series are plotted against each other on the
-X and Y axes, and at every point where they share the same state, and point
-in placed on the plot to indicate recurrence. Visually analyzing these plots
-can help reveal patterns of structure and recurrence. The line y = x is known
-as the line of identity. This line falls where the time series match
-temporally, and a filled line would indicate perfect synchrony between the
+A cross-recurrence plot (CRP) is the visual representation of CRQA. To construct
+a cross-recurrence plot, two time series are plotted against each other on the
+\(x\) and \(y\) axes. At every point where they share the same state, a point
+in placed on the plot to indicate recurrence. (For categorical CRQA, this process
+is similar to the Cartesian product.)
+
+We can visually analyze these plots
+to reveal patterns of structure and recurrence. The line \(y = x\) is known
+as the \emph{line of identity}. This line falls where the time series match
+temporally. A filled line would indicate perfect in-phase synchrony between the
 two time series. See
@@
 
+While visual inspections can be informative, we can derive a variety of
+quantitative metrics from the cross-recurrence plot. Each of these metrics
+provides information into the pattern and dynamics of the new shared system
+between the original time series. These metrics are also critical for inferential
+statistics. We will focus most directly on two of these metrics:
+\emph{recurrence rate} and \emph{determinism}.
+
 The percentage of recurrent points to total possible points is a metric
-called recurrence rate (RR). This metrics gives a general description of
+called the \emph{recurrence rate} (\emph{RR}). This metrics gives a general description of
 how frequently the time series are sharing the same states. In the current
@@
 are moving together across time in a shared state. The percentage of
-recurrent points that make up diagonal line structures (i.e., two or more
-consecutive points) is a metric called percent determinism (DET). For the
+recurrent points on the plot that fall along diagonal line structures
+(i.e., two or more
+consecutive points) is a metric called \emph{percent determinism}
+(or simply \emph{determinism}; \emph{DET}). For the
 current project, a high DET would indicate that not only are the levels of
@@
 
-The average length of the line structures is called mean line (L). This can
+A number of other metrics provide insight not only into the amount of structure
+between the systems but about the nature of this shared structure.
+The average length of the line structures is called \emph{mean line} (L), which can
 be conceptualized as the average amount of time that the two time series move
 together before one or both shift states. The longest line length is called
-max line (maxL). maxL indicates the longest instance of being \enquote{stuck} in a
-particular state together. The total number of lines is called NRLINE. The
-more lines there are, the more coordinated the system may be. The
+\emph{max line} (\emph{maxL}); it indicates the longest instance of being \enquote{stuck} in a
+particular state together and is a measure of the stability of the system.
+The total \emph{number of lines} on the plot (\emph{NRLINE})
+scales with structure: The more lines that exist, the more coupled the systems are. The
 complexity or variability of line lengths is captured by a metric called
-entropy (ENTR) and entropy while accounting for the total number of lines in
-the plot is normalized entropy (rENTR). These entropy metrics help indicate
+\emph{entropy} (\emph{ENTR})---which may also be normalized by the total number of lines
+(i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
 the stability and predictability of the system. When one of the signals gets
 \enquote{stuck} in a state and the other moves on to other states, this results in
-vertical line structures. The proportion of points forming vertical line
-structures is a metric called laminarity (LAM) and the average length of the
-vertical trajectories is called trapping time (TT). For more detail on CRQA
-metrics, see Coco and Dale (2018).
+vertical line structures, which are quantified in \emph{laminarity} (\emph{LAM};
+i.e., the proportion of points forming vertical line structures)
+and trapping time (\emph{TT}; i.e., the average length of the
+vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).
 
@@
 To conduct the analyses on the decile data, the parameters were set to those
-typically used in categorical CRQA. Delay was set to zero, embedding dimension
-was set to 1, and radius was set to .001 to allow for only exact recurrent
+typically used in categorical CRQA: Delay was set to \(0\), embedding dimension
+was set to \(1\), and radius was set to \(.001\) to allow for only exact recurrent
 matches. No normalization was done, and lines were considered two or more
-consecutive recurrent points. The Theiler window was set to zero to include
+consecutive recurrent points. The Theiler window was set to \(0\) to include
 points along the line of identity. For more details on the CRQA parameters and
@@
 
-Using the deciled, real time series of social cohesion, count of all events,
-count of positive events, and count of negative events, a permutation test was
-done to determine statistical difference from chance for each CRQA metric.
-Using the sample function in base R (R Core Team, 2019), 1000 permuted time series were
-created for each of the real time series. A permutation test is similar to
+Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not have
+inherently meaningful values. As a result, CRQA is best used as a relative
+metric---that is, comparing the CRQA values across conditions or subsets
+of the data. Typically, meaningful differences between values are determined with
+traditional inferential statistics. While this may not be a problem for
+experimentally derived datasets, it can pose a barrier to researchers using
+small-\(n\) data or conducting data-informed case studies.
+
+For CRQA, this can be addressed using \emph{permutation tests}.
+Similar to more established methods of statistical significance in CRQA research
+(which create surrogate time series; e.g., Paxton \& Dale, 2017),
+the permutation test approach to significance testing allows the researcher
+to use a time series as its own baseline by testing whether the \emph{structure}
+of the unfolding events of the time series---rather than the \emph{raw frequency} of the
+events within the time series---cohere together more than would be expected
+by chance. A permutation test is similar to
 bootstrapping, except that the sampling of observations is done without
-replacement. CRQA was then run 1000 times for social cohesion and count of all
+replacement. In this approach, we simply create a large number of permutations
+of the original time series (i.e., breaking up the dependency across time points but
+preserving the frequencies of the events), conduct CRQA for each of those
+permutations, and then examine whether the real time series' CRQA metrics
+exceed those that we would expect to see by chance. The proportion of times that
+the real time series' values exceeds the surrogate time series' values can
+be interpreted as the alpha criterion to determine significance.
+For more information on permutation
+tests, see Good (2013).
+
+Using the real deciles of social cohesion, count of all events,
+count of positive events, and count of negative events, we conducted a series
+of permutation tests
+(one for the comparison between social cohesion and each type of event count)
+to determine statistical difference from chance for each CRQA metric.
+Using the \texttt{sample} function in base R (R Core Team, 2019), \(1000\) permuted time series were
+created for each of the real time series.\\
+CRQA was then run \(1000\) times for social cohesion and count of all
 events, social cohesion and count of positive events, and social cohesion and
 count of negative events using the permuted time series. This resulted in
-1000 results for each of the CRQA metrics for each combination of time series.
+\(1000\) results for each of the CRQA metrics for each combination of time series.
 Statistical significance from chance was set at the 95th and 99th percentiles
@@
 is similar to bootstrapping but does not include replacement, all points were
-included in each CRQA analysis, leaving RR the same across all analyses. Thus,
-RR is not included in the inferential tests. For more information on permutation
-tests, see Good (2013).
+included in each CRQA analysis, leaving RR constant across all permutations. Thus,
+RR is not included in the inferential tests.
 
@@
 a smaller \enquote{window} of time points is used to calculate CRQA and capture more
-fine-grain dynamics of two time series. The window remains the same size and
+fine-grained dynamics of two time series. The window remains the same size and
 \enquote{slides} diagonally up the line of identity. The changes in the CRQA metrics
@@
 external, real-world events.
+We implemented WCRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R (R Core Team, 2019).
 
@@
 In addition to the CRQA parameters, two other parameters are required when
-conducting WCRQA. First, a window size must be decided on. The window size
+conducting WCRQA. First, the \emph{window size}
 will determine how many observations are used in each CRQA analysis. We
-conducted WCRQA with a window size of 14 to investigate the dynamics over
+conducted WCRQA with a window size of \(14\) to investigate the dynamics over
 two weeks and allow for the capture of more structure and thus a more
-meaningful interpretation of DET. The second parameter to be chosen is a
-step size. Window step size is how far the window moves up the line of identity
-before conducting CRQA again. We chose 1 for the step size to understand
-how the metrics evolve from day to day. All other CRQA metrics remained the
-same as previously noted.
+meaningful interpretation of DET.
+
+The second parameter to be chosen is a \emph{window step size}.
+Window step size is how far the window moves up the line of identity
+before conducting CRQA again. We chose \(1\) for the step size to understand
+how the metrics evolve from day to day.
+
+All other CRQA metrics remained the same as those previously noted.
 
@@
 chance, a permutation test was done to set upper and lower bounds for the
-95th and 99th percentiles. Using a sample size of 14, one-thousand permuted
+95th and 99th percentiles. Using a sample size of 14, \(1000\) permuted
 time series were generated without replacement for each real time series. The
 upper and lower 95th and 99th percentiles were set based on the distribution
-of CRQA metrics from these one-thousand CRQ analyses.
+of the permuted WCRQA metrics.
 
@@
 
-CRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). We
-conducted a permutation test to check for statistical difference from chance
-for all analyses and metrics.
-
 \hypertarget{syria-as-target}{%
@@
 found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics were non-significant (Figure \ref{fig:plot-rp-targ-all};
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and
-count of positive events found no statistical difference from chance for any
+All other metrics did not reach significance (Figure \ref{fig:plot-rp-targ-all};
+\autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and
+count of positive events found no statistically significant difference for any
 of the metrics other than TT (Figure \ref{fig:plot-rp-targ-pos};
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and
-count of negative events found a statistical difference from chance for DET,
-NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
-\ref{fig:plot-rp-targ-neg}; \autoref{table-1}). Looking at the recurrence
-plots there appears, to be a shift in dynamics around the 36th observation
+\autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and
+count of negative events found a statistically significant difference for DET,
+NRLINE, L, ENTR, LAM, and TT. All other metrics did not reach significance
+(Figure \ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
+
+A qualitative investigation of the recurrence plots suggests
+a shift in dynamics around the 36th observation,
 which corresponds to May 4th, 2012.
@@
 
-A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-all}; \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR.
-All other metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-neg}; \autoref{table-2}).
-Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all
+events found a statistical difference from chance for DET, NRLINE, and
+LAM. All other metrics were non-significant (Figure
+\ref{fig:plot-rp-source-targ-all}; \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of positive
+events found a statistical difference from chance for maxL, ENTR, and LAM
+(Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative
+events found a statistical difference from chance for DET, NRLINE, and rENTR.
+All other metrics were non-significant (Figure
+\ref{fig:plot-rp-source-targ-neg}; \autoref{table-2}).
+
+Looking qualitatively at the recurrence plots, there again appeared
+to be a shift in dynamics around the 36th observation (May 4th, 2012).
 
@@
 
-WCRQA was performed using the crqa package (Coco \& Dale, 2018) for R (R Core Team, 2019). Permutation tests
-were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
-the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and \ref{fig:plot-wcrqa-source-targ-all}),
-the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
+In the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and
+\ref{fig:plot-wcrqa-source-targ-all}), the 95th percentiles are represented
+by horizontal red lines, and the 99th percentiles are
 represented by horizontal orange lines. The trend lines are plotted in blue.
@@
 
-For social cohesion and count of all events, there is a consistent period
-of above chance recurrence rate from the 7th-12th and 36th-47th window
-(Figure \ref{fig:plot-wcrqa-targ-all}). Determinism is largely above chance
-from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}). For
-social cohesion and count of positive events there is a downward trend in RR
-as the window moves with largly above chance RR from the 1st-18th and
-32nd-45th windows. Determinism was at or above chance for the 8th-17th,
-32nd-34th, and the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
-For social cohesion and count of negative events, recurrence rate stays above
-or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
-is above or nearly above chance in the 1st and 2nd windows, with short intermittent
+For social cohesion and count of all events, there was a consistent period
+of above-chance RR from the 7th-12th and 36th-47th window
+(Figure \ref{fig:plot-wcrqa-targ-all}). DET was largely above chance
+from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}).
+
+For social cohesion and count of positive events, there was a downward trend in RR
+as the window moves with largely above-chance RR from the 1st-18th and
+32nd-45th windows. DET was at or above chance for the 8th-17th,
+32nd-34th and at the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+
+For social cohesion and count of negative events, RR stayed above
+or almost above chance from the 4th-7th and 43rd-47th windows. DET
+was above or nearly above chance in the 1st and 2nd windows, with intermittent
 peaks in later windows (Figure \ref{fig:plot-wcrqa-targ-all}).
@@
 
-For social cohesion and count of all events, there is a consistent period of
-above or nearly above chance determinism from the 7th-13th and 26th-47th
-windows (Figure \ref{fig:plot-wcrqa-source-targ-all}). Determinism also
-shows above or nearly above chance values in windows 7th-17th and short,
+For social cohesion and count of all events, there was a consistent period of
+above- or nearly above-chance DET from the 7th-13th and 26th-47th
+windows (Figure \ref{fig:plot-wcrqa-source-targ-all}). DET also
+showed above- or nearly above-chance values in windows 7th-17th and
 intermittent peaks between the 34th and 61st windows (Figure
-\ref{fig:plot-wcrqa-source-targ-all}). For social cohesion and count of
-positive events, there is a downward trend in RR as the window moves with
-largely above chance values in the first 20 windows and the 32nd-45th windows.
-Determinism stays largely within chance with the exception of windows 13
-through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}). For social cohesion
-and negative events, there appears to be an extended time period where RR
-(32nd-47th windows) and DET (35th-39th windows) were above of nearly above
+\ref{fig:plot-wcrqa-source-targ-all}).
+
+For social cohesion and count of
+positive events, there was a downward trend in RR as the window moved, with
+largely above-chance values in the first 20 windows and the 32nd-45th windows.
+DET stayed largely within chance, with the exception of windows 13
+through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+
+For social cohesion
+and negative events, there was an extended period of time during which RR
+(32nd-47th windows) and DET (35th-39th windows) were above or nearly above
 chance (Figure \ref{fig:plot-wcrqa-source-targ-all}). These windows span from
-May 3rd, 2012 to May 14th, 2012.
+May 3rd--14th, 2012.
 
@@
 
-The significant result of DET for social cohesion and both the all events
-and negative events time series confirms our hypothesis, that increased
-salience of events is reflected in social cohesion on Twitter. The frequency
-of all events and of negative events thus result in a significant number
-of shared trajectories that are statistically different from chance. The
-non-significant results for all metrics for positive event count also
-confirm our hypothesis, and gives support to the theory that positive events
-are less coupled to social cohesion than the more salient, negative events
-during times of turmoil. The inevitable increased salience of event
-frequency and event violence thus leads to increased coupling with Twitter
-social cohesion.
+The significant result of DET for social cohesion with all and negative
+events supports our hypothesis that
+event salience is coupled with online social cohesion The frequency
+of all and negative events are thus associated with greater
+shared trajectories with social cohesion that would be expected by chance.
+However, when we specifically target positive events, the connection
+to social cohesion fades, providing further
+support for our hypothesis. Positive events
+may be less coupled to social cohesion than more salient negative events
+during times of turmoil; by contrast, overall event frequency and
+negative event frequency are coupled with Twitter social cohesion.
 
@@
 but directed internally within the country were already captured by the
-target only filtering. The increase in coupling between positive events
-and social cohesion is thus due to the inclusion of these externally
-directed events. Though CRQA metrics for count of all and count of
-negative events with social cohesion were largely unaffected, count of
-positive events and social cohesion showed significant levels of
-determinism, number of lines, max line length, and laminarity that were
-not present in the target filtered data. Given that the Syria during
-this time was still under Authoritarian rule, the government may have
-been initiating more positive external events to prevent intervention
-by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not
-reflective of actual social cohesion, but happened by chance. The
-inflation of the number of positive events when including source
-observations is causing increased coupling, but it is more likely that
-the Twitter users were using the platform to raise awareness of the
-violent, internal events that were being inflicted on them by their
-government officials and armies and not reporting on the positive
-external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet
-corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs;
-Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}),
-there appears to be a shift in the dynamics of these systems around
-observation 35, or May 3rd, 2012. To further investigate these local
-dynamics, we performed a sliding window technique known as windowed
-cross-recurrence quantification analysis (WCRQA).
+target-only filtering. The increase in coupling between positive events
+and social cohesion can thus only be due to the externally
+directed events. Though the coupling between social cohesion with
+negative and all events were largely unchanged,
+positive events and social cohesion showed greater stability
+in their coupling (reflected in maxL); while TT was no longer
+significant in these analyses, LAM (related to TT) did
+reach statistical significance.
+
+While interesting, the underlying meaning or drivers of this change
+in results requires further investigation that incorporates the
+actual content of the tweets themselves. One possible reason (among
+many) may be that the finding was spurious. The positive external
+events from Syria may have been self-serving, aiming to prevent intervention
+by other countries or to cover up what was happening internally.
+During these moments, the increased cohesion may reflect a surge from
+the Syrian people trying to raise awareness of the situation or
+to decry the Syrian government's attempts to improve their international
+standing. In this case, the increased coupling of positive events would
+coupled not with shared positive affect in social media but instead
+to shared negative affect in social media in response. However, we
+cannot test this hypothesis with the current data; future\\
+research should explore the semantic content of this tweet
+corpus to determine the nature of the socially cohered language.
 
@@
 
-The time period of differing dynamics, from observation 38 through 43,
-appears to be captured by WCRQA of social cohesion and count of negative
-events for both RR and DET (Figure \ref{fig:plot-wcrqa-targ-all}). The
+The time period of differing dynamics---from observation 38 through
+43---appears to be captured by the RR and DET values in
+WCRQA of social cohesion and count of negative
+events (Figure \ref{fig:plot-wcrqa-targ-all}). The
 amount of recurrence and determinism for these periods almost consistently
 lie above chance, suggesting that the intensity of negative events coincide
-with the degree of social cohesion found on Twitter, and that these states
-carry across multiple days in a way that is different from that of chance.
-
-The above-chance levels of determinism and recurrence rate are demonstrating
-the coupling of social cohesion and counts of all and negative events during
-times of strife. We can see this string of highly violent events reflected
-in the mode ICEWS event for each day (Figure \ref{fig:plot-mode-event}),
-where from May 1st, 2020 to May 15th, 2020, the most frequently occurring
-event was almost consistently -10, the most violent event in the coding
-system. These dates directly correlate with the above chance RR and DET
+with the degree of social cohesion found on Twitter and that these
+shared trajectories extend across multiple days.
+
+The above-chance levels of determinism and recurrence rate demonstrate
+the coupling of social cohesion to both total and negative events during
+times of strife. During this period,
+the modal ICEWS event for each day (Figure \ref{fig:plot-mode-event})
+during May 1st---15th was almost consistently -10, the most violent
+event category. These dates directly correlate with the above-chance RR and DET
 metrics for the WCRQA of social cohesion and count of negative events.
@@
 that large numbers on a given day will be reflective of increased levels
-of social cohesion. Determinism showed more frequent above-chance metrics
+of social cohesion. DET showed more frequent above-chance metrics
 for windows 39 and up, suggesting that the inclusion of externally
 directed events lead to higher event counts during these days and then
-was more reflective of the level of social cohesion on Twitter. WCRQA for
-count of positive events and social cohesion remained largely the same for
-RR and DET as the source only data. This again seems to support the idea
-that these two aren't actually coupled, but rather that the inflation of
-the positive counts lead to a spurious relationship. Count of negative
-events and social cohesion also showed similar trends for RR and DET,
-again attesting to the theory that negative events were coupled to social
-cohesion on Twitter while positive events happened by chance.
+was more reflective of the level of social cohesion on Twitter.
+
+WCRQA metrics for positive-only and negative-only event counts with
+social cohesion remained largely the same for
+RR and DET as the source-only data. This may support the ideas suggested
+in the CRQA section, but again, only future work including the \emph{content}
+of those tweets can directly speak to that explanation.
 
@@
 
-Considering the invasiveness of social media in our everyday lives, it is
-inevitable that individuals involved in real-world social mobilization have
-utilized these platforms to their advantage. If consistent across other civil
-wars, these results have serious implications for monitoring global
+Given the pervasiveness of social media, it is unsurprising
+that social activists and protesters have
+utilized these platforms to support real-world mobilization.
+Here, we quantitatively explored the connection
+between online social cohesion and real-world events. In addition
+to introducing political scientists to a family of powerful nonlinear
+dynamics analyses, our results have serious implications for monitoring global
 movements. While traditional media in regions of authoritarian rule are
 often biased, the self-organized nature of Twitter poses a new avenue to gain
-insight into truths about up-risings and social mobilization. By
-conceptualizing Twitter and real-world events as two components of an
-inextricably linked dynamical system, the levels of social cohesion within the
-virtual platform could be monitored for fluctuations indicating global shifts
-in power and peace. Social media mobilization can thus help alert us to
-real-world mobilization not communicated in mainstream media and allow for
-faster intervention.
+insight into truths about uprisings and social mobilization. By
+conceptualizing Twitter and real-world events as two elements of an
+inextricably linked dynamical system, the levels of social cohesion within
+social media platforms could be monitored for fluctuations indicating shifts
+in power and peace. Social media mobilization may thus help alert the world to
+citizens' actions and reactions that are suppressed by government regimes,
+providing insight into events that may not otherwise be broadcast.
 
@@
 
+\leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
+Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.
+
 \leavevmode\hypertarget{ref-paxton2017finding}{}%

### 2020-05-31 manuscript.Rmd
add literature review section

--- 2020-05-29 manuscript.Rmd
@@
 abstract: |
-  Social mobilization requires effective collective coordination. In recent 
-  years, individuals involved in social movements have taken to social media
-  platforms to reach broader audiences at rapid speeds. Effective virtual 
-  mobilization similarly requires social cohesion and coordination, yet the 
-  degree to which virtual mobilization reflects or drives real-world movements
-  is unclear. Here, we explore the dynamics of real-world events and social 
-  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear 
-  methods cross-recurrence quantification analysis and windowed cross-recurrence
-  quantification analysis, we investigate if counts of all daily events, daily 
-  positive events, and daily negative events are coupled with social cohesion 
-  found in Syrian tweets. Results indicate that virtual social cohesion is 
-  coupled with the counts of all and negative events each day but not with 
-  counts of positive events. This suggests that virtual mobilization does reflect 
-  real-world movements but only for salient, frequent and negative events. We 
-  conclude with a discussion of implications and applications of nonlinear 
-  methods in political science research.
+  Social mobilization requires effective collective coordination.
+In recent years, individuals involved in social movements have taken to social media platforms such as Twitter to reach broader audiences at rapid speeds.
+Effective virtual mobilization similarly requires social cohesion and coordination, yet it is still unclear if virtual mobilization reflects real-world movements.
+Here, we explore the dynamics of real-world events and social cohesion on Twitter in Syria during the Arab Spring.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if counts of all daily events, daily positive events, and daily negative events are coupled with social cohesion found in Syrian tweets.
+Results indicate that virtual social cohesion is coupled with the counts of all and negative events each day, but not with counts of positive events.
+This suggests that virtual mobilization does reflect real-world movements, but only for salient, frequent and negative events.
+We conclude with a discussion of implications and applications of nonlinear methods in political science research.
   <!-- https://tinyurl.com/ybremelq -->
 
-keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
+keywords          : "Social cohesion, recurrence quantification analysis, complex systems, Twitter, nonlinear dynamics, Arab Spring"
 wordcount         : "X"
@@
 draft             : no
-appendix          :
+appendix          : "appendix.Rmd"
 
@@
 knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)
+#knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
 
@@
 
-Social coordination has long been used both physically and virtually
-to start and carry out collective actions. These collective events
-bring individuals together and create emergent patterns of communication
-and action. Online communication has historically been used to document
-and communicate archival information about events, but it has been
-increasingly used to bring about social change. From a dynamical
-systems perspective, these different means of social coordination during
-times of turmoil can be considered two complementary components of a
-single system, mutually constrained and constantly interacting and
-influencing one another [@mahner1997foundations]. Investigation of the
-coupling of real-world mobilization and social cohesion could provide
-new insight into the power of social media during mobilization and the
-ways in which individuals utilize it to bring about, or respond to, social
-change. Increasingly, social media platforms are being utilized during
-social mobilization, but the relationship between virtual and real-world
-mobilization is still largely unknown. The present work aims to understand
-how physical and virtual movements coexist and interact from a dynamical
-systems perspective.
+Social coordination has long been used both physically and virtually to start and carry out collective actions.
+These collective events bring individuals together and create emergent patterns of communication and action.
+Online communication has historically been used to document and communicate archival information about events, but it has been increasingly used to bring about social change.
+From a dynamical systems perspective, these different means of social coordination during times of turmoil can be considered two complementary components of a single system, mutually constrained and constantly interacting and influencing one another [@mahner1997foundations].
+Investigation of the coupling of real-world mobilization and social cohesion could provide new insight into the power of social media during mobilization and the ways in which individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social mobilization, but the relationship between virtual and real-world mobilization is still largely unknown.
+The present work aims to understand how physical and virtual movements coexist and interact from a dynamical systems perspective.
 
 ## Arab Spring
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian
-rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death,
-Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
-country. The events of Tunisia rapidly spread to surrounding countries 
-also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
-and Syria.
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and unjustifiably stripped of his vendor cart by municipal officials.
+His humiliation led him to set himself on fire in protest to the authoritarian rule, ultimately leading to his death several days later.
+His actions served as a catalyst for the Tunisian Revolution, and one week after his death, the long-withstanding authoritarian president, Zine El Abidine Ben Ali, fled the country.
+The events of Tunisia rapidly spread to surrounding countries that were also subject to unjust authoritarian rule, such as Yemen, Egypt, Libya, and Syria.
+These mass movements would not have been possible without efficient interpersonal coordination, both physically and virtually on social media platforms, such as Twitter.
+The events of Arab Spring have been thoroughly discussed within the political science literature [e.g., @lutterbeck2013arab; @koehler2017political] but to our knowledge, the use of Twitter by Syrian citizens has not been investigated.
 
-These mass movements would not have been possible without
-efficient large-scale coordination, both physically and virtually on social
-media platforms. Along with Facebook, Twitter has been credited as essential 
-to the Arab Spring---both for protesters (as a means to coordinate with one 
-another and to communicate with the world) and for the government response
-(to monitor and track protestors to crack down on dissent) [@comninos2011twitter]. 
-The events of Arab Spring have been
-thoroughly discussed within the political science literature
-[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
-the direct coupling between Syrian Twitter use and international action
-has not been investigated.
+## Literature review
 
-## Social Cohesion and Social Mobilization
-Real-world collective action is known to bring about a sense of togetherness,
-also known as “collective effervescence” [@durkheim1995elementary]. This
-feeling of being a part of something larger than oneself leads individuals
-to act in ways that would not have on their own. Being overcome with this
-feeling can lead to violence [@collins2009violence; @spaaij2014sports].
-Conversely, increased exposure
-to violence can result in positive social cohesion. @gilligan2014civil
-found that exposure to fatal wartime violence resulted in increased prosocial
-motivations, including cooperative behaviors, feelings of trust, and overall
-community-level social cohesion.
+## Social Cohesion
+Real-world collective action is known to bring about a sense of togetherness, also known as “collective effervescence” [@durkheim1995elementary].
+This feeling of being a part of something larger than oneself leads individuals to act in ways that would not have on their own.
+Being overcome with this feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
+While feelings of social connection may lead to violence, increased exposure to violence can result in feelings of social cohesion.
+@gilligan2014civil found that exposure to fatal wartime violence resulted in increased prosocial motivations, including cooperative behaviors, feelings of trust, and overall community-level social cohesion.
+Just as real-world social cohesion can be quantified, the same is true for online cohesion.
+Strategic communication on social media in the form of social cohesion of language can lead to real-world social change, and exposure to real-world violence could result in social cohesion in the virtual world.
+Increased social cohesion is thus potentially an indicator of increased social organization and mobilization on the ground.
 
-Just as real-world social cohesion can be
-quantified, so can online cohesion. While this can be quantified in many ways,
-one kind of cohesion can be found in the similarity in language use on social media.
-This implicit or explicit similarity in language use can indicate shared
-beliefs, thoughts, and feelings, as has been studied in research on language style
-in psycholinguistics and social psychology 
-[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
-although previous work on language style
-has often focused on individuals and small groups, this can be scaled up to examine
-massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
-This kind of massive online social cohesion can lead to real-world
-social change.
+## Social Media as a Platform for Mobilization
+Social media platforms, such as Twitter, offer rapid real-time dissemination of information.
+Given its accessibility and proficiency as an information exchange tool, individuals involved in social movements have taken to them in conjunction, or in replacement, of real-world social mobilization.
+During the 2012 Italian protests for global economic change, the riots in Rome were mirrored by Twitter activity both on the same day and in the following days after the protests [@vicari2013public].
+Tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms.
+As more and more individuals rely on social media to obtain local news and information, it becomes increasingly important to understand just how these micro-blogs reflect real-world action.
 
-Combining these separate threads, it is reasonable to expect that real-world actions 
-and online social interactions would be enmeshed, driving and being driven by 
-one another. Rather than expecting that only real-world social cohesion would be
-driven by real-world action, we would expect interaction between real-world and
-virtual dynamics: In this case, exposure to real-world violence could result in social
-cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator and a result of increased social organization and mobilization 
-on the ground.
-
-Social media platforms provide one way of enabling this kind of online social
-cohesion by offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements
-an opportunity to complement or even replace real-world social mobilization.
-For example, during the 2012 Italian protests for global economic change, the riots in
-Rome were mirrored by Twitter activity both on the day of the protests and in the
-days following them [@vicari2013public]. Tweeting was
-determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more
-individuals rely on social media to obtain local news and information, it
-becomes increasingly important to understand just how these micro-blogs
-reflect real-world action.
-
-## Using Nonlinear Methods to Capture Complex Relationships
-Given the hypothesized interrelationship between the real-world
-and online actions---and the notorious messiness of naturally occurring
-data---it is critical to find appropriate analysis tools that can
-identify the complex interconnections.
-Traditional linear analyses have led to many notable discoveries in the
-domains of psychology and political science, but time series data pose
-problems that are not easily overcome with these methods. Events have
-historically been conceptualized as linear chains of smaller, sequential
-events with one occurrence leading to the next. 
-Certain kinds of data are relatively well-suited to these analyses,
-but messy, complex, variable data from real-world events can pose
-challenges from overpowered samples to violation of underlying
-statistical assumptions [@paxton2017finding].
-
-At the same time, the foundational theoretical assumptions of a 
-linear world has been
-increasingly replaced by ideas from dynamical systems theory. Rather than
-a chain of events, time series data can be thought of as nested occurrences,
-where mutually constrained parts (e.g., citizens, governments, real-world
-events, social media platforms) are constantly interacting, leading to
-more global behaviors that are larger than the sum of the parts
-[@turvey2018lectures]. Linear analyses flatten these nonlinear patterns in 
-time series data and ignore the variability
-that is fundamental to these systems and their evolution over time. 
-However, when analyzed as dynamical systems, many phenomena
-exhibit new nonlinear patterns that were formerly overlooked. 
-Nonlinear methods provide means for capturing the rich temporal
-dynamics and variability that unfold in time series data.
-
-Although a number of other nonlinear methods exist, 
-the primary nonlinear method used in the current work is cross-recurrence
-quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
-windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
-CRQA has successfully been used to gain a better understanding of many
-complex human phenomena, including a variety of human social interactions
-[for a review, see @fusaroli2014analyzing]. 
-Much as it has for psychology, we argue that the use of nonlinear methods in
-the investigation of political science phenomena will lead to new insights
-and the development of more robust theories.
+## Use of Nonlinear Methods in Naturally Occurring Data
+Traditional linear analyses have led to many notable discoveries in the domains of psychology and political science, but continuous data pose problems that are not easily overcome with these methods.
+Events have historically been conceptualized as linear chains of smaller, sequential events with one occurrence leading to the next.
+This notion has been increasingly replaced by ideas from dynamical systems theory.
+Rather than a chain of events, continuous data can be thought of as nested occurrences, where mutually constrained parts (e.g., citizens, governments, real-world events, social media platforms) are constantly interacting, leading to more global behaviors that are larger than the sum of the parts [@turvey2018lectures].
+When analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns that were formerly overlooked.
+Continuous data subject to linear analyses becomes flattened, and the variability that is fundamental to these systems and their evolution over time is ignored.
+Nonlinear methods provide means for capturing the rich temporal dynamics and variability that unfold in continuous data.
+The primary methods used in the current work is cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and it’s off-shoot, windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
+CRQA has successfully been used to gain a better understanding of many complex human phenomena, such as human social interactions [for a review, see @fusaroli2014analyzing] and interpersonal synchrony [@paxton2017interpersonal].
+We argue that the use of nonlinear methods in the investigation of political science phenomena will lead to new insights and development of more robust theories.
 
 ## The Present Work
-Social media has become a primary platform for social movements and
-activism across the world, but the extent to which virtual activism
-reflects and drives real-world mobilization is still largely unknown. 
-In the current work, we
-conceptualize the physical and virtual movements as a dynamical system,
-both constantly interacting and influencing the other. We aim to study
-this by analyzing the real-world events and online social cohesion
-during nearly three months of the Arab Spring. Both real- and
-virtual-world collective coordination were powerful tools in the events
-of the Arab Spring and are undeniably linked. This study aims to explore
-the dynamics of Syrian Twitter users, who used the social media platform to raise
-awareness about the Arab Spring and bring about mass mobilization.
-
-Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
-and windowed cross-recurrence quantification analysis
-[WCRQA; @webber2005recurrence], we analyzed the co-evolution of social
-cohesion online and real-world events. Specifically, using heterogeneous
-data from March 30, 2012, to June 15, 2012, we compared the social cohesion
-of Syrian tweets with the counts
-of all, positive, and negative real-world events derived from gold-standard
-international event data [i.e., the Integrated Crisis Early Warning
-System; @DVN/28075_2015].
-
-We hypothesized that the count of all events and the count of negative
-events would show high levels of determinism, as this time period was
-marked by daily violence which often leads to increased salience. We also
-hypothesized that the count of positive events would not show patterns of
-determinism, as these events were likely overshadowed by the salient
-negative daily occurrences. 
-After testing these hypotheses, we then conducted exploratory analyses 
-to further examine the patterns identified with CRQA. Using WCRQA,
-we sought to identify shifts in the
-dynamics of the systems that could then be linked to real-world shifts in
-conflict frequency.
-Through these analyses, our two primary goals in the current work were to uncover
-(1) how different intensities during times of turmoil may enhance or deter
-social cohesion in social media communication and (2) how social mobilization
-may be evident in the dynamic coupling of cohesion and real-world events.
-
-An additional focus of the current work is to introduce cross-recurrence
-quantification analysis---a longstanding method from physics that has 
-since become influential in a variety of other fields---to political 
-science. We do so by providing detailed descriptions of the methods and
-providing clear directions about interpretation and significance testing
-even with relatively small-*n* or case studies. After demonstrating these
-methods' utility with this dataset, we close the paper with specific
-suggestions to political scientists interested in incorporating these
-methods into their work.
+Social media has become a primary platform for social movements and activism across the world, but the extent to which virtual activism reflects real-world mobilization is still largely unknown.
+We conceptualize the physical and virtual movements as a dynamical system, both constantly interacting and influencing the other.
+Both real- and virtual-world collective coordination were powerful tools in the events of Arab Spring, and are undeniably linked.
+This study aims to explore the dynamics of Syrian individuals who took to Twitter to raise awareness about the events of Arab Spring and bring about mass mobilization.
+Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence], we analyzed the dynamics of social cohesion of tweets from March 30, 2012 to June 15, 2012 and the counts of all, positive, and negative real-world events on those respective days.
+We hypothesized that the count of all events and the count of negative events would show high levels of determinism, as this time period was marked by daily violence which often leads to increased salience.
+We also hypothesized that the count of positive events would not show patterns of determinism, as these events were likely overshadowed by the salient negative daily occurrences.
+Using WCRQA, we hoped to identify shifts in the dynamics of the systems that could then be linked to real world shifts in conflict frequency.
+As social cohesion has never been analyzed using nonlinear methods, the analyses contained herein are largely exploratory.
+The goal of this endeavor is to gain a better understanding of how events of different intensities during times of turmoil may enhance or deter social cohesion in social media communication, and how social mobilization may be evident in the dynamic coupling of cohesion and real-world events.
 
@@
 ### Tweet Corpus
-
-```{r tweet-count, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# read in social cohesion data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
-
-```
-
-The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
-occurring between March 30--June 15, 2012. Using the Twitter
-streaming API, servers at the University of Texas at Austin collected
-the tweets. The servers were run on a stable (LTS) version of Ubuntu
-Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
-maintained by IT services.
-
-Tweets collected contained one or more of the following keywords:
-“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These
-keywords were chosen based on the most distinctive terms used in news
-articles covering the Arab Spring in Syria at the time. A node.js script
-was used to reinitialize the connection to Twitter's servers whenever the
-script timed out due to a period of silence. The script requested data from
-the API endpoint using basic HTTP authentication (OAuth was optional, at
-the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored
-the data directly to the local hard disk. The tweets were then post-processed
-with a Python script to convert the JSON-formatted tweets to tab-separated
-files, which were then compressed to maximize storage efficiency.
-
-All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.
+The corpus of tweets used included 8,084,644 Syrian tweets occurring between March 1, 2012 and June 15, 2012.
+A server malfunction during data collection resulted in missing data from March 12, 2012 to March 29, 2012.
+For the current analyses, the data were truncated to remove missing data, making the final dataset from March 30, 2012 to June 15, 2012 (n = 78).
+The tweet corpus was scraped from Twitter by [insert search parameters here].
 
 ### Event Data
-Event data were obtained from the 2012 Integrated Crisis Early Warning
-System [ICEWS; @DVN/28075_2015]. The event data were first filtered to
-remove incomplete and incorrectly formatted data. They were then filtered
-to include only events that were directed at (i.e., `target`) Syria ($n = 6300$).
-To explore the impact of outwardly directed Syrian events, the data were
-filtered again to include events that were both directed at (i.e., `target`)
-or directed by (i.e., `source`) Syria ($n = 7990$).
+Event data were obtained from the 2012 Integrated Crisis Early Warning System [ICEWS; @DVN/28075_2015].
+The event data were first filtered to remove incomplete and incorrectly formatted data.
+They were then filtered to include only events that were directed (i.e., target) at Syria (n = 6300).
+To explore the impact of outwardly directed Syrian events, the data were filtered again to include events that were both directed at (i.e., target) or directed by (i.e., source) Syria (n = 7990).
 
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated
-by quantifying the frequency of shared content words with respect to those
-words’ frequencies in the entire tweet corpus. If a linguistic term has a
-high frequency in one tweet but has a low frequency in the whole tweet
-corpus, then it is more likely a content word and is thus given more weight
-in calculating social cohesion. 
-This method is similar to inverse document frequency (IDF).
-For more information on IDF, see @jones1972statistical and
-@robertson2004understanding.
+The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
+If a linguistic term has a high frequency in one tweet but has a low frequency in the whole tweet corpus, then it is more likely a content word and is this given more weight in calculating social cohesion.
+The tweets were first sorted into ascending order by timestamp.
+They were then grouped into successive sets of five tweets.
+Inverse frequency weighting for the overlap words and all words was conducted for each pair of two tweets in the group of five, then divided to get the social cohesion score for that pair (see Eq.
+1-3).
+This resulted in ten social cohesion values for each group of five tweets, which were then averaged.
+Finally, the mean of all average cohesion values for all groups was taken to get a social cohesion score for each day.
 
-The tweets were first sorted into ascending order by timestamp. They were
-then grouped into successive sets of five tweets. Inverse frequency
-weighting for the overlap words and all words was conducted for each pair
-of two tweets in the group of five, then divided to get the social cohesion
-score for that pair (see Eq. 1-3). This resulted in ten social cohesion
-values for each group of five tweets; these values were then averaged to get
-a social cohesion score for the entire set of five tweets. Finally,
-the mean of all average cohesion values for all groups was taken to get
-a social cohesion score for each day.
+(insert social cohesion equations here)
 
-\begin{align}
-\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
-\end{align}
-
-\begin{align}
-\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
-\end{align}
-
-\begin{align}
-\text{Two tweets similarity =}\frac{\text{inverse frequency weighting of overlap words}}{\text{inverse frequency weighting of all words}}
-\end{align}
-
-The social cohesion calculation was performed on the tweet corpus
-containing (recalculate with new date span) English and (recalculate with
-new date span) Arabic tweets. All hashtags and URLs were included in the
-analysis.
+The social cohesion calculation was performed on a subset of the corpus containing (recalculate with new date span) English and (recalculate with new date span) Arabic tweets.
+All hashtags and URLs were included in the analysis.
+This method is similar to that of inverse document frequency (IDF).
+For more information on IDF, see @jones1972statistical and @robertson2004understanding.
 
 ### ICEWS Event Time Series
-Using the Integrated Crisis Early Warning System (ICEWS) developed at the
-Defense Advanced Research Project Agency, the daily events were
-scored with an intensity rating ranging from -10 to 10. Negative 
-events---such as riots and attacks---are coded with low negative numbers, while
-positive or peaceful events are coded with high positive numbers. This
-well-validated coding scheme allows for numerical quantification of
-different event types.
-
-For both the target only and the target and source data described above, time series of
-the count of all events were generated by summing the total number of events
-on each day, irrespective of ICEWS score. Similarly, time series of count
-of positive events were generated by summing the number of ICEWS events
-for each day that had an intensity rating greater than zero. Lastly,
-time series of count of negative events were generated by summing the number
-of ICEWS events for each day that had an intensity rating less than zero.
+Using the Integrated Crisis Early Warning System (ICEWS) developed at the Defense Advanced Research Project Agency, the daily events in Syria were scored with an intensity rating ranging from -10 to 10.
+Negative events, such as riots and attacks, are coded with low negative numbers while positive, peaceful events are coded with high positive numbers.
+This well-validated coding scheme allows for numerical quantification of different event types.
+For both the target only and the target and source data, time series of the count of all events were generated by summing the total number of events on each day, irrespective of ICEWS score.
+Similarly, time series of count of positive events were generated by summing the number of ICEWS events for each day that had an intensity rating greater than zero.
+Lastly, time series of count of negative events were generated by summing the number of ICEWS events for each day that had an intensity rating less than zero.
 
@@
 ### Cross-Recurrence Quantification Analysis
-We first used cross-recurrence quantification analysis
-[CRQA; @zbilut1998detecting] to investigate the temporal patterns of
-social cohesion and real-world events in Syria during Arab Spring. CRQA
-is an extension of RQA, which captures the patterns of revisited states of
-a single time series [@zbilut1992embeddings; @webber1994dynamical]. CRQA
-allows for two time series to be projected onto one another to investigate
-shared states and trajectories.
-In CRQA, we track these shared states by identifying *recurrent points*,
-or intersections of time during which two signals shared or revisited the same
-state. These shared states can be at the same time or at later points in
-the time series. We can further chart shared trajectories by examining
-the occurrences and patterns of multiple sequential recurrent points.
-
-To perform CRQA, the time series must be converted to the same
-scale, while still preserving a sampling rate that respects the native
-timescale of the system
-[cf. Nyquist frequency in signal processing; @grenander1959probability].
-Because the social cohesion and event data have different scales and values,
-we converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
-(e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
-levels of social cohesion and counts of all, positive, and negative events
-on each day. 
-We implemented CRQA using the `crqa` package [@R-crqa] for R [@R-base].
+We first used cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] to investigate the temporal patterns of social cohesion and real-world events in Syria during Arab Spring.
+As an extension of RQA, which captures the patterns of revisited states of a single time series [@zbilut1992embeddings; @webber1994dynamical], CRQA allows for two time series to be projected onto one another to investigate shared states and trajectories.
+Nonlinear analyses such as CRQA can reveal dynamics that are not captured by traditional linear methods.
+In order to perform CRQA, the time series need to be converted to the same scale, while still preserving a sampling rate that respects the native timescale of the system [cf.
+Nyquist frequency in signal processing; @grenander1959probability].
+We converted each time series (e.g., Figure 1) into deciles (e.g., Figure 2) to analyze the dynamics of different levels of social cohesion and counts of all, positive, and negative events on each day.
+In CRQA, a recurrent point is when two signals share the same state.
+These shared states can be at the same time or at later points in the time series.
 
 #### Visualization
-A cross-recurrence plot (CRP) is the visual representation of CRQA. To construct
-a cross-recurrence plot, two time series are plotted against each other on the
-$x$ and $y$ axes. At every point where they share the same state, a point
-in placed on the plot to indicate recurrence. (For categorical CRQA, this process
-is similar to the Cartesian product.)
-
-We can visually analyze these plots
-to reveal patterns of structure and recurrence. The line $y = x$ is known
-as the *line of identity*. This line falls where the time series match
-temporally. A filled line would indicate perfect in-phase synchrony between the
-two time series. See
-Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)
-for examples of RPs.
+A recurrence plot (RP) is the visual representation of CRQA.
+To construct a recurrence plot, two time series are plotted against each other on the X and Y axes, and at every point where they share the same state, and point in placed on the plot to indicate recurrence.
+Visually analyzing these plots can help reveal patterns of structure and recurrence.
+The line y = x is known as the line of identity.
+This line falls where the time series match temporally, and a filled line would indicate perfect synchrony between the two time series.
+See Figures 3-5 for examples of RPs.
 
 #### Metrics
-While visual inspections can be informative, we can derive a variety of 
-quantitative metrics from the cross-recurrence plot. Each of these metrics
-provides information into the pattern and dynamics of the new shared system
-between the original time series. These metrics are also critical for inferential
-statistics. We will focus most directly on two of these metrics: 
-*recurrence rate* and *determinism*.
-
-The percentage of recurrent points to total possible points is a metric
-called the *recurrence rate* (*RR*). This metrics gives a general description of
-how frequently the time series are sharing the same states. In the current
-study, a recurrent point would indicate that the level of social cohesion
-and frequency of events were at the same intensity.
-
+The percentage of recurrent points to total possible points is a metric called recurrence rate (RR).
+This metrics gives a general description of how frequently the time series are sharing the same states.
+In the current study, a recurrent point would indicate that the level of social cohesion and frequency of events were at the same intensity.
 Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series
-are moving together across time in a shared state. The percentage of
-recurrent points on the plot that fall along diagonal line structures 
-(i.e., two or more
-consecutive points) is a metric called *percent determinism* 
-(or simply *determinism*; *DET*). For the
-current project, a high DET would indicate that not only are the levels of
-social cohesion and frequency of events occurring at similar intensities,
-but they are doing so across consecutive days.
-
-A number of other metrics provide insight not only into the amount of structure
-between the systems but about the nature of this shared structure.
-The average length of the line structures is called *mean line* (L), which can
-be conceptualized as the average amount of time that the two time series move
-together before one or both shift states. The longest line length is called
-*max line* (*maxL*); it indicates the longest instance of being “stuck” in a
-particular state together. The total *number of lines* on the plot (*NRLINE*) 
-scales with structure: The more lines that exist, the more coupled the systems are. The
-complexity or variability of line lengths is captured by a metric called
-*entropy* (*ENTR*)---which may also be normalized by the total number of lines
-(i.e., *normalized entropy*; *rENTR*)---and indicates
-the stability and predictability of the system. When one of the signals gets
-“stuck” in a state and the other moves on to other states, this results in
-vertical line structures, which are quantified in *laminarity* (*LAM*;
-i.e., the proportion of points forming vertical line structures) 
-and trapping time (*TT*; i.e., the average length of the
-vertical trajectories). For more detail on CRQA metrics, see @R-crqa.
+These are conceptualized as shared trajectories, where the two time series are moving together across time in a shared state.
+The percentage of recurrent points that make up diagonal line structures (i.e., two or more consecutive points) is a metric called percent determinism (DET).
+For the current project, a high DET would indicate that not only are the levels of social cohesion and frequency of events occurring at similar intensities, but they are doing so across consecutive days.
+The average length of the line structures is called mean line (L).
+This can be conceptualized as the average amount of time that the two time series move together before one or both shift states.
+The longest line length is called max line (maxL).
+maxL indicates the longest instance of being “stuck” in a particular state together.
+The total number of lines is called NRLINE.
+The more lines there are, the more coordinated the system may be.
+The complexity or variability of line lengths is captured by a metric called entropy (ENTR) and entropy while accounting for the total number of lines in the plot is normalized entropy (rENTR).
+These entropy metrics help indicate the stability and predictability of the system.
+When one of the signals gets “stuck” in a state and the other moves on to other states, this results in vertical line structures.
+The proportion of points forming vertical line structures is a metric called laminarity (LAM) and the average length of the vertical trajectories is called trapping time (TT).
+For more detail on CRQA metrics, see @R-crqa.
 
 #### Parameters
-To conduct the analyses on the decile data, the parameters were set to those
-typically used in categorical CRQA: Delay was set to $0$, embedding dimension
-was set to $1$, and radius was set to $.001$ to allow for only exact recurrent
-matches. No normalization was done, and lines were considered two or more
-consecutive recurrent points. The Theiler window was set to $0$ to include
-points along the line of identity. For more details on the CRQA parameters and
-how they impact the analysis, see @R-crqa.
+To conduct the analyses on the decile data, the parameters were set to those typically used in categorical CRQA.
+Delay was set to zero, embedding dimension was set to 1, and radius was set to .001 to allow for only exact recurrent matches.
+No normalization was done, and lines were considered two or more consecutive recurrent points.
+The Theiler window was set to zero to include points along the line of identity.
+For more details on the CRQA parameters and how they impact the analysis, see @R-crqa.
 
 #### Permutation Test
-Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not have
-inherently meaningful values. As a result, CRQA is best used as a relative
-metric---that is, comparing the CRQA values across conditions or subsets
-of the data. Typically, meaningful differences between values are determined with
-traditional inferential statistics. While this may not be a problem for 
-experimentally derived datasets, it can pose a barrier to researchers using
-small-$n$ data or conducting data-informed case studies.
-
-For CRQA, this can be addressed using *permutation tests*.
-Similar to more established methods of statistical significance in CRQA research
-[which create surrogate time series; e.g., @paxton2017interpersonal],
-the permutation test approach to significance testing allows the researcher
-to use a time series as its own baseline by testing whether the *structure*
-of the unfolding events of the time series---rather than the *raw frequency* of the 
-events within the time series---cohere together more than would be expected
-by chance. A permutation test is similar to
-bootstrapping, except that the sampling of observations is done without
-replacement. In this approach, we simply create a large number of permutations
-of the original time series (i.e., breaking up the dependency across time points but
-preserving the frequencies of the events), conduct CRQA for each of those
-permutations, and then examine whether the real time series' CRQA metrics
-exceed those that we would expect to see by chance. The proportion of times that
-the real time series' values exceeds the surrogate time series' values can
-be interpreted as the alpha criterion to determine significance. 
-For more information on permutation
-tests, see @good2013permutation.
-
-Using the real deciles of social cohesion, count of all events,
-count of positive events, and count of negative events, we conducted a series
-of permutation tests 
-(one for the comparison between social cohesion and each type of event count)
-to determine statistical difference from chance for each CRQA metric.
-Using the `sample` function in base R [@R-base], $1000$ permuted time series were
-created for each of the real time series.  
-CRQA was then run $1000$ times for social cohesion and count of all
-events, social cohesion and count of positive events, and social cohesion and
-count of negative events using the permuted time series. This resulted in
-$1000$ results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles
-of the metrics from the permuted CRQ analyses. Given that a permutation test
-is similar to bootstrapping but does not include replacement, all points were
-included in each CRQA analysis, leaving RR constant across all permutations. Thus,
-RR is not included in the inferential tests.
+Using the deciled, real time series of social cohesion, count of all events, count of positive events, and count of negative events, a permutation test was done to determine statistical difference from chance for each CRQA metric.
+Using the sample function in base R [@R-base], 1000 permuted time series were created for each of the real time series.
+A permutation test is similar to bootstrapping, except that the sampling of observations is done without replacement.
+CRQA was then run 1000 times for social cohesion and count of all events, social cohesion and count of positive events, and social cohesion and count of negative events using the permuted time series.
+This resulted in 1000 results for each of the CRQA metrics for each combination of time series.
+Statistical significance from chance was set at the 95th and 99th percentiles of the metrics from the permuted CRQ analyses.
+Given that a permutation test is similar to bootstrapping but does not include replacement, all points were included in each CRQA analysis, leaving RR the same across all analyses.
+Thus, RR is not included in the inferential tests.
+For more information on permutation tests, see @good2013permutation.
 
 ### Windowed Cross-Recurrence Quantification Analysis
-We used windowed cross-recurrence quantification analysis
-[WCRQA; @webber2005recurrence] to further investigate the evolution of the
-temporal dynamics of social cohesion and real-world events. In this analysis,
-a smaller “window” of time points is used to calculate CRQA and capture more
-fine-grained dynamics of two time series. The window remains the same size and
-“slides” diagonally up the line of identity. The changes in the CRQA metrics
-across the windows can reveal changes in dynamics that can then be linked to
-external, real-world events. 
-We implemented WCRQA using the `crqa` package [@R-crqa] for R [@R-base].
+We used windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence] to further investigate the evolution of the temporal dynamics of social cohesion and real-world events.
+In this analysis, a smaller “window” of time points is used to calculate CRQA and capture more fine-grain dynamics of two time series.
+The window remains the same size and “slides” diagonally up the line of identity.
+The changes in the CRQA metrics across the windows can reveal changes in dynamics that can then be linked to external, real-world events.
 
 #### Metrics
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
-respective window. These metrics can then be plotted as a time series to
-visualize their evolution over time. For these analyses, we decided to
-focus on recurrence rate and determinism.
+Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each respective window.
+These metrics can then be plotted as a time series to visualize their evolution over time.
+For these analyses, we decided to visualize recurrence rate and determinism.
 
 #### Parameters
-In addition to the CRQA parameters, two other parameters are required when
-conducting WCRQA. First, the *window size*
-will determine how many observations are used in each CRQA analysis. We
-conducted WCRQA with a window size of $14$ to investigate the dynamics over
-two weeks and allow for the capture of more structure and thus a more
-meaningful interpretation of DET.
-
-The second parameter to be chosen is a *window step size*. 
-Window step size is how far the window moves up the line of identity
-before conducting CRQA again. We chose $1$ for the step size to understand
-how the metrics evolve from day to day.
-
-All other CRQA metrics remained the same as those previously noted.
+In addition to the CRQA parameters, two other parameters are required when conducting WCRQA.
+First, a window size must be decided on.
+The window size will determine how many observations are used in each CRQA analysis.
+We conducted WCRQA with a window size of 14 to investigate the dynamics over two weeks and allow for the capture of more structure and thus a more meaningful interpretation of DET.
+The second parameter to be chosen is a step size.
+Window step size is how far the window moves up the line of identity before conducting CRQA again.
+We chose 1 for the step size to understand how the metrics evolve from day to day.
+All other CRQA metrics remained the same as previously noted.
 
 #### Visualization
-To visualize WCRQA, the resulting metrics from each window can be plotted
-as a time series. This allows for visual interpretation of the pattern or
-fluctuation of the metrics across time. These dynamics can then be linked
-to other external events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
-\@ref(fig:plot-wcrqa-source-targ-all) for examples.
+To visualize WCRQA, the resulting metrics from each window can be plotted as a time series.
+This allows for visual interpretation of the pattern or fluctuation of the metrics across time.
+These dynamics can then be linked to other external events.
+See Figures 9-14 and 16-21 for examples.
 
 #### Permutation Test
-To visualize the differences in the WCRQA metrics from those obtained by
-chance, a permutation test was done to set upper and lower bounds for the
-95th and 99th percentiles. Using a sample size of 14, $1000$ permuted
-time series were generated without replacement for each real time series. The
-upper and lower 95th and 99th percentiles were set based on the distribution
-of the permuted WCRQA metrics.
+To visualize the differences in the WCRQA metrics from those obtained by chance, a permutation test was done to set upper and lower bounds for the 95th and 99th percentiles.
+Using a sample size of 14, one-thousand permuted time series were generated without replacement for each real time series.
+The upper and lower 95th and 99th percentiles were set based on the distribution of CRQA metrics from these one-thousand CRQ analyses.
 
@@
 
-# run primary crqa analysis
+# run primary crq analysis
 source('./scripts/primary-analyses/02_crqa.R')
@@
 # read in metric names
-metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", 
-                      header = FALSE)[-2,-1])
+metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-2,-1])
 
 # read in metrics from crq analyses (target filtered)
-metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", 
-                               header = FALSE)[-1,-1])
-metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", 
-                               header = FALSE)[-1,-1])
-metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", 
-                               header = FALSE)[-1,-1])
+metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
-# read in significance from permutation tests (target filtered)
-sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", 
-                           header = FALSE)[-1,-1])
-sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", 
-                           header = FALSE)[-1,-1])
-sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", 
-                           header = FALSE)[-1,-1])
+# read in signficiance from permutation tests (target filtered)
+sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
 # read in metrics from crq analyses (source and target filtered)
-metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv",
-                                      header = FALSE)[-1,-1])
-metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv",
-                                      header = FALSE)[-1,-1])
-metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv",
-                                      header = FALSE)[-1,-1])
+metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv", header = FALSE)[-1,-1])
+metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv", header = FALSE)[-1,-1])
+metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv", header = FALSE)[-1,-1])
 
-# read in significance from permutation tests (source and target filtered)
-sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", 
-                                  header = FALSE)[-1,-1])
-sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", 
-                                  header = FALSE)[-1,-1])
-sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", 
-                                  header = FALSE)[-1,-1])
+# read in signficiance from permutation tests (source and target filtered)
+sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv", header = FALSE)[-1,-1])
+sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv", header = FALSE)[-1,-1])
+sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv", header = FALSE)[-1,-1])
 
@@
 ## Cross-Recurrence Quantification Analysis
+CRQA was performed using the crqa package [@R-crqa] for R [@R-base]. We conducted a permutation test to check for statistical difference from chance for all analyses and metrics.
 
 ### Syria as Target
-A permutation test for the CRQA of social cohesion and count of all events 
-found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all);
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
-count of positive events found no statistical difference from chance for any 
-of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
-\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
-count of negative events found a statistical difference from chance for DET, 
-NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
-\@ref(fig:plot-rp-targ-neg); \autoref{table-1}). Looking at the recurrence 
-plots there appears, to be a shift in dynamics around the 36th observation 
-which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
+All other metrics were non-significant (Figure 3; Table 1).
+A permutation test for the CRQA of social cohesion and count of positive events found no statistical difference from chance for any of the metrics (Figure 4; Table 1).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and TT.
+All other metrics were non-significant (Figure 5; Table 1).
+Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
 
@@
 # build table
-pander(target_results, caption = "\\label{table-1}CRQA results for target only data.")
+pander(target_results, caption = "CRQA results for target only data.")
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
-A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR.
-All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
+All other metrics were non-significant (Figure 6; Table 2).
+A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for DET, NRLINE, maxL, and LAM (Figure 7; Table 2).
+A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, maxL, L, and ENTR.
+All other metrics were non-significant (Figure 8; Table 2).
 Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.
@@
 # build table
-pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.")
+pander(source_target_results, caption = "CRQA results for source and target data.")
 
@@
 ## Windowed Cross-Recurrence Quantification Analysis
-```{r primary-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide', include = FALSE}
+```{r primary-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
 
@@
 
-WCRQA was performed using the crqa package [@R-crqa] for R [@R-base]. Permutation tests
-were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
-the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)),
-the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
-represented by horizontal orange lines. The trend lines are plotted in blue.
+WCRQA was performed using the crqa package [@R-crqa] for R [@R-base].
+Permutation tests were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles.
+In the plots (see Figures 9-14 and 16-21), the 95th percentiles are represented by horizontal red lines and the 99th percentiles are represented by horizontal orange lines.
+The trend lines are plotted in blue.
 
@@
 
-```{r plot-wcrqa-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from target filtered data.', out.extra='angle=90'}
+```{r plot-RR-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.'}
 
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all.png")
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_RR.png")
+
+```
+
+```{r plot-DET-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all_DET.png")
+
+```
+
+```{r plot-RR-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_neg_DET.png")
 
@@
 
-For social cohesion and count of all events, there is a consistent period 
-of above chance recurrence rate from the 7th-12th and 36th-47th window 
-(Figure \@ref(fig:plot-wcrqa-targ-all)). Determinism is largely above chance 
-from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)). For
-social cohesion and count of positive events there is a downward trend in RR 
-as the window moves with largly above chance RR from the 1st-18th and 
-32nd-45th windows. Determinism was at or above chance for the 8th-17th, 
-32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)). 
-For social cohesion and count of negative events, recurrence rate stays above
-or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
-is above or nearly above chance in the 1st and 2nd windows, with short intermittent 
-peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of all events, there is a consistent period of above chance recurrence rate from the 31st through 48th window (Figure 9).
+Determinism is also almost consistently above chance from the 39th window onwards (Figure 10).
+For social cohesion and count of positive events there is a downward trend in RR as the window moves (Figure 11) and determinism stays almost entirely within chance across windows (Figure 12).
+For social cohesion and count of negative events, recurrence rate stay above or almost above chance from the 36th through the 48th window (Figure 13) and determinism is also above or nearly above chance from the 38th through 43rd window (Figure 14).
 
@@
 
-```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
+```{r plot-RR-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.'}
 
 # call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_RR.png")
 
@@
 
-For social cohesion and count of all events, there is a consistent period of
-above or nearly above chance determinism from the 7th-13th and 26th-47th 
-windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). Determinism also 
-shows above or nearly above chance values in windows 7th-17th and short, 
-intermittent peaks between the 34th and 61st windows (Figure 
-\@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and count of 
-positive events, there is a downward trend in RR as the window moves with 
-largely above chance values in the first 20 windows and the 32nd-45th windows. 
-Determinism stays largely within chance with the exception of windows 13 
-through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion
-and negative events, there appears to be an extended time period where RR 
-(32nd-47th windows) and DET (35th-39th windows) were above of nearly above 
-chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
-May 3rd, 2012 to May 14th, 2012.
+```{r plot-DET-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all_DET.png")
+
+```
+
+```{r plot-RR-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_RR.png")
+
+```
+
+```{r plot-DET-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_pos_DET.png")
+
+```
+
+```{r plot-RR-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_RR.png")
+
+```
+
+```{r plot-DET-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_neg_DET.png")
+
+```
+
+For social cohesion and count of all events, there is a consistent period of above or nearly above chance determinism from the 26th through 46th window (Figure 16).
+Determinism also shows above or nearly above chance values in window spans 11-16 and 35-37 (Figure 17).
+For social cohesion and count of positive events, there is a downward trend in RR as the window moves (Figure 18) and determinism stays largely within chance with the exception of windows 13-19.
+For social cohesion and negative events, there appears to be an extended time period where RR (Figure 11) and DET (Figure 12) were greater than chance, from the 35th through 46th windows.
+These windows span from May 3rd, 2012 to May 14th, 2012.
 
 # Discussion
-In the present study, we investigated the dynamics of real-world events
-and online communication on Twitter in Syria during Arab Spring. We examined
-how social mobilization both virtually and physically evolve over time in
-tandem. Prior to now, the extent to which virtual mobilization on social
-media platforms such as Twitter has been largely unexplored. Using the
-nonlinear methods cross-recurrence quantification analysis and windowed
-cross-recurrence quantification analysis, we investigated the theory that
-virtual mobilization is increasingly reflective of real-world events
-during times of strife.
+In the present study, we investigated the dynamics of real-world events and online communication on Twitter in Syria during Arab Spring.
+We examined how social mobilization both virtually and physically evolve over time in tandem.
+Prior to now, the extent to which virtual mobilization on social media platforms such as Twitter has been largely unexplored.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigated the theory that virtual mobilization is increasingly reflective of real-world events during times of strife.
 
@@
 ### Syria as Target
-The significant result of DET for social cohesion and both the all events
-and negative events time series confirms our hypothesis, that increased
-salience of events is reflected in social cohesion on Twitter. The frequency
-of all events and of negative events thus result in a significant number
-of shared trajectories that are statistically different from chance. The
-non-significant results for all metrics for positive event count also
-confirm our hypothesis, and gives support to the theory that positive events
-are less coupled to social cohesion than the more salient, negative events
-during times of turmoil. The inevitable increased salience of event
-frequency and event violence thus leads to increased coupling with Twitter
-social cohesion.
+The significant result of DET for social cohesion and both the all events and negative events time series confirms our hypothesis, that increased salience of events is reflected in social cohesion on Twitter.
+The frequency of all events and of negative events thus result in a significant number of shared trajectories that are statistically different from chance.
+The non-significant results for all metrics for positive event count also confirm our hypothesis, and gives support to the theory that positive events are less coupled to social cohesion than the more salient, negative events during times of turmoil.
+The inevitable increased salience of event frequency and event violence thus leads to increased coupling with Twitter social cohesion.
 
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the dataset increased
-in size by 1,690 samples. These additional observations are times where
-Syria initiated an event with another country. Events initiated by Syria
-but directed internally within the country were already captured by the
-target only filtering. The increase in coupling between positive events
-and social cohesion is thus due to the inclusion of these externally
-directed events. Though CRQA metrics for count of all and count of
-negative events with social cohesion were largely unaffected, count of
-positive events and social cohesion showed significant levels of
-determinism, number of lines, max line length, and laminarity that were
-not present in the target filtered data. Given that the Syria during
-this time was still under Authoritarian rule, the government may have
-been initiating more positive external events to prevent intervention
-by other countries or try to cover up what was happening internally.
-We believe that the increased coupling of positive events is thus not
-reflective of actual social cohesion, but happened by chance. The
-inflation of the number of positive events when including source
-observations is causing increased coupling, but it is more likely that
-the Twitter users were using the platform to raise awareness of the
-violent, internal events that were being inflicted on them by their
-government officials and armies and not reporting on the positive
-external events that did not directly affect them or their safety.
-Further research should explore the semantic content of this tweet
-corpus to determine what the socially cohered language was focused on.
-By visual inspection of the recurrence plots (RPs;
-Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)),
-there appears to be a shift in the dynamics of these systems around
-observation 35, or May 3rd, 2012. To further investigate these local
-dynamics, we performed a sliding window technique known as windowed
-cross-recurrence quantification analysis (WCRQA).
+By adding Syria as a source in the data filtering, the dataset increased in size by 1,690 samples.
+These additional observations are times where Syria initiated an event with another country.
+Events initiated by Syria but directed internally within the country were already captured by the target only filtering.
+The increase in coupling between positive events and social cohesion is thus due to the inclusion of these externally directed events.
+Though CRQA metrics for count of all and count of negative events with social cohesion were largely unaffected, count of positive events and social cohesion showed significant levels of determinism, number of lines, max line length, and laminarity that were not present in the target filtered data.
+Given that the Syria during this time was still under Authoritarian rule, the government may have been initiating more positive external events to prevent intervention by other countries or try to cover up what was happening internally.
+We believe that the increased coupling of positive events is thus not reflective of actual social cohesion, but happened by chance.
+The inflation of the number of positive events when including source observations is causing increased coupling, but it is more likely that the Twitter users were using the platform to raise awareness of the violent, internal events that were being inflicted on them by their government officials and armies and not reporting on the positive external events that did not directly affect them or their safety.
+Further research should explore the semantic content of this tweet corpus to determine what the socially cohered language was focused on.
+By visual inspection of the recurrence plots (RPs; Figures 3-8), there appears to be a shift in the dynamics of these systems around observation 35, or May 3rd, 2012.
+To further investigate these local dynamics, we performed a sliding window technique known as windowed cross-recurrence quantification analysis (WCRQA).
 
@@
 ### Syria as Target
-The time period of differing dynamics, from observation 38 through 43,
-appears to be captured by WCRQA of social cohesion and count of negative
-events for both RR and DET (Figure \@ref(fig:plot-wcrqa-targ-all)). The
-amount of recurrence and determinism for these periods almost consistently
-lie above chance, suggesting that the intensity of negative events coincide
-with the degree of social cohesion found on Twitter, and that these states
-carry across multiple days in a way that is different from that of chance.
-
-The above-chance levels of determinism and recurrence rate are demonstrating
-the coupling of social cohesion and counts of all and negative events during
-times of strife. We can see this string of highly violent events reflected
-in the mode ICEWS event for each day (Figure \@ref(fig:plot-mode-event)),
-where from May 1st, 2020 to May 15th, 2020, the most frequently occurring
-event was almost consistently -10, the most violent event in the coding
-system. These dates directly correlate with the above chance RR and DET
-metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during
-this time period, DET was entirely within chance (Figure
-\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
-positive events are seemingly not coupled with the social cohesion on Twitter
-during civil uprisings during the Arab Spring.
+The time period of differing dynamics, from observation 38 through 43, appears to be captured by WCRQA of social cohesion and count of negative events for both RR (Figure 13) and DET (Figure 14).
+The amount of recurrence and determinism for these periods almost consistently lie above chance, suggesting that the intensity of negative events coincide with the degree of social cohesion found on Twitter, and that these states carry across multiple days in a way that is different from that of chance.
+The above-chance levels of determinism and recurrence rate are demonstrating the coupling of social cohesion and counts of all and negative events during times of strife.
+We can see this string of highly violent events reflected in the mode ICEWS event for each day (Figure 15), where from May 1st, 2020 to May 15th, 2020, the most frequently occurring event was almost consistently -10, the most violent event in the coding system.
+These dates directly correlate with the above chance RR and DET metrics for the WCRQA of social cohesion and count of negative events.
+Furthermore, for WCRQA of social cohesion and positive event count during this time period, DET (Figure 12) was entirely within chance.
+This supports our hypothesis, as the positive events are seemingly not coupled with the social cohesion on Twitter during civil uprisings during the Arab Spring.
 
 ### Syria as Source and Target
-WCRQA of recurrence rate on the source and target filtered data remained
-largely the same for count of all events and social cohesion, suggesting
-that large numbers on a given day will be reflective of increased levels
-of social cohesion. Determinism showed more frequent above-chance metrics
-for windows 39 and up, suggesting that the inclusion of externally
-directed events lead to higher event counts during these days and then
-was more reflective of the level of social cohesion on Twitter. WCRQA for
-count of positive events and social cohesion remained largely the same for
-RR and DET as the source only data. This again seems to support the idea
-that these two aren't actually coupled, but rather that the inflation of
-the positive counts lead to a spurious relationship. Count of negative
-events and social cohesion also showed similar trends for RR and DET,
-again attesting to the theory that negative events were coupled to social
-cohesion on Twitter while positive events happened by chance.
+WCRQA of recurrence rate on the source and target filtered data remained largely the same for count of all events and social cohesion, suggesting that large numbers on a given day will be reflective of increased levels of social cohesion.
+Determinism showed more frequent above-chance metrics for windows 39 and up, suggesting that the inclusion of externally directed events lead to higher event counts during these days and then was more reflective of the level of social cohesion on Twitter.
+WCRQA for count of positive events and social cohesion remained largely the same for RR and DET as the source only data.
+This again seems to support the idea that these two aren't actually coupled, but rather that the inflation of the positive counts lead to a spurious relationship.
+Count of negative events and social cohesion also showed similar trends for RR and DET, again attesting to the theory that negative events were coupled to social cohesion on Twitter while positive events happened by chance.
 
 ## Conclusion
-Considering the invasiveness of social media in our everyday lives, it is
-inevitable that individuals involved in real-world social mobilization have
-utilized these platforms to their advantage. If consistent across other civil
-wars, these results have serious implications for monitoring global
-movements. While traditional media in regions of authoritarian rule are
-often biased, the self-organized nature of Twitter poses a new avenue to gain
-insight into truths about up-risings and social mobilization. By
-conceptualizing Twitter and real-world events as two components of an
-inextricably linked dynamical system, the levels of social cohesion within the
-virtual platform could be monitored for fluctuations indicating global shifts
-in power and peace. Social media mobilization can thus help alert us to
-real-world mobilization not communicated in mainstream media and allow for 
-faster intervention.
+Considering the invasiveness of social media in our everyday lives, it is inevitable that individuals involved in real-world social mobilization have utilized these platforms to their advantage.
+If consistent across other civil wars, these results have serious implications for monitoring global movements.
+While traditional media in regions of authoritarian rule are often biased, the self-organized nature of Twitter poses a new avenue to gain insight into truths about up-risings and social mobilization.
+By conceptualizing Twitter and real-world events as two components of an inextricably linked dynamical system, the levels of social cohesion within the virtual platform could be monitored for fluctuations indicating global shifts in power and peace.
+Social media mobilization can thus help alert us to real-world mobilization not communicated in mainstream media and allow for faster intervention.
 

### 2020-05-31 manuscript.Rmd
Add implications section

--- 2020-05-29 manuscript.Rmd
@@
 
+## Implications
+
+### Implications for Methodology
+
+Nonlinear methods have been transformative for a variety of research
+areas [including psychology, @coco2014cross]. One of the goals in the
+present work was to introduce variants of one kind of nonlinear
+method---specifically, recurrence quantification analysis---to
+this research area. While a number of excellent guides can provide
+detailed explanations of the methods and their statistical underpinnings 
+[e.g., @riley2005tutorials; @webber1994dynamical; @webber2005recurrence],
+one of the most important considerations that should be briefly
+summarized here is about data.
+
+Nonlinear methods---including recurrence-based analyses---require
+time series data. This requires repeated observations of the behavior
+at interest, preferably at a frequency that provides information 
+about timing at a temporal resolution that allows the researcher to 
+make observations about interesting variations over time. While
+this is easily controlled by scientists who conduct experimental
+research, it can be more difficult for scientists who rely on
+trace data or naturally occurring data. However, where possible,
+we recommend political scientists work to expand efforts for
+improving the temporal granularity of the data. One possible
+means of achieving this may be through collaborative efforts
+like the Open Event Data Alliance [@schrodt2014three].
+
+### Implications for Theory
+
+(This would be where Leah should update her part.)
+
 ## Conclusion

### 2020-06-01 manuscript.Rmd
Edits to intro

@@
 These mass movements would not have been possible without
-efficient large-scale coordination, both physically and virtually on social
-media platforms. Along with Facebook, Twitter has been credited as essential 
-to the Arab Spring---both for protesters (as a means to coordinate with one 
-another and to communicate with the world) and for the government response
-(to monitor and track protestors to crack down on dissent) [@comninos2011twitter]. 
-The events of Arab Spring have been
-thoroughly discussed within the political science literature
+efficient large-scale coordination, both physically on the ground and virtually 
+on social media platforms. Along with Facebook, Twitter has been credited as 
+essential to the Arab Spring---both for protesters (as a means to coordinate 
+with one another and to communicate with the world) and for the government 
+response (to monitor and track protestors to crack down on dissent) 
+[@comninos2011twitter]. The events of Arab Spring have been thoroughly 
+discussed within the political science literature 
 [e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
-the direct coupling between Syrian Twitter use and international action
-has not been investigated.
+the direct *coupling* between Syrian Twitter cohesion and international action
+coordination has not been investigated.
 
@@
 massive social-level changes [@michel2011quantitative; @fusaroli2015timescales]. 
-This kind of massive online social cohesion can lead to real-world
+This kind of widespread online social cohesion can lead to real-world
 social change.
@@
 
-Social media platforms provide one way of enabling this kind of online social
+Social media platforms provide one way to enable this kind of online social
 cohesion by offering distributed information-gathering and real-time information
@@
 data---it is critical to find appropriate analysis tools that can
-identify the complex interconnections.
-Traditional linear analyses have led to many notable discoveries in the
-domains of psychology and political science, but time series data pose
-problems that are not easily overcome with these methods. Events have
-historically been conceptualized as linear chains of smaller, sequential
-events with one occurrence leading to the next. 
+identify the complex interconnections. Traditional linear analyses have led to 
+many notable discoveries in the domains of psychology and political science, 
+but time series data pose problems that are not easily overcome with these 
+methods. Events have historically been conceptualized as linear chains of 
+smaller, sequential events with one occurrence leading to the next. 
 Certain kinds of data are relatively well-suited to these analyses,
 but messy, complex, variable data from real-world events can pose
-challenges from overpowered samples to violation of underlying
+challenges, from overpowered samples to violation of underlying
 statistical assumptions [@paxton2017finding].
@@
 more global behaviors that are larger than the sum of the parts
-[@turvey2018lectures]. Linear analyses flatten these nonlinear patterns in 
-time series data and ignore the variability
-that is fundamental to these systems and their evolution over time. 
-However, when analyzed as dynamical systems, many phenomena
+[@turvey2018lectures]. Linear analyses flatten time series data and ignore 
+the variability that is fundamental to these systems and their evolution over 
+time. However, when analyzed as dynamical systems, many phenomena
 exhibit new nonlinear patterns that were formerly overlooked. 

### 2020-06-01 manuscript.tex
Edits to intro

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
 \PassOptionsToPackage{hyphens}{url}
 %
-\documentclass[
-  english,
-  man]{apa6}
+\documentclass[english,man]{apa6}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
   \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
-% Use upquote if available, for straight quotes in verbatim environments
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
 \IfFileExists{parskip.sty}{%
@@
 \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{hyperref}
 \hypersetup{
             pdftitle={Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring},
-  pdflang={en-EN},
             pdfkeywords={social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage{longtable,booktabs}
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
+% Fix footnotes in tables (requires footnote package)
+\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{longtable}}{}
 \usepackage{graphicx,grffile}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+
+% set default figure placement to htbp
 \makeatletter
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+
 % Manuscript styling
@@
 \usepackage{float}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
-\else
-  \usepackage[shorthands=off,main=english]{babel}
 \fi
@@
 These mass movements would not have been possible without
-efficient large-scale coordination, both physically and virtually on social
-media platforms. Along with Facebook, Twitter has been credited as essential
-to the Arab Spring---both for protesters (as a means to coordinate with one
-another and to communicate with the world) and for the government response
-(to monitor and track protestors to crack down on dissent) (Comninos, 2011).
-The events of Arab Spring have been
-thoroughly discussed within the political science literature
+efficient large-scale coordination, both physically on the ground and virtually
+on social media platforms. Along with Facebook, Twitter has been credited as
+essential to the Arab Spring---both for protesters (as a means to coordinate
+with one another and to communicate with the world) and for the government
+response (to monitor and track protestors to crack down on dissent)
+(Comninos, 2011). The events of Arab Spring have been thoroughly
+discussed within the political science literature
 (e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
-the direct coupling between Syrian Twitter use and international action
-has not been investigated.
+the direct \emph{coupling} between Syrian Twitter cohesion and international action
+coordination has not been investigated.
 
@@
 massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
-This kind of massive online social cohesion can lead to real-world
+This kind of widespread online social cohesion can lead to real-world
 social change.
@@
 data---it is critical to find appropriate analysis tools that can
-identify the complex interconnections.
-Traditional linear analyses have led to many notable discoveries in the
-domains of psychology and political science, but time series data pose
-problems that are not easily overcome with these methods. Events have
-historically been conceptualized as linear chains of smaller, sequential
-events with one occurrence leading to the next.
+identify the complex interconnections. Traditional linear analyses have led to
+many notable discoveries in the domains of psychology and political science,
+but time series data pose problems that are not easily overcome with these
+methods. Events have historically been conceptualized as linear chains of
+smaller, sequential events with one occurrence leading to the next.
 Certain kinds of data are relatively well-suited to these analyses,
 but messy, complex, variable data from real-world events can pose
-challenges from overpowered samples to violation of underlying
+challenges, from overpowered samples to violation of underlying
 statistical assumptions (Paxton \& Griffiths, 2017).
@@
 more global behaviors that are larger than the sum of the parts
-(Turvey, 2018). Linear analyses flatten these nonlinear patterns in
-time series data and ignore the variability
-that is fundamental to these systems and their evolution over time.
-However, when analyzed as dynamical systems, many phenomena
+(Turvey, 2018). Linear analyses flatten time series data and ignore
+the variability that is fundamental to these systems and their evolution over
+time. However, when analyzed as dynamical systems, many phenomena
 exhibit new nonlinear patterns that were formerly overlooked.
@@
 \endhead
-DET & 25.246 & 0.001 & *** & 21.803 & 0.074 & . & 22.623 & 0.023 & *\tabularnewline
-NRLINE & 75.000 & 0.000 & *** & 61.000 & 0.121 & & 64.000 & 0.038 & *\tabularnewline
-maxL & 3.000 & 0.423 & & 4.000 & 0.037 & * & 3.000 & 0.370 &\tabularnewline
-L & 2.053 & 0.911 & & 2.180 & 0.079 & . & 2.156 & 0.155 &\tabularnewline
-ENTR & 0.208 & 0.901 & & 0.499 & 0.064 & . & 0.433 & 0.165 &\tabularnewline
-rENTR & 0.300 & 0.802 & & 0.455 & 0.305 & & 0.625 & 0.032 & *\tabularnewline
-LAM & 34.262 & 0.003 & ** & 30.328 & 0.016 & * & 24.098 & 0.113 &\tabularnewline
-TT & 2.247 & 0.107 & & 2.176 & 0.165 & & 2.100 & 0.360 &\tabularnewline
+DET & 25.246 & 0.001 & *** & 21.148 & 0.127 & & 22.623 & 0.023 & *\tabularnewline
+NRLINE & 75.000 & 0.000 & *** & 59.000 & 0.193 & & 64.000 & 0.038 & *\tabularnewline
+maxL & 3.000 & 0.423 & & 4.000 & 0.036 & * & 3.000 & 0.370 &\tabularnewline
+L & 2.053 & 0.911 & & 2.186 & 0.060 & . & 2.156 & 0.155 &\tabularnewline
+ENTR & 0.208 & 0.901 & & 0.510 & 0.047 & * & 0.433 & 0.165 &\tabularnewline
+rENTR & 0.300 & 0.802 & & 0.464 & 0.255 & & 0.625 & 0.032 & *\tabularnewline
+LAM & 34.262 & 0.003 & ** & 27.705 & 0.035 & * & 24.098 & 0.113 &\tabularnewline
+TT & 2.247 & 0.107 & & 2.195 & 0.156 & & 2.100 & 0.360 &\tabularnewline
 \bottomrule
@@
 of those tweets can directly speak to that explanation.
+
+\hypertarget{implications}{%
+\subsection{Implications}\label{implications}}
+
+\hypertarget{implications-for-methodology}{%
+\subsubsection{Implications for Methodology}\label{implications-for-methodology}}
+
+Nonlinear methods have been transformative for a variety of research
+areas (including psychology, Coco \& Dale, 2014). One of the goals in the
+present work was to introduce variants of one kind of nonlinear
+method---specifically, recurrence quantification analysis---to
+this research area. While a number of excellent guides can provide
+detailed explanations of the methods and their statistical underpinnings
+(e.g., Riley \& Van Orden, 2005; Webber Jr \& Zbilut, 1994, 2005),
+one of the most important considerations that should be briefly
+summarized here is about data.
+
+Nonlinear methods---including recurrence-based analyses---require
+time series data. This requires repeated observations of the behavior
+at interest, preferably at a frequency that provides information
+about timing at a temporal resolution that allows the researcher to
+make observations about interesting variations over time. While
+this is easily controlled by scientists who conduct experimental
+research, it can be more difficult for scientists who rely on
+trace data or naturally occurring data. However, where possible,
+we recommend political scientists work to expand efforts for
+improving the temporal granularity of the data. One possible
+means of achieving this may be through collaborative efforts
+like the Open Event Data Alliance (Schrodt, Beieler, \& Idris, 2014).
+
+\hypertarget{implications-for-theory}{%
+\subsubsection{Implications for Theory}\label{implications-for-theory}}
+
+(This would be where Leah should update her part.)
 
@@
 
+\leavevmode\hypertarget{ref-coco2014cross}{}%
+Coco, M. I., \& Dale, R. (2014). Cross-recurrence quantification analysis of categorical and continuous time series: An r package. \emph{Frontiers in Psychology}, \emph{5}, 510.
+
 \leavevmode\hypertarget{ref-R-crqa}{}%
@@
 
+\leavevmode\hypertarget{ref-riley2005tutorials}{}%
+Riley, M. A., \& Van Orden, G. C. (Eds.). (2005). \emph{Tutorials in contemporary nonlinear methods for the behavioral sciences}. National Science Foundation.
+
 \leavevmode\hypertarget{ref-robertson2004understanding}{}%
@@
 
+\leavevmode\hypertarget{ref-schrodt2014three}{}%
+Schrodt, P.
+A., Beieler, J., \& Idris, M.
+(2014).
+Three's a charm?: Open event data coding with EL:DIABLO, PETRARCH, and the Open Event Data Alliance.
+In \emph{International studies association annual convention}.
+
 \leavevmode\hypertarget{ref-spaaij2014sports}{}%
@@
 \leavevmode\hypertarget{ref-vicari2013public}{}%
-Vicari, S. (2013). Public reasoning around social contention: A case study of twitter use in the italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
+Vicari, S. (2013). Public reasoning around social contention: A case study of Twitter use in the Italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
 

### 2020-06-01 manuscript.Rmd
Edits to methods

@@
 The social cohesion calculation was performed on the tweet corpus
-containing (recalculate with new date span) English and (recalculate with
-new date span) Arabic tweets. All hashtags and URLs were included in the
-analysis.
+containing both English and Arabic tweets. All hashtags and URLs were included 
+in the analysis.
 
@@
 quantitative metrics from the cross-recurrence plot. Each of these metrics
-provides information into the pattern and dynamics of the new shared system
-between the original time series. These metrics are also critical for inferential
+provides information into the patterns and dynamics of the new shared system. 
+These metrics are also critical for inferential
 statistics. We will focus most directly on two of these metrics: 
@@
 The total *number of lines* on the plot (*NRLINE*) 
-scales with structure: The more lines that exist, the more coupled the systems are. The
-complexity or variability of line lengths is captured by a metric called
-*entropy* (*ENTR*)---which may also be normalized by the total number of lines
-(i.e., *normalized entropy*; *rENTR*)---and indicates
+scales with structure: The more lines that exist, the more coupled the two 
+systems are. The complexity or variability of line lengths is captured by a 
+metric called *entropy* (*ENTR*)---which may also be normalized by the total 
+number of lines (i.e., *normalized entropy*; *rENTR*)---and indicates
 the stability and predictability of the system. When one of the signals gets
@@
 i.e., the proportion of points forming vertical line structures) 
-and trapping time (*TT*; i.e., the average length of the
+and *trapping time* (*TT*; i.e., the average length of the
 vertical trajectories). For more detail on CRQA metrics, see @R-crqa.
@@
 Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
-respective window. These metrics can then be plotted as a time series to
-visualize their evolution over time. For these analyses, we decided to
-focus on recurrence rate and determinism.
+respective window. For these analyses, we decided to focus on recurrence rate 
+and determinism.
 

### 2020-06-01 manuscript.tex
Edits to methods

@@
 The social cohesion calculation was performed on the tweet corpus
-containing (recalculate with new date span) English and (recalculate with
-new date span) Arabic tweets. All hashtags and URLs were included in the
-analysis.
+containing both English and Arabic tweets. All hashtags and URLs were included
+in the analysis.
 
@@
 quantitative metrics from the cross-recurrence plot. Each of these metrics
-provides information into the pattern and dynamics of the new shared system
-between the original time series. These metrics are also critical for inferential
+provides information into the patterns and dynamics of the new shared system.
+These metrics are also critical for inferential
 statistics. We will focus most directly on two of these metrics:
@@
 The total \emph{number of lines} on the plot (\emph{NRLINE})
-scales with structure: The more lines that exist, the more coupled the systems are. The
-complexity or variability of line lengths is captured by a metric called
-\emph{entropy} (\emph{ENTR})---which may also be normalized by the total number of lines
-(i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
+scales with structure: The more lines that exist, the more coupled the two
+systems are. The complexity or variability of line lengths is captured by a
+metric called \emph{entropy} (\emph{ENTR})---which may also be normalized by the total
+number of lines (i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
 the stability and predictability of the system. When one of the signals gets
@@
 i.e., the proportion of points forming vertical line structures)
-and trapping time (\emph{TT}; i.e., the average length of the
+and \emph{trapping time} (\emph{TT}; i.e., the average length of the
 vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).
@@
 Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
-respective window. These metrics can then be plotted as a time series to
-visualize their evolution over time. For these analyses, we decided to
-focus on recurrence rate and determinism.
+respective window. For these analyses, we decided to focus on recurrence rate
+and determinism.
 

### 2020-06-01 manuscript.Rmd
Edits to results

@@
 For social cohesion and count of all events, there was a consistent period 
-of above-chance RR from the 7th-12th and 36th-47th window 
-(Figure \@ref(fig:plot-wcrqa-targ-all)). DET was largely above chance 
-from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+of above-chance RR from the 7th-12th and 36th-47th window. DET was largely 
+above chance from the 46th to the 61st window 
+(Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 above- or nearly above-chance DET from the 7th-13th and 26th-47th 
-windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). DET also 
-showed above- or nearly above-chance values in windows 7th-17th and 
-intermittent peaks between the 34th and 61st windows (Figure 
-\@ref(fig:plot-wcrqa-source-targ-all)).
+windows. DET also showed above- or nearly above-chance values in windows 7 
+through 17 and intermittent peaks between the 34th and 61st windows 
+(Figure \@ref(fig:plot-wcrqa-source-targ-all)).
 

### 2020-06-01 manuscript.tex
Edits to results

@@
 For social cohesion and count of all events, there was a consistent period
-of above-chance RR from the 7th-12th and 36th-47th window
-(Figure \ref{fig:plot-wcrqa-targ-all}). DET was largely above chance
-from the 46th to the 61st window (Figure \ref{fig:plot-wcrqa-targ-all}).
+of above-chance RR from the 7th-12th and 36th-47th window. DET was largely
+above chance from the 46th to the 61st window
+(Figure \ref{fig:plot-wcrqa-targ-all}).
 
@@
 above- or nearly above-chance DET from the 7th-13th and 26th-47th
-windows (Figure \ref{fig:plot-wcrqa-source-targ-all}). DET also
-showed above- or nearly above-chance values in windows 7th-17th and
-intermittent peaks between the 34th and 61st windows (Figure
-\ref{fig:plot-wcrqa-source-targ-all}).
+windows. DET also showed above- or nearly above-chance values in windows 7
+through 17 and intermittent peaks between the 34th and 61st windows
+(Figure \ref{fig:plot-wcrqa-source-targ-all}).
 

### 2020-06-01 manuscript.Rmd
Edits to crqa results

@@
 how social mobilization both virtually and physically evolve over time in
-tandem. Using the
-nonlinear dynamical time series analyses, we investigated the theory that
-virtual mobilization is increasingly reflective of real-world events
-during times of strife.
+tandem. Using nonlinear dynamical time series analyses, we investigated the 
+theory that virtual mobilization is increasingly reflective of real-world 
+events during times of strife.
 
@@
 The significant result of DET for social cohesion with all and negative 
-events supports our hypothesis that
-event salience is coupled with online social cohesion The frequency
-of all and negative events are thus associated with greater
-shared trajectories with social cohesion that would be expected by chance. 
-However, when we specifically target positive events, the connection
-to social cohesion fades, providing further
-support for our hypothesis. Positive events
-may be less coupled to social cohesion than more salient negative events
-during times of turmoil; by contrast, overall event frequency and
-negative event frequency are coupled with Twitter social cohesion.
+events supports our hypothesis that event salience is coupled with online 
+social cohesion. The frequency of all and negative events are thus associated 
+with greater shared trajectories with social cohesion that would be expected 
+by chance. However, when we specifically target positive events, the connection
+to social cohesion fades, providing further support for our hypothesis. 
+Positive events may be less coupled to social cohesion than more salient 
+negative events during times of turmoil; by contrast, overall event frequency 
+and negative event frequency are coupled with Twitter social cohesion.
 
@@
 standing. In this case, the increased coupling of positive events would
-coupled not with shared positive affect in social media but instead
+be coupled not with shared positive affect in social media but instead
 to shared negative affect in social media in response. However, we

### 2020-06-01 manuscript.tex
Edits to crqa results

@@
 how social mobilization both virtually and physically evolve over time in
-tandem. Using the
-nonlinear dynamical time series analyses, we investigated the theory that
-virtual mobilization is increasingly reflective of real-world events
-during times of strife.
+tandem. Using nonlinear dynamical time series analyses, we investigated the
+theory that virtual mobilization is increasingly reflective of real-world
+events during times of strife.
 
@@
 The significant result of DET for social cohesion with all and negative
-events supports our hypothesis that
-event salience is coupled with online social cohesion The frequency
-of all and negative events are thus associated with greater
-shared trajectories with social cohesion that would be expected by chance.
-However, when we specifically target positive events, the connection
-to social cohesion fades, providing further
-support for our hypothesis. Positive events
-may be less coupled to social cohesion than more salient negative events
-during times of turmoil; by contrast, overall event frequency and
-negative event frequency are coupled with Twitter social cohesion.
+events supports our hypothesis that event salience is coupled with online
+social cohesion. The frequency of all and negative events are thus associated
+with greater shared trajectories with social cohesion that would be expected
+by chance. However, when we specifically target positive events, the connection
+to social cohesion fades, providing further support for our hypothesis.
+Positive events may be less coupled to social cohesion than more salient
+negative events during times of turmoil; by contrast, overall event frequency
+and negative event frequency are coupled with Twitter social cohesion.
 
@@
 standing. In this case, the increased coupling of positive events would
-coupled not with shared positive affect in social media but instead
+be coupled not with shared positive affect in social media but instead
 to shared negative affect in social media in response. However, we
-cannot test this hypothesis with the current data; future\\
+cannot test this hypothesis with the current data; future
 research should explore the semantic content of this tweet

### 2020-06-01 manuscript.Rmd
Add Leah's contributions to discussion

@@
 In the present study, we investigated the dynamics of real-world events
-and online communication on Twitter in Syria during Arab Spring. We examined
+and online communication on Twitter in Syria during Arab Spring. 
+CRQA methodology allows us to model the relationship between sociolinguistic 
+cohesion and exogenous political events. This work stands alongside the model 
+of Palestinian-Israeli social media and events developed by Zeitzoff (2011), 
+and the role of peripheral participants in the Syrian Arab Spring movement by 
+Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we 
+demonstrate how language and social mobilization interact with events along 
+the conflict-cooperation continuum in Syria. We have introduced a novel 
+theoretical framework of sociolinguistic cohesion which we operationalize 
+using a weighted measure of lexical relationships. We examined
 how social mobilization both virtually and physically evolve over time in
@@
 
-(This would be where Leah should update her part.)
+This methodology should be of great interest to social scientists investigating social mobilization.
+It has potential applications for gender studies and the #MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests.
+Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life.
+Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior.
+If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.
 
 ## Conclusion
-Given the pervasiveness of social media, it is unsurprising
+Considering the pervasiveness of social media, it is unsurprising
 that social activists and protesters have
@@
 dynamics analyses, our results have serious implications for monitoring global
-movements. While traditional media in regions of authoritarian rule are
-often biased, the self-organized nature of Twitter poses a new avenue to gain
-insight into truths about uprisings and social mobilization. By
-conceptualizing Twitter and real-world events as two elements of an
-inextricably linked dynamical system, the levels of social cohesion within 
-social media platforms could be monitored for fluctuations indicating shifts
-in power and peace. Social media mobilization may thus help alert the world to
-citizens' actions and reactions that are suppressed by government regimes,
-providing insight into events that may not otherwise be broadcast.
+movements in consistent across other social uprisings. While traditional, 
+state-run media in regions of authoritarian rule are often biased and 
+propaganda for the leader and central government, the 
+self-organized nature of Twitter poses a new avenue to gain insight into 
+truths about up-risings and social mobilization. By conceptualizing Twitter 
+and real-world events as two elements of an inextricably linked dynamical 
+system, the levels of social cohesion within social media platforms could be 
+monitored for fluctuations indicating shifts in power and peace. Social media
+mobilization may thus help alert the world to citizens' actions and reactions 
+that are suppressed by government regimes, providing insight into events that 
+may not otherwise be broadcast and allowing for faster intervention.
 

### 2020-06-01 manuscript.tex
Add Leah's contributions to discussion

@@
 In the present study, we investigated the dynamics of real-world events
-and online communication on Twitter in Syria during Arab Spring. We examined
+and online communication on Twitter in Syria during Arab Spring.
+CRQA methodology allows us to model the relationship between sociolinguistic
+cohesion and exogenous political events. This work stands alongside the model
+of Palestinian-Israeli social media and events developed by Zeitzoff (2011),
+and the role of peripheral participants in the Syrian Arab Spring movement by
+Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
+demonstrate how language and social mobilization interact with events along
+the conflict-cooperation continuum in Syria. We have introduced a novel
+theoretical framework of sociolinguistic cohesion which we operationalize
+using a weighted measure of lexical relationships. We examined
 how social mobilization both virtually and physically evolve over time in
@@
 
-(This would be where Leah should update her part.)
+This methodology should be of great interest to social scientists investigating social mobilization.
+It has potential applications for gender studies and the \#MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests.
+Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life.
+Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior.
+If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.
 
@@
 
-Given the pervasiveness of social media, it is unsurprising
+Considering the pervasiveness of social media, it is unsurprising
 that social activists and protesters have
@@
 dynamics analyses, our results have serious implications for monitoring global
-movements. While traditional media in regions of authoritarian rule are
-often biased, the self-organized nature of Twitter poses a new avenue to gain
-insight into truths about uprisings and social mobilization. By
-conceptualizing Twitter and real-world events as two elements of an
-inextricably linked dynamical system, the levels of social cohesion within
-social media platforms could be monitored for fluctuations indicating shifts
-in power and peace. Social media mobilization may thus help alert the world to
-citizens' actions and reactions that are suppressed by government regimes,
-providing insight into events that may not otherwise be broadcast.
+movements in consistent across other social uprisings. While traditional,
+state-run media in regions of authoritarian rule are often biased and
+propaganda for the leader and central government, the
+self-organized nature of Twitter poses a new avenue to gain insight into
+truths about up-risings and social mobilization. By conceptualizing Twitter
+and real-world events as two elements of an inextricably linked dynamical
+system, the levels of social cohesion within social media platforms could be
+monitored for fluctuations indicating shifts in power and peace. Social media
+mobilization may thus help alert the world to citizens' actions and reactions
+that are suppressed by government regimes, providing insight into events that
+may not otherwise be broadcast and allowing for faster intervention.
 

### 2020-06-01 manuscript.Rmd
Update Results

@@
 For social cohesion and count of all events, there was a consistent period 
-of above-chance RR from the 7th-12th and 36th-47th window. DET was largely 
-above chance from the 46th to the 61st window 
+of above-chance RR from the 7th--12th and 36th--47th window. In addition
+to some one-week peaks at the beginning of the time period, DET was largely 
+above chance from the 46th to the 61st window, with some exceptions 
 (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
-For social cohesion and count of positive events, there was a downward trend in RR 
-as the window moves with largely above-chance RR from the 1st-18th and 
-32nd-45th windows. DET was at or above chance for the 8th-17th, 
-32nd-34th and at the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of positive events, we saw a downward trend in 
+RR as the window advances throughout the sample. Interestingly, we see
+largely above-chance RR until the 50th window, with some exceptions during
+window periods 20-30. DET was at or above chance for the 7th--17th, 32nd-34th, 
+and 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
 For social cohesion and count of negative events, RR stayed above
-or almost above chance from the 4th-7th and 43rd-47th windows. DET
+or almost above chance from the 4th--7th and 43rd-47th windows. DET
 was above or nearly above chance in the 1st and 2nd windows, with intermittent 
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 7th-13th and 26th-47th 
+above- or nearly above-chance DET from the 7th--13th and 26th--47th 
 windows. DET also showed above- or nearly above-chance values in windows 7 
@@
 positive events, there was a downward trend in RR as the window moved, with 
-largely above-chance values in the first 20 windows and the 32nd-45th windows. 
+largely above-chance values in the first 20 windows and the 32nd--45th windows. 
 DET stayed largely within chance, with the exception of windows 13 
@@
 and negative events, there was an extended period of time during which RR 
-(32nd-47th windows) and DET (35th-39th windows) were above or nearly above 
+(32nd--47th windows) and DET (35th--39th windows) were above or nearly above 
 chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from

### 2020-06-01 manuscript.Rmd
Formatting and typos

@@
 
-All scripts used for scrapping tweets and compressing data can be found at https://github.com/chbrown/twilight.
+All scripts used for scraping tweets and compressing data can be found 
+at https://github.com/chbrown/twilight.
 
@@
 
-For both the target only and the target and source data described above, time series of
+For both the target-only and the target and source data described above, time series of
 the count of all events were generated by summing the total number of events
@@
 # build table
-pander(target_results, caption = "\\label{table-1}CRQA results for target only data.")
+pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.")
 
@@
 the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
-during May 1st---15th was almost consistently -10, the most violent 
+during May 1st--15th was almost consistently -10, the most violent 
 event category. These dates directly correlate with the above-chance RR and DET

### 2020-06-01 manuscript.Rmd
Integrating Leah's edits pt. 1

@@
 
+Prior to the advent of social media, people coordinated their protest behavior using phone tree calling sheets and flyers generated on mimeograph machines, through in-person meetings for social organizations and in churches, and through word of mouth.
+They gathered together and hand-made protest signs that reflected their agendas.
+As McAdam found, people were more likely to join movements when they had a personal connection [@McAdam_1986; @McAdam_1986].
+Strong ties were better predictors of involvement in high-risk protest activity.
+However, the era of the Internet and online social mobilization through decentralized networks has upended theories about recruitment to, and participation in, social movements.
+Strong interpersonal ties have yielded to weak impersonal ties that strongly predict involvement in social movements [@Threlkeld_2017].
+The research methodologies for measuring social movements have similarly evolved from ethnographic interviews to big data analysis of language on social media.
+The cohesiveness and strength of social movements in the pre-Internet era could be operationalized by the number of people turning out to protest, and through the political events that precipitated and resulted from social gatherings en masse.
+
+In the offline era of social mobilization, the content of placards and protest signs provided the protest narrative for onlookers near and far.
+For cohesive social movements, the content of placards and posters itself was cohesive.
+For example, the “I am a man” posters held by the men involved in the 1968 sanitation workers’ strike reflected their internal cohesion and unified, goal-oriented movement [@Windsor_2020].
+Social media replicates and amplifies this phenomenon during moments of social unrest.
+Amid the cacophony of messages during political upheaval, such as the Arab Spring, consistent themes emerge through hashtags, retweets, and the repeated mentions of concepts such as regime, security, demonstration, and human rights.
+The cohesiveness of these themes, i.e., whether movement participants are “singing in one voice,” reflects the real-world events happening contemporaneously with collective action in social movements or civil conflicts.
+
+In the present research, we investigate the relationship between linguistic cohesion and social cohesion in times of social conflict and unrest.
+We tackle a question related to the one posed by Zeitzoff (2017): how does social media reflect on-the-ground realities during times of social conflict [@Zeitzoff_2017]?
+We examine patterns of linguistic cohesion on Twitter during the Arab Spring uprising in Syria between March and June 2012.
+We contextualize the linguistic cohesion with social mobilization and response to the relative intensity of the conflict.
+Cohesion is a multi-layered concept referring to the connectedness of words, thoughts, speakers, and actions.
+Cohesion reflects the continuity of language and expression, and it shows the connectivity of participants in a social movement.
+To address the relationship between language and discourse and social movements, we adopt an interdisciplinary approach that incorporates linguistics, psychology, and political science using non-linear dynamical systems methodology to model the relationship between language and action.
+We find that in the early months of 2012, conflict-related events were more strongly associated with linguistic cohesion than were more neutral or peaceful events.
+
+Disentangling the complicated relationship between mass online mobilization, and social mobilization in person, continues to be a relevant question.
+The political processes that transpired during and after the Arab Spring are still in the process of being understood.
+As Zeitzoff (2017) recognizes, social media is changing conflict, but the mechanisms and relationships are still being understood [@Zeitzoff_2017].
+
+## Syria in context
+The decades prior to the onset of the Arabs Spring in Syria were marked by social repression and fear.
+In 1971, Hafez al-Assad overthrew the previous leader and remained in power for thirty years, presiding during times of regional contentiousness and cooperation until his death in 2000.
+His son, Bashar al-Assad, who continued the regime of authoritarian leadership, assumed his office.
+The Assad lineage hails from a minority Islamic sect, the Alawites, in a multi-religious and multi-ethnic country comprised of Christians, Sunni and Shia Muslims, Kurds, and Palestinian refugees.
+
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
+unjustifiably stripped of his vendor cart by municipal officials. His
+humiliation led him to set himself on fire in protest to the authoritarian
+rule, ultimately leading to his death several days later. His actions served
+as a catalyst for the Tunisian Revolution, and one week after his death,
+Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
+country. The events of Tunisia rapidly spread to surrounding countries 
+also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
+and Syria.
+
+Following a wave of democratization efforts across the Middle East and North Africa, protests began modestly in Syria in March 2011.
+The regime responded harshly with imprisonments, detentions, censorship, and military operations as the resistance to Assad’s regime grew and spread throughout the country.
+The fighting escalated in earnest in March 2012, after increased unrest in the western city of Homs.
+International actors, including the Red Cross/Red Crescent Society, the United Nations General Assembly, the Security Council, and individual leaders throughout the world worked toward cease-fires, negotiations, and concessions, without much success.
+While many high-level military and diplomatic officials have defected from the regime, sufficient loyal forces have been able to execute continued repression.
+During this time between March and June 2012, more than eight million tweets were sent within Syria revealing the details of the conflict.
+
+Syria is a multi-ethnic, multi-lingual, and multi-religious state.
+Kurdish people comprise between 10-15% of the population, Alawites between 8-15%, Christians about 10%.
+There are also much smaller sects, i.e.
+the Ismailis and Druze, but Sunni Muslims comprise the vast majority of society, and most people speak Arabic as their mother tongue.
+Most policy reports addressing the current conflict report on the cohesion of the ruling Alawite military elite, rather than on the cohesiveness of the opposition movement.
+However, the Sunni majority’s disaffection with the Syrian government and lack of political representation provide sufficient grievance and collective group identification to make them a cohesive force.
+
+## Social Media and Social Movements
+
+During the Arab Spring, social media provided real-time information about the events transpiring in countries across the Middle East and North Africa.
+Our understanding about the role of social media in social movements is still evolving.
+Some argue that these mass movements would not have been possible without
+efficient large-scale coordination, both physically on the ground and virtually 
+on social media platforms. Along with Facebook, Twitter has been credited as 
+essential to the Arab Spring---both for protesters (as a means to coordinate 
+with one another and to communicate with the world) and for the government 
+response (to monitor and track protestors to crack down on dissent) 
+[@comninos2011twitter]. The events of Arab Spring have been thoroughly 
+discussed within the political science literature 
+[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
+the direct *coupling* between Syrian Twitter cohesion and international action
+coordination has not been investigated. Others provide skepticism about the effect of social media on collective action [@Seay_2014].
+
+In Foreign Affairs, Anderson writes that, “The important story about the 2011 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the norms of civic engagement shaped the protesters' aspirations.
+Nor is it about how activists used technology to share ideas and tactics.
+Instead, the critical issue is how and why these ambitions and techniques resonated in their various local contexts [@Anderson_2011].” Malcolm Gladwell, in highlighting the notions of strong and weak ties, @Gladwell_2010 and @McAdam_1986, similarly expressed hesitation about the role of online organizing, arguing that real-life strong ties outweigh online weak ties and that participation in online activism only requires scant sacrifices whereas recruitment to higher-risk activities is done through in-person contact, namely strong ties [@Gladwell_2010; [@McAdam_1986].
+Interestingly, these views may actually help to make the case for bridging the gap between social media and social mobilization, by suggesting the strength of social ties in an online environment is inextricably linked to the context and ambitions of the actors.
+Granovetter notes that while strong ties tend to bind smaller groups, weak ties tend to bind groups across distances [@Granovetter_1973].
+
+Social media generates critical information about events, such as whether or not a demonstration will take place and what transpires when it does, how many people participate, and how the state, the military, and the security apparatus respond.
+Similarly, these media platforms alert us to more global shifts within a conflict, such as when fighting moves to a new city or region, the number of casualties and wounded, and the types of weaponry used by parties to the conflict [@Zeitzoff_2017].
+Social media is not entirely event-driven, however.
+In monitoring social media channels, government forces may respond to the perception that citizens are gaining strength and sympathy.
+Governments have been shown to be quite tolerant of dissent so long as it does not metamorphosize into collective action [@King_Pan_Roberts_2013].
+Additionally, the insulated nature of online social platforms allows valuable social dynamics to be detailed at unprecedented resolution and scale.
+As such, the digital traces left by individuals and collectively as groups are regarded as a valuable source of information that can offer powerful insights into states of social disequilibrium, up-risings, and escalations into civil wars.
+
+Citizens communicate with each other with increased transparency due to the ubiquitous availability of social media such as low-cost and egalitarian platforms like Twitter.
+Citizens are able to access these tools via mobile phones and computers with Internet connectivity, providing a stream of real-time shared information.
+This facilitates studying the degree of cohesion between speakers, and the alignment between that cohesion and their collective political behavior.
+Citizens can tweet the location of events like protests and military incursions, the degree of state repression, and the number of casualties.
+In kind, the government, interested in remaining in power, monitors social media platforms to ascertain emerging threats, such as where new groups are forming and where existing groups are strengthening, where gatherings are held, and who the idea entrepreneurs are.
+An example of a leader manifesting his interest in such public conversation is given in a speech of June 3, 2012 by Bashar al-Assad:
+
+“I know that I have been away from the media for a long time, and I have missed having direct contact with the citizens, but I have always been following up with the daily occurrences and gathering the information so that my speech can be built on what is said by the street.”
+
+With few exceptions, Assad chose to keep social media platforms up and running.
+Gohdes (2015) notes that regimes can attempt to thwart the growth of social protest online and in the streets by shutting down the Internet [@Gohdes_2015].
+During these times, however, she finds that military repression increases.
+However, government information about the citizens decreases, and as such, many regimes have elected to maintain Internet connectivity as a means of monitoring and surveilling their citizens.
+
+## Social Cohesion and Social Mobilization
+Real-world collective action is known to bring about a sense of togetherness,
+also known as “collective effervescence” [@durkheim1995elementary]. This
+feeling of being a part of something larger than oneself leads individuals
+to act in ways that would not have on their own. Being overcome with this
+feeling can lead to violence [@collins2009violence; @spaaij2014sports].
+Conversely, increased exposure
+to violence can result in positive social cohesion. @gilligan2014civil
+found that exposure to fatal wartime violence resulted in increased prosocial
+motivations, including cooperative behaviors, feelings of trust, and overall
+community-level social cohesion.
+
+## Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
+We tie the constructs of lexical, interlocutor, and social/physical cohesion together in a theoretical framework called sociolinguistic cohesion, as shown in Figure X.
+We can measure the changes in cohesion preceding and in response to external stimuli by evaluating the messages and the context in which they occur.
+Several mechanisms are in motion here.
+Previous values of linguistic cohesion should influence future values of linguistic cohesion.
+They should also influence future actions in the real world space.
+Previous events influence future events, and also the future cohesiveness of the opposition.
+
+Sociolinguistic cohesion is not a static concept.
+Just as social movements experience increased participation as well as setbacks – indicating dynamic relationships between participants, and participants and the sociopolitical environment – sociolinguistic cohesion is also dynamic, reflecting the changing states of the political sphere.
+Other scholars have noted the diffusion of messages whereby they reach a critical mass, whereby “behaviors, beliefs, and preferences” spread within a population [@Barash_Cameron_Macy_2012].
+Cohesion changes over time in response to external events and the internal dynamics of the social movement.
+Some may wonder whether social cohesion can diffuse among distant actors who do not interact face-to-face; Centola and Macy show that Internet weak ties extend over long distances and as such have spatially significant abilities to influence actors [@Centola_Macy_2007].
+Fink et al.
+also explored diffusion of hashtags in viral contagion in Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion [@Fink_Schmidt_Barash_Cameron_Macy_2016].
+The prevalence and rate of particular hashtags contribute to the overall sociolinguistic cohesion.
+he more that people reuse hashtags or common phrases, the greater the sociolinguistic cohesion when this phenomenon occurs during socially significant times like protests [@Adamic_others_2015].
+Exogenous events, like intervention by another country or international organization like the United Nations, can affect sociolinguistic cohesion.
+Endogenous events, like the recruitment of new members to the rebel or resistance movement, can also affect the level of cohesion.
+
+Combining these separate threads, it is reasonable to expect that real-world actions 
+and online social interactions would be enmeshed, driving and being driven by 
+one another. Rather than expecting that only real-world social cohesion would be
+driven by real-world action, we would expect interaction between real-world and
+virtual dynamics: In this case, exposure to real-world violence could result in social
+cohesion in the virtual world. Increased social cohesion is thus potentially
+an indicator and a result of increased social organization and mobilization 
+on the ground.
+
+Exploring how social media influences contentious behavior, Tilly notes that social media lowers coordination and transaction costs for participants, and that older versions of organizing social movements have become less effective, yielding to the new frontier of online organizing [@McAdam_Tarrow_Tilly_2003].
+Koopmans extends this further, writing that, “Authorities react to social movement activities if and as they are depicted in the mass media, and conversely movement activists become aware of political opportunities and constraints through the reactions (or non-reactions) that their actions provoke in the public sphere” [@Koopmans_2004].
+
+Lexical cohesion, then, should be a useful indicator of social cohesion in political crisis.
+Lexical cohesion happens at the word level.
+Interlocutor cohesion happens between speakers.
+Political cohesion happens at the social level during moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion is comprised of lexical, interlocutor, and socio-political events, where the words and their context reveal the disposition of socially connected linguistic communities.
+Sociolinguistic cohesion combines the elements of lexical cohesion in that it captures the degree of similarity between what is said, and how it is said.
+It accounts for the cohesion between multiple speakers in an environment whose language evolves to become more aligned and similar.
+Sociolinguistic cohesion also addresses how groups involved in political rebellion must have internal cohesion to overcome the collective action problem to mount sustained resistance to state authority.
+
 Social coordination has long been used both physically and virtually
@@
 
-## Arab Spring
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian
-rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death,
-Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
-country. The events of Tunisia rapidly spread to surrounding countries 
-also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
-and Syria.
-
-These mass movements would not have been possible without
-efficient large-scale coordination, both physically on the ground and virtually 
-on social media platforms. Along with Facebook, Twitter has been credited as 
-essential to the Arab Spring---both for protesters (as a means to coordinate 
-with one another and to communicate with the world) and for the government 
-response (to monitor and track protestors to crack down on dissent) 
-[@comninos2011twitter]. The events of Arab Spring have been thoroughly 
-discussed within the political science literature 
-[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
-the direct *coupling* between Syrian Twitter cohesion and international action
-coordination has not been investigated.
-
-## Social Cohesion and Social Mobilization
-Real-world collective action is known to bring about a sense of togetherness,
-also known as “collective effervescence” [@durkheim1995elementary]. This
-feeling of being a part of something larger than oneself leads individuals
-to act in ways that would not have on their own. Being overcome with this
-feeling can lead to violence [@collins2009violence; @spaaij2014sports].
-Conversely, increased exposure
-to violence can result in positive social cohesion. @gilligan2014civil
-found that exposure to fatal wartime violence resulted in increased prosocial
-motivations, including cooperative behaviors, feelings of trust, and overall
-community-level social cohesion.
-
 Just as real-world social cohesion can be
@@
 
-Combining these separate threads, it is reasonable to expect that real-world actions 
-and online social interactions would be enmeshed, driving and being driven by 
-one another. Rather than expecting that only real-world social cohesion would be
-driven by real-world action, we would expect interaction between real-world and
-virtual dynamics: In this case, exposure to real-world violence could result in social
-cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator and a result of increased social organization and mobilization 
-on the ground.
-
-Social media platforms provide one way to enable this kind of online social
+This kind of massive online social cohesion can lead to real-world
+social manifestations. Social media platforms provide one way to enable this kind of online social
 cohesion by offering distributed information-gathering and real-time information

### 2020-06-01 manuscript.tex
Integrating Leah's edits pt. 1

@@
 
+Prior to the advent of social media, people coordinated their protest behavior using phone tree calling sheets and flyers generated on mimeograph machines, through in-person meetings for social organizations and in churches, and through word of mouth.
+They gathered together and hand-made protest signs that reflected their agendas.
+As McAdam found, people were more likely to join movements when they had a personal connection ({\textbf{???}}; {\textbf{???}}).
+Strong ties were better predictors of involvement in high-risk protest activity.
+However, the era of the Internet and online social mobilization through decentralized networks has upended theories about recruitment to, and participation in, social movements.
+Strong interpersonal ties have yielded to weak impersonal ties that strongly predict involvement in social movements ({\textbf{???}}).
+The research methodologies for measuring social movements have similarly evolved from ethnographic interviews to big data analysis of language on social media.
+The cohesiveness and strength of social movements in the pre-Internet era could be operationalized by the number of people turning out to protest, and through the political events that precipitated and resulted from social gatherings en masse.
+
+In the offline era of social mobilization, the content of placards and protest signs provided the protest narrative for onlookers near and far.
+For cohesive social movements, the content of placards and posters itself was cohesive.
+For example, the \enquote{I am a man} posters held by the men involved in the 1968 sanitation workers' strike reflected their internal cohesion and unified, goal-oriented movement ({\textbf{???}}).
+Social media replicates and amplifies this phenomenon during moments of social unrest.
+Amid the cacophony of messages during political upheaval, such as the Arab Spring, consistent themes emerge through hashtags, retweets, and the repeated mentions of concepts such as regime, security, demonstration, and human rights.
+The cohesiveness of these themes, i.e., whether movement participants are \enquote{singing in one voice,} reflects the real-world events happening contemporaneously with collective action in social movements or civil conflicts.
+
+In the present research, we investigate the relationship between linguistic cohesion and social cohesion in times of social conflict and unrest.
+We tackle a question related to the one posed by Zeitzoff (2017): how does social media reflect on-the-ground realities during times of social conflict ({\textbf{???}})?
+We examine patterns of linguistic cohesion on Twitter during the Arab Spring uprising in Syria between March and June 2012.
+We contextualize the linguistic cohesion with social mobilization and response to the relative intensity of the conflict.
+Cohesion is a multi-layered concept referring to the connectedness of words, thoughts, speakers, and actions.
+Cohesion reflects the continuity of language and expression, and it shows the connectivity of participants in a social movement.
+To address the relationship between language and discourse and social movements, we adopt an interdisciplinary approach that incorporates linguistics, psychology, and political science using non-linear dynamical systems methodology to model the relationship between language and action.
+We find that in the early months of 2012, conflict-related events were more strongly associated with linguistic cohesion than were more neutral or peaceful events.
+
+Disentangling the complicated relationship between mass online mobilization, and social mobilization in person, continues to be a relevant question.
+The political processes that transpired during and after the Arab Spring are still in the process of being understood.
+As Zeitzoff (2017) recognizes, social media is changing conflict, but the mechanisms and relationships are still being understood ({\textbf{???}}).
+
+\hypertarget{syria-in-context}{%
+\subsection{Syria in context}\label{syria-in-context}}
+
+The decades prior to the onset of the Arabs Spring in Syria were marked by social repression and fear.
+In 1971, Hafez al-Assad overthrew the previous leader and remained in power for thirty years, presiding during times of regional contentiousness and cooperation until his death in 2000.
+His son, Bashar al-Assad, who continued the regime of authoritarian leadership, assumed his office.
+The Assad lineage hails from a minority Islamic sect, the Alawites, in a multi-religious and multi-ethnic country comprised of Christians, Sunni and Shia Muslims, Kurds, and Palestinian refugees.
+
+In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
+unjustifiably stripped of his vendor cart by municipal officials. His
+humiliation led him to set himself on fire in protest to the authoritarian
+rule, ultimately leading to his death several days later. His actions served
+as a catalyst for the Tunisian Revolution, and one week after his death,
+Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
+country. The events of Tunisia rapidly spread to surrounding countries
+also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
+and Syria.
+
+Following a wave of democratization efforts across the Middle East and North Africa, protests began modestly in Syria in March 2011.
+The regime responded harshly with imprisonments, detentions, censorship, and military operations as the resistance to Assad's regime grew and spread throughout the country.
+The fighting escalated in earnest in March 2012, after increased unrest in the western city of Homs.
+International actors, including the Red Cross/Red Crescent Society, the United Nations General Assembly, the Security Council, and individual leaders throughout the world worked toward cease-fires, negotiations, and concessions, without much success.
+While many high-level military and diplomatic officials have defected from the regime, sufficient loyal forces have been able to execute continued repression.
+During this time between March and June 2012, more than eight million tweets were sent within Syria revealing the details of the conflict.
+
+Syria is a multi-ethnic, multi-lingual, and multi-religious state.
+Kurdish people comprise between 10-15\% of the population, Alawites between 8-15\%, Christians about 10\%.
+There are also much smaller sects, i.e.~the Ismailis and Druze, but Sunni Muslims comprise the vast majority of society, and most people speak Arabic as their mother tongue.
+Most policy reports addressing the current conflict report on the cohesion of the ruling Alawite military elite, rather than on the cohesiveness of the opposition movement.
+However, the Sunni majority's disaffection with the Syrian government and lack of political representation provide sufficient grievance and collective group identification to make them a cohesive force.
+
+\hypertarget{social-media-and-social-movements}{%
+\subsection{Social Media and Social Movements}\label{social-media-and-social-movements}}
+
+During the Arab Spring, social media provided real-time information about the events transpiring in countries across the Middle East and North Africa.
+Our understanding about the role of social media in social movements is still evolving.
+Some argue that these mass movements would not have been possible without
+efficient large-scale coordination, both physically on the ground and virtually
+on social media platforms. Along with Facebook, Twitter has been credited as
+essential to the Arab Spring---both for protesters (as a means to coordinate
+with one another and to communicate with the world) and for the government
+response (to monitor and track protestors to crack down on dissent)
+(Comninos, 2011). The events of Arab Spring have been thoroughly
+discussed within the political science literature
+(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
+the direct \emph{coupling} between Syrian Twitter cohesion and international action
+coordination has not been investigated. Others provide skepticism about the effect of social media on collective action ({\textbf{???}}).
+
+In Foreign Affairs, Anderson writes that, \enquote{The important story about the 2011 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the norms of civic engagement shaped the protesters' aspirations.
+Nor is it about how activists used technology to share ideas and tactics.
+Instead, the critical issue is how and why these ambitions and techniques resonated in their various local contexts ({\textbf{???}}).} Malcolm Gladwell, in highlighting the notions of strong and weak ties, ({\textbf{???}}) and ({\textbf{???}}), similarly expressed hesitation about the role of online organizing, arguing that real-life strong ties outweigh online weak ties and that participation in online activism only requires scant sacrifices whereas recruitment to higher-risk activities is done through in-person contact, namely strong ties {[}({\textbf{???}}); ({\textbf{???}}).
+Interestingly, these views may actually help to make the case for bridging the gap between social media and social mobilization, by suggesting the strength of social ties in an online environment is inextricably linked to the context and ambitions of the actors.
+Granovetter notes that while strong ties tend to bind smaller groups, weak ties tend to bind groups across distances ({\textbf{???}}).
+
+Social media generates critical information about events, such as whether or not a demonstration will take place and what transpires when it does, how many people participate, and how the state, the military, and the security apparatus respond.
+Similarly, these media platforms alert us to more global shifts within a conflict, such as when fighting moves to a new city or region, the number of casualties and wounded, and the types of weaponry used by parties to the conflict ({\textbf{???}}).
+Social media is not entirely event-driven, however.
+In monitoring social media channels, government forces may respond to the perception that citizens are gaining strength and sympathy.
+Governments have been shown to be quite tolerant of dissent so long as it does not metamorphosize into collective action ({\textbf{???}}).
+Additionally, the insulated nature of online social platforms allows valuable social dynamics to be detailed at unprecedented resolution and scale.
+As such, the digital traces left by individuals and collectively as groups are regarded as a valuable source of information that can offer powerful insights into states of social disequilibrium, up-risings, and escalations into civil wars.
+
+Citizens communicate with each other with increased transparency due to the ubiquitous availability of social media such as low-cost and egalitarian platforms like Twitter.
+Citizens are able to access these tools via mobile phones and computers with Internet connectivity, providing a stream of real-time shared information.
+This facilitates studying the degree of cohesion between speakers, and the alignment between that cohesion and their collective political behavior.
+Citizens can tweet the location of events like protests and military incursions, the degree of state repression, and the number of casualties.
+In kind, the government, interested in remaining in power, monitors social media platforms to ascertain emerging threats, such as where new groups are forming and where existing groups are strengthening, where gatherings are held, and who the idea entrepreneurs are.
+An example of a leader manifesting his interest in such public conversation is given in a speech of June 3, 2012 by Bashar al-Assad:
+
+\enquote{I know that I have been away from the media for a long time, and I have missed having direct contact with the citizens, but I have always been following up with the daily occurrences and gathering the information so that my speech can be built on what is said by the street.}
+
+With few exceptions, Assad chose to keep social media platforms up and running.
+Gohdes (2015) notes that regimes can attempt to thwart the growth of social protest online and in the streets by shutting down the Internet ({\textbf{???}}).
+During these times, however, she finds that military repression increases.
+However, government information about the citizens decreases, and as such, many regimes have elected to maintain Internet connectivity as a means of monitoring and surveilling their citizens.
+
+\hypertarget{social-cohesion-and-social-mobilization}{%
+\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}
+
+Real-world collective action is known to bring about a sense of togetherness,
+also known as \enquote{collective effervescence} (Durkheim, 1995). This
+feeling of being a part of something larger than oneself leads individuals
+to act in ways that would not have on their own. Being overcome with this
+feeling can lead to violence (Collins, 2009; Spaaij, 2014).
+Conversely, increased exposure
+to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
+found that exposure to fatal wartime violence resulted in increased prosocial
+motivations, including cooperative behaviors, feelings of trust, and overall
+community-level social cohesion.
+
+\hypertarget{sociolinguistic-cohesion-connectedness-of-speakers-events-and-ideas}{%
+\subsection{Sociolinguistic cohesion: Connectedness of speakers, events, and ideas}\label{sociolinguistic-cohesion-connectedness-of-speakers-events-and-ideas}}
+
+We tie the constructs of lexical, interlocutor, and social/physical cohesion together in a theoretical framework called sociolinguistic cohesion, as shown in Figure X.
+We can measure the changes in cohesion preceding and in response to external stimuli by evaluating the messages and the context in which they occur.
+Several mechanisms are in motion here.
+Previous values of linguistic cohesion should influence future values of linguistic cohesion.
+They should also influence future actions in the real world space.
+Previous events influence future events, and also the future cohesiveness of the opposition.
+
+Sociolinguistic cohesion is not a static concept.
+Just as social movements experience increased participation as well as setbacks -- indicating dynamic relationships between participants, and participants and the sociopolitical environment -- sociolinguistic cohesion is also dynamic, reflecting the changing states of the political sphere.
+Other scholars have noted the diffusion of messages whereby they reach a critical mass, whereby \enquote{behaviors, beliefs, and preferences} spread within a population ({\textbf{???}}).
+Cohesion changes over time in response to external events and the internal dynamics of the social movement.
+Some may wonder whether social cohesion can diffuse among distant actors who do not interact face-to-face; Centola and Macy show that Internet weak ties extend over long distances and as such have spatially significant abilities to influence actors ({\textbf{???}}).
+Fink et al.~also explored diffusion of hashtags in viral contagion in Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion ({\textbf{???}}).
+The prevalence and rate of particular hashtags contribute to the overall sociolinguistic cohesion.
+he more that people reuse hashtags or common phrases, the greater the sociolinguistic cohesion when this phenomenon occurs during socially significant times like protests ({\textbf{???}}).
+Exogenous events, like intervention by another country or international organization like the United Nations, can affect sociolinguistic cohesion.
+Endogenous events, like the recruitment of new members to the rebel or resistance movement, can also affect the level of cohesion.
+
+Combining these separate threads, it is reasonable to expect that real-world actions
+and online social interactions would be enmeshed, driving and being driven by
+one another. Rather than expecting that only real-world social cohesion would be
+driven by real-world action, we would expect interaction between real-world and
+virtual dynamics: In this case, exposure to real-world violence could result in social
+cohesion in the virtual world. Increased social cohesion is thus potentially
+an indicator and a result of increased social organization and mobilization
+on the ground.
+
+Exploring how social media influences contentious behavior, Tilly notes that social media lowers coordination and transaction costs for participants, and that older versions of organizing social movements have become less effective, yielding to the new frontier of online organizing ({\textbf{???}}).
+Koopmans extends this further, writing that, \enquote{Authorities react to social movement activities if and as they are depicted in the mass media, and conversely movement activists become aware of political opportunities and constraints through the reactions (or non-reactions) that their actions provoke in the public sphere} ({\textbf{???}}).
+
+Lexical cohesion, then, should be a useful indicator of social cohesion in political crisis.
+Lexical cohesion happens at the word level.
+Interlocutor cohesion happens between speakers.
+Political cohesion happens at the social level during moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion is comprised of lexical, interlocutor, and socio-political events, where the words and their context reveal the disposition of socially connected linguistic communities.
+Sociolinguistic cohesion combines the elements of lexical cohesion in that it captures the degree of similarity between what is said, and how it is said.
+It accounts for the cohesion between multiple speakers in an environment whose language evolves to become more aligned and similar.
+Sociolinguistic cohesion also addresses how groups involved in political rebellion must have internal cohesion to overcome the collective action problem to mount sustained resistance to state authority.
+
 Social coordination has long been used both physically and virtually
@@
 
-\hypertarget{arab-spring}{%
-\subsection{Arab Spring}\label{arab-spring}}
-
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian
-rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death,
-Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
-country. The events of Tunisia rapidly spread to surrounding countries
-also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
-and Syria.
-
-These mass movements would not have been possible without
-efficient large-scale coordination, both physically on the ground and virtually
-on social media platforms. Along with Facebook, Twitter has been credited as
-essential to the Arab Spring---both for protesters (as a means to coordinate
-with one another and to communicate with the world) and for the government
-response (to monitor and track protestors to crack down on dissent)
-(Comninos, 2011). The events of Arab Spring have been thoroughly
-discussed within the political science literature
-(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
-the direct \emph{coupling} between Syrian Twitter cohesion and international action
-coordination has not been investigated.
-
-\hypertarget{social-cohesion-and-social-mobilization}{%
-\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}
-
-Real-world collective action is known to bring about a sense of togetherness,
-also known as \enquote{collective effervescence} (Durkheim, 1995). This
-feeling of being a part of something larger than oneself leads individuals
-to act in ways that would not have on their own. Being overcome with this
-feeling can lead to violence (Collins, 2009; Spaaij, 2014).
-Conversely, increased exposure
-to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
-found that exposure to fatal wartime violence resulted in increased prosocial
-motivations, including cooperative behaviors, feelings of trust, and overall
-community-level social cohesion.
-
 Just as real-world social cohesion can be
@@
 
-Combining these separate threads, it is reasonable to expect that real-world actions
-and online social interactions would be enmeshed, driving and being driven by
-one another. Rather than expecting that only real-world social cohesion would be
-driven by real-world action, we would expect interaction between real-world and
-virtual dynamics: In this case, exposure to real-world violence could result in social
-cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator and a result of increased social organization and mobilization
-on the ground.
-
-Social media platforms provide one way to enable this kind of online social
+This kind of massive online social cohesion can lead to real-world
+social manifestations. Social media platforms provide one way to enable this kind of online social
 cohesion by offering distributed information-gathering and real-time information
@@
 
-All scripts used for scrapping tweets and compressing data can be found at \url{https://github.com/chbrown/twilight}.
+All scripts used for scraping tweets and compressing data can be found
+at \url{https://github.com/chbrown/twilight}.
 
@@
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{\label{table-1}CRQA results for target only data.}\tabularnewline
+\caption{\label{table-1}CRQA results for target-only data.}\tabularnewline
 \toprule
@@
 For social cohesion and count of all events, there was a consistent period
-of above-chance RR from the 7th-12th and 36th-47th window. DET was largely
-above chance from the 46th to the 61st window
+of above-chance RR from the 7th--12th and 36th--47th window. In addition
+to some one-week peaks at the beginning of the time period, DET was largely
+above chance from the 46th to the 61st window, with some exceptions
 (Figure \ref{fig:plot-wcrqa-targ-all}).
 
-For social cohesion and count of positive events, there was a downward trend in RR
-as the window moves with largely above-chance RR from the 1st-18th and
-32nd-45th windows. DET was at or above chance for the 8th-17th,
-32nd-34th and at the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of positive events, we saw a downward trend in
+RR as the window advances throughout the sample. Interestingly, we see
+largely above-chance RR until the 50th window, with some exceptions during
+window periods 20-30. DET was at or above chance for the 7th--17th, 32nd-34th,
+and 60th windows (Figure \ref{fig:plot-wcrqa-targ-all}).
 
 For social cohesion and count of negative events, RR stayed above
-or almost above chance from the 4th-7th and 43rd-47th windows. DET
+or almost above chance from the 4th--7th and 43rd-47th windows. DET
 was above or nearly above chance in the 1st and 2nd windows, with intermittent
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 7th-13th and 26th-47th
+above- or nearly above-chance DET from the 7th--13th and 26th--47th
 windows. DET also showed above- or nearly above-chance values in windows 7
@@
 positive events, there was a downward trend in RR as the window moved, with
-largely above-chance values in the first 20 windows and the 32nd-45th windows.
+largely above-chance values in the first 20 windows and the 32nd--45th windows.
 DET stayed largely within chance, with the exception of windows 13
@@
 and negative events, there was an extended period of time during which RR
-(32nd-47th windows) and DET (35th-39th windows) were above or nearly above
+(32nd--47th windows) and DET (35th--39th windows) were above or nearly above
 chance (Figure \ref{fig:plot-wcrqa-source-targ-all}). These windows span from
@@
 the modal ICEWS event for each day (Figure \ref{fig:plot-mode-event})
-during May 1st---15th was almost consistently -10, the most violent
+during May 1st--15th was almost consistently -10, the most violent
 event category. These dates directly correlate with the above-chance RR and DET

### 2020-06-01 manuscript.Rmd
Integrating Leah's edits pt. 2

@@
 ## Social Media and Social Movements
-
 During the Arab Spring, social media provided real-time information about the events transpiring in countries across the Middle East and North Africa.
@@
 
-## Social Cohesion and Social Mobilization
+## Lexical cohesion: Connectedness of words
+The words that comprise social media posts are the first level at which cohesion occurs.
+In Figure 1, we see four sequential tweets, each containing four words.
+Each sequential tweet contains some content included in the previous tweets.
+The linguistic construct of content word overlap measures the relationship across units of meaning – here, tweets – where identical and semantically similar words are repeated [@Graesser_McNamara_Louwerse_Cai_2004].
+These repeated lexical items constitute a theme; on Twitter, this might be a particular hashtag, a name, a location, or other nominal category.
+This localized cohesion is referential; words are repeated and co-referred across tweets, creating a sense of continuity and cohesiveness of meaning and message.
+
+Lexical cohesion also includes latent semantic analysis (LSA) [@Graesser_McNamara_Louwerse_Cai_2004.
+LSA measures semantic similarity across meaning units using a statistical method called singular value decomposition, an automated method used to detect plagiarism [@Ceska_2008; @Gamallo_Bordag_2011].
+In this process, each meaning unit (tweet) is a weighted vector, and the match between the tweets is measured as the cosine between the two vectors.
+This process provides an empirical relationship between the words used from one tweet to the next.
+We identify this as lexical cohesion.
+
+The concept of lexical, or semantic, cohesion has already been applied to the analysis of political speech, for example the language of Margaret Thatcher, as well as non-political speech [@Barzilay_Elhadad_1999; @Morris_Hirst_1991].
+McNamara and Graesser operationalize the concept of cohesion in their software, Coh-Metrix, an automated tool that analyzes text and discourse  [@Graesser_Jeon_Yan_Cai_2007; @Graesser_McNamara_Louwerse_Cai_2004; [@Graesser_McNamara_Kulikowich_2011].
+This software generates measures of co-referential cohesion that captures the amount of overlap in content words (as opposed to function words, like a, the, and and) in adjacent, local, and global sentences in the passage.
+Content word overlap refers to the proportion of words and word stems that are shared between sentences.
+A higher proportion of overlap indicates greater cohesion in the sentence.
+
+In estimating cohesion in Twitter posts, tweets that share content words and stems will yield higher cohesion values, even amongst speakers with opposing views on the subject matter.
+Repetition of terms and concepts is captured by reiteration, which is a type of lexical cohesion in which a subsequent item repeats a previous item, or refers to it through synonymous language [@Halliday_Hasan_1976].
+In social media, we can conceive of retweets – reposts or forwards of previous messages in part or in whole – as a form of reiteration that increase message cohesion.
+Since retweets replicate verbatim some part of another tweet, these tweets would also have higher cohesion.
+Hashtags function similarly, and are included in our analysis.
+
+```{r figure-1}
+
+# call figure 1 here
+
+```
+
+## Interlocutor cohesion
+Lexical cohesion contributes to the next level of relatedness among tweets: interlocutor cohesion.
+This is the degree to which people in a conversation, whether in person or online, have aligned their language [@Coupland_Giles_1988].
+Known as communication accommodation theory, the degree of alignment between speakers reveals their closeness, status, and deliberative strategy [@Giles_2016].
+Speakers can converge and diverge in their communication.
+Convergence facilitates easier transmission of information, because the speakers – or interlocutors – presume some existing familiarity or knowledge base between them.
+When you know someone well enough to finish their sentence, this is an example of convergence.
+Divergence, on the other hand, is more laborious because the speakers must make their presumptions explicit and tacit.
+Interlocutor cohesion, or convergence, happens when speakers are “singing in the same key” or are “on the same page.” Windsor (2020) describes various types of cohesion, using the example of the Occupy Wall Street movement as a symbol of divergence given the myriad signs, slogans, and interests of the participants [@Windsor_2020].
+On the other hand, the “I am a man” protest captured by Ernest Withers during the 1968 santiation workers’ strike in Memphis, TN, or the “Black Lives Matter” placards following the uprising in Ferguson, MO, symbolize convergence and strong interlocutor cohesion [@Edgar_Johnson_2018].
+
+Cognitive and social psychology theories of alignment and coordination lend themselves nicely to the study of social media communication during times of conflict and contentious behavior [@Tollefsen_Dale_Paxton_2013; @Garrod_Pickering_2004; @Pickering_Garrod_2004].
+Over the past few decades, this area has garnered significant attention and produced evidence showing that people sometimes linguistically and behaviorally align as they interact more [@Giles_Coupland_Coupland_1991; @Tollefsen_Dale_Paxton_2013].
+Similarly, accommodation theory refers to the ways in which individuals and groups linguistically adapt to minimize the social space distance.
+Speakers in a collective setting pursue strategies which increase their common ground, and this is reflected in the language they use to communicate with one another.
+
+A similar process happens among participants in social media discussions.
+The process of speakers’ (or tweeters) language becoming more similar is called linguistic style matching (LSM) [@Niederhoffer_Pennebaker_2002].
+LSM is a form of synchrony between speakers, akin to linguistic convergence.
+As Bernieri and Rosenthal (1991) describe, people engaged in linguistic synchrony match each others’ verbal behaviors, adopting not only similar terms, but similar patterns of language [@Bernieri_Rosenthal_1991].
+For example, LSM is particularly evident when one speaker introduces swearing into a genteel conversation; the first usage opens the vulgarity floodgates, and subsequent speakers may repeat the initial curse, as well as innovate new curses into the conversation.
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline contextualized by variation in real world events.
+Interlocutor cohesion may increase preceding an in-person social mobilization event, alerting a repressive government that collective mobilization is happening.
+Interlocutor cohesion may also respond to exogenous events such as spontaneous, unprovoked militarized conflict.
+If government forces target a new location using military weapons, this can precipitate online mobilization and discussion of the event.
+
+## Social and Physical Cohesion
+In turn, other studies show that linguistic alignment leads to increased social connectedness and solidarity [@Miles_Nind_Macrae_2009], which is associated with increased motivation for participation [@Walton_Cohen_Cwir_Spencer_2012], facilitating successful coordination of group actions toward shared goals [@Fusaroli_Bahrami_Olsen_Roepstorff_Rees_Frith_Tylén_2012; @Richardson_Dale_2005].
+This research emphasizes both the importance of and connections between linguistic alignment and behavioral alignment.
+The more people interact, the more similar their language and linguistic patterns become.
+This holds true for face-to-face interactions as well as online communication [@Riordan_Dale_Kreuz_Olney_2011}.
+Given this, we should expect to see increased linguistic cohesion amongst people participating in online discussions about an idea, event, or individual.
+Given that social media reports in real time about actual events taking place, i.e., protests or demonstrations in which people are assembled together in a location, or attacks that require coordination between members of a unit, the cohesion in social media should be expected to correlate with the social cohesion of the group [@Zeitzoff_2011}.
+
+A socially cohesive group is inherently more threatening to the existing regime because it reflects the professionalization of potential alternate leadership, and collective opposition momentum.
+Groups with high social cohesion are more difficult to divide and conquer, and more cohesive messages may also garner increased international support.
+A paper published in Nature argues that global insurgency movements all exhibit a similar pattern to their social structure [@Bohorquez_Gourley_Dixon_Spagat_Johnson_2009}.
+The authors assert that each violent group has a stable state, and that exogenous events can create perturbations that push the group to become more cohesive, or alternatively to become more fragmented.
+Rather than frenetic, patchwork messages via Twitter, cohesive messages indicate increased organizational structure, which should incentivize a response from the government.
+What process is the driving force, though?
+Does an increase in linguistic cohesion precede or follow increased repression by the government?
+Do movements get stronger first, and then the government responds, or does the government increase its offensive measures, and thus social groups have a clear opponent around whom they can coalesce both socially and linguistically?
+
+Thus, verbal synchrony leads to physical synchrony.
+Shared language in an online environment can influence individuals’ propensity to engage in similar coordinated behavior.
+In the case of the Arab Spring, this may mean social mobilization in public spaces to protest against government brutality.
+Words in a passage of text – or series of tweets – have some degree of semantic relation.
+Individuals engaged in a conversation, whether in real life or online, have the tendency to use similar language as they interact, increasing the cohesion of their language.
+As an extension, multiple individuals collectively communicating can also demonstrate linguistic alignment.
+In the context of social conflict, the linguistic cohesion of participants in the online conversation should correspond to the degree of social cohesion on the ground.
+We link these concepts of social and linguistic cohesion together to demonstrate how language serves as an indicator of the degree of social mobilization, using Twitter feeds during the spring of 2012 in Syria.
+
 Real-world collective action is known to bring about a sense of togetherness,
@@
 community-level social cohesion.
+
+Physical and social cohesion in the world can be modeled using event data which encodes who does what to whom on a given day.
+This could include events such as the government (GOV) imposing a blockade or fighting with artillery or tanks on a civilian group (CIV).
+CAMEO (Conflict and Mediation Event Observations) encode a set of activities with numerical values, rescaled to reflect a conflict-cooperation scale [@Schrodt_Hall_2006; @Goldstein_1992].
+These event codes include a range of behaviors, from making public statements and appeals, to demanding, threatening, protesting, and using unconventional mass violence.
+Steinert-Threlkeld (2017) modeled a similar relationship between social media and social mobilization using a Gini coefficient measure, rather than a tf-idf (term frequency-inverse document frequency) measure alongside event data [@Ramos_2003; @Threlkeld_2017].
+This pathbreaking work demonstrates that participants on the fringe of a social movement contribute substantially to the overall level of protest.
+We add to this discussion by demonstrating how sociolinguistic cohesion evolves in response to negative and positive exogenous events.
+
+### Cohesion in Social Movements and Civil Wars
+People join social and political resistance movements because they feel a sense of connection to the cause, and because they have been sufficiently convinced to participate.
+Given that people are generally risk averse, overcoming inertia requires a strong connection to the group identity, or against an individual, event, or political injustice [@Goldstone_1980; Goldstone_2011].
+Political resistance offers participants the opportunity to “lose themselves” and relinquish their individual identity in favor of identification with a larger group identity, thus contributing to a cohesive group ready and mobilized for action [@Hoffer_2011.
+Previous research on social movements supports the idea that participants are likely to join movements when they know and have a personal connection to someone else already involved [@McAdam_1986.
+The type of collective contentious behavior that manifests in society is a function of the available political opportunity structures.
+The political opportunity structure, as defined by Kitschelt (1986) are “comprised of specific configuration of resources, institutional arrangements and historical precedents for social mobilization, which facilitate the development of protest movements in some instances and constrain them in others [@Kitschelt_1986].” What emerges as strategies and tactics in contentious politics is in essence, a function of what the system makes possible.
+This includes the number of people and their disposition, i.e.
+nonviolent or violent, as well as their internal structure.
+The more cohesive a group is, the greater threat they pose to the establishment.
+
+Cohesion is also a familiar concept in the study of civil conflicts as it pertains to group affiliation and the ability to overcome collective action problems.
+Olson’s (Olson, 1965) seminal work on collective action informs the theory of group behavior.
+Individuals must act in concert – cohesively – to accomplish the task of challenging the authority of the state.
+Building on Eisinger’s (1973) analysis of social protest movements [@Eisinger_1973, McAdam, Tilly and Tarrow [@Tilly_2004, and Francisco [@Francisco_1995 have provided foundational work on the dynamics of social movements and contentious behavior.
+More recently, Gates (2002) considers rebel recruitment for participation in civil conflicts as a function of internal cohesion [@Gates_2002].
+He notes that rebel movement success is influenced by the degree of group cohesion, which itself is a function of geographic distance, ideology and ethnicity.
+
+There are multiple rebel groups within Syria, some with fighters sourced locally from the disaffected Syrian population, and an increasing number of foreign fighters from transnational terrorist organizations.
+Gates’ work helps us understand the intergroup competition for participation in the rebel movement, as well as the groups’ abilities to punish defectors for nonparticipation.
+Foreign fighters would appear to be amply motivated to fight, given their decision to relocate from their home country which is sometimes in the region but other times requires them to travel large distances.
+
+Similarly, Sambanis and Shayo (2013) find in their model that “intense ethnic conflict makes people care more about their ethnic group relative to other groups, and seek to resemble it more [@Sambanis_Shayo_2013].” As ethnic conflict intensifies, groups seeking to become more quintessentially like the typical member of their ethnic group, this should be manifested in their language on social media.
+Social medial should reflect this delineation amongst ethnic groups and between them.
+However, this may also include a general identification across ethnic groups in a membership of an opposition to an oppressive leader.
+
+It is this general identification with the larger opposition movement, not the individual identity groups within Syria, which we seek to understand in this paper.
+It is implausible to expect there to be one cohesive narrative from the multiple groups with disparate incentives.
+However, they do have important similarities, namely, they are all interested in opposing the current Syrian regime using largely violent means, although there are notable and regular instances of nonviolent protests on Fridays, following prayer services.
+Thus, what we are able to capture in this study is the degree to which all opposition movements to the Syrian government have a similar content and tone, with a similar ebb and flow.
+It should be increasingly threatening to the regime if the rebel movement across the disparate groups is growing stronger and more unified, represented by similar language used across groups.
+
+The civil war literature has further explored the role of social cohesion in detail.
+Collier and Hoeffler identified the role of social homogeneity as having an increased likelihood on social conflict, especially when the society is polarized [@Collier_Hoeffler_2004].
+Cederman and Girardin  write that, “In general, nationalist groups derive their cohesion from collective-level identities that resonate deeply with the emotional needs of modern citizens.” Sambanis and Schulhofer-Wohl note that “group cohesion and solidarity (underlie) the offensive advantage (Sambanis & Schulhofer-Wohl, 2009).” Anyanwu (2002) writes, “Another source of rebel military opportunity is social cohesion…an ethnically diverse society may reduce the opportunity for rebellion by limiting the recruitment pool [@Anyanwu_2002].” Referencing Gurr’s work on minorities at risk, Regan and Norton (2005) note that “a religious or linguistic minority might suffer disproportionately in a given society, and this form of aggrievement can lead to unrest across the social lines that distinguish the minority group.
+Therefore, while collective cohesion is a function of targeted maldistributions, it is individual penury that allows for this collective mobilization [@Gurr_2000; @Regan_Norton_2005].” Thus scholarship concurs that group cohesion matters to group mobilization; we add to this concept by introducing the role of language in facilitating cohesion.
 

### 2020-06-01 manuscript.tex
Integrating Leah's edits pt. 2

@@
 
-\hypertarget{social-cohesion-and-social-mobilization}{%
-\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}
+\hypertarget{lexical-cohesion-connectedness-of-words}{%
+\subsection{Lexical cohesion: Connectedness of words}\label{lexical-cohesion-connectedness-of-words}}
+
+The words that comprise social media posts are the first level at which cohesion occurs.
+In Figure 1, we see four sequential tweets, each containing four words.
+Each sequential tweet contains some content included in the previous tweets.
+The linguistic construct of content word overlap measures the relationship across units of meaning -- here, tweets -- where identical and semantically similar words are repeated ({\textbf{???}}).
+These repeated lexical items constitute a theme; on Twitter, this might be a particular hashtag, a name, a location, or other nominal category.
+This localized cohesion is referential; words are repeated and co-referred across tweets, creating a sense of continuity and cohesiveness of meaning and message.
+
+Lexical cohesion also includes latent semantic analysis (LSA) {[}({\textbf{???}}).
+LSA measures semantic similarity across meaning units using a statistical method called singular value decomposition, an automated method used to detect plagiarism ({\textbf{???}}; {\textbf{???}}).
+In this process, each meaning unit (tweet) is a weighted vector, and the match between the tweets is measured as the cosine between the two vectors.
+This process provides an empirical relationship between the words used from one tweet to the next.
+We identify this as lexical cohesion.
+
+The concept of lexical, or semantic, cohesion has already been applied to the analysis of political speech, for example the language of Margaret Thatcher, as well as non-political speech ({\textbf{???}}; {\textbf{???}}).
+McNamara and Graesser operationalize the concept of cohesion in their software, Coh-Metrix, an automated tool that analyzes text and discourse {[}({\textbf{???}}); ({\textbf{???}}); ({\textbf{???}}).
+This software generates measures of co-referential cohesion that captures the amount of overlap in content words (as opposed to function words, like a, the, and and) in adjacent, local, and global sentences in the passage.
+Content word overlap refers to the proportion of words and word stems that are shared between sentences.
+A higher proportion of overlap indicates greater cohesion in the sentence.
+
+In estimating cohesion in Twitter posts, tweets that share content words and stems will yield higher cohesion values, even amongst speakers with opposing views on the subject matter.
+Repetition of terms and concepts is captured by reiteration, which is a type of lexical cohesion in which a subsequent item repeats a previous item, or refers to it through synonymous language ({\textbf{???}}).
+In social media, we can conceive of retweets -- reposts or forwards of previous messages in part or in whole -- as a form of reiteration that increase message cohesion.
+Since retweets replicate verbatim some part of another tweet, these tweets would also have higher cohesion.
+Hashtags function similarly, and are included in our analysis.
+
+\hypertarget{interlocutor-cohesion}{%
+\subsection{Interlocutor cohesion}\label{interlocutor-cohesion}}
+
+Lexical cohesion contributes to the next level of relatedness among tweets: interlocutor cohesion.
+This is the degree to which people in a conversation, whether in person or online, have aligned their language ({\textbf{???}}).
+Known as communication accommodation theory, the degree of alignment between speakers reveals their closeness, status, and deliberative strategy ({\textbf{???}}).
+Speakers can converge and diverge in their communication.
+Convergence facilitates easier transmission of information, because the speakers -- or interlocutors -- presume some existing familiarity or knowledge base between them.
+When you know someone well enough to finish their sentence, this is an example of convergence.
+Divergence, on the other hand, is more laborious because the speakers must make their presumptions explicit and tacit.
+Interlocutor cohesion, or convergence, happens when speakers are \enquote{singing in the same key} or are \enquote{on the same page.} Windsor (2020) describes various types of cohesion, using the example of the Occupy Wall Street movement as a symbol of divergence given the myriad signs, slogans, and interests of the participants ({\textbf{???}}).
+On the other hand, the \enquote{I am a man} protest captured by Ernest Withers during the 1968 santiation workers' strike in Memphis, TN, or the \enquote{Black Lives Matter} placards following the uprising in Ferguson, MO, symbolize convergence and strong interlocutor cohesion ({\textbf{???}}).
+
+Cognitive and social psychology theories of alignment and coordination lend themselves nicely to the study of social media communication during times of conflict and contentious behavior ({\textbf{???}}; {\textbf{???}}; {\textbf{???}}).
+Over the past few decades, this area has garnered significant attention and produced evidence showing that people sometimes linguistically and behaviorally align as they interact more ({\textbf{???}}; {\textbf{???}}).
+Similarly, accommodation theory refers to the ways in which individuals and groups linguistically adapt to minimize the social space distance.
+Speakers in a collective setting pursue strategies which increase their common ground, and this is reflected in the language they use to communicate with one another.
+
+A similar process happens among participants in social media discussions.
+The process of speakers' (or tweeters) language becoming more similar is called linguistic style matching (LSM) ({\textbf{???}}).
+LSM is a form of synchrony between speakers, akin to linguistic convergence.
+As Bernieri and Rosenthal (1991) describe, people engaged in linguistic synchrony match each others' verbal behaviors, adopting not only similar terms, but similar patterns of language ({\textbf{???}}).
+For example, LSM is particularly evident when one speaker introduces swearing into a genteel conversation; the first usage opens the vulgarity floodgates, and subsequent speakers may repeat the initial curse, as well as innovate new curses into the conversation.
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline contextualized by variation in real world events.
+Interlocutor cohesion may increase preceding an in-person social mobilization event, alerting a repressive government that collective mobilization is happening.
+Interlocutor cohesion may also respond to exogenous events such as spontaneous, unprovoked militarized conflict.
+If government forces target a new location using military weapons, this can precipitate online mobilization and discussion of the event.
+
+\hypertarget{social-and-physical-cohesion}{%
+\subsection{Social and Physical Cohesion}\label{social-and-physical-cohesion}}
+
+In turn, other studies show that linguistic alignment leads to increased social connectedness and solidarity ({\textbf{???}}), which is associated with increased motivation for participation ({\textbf{???}}), facilitating successful coordination of group actions toward shared goals ({\textbf{???}}; {\textbf{???}}).
+This research emphasizes both the importance of and connections between linguistic alignment and behavioral alignment.
+The more people interact, the more similar their language and linguistic patterns become.
+This holds true for face-to-face interactions as well as online communication {[}({\textbf{???}})\}.
+Given this, we should expect to see increased linguistic cohesion amongst people participating in online discussions about an idea, event, or individual.
+Given that social media reports in real time about actual events taking place, i.e., protests or demonstrations in which people are assembled together in a location, or attacks that require coordination between members of a unit, the cohesion in social media should be expected to correlate with the social cohesion of the group {[}({\textbf{???}})\}.
+
+A socially cohesive group is inherently more threatening to the existing regime because it reflects the professionalization of potential alternate leadership, and collective opposition momentum.
+Groups with high social cohesion are more difficult to divide and conquer, and more cohesive messages may also garner increased international support.
+A paper published in Nature argues that global insurgency movements all exhibit a similar pattern to their social structure {[}({\textbf{???}})\}.
+The authors assert that each violent group has a stable state, and that exogenous events can create perturbations that push the group to become more cohesive, or alternatively to become more fragmented.
+Rather than frenetic, patchwork messages via Twitter, cohesive messages indicate increased organizational structure, which should incentivize a response from the government.
+What process is the driving force, though?
+Does an increase in linguistic cohesion precede or follow increased repression by the government?
+Do movements get stronger first, and then the government responds, or does the government increase its offensive measures, and thus social groups have a clear opponent around whom they can coalesce both socially and linguistically?
+
+Thus, verbal synchrony leads to physical synchrony.
+Shared language in an online environment can influence individuals' propensity to engage in similar coordinated behavior.
+In the case of the Arab Spring, this may mean social mobilization in public spaces to protest against government brutality.
+Words in a passage of text -- or series of tweets -- have some degree of semantic relation.
+Individuals engaged in a conversation, whether in real life or online, have the tendency to use similar language as they interact, increasing the cohesion of their language.
+As an extension, multiple individuals collectively communicating can also demonstrate linguistic alignment.
+In the context of social conflict, the linguistic cohesion of participants in the online conversation should correspond to the degree of social cohesion on the ground.
+We link these concepts of social and linguistic cohesion together to demonstrate how language serves as an indicator of the degree of social mobilization, using Twitter feeds during the spring of 2012 in Syria.
 
@@
 community-level social cohesion.
+
+Physical and social cohesion in the world can be modeled using event data which encodes who does what to whom on a given day.
+This could include events such as the government (GOV) imposing a blockade or fighting with artillery or tanks on a civilian group (CIV).
+CAMEO (Conflict and Mediation Event Observations) encode a set of activities with numerical values, rescaled to reflect a conflict-cooperation scale ({\textbf{???}}; {\textbf{???}}).
+These event codes include a range of behaviors, from making public statements and appeals, to demanding, threatening, protesting, and using unconventional mass violence.
+Steinert-Threlkeld (2017) modeled a similar relationship between social media and social mobilization using a Gini coefficient measure, rather than a tf-idf (term frequency-inverse document frequency) measure alongside event data ({\textbf{???}}; {\textbf{???}}).
+This pathbreaking work demonstrates that participants on the fringe of a social movement contribute substantially to the overall level of protest.
+We add to this discussion by demonstrating how sociolinguistic cohesion evolves in response to negative and positive exogenous events.
+
+\hypertarget{cohesion-in-social-movements-and-civil-wars}{%
+\subsubsection{Cohesion in Social Movements and Civil Wars}\label{cohesion-in-social-movements-and-civil-wars}}
+
+People join social and political resistance movements because they feel a sense of connection to the cause, and because they have been sufficiently convinced to participate.
+Given that people are generally risk averse, overcoming inertia requires a strong connection to the group identity, or against an individual, event, or political injustice {[}({\textbf{???}}); Goldstone\_2011{]}.
+Political resistance offers participants the opportunity to \enquote{lose themselves} and relinquish their individual identity in favor of identification with a larger group identity, thus contributing to a cohesive group ready and mobilized for action {[}({\textbf{???}}).
+Previous research on social movements supports the idea that participants are likely to join movements when they know and have a personal connection to someone else already involved {[}({\textbf{???}}).
+The type of collective contentious behavior that manifests in society is a function of the available political opportunity structures.
+The political opportunity structure, as defined by Kitschelt (1986) are \enquote{comprised of specific configuration of resources, institutional arrangements and historical precedents for social mobilization, which facilitate the development of protest movements in some instances and constrain them in others ({\textbf{???}}).} What emerges as strategies and tactics in contentious politics is in essence, a function of what the system makes possible.
+This includes the number of people and their disposition, i.e.~nonviolent or violent, as well as their internal structure.
+The more cohesive a group is, the greater threat they pose to the establishment.
+
+Cohesion is also a familiar concept in the study of civil conflicts as it pertains to group affiliation and the ability to overcome collective action problems.
+Olson's (Olson, 1965) seminal work on collective action informs the theory of group behavior.
+Individuals must act in concert -- cohesively -- to accomplish the task of challenging the authority of the state.
+Building on Eisinger's (1973) analysis of social protest movements {[}({\textbf{???}}), McAdam, Tilly and Tarrow {[}({\textbf{???}}), and Francisco {[}({\textbf{???}}) have provided foundational work on the dynamics of social movements and contentious behavior.
+More recently, Gates (2002) considers rebel recruitment for participation in civil conflicts as a function of internal cohesion ({\textbf{???}}).
+He notes that rebel movement success is influenced by the degree of group cohesion, which itself is a function of geographic distance, ideology and ethnicity.
+
+There are multiple rebel groups within Syria, some with fighters sourced locally from the disaffected Syrian population, and an increasing number of foreign fighters from transnational terrorist organizations.
+Gates' work helps us understand the intergroup competition for participation in the rebel movement, as well as the groups' abilities to punish defectors for nonparticipation.
+Foreign fighters would appear to be amply motivated to fight, given their decision to relocate from their home country which is sometimes in the region but other times requires them to travel large distances.
+
+Similarly, Sambanis and Shayo (2013) find in their model that \enquote{intense ethnic conflict makes people care more about their ethnic group relative to other groups, and seek to resemble it more ({\textbf{???}}).} As ethnic conflict intensifies, groups seeking to become more quintessentially like the typical member of their ethnic group, this should be manifested in their language on social media.
+Social medial should reflect this delineation amongst ethnic groups and between them.
+However, this may also include a general identification across ethnic groups in a membership of an opposition to an oppressive leader.
+
+It is this general identification with the larger opposition movement, not the individual identity groups within Syria, which we seek to understand in this paper.
+It is implausible to expect there to be one cohesive narrative from the multiple groups with disparate incentives.
+However, they do have important similarities, namely, they are all interested in opposing the current Syrian regime using largely violent means, although there are notable and regular instances of nonviolent protests on Fridays, following prayer services.
+Thus, what we are able to capture in this study is the degree to which all opposition movements to the Syrian government have a similar content and tone, with a similar ebb and flow.
+It should be increasingly threatening to the regime if the rebel movement across the disparate groups is growing stronger and more unified, represented by similar language used across groups.
+
+The civil war literature has further explored the role of social cohesion in detail.
+Collier and Hoeffler identified the role of social homogeneity as having an increased likelihood on social conflict, especially when the society is polarized ({\textbf{???}}).
+Cederman and Girardin write that, \enquote{In general, nationalist groups derive their cohesion from collective-level identities that resonate deeply with the emotional needs of modern citizens.} Sambanis and Schulhofer-Wohl note that \enquote{group cohesion and solidarity (underlie) the offensive advantage (Sambanis \& Schulhofer-Wohl, 2009).} Anyanwu (2002) writes, \enquote{Another source of rebel military opportunity is social cohesion\ldots{}an ethnically diverse society may reduce the opportunity for rebellion by limiting the recruitment pool ({\textbf{???}}).} Referencing Gurr's work on minorities at risk, Regan and Norton (2005) note that \enquote{a religious or linguistic minority might suffer disproportionately in a given society, and this form of aggrievement can lead to unrest across the social lines that distinguish the minority group.
+Therefore, while collective cohesion is a function of targeted maldistributions, it is individual penury that allows for this collective mobilization ({\textbf{???}}; {\textbf{???}}).} Thus scholarship concurs that group cohesion matters to group mobilization; we add to this concept by introducing the role of language in facilitating cohesion.
 

### 2020-06-01 manuscript.Rmd
Update interpretations for target-only WCRQA

@@
 ### Syria as Target
-The time period of differing dynamics---from observation 38 through 
-43---appears to be captured by the RR and DET values in
-WCRQA of social cohesion and count of negative
-events (Figure \@ref(fig:plot-wcrqa-targ-all)). The
-amount of recurrence and determinism for these periods almost consistently
-lie above chance, suggesting that the intensity of negative events coincide
-with the degree of social cohesion found on Twitter and that these 
-shared trajectories extend across multiple days.
-
-The above-chance levels of determinism and recurrence rate demonstrate
-the coupling of social cohesion to both total and negative events during
-times of strife. During this period, 
+The time period of differing dynamics noted in the cross-recurrence
+plots---from observation 32 through 47---appears to be captured 
+by the above-chance RR values in WCRQA of social cohesion and count of all
+events (Figure \@ref(fig:plot-wcrqa-targ-all)). However,
+DET for these periods only intermittently
+rises above chance; it more consistently reaches statistical
+significance only at the end of the window through the end of the observation
+period, following a spike in the RR between
+negative event count and social cohesion. 
+During this period, 
 the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
-during May 1st--15th was almost consistently -10, the most violent 
-event category. These dates directly correlate with the above-chance RR and DET
-metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during
-this time period, DET was entirely within chance (Figure
-\@ref(fig:plot-wcrqa-targ-all)). This supports our hypothesis, as the
-positive events are seemingly not coupled with the social cohesion on Twitter
-during civil uprisings during the Arab Spring.
+was almost consistently -10, the most violent 
+event category. This supports our first hypothesis.
+
+Surprisingly---and contrary to our second hypothesis---we saw consistent
+coupling between positive event count and social cohesion. Although
+both had a downward trajectory throughout the time period under consideration,
+RR was at or above chance in nearly all windows, and DET showed
+much more consistent shared trajectories than negative events.
+This may suggest that Syrian Twitter community was reacting more cohesively
+to the positive events aimed at Syria from the international community;
+this interpretation is supported by the attenuation of the effect in the
+analyses that include Syria as both a source and a target.
 

### 2020-06-01 manuscript.Rmd
Update interpretations for soruce and target WCRQA

@@
 ### Syria as Source and Target
-WCRQA of recurrence rate on the source and target filtered data remained
-largely the same for count of all events and social cohesion, suggesting
-that large numbers on a given day will be reflective of increased levels
-of social cohesion. DET showed more frequent above-chance metrics
-for windows 39 and up, suggesting that the inclusion of externally
-directed events lead to higher event counts during these days and then
-was more reflective of the level of social cohesion on Twitter.
-
-WCRQA metrics for positive-only and negative-only event counts with 
-social cohesion remained largely the same for
-RR and DET as the source-only data. This may support the ideas suggested
+WCRQA on the source-and-target-filtered data showed similar
+patterns of RR between the count of all events and social cohesion
+(as observed in the target-only data), 
+though the values increased. This suggests
+that large numbers on a given day match increased levels
+of social cohesion online. However, the results for DET changed:
+While the majority of statistically significant DET windows
+occurred toward the end of the observation period for target-only
+data (creating a positive trendline), the source-and-target data
+showed a negative trendline for DET.
+
+The divergences in the all-event count data for these two
+datasets underscores the differences
+between RR and DET. As noted earlier, DET captures *trajectories*---in
+this case, similar to the impact of actions and social cohesion
+carrying across time. The same number of points (RR) can fall in
+different patterns (DET), providing important information
+about the structure of the system in question.
+
+WCRQA metrics for positive-only event counts with social cohesion showed 
+similar patterns in RR and DET as the target-only data, but the precise
+values of DET and RR were diminished. This may support the ideas suggested
 in the CRQA section, but again, only future work including the *content*
 of those tweets can directly speak to that explanation.
+
+Finally, the coupling between negative-only event counts and
+social cohesion also remained relatively similar but demonstrated some 
+important differences. First, we see a greater number of windows at
+above-chance levels for RR, including an interesting spike around window
+32 that suggests a negative externally focused action taken by Syria
+prompted a sharp rise in social cohesion. (This would not have been
+captured by the target-only dataset.) Second---like with the all-event
+data---we see different structuring of the data through differences
+in the patterns of DET; above-chance DET only occurrs within the middle
+of the observation period, around a time of increased strive (as
+noted above).
 

### 2020-06-01 manuscript.Rmd
Add clarity by labeling hypotheses

@@
 The significant result of DET for social cohesion with all and negative 
-events supports our hypothesis that event salience is coupled with online 
+events supports our first hypothesis that event salience is coupled with online 
 social cohesion. The frequency of all and negative events are thus associated 
@@
 by chance. However, when we specifically target positive events, the connection
-to social cohesion fades, providing further support for our hypothesis. 
+to social cohesion fades, providing further support for our second hypothesis. 
 Positive events may be less coupled to social cohesion than more salient 

### 2020-06-01 manuscript.Rmd
Update abstract

@@
   found in Syrian tweets. Results indicate that virtual social cohesion is 
-  coupled with the counts of all and negative events each day but not with 
-  counts of positive events. This suggests that virtual mobilization does reflect 
-  real-world movements but only for salient, frequent and negative events. We 
+  coupled with the counts of all and negative events each day but shows a more
+  nuanced connection to positive events, only visible when examining finer-grained
+  data. This suggests that virtual mobilization does reflect 
+  real-world movements, with the strongest connections to the frequency of all
+  events and the frequency of negative events. We 
   conclude with a discussion of implications and applications of nonlinear 

### 2020-06-01 manuscript.Rmd
Update Acknowledgements
Update Implications section

@@
 
-## Implications
-
-### Implications for Methodology
+## Implications for Methodology and Theory
 
@@
 
-### Implications for Theory
-
-This methodology should be of great interest to social scientists investigating social mobilization.
-It has potential applications for gender studies and the #MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests.
-Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life.
-Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior.
-If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.
+This methodology should be of great interest to social scientists 
+investigating social mobilization. It has potential applications for 
+gender studies and the #MeToo movement and for the relationship between 
+social protest and repression during the Black Lives Matter protests. 
+Fundamentally, this methodological approach can help us better understand
+the human social mechanisms underlying social media and its influence on human 
+behavior in real life. Given that many governments enact repressive 
+measures when they determine that collective action by citizens is
+imminent, this methodology should help to improve 
+the predictive power of using social media data in estimating repressive 
+behavior. If social media messages are increasing in cohesion, this may 
+represent a threat to civil and political liberties of citizens engaging
+in collective action.
 
@@
 
-### Acknowledgements
+# Acknowledgements
+
+This work was completed in part as coursework done by lead author M. Chiovaro
+in the ``Applications of Nonlinear Time Series Analysis'' graduate
+course at the University of Connecticut (co-taught by coauthor A. Paxton and
+Steven J. Harrison).
 

### 2020-06-01 manuscript.Rmd
Update Conclusion

@@
 dynamics analyses, our results have serious implications for monitoring global
-movements in consistent across other social uprisings. While traditional, 
+movements in consistent across other social uprisings. While  
 state-run media in regions of authoritarian rule are often biased and 
-propaganda for the leader and central government, the 
-self-organized nature of Twitter poses a new avenue to gain insight into 
-truths about up-risings and social mobilization. By conceptualizing Twitter 
+serve as propaganda for the leader and central government, the 
+self-organized nature of Twitter provides a new avenue to gain insight into 
+truths about uprisings and social mobilization. By conceptualizing Twitter 
 and real-world events as two elements of an inextricably linked dynamical 

### 2020-06-01 manuscript.Rmd
Formatting for equations

@@
 \begin{align}
-\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k
+\frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
 \end{align}
@@
 \begin{align}
-\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i,
+d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
 \end{align}
@@
 \begin{align}
-\text{Two tweets similarity =}\frac{\text{inverse frequency weighting of overlap words}}{\text{inverse frequency weighting of all words}}
+\text{Two tweets' similarity =}\frac{\text{inverse frequency weighting of overlap
+words}}{\text{inverse frequency weighting of all words}}
 \end{align}

### 2020-06-01 manuscript.Rmd
Reformatted hard wrap for text

@@
 
-Prior to the advent of social media, people coordinated their protest behavior using phone tree calling sheets and flyers generated on mimeograph machines, through in-person meetings for social organizations and in churches, and through word of mouth.
-They gathered together and hand-made protest signs that reflected their agendas.
-As McAdam found, people were more likely to join movements when they had a personal connection [@McAdam_1986; @McAdam_1986].
-Strong ties were better predictors of involvement in high-risk protest activity.
-However, the era of the Internet and online social mobilization through decentralized networks has upended theories about recruitment to, and participation in, social movements.
-Strong interpersonal ties have yielded to weak impersonal ties that strongly predict involvement in social movements [@Threlkeld_2017].
-The research methodologies for measuring social movements have similarly evolved from ethnographic interviews to big data analysis of language on social media.
-The cohesiveness and strength of social movements in the pre-Internet era could be operationalized by the number of people turning out to protest, and through the political events that precipitated and resulted from social gatherings en masse.
-
-In the offline era of social mobilization, the content of placards and protest signs provided the protest narrative for onlookers near and far.
-For cohesive social movements, the content of placards and posters itself was cohesive.
-For example, the “I am a man” posters held by the men involved in the 1968 sanitation workers’ strike reflected their internal cohesion and unified, goal-oriented movement [@Windsor_2020].
-Social media replicates and amplifies this phenomenon during moments of social unrest.
-Amid the cacophony of messages during political upheaval, such as the Arab Spring, consistent themes emerge through hashtags, retweets, and the repeated mentions of concepts such as regime, security, demonstration, and human rights.
-The cohesiveness of these themes, i.e., whether movement participants are “singing in one voice,” reflects the real-world events happening contemporaneously with collective action in social movements or civil conflicts.
-
-In the present research, we investigate the relationship between linguistic cohesion and social cohesion in times of social conflict and unrest.
-We tackle a question related to the one posed by Zeitzoff (2017): how does social media reflect on-the-ground realities during times of social conflict [@Zeitzoff_2017]?
-We examine patterns of linguistic cohesion on Twitter during the Arab Spring uprising in Syria between March and June 2012.
-We contextualize the linguistic cohesion with social mobilization and response to the relative intensity of the conflict.
-Cohesion is a multi-layered concept referring to the connectedness of words, thoughts, speakers, and actions.
-Cohesion reflects the continuity of language and expression, and it shows the connectivity of participants in a social movement.
-To address the relationship between language and discourse and social movements, we adopt an interdisciplinary approach that incorporates linguistics, psychology, and political science using non-linear dynamical systems methodology to model the relationship between language and action.
-We find that in the early months of 2012, conflict-related events were more strongly associated with linguistic cohesion than were more neutral or peaceful events.
-
-Disentangling the complicated relationship between mass online mobilization, and social mobilization in person, continues to be a relevant question.
-The political processes that transpired during and after the Arab Spring are still in the process of being understood.
-As Zeitzoff (2017) recognizes, social media is changing conflict, but the mechanisms and relationships are still being understood [@Zeitzoff_2017].
+Prior to the advent of social media, people coordinated their protest behavior
+using phone tree calling sheets and flyers generated on mimeograph machines,
+through in-person meetings for social organizations and in churches, and through
+word of mouth. They gathered together and hand-made protest signs that reflected
+their agendas. As McAdam found, people were more likely to join movements when
+they had a personal connection [@McAdam_1986; @McAdam_1986]. Strong ties were
+better predictors of involvement in high-risk protest activity. However, the era
+of the Internet and online social mobilization through decentralized networks
+has upended theories about recruitment to, and participation in, social
+movements. Strong interpersonal ties have yielded to weak impersonal ties that
+strongly predict involvement in social movements [@Threlkeld_2017]. The research
+methodologies for measuring social movements have similarly evolved from
+ethnographic interviews to big data analysis of language on social media. The
+cohesiveness and strength of social movements in the pre-Internet era could be
+operationalized by the number of people turning out to protest, and through the
+political events that precipitated and resulted from social gatherings en masse.
+
+In the offline era of social mobilization, the content of placards and protest
+signs provided the protest narrative for onlookers near and far. For cohesive
+social movements, the content of placards and posters itself was cohesive. For
+example, the “I am a man” posters held by the men involved in the 1968
+sanitation workers’ strike reflected their internal cohesion and unified,
+goal-oriented movement [@Windsor_2020]. Social media replicates and amplifies
+this phenomenon during moments of social unrest. Amid the cacophony of messages
+during political upheaval, such as the Arab Spring, consistent themes emerge
+through hashtags, retweets, and the repeated mentions of concepts such as
+regime, security, demonstration, and human rights. The cohesiveness of these
+themes, i.e., whether movement participants are “singing in one voice,” reflects
+the real-world events happening contemporaneously with collective action in
+social movements or civil conflicts.
+
+In the present research, we investigate the relationship between linguistic
+cohesion and social cohesion in times of social conflict and unrest. We tackle a
+question related to the one posed by Zeitzoff (2017): how does social media
+reflect on-the-ground realities during times of social conflict
+[@Zeitzoff_2017]? We examine patterns of linguistic cohesion on Twitter during
+the Arab Spring uprising in Syria between March and June 2012. We contextualize
+the linguistic cohesion with social mobilization and response to the relative
+intensity of the conflict. Cohesion is a multi-layered concept referring to the
+connectedness of words, thoughts, speakers, and actions. Cohesion reflects the
+continuity of language and expression, and it shows the connectivity of
+participants in a social movement. To address the relationship between language
+and discourse and social movements, we adopt an interdisciplinary approach that
+incorporates linguistics, psychology, and political science using nonlinear
+dynamical systems methodology to model the relationship between language and
+action. We find that in the early months of 2012, conflict-related events were
+more strongly associated with linguistic cohesion than were more neutral or
+peaceful events.
+
+Disentangling the complicated relationship between mass online mobilization, and
+social mobilization in person, continues to be a relevant question. The
+political processes that transpired during and after the Arab Spring are still
+in the process of being understood. As Zeitzoff (2017) recognizes, social media
+is changing conflict, but the mechanisms and relationships are still being
+understood [@Zeitzoff_2017].
 
 ## Syria in context
-The decades prior to the onset of the Arabs Spring in Syria were marked by social repression and fear.
-In 1971, Hafez al-Assad overthrew the previous leader and remained in power for thirty years, presiding during times of regional contentiousness and cooperation until his death in 2000.
-His son, Bashar al-Assad, who continued the regime of authoritarian leadership, assumed his office.
-The Assad lineage hails from a minority Islamic sect, the Alawites, in a multi-religious and multi-ethnic country comprised of Christians, Sunni and Shia Muslims, Kurds, and Palestinian refugees.
+The decades prior to the onset of the Arabs Spring in Syria were marked by
+social repression and fear. In 1971, Hafez al-Assad overthrew the previous
+leader and remained in power for thirty years, presiding during times of
+regional contentiousness and cooperation until his death in 2000. His son,
+Bashar al-Assad, who continued the regime of authoritarian leadership, assumed
+his office. The Assad lineage hails from a minority Islamic sect, the Alawites,
+in a multi-religious and multi-ethnic country comprised of Christians, Sunni and
+Shia Muslims, Kurds, and Palestinian refugees.
 
@@
 unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian
-rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death,
-Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
-country. The events of Tunisia rapidly spread to surrounding countries 
-also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
-and Syria.
-
-Following a wave of democratization efforts across the Middle East and North Africa, protests began modestly in Syria in March 2011.
-The regime responded harshly with imprisonments, detentions, censorship, and military operations as the resistance to Assad’s regime grew and spread throughout the country.
-The fighting escalated in earnest in March 2012, after increased unrest in the western city of Homs.
-International actors, including the Red Cross/Red Crescent Society, the United Nations General Assembly, the Security Council, and individual leaders throughout the world worked toward cease-fires, negotiations, and concessions, without much success.
-While many high-level military and diplomatic officials have defected from the regime, sufficient loyal forces have been able to execute continued repression.
-During this time between March and June 2012, more than eight million tweets were sent within Syria revealing the details of the conflict.
-
-Syria is a multi-ethnic, multi-lingual, and multi-religious state.
-Kurdish people comprise between 10-15% of the population, Alawites between 8-15%, Christians about 10%.
-There are also much smaller sects, i.e.
-the Ismailis and Druze, but Sunni Muslims comprise the vast majority of society, and most people speak Arabic as their mother tongue.
-Most policy reports addressing the current conflict report on the cohesion of the ruling Alawite military elite, rather than on the cohesiveness of the opposition movement.
-However, the Sunni majority’s disaffection with the Syrian government and lack of political representation provide sufficient grievance and collective group identification to make them a cohesive force.
+humiliation led him to set himself on fire in protest to the authoritarian rule,
+ultimately leading to his death several days later. His actions served as a
+catalyst for the Tunisian Revolution, and one week after his death, Zine El
+Abidine Ben Ali---the longstanding authoritarian president---fled the country.
+The events of Tunisia rapidly spread to surrounding countries also subject to
+unjust authoritarian rule, including Yemen, Egypt, Libya, and Syria.
+
+Following a wave of democratization efforts across the Middle East and North
+Africa, protests began modestly in Syria in March 2011. The regime responded
+harshly with imprisonments, detentions, censorship, and military operations as
+the resistance to Assad’s regime grew and spread throughout the country. The
+fighting escalated in earnest in March 2012, after increased unrest in the
+western city of Homs. International actors, including the Red Cross/Red Crescent
+Society, the United Nations General Assembly, the Security Council, and
+individual leaders throughout the world worked toward cease-fires, negotiations,
+and concessions, without much success. While many high-level military and
+diplomatic officials have defected from the regime, sufficient loyal forces have
+been able to execute continued repression. During this time between March and
+June 2012, more than eight million tweets were sent within Syria revealing the
+details of the conflict.
+
+Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
+people comprise between 10-15% of the population, Alawites between 8-15%,
+Christians about 10%. There are also much smaller sects, i.e. the Ismailis and
+Druze, but Sunni Muslims comprise the vast majority of society, and most people
+speak Arabic as their mother tongue. Most policy reports addressing the current
+conflict report on the cohesion of the ruling Alawite military elite, rather
+than on the cohesiveness of the opposition movement. However, the Sunni
+majority’s disaffection with the Syrian government and lack of political
+representation provide sufficient grievance and collective group identification
+to make them a cohesive force.
 
 ## Social Media and Social Movements
-During the Arab Spring, social media provided real-time information about the events transpiring in countries across the Middle East and North Africa.
-Our understanding about the role of social media in social movements is still evolving.
-Some argue that these mass movements would not have been possible without
-efficient large-scale coordination, both physically on the ground and virtually 
-on social media platforms. Along with Facebook, Twitter has been credited as 
-essential to the Arab Spring---both for protesters (as a means to coordinate 
-with one another and to communicate with the world) and for the government 
-response (to monitor and track protestors to crack down on dissent) 
-[@comninos2011twitter]. The events of Arab Spring have been thoroughly 
-discussed within the political science literature 
-[e.g., @lutterbeck2013arab; @koehler2017political], but to our knowledge,
-the direct *coupling* between Syrian Twitter cohesion and international action
-coordination has not been investigated. Others provide skepticism about the effect of social media on collective action [@Seay_2014].
-
-In Foreign Affairs, Anderson writes that, “The important story about the 2011 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the norms of civic engagement shaped the protesters' aspirations.
-Nor is it about how activists used technology to share ideas and tactics.
-Instead, the critical issue is how and why these ambitions and techniques resonated in their various local contexts [@Anderson_2011].” Malcolm Gladwell, in highlighting the notions of strong and weak ties, @Gladwell_2010 and @McAdam_1986, similarly expressed hesitation about the role of online organizing, arguing that real-life strong ties outweigh online weak ties and that participation in online activism only requires scant sacrifices whereas recruitment to higher-risk activities is done through in-person contact, namely strong ties [@Gladwell_2010; [@McAdam_1986].
-Interestingly, these views may actually help to make the case for bridging the gap between social media and social mobilization, by suggesting the strength of social ties in an online environment is inextricably linked to the context and ambitions of the actors.
-Granovetter notes that while strong ties tend to bind smaller groups, weak ties tend to bind groups across distances [@Granovetter_1973].
-
-Social media generates critical information about events, such as whether or not a demonstration will take place and what transpires when it does, how many people participate, and how the state, the military, and the security apparatus respond.
-Similarly, these media platforms alert us to more global shifts within a conflict, such as when fighting moves to a new city or region, the number of casualties and wounded, and the types of weaponry used by parties to the conflict [@Zeitzoff_2017].
-Social media is not entirely event-driven, however.
-In monitoring social media channels, government forces may respond to the perception that citizens are gaining strength and sympathy.
-Governments have been shown to be quite tolerant of dissent so long as it does not metamorphosize into collective action [@King_Pan_Roberts_2013].
-Additionally, the insulated nature of online social platforms allows valuable social dynamics to be detailed at unprecedented resolution and scale.
-As such, the digital traces left by individuals and collectively as groups are regarded as a valuable source of information that can offer powerful insights into states of social disequilibrium, up-risings, and escalations into civil wars.
-
-Citizens communicate with each other with increased transparency due to the ubiquitous availability of social media such as low-cost and egalitarian platforms like Twitter.
-Citizens are able to access these tools via mobile phones and computers with Internet connectivity, providing a stream of real-time shared information.
-This facilitates studying the degree of cohesion between speakers, and the alignment between that cohesion and their collective political behavior.
-Citizens can tweet the location of events like protests and military incursions, the degree of state repression, and the number of casualties.
-In kind, the government, interested in remaining in power, monitors social media platforms to ascertain emerging threats, such as where new groups are forming and where existing groups are strengthening, where gatherings are held, and who the idea entrepreneurs are.
-An example of a leader manifesting his interest in such public conversation is given in a speech of June 3, 2012 by Bashar al-Assad:
-
-“I know that I have been away from the media for a long time, and I have missed having direct contact with the citizens, but I have always been following up with the daily occurrences and gathering the information so that my speech can be built on what is said by the street.”
+During the Arab Spring, social media provided real-time information about the
+events transpiring in countries across the Middle East and North Africa. Our
+understanding about the role of social media in social movements is still
+evolving. Some argue that these mass movements would not have been possible
+without efficient large-scale coordination, both physically on the ground and
+virtually on social media platforms. Along with Facebook, Twitter has been
+credited as essential to the Arab Spring---both for protesters (as a means to
+coordinate with one another and to communicate with the world) and for the
+government response (to monitor and track protestors to crack down on dissent)
+[@comninos2011twitter]. The events of Arab Spring have been thoroughly discussed
+within the political science literature [e.g., @lutterbeck2013arab;
+@koehler2017political], but to our knowledge, the direct *coupling* between
+Syrian Twitter cohesion and international action coordination has not been
+investigated. Others provide skepticism about the effect of social media on
+collective action [@Seay_2014].
+
+In Foreign Affairs, Anderson writes that, “The important story about the 2011
+Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
+norms of civic engagement shaped the protesters' aspirations. Nor is it about
+how activists used technology to share ideas and tactics. Instead, the critical
+issue is how and why these ambitions and techniques resonated in their various
+local contexts [@Anderson_2011].” Malcolm Gladwell, in highlighting the notions
+of strong and weak ties, @Gladwell_2010 and
+@McAdam_1986, similarly expressed hesitation about the role of online
+organizing, arguing that real-life strong ties outweigh online weak ties and
+that participation in online activism only requires scant sacrifices whereas
+recruitment to higher-risk activities is done through in-person contact, namely
+strong ties [@Gladwell_2010; [@McAdam_1986]. Interestingly, these views may
+actually help to make the case for bridging the gap between social media and
+social mobilization, by suggesting the strength of social ties in an online
+environment is inextricably linked to the context and ambitions of the actors.
+Granovetter notes that while strong ties tend to bind smaller groups, weak ties
+tend to bind groups across distances [@Granovetter_1973].
+
+Social media generates critical information about events, such as whether or not
+a demonstration will take place and what transpires when it does, how many
+people participate, and how the state, the military, and the security apparatus
+respond. Similarly, these media platforms alert us to more global shifts within
+a conflict, such as when fighting moves to a new city or region, the number of
+casualties and wounded, and the types of weaponry used by parties to the
+conflict [@Zeitzoff_2017]. Social media is not entirely event-driven, however.
+In monitoring social media channels, government forces may respond to the
+perception that citizens are gaining strength and sympathy. Governments have
+been shown to be quite tolerant of dissent so long as it does not metamorphosize
+into collective action [@King_Pan_Roberts_2013]. Additionally, the insulated
+nature of online social platforms allows valuable social dynamics to be detailed
+at unprecedented resolution and scale. As such, the digital traces left by
+individuals and collectively as groups are regarded as a valuable source of
+information that can offer powerful insights into states of social
+disequilibrium, up-risings, and escalations into civil wars.
+
+Citizens communicate with each other with increased transparency due to the
+ubiquitous availability of social media such as low-cost and egalitarian
+platforms like Twitter. Citizens are able to access these tools via mobile
+phones and computers with Internet connectivity, providing a stream of real-time
+shared information. This facilitates studying the degree of cohesion between
+speakers, and the alignment between that cohesion and their collective political
+behavior. Citizens can tweet the location of events like protests and military
+incursions, the degree of state repression, and the number of casualties. In
+kind, the government, interested in remaining in power, monitors social media
+platforms to ascertain emerging threats, such as where new groups are forming
+and where existing groups are strengthening, where gatherings are held, and who
+the idea entrepreneurs are. An example of a leader manifesting his interest in
+such public conversation is given in a speech of June 3, 2012 by Bashar
+al-Assad:
+
+“I know that I have been away from the media for a long time, and I have missed
+having direct contact with the citizens, but I have always been following up
+with the daily occurrences and gathering the information so that my speech can
+be built on what is said by the street.”
 
 With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes (2015) notes that regimes can attempt to thwart the growth of social protest online and in the streets by shutting down the Internet [@Gohdes_2015].
+Gohdes (2015) notes that regimes can attempt to thwart the growth of social
+protest online and in the streets by shutting down the Internet [@Gohdes_2015].
 During these times, however, she finds that military repression increases.
-However, government information about the citizens decreases, and as such, many regimes have elected to maintain Internet connectivity as a means of monitoring and surveilling their citizens.
+However, government information about the citizens decreases, and as such, many
+regimes have elected to maintain Internet connectivity as a means of monitoring
+and surveilling their citizens.
 
 ## Lexical cohesion: Connectedness of words
-The words that comprise social media posts are the first level at which cohesion occurs.
-In Figure 1, we see four sequential tweets, each containing four words.
-Each sequential tweet contains some content included in the previous tweets.
-The linguistic construct of content word overlap measures the relationship across units of meaning – here, tweets – where identical and semantically similar words are repeated [@Graesser_McNamara_Louwerse_Cai_2004].
-These repeated lexical items constitute a theme; on Twitter, this might be a particular hashtag, a name, a location, or other nominal category.
-This localized cohesion is referential; words are repeated and co-referred across tweets, creating a sense of continuity and cohesiveness of meaning and message.
-
-Lexical cohesion also includes latent semantic analysis (LSA) [@Graesser_McNamara_Louwerse_Cai_2004.
-LSA measures semantic similarity across meaning units using a statistical method called singular value decomposition, an automated method used to detect plagiarism [@Ceska_2008; @Gamallo_Bordag_2011].
-In this process, each meaning unit (tweet) is a weighted vector, and the match between the tweets is measured as the cosine between the two vectors.
-This process provides an empirical relationship between the words used from one tweet to the next.
-We identify this as lexical cohesion.
-
-The concept of lexical, or semantic, cohesion has already been applied to the analysis of political speech, for example the language of Margaret Thatcher, as well as non-political speech [@Barzilay_Elhadad_1999; @Morris_Hirst_1991].
-McNamara and Graesser operationalize the concept of cohesion in their software, Coh-Metrix, an automated tool that analyzes text and discourse  [@Graesser_Jeon_Yan_Cai_2007; @Graesser_McNamara_Louwerse_Cai_2004; [@Graesser_McNamara_Kulikowich_2011].
-This software generates measures of co-referential cohesion that captures the amount of overlap in content words (as opposed to function words, like a, the, and and) in adjacent, local, and global sentences in the passage.
-Content word overlap refers to the proportion of words and word stems that are shared between sentences.
-A higher proportion of overlap indicates greater cohesion in the sentence.
-
-In estimating cohesion in Twitter posts, tweets that share content words and stems will yield higher cohesion values, even amongst speakers with opposing views on the subject matter.
-Repetition of terms and concepts is captured by reiteration, which is a type of lexical cohesion in which a subsequent item repeats a previous item, or refers to it through synonymous language [@Halliday_Hasan_1976].
-In social media, we can conceive of retweets – reposts or forwards of previous messages in part or in whole – as a form of reiteration that increase message cohesion.
-Since retweets replicate verbatim some part of another tweet, these tweets would also have higher cohesion.
-Hashtags function similarly, and are included in our analysis.
+The words that comprise social media posts are the first level at which cohesion
+occurs. In Figure 1, we see four sequential tweets, each containing four words.
+Each sequential tweet contains some content included in the previous tweets. The
+linguistic construct of content word overlap measures the relationship across
+units of meaning – here, tweets – where identical and semantically similar words
+are repeated [@Graesser_McNamara_Louwerse_Cai_2004]. These repeated lexical
+items constitute a theme; on Twitter, this might be a particular hashtag, a
+name, a location, or other nominal category. This localized cohesion is
+referential; words are repeated and co-referred across tweets, creating a sense
+of continuity and cohesiveness of meaning and message.
+
+Lexical cohesion also includes latent semantic analysis (LSA)
+[@Graesser_McNamara_Louwerse_Cai_2004. LSA measures semantic similarity across
+meaning units using a statistical method called singular value decomposition, an
+automated method used to detect plagiarism [@Ceska_2008; @Gamallo_Bordag_2011].
+In this process, each meaning unit (tweet) is a weighted vector, and the match
+between the tweets is measured as the cosine between the two vectors. This
+process provides an empirical relationship between the words used from one tweet
+to the next. We identify this as lexical cohesion.
+
+The concept of lexical, or semantic, cohesion has already been applied to the
+analysis of political speech, for example the language of Margaret Thatcher, as
+well as non-political speech [@Barzilay_Elhadad_1999; @Morris_Hirst_1991].
+McNamara and Graesser operationalize the concept of cohesion in their software,
+Coh-Metrix, an automated tool that analyzes text and discourse
+[@Graesser_Jeon_Yan_Cai_2007; @Graesser_McNamara_Louwerse_Cai_2004;
+[@Graesser_McNamara_Kulikowich_2011]. This software generates measures of
+co-referential cohesion that captures the amount of overlap in content words (as
+opposed to function words, like a, the, and and) in adjacent, local, and global
+sentences in the passage. Content word overlap refers to the proportion of words
+and word stems that are shared between sentences. A higher proportion of overlap
+indicates greater cohesion in the sentence.
+
+In estimating cohesion in Twitter posts, tweets that share content words and
+stems will yield higher cohesion values, even amongst speakers with opposing
+views on the subject matter. Repetition of terms and concepts is captured by
+reiteration, which is a type of lexical cohesion in which a subsequent item
+repeats a previous item, or refers to it through synonymous language
+[@Halliday_Hasan_1976]. In social media, we can conceive of retweets – reposts
+or forwards of previous messages in part or in whole – as a form of reiteration
+that increase message cohesion. Since retweets replicate verbatim some part of
+another tweet, these tweets would also have higher cohesion. Hashtags function
+similarly, and are included in our analysis.
 
@@
 ## Interlocutor cohesion
-Lexical cohesion contributes to the next level of relatedness among tweets: interlocutor cohesion.
-This is the degree to which people in a conversation, whether in person or online, have aligned their language [@Coupland_Giles_1988].
-Known as communication accommodation theory, the degree of alignment between speakers reveals their closeness, status, and deliberative strategy [@Giles_2016].
-Speakers can converge and diverge in their communication.
-Convergence facilitates easier transmission of information, because the speakers – or interlocutors – presume some existing familiarity or knowledge base between them.
-When you know someone well enough to finish their sentence, this is an example of convergence.
-Divergence, on the other hand, is more laborious because the speakers must make their presumptions explicit and tacit.
-Interlocutor cohesion, or convergence, happens when speakers are “singing in the same key” or are “on the same page.” Windsor (2020) describes various types of cohesion, using the example of the Occupy Wall Street movement as a symbol of divergence given the myriad signs, slogans, and interests of the participants [@Windsor_2020].
-On the other hand, the “I am a man” protest captured by Ernest Withers during the 1968 santiation workers’ strike in Memphis, TN, or the “Black Lives Matter” placards following the uprising in Ferguson, MO, symbolize convergence and strong interlocutor cohesion [@Edgar_Johnson_2018].
-
-Cognitive and social psychology theories of alignment and coordination lend themselves nicely to the study of social media communication during times of conflict and contentious behavior [@Tollefsen_Dale_Paxton_2013; @Garrod_Pickering_2004; @Pickering_Garrod_2004].
-Over the past few decades, this area has garnered significant attention and produced evidence showing that people sometimes linguistically and behaviorally align as they interact more [@Giles_Coupland_Coupland_1991; @Tollefsen_Dale_Paxton_2013].
-Similarly, accommodation theory refers to the ways in which individuals and groups linguistically adapt to minimize the social space distance.
-Speakers in a collective setting pursue strategies which increase their common ground, and this is reflected in the language they use to communicate with one another.
-
-A similar process happens among participants in social media discussions.
-The process of speakers’ (or tweeters) language becoming more similar is called linguistic style matching (LSM) [@Niederhoffer_Pennebaker_2002].
-LSM is a form of synchrony between speakers, akin to linguistic convergence.
-As Bernieri and Rosenthal (1991) describe, people engaged in linguistic synchrony match each others’ verbal behaviors, adopting not only similar terms, but similar patterns of language [@Bernieri_Rosenthal_1991].
-For example, LSM is particularly evident when one speaker introduces swearing into a genteel conversation; the first usage opens the vulgarity floodgates, and subsequent speakers may repeat the initial curse, as well as innovate new curses into the conversation.
-Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline contextualized by variation in real world events.
-Interlocutor cohesion may increase preceding an in-person social mobilization event, alerting a repressive government that collective mobilization is happening.
-Interlocutor cohesion may also respond to exogenous events such as spontaneous, unprovoked militarized conflict.
-If government forces target a new location using military weapons, this can precipitate online mobilization and discussion of the event.
+Lexical cohesion contributes to the next level of relatedness among tweets:
+interlocutor cohesion. This is the degree to which people in a conversation,
+whether in person or online, have aligned their language [@Coupland_Giles_1988].
+Known as communication accommodation theory, the degree of alignment between
+speakers reveals their closeness, status, and deliberative strategy
+[@Giles_2016]. Speakers can converge and diverge in their communication.
+Convergence facilitates easier transmission of information, because the speakers
+– or interlocutors – presume some existing familiarity or knowledge base between
+them. When you know someone well enough to finish their sentence, this is an
+example of convergence. Divergence, on the other hand, is more laborious because
+the speakers must make their presumptions explicit and tacit. Interlocutor
+cohesion, or convergence, happens when speakers are “singing in the same key” or
+are “on the same page.” Windsor (2020) describes various types of cohesion,
+using the example of the Occupy Wall Street movement as a symbol of divergence
+given the myriad signs, slogans, and interests of the participants
+[@Windsor_2020]. On the other hand, the “I am a man” protest captured by Ernest
+Withers during the 1968 santiation workers’ strike in Memphis, TN, or the “Black
+Lives Matter” placards following the uprising in Ferguson, MO, symbolize
+convergence and strong interlocutor cohesion [@Edgar_Johnson_2018].
+
+Cognitive and social psychology theories of alignment and coordination lend
+themselves nicely to the study of social media communication during times of
+conflict and contentious behavior [@Tollefsen_Dale_Paxton_2013;
+@Garrod_Pickering_2004; @Pickering_Garrod_2004]. Over the past few decades, this
+area has garnered significant attention and produced evidence showing that
+people sometimes linguistically and behaviorally align as they interact more
+[@Giles_Coupland_Coupland_1991; @Tollefsen_Dale_Paxton_2013]. Similarly,
+accommodation theory refers to the ways in which individuals and groups
+linguistically adapt to minimize the social space distance. Speakers in a
+collective setting pursue strategies which increase their common ground, and
+this is reflected in the language they use to communicate with one another.
+
+A similar process happens among participants in social media discussions. The
+process of speakers’ (or tweeters) language becoming more similar is called
+linguistic style matching (LSM) [@Niederhoffer_Pennebaker_2002]. LSM is a form
+of synchrony between speakers, akin to linguistic convergence. As Bernieri and
+Rosenthal (1991) describe, people engaged in linguistic synchrony match each
+others’ verbal behaviors, adopting not only similar terms, but similar patterns
+of language [@Bernieri_Rosenthal_1991]. For example, LSM is particularly evident
+when one speaker introduces swearing into a genteel conversation; the first
+usage opens the vulgarity floodgates, and subsequent speakers may repeat the
+initial curse, as well as innovate new curses into the conversation. Fed by
+lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
+contextualized by variation in real world events. Interlocutor cohesion may
+increase preceding an in-person social mobilization event, alerting a repressive
+government that collective mobilization is happening. Interlocutor cohesion may
+also respond to exogenous events such as spontaneous, unprovoked militarized
+conflict. If government forces target a new location using military weapons,
+this can precipitate online mobilization and discussion of the event.
 
 ## Social and Physical Cohesion
-In turn, other studies show that linguistic alignment leads to increased social connectedness and solidarity [@Miles_Nind_Macrae_2009], which is associated with increased motivation for participation [@Walton_Cohen_Cwir_Spencer_2012], facilitating successful coordination of group actions toward shared goals [@Fusaroli_Bahrami_Olsen_Roepstorff_Rees_Frith_Tylén_2012; @Richardson_Dale_2005].
-This research emphasizes both the importance of and connections between linguistic alignment and behavioral alignment.
-The more people interact, the more similar their language and linguistic patterns become.
-This holds true for face-to-face interactions as well as online communication [@Riordan_Dale_Kreuz_Olney_2011}.
-Given this, we should expect to see increased linguistic cohesion amongst people participating in online discussions about an idea, event, or individual.
-Given that social media reports in real time about actual events taking place, i.e., protests or demonstrations in which people are assembled together in a location, or attacks that require coordination between members of a unit, the cohesion in social media should be expected to correlate with the social cohesion of the group [@Zeitzoff_2011}.
-
-A socially cohesive group is inherently more threatening to the existing regime because it reflects the professionalization of potential alternate leadership, and collective opposition momentum.
-Groups with high social cohesion are more difficult to divide and conquer, and more cohesive messages may also garner increased international support.
-A paper published in Nature argues that global insurgency movements all exhibit a similar pattern to their social structure [@Bohorquez_Gourley_Dixon_Spagat_Johnson_2009}.
-The authors assert that each violent group has a stable state, and that exogenous events can create perturbations that push the group to become more cohesive, or alternatively to become more fragmented.
-Rather than frenetic, patchwork messages via Twitter, cohesive messages indicate increased organizational structure, which should incentivize a response from the government.
-What process is the driving force, though?
-Does an increase in linguistic cohesion precede or follow increased repression by the government?
-Do movements get stronger first, and then the government responds, or does the government increase its offensive measures, and thus social groups have a clear opponent around whom they can coalesce both socially and linguistically?
-
-Thus, verbal synchrony leads to physical synchrony.
-Shared language in an online environment can influence individuals’ propensity to engage in similar coordinated behavior.
-In the case of the Arab Spring, this may mean social mobilization in public spaces to protest against government brutality.
-Words in a passage of text – or series of tweets – have some degree of semantic relation.
-Individuals engaged in a conversation, whether in real life or online, have the tendency to use similar language as they interact, increasing the cohesion of their language.
-As an extension, multiple individuals collectively communicating can also demonstrate linguistic alignment.
-In the context of social conflict, the linguistic cohesion of participants in the online conversation should correspond to the degree of social cohesion on the ground.
-We link these concepts of social and linguistic cohesion together to demonstrate how language serves as an indicator of the degree of social mobilization, using Twitter feeds during the spring of 2012 in Syria.
+In turn, other studies show that linguistic alignment leads to increased social
+connectedness and solidarity [@Miles_Nind_Macrae_2009], which is associated with
+increased motivation for participation [@Walton_Cohen_Cwir_Spencer_2012],
+facilitating successful coordination of group actions toward shared goals
+[@Fusaroli_Bahrami_Olsen_Roepstorff_Rees_Frith_Tylén_2012;
+@Richardson_Dale_2005]. This research emphasizes both the importance of and
+connections between linguistic alignment and behavioral alignment. The more
+people interact, the more similar their language and linguistic patterns become.
+This holds true for face-to-face interactions as well as online communication
+[@Riordan_Dale_Kreuz_Olney_2011}. Given this, we should expect to see increased
+linguistic cohesion amongst people participating in online discussions about an
+idea, event, or individual. Given that social media reports in real time about
+actual events taking place, i.e., protests or demonstrations in which people are
+assembled together in a location, or attacks that require coordination between
+members of a unit, the cohesion in social media should be expected to correlate
+with the social cohesion of the group [@Zeitzoff_2011}.
+
+A socially cohesive group is inherently more threatening to the existing regime
+because it reflects the professionalization of potential alternate leadership,
+and collective opposition momentum. Groups with high social cohesion are more
+difficult to divide and conquer, and more cohesive messages may also garner
+increased international support. A paper published in Nature argues that global
+insurgency movements all exhibit a similar pattern to their social structure
+[@Bohorquez_Gourley_Dixon_Spagat_Johnson_2009}. The authors assert that each
+violent group has a stable state, and that exogenous events can create
+perturbations that push the group to become more cohesive, or alternatively to
+become more fragmented. Rather than frenetic, patchwork messages via Twitter,
+cohesive messages indicate increased organizational structure, which should
+incentivize a response from the government. What process is the driving force,
+though? Does an increase in linguistic cohesion precede or follow increased
+repression by the government? Do movements get stronger first, and then the
+government responds, or does the government increase its offensive measures, and
+thus social groups have a clear opponent around whom they can coalesce both
+socially and linguistically?
+
+Thus, verbal synchrony leads to physical synchrony. Shared language in an online
+environment can influence individuals’ propensity to engage in similar
+coordinated behavior. In the case of the Arab Spring, this may mean social
+mobilization in public spaces to protest against government brutality. Words in
+a passage of text – or series of tweets – have some degree of semantic relation.
+Individuals engaged in a conversation, whether in real life or online, have the
+tendency to use similar language as they interact, increasing the cohesion of
+their language. As an extension, multiple individuals collectively communicating
+can also demonstrate linguistic alignment. In the context of social conflict,
+the linguistic cohesion of participants in the online conversation should
+correspond to the degree of social cohesion on the ground. We link these
+concepts of social and linguistic cohesion together to demonstrate how language
+serves as an indicator of the degree of social mobilization, using Twitter feeds
+during the spring of 2012 in Syria.
 
 Real-world collective action is known to bring about a sense of togetherness,
-also known as “collective effervescence” [@durkheim1995elementary]. This
-feeling of being a part of something larger than oneself leads individuals
-to act in ways that would not have on their own. Being overcome with this
-feeling can lead to violence [@collins2009violence; @spaaij2014sports].
-Conversely, increased exposure
-to violence can result in positive social cohesion. @gilligan2014civil
+also known as “collective effervescence” [@durkheim1995elementary]. This feeling
+of being a part of something larger than oneself leads individuals to act in
+ways that would not have on their own. Being overcome with this feeling can lead
+to violence [@collins2009violence; @spaaij2014sports]. Conversely, increased
+exposure to violence can result in positive social cohesion. @gilligan2014civil
 found that exposure to fatal wartime violence resulted in increased prosocial
@@
 
-Physical and social cohesion in the world can be modeled using event data which encodes who does what to whom on a given day.
-This could include events such as the government (GOV) imposing a blockade or fighting with artillery or tanks on a civilian group (CIV).
-CAMEO (Conflict and Mediation Event Observations) encode a set of activities with numerical values, rescaled to reflect a conflict-cooperation scale [@Schrodt_Hall_2006; @Goldstein_1992].
-These event codes include a range of behaviors, from making public statements and appeals, to demanding, threatening, protesting, and using unconventional mass violence.
-Steinert-Threlkeld (2017) modeled a similar relationship between social media and social mobilization using a Gini coefficient measure, rather than a tf-idf (term frequency-inverse document frequency) measure alongside event data [@Ramos_2003; @Threlkeld_2017].
-This pathbreaking work demonstrates that participants on the fringe of a social movement contribute substantially to the overall level of protest.
-We add to this discussion by demonstrating how sociolinguistic cohesion evolves in response to negative and positive exogenous events.
+Physical and social cohesion in the world can be modeled using event data which
+encodes who does what to whom on a given day. This could include events such as
+the government (GOV) imposing a blockade or fighting with artillery or tanks on
+a civilian group (CIV). CAMEO (Conflict and Mediation Event Observations) encode
+a set of activities with numerical values, rescaled to reflect a
+conflict-cooperation scale [@Schrodt_Hall_2006; @Goldstein_1992]. These event
+codes include a range of behaviors, from making public statements and appeals,
+to demanding, threatening, protesting, and using unconventional mass violence.
+Steinert-Threlkeld (2017) modeled a similar relationship between social media
+and social mobilization using a Gini coefficient measure, rather than a tf-idf
+(term frequency-inverse document frequency) measure alongside event data
+[@Ramos_2003; @Threlkeld_2017]. This pathbreaking work demonstrates that
+participants on the fringe of a social movement contribute substantially to the
+overall level of protest. We add to this discussion by demonstrating how
+sociolinguistic cohesion evolves in response to negative and positive exogenous
+events.
 
 ### Cohesion in Social Movements and Civil Wars
-People join social and political resistance movements because they feel a sense of connection to the cause, and because they have been sufficiently convinced to participate.
-Given that people are generally risk averse, overcoming inertia requires a strong connection to the group identity, or against an individual, event, or political injustice [@Goldstone_1980; Goldstone_2011].
-Political resistance offers participants the opportunity to “lose themselves” and relinquish their individual identity in favor of identification with a larger group identity, thus contributing to a cohesive group ready and mobilized for action [@Hoffer_2011.
-Previous research on social movements supports the idea that participants are likely to join movements when they know and have a personal connection to someone else already involved [@McAdam_1986.
-The type of collective contentious behavior that manifests in society is a function of the available political opportunity structures.
-The political opportunity structure, as defined by Kitschelt (1986) are “comprised of specific configuration of resources, institutional arrangements and historical precedents for social mobilization, which facilitate the development of protest movements in some instances and constrain them in others [@Kitschelt_1986].” What emerges as strategies and tactics in contentious politics is in essence, a function of what the system makes possible.
-This includes the number of people and their disposition, i.e.
-nonviolent or violent, as well as their internal structure.
+People join social and political resistance movements because they feel a sense
+of connection to the cause, and because they have been sufficiently convinced to
+participate. Given that people are generally risk averse, overcoming inertia
+requires a strong connection to the group identity, or against an individual,
+event, or political injustice [@Goldstone_1980; Goldstone_2011]. Political
+resistance offers participants the opportunity to “lose themselves” and
+relinquish their individual identity in favor of identification with a larger
+group identity, thus contributing to a cohesive group ready and mobilized for
+action [@Hoffer_2011. Previous research on social movements supports the idea
+that participants are likely to join movements when they know and have a
+personal connection to someone else already involved [@McAdam_1986. The type of
+collective contentious behavior that manifests in society is a function of the
+available political opportunity structures. The political opportunity structure,
+as defined by Kitschelt (1986) are “comprised of specific configuration of
+resources, institutional arrangements and historical precedents for social
+mobilization, which facilitate the development of protest movements in some
+instances and constrain them in others [@Kitschelt_1986].” What emerges as
+strategies and tactics in contentious politics is in essence, a function of what
+the system makes possible. This includes the number of people and their
+disposition, i.e. nonviolent or violent, as well as their internal structure.
 The more cohesive a group is, the greater threat they pose to the establishment.
 
-Cohesion is also a familiar concept in the study of civil conflicts as it pertains to group affiliation and the ability to overcome collective action problems.
-Olson’s (Olson, 1965) seminal work on collective action informs the theory of group behavior.
-Individuals must act in concert – cohesively – to accomplish the task of challenging the authority of the state.
-Building on Eisinger’s (1973) analysis of social protest movements [@Eisinger_1973, McAdam, Tilly and Tarrow [@Tilly_2004, and Francisco [@Francisco_1995 have provided foundational work on the dynamics of social movements and contentious behavior.
-More recently, Gates (2002) considers rebel recruitment for participation in civil conflicts as a function of internal cohesion [@Gates_2002].
-He notes that rebel movement success is influenced by the degree of group cohesion, which itself is a function of geographic distance, ideology and ethnicity.
-
-There are multiple rebel groups within Syria, some with fighters sourced locally from the disaffected Syrian population, and an increasing number of foreign fighters from transnational terrorist organizations.
-Gates’ work helps us understand the intergroup competition for participation in the rebel movement, as well as the groups’ abilities to punish defectors for nonparticipation.
-Foreign fighters would appear to be amply motivated to fight, given their decision to relocate from their home country which is sometimes in the region but other times requires them to travel large distances.
-
-Similarly, Sambanis and Shayo (2013) find in their model that “intense ethnic conflict makes people care more about their ethnic group relative to other groups, and seek to resemble it more [@Sambanis_Shayo_2013].” As ethnic conflict intensifies, groups seeking to become more quintessentially like the typical member of their ethnic group, this should be manifested in their language on social media.
-Social medial should reflect this delineation amongst ethnic groups and between them.
-However, this may also include a general identification across ethnic groups in a membership of an opposition to an oppressive leader.
-
-It is this general identification with the larger opposition movement, not the individual identity groups within Syria, which we seek to understand in this paper.
-It is implausible to expect there to be one cohesive narrative from the multiple groups with disparate incentives.
-However, they do have important similarities, namely, they are all interested in opposing the current Syrian regime using largely violent means, although there are notable and regular instances of nonviolent protests on Fridays, following prayer services.
-Thus, what we are able to capture in this study is the degree to which all opposition movements to the Syrian government have a similar content and tone, with a similar ebb and flow.
-It should be increasingly threatening to the regime if the rebel movement across the disparate groups is growing stronger and more unified, represented by similar language used across groups.
-
-The civil war literature has further explored the role of social cohesion in detail.
-Collier and Hoeffler identified the role of social homogeneity as having an increased likelihood on social conflict, especially when the society is polarized [@Collier_Hoeffler_2004].
-Cederman and Girardin  write that, “In general, nationalist groups derive their cohesion from collective-level identities that resonate deeply with the emotional needs of modern citizens.” Sambanis and Schulhofer-Wohl note that “group cohesion and solidarity (underlie) the offensive advantage (Sambanis & Schulhofer-Wohl, 2009).” Anyanwu (2002) writes, “Another source of rebel military opportunity is social cohesion…an ethnically diverse society may reduce the opportunity for rebellion by limiting the recruitment pool [@Anyanwu_2002].” Referencing Gurr’s work on minorities at risk, Regan and Norton (2005) note that “a religious or linguistic minority might suffer disproportionately in a given society, and this form of aggrievement can lead to unrest across the social lines that distinguish the minority group.
-Therefore, while collective cohesion is a function of targeted maldistributions, it is individual penury that allows for this collective mobilization [@Gurr_2000; @Regan_Norton_2005].” Thus scholarship concurs that group cohesion matters to group mobilization; we add to this concept by introducing the role of language in facilitating cohesion.
+Cohesion is also a familiar concept in the study of civil conflicts as it
+pertains to group affiliation and the ability to overcome collective action
+problems. Olson’s (Olson, 1965) seminal work on collective action informs the
+theory of group behavior. Individuals must act in concert – cohesively – to
+accomplish the task of challenging the authority of the state. Building on
+Eisinger’s (1973) analysis of social protest movements [@Eisinger_1973, McAdam,
+Tilly and Tarrow [@Tilly_2004, and Francisco [@Francisco_1995 have provided
+foundational work on the dynamics of social movements and contentious behavior.
+More recently, Gates (2002) considers rebel recruitment for participation in
+civil conflicts as a function of internal cohesion [@Gates_2002]. He notes that
+rebel movement success is influenced by the degree of group cohesion, which
+itself is a function of geographic distance, ideology and ethnicity.
+
+There are multiple rebel groups within Syria, some with fighters sourced locally
+from the disaffected Syrian population, and an increasing number of foreign
+fighters from transnational terrorist organizations. Gates’ work helps us
+understand the intergroup competition for participation in the rebel movement,
+as well as the groups’ abilities to punish defectors for nonparticipation.
+Foreign fighters would appear to be amply motivated to fight, given their
+decision to relocate from their home country which is sometimes in the region
+but other times requires them to travel large distances.
+
+Similarly, Sambanis and Shayo (2013) find in their model that “intense ethnic
+conflict makes people care more about their ethnic group relative to other
+groups, and seek to resemble it more [@Sambanis_Shayo_2013].” As ethnic conflict
+intensifies, groups seeking to become more quintessentially like the typical
+member of their ethnic group, this should be manifested in their language on
+social media. Social medial should reflect this delineation amongst ethnic
+groups and between them. However, this may also include a general identification
+across ethnic groups in a membership of an opposition to an oppressive leader.
+
+It is this general identification with the larger opposition movement, not the
+individual identity groups within Syria, which we seek to understand in this
+paper. It is implausible to expect there to be one cohesive narrative from the
+multiple groups with disparate incentives. However, they do have important
+similarities, namely, they are all interested in opposing the current Syrian
+regime using largely violent means, although there are notable and regular
+instances of nonviolent protests on Fridays, following prayer services. Thus,
+what we are able to capture in this study is the degree to which all opposition
+movements to the Syrian government have a similar content and tone, with a
+similar ebb and flow. It should be increasingly threatening to the regime if the
+rebel movement across the disparate groups is growing stronger and more unified,
+represented by similar language used across groups.
+
+The civil war literature has further explored the role of social cohesion in
+detail. Collier and Hoeffler identified the role of social homogeneity as having
+an increased likelihood on social conflict, especially when the society is
+polarized [@Collier_Hoeffler_2004]. Cederman and Girardin  write that, “In
+general, nationalist groups derive their cohesion from collective-level
+identities that resonate deeply with the emotional needs of modern citizens.”
+Sambanis and Schulhofer-Wohl note that “group cohesion and solidarity (underlie)
+the offensive advantage (Sambanis & Schulhofer-Wohl, 2009).” Anyanwu (2002)
+writes, “Another source of rebel military opportunity is social cohesion…an
+ethnically diverse society may reduce the opportunity for rebellion by limiting
+the recruitment pool [@Anyanwu_2002].” Referencing Gurr’s work on minorities at
+risk, Regan and Norton (2005) note that “a religious or linguistic minority
+might suffer disproportionately in a given society, and this form of
+aggrievement can lead to unrest across the social lines that distinguish the
+minority group. Therefore, while collective cohesion is a function of targeted
+maldistributions, it is individual penury that allows for this collective
+mobilization [@Gurr_2000; @Regan_Norton_2005].” Thus scholarship concurs that
+group cohesion matters to group mobilization; we add to this concept by
+introducing the role of language in facilitating cohesion.
 
 ## Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
-We tie the constructs of lexical, interlocutor, and social/physical cohesion together in a theoretical framework called sociolinguistic cohesion, as shown in Figure X.
-We can measure the changes in cohesion preceding and in response to external stimuli by evaluating the messages and the context in which they occur.
-Several mechanisms are in motion here.
-Previous values of linguistic cohesion should influence future values of linguistic cohesion.
-They should also influence future actions in the real world space.
-Previous events influence future events, and also the future cohesiveness of the opposition.
-
-Sociolinguistic cohesion is not a static concept.
-Just as social movements experience increased participation as well as setbacks – indicating dynamic relationships between participants, and participants and the sociopolitical environment – sociolinguistic cohesion is also dynamic, reflecting the changing states of the political sphere.
-Other scholars have noted the diffusion of messages whereby they reach a critical mass, whereby “behaviors, beliefs, and preferences” spread within a population [@Barash_Cameron_Macy_2012].
-Cohesion changes over time in response to external events and the internal dynamics of the social movement.
-Some may wonder whether social cohesion can diffuse among distant actors who do not interact face-to-face; Centola and Macy show that Internet weak ties extend over long distances and as such have spatially significant abilities to influence actors [@Centola_Macy_2007].
-Fink et al.
-also explored diffusion of hashtags in viral contagion in Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion [@Fink_Schmidt_Barash_Cameron_Macy_2016].
-The prevalence and rate of particular hashtags contribute to the overall sociolinguistic cohesion.
-he more that people reuse hashtags or common phrases, the greater the sociolinguistic cohesion when this phenomenon occurs during socially significant times like protests [@Adamic_others_2015].
-Exogenous events, like intervention by another country or international organization like the United Nations, can affect sociolinguistic cohesion.
-Endogenous events, like the recruitment of new members to the rebel or resistance movement, can also affect the level of cohesion.
-
-Combining these separate threads, it is reasonable to expect that real-world actions 
-and online social interactions would be enmeshed, driving and being driven by 
-one another. Rather than expecting that only real-world social cohesion would be
-driven by real-world action, we would expect interaction between real-world and
-virtual dynamics: In this case, exposure to real-world violence could result in social
-cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator and a result of increased social organization and mobilization 
-on the ground.
-
-Exploring how social media influences contentious behavior, Tilly notes that social media lowers coordination and transaction costs for participants, and that older versions of organizing social movements have become less effective, yielding to the new frontier of online organizing [@McAdam_Tarrow_Tilly_2003].
-Koopmans extends this further, writing that, “Authorities react to social movement activities if and as they are depicted in the mass media, and conversely movement activists become aware of political opportunities and constraints through the reactions (or non-reactions) that their actions provoke in the public sphere” [@Koopmans_2004].
-
-Lexical cohesion, then, should be a useful indicator of social cohesion in political crisis.
-Lexical cohesion happens at the word level.
-Interlocutor cohesion happens between speakers.
-Political cohesion happens at the social level during moments of political crisis, like civil wars and social movements.
-Sociolinguistic cohesion is comprised of lexical, interlocutor, and socio-political events, where the words and their context reveal the disposition of socially connected linguistic communities.
-Sociolinguistic cohesion combines the elements of lexical cohesion in that it captures the degree of similarity between what is said, and how it is said.
-It accounts for the cohesion between multiple speakers in an environment whose language evolves to become more aligned and similar.
-Sociolinguistic cohesion also addresses how groups involved in political rebellion must have internal cohesion to overcome the collective action problem to mount sustained resistance to state authority.
-
-Social coordination has long been used both physically and virtually
-to start and carry out collective actions. These collective events
-bring individuals together and create emergent patterns of communication
-and action. Online communication has historically been used to document
-and communicate archival information about events, but it has been
-increasingly used to bring about social change. From a dynamical
-systems perspective, these different means of social coordination during
-times of turmoil can be considered two complementary components of a
-single system, mutually constrained and constantly interacting and
-influencing one another [@mahner1997foundations]. Investigation of the
-coupling of real-world mobilization and social cohesion could provide
-new insight into the power of social media during mobilization and the
-ways in which individuals utilize it to bring about, or respond to, social
-change. Increasingly, social media platforms are being utilized during
-social mobilization, but the relationship between virtual and real-world
-mobilization is still largely unknown. The present work aims to understand
-how physical and virtual movements coexist and interact from a dynamical
-systems perspective.
-
-Just as real-world social cohesion can be
-quantified, so can online cohesion. While this can be quantified in many ways,
-one kind of cohesion can be found in the similarity in language use on social media.
-This implicit or explicit similarity in language use can indicate shared
-beliefs, thoughts, and feelings, as has been studied in research on language style
-in psycholinguistics and social psychology 
-[@gonzales2010language; @tausczik2010psychological; @brennan1996conceptual]; 
-although previous work on language style
-has often focused on individuals and small groups, this can be scaled up to examine
+We tie the constructs of lexical, interlocutor, and social/physical cohesion
+together in a theoretical framework called sociolinguistic cohesion, as shown in
+Figure X. We can measure the changes in cohesion preceding and in response to
+external stimuli by evaluating the messages and the context in which they occur.
+Several mechanisms are in motion here. Previous values of linguistic cohesion
+should influence future values of linguistic cohesion. They should also
+influence future actions in the real world space. Previous events influence
+future events, and also the future cohesiveness of the opposition.
+
+Sociolinguistic cohesion is not a static concept. Just as social movements
+experience increased participation as well as setbacks – indicating dynamic
+relationships between participants, and participants and the sociopolitical
+environment – sociolinguistic cohesion is also dynamic, reflecting the changing
+states of the political sphere. Other scholars have noted the diffusion of
+messages whereby they reach a critical mass, whereby “behaviors, beliefs, and
+preferences” spread within a population [@Barash_Cameron_Macy_2012].  Cohesion
+changes over time in response to external events and the internal dynamics of
+the social movement. Some may wonder whether social cohesion can diffuse among
+distant actors who do not interact face-to-face; Centola and Macy show that
+Internet weak ties extend over long distances and as such have spatially
+significant abilities to influence actors [@Centola_Macy_2007]. Fink et al. also
+explored diffusion of hashtags in viral contagion in Nigeria, a phenomenon
+similar to what we identify as sociolinguistic cohesion
+[@Fink_Schmidt_Barash_Cameron_Macy_2016]. The prevalence and rate of particular
+hashtags contribute to the overall sociolinguistic cohesion. he more that people
+reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
+this phenomenon occurs during socially significant times like protests
+[@Adamic_others_2015]. Exogenous events, like intervention by another country or
+international organization like the United Nations, can affect sociolinguistic
+cohesion. Endogenous events, like the recruitment of new members to the rebel or
+resistance movement, can also affect the level of cohesion.
+
+Combining these separate threads, it is reasonable to expect that real-world
+actions and online social interactions would be enmeshed, driving and being
+driven by one another. Rather than expecting that only real-world social
+cohesion would be driven by real-world action, we would expect interaction
+between real-world and virtual dynamics: In this case, exposure to real-world
+violence could result in social cohesion in the virtual world. Increased social
+cohesion is thus potentially an indicator and a result of increased social
+organization and mobilization on the ground.
+
+Exploring how social media influences contentious behavior, Tilly notes that
+social media lowers coordination and transaction costs for participants, and
+that older versions of organizing social movements have become less effective,
+yielding to the new frontier of online organizing [@McAdam_Tarrow_Tilly_2003].
+Koopmans extends this further, writing that, “Authorities react to social
+movement activities if and as they are depicted in the mass media, and
+conversely movement activists become aware of political opportunities and
+constraints through the reactions (or non-reactions) that their actions provoke
+in the public sphere” [@Koopmans_2004].
+
+Lexical cohesion, then, should be a useful indicator of social cohesion in
+political crisis. Lexical cohesion happens at the word level. Interlocutor
+cohesion happens between speakers. Political cohesion happens at the social
+level during moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion is comprised of lexical, interlocutor, and
+socio-political events, where the words and their context reveal the disposition
+of socially connected linguistic communities. Sociolinguistic cohesion combines
+the elements of lexical cohesion in that it captures the degree of similarity
+between what is said, and how it is said. It accounts for the cohesion between
+multiple speakers in an environment whose language evolves to become more
+aligned and similar. Sociolinguistic cohesion also addresses how groups involved
+in political rebellion must have internal cohesion to overcome the collective
+action problem to mount sustained resistance to state authority.
+
+Social coordination has long been used both physically and virtually to start
+and carry out collective actions. These collective events bring individuals
+together and create emergent patterns of communication and action. Online
+communication has historically been used to document and communicate archival
+information about events, but it has been increasingly used to bring about
+social change. From a dynamical systems perspective, these different means of
+social coordination during times of turmoil can be considered two complementary
+components of a single system, mutually constrained and constantly interacting
+and influencing one another [@mahner1997foundations]. Investigation of the
+coupling of real-world mobilization and social cohesion could provide new
+insight into the power of social media during mobilization and the ways in which
+individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social
+mobilization, but the relationship between virtual and real-world mobilization
+is still largely unknown. The present work aims to understand how physical and
+virtual movements coexist and interact from a dynamical systems perspective.
+
+Just as real-world social cohesion can be quantified, so can online cohesion.
+While this can be quantified in many ways, one kind of cohesion can be found in
+the similarity in language use on social media. This implicit or explicit
+similarity in language use can indicate shared beliefs, thoughts, and feelings,
+as has been studied in research on language style in psycholinguistics and
+social psychology [@gonzales2010language; @tausczik2010psychological;
+@brennan1996conceptual]; although previous work on language style has often
+focused on individuals and small groups, this can be scaled up to examine
 massive social-level changes [@michel2011quantitative; @fusaroli2015timescales].
-This kind of widespread online social cohesion can lead to real-world
-social change.
-
-This kind of massive online social cohesion can lead to real-world
-social manifestations. Social media platforms provide one way to enable this kind of online social
-cohesion by offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements
-an opportunity to complement or even replace real-world social mobilization.
-For example, during the 2012 Italian protests for global economic change, the riots in
-Rome were mirrored by Twitter activity both on the day of the protests and in the
-days following them [@vicari2013public]. Tweeting was
+This kind of widespread online social cohesion can lead to real-world social
+change.
+
+This kind of massive online social cohesion can lead to real-world social
+manifestations. Social media platforms provide one way to enable this kind of
+online social cohesion by offering distributed information-gathering and
+real-time information dissemination. Given its accessibility and proficiency as
+an information exchange tool, Twitter has provided individuals involved in
+social movements an opportunity to complement or even replace real-world social
+mobilization. For example, during the 2012 Italian protests for global economic
+change, the riots in Rome were mirrored by Twitter activity both on the day of
+the protests and in the days following them [@vicari2013public]. Tweeting was
 determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more
-individuals rely on social media to obtain local news and information, it
-becomes increasingly important to understand just how these micro-blogs
-reflect real-world action.
+events than traditional mainstream media platforms. As more and more individuals
+rely on social media to obtain local news and information, it becomes
+increasingly important to understand just how these micro-blogs reflect
+real-world action.
 
 ## Using Nonlinear Methods to Capture Complex Relationships
-Given the hypothesized interrelationship between the real-world
-and online actions---and the notorious messiness of naturally occurring
-data---it is critical to find appropriate analysis tools that can
-identify the complex interconnections. Traditional linear analyses have led to 
-many notable discoveries in the domains of psychology and political science, 
-but time series data pose problems that are not easily overcome with these 
-methods. Events have historically been conceptualized as linear chains of 
-smaller, sequential events with one occurrence leading to the next. 
-Certain kinds of data are relatively well-suited to these analyses,
-but messy, complex, variable data from real-world events can pose
-challenges, from overpowered samples to violation of underlying
+Given the hypothesized interrelationship between the real-world and online
+actions---and the notorious messiness of naturally occurring data---it is
+critical to find appropriate analysis tools that can identify the complex
+interconnections. Traditional linear analyses have led to many notable
+discoveries in the domains of psychology and political science, but time series
+data pose problems that are not easily overcome with these methods. Events have
+historically been conceptualized as linear chains of smaller, sequential events
+with one occurrence leading to the next. Certain kinds of data are relatively
+well-suited to these analyses, but messy, complex, variable data from real-world
+events can pose challenges, from overpowered samples to violation of underlying
 statistical assumptions [@paxton2017finding].
 
-At the same time, the foundational theoretical assumptions of a 
-linear world has been
-increasingly replaced by ideas from dynamical systems theory. Rather than
-a chain of events, time series data can be thought of as nested occurrences,
-where mutually constrained parts (e.g., citizens, governments, real-world
-events, social media platforms) are constantly interacting, leading to
-more global behaviors that are larger than the sum of the parts
-[@turvey2018lectures]. Linear analyses flatten time series data and ignore 
-the variability that is fundamental to these systems and their evolution over 
-time. However, when analyzed as dynamical systems, many phenomena
-exhibit new nonlinear patterns that were formerly overlooked. 
-Nonlinear methods provide means for capturing the rich temporal
-dynamics and variability that unfold in time series data.
-
-Although a number of other nonlinear methods exist, 
-the primary nonlinear method used in the current work is cross-recurrence
-quantification analysis [CRQA; @zbilut1998detecting] and its offshoot,
-windowed cross-recurrence quantification analysis [WCRQA; @webber2005recurrence].
-CRQA has successfully been used to gain a better understanding of many
-complex human phenomena, including a variety of human social interactions
-[for a review, see @fusaroli2014analyzing]. 
-Much as it has for psychology, we argue that the use of nonlinear methods in
-the investigation of political science phenomena will lead to new insights
-and the development of more robust theories.
+At the same time, the foundational theoretical assumptions of a linear world has
+been increasingly replaced by ideas from dynamical systems theory. Rather than a
+chain of events, time series data can be thought of as nested occurrences, where
+mutually constrained parts (e.g., citizens, governments, real-world events,
+social media platforms) are constantly interacting, leading to more global
+behaviors that are larger than the sum of the parts [@turvey2018lectures].
+Linear analyses flatten time series data and ignore the variability that is
+fundamental to these systems and their evolution over time. However, when
+analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
+that were formerly overlooked. Nonlinear methods provide means for capturing the
+rich temporal dynamics and variability that unfold in time series data.
+
+Although a number of other nonlinear methods exist, the primary nonlinear method
+used in the current work is cross-recurrence quantification analysis [CRQA;
+@zbilut1998detecting] and its offshoot, windowed cross-recurrence quantification
+analysis [WCRQA; @webber2005recurrence]. CRQA has successfully been used to gain
+a better understanding of many complex human phenomena, including a variety of
+human social interactions [for a review, see @fusaroli2014analyzing]. Much as it
+has for psychology, we argue that the use of nonlinear methods in the
+investigation of political science phenomena will lead to new insights and the
+development of more robust theories.
 
 ## The Present Work
-Social media has become a primary platform for social movements and
-activism across the world, but the extent to which virtual activism
-reflects and drives real-world mobilization is still largely unknown. 
-In the current work, we
-conceptualize the physical and virtual movements as a dynamical system,
-both constantly interacting and influencing the other. We aim to study
-this by analyzing the real-world events and online social cohesion
-during nearly three months of the Arab Spring. Both real- and
-virtual-world collective coordination were powerful tools in the events
-of the Arab Spring and are undeniably linked. This study aims to explore
-the dynamics of Syrian Twitter users, who used the social media platform to raise
-awareness about the Arab Spring and bring about mass mobilization.
-
-Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting]
-and windowed cross-recurrence quantification analysis
-[WCRQA; @webber2005recurrence], we analyzed the co-evolution of social
-cohesion online and real-world events. Specifically, using heterogeneous
-data from March 30, 2012, to June 15, 2012, we compared the social cohesion
-of Syrian tweets with the counts
-of all, positive, and negative real-world events derived from gold-standard
-international event data [i.e., the Integrated Crisis Early Warning
-System; @DVN/28075_2015].
-
-We hypothesized that the count of all events and the count of negative
-events would show high levels of determinism, as this time period was
-marked by daily violence which often leads to increased salience. We also
-hypothesized that the count of positive events would not show patterns of
-determinism, as these events were likely overshadowed by the salient
-negative daily occurrences. 
-After testing these hypotheses, we then conducted exploratory analyses 
-to further examine the patterns identified with CRQA. Using WCRQA,
-we sought to identify shifts in the
-dynamics of the systems that could then be linked to real-world shifts in
-conflict frequency.
-Through these analyses, our two primary goals in the current work were to uncover
-(1) how different intensities during times of turmoil may enhance or deter
-social cohesion in social media communication and (2) how social mobilization
-may be evident in the dynamic coupling of cohesion and real-world events.
+Social media has become a primary platform for social movements and activism
+across the world, but the extent to which virtual activism reflects and drives
+real-world mobilization is still largely unknown. In the current work, we
+conceptualize the physical and virtual movements as a dynamical system, both
+constantly interacting and influencing the other. We aim to study this by
+analyzing the real-world events and online social cohesion during nearly three
+months of the Arab Spring. Both real- and virtual-world collective coordination
+were powerful tools in the events of the Arab Spring and are undeniably linked.
+This study aims to explore the dynamics of Syrian Twitter users, who used the
+social media platform to raise awareness about the Arab Spring and bring about
+mass mobilization.
+
+Using cross-recurrence quantification analysis [CRQA; @zbilut1998detecting] and
+windowed cross-recurrence quantification analysis [WCRQA;
+@webber2005recurrence], we analyzed the co-evolution of social cohesion online
+and real-world events. Specifically, using heterogeneous data from March 30,
+2012, to June 15, 2012, we compared the social cohesion of Syrian tweets with
+the counts of all, positive, and negative real-world events derived from
+gold-standard international event data [i.e., the Integrated Crisis Early
+Warning System; @DVN/28075_2015].
+
+We hypothesized that the count of all events and the count of negative events
+would show high levels of determinism, as this time period was marked by daily
+violence which often leads to increased salience. We also hypothesized that the
+count of positive events would not show patterns of determinism, as these events
+were likely overshadowed by the salient negative daily occurrences. After
+testing these hypotheses, we then conducted exploratory analyses to further
+examine the patterns identified with CRQA. Using WCRQA, we sought to identify
+shifts in the dynamics of the systems that could then be linked to real-world
+shifts in conflict frequency. Through these analyses, our two primary goals in
+the current work were to uncover (1) how different intensities during times of
+turmoil may enhance or deter social cohesion in social media communication and
+(2) how social mobilization may be evident in the dynamic coupling of cohesion
+and real-world events.
 
 An additional focus of the current work is to introduce cross-recurrence
-quantification analysis---a longstanding method from physics that has 
-since become influential in a variety of other fields---to political 
-science. We do so by providing detailed descriptions of the methods and
-providing clear directions about interpretation and significance testing
-even with relatively small-*n* or case studies. After demonstrating these
-methods' utility with this dataset, we close the paper with specific
-suggestions to political scientists interested in incorporating these
-methods into their work.
+quantification analysis---a longstanding method from physics that has since
+become influential in a variety of other fields---to political science. We do so
+by providing detailed descriptions of the methods and providing clear directions
+about interpretation and significance testing even with relatively small-*n* or
+case studies. After demonstrating these methods' utility with this dataset, we
+close the paper with specific suggestions to political scientists interested in
+incorporating these methods into their work.
 
@@
 The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
-occurring between March 30--June 15, 2012. Using the Twitter
-streaming API, servers at the University of Texas at Austin collected
-the tweets. The servers were run on a stable (LTS) version of Ubuntu
-Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
-maintained by IT services.
-
-Tweets collected contained one or more of the following keywords:
-“syria,” “syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These
-keywords were chosen based on the most distinctive terms used in news
-articles covering the Arab Spring in Syria at the time. A node.js script
-was used to reinitialize the connection to Twitter's servers whenever the
-script timed out due to a period of silence. The script requested data from
-the API endpoint using basic HTTP authentication (OAuth was optional, at
-the time) at https://stream.twitter.com/1.1/statuses/filter.json, and stored
-the data directly to the local hard disk. The tweets were then post-processed
-with a Python script to convert the JSON-formatted tweets to tab-separated
-files, which were then compressed to maximize storage efficiency.
-
-All scripts used for scraping tweets and compressing data can be found 
-at https://github.com/chbrown/twilight.
+occurring between March 30--June 15, 2012. Using the Twitter streaming API,
+servers at the University of Texas at Austin collected the tweets. The servers
+were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
+directly to the high-bandwidth UT network maintained by IT services.
+
+Tweets collected contained one or more of the following keywords: “syria,”
+“syrian,” “damascus,” “homs,” “al-assad,” and “sunni.” These keywords were
+chosen based on the most distinctive terms used in news articles covering the
+Arab Spring in Syria at the time. A node.js script was used to reinitialize the
+connection to Twitter's servers whenever the script timed out due to a period of
+silence. The script requested data from the API endpoint using basic HTTP
+authentication (OAuth was optional, at the time) at
+https://stream.twitter.com/1.1/statuses/filter.json, and stored the data
+directly to the local hard disk. The tweets were then post-processed with a
+Python script to convert the JSON-formatted tweets to tab-separated files, which
+were then compressed to maximize storage efficiency.
+
+All scripts used for scraping tweets and compressing data can be found at
+https://github.com/chbrown/twilight.
 
 ### Event Data
-Event data were obtained from the 2012 Integrated Crisis Early Warning
-System [ICEWS; @DVN/28075_2015]. The event data were first filtered to
-remove incomplete and incorrectly formatted data. They were then filtered
-to include only events that were directed at (i.e., `target`) Syria ($n = 6300$).
-To explore the impact of outwardly directed Syrian events, the data were
-filtered again to include events that were both directed at (i.e., `target`)
-or directed by (i.e., `source`) Syria ($n = 7990$).
+Event data were obtained from the 2012 Integrated Crisis Early Warning System
+[ICEWS; @DVN/28075_2015]. The event data were first filtered to remove
+incomplete and incorrectly formatted data. They were then filtered to include
+only events that were directed at (i.e., `target`) Syria ($n = 6300$). To
+explore the impact of outwardly directed Syrian events, the data were filtered
+again to include events that were both directed at (i.e., `target`) or directed
+by (i.e., `source`) Syria ($n = 7990$).
 
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated
-by quantifying the frequency of shared content words with respect to those
-words’ frequencies in the entire tweet corpus. If a linguistic term has a
-high frequency in one tweet but has a low frequency in the whole tweet
-corpus, then it is more likely a content word and is thus given more weight
-in calculating social cohesion. 
-This method is similar to inverse document frequency (IDF).
-For more information on IDF, see @jones1972statistical and
+The social cohesion or linguistic similarity of daily tweets was calculated by
+quantifying the frequency of shared content words with respect to those words’
+frequencies in the entire tweet corpus. If a linguistic term has a high
+frequency in one tweet but has a low frequency in the whole tweet corpus, then
+it is more likely a content word and is thus given more weight in calculating
+social cohesion. This method is similar to inverse document frequency (IDF). For
+more information on IDF, see @jones1972statistical and
 @robertson2004understanding.
 
-The tweets were first sorted into ascending order by timestamp. They were
-then grouped into successive sets of five tweets. Inverse frequency
-weighting for the overlap words and all words was conducted for each pair
-of two tweets in the group of five, then divided to get the social cohesion
-score for that pair (see Eq. 1-3). This resulted in ten social cohesion
-values for each group of five tweets; these values were then averaged to get
-a social cohesion score for the entire set of five tweets. Finally,
-the mean of all average cohesion values for all groups was taken to get
-a social cohesion score for each day.
+The tweets were first sorted into ascending order by timestamp. They were then
+grouped into successive sets of five tweets. Inverse frequency weighting for the
+overlap words and all words was conducted for each pair of two tweets in the
+group of five, then divided to get the social cohesion score for that pair (see
+Eq. 1-3). This resulted in ten social cohesion values for each group of five
+tweets; these values were then averaged to get a social cohesion score for the
+entire set of five tweets. Finally, the mean of all average cohesion values for
+all groups was taken to get a social cohesion score for each day.
 
@@
 
-The social cohesion calculation was performed on the tweet corpus
-containing both English and Arabic tweets. All hashtags and URLs were included 
-in the analysis.
+The social cohesion calculation was performed on the tweet corpus containing
+both English and Arabic tweets. All hashtags and URLs were included in the
+analysis.
 
@@
 Using the Integrated Crisis Early Warning System (ICEWS) developed at the
-Defense Advanced Research Project Agency, the daily events were
-scored with an intensity rating ranging from -10 to 10. Negative 
-events---such as riots and attacks---are coded with low negative numbers, while
-positive or peaceful events are coded with high positive numbers. This
-well-validated coding scheme allows for numerical quantification of
-different event types.
-
-For both the target-only and the target and source data described above, time series of
-the count of all events were generated by summing the total number of events
-on each day, irrespective of ICEWS score. Similarly, time series of count
-of positive events were generated by summing the number of ICEWS events
-for each day that had an intensity rating greater than zero. Lastly,
-time series of count of negative events were generated by summing the number
-of ICEWS events for each day that had an intensity rating less than zero.
+Defense Advanced Research Project Agency, the daily events were scored with an
+intensity rating ranging from -10 to 10. Negative events---such as riots and
+attacks---are coded with low negative numbers, while positive or peaceful events
+are coded with high positive numbers. This well-validated coding scheme allows
+for numerical quantification of different event types.
+
+For both the target-only and the target and source data described above, time
+series of the count of all events were generated by summing the total number of
+events on each day, irrespective of ICEWS score. Similarly, time series of count
+of positive events were generated by summing the number of ICEWS events for each
+day that had an intensity rating greater than zero. Lastly, time series of count
+of negative events were generated by summing the number of ICEWS events for each
+day that had an intensity rating less than zero.
 
@@
 ### Cross-Recurrence Quantification Analysis
-We first used cross-recurrence quantification analysis
-[CRQA; @zbilut1998detecting] to investigate the temporal patterns of
-social cohesion and real-world events in Syria during Arab Spring. CRQA
-is an extension of RQA, which captures the patterns of revisited states of
-a single time series [@zbilut1992embeddings; @webber1994dynamical]. CRQA
-allows for two time series to be projected onto one another to investigate
-shared states and trajectories.
-In CRQA, we track these shared states by identifying *recurrent points*,
-or intersections of time during which two signals shared or revisited the same
-state. These shared states can be at the same time or at later points in
-the time series. We can further chart shared trajectories by examining
-the occurrences and patterns of multiple sequential recurrent points.
-
-To perform CRQA, the time series must be converted to the same
-scale, while still preserving a sampling rate that respects the native
-timescale of the system
-[cf. Nyquist frequency in signal processing; @grenander1959probability].
-Because the social cohesion and event data have different scales and values,
-we converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles
-(e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
-levels of social cohesion and counts of all, positive, and negative events
-on each day. 
-We implemented CRQA using the `crqa` package [@R-crqa] for R [@R-base].
+We first used cross-recurrence quantification analysis [CRQA;
+@zbilut1998detecting] to investigate the temporal patterns of social cohesion
+and real-world events in Syria during Arab Spring. CRQA is an extension of RQA,
+which captures the patterns of revisited states of a single time series
+[@zbilut1992embeddings; @webber1994dynamical]. CRQA allows for two time series
+to be projected onto one another to investigate shared states and trajectories.
+In CRQA, we track these shared states by identifying *recurrent points*, or
+intersections of time during which two signals shared or revisited the same
+state. These shared states can be at the same time or at later points in the
+time series. We can further chart shared trajectories by examining the
+occurrences and patterns of multiple sequential recurrent points.
+
+To perform CRQA, the time series must be converted to the same scale, while
+still preserving a sampling rate that respects the native timescale of the
+system [cf. Nyquist frequency in signal processing; @grenander1959probability].
+Because the social cohesion and event data have different scales and values, we
+converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g.,
+Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
+levels of social cohesion and counts of all, positive, and negative events on
+each day. We implemented CRQA using the `crqa` package [@R-crqa] for R
+[@R-base].
 
@@
 a cross-recurrence plot, two time series are plotted against each other on the
-$x$ and $y$ axes. At every point where they share the same state, a point
-in placed on the plot to indicate recurrence. (For categorical CRQA, this process
+$x$ and $y$ axes. At every point where they share the same state, a point in
+placed on the plot to indicate recurrence. (For categorical CRQA, this process
 is similar to the Cartesian product.)
 
-We can visually analyze these plots
-to reveal patterns of structure and recurrence. The line $y = x$ is known
-as the *line of identity*. This line falls where the time series match
-temporally. A filled line would indicate perfect in-phase synchrony between the
-two time series. See
-Figures \@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg)
-for examples of RPs.
+We can visually analyze these plots to reveal patterns of structure and
+recurrence. The line $y = x$ is known as the *line of identity*. This line falls
+where the time series match temporally. A filled line would indicate perfect
+in-phase synchrony between the two time series. See Figures
+\@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) for examples of
+RPs.
 
@@
 provides information into the patterns and dynamics of the new shared system.
-These metrics are also critical for inferential
-statistics. We will focus most directly on two of these metrics: 
-*recurrence rate* and *determinism*.
-
-The percentage of recurrent points to total possible points is a metric
-called the *recurrence rate* (*RR*). This metrics gives a general description of
-how frequently the time series are sharing the same states. In the current
-study, a recurrent point would indicate that the level of social cohesion
-and frequency of events were at the same intensity.
-
-Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series
-are moving together across time in a shared state. The percentage of
-recurrent points on the plot that fall along diagonal line structures 
-(i.e., two or more
-consecutive points) is a metric called *percent determinism* 
-(or simply *determinism*; *DET*). For the
-current project, a high DET would indicate that not only are the levels of
-social cohesion and frequency of events occurring at similar intensities,
-but they are doing so across consecutive days.
+These metrics are also critical for inferential statistics. We will focus most
+directly on two of these metrics: *recurrence rate* and *determinism*.
+
+The percentage of recurrent points to total possible points is a metric called
+the *recurrence rate* (*RR*). This metrics gives a general description of how
+frequently the time series are sharing the same states. In the current study, a
+recurrent point would indicate that the level of social cohesion and frequency
+of events were at the same intensity.
+
+Recurrent points that occur in successive moments form line structures. These
+are conceptualized as shared trajectories, where the two time series are moving
+together across time in a shared state. The percentage of recurrent points on
+the plot that fall along diagonal line structures (i.e., two or more consecutive
+points) is a metric called *percent determinism* (or simply *determinism*;
+*DET*). For the current project, a high DET would indicate that not only are the
+levels of social cohesion and frequency of events occurring at similar
+intensities, but they are doing so across consecutive days.
 
 A number of other metrics provide insight not only into the amount of structure
-between the systems but about the nature of this shared structure.
-The average length of the line structures is called *mean line* (L), which can
-be conceptualized as the average amount of time that the two time series move
-together before one or both shift states. The longest line length is called
-*max line* (*maxL*); it indicates the longest instance of being “stuck” in a
-particular state together and is a measure of the stability of the system. 
-The total *number of lines* on the plot (*NRLINE*) 
-scales with structure: The more lines that exist, the more coupled the two 
-systems are. The complexity or variability of line lengths is captured by a 
-metric called *entropy* (*ENTR*)---which may also be normalized by the total 
-number of lines (i.e., *normalized entropy*; *rENTR*)---and indicates
-the stability and predictability of the system. When one of the signals gets
-“stuck” in a state and the other moves on to other states, this results in
-vertical line structures, which are quantified in *laminarity* (*LAM*;
-i.e., the proportion of points forming vertical line structures) 
-and *trapping time* (*TT*; i.e., the average length of the
-vertical trajectories). For more detail on CRQA metrics, see @R-crqa.
+between the systems but about the nature of this shared structure. The average
+length of the line structures is called *mean line* (L), which can be
+conceptualized as the average amount of time that the two time series move
+together before one or both shift states. The longest line length is called *max
+line* (*maxL*); it indicates the longest instance of being “stuck” in a
+particular state together and is a measure of the stability of the system. The
+total *number of lines* on the plot (*NRLINE*) scales with structure: The more
+lines that exist, the more coupled the two systems are. The complexity or
+variability of line lengths is captured by a metric called *entropy*
+(*ENTR*)---which may also be normalized by the total number of lines (i.e.,
+*normalized entropy*; *rENTR*)---and indicates the stability and predictability
+of the system. When one of the signals gets “stuck” in a state and the other
+moves on to other states, this results in vertical line structures, which are
+quantified in *laminarity* (*LAM*; i.e., the proportion of points forming
+vertical line structures) and *trapping time* (*TT*; i.e., the average length of
+the vertical trajectories). For more detail on CRQA metrics, see @R-crqa.
 
@@
 #### Permutation Test
-Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not have
-inherently meaningful values. As a result, CRQA is best used as a relative
-metric---that is, comparing the CRQA values across conditions or subsets
-of the data. Typically, meaningful differences between values are determined with
+Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not
+have inherently meaningful values. As a result, CRQA is best used as a relative
+metric---that is, comparing the CRQA values across conditions or subsets of the
+data. Typically, meaningful differences between values are determined with
 traditional inferential statistics. While this may not be a problem for
@@
 
-For CRQA, this can be addressed using *permutation tests*.
-Similar to more established methods of statistical significance in CRQA research
-[which create surrogate time series; e.g., @paxton2017interpersonal],
-the permutation test approach to significance testing allows the researcher
-to use a time series as its own baseline by testing whether the *structure*
-of the unfolding events of the time series---rather than the *raw frequency* of the 
-events within the time series---cohere together more than would be expected
-by chance. A permutation test is similar to
-bootstrapping, except that the sampling of observations is done without
-replacement. In this approach, we simply create a large number of permutations
-of the original time series (i.e., breaking up the dependency across time points but
-preserving the frequencies of the events), conduct CRQA for each of those
-permutations, and then examine whether the real time series' CRQA metrics
-exceed those that we would expect to see by chance. The proportion of times that
-the real time series' values exceeds the surrogate time series' values can
-be interpreted as the alpha criterion to determine significance. 
-For more information on permutation
-tests, see @good2013permutation.
-
-Using the real deciles of social cohesion, count of all events,
-count of positive events, and count of negative events, we conducted a series
-of permutation tests 
-(one for the comparison between social cohesion and each type of event count)
-to determine statistical difference from chance for each CRQA metric.
-Using the `sample` function in base R [@R-base], $1000$ permuted time series were
-created for each of the real time series.  
-CRQA was then run $1000$ times for social cohesion and count of all
-events, social cohesion and count of positive events, and social cohesion and
-count of negative events using the permuted time series. This resulted in
-$1000$ results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles
-of the metrics from the permuted CRQ analyses. Given that a permutation test
-is similar to bootstrapping but does not include replacement, all points were
-included in each CRQA analysis, leaving RR constant across all permutations. Thus,
-RR is not included in the inferential tests.
+For CRQA, this can be addressed using *permutation tests*. Similar to more
+established methods of statistical significance in CRQA research [which create
+surrogate time series; e.g., @paxton2017interpersonal], the permutation test
+approach to significance testing allows the researcher to use a time series as
+its own baseline by testing whether the *structure* of the unfolding events of
+the time series---rather than the *raw frequency* of the events within the time
+series---cohere together more than would be expected by chance. A permutation
+test is similar to bootstrapping, except that the sampling of observations is
+done without replacement. In this approach, we simply create a large number of
+permutations of the original time series (i.e., breaking up the dependency
+across time points but preserving the frequencies of the events), conduct CRQA
+for each of those permutations, and then examine whether the real time series'
+CRQA metrics exceed those that we would expect to see by chance. The proportion
+of times that the real time series' values exceeds the surrogate time series'
+values can be interpreted as the alpha criterion to determine significance. For
+more information on permutation tests, see @good2013permutation.
+
+Using the real deciles of social cohesion, count of all events, count of
+positive events, and count of negative events, we conducted a series of
+permutation tests (one for the comparison between social cohesion and each type
+of event count) to determine statistical difference from chance for each CRQA
+metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
+series were created for each of the real time series. CRQA was then run $1000$
+times for social cohesion and count of all events, social cohesion and count of
+positive events, and social cohesion and count of negative events using the
+permuted time series. This resulted in $1000$ results for each of the CRQA
+metrics for each combination of time series. Statistical significance from
+chance was set at the 95th and 99th percentiles of the metrics from the permuted
+CRQ analyses. Given that a permutation test is similar to bootstrapping but does
+not include replacement, all points were included in each CRQA analysis, leaving
+RR constant across all permutations. Thus, RR is not included in the inferential
+tests.
 
 ### Windowed Cross-Recurrence Quantification Analysis
-We used windowed cross-recurrence quantification analysis
-[WCRQA; @webber2005recurrence] to further investigate the evolution of the
-temporal dynamics of social cohesion and real-world events. In this analysis,
-a smaller “window” of time points is used to calculate CRQA and capture more
-fine-grained dynamics of two time series. The window remains the same size and
-“slides” diagonally up the line of identity. The changes in the CRQA metrics
-across the windows can reveal changes in dynamics that can then be linked to
-external, real-world events. 
-We implemented WCRQA using the `crqa` package [@R-crqa] for R [@R-base].
+We used windowed cross-recurrence quantification analysis [WCRQA;
+@webber2005recurrence] to further investigate the evolution of the temporal
+dynamics of social cohesion and real-world events. In this analysis, a smaller
+“window” of time points is used to calculate CRQA and capture more fine-grained
+dynamics of two time series. The window remains the same size and “slides”
+diagonally up the line of identity. The changes in the CRQA metrics across the
+windows can reveal changes in dynamics that can then be linked to external,
+real-world events. We implemented WCRQA using the `crqa` package [@R-crqa] for R
+[@R-base].
 
 #### Metrics
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
-respective window. For these analyses, we decided to focus on recurrence rate 
-and determinism.
+For WCRQA analyses, we decided to focus on RR and DET.
 
@@
 In addition to the CRQA parameters, two other parameters are required when
-conducting WCRQA. First, the *window size*
-will determine how many observations are used in each CRQA analysis. We
-conducted WCRQA with a window size of $14$ to investigate the dynamics over
-two weeks and allow for the capture of more structure and thus a more
-meaningful interpretation of DET.
-
-The second parameter to be chosen is a *window step size*. 
-Window step size is how far the window moves up the line of identity
-before conducting CRQA again. We chose $1$ for the step size to understand
-how the metrics evolve from day to day.
+conducting WCRQA. First, the *window size* will determine how many observations
+are used in each CRQA analysis. We conducted WCRQA with a window size of $14$ to
+investigate the dynamics over two weeks and allow for the capture of more
+structure and thus a more meaningful interpretation of DET.
+
+The second parameter to be chosen is a *window step size*. Window step size is
+how far the window moves up the line of identity before conducting CRQA again.
+We chose $1$ for the step size to understand how the metrics evolve from day to
+day.
 
@@
 #### Visualization
-To visualize WCRQA, the resulting metrics from each window can be plotted
-as a time series. This allows for visual interpretation of the pattern or
-fluctuation of the metrics across time. These dynamics can then be linked
-to other external events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
+To visualize WCRQA, the resulting metrics from each window can be plotted as a
+time series. This allows for visual interpretation of the pattern or fluctuation
+of the metrics across time. These dynamics can then be linked to other external
+events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
 \@ref(fig:plot-wcrqa-source-targ-all) for examples.
@@
 #### Permutation Test
-To visualize the differences in the WCRQA metrics from those obtained by
-chance, a permutation test was done to set upper and lower bounds for the
-95th and 99th percentiles. Using a sample size of 14, $1000$ permuted
-time series were generated without replacement for each real time series. The
-upper and lower 95th and 99th percentiles were set based on the distribution
-of the permuted WCRQA metrics.
+To visualize the differences in the WCRQA metrics from those obtained by chance,
+a permutation test was done to set upper and lower bounds for the 95th and 99th
+percentiles. Using a sample size of 14, $1000$ permuted time series were
+generated without replacement for each real time series. The upper and lower
+95th and 99th percentiles were set based on the distribution of the permuted
+WCRQA metrics.
 
@@
 
-A permutation test for the CRQA of social cohesion and count of all events 
-found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
-All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ-all);
+A permutation test for the CRQA of social cohesion and count of all events found
+a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
+metrics did not reach significance (Figure \@ref(fig:plot-rp-targ-all);
 \autoref{table-1}).
 
-A permutation test for the CRQA of social cohesion and 
-count of positive events found no statistically significant difference for any 
-of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
-\autoref{table-1}).
-
-A permutation test for the CRQA of social cohesion and 
-count of negative events found a statistically significant difference for DET, 
-NRLINE, L, ENTR, LAM, and TT. All other metrics did not reach significance 
-(Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
-
-A qualitative investigation of the recurrence plots suggests
-a shift in dynamics around the 36th observation, 
-which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of positive events
+found no statistically significant difference for any of the metrics other than
+TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found a statistically significant difference for DET, NRLINE, L, ENTR, LAM, and
+TT. All other metrics did not reach significance (Figure
+\@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
+
+A qualitative investigation of the recurrence plots suggests a shift in dynamics
+around the 36th observation, which corresponds to May 4th, 2012.
 
@@
 ### Syria as Source and Target
-A permutation test for the CRQA of social cohesion and count of all 
-events found a statistical difference from chance for DET, NRLINE, and 
-LAM. All other metrics were non-significant (Figure 
-\@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of positive 
-events found a statistical difference from chance for maxL, ENTR, and LAM 
-(Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of negative 
-events found a statistical difference from chance for DET, NRLINE, and rENTR. 
-All other metrics were non-significant (Figure 
-\@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).
-
-Looking qualitatively at the recurrence plots, there again appeared 
-to be a shift in dynamics around the 36th observation (May 4th, 2012).
+A permutation test for the CRQA of social cohesion and count of all events found
+a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
+were non-significant (Figure \@ref(fig:plot-rp-source-targ-all);
+\autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of positive events
+found a statistical difference from chance for maxL, ENTR, and LAM (Figure
+\@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found a statistical difference from chance for DET, NRLINE, and rENTR. All other
+metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg);
+\autoref{table-2}).
+
+Looking qualitatively at the recurrence plots, there again appeared to be a
+shift in dynamics around the 36th observation (May 4th, 2012).
 
@@
 In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
-\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented
-by horizontal red lines, and the 99th percentiles are
-represented by horizontal orange lines. The trend lines are plotted in blue.
+\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by
+horizontal red lines, and the 99th percentiles are represented by horizontal
+orange lines. The trend lines are plotted in blue.
 
@@
 
-For social cohesion and count of all events, there was a consistent period 
-of above-chance RR from the 7th--12th and 36th--47th window. In addition
-to some one-week peaks at the beginning of the time period, DET was largely 
-above chance from the 46th to the 61st window, with some exceptions 
-(Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of positive events, we saw a downward trend in 
-RR as the window advances throughout the sample. Interestingly, we see
-largely above-chance RR until the 50th window, with some exceptions during
-window periods 20-30. DET was at or above chance for the 7th--17th, 32nd-34th, 
-and 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of negative events, RR stayed above
-or almost above chance from the 4th--7th and 43rd-47th windows. DET
-was above or nearly above chance in the 1st and 2nd windows, with intermittent 
-peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+For social cohesion and count of all events, there was a consistent period of
+above-chance RR from the 7th--12th and 36th--47th window. In addition to some
+one-week peaks at the beginning of the time period, DET was largely above chance
+from the 46th to the 61st window, with some exceptions (Figure
+\@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of positive events, we saw a downward trend in RR
+as the window advances throughout the sample. Interestingly, we see largely
+above-chance RR until the 50th window, with some exceptions during window
+periods 20-30. DET was at or above chance for the 7th--17th, 32nd--34th, and
+60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of negative events, RR stayed above or almost
+above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
+above chance in the 1st and 2nd windows, with intermittent peaks in later
+windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 7th--13th and 26th--47th 
-windows. DET also showed above- or nearly above-chance values in windows 7 
-through 17 and intermittent peaks between the 34th and 61st windows 
-(Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-For social cohesion and count of 
-positive events, there was a downward trend in RR as the window moved, with 
-largely above-chance values in the first 20 windows and the 32nd--45th windows. 
-DET stayed largely within chance, with the exception of windows 13 
-through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-For social cohesion
-and negative events, there was an extended period of time during which RR 
-(32nd--47th windows) and DET (35th--39th windows) were above or nearly above 
-chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
-May 3rd--14th, 2012.
+above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
+also showed above- or nearly above-chance values in windows 7 through 17 and
+intermittent peaks between the 34th and 61st windows (Figure
+\@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and count of positive events, there was a downward trend in
+RR as the window moved, with largely above-chance values in the first 20 windows
+and the 32nd--45th windows. DET stayed largely within chance, with the exception
+of windows 13 through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and negative events, there was an extended period of time
+during which RR (32nd--47th windows) and DET (35th--39th windows) were above or
+nearly above chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These
+windows span from May 3rd--14th, 2012.
 
 # Discussion
-In the present study, we investigated the dynamics of real-world events
-and online communication on Twitter in Syria during Arab Spring. 
-CRQA methodology allows us to model the relationship between sociolinguistic 
-cohesion and exogenous political events. This work stands alongside the model 
-of Palestinian-Israeli social media and events developed by Zeitzoff (2011), 
-and the role of peripheral participants in the Syrian Arab Spring movement by 
+In the present study, we investigated the dynamics of real-world events and
+online communication on Twitter in Syria during Arab Spring. CRQA methodology
+allows us to model the relationship between sociolinguistic cohesion and
+exogenous political events. This work stands alongside the model of
+Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
+the role of peripheral participants in the Syrian Arab Spring movement by
 Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
-demonstrate how language and social mobilization interact with events along 
-the conflict-cooperation continuum in Syria. We have introduced a novel 
-theoretical framework of sociolinguistic cohesion which we operationalize 
-using a weighted measure of lexical relationships. We examined
-how social mobilization both virtually and physically evolve over time in
-tandem. Using nonlinear dynamical time series analyses, we investigated the 
-theory that virtual mobilization is increasingly reflective of real-world 
-events during times of strife.
+demonstrate how language and social mobilization interact with events along the
+conflict-cooperation continuum in Syria. We have introduced a novel theoretical
+framework of sociolinguistic cohesion which we operationalize using a weighted
+measure of lexical relationships. We examined how social mobilization both
+virtually and physically evolve over time in tandem. Using nonlinear dynamical
+time series analyses, we investigated the theory that virtual mobilization is
+increasingly reflective of real-world events during times of strife.
 
@@
 ### Syria as Target
-The significant result of DET for social cohesion with all and negative 
-events supports our first hypothesis that event salience is coupled with online 
-social cohesion. The frequency of all and negative events are thus associated 
-with greater shared trajectories with social cohesion that would be expected 
-by chance. However, when we specifically target positive events, the connection
-to social cohesion fades, providing further support for our second hypothesis. 
+The significant result of DET for social cohesion with all and negative events
+supports our first hypothesis that event salience is coupled with online social
+cohesion. The frequency of all and negative events are thus associated with
+greater shared trajectories with social cohesion that would be expected by
+chance. However, when we specifically target positive events, the connection to
+social cohesion fades, providing further support for our second hypothesis.
 Positive events may be less coupled to social cohesion than more salient
@@
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the dataset increased
-in size by 1,690 samples. These additional observations are times where
-Syria initiated an event with another country. Events initiated by Syria
-but directed internally within the country were already captured by the
-target-only filtering. The increase in coupling between positive events
-and social cohesion can thus only be due to the externally
-directed events. Though the coupling between social cohesion with
-negative and all events were largely unchanged, 
-positive events and social cohesion showed greater stability
-in their coupling (reflected in maxL); while TT was no longer
-significant in these analyses, LAM (related to TT) did
-reach statistical significance.
-
-While interesting, the underlying meaning or drivers of this change
-in results requires further investigation that incorporates the
-actual content of the tweets themselves. One possible reason (among
-many) may be that the finding was spurious. The positive external 
-events from Syria may have been self-serving, aiming to prevent intervention
-by other countries or to cover up what was happening internally.
-During these moments, the increased cohesion may reflect a surge from 
-the Syrian people trying to raise awareness of the situation or
-to decry the Syrian government's attempts to improve their international
-standing. In this case, the increased coupling of positive events would
-be coupled not with shared positive affect in social media but instead
-to shared negative affect in social media in response. However, we
-cannot test this hypothesis with the current data; future 
-research should explore the semantic content of this tweet
-corpus to determine the nature of the socially cohered language.
+By adding Syria as a source in the data filtering, the dataset increased in size
+by 1,690 samples. These additional observations are times where Syria initiated
+an event with another country. Events initiated by Syria but directed internally
+within the country were already captured by the target-only filtering. The
+increase in coupling between positive events and social cohesion can thus only
+be due to the externally directed events. Though the coupling between social
+cohesion with negative and all events were largely unchanged, positive events
+and social cohesion showed greater stability in their coupling (reflected in
+maxL); while TT was no longer significant in these analyses, LAM (related to TT)
+did reach statistical significance.
+
+While interesting, the underlying meaning or drivers of this change in results
+requires further investigation that incorporates the actual content of the
+tweets themselves. One possible reason (among many) may be that the finding was
+spurious. The positive external events from Syria may have been self-serving,
+aiming to prevent intervention by other countries or to cover up what was
+happening internally. During these moments, the increased cohesion may reflect a
+surge from the Syrian people trying to raise awareness of the situation or to
+decry the Syrian government's attempts to improve their international standing.
+In this case, the increased coupling of positive events would be coupled not
+with shared positive affect in social media but instead to shared negative
+affect in social media in response. However, we cannot test this hypothesis with
+the current data; future research should explore the semantic content of this
+tweet corpus to determine the nature of the socially cohered language.
 
@@
 ### Syria as Target
-The time period of differing dynamics noted in the cross-recurrence
-plots---from observation 32 through 47---appears to be captured 
-by the above-chance RR values in WCRQA of social cohesion and count of all
-events (Figure \@ref(fig:plot-wcrqa-targ-all)). However,
-DET for these periods only intermittently
-rises above chance; it more consistently reaches statistical
+The time period of differing dynamics noted in the cross-recurrence plots---from
+observation 32 through 47---appears to be captured by the above-chance RR values
+in WCRQA of social cohesion and count of all events (Figure
+\@ref(fig:plot-wcrqa-targ-all)). However, DET for these periods only
+intermittently rises above chance; it more consistently reaches statistical
 significance only at the end of the window through the end of the observation
-period, following a spike in the RR between
-negative event count and social cohesion. 
-During this period, 
-the modal ICEWS event for each day (Figure \@ref(fig:plot-mode-event))
-was almost consistently -10, the most violent 
-event category. This supports our first hypothesis.
+period, following a spike in the RR between negative event count and social
+cohesion. During this period, the modal ICEWS event for each day (Figure
+\@ref(fig:plot-mode-event)) was almost consistently -10, the most violent event
+category. This supports our first hypothesis.
 
 Surprisingly---and contrary to our second hypothesis---we saw consistent
-coupling between positive event count and social cohesion. Although
-both had a downward trajectory throughout the time period under consideration,
-RR was at or above chance in nearly all windows, and DET showed
-much more consistent shared trajectories than negative events.
-This may suggest that Syrian Twitter community was reacting more cohesively
-to the positive events aimed at Syria from the international community;
-this interpretation is supported by the attenuation of the effect in the
-analyses that include Syria as both a source and a target.
+coupling between positive event count and social cohesion. Although both had a
+downward trajectory throughout the time period under consideration, RR was at or
+above chance in nearly all windows, and DET showed much more consistent shared
+trajectories than negative events. This may suggest that Syrian Twitter
+community was reacting more cohesively to the positive events aimed at Syria
+from the international community; this interpretation is supported by the
+attenuation of the effect in the analyses that include Syria as both a source
+and a target.
 
 ### Syria as Source and Target
-WCRQA on the source-and-target-filtered data showed similar
-patterns of RR between the count of all events and social cohesion
-(as observed in the target-only data), 
-though the values increased. This suggests
-that large numbers on a given day match increased levels
-of social cohesion online. However, the results for DET changed:
-While the majority of statistically significant DET windows
-occurred toward the end of the observation period for target-only
-data (creating a positive trendline), the source-and-target data
-showed a negative trendline for DET.
-
-The divergences in the all-event count data for these two
-datasets underscores the differences
-between RR and DET. As noted earlier, DET captures *trajectories*---in
-this case, similar to the impact of actions and social cohesion
-carrying across time. The same number of points (RR) can fall in
-different patterns (DET), providing important information
-about the structure of the system in question.
-
-WCRQA metrics for positive-only event counts with social cohesion showed 
-similar patterns in RR and DET as the target-only data, but the precise
-values of DET and RR were diminished. This may support the ideas suggested
-in the CRQA section, but again, only future work including the *content*
-of those tweets can directly speak to that explanation.
-
-Finally, the coupling between negative-only event counts and
-social cohesion also remained relatively similar but demonstrated some 
-important differences. First, we see a greater number of windows at
-above-chance levels for RR, including an interesting spike around window
-32 that suggests a negative externally focused action taken by Syria
-prompted a sharp rise in social cohesion. (This would not have been
-captured by the target-only dataset.) Second---like with the all-event
-data---we see different structuring of the data through differences
-in the patterns of DET; above-chance DET only occurrs within the middle
-of the observation period, around a time of increased strive (as
+WCRQA on the source-and-target-filtered data showed similar patterns of RR
+between the count of all events and social cohesion (as observed in the
+target-only data), though the values increased. This suggests that large numbers
+on a given day match increased levels of social cohesion online. However, the
+results for DET changed: While the majority of statistically significant DET
+windows occurred toward the end of the observation period for target-only data
+(creating a positive trendline), the source-and-target data showed a negative
+trendline for DET.
+
+The divergences in the all-event count data for these two datasets underscores
+the differences between RR and DET. As noted earlier, DET captures
+*trajectories*---in this case, similar to the impact of actions and social
+cohesion carrying across time. The same number of points (RR) can fall in
+different patterns (DET), providing important information about the structure of
+the system in question.
+
+WCRQA metrics for positive-only event counts with social cohesion showed similar
+patterns in RR and DET as the target-only data, but the precise values of DET
+and RR were diminished. This may support the ideas suggested in the CRQA
+section, but again, only future work including the *content* of those tweets can
+directly speak to that explanation.
+
+Finally, the coupling between negative-only event counts and social cohesion
+also remained relatively similar but demonstrated some important differences.
+First, we see a greater number of windows at above-chance levels for RR,
+including an interesting spike around window 32 that suggests a negative
+externally focused action taken by Syria prompted a sharp rise in social
+cohesion. (This would not have been captured by the target-only dataset.)
+Second---like with the all-event data---we see different structuring of the data
+through differences in the patterns of DET; above-chance DET only occurrs within
+the middle of the observation period, around a time of increased strive (as
 noted above).
@@
 
-Nonlinear methods have been transformative for a variety of research
-areas [including psychology, @coco2014cross]. One of the goals in the
-present work was to introduce variants of one kind of nonlinear
-method---specifically, recurrence quantification analysis---to
-this research area. While a number of excellent guides can provide
-detailed explanations of the methods and their statistical underpinnings 
-[e.g., @riley2005tutorials; @webber1994dynamical; @webber2005recurrence],
-one of the most important considerations that should be briefly
-summarized here is about data.
-
-Nonlinear methods---including recurrence-based analyses---require
-time series data. This requires repeated observations of the behavior
-at interest, preferably at a frequency that provides information 
-about timing at a temporal resolution that allows the researcher to 
-make observations about interesting variations over time. While
-this is easily controlled by scientists who conduct experimental
-research, it can be more difficult for scientists who rely on
-trace data or naturally occurring data. However, where possible,
-we recommend political scientists work to expand efforts for
-improving the temporal granularity of the data. One possible
-means of achieving this may be through collaborative efforts
-like the Open Event Data Alliance [@schrodt2014three].
-
-This methodology should be of great interest to social scientists 
-investigating social mobilization. It has potential applications for 
-gender studies and the #MeToo movement and for the relationship between 
-social protest and repression during the Black Lives Matter protests. 
-Fundamentally, this methodological approach can help us better understand
-the human social mechanisms underlying social media and its influence on human 
-behavior in real life. Given that many governments enact repressive 
-measures when they determine that collective action by citizens is
-imminent, this methodology should help to improve 
-the predictive power of using social media data in estimating repressive 
-behavior. If social media messages are increasing in cohesion, this may 
-represent a threat to civil and political liberties of citizens engaging
-in collective action.
+Nonlinear methods have been transformative for a variety of research areas
+[including psychology, @coco2014cross]. One of the goals in the present work was
+to introduce variants of one kind of nonlinear method---specifically, recurrence
+quantification analysis---to this research area. While a number of excellent
+guides can provide detailed explanations of the methods and their statistical
+underpinnings [e.g., @riley2005tutorials; @webber1994dynamical;
+@webber2005recurrence], one of the most important considerations that should be
+briefly summarized here is about data.
+
+Nonlinear methods---including recurrence-based analyses---require time series
+data. This requires repeated observations of the behavior at interest,
+preferably at a frequency that provides information about timing at a temporal
+resolution that allows the researcher to make observations about interesting
+variations over time. While this is easily controlled by scientists who conduct
+experimental research, it can be more difficult for scientists who rely on trace
+data or naturally occurring data. However, where possible, we recommend
+political scientists work to expand efforts for improving the temporal
+granularity of the data. One possible means of achieving this may be through
+collaborative efforts like the Open Event Data Alliance [@schrodt2014three].
+
+This methodology should be of great interest to social scientists investigating
+social mobilization. It has potential applications for gender studies and 
+the #MeToo movement and for the relationship between social protest and repression
+during the Black Lives Matter protests. Fundamentally, this methodological
+approach can help us better understand the human social mechanisms underlying
+social media and its influence on human behavior in real life. Given that many
+governments enact repressive measures when they determine that collective action
+by citizens is imminent, this methodology should help to improve the predictive
+power of using social media data in estimating repressive behavior. If social
+media messages are increasing in cohesion, this may represent a threat to civil
+and political liberties of citizens engaging in collective action.
 
 ## Conclusion
-Considering the pervasiveness of social media, it is unsurprising
-that social activists and protesters have
-utilized these platforms to support real-world mobilization. 
-Here, we quantitatively explored the connection
-between online social cohesion and real-world events. In addition
-to introducing political scientists to a family of powerful nonlinear 
-dynamics analyses, our results have serious implications for monitoring global
-movements in consistent across other social uprisings. While  
-state-run media in regions of authoritarian rule are often biased and 
-serve as propaganda for the leader and central government, the 
+Considering the pervasiveness of social media, it is unsurprising that social
+activists and protesters have utilized these platforms to support real-world
+mobilization. Here, we quantitatively explored the connection between online
+social cohesion and real-world events. In addition to introducing political
+scientists to a family of powerful nonlinear dynamics analyses, our results have
+serious implications for monitoring global movements in consistent across other
+social uprisings. While state-run media in regions of authoritarian rule are
+often biased and serve as propaganda for the leader and central government, the
 self-organized nature of Twitter provides a new avenue to gain insight into
-truths about uprisings and social mobilization. By conceptualizing Twitter 
-and real-world events as two elements of an inextricably linked dynamical 
-system, the levels of social cohesion within social media platforms could be 
-monitored for fluctuations indicating shifts in power and peace. Social media
-mobilization may thus help alert the world to citizens' actions and reactions 
-that are suppressed by government regimes, providing insight into events that 
-may not otherwise be broadcast and allowing for faster intervention.
+truths about uprisings and social mobilization. By conceptualizing Twitter and
+real-world events as two elements of an inextricably linked dynamical system,
+the levels of social cohesion within social media platforms could be monitored
+for fluctuations indicating shifts in power and peace. Social media mobilization
+may thus help alert the world to citizens' actions and reactions that are
+suppressed by government regimes, providing insight into events that may not
+otherwise be broadcast and allowing for faster intervention.
 
@@
 
-This work was completed in part as coursework done by lead author M. Chiovaro
-in the ``Applications of Nonlinear Time Series Analysis'' graduate
-course at the University of Connecticut (co-taught by coauthor A. Paxton and
-Steven J. Harrison).
+This work was completed in part as coursework done by lead author M. Chiovaro in
+the ``Applications of Nonlinear Time Series Analysis'' graduate course at the
+University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
+Harrison).
 

### 2020-06-01 manuscript.Rmd
Editing intro

@@
 Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and flyers generated on mimeograph machines,
-through in-person meetings for social organizations and in churches, and through
+using phone tree calling sheets and mimeographed flyers,
+through in-person meetings of social organizations and churches, and through
 word of mouth. They gathered together and hand-made protest signs that reflected
 their agendas. As McAdam found, people were more likely to join movements when
-they had a personal connection [@McAdam_1986; @McAdam_1986]. Strong ties were
-better predictors of involvement in high-risk protest activity. However, the era
-of the Internet and online social mobilization through decentralized networks
-has upended theories about recruitment to, and participation in, social
+they had a personal connection [@mcadam1986recruitment; @mcadam1993specifying]: 
+Historically, strong ties have been
+strong predictors of involvement in high-risk protest activity. 
+However, the rise of the Internet and its decentralized online networks
+has upended theories about recruitment to---and participation in---social
 movements. Strong interpersonal ties have yielded to weak impersonal ties that
-strongly predict involvement in social movements [@Threlkeld_2017]. The research
+strongly predict involvement in social movements [@steinert2017spontaneous]. Research
 methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to big data analysis of language on social media. The
-cohesiveness and strength of social movements in the pre-Internet era could be
-operationalized by the number of people turning out to protest, and through the
-political events that precipitated and resulted from social gatherings en masse.
-
-In the offline era of social mobilization, the content of placards and protest
-signs provided the protest narrative for onlookers near and far. For cohesive
-social movements, the content of placards and posters itself was cohesive. For
-example, the “I am a man” posters held by the men involved in the 1968
-sanitation workers’ strike reflected their internal cohesion and unified,
-goal-oriented movement [@Windsor_2020]. Social media replicates and amplifies
+ethnographic interviews to ``big data'' analyses of language on social media. 
+*(Probably need to wrap up with a sentence here.)*
+
+The cohesiveness and strength of social movements in the pre-Internet era could be
+operationalized by the number of people turning out to protest and through the
+political events that precipitated and resulted from social gatherings *en masse*.
+The content of placards and protest
+signs provided the protest narrative in their own words. Cohesive
+social movements were reflected in their cohesive placards and posters. For
+example, the ``I am a man'' posters held by the men involved in the 1968
+sanitation workers' strike reflected their internal cohesion and unified,
+goal-oriented movement [@Windsor2020].
+
+In the Internet age, social media replicates and amplifies
 this phenomenon during moments of social unrest. Amid the cacophony of messages
-during political upheaval, such as the Arab Spring, consistent themes emerge
+during political upheaval---such as the Arab Spring---consistent themes emerge
 through hashtags, retweets, and the repeated mentions of concepts such as
 regime, security, demonstration, and human rights. The cohesiveness of these
-themes, i.e., whether movement participants are “singing in one voice,” reflects
-the real-world events happening contemporaneously with collective action in
+themes (i.e., whether movement participants are metaphorically singing in one voice) 
+reflects the real-world events happening contemporaneously with collective action in
 social movements or civil conflicts.
@@
 cohesion and social cohesion in times of social conflict and unrest. We tackle a
-question related to the one posed by Zeitzoff (2017): how does social media
-reflect on-the-ground realities during times of social conflict
-[@Zeitzoff_2017]? We examine patterns of linguistic cohesion on Twitter during
-the Arab Spring uprising in Syria between March and June 2012. We contextualize
-the linguistic cohesion with social mobilization and response to the relative
+question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does 
+social media reflect on-the-ground realities during times of social conflict?
+To do so, we examine patterns of linguistic cohesion on Twitter during
+the Arab Spring uprising in Syria between March and June 2012.
+
+We contextualize linguistic cohesion with social mobilization and response to the relative
 intensity of the conflict. Cohesion is a multi-layered concept referring to the
@@
 dynamical systems methodology to model the relationship between language and
-action. We find that in the early months of 2012, conflict-related events were
-more strongly associated with linguistic cohesion than were more neutral or
-peaceful events.
-
-Disentangling the complicated relationship between mass online mobilization, and
-social mobilization in person, continues to be a relevant question. The
+action.
+
+Disentangling the complicated relationship between mass online mobilization---and
+social mobilization in person---continues to be relevant, even as our modes
+of communication change. The
 political processes that transpired during and after the Arab Spring are still
-in the process of being understood. As Zeitzoff (2017) recognizes, social media
-is changing conflict, but the mechanisms and relationships are still being
-understood [@Zeitzoff_2017].
+in the process of being understood. As Zeitzoff [-@zeitzoff2017social] recognizes, 
+social media is changing conflict, but the mechanisms and relationships by
+which it does so are still being understood.
 

### 2020-06-01 manuscript.Rmd
Edits to Syria in Context section

@@
 
-## Syria in context
-The decades prior to the onset of the Arabs Spring in Syria were marked by
+## Syria in Context
+The decades preceding the Arab Spring in Syria were marked by
 social repression and fear. In 1971, Hafez al-Assad overthrew the previous
-leader and remained in power for thirty years, presiding during times of
+leader and remained in power for thirty years, presiding during
 regional contentiousness and cooperation until his death in 2000. His son,
-Bashar al-Assad, who continued the regime of authoritarian leadership, assumed
-his office. The Assad lineage hails from a minority Islamic sect, the Alawites,
-in a multi-religious and multi-ethnic country comprised of Christians, Sunni and
+Bashar al-Assad continued the regime of authoritarian leadership as he assumed
+his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
+in a multi-religious and multi-ethnic country comprising Christians, Sunni and
 Shia Muslims, Kurds, and Palestinian refugees.
@@
 Following a wave of democratization efforts across the Middle East and North
-Africa, protests began modestly in Syria in March 2011. The regime responded
+Africa, modest Syrian protests began in March 2011. The regime responded
 harshly with imprisonments, detentions, censorship, and military operations as
 the resistance to Assad’s regime grew and spread throughout the country. The
-fighting escalated in earnest in March 2012, after increased unrest in the
-western city of Homs. International actors, including the Red Cross/Red Crescent
+fighting escalated dramatically in March 2012, after increased unrest in the
+western city of Homs. International actors---including the Red Cross/Red Crescent
 Society, the United Nations General Assembly, the Security Council, and
-individual leaders throughout the world worked toward cease-fires, negotiations,
-and concessions, without much success. While many high-level military and
-diplomatic officials have defected from the regime, sufficient loyal forces have
-been able to execute continued repression. During this time between March and
-June 2012, more than eight million tweets were sent within Syria revealing the
-details of the conflict.
+individual world leaders---worked toward cease-fires, negotiations,
+and concessions without much success. While many high-level military and
+diplomatic officials defected from the regime, numerous loyal forces
+continued the regime's repression, and the Syrian people turned to social
+media to help coordinate their activism and communicate to the world. Between March and
+June 2012, more than 8 million tweets were sent within Syria, revealing the
+details of the conflict suppressed by the government.
 
 Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
-people comprise between 10-15% of the population, Alawites between 8-15%,
-Christians about 10%. There are also much smaller sects, i.e. the Ismailis and
-Druze, but Sunni Muslims comprise the vast majority of society, and most people
-speak Arabic as their mother tongue. Most policy reports addressing the current
+people make up between 10-15% of the population, Alawites between 8-15%,
+Christians about 10%. There are also much smaller sects (e.g., Ismailis,
+Druze), but Sunni Muslims comprise the vast majority of society. Most people
+speak Arabic as their primary language. Most policy reports addressing the current
 conflict report on the cohesion of the ruling Alawite military elite, rather
 than on the cohesiveness of the opposition movement. However, the Sunni
-majority’s disaffection with the Syrian government and lack of political
+majority's disaffection with the Syrian government and their lack of political
 representation provide sufficient grievance and collective group identification

### 2020-06-01 manuscript.Rmd
Reorganize introduction
Edits to Social Media and Social Movements section

@@
 strong predictors of involvement in high-risk protest activity.
-However, the rise of the Internet and its decentralized online networks
-has upended theories about recruitment to---and participation in---social
-movements. Strong interpersonal ties have yielded to weak impersonal ties that
-strongly predict involvement in social movements [@steinert2017spontaneous]. Research
-methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to ``big data'' analyses of language on social media. 
-*(Probably need to wrap up with a sentence here.)*
 
@@
 
-In the Internet age, social media replicates and amplifies
+However, the rise of the Internet and its decentralized online networks
+has upended theories about recruitment to---and participation in---social
+movements. Strong interpersonal ties have yielded to weak impersonal ties that
+strongly predict involvement in social movements [@steinert2017spontaneous]. Research
+methodologies for measuring social movements have similarly evolved from
+ethnographic interviews to ``big data'' analyses of language on social media.
+
+Today, social media replicates and amplifies
 this phenomenon during moments of social unrest. Amid the cacophony of messages
@@
 without efficient large-scale coordination, both physically on the ground and
-virtually on social media platforms. Along with Facebook, Twitter has been
+virtually on social media platforms.
+
+Along with Facebook, Twitter has been
 credited as essential to the Arab Spring---both for protesters (as a means to
@@
 Syrian Twitter cohesion and international action coordination has not been
-investigated. Others provide skepticism about the effect of social media on
-collective action [@Seay_2014].
-
-In Foreign Affairs, Anderson writes that, “The important story about the 2011
+investigated. In fact, some have been skeptical about the effect of social media on
+collective action at all [@seay2014slacktivism].
+
+This skepticism can be summarized in a quote by Lisa Anderson:
+
+> The important story about the 2011
 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts [@Anderson_2011].” Malcolm Gladwell, in highlighting the notions
-of strong and weak ties, @Gladwell_2010 and
-@McAdam_1986, similarly expressed hesitation about the role of online
-organizing, arguing that real-life strong ties outweigh online weak ties and
-that participation in online activism only requires scant sacrifices whereas
-recruitment to higher-risk activities is done through in-person contact, namely
-strong ties [@Gladwell_2010; [@McAdam_1986]. Interestingly, these views may
+local contexts. [anderson2011demystifying]
+
+Others have similarly expressed hesitation about the role of online
+organizing. Some have argued that real-life strong ties outweigh online weak ties and
+that the power of the strong ties through in-person contact is critical
+to recruiting people for higher-risk activities 
+[@gladwell2010revolution; @mcadam1986recruitment].
+
+Interestingly, these views may
 actually help to make the case for bridging the gap between social media and
-social mobilization, by suggesting the strength of social ties in an online
-environment is inextricably linked to the context and ambitions of the actors.
-Granovetter notes that while strong ties tend to bind smaller groups, weak ties
-tend to bind groups across distances [@Granovetter_1973].
-
-Social media generates critical information about events, such as whether or not
-a demonstration will take place and what transpires when it does, how many
-people participate, and how the state, the military, and the security apparatus
+social mobilization. Such views suggest the strength of social ties in an online
+environment is inextricably linked to the *context* and *ambitions* of the actors.
+Moreover, research suggests that weak ties still retain considerable political
+power: While strong ties tend to bind smaller groups, weak ties
+tend to bind groups across distances [@granovetter1977strength].
+
+Social media generates critical information about events, including whether and how
+a demonstration will take place, how many
+people participate, and how those in power (e.g., state, military, security apparatus)
 respond. Similarly, these media platforms alert us to more global shifts within
@@
 casualties and wounded, and the types of weaponry used by parties to the
-conflict [@Zeitzoff_2017]. Social media is not entirely event-driven, however.
+conflict [@zeitzoff2017social]. Social media is not entirely event-driven, however.
 In monitoring social media channels, government forces may respond to the
 perception that citizens are gaining strength and sympathy. Governments have
-been shown to be quite tolerant of dissent so long as it does not metamorphosize
-into collective action [@King_Pan_Roberts_2013]. Additionally, the insulated
-nature of online social platforms allows valuable social dynamics to be detailed
-at unprecedented resolution and scale. As such, the digital traces left by
-individuals and collectively as groups are regarded as a valuable source of
-information that can offer powerful insights into states of social
-disequilibrium, up-risings, and escalations into civil wars.
+been shown to be quite tolerant of dissent so long as it does not metamorphose
+into collective action [@king2013censorship].
 
@@
 phones and computers with Internet connectivity, providing a stream of real-time
-shared information. This facilitates studying the degree of cohesion between
-speakers, and the alignment between that cohesion and their collective political
-behavior. Citizens can tweet the location of events like protests and military
+shared information. Citizens can share the location of events like protests and military
 incursions, the degree of state repression, and the number of casualties. In
-kind, the government, interested in remaining in power, monitors social media
-platforms to ascertain emerging threats, such as where new groups are forming
+turn, the government---interested in remaining in power---monitors social media
+platforms to ascertain emerging threats [@comninos2011twitter], 
+such as where new groups are forming
 and where existing groups are strengthening, where gatherings are held, and who
-the idea entrepreneurs are. An example of a leader manifesting his interest in
-such public conversation is given in a speech of June 3, 2012 by Bashar
-al-Assad:
-
-“I know that I have been away from the media for a long time, and I have missed
+the idea entrepreneurs are. An example of a leader 
+expressing his interest in
+such public conversation is given by Bashar al-Assad in a speech on June 3, 2012:
+
+>I know that I have been away from the media for a long time, and I have missed
 having direct contact with the citizens, but I have always been following up
 with the daily occurrences and gathering the information so that my speech can
-be built on what is said by the street.”
+be built on what is said by the street.
 
 With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes (2015) notes that regimes can attempt to thwart the growth of social
-protest online and in the streets by shutting down the Internet [@Gohdes_2015].
+Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth of social
+protest online and in the streets by shutting down the Internet.
 During these times, however, she finds that military repression increases.
-However, government information about the citizens decreases, and as such, many
+However, government information about the citizens decreases; as such, many
 regimes have elected to maintain Internet connectivity as a means of monitoring
 and surveilling their citizens.
+
+At the same time, the insulation
+of online social platforms allows researchers to detail real-world social dynamics
+at unprecedented resolution and scale [@paxton2017finding]. The digital traces left by
+individuals and collectively as groups are regarded as a valuable source of
+information that can offer powerful insights into states of social
+disequilibrium, uprisings, and escalations into civil wars.
+By examining these conversations, researchers can study the degree of cohesion between
+speakers and the alignment between that cohesion and their collective political
+behavior.
 

### 2020-06-01 manuscript.Rmd
Updates to Lexical Cohesion section and Cohesion structure

@@
 social media reflect on-the-ground realities during times of social conflict?
-To do so, we examine patterns of linguistic cohesion on Twitter during
+To do so, we examine patterns of linguistic cohesion on Twitter and their
+connection to real-world events during
 the Arab Spring uprising in Syria between March and June 2012.
-
-We contextualize linguistic cohesion with social mobilization and response to the relative
-intensity of the conflict. Cohesion is a multi-layered concept referring to the
-connectedness of words, thoughts, speakers, and actions. Cohesion reflects the
-continuity of language and expression, and it shows the connectivity of
-participants in a social movement. To address the relationship between language
-and discourse and social movements, we adopt an interdisciplinary approach that
-incorporates linguistics, psychology, and political science using nonlinear
-dynamical systems methodology to model the relationship between language and
-action.
 
@@
 
-## Lexical cohesion: Connectedness of words
+## Cohesion: A Multi-Leveled, Multi-Layered Concept
+
+We contextualize linguistic cohesion with social mobilization and response to the relative
+intensity of the conflict. Cohesion is a multi-layered concept referring to the
+connectedness of words, thoughts, speakers, and actions. Cohesion reflects the
+continuity of language and expression, and it shows the connectivity of
+participants in a social movement. To address the relationship between language
+and discourse and social movements, we adopt an interdisciplinary approach that
+incorporates linguistics, psychology, and political science using nonlinear
+dynamical systems methodology to model the relationship between language and
+action.
+
+### Lexical Cohesion: Connectedness of Words
+
+The concept of lexical, or semantic, cohesion has already been applied to the
+analysis of political speech (for example, the language of Margaret Thatcher) 
+and non-political speech [@barzilay1999using; @morris1991lexical].
+
 The words that comprise social media posts are the first level at which cohesion
-occurs. In Figure 1, we see four sequential tweets, each containing four words.
+occurs. In Figure \@ref(fig:cohesion-in-tweets), we see four sequential tweets, 
+each containing four words.
 Each sequential tweet contains some content included in the previous tweets. The
 linguistic construct of content word overlap measures the relationship across
-units of meaning – here, tweets – where identical and semantically similar words
-are repeated [@Graesser_McNamara_Louwerse_Cai_2004]. These repeated lexical
+units of meaning---here, tweets---where identical and semantically similar words
+are repeated [@graesser2004coh]. These repeated lexical
 items constitute a theme; on Twitter, this might be a particular hashtag, a
@@
 
-Lexical cohesion also includes latent semantic analysis (LSA)
-[@Graesser_McNamara_Louwerse_Cai_2004. LSA measures semantic similarity across
-meaning units using a statistical method called singular value decomposition, an
-automated method used to detect plagiarism [@Ceska_2008; @Gamallo_Bordag_2011].
-In this process, each meaning unit (tweet) is a weighted vector, and the match
-between the tweets is measured as the cosine between the two vectors. This
-process provides an empirical relationship between the words used from one tweet
-to the next. We identify this as lexical cohesion.
-
-The concept of lexical, or semantic, cohesion has already been applied to the
-analysis of political speech, for example the language of Margaret Thatcher, as
-well as non-political speech [@Barzilay_Elhadad_1999; @Morris_Hirst_1991].
-McNamara and Graesser operationalize the concept of cohesion in their software,
-Coh-Metrix, an automated tool that analyzes text and discourse
-[@Graesser_Jeon_Yan_Cai_2007; @Graesser_McNamara_Louwerse_Cai_2004;
-[@Graesser_McNamara_Kulikowich_2011]. This software generates measures of
-co-referential cohesion that captures the amount of overlap in content words (as
-opposed to function words, like a, the, and and) in adjacent, local, and global
-sentences in the passage. Content word overlap refers to the proportion of words
-and word stems that are shared between sentences. A higher proportion of overlap
-indicates greater cohesion in the sentence.
-
-In estimating cohesion in Twitter posts, tweets that share content words and
-stems will yield higher cohesion values, even amongst speakers with opposing
+Typically, these analyses focus on *content words* (e.g., nouns, adjectives,
+verbs), which convey more meaningful semantic information than *function words*
+(e.g., articles, conjunctions). While function words can provide important
+information about complexity and language structure
+[@tausczik2010psychological], content words have more specialized meaning and
+are therefore more useful when researchers want to understand *what* people are
+discussing, rather than *how* they are discussing it [@graesser2004coh;
+@mcnamara2014automated].
+
+In estimating cohesion in Twitter posts, tweets that share content words 
+will yield higher cohesion values, even among speakers with opposing
 views on the subject matter. Repetition of terms and concepts is captured by
@@
 repeats a previous item, or refers to it through synonymous language
-[@Halliday_Hasan_1976]. In social media, we can conceive of retweets – reposts
-or forwards of previous messages in part or in whole – as a form of reiteration
+[@halliday1976cohesion]. In social media, we can conceive of retweets (i.e., reposts
+or forwards of previous messages) as a form of reiteration
 that increase message cohesion. Since retweets replicate verbatim some part of
 another tweet, these tweets would also have higher cohesion. Hashtags function
-similarly, and are included in our analysis.
-
-```{r figure-1}
+similarly and are included in our analysis.
+
+```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}
 

### 2020-06-01 manuscript.Rmd
Fix characters
Call tweet cohesion figure

@@
 
-```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}
-
-# call figure 1 here
+```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = ""}
+
+# call the image
+knitr::include_graphics("./figs/cohesion-in-tweets.png")
 
@@
 This work was completed in part as coursework done by lead author M. Chiovaro in
-the ``Applications of Nonlinear Time Series Analysis'' graduate course at the
+the “Applications of Nonlinear Time Series Analysis” graduate course at the
 University of Connecticut (co-taught by coauthor A. Paxton and Steven J.

### 2020-06-01 manuscript.Rmd
Edits to Lexical and Interlocutor Cohesion sections

--- 2020-06-01 manuscript.Rmd
@@
 social movements were reflected in their cohesive placards and posters. For
-example, the ``I am a man'' posters held by the men involved in the 1968
+example, the “I am a man” posters held by the men involved in the 1968
 sanitation workers' strike reflected their internal cohesion and unified,
@@
 methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to ``big data'' analyses of language on social media.
+ethnographic interviews to “big data” analyses of language on social media.
 
@@
 intensity of the conflict. Cohesion is a multi-layered concept referring to the
-connectedness of words, thoughts, speakers, and actions. Cohesion reflects the
+connectedness of speakers, actions, and societies. Cohesion reflects the
 continuity of language and expression, and it shows the connectivity of
@@
 
-### Lexical Cohesion: Connectedness of Words
+### Lexical Cohesion: Connectedness of Words between Interlocutors
 
@@
 
-## Interlocutor cohesion
-Lexical cohesion contributes to the next level of relatedness among tweets:
-interlocutor cohesion. This is the degree to which people in a conversation,
-whether in person or online, have aligned their language [@Coupland_Giles_1988].
-Known as communication accommodation theory, the degree of alignment between
-speakers reveals their closeness, status, and deliberative strategy
-[@Giles_2016]. Speakers can converge and diverge in their communication.
-Convergence facilitates easier transmission of information, because the speakers
-– or interlocutors – presume some existing familiarity or knowledge base between
-them. When you know someone well enough to finish their sentence, this is an
-example of convergence. Divergence, on the other hand, is more laborious because
-the speakers must make their presumptions explicit and tacit. Interlocutor
-cohesion, or convergence, happens when speakers are “singing in the same key” or
-are “on the same page.” Windsor (2020) describes various types of cohesion,
-using the example of the Occupy Wall Street movement as a symbol of divergence
-given the myriad signs, slogans, and interests of the participants
-[@Windsor_2020]. On the other hand, the “I am a man” protest captured by Ernest
-Withers during the 1968 santiation workers’ strike in Memphis, TN, or the “Black
-Lives Matter” placards following the uprising in Ferguson, MO, symbolize
-convergence and strong interlocutor cohesion [@Edgar_Johnson_2018].
-
-Cognitive and social psychology theories of alignment and coordination lend
-themselves nicely to the study of social media communication during times of
-conflict and contentious behavior [@Tollefsen_Dale_Paxton_2013;
-@Garrod_Pickering_2004; @Pickering_Garrod_2004]. Over the past few decades, this
-area has garnered significant attention and produced evidence showing that
-people sometimes linguistically and behaviorally align as they interact more
-[@Giles_Coupland_Coupland_1991; @Tollefsen_Dale_Paxton_2013]. Similarly,
-accommodation theory refers to the ways in which individuals and groups
-linguistically adapt to minimize the social space distance. Speakers in a
-collective setting pursue strategies which increase their common ground, and
-this is reflected in the language they use to communicate with one another.
-
-A similar process happens among participants in social media discussions. The
-process of speakers’ (or tweeters) language becoming more similar is called
-linguistic style matching (LSM) [@Niederhoffer_Pennebaker_2002]. LSM is a form
-of synchrony between speakers, akin to linguistic convergence. As Bernieri and
-Rosenthal (1991) describe, people engaged in linguistic synchrony match each
-others’ verbal behaviors, adopting not only similar terms, but similar patterns
-of language [@Bernieri_Rosenthal_1991]. For example, LSM is particularly evident
-when one speaker introduces swearing into a genteel conversation; the first
-usage opens the vulgarity floodgates, and subsequent speakers may repeat the
-initial curse, as well as innovate new curses into the conversation. Fed by
-lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
+The use of similar language can provide insight into *interlocutor cohesion*, or
+the degree to which people are talking about similar things. This can---as noted
+earlier---include people who are talking about similar things from radically
+perspectives, as well as those who are talking about something from the same
+perspective. Previous research from political science has investigated these
+ideas [@Windsor2020]: The “Occupy Wall Street” movement has been held up as an
+example of a movement with low interlocutor and linguistic cohesion because of
+its wide range of signs and slogans, while the “I am a man” protest (captured by
+Ernest Withers during the 1968 sanitation workers' strike in Memphis, TN) or the
+“Black Lives Matter” placards (following the uprising in Ferguson, MO) have high
+lexical and interlocutor cohesion [@edgar2018struggle].
+
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
 contextualized by variation in real world events. Interlocutor cohesion may

### 2020-06-01 manuscript.Rmd
Add descriptive caption

@@
 
-```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "Add more informative caption."}
-
-# call figure 1 here
+```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets.
+Content word overlap indicates a shared relationship among tweets.
+The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring."}
+
+# call the image
+knitr::include_graphics("./figs/cohesion-in-tweets.png")
 

### 2020-06-01 manuscript.Rmd
Add theoretical framework image

@@
 
+```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion.
+Real-world events and linguistic cohesion continually interact and influence one another throughout time."}
+
+# call the image
+knitr::include_graphics("./figs/theoretical-framework.png")
+
+```
+
 ## Using Nonlinear Methods to Capture Complex Relationships

### 2020-06-01 manuscript.Rmd
Fix figure reference

@@
 together in a theoretical framework called sociolinguistic cohesion, as shown in
-Figure X. We can measure the changes in cohesion preceding and in response to
-external stimuli by evaluating the messages and the context in which they occur.
-Several mechanisms are in motion here. Previous values of linguistic cohesion
-should influence future values of linguistic cohesion. They should also
-influence future actions in the real world space. Previous events influence
-future events, and also the future cohesiveness of the opposition.
+Figure \@ref(fig:theoretical-framework). We can measure the changes in cohesion
+preceding and in response to external stimuli by evaluating the messages and the
+context in which they occur. Several mechanisms are in motion here. Previous
+values of linguistic cohesion should influence future values of linguistic
+cohesion. They should also influence future actions in the real world space.
+Previous events influence future events, and also the future cohesiveness of the
+opposition.
 

### 2020-06-01 manuscript.Rmd
Small tweak to crqa results

@@
 A permutation test for the CRQA of social cohesion and count of positive events
-found no statistically significant difference for any of the metrics other than
-TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
+found no statistically significant difference from chance for any of the metrics
+other than TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
 
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistically significant difference for DET, NRLINE, L, ENTR, LAM, and
-TT. All other metrics did not reach significance (Figure
+found a statistically significant difference from chance for DET, NRLINE, L,
+ENTR, LAM, and TT. All other metrics did not reach significance (Figure
 \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).

### 2020-06-01 manuscript.Rmd
Fit figure width

@@
 Content word overlap indicates a shared relationship among tweets.
-The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring."}
+The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}
 
@@
 ```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion.
-Real-world events and linguistic cohesion continually interact and influence one another throughout time."}
+Real-world events and linguistic cohesion continually interact and influence one another throughout time.", out.width='100%'}
 
@@
 
-In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
+In the WCRQA plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
 \@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by

### 2020-06-01 manuscript.Rmd
Update windows for wcrqa results for target filtering

@@
 For social cohesion and count of all events, there was a consistent period of
-above-chance RR from the 7th--12th and 36th--47th window. In addition to some
+above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
 one-week peaks at the beginning of the time period, DET was largely above chance
@@
 above-chance RR until the 50th window, with some exceptions during window
-periods 20-30. DET was at or above chance for the 7th--17th, 32nd--34th, and
+periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

### 2020-06-01 manuscript.Rmd
More edits to the Cohesion section

@@
 
-### Lexical Cohesion: Connectedness of Words between Interlocutors
+### Lexical and Interlocutor Cohesion
 
@@
 
-## Social and Physical Cohesion
-In turn, other studies show that linguistic alignment leads to increased social
-connectedness and solidarity [@Miles_Nind_Macrae_2009], which is associated with
-increased motivation for participation [@Walton_Cohen_Cwir_Spencer_2012],
-facilitating successful coordination of group actions toward shared goals
-[@Fusaroli_Bahrami_Olsen_Roepstorff_Rees_Frith_Tylén_2012;
-@Richardson_Dale_2005]. This research emphasizes both the importance of and
-connections between linguistic alignment and behavioral alignment. The more
-people interact, the more similar their language and linguistic patterns become.
-This holds true for face-to-face interactions as well as online communication
-[@Riordan_Dale_Kreuz_Olney_2011}. Given this, we should expect to see increased
-linguistic cohesion amongst people participating in online discussions about an
-idea, event, or individual. Given that social media reports in real time about
-actual events taking place, i.e., protests or demonstrations in which people are
-assembled together in a location, or attacks that require coordination between
-members of a unit, the cohesion in social media should be expected to correlate
-with the social cohesion of the group [@Zeitzoff_2011}.
-
-A socially cohesive group is inherently more threatening to the existing regime
-because it reflects the professionalization of potential alternate leadership,
-and collective opposition momentum. Groups with high social cohesion are more
-difficult to divide and conquer, and more cohesive messages may also garner
-increased international support. A paper published in Nature argues that global
-insurgency movements all exhibit a similar pattern to their social structure
-[@Bohorquez_Gourley_Dixon_Spagat_Johnson_2009}. The authors assert that each
-violent group has a stable state, and that exogenous events can create
-perturbations that push the group to become more cohesive, or alternatively to
-become more fragmented. Rather than frenetic, patchwork messages via Twitter,
-cohesive messages indicate increased organizational structure, which should
-incentivize a response from the government. What process is the driving force,
-though? Does an increase in linguistic cohesion precede or follow increased
-repression by the government? Do movements get stronger first, and then the
-government responds, or does the government increase its offensive measures, and
-thus social groups have a clear opponent around whom they can coalesce both
-socially and linguistically?
-
-Thus, verbal synchrony leads to physical synchrony. Shared language in an online
-environment can influence individuals’ propensity to engage in similar
-coordinated behavior. In the case of the Arab Spring, this may mean social
-mobilization in public spaces to protest against government brutality. Words in
-a passage of text – or series of tweets – have some degree of semantic relation.
-Individuals engaged in a conversation, whether in real life or online, have the
-tendency to use similar language as they interact, increasing the cohesion of
-their language. As an extension, multiple individuals collectively communicating
-can also demonstrate linguistic alignment. In the context of social conflict,
-the linguistic cohesion of participants in the online conversation should
-correspond to the degree of social cohesion on the ground. We link these
-concepts of social and linguistic cohesion together to demonstrate how language
-serves as an indicator of the degree of social mobilization, using Twitter feeds
-during the spring of 2012 in Syria.
+Given the importance of lexical and interlocutor cohesion for messaging in
+political movements, lexical cohesion may be an important bit of trace data for
+researchers interested in leveraging social media data to analyze social
+movements. Similar to large-scale studies of sociocultural movements [sometimes
+referred to as *culturomics*; e.g., @michel2011quantitative], political
+scientists can track the ways in which conversations on social media coalesce or
+diffuse around similar content words. In this way, it matters relatively little
+whether the interlocutors have precisely the same views: The point is to
+understand whether the society-level conversation is converging on similar
+language.
+
+### Social and Political Cohesion
 
@@
 
-Physical and social cohesion in the world can be modeled using event data which
+At the same time, behavioral similarity in certain contexts has been
+connected to important psychological and social effects. For example, shared
+language is associated with rapport [both in face-to-face and computer-mediated
+conversations; @niederhoffer2002linguistic; @riordan2011evidence] and
+can even be connected to better performance on shared tasks [as long as
+the language is relevant to the task at hand; @fusaroli2012coming]. Shared
+movement is associated with greater group bonding and greater willingness
+to contribute to the group [@wiltermuth2009synchrony], and shared identity 
+is associated with a greater willingness to adopt the group's goals and
+motivations [@walton2012mere].
+
+We should expect to see increased linguistic cohesion among people participating
+in online discussions about an idea, event, individual, or movement. Given that
+Syrian protesters are known to have coordinated their activity through Twitter
+by discussing their own events (e.g., planned protests, active demonstrations)
+and their reactions to events happening around them (e.g., government reactions,
+international action or inaction), the cohesion in social media should be
+expected to correlate with the social cohesion of the group [@zeitzoff2011using].
+
+This social cohesion can have real and wide-ranging impacts on a political
+movement and the people in it. A socially cohesive group is inherently more
+threatening to the existing regime because it reflects collective opposition
+momentum and the professionalization of potential alternate leadership. Groups
+with high social cohesion are more difficult to divide and conquer, and more
+cohesive messages may also garner increased international support. Global
+insurgency movements exhibit similar patterns in their social structure
+[@bohorquez2009common]. Each violent group has a stable state. Exogenous events
+can create perturbations that push the group to become either more cohesive or
+more fragmented. Rather than frenetic, patchwork messages via Twitter, emergent
+or intentional cohesive online messaging---using similar language, paralleling
+in-person messaging [@Windsor2020]---are a sign of increased organizational
+structure, inciting a government response.
+
+Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
+and political cohesion. Shared language in an online environment may lead to the
+development or expression of a shared identity [@wiltermuth2009synchrony]. This,
+in turn, may drive individuals’ propensity to engage in similar coordinated
+behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
+Taken together, these two processes may grow movement participants' weak and
+strong ties [@granovetter1977strength; @gladwell2010revolution;
+@mcadam1986recruitment], strengthening the movement overall by expanding and
+deepening heterogenous ties. Therefore, 
+in the context of social conflict, the linguistic cohesion
+of the online conversation should correspond to the degree of
+social cohesion on the ground.
+
+Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
+between social media and social mobilization alongside event data. This
+groundbreaking work demonstrates that participants on the fringe of a social
+movement contribute substantially to the overall level of protest. In addition
+to providing new methods to this growing field of study, we build on this
+previous work by demonstrating how sociolinguistic cohesion evolves in
+response to negative and positive exogenous events.
+
+Political and social cohesion in the world can be modeled using event data which
 encodes who does what to whom on a given day. This could include events such as
-the government (GOV) imposing a blockade or fighting with artillery or tanks on
-a civilian group (CIV). CAMEO (Conflict and Mediation Event Observations) encode
+the government imposing a blockade or fighting with artillery or tanks on
+a civilian group. CAMEO (Conflict and Mediation Event Observations) encode
 a set of activities with numerical values, rescaled to reflect a
-conflict-cooperation scale [@Schrodt_Hall_2006; @Goldstein_1992]. These event
+conflict-cooperation scale [@schrodt2006twenty; @goldstein1992conflict]. These event
 codes include a range of behaviors, from making public statements and appeals,
 to demanding, threatening, protesting, and using unconventional mass violence.
-Steinert-Threlkeld (2017) modeled a similar relationship between social media
-and social mobilization using a Gini coefficient measure, rather than a tf-idf
-(term frequency-inverse document frequency) measure alongside event data
-[@Ramos_2003; @Threlkeld_2017]. This pathbreaking work demonstrates that
-participants on the fringe of a social movement contribute substantially to the
-overall level of protest. We add to this discussion by demonstrating how
-sociolinguistic cohesion evolves in response to negative and positive exogenous
-events.
-
-### Cohesion in Social Movements and Civil Wars
+
+#### Cohesion in Social Movements and Civil Wars
 People join social and political resistance movements because they feel a sense

### 2020-06-01 manuscript.Rmd
Minor tweaks to intro
Small tweak to wcrqa source-target filtering results

@@
 
-For social cohesion and negative events, there was an extended period of time
-during which RR (32nd--47th windows) and DET (35th--39th windows) were above or
-nearly above chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These
-windows span from May 3rd--14th, 2012.
+For social cohesion and negative events, there was an extended, overlapping
+period of time during which RR (32nd--47th windows) and DET (35th--39th windows)
+were above or nearly above chance (Figure
+\@ref(fig:plot-wcrqa-source-targ-all)). These windows span from May 3rd--14th,
+2012.
 

### 2020-06-01 manuscript.Rmd
Add page number

@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts. [anderson2011demystifying]
+local contexts. [@anderson2011demystifying]
 
@@
 
-The concept of lexical, or semantic, cohesion has already been applied to the
-analysis of political speech (for example, the language of Margaret Thatcher) 
-and non-political speech [@barzilay1999using; @morris1991lexical].
-
-The words that comprise social media posts are the first level at which cohesion
-occurs. In Figure \@ref(fig:cohesion-in-tweets), we see four sequential tweets, 
-each containing four words.
+The words that comprise social media posts are the first level of cohesion that
+we will consider. The concept of lexical, or semantic, cohesion has already been
+applied to the analysis of political speech (for example, the language of
+Margaret Thatcher) and non-political speech [@barzilay1999using;
+@morris1991lexical]. In Figure \@ref(fig:cohesion-in-tweets), we see four
+sequential tweets, each containing four words.
 Each sequential tweet contains some content included in the previous tweets. The
@@
 mobilization, which facilitate the development of protest movements in some
-instances and constrain them in others [@Kitschelt_1986].” What emerges as
-strategies and tactics in contentious politics is in essence, a function of what
-the system makes possible. This includes the number of people and their
+instances and constrain them in others” [@Kitschelt_1986, p. 58]. What emerges
+as strategies and tactics in contentious politics is in essence, a function of
+what the system makes possible. This includes the number of people and their
 disposition, i.e. nonviolent or violent, as well as their internal structure.

### 2020-06-01 manuscript.Rmd
Edit and shift Social Movements and Civil Wars section

--- 2020-06-01 manuscript.Rmd
@@
 
+## The Role of Cohesion in Social Movements and Civil Wars
+
+People join social and political resistance movements because they feel a sense
+of connection to the cause and because they have been sufficiently convinced to
+participate. Given that people are generally risk-averse, overcoming inertia
+requires a strong connection to the group identity or a strong aversion to an individual,
+event, or political injustice [@goldstone1980theories; @goldstone2011understanding]. 
+Political resistance offers participants the opportunity to “lose themselves” and
+relinquish their individual identity in favor of identification with a larger
+group identity, contributing to a cohesive group ready and mobilized for
+action [@Hoffer2011true].
+
+Previous research on social movements supports the idea that participants are
+likely to join movements when they know and have a personal connection to
+someone else already involved [@mcadam1986recruitment]. The type of collective
+contentious behavior that manifests in society is a function of the available
+political opportunity structures. The political opportunity structure are
+“comprised *(sic)* of specific configuration of resources, institutional
+arrangements and historical precedents for social mobilization, which facilitate
+the development of protest movements in some instances and constrain them in
+others” [@Kitschelt_1986]. What emerges as strategies and tactics in contentious
+politics are, in essence, a function of what the system makes possible. This
+includes the number of people and their disposition (i.e. nonviolent or
+violent), as well as their internal structure. The more cohesive a group is, the
+greater threat they pose to the establishment.
+
+Cohesion is also a familiar concept in the study of civil conflicts, as it
+pertains to group affiliation and the ability to overcome collective action
+problems. Individuals must act in concert---that is, cohesively---to
+accomplish the task of challenging the authority of the state [@olson1965logic;
+@eisinger1973conditions; @tilly2004contentious; @francisco1995relationship].
+Recent work has considered rebel recruitment for participation in
+civil conflicts as a function of internal cohesion [@gates2002recruitment]:
+Rebel movement success is influenced by the degree of group cohesion, which
+itself is a function of geographic distance, ideology, and ethnicity.
+Within Syria, multiple rebel groups within Syria exist, sourcing fighters locally
+from the disaffected Syrian population and internationally through
+fighters from transnational terrorist organizations. There is considerable 
+intergroup competition for participation in the rebel movement and
+punishment for defectors for nonparticipation [@gates2002recruitment].
+Foreign fighters would appear to be amply motivated to fight, given their
+decision to relocate from a home country that may be located in the region
+or much farther away.
+
+Another factor influencing social cohesion during social movements and
+civil wars is ethnic identity and the degree of ethnic conflict associated with
+the movement. Greater degrees of ethnic conflict increase the salience of
+ethnic identity, leading people to identify more strongly with their own
+ethnic identity [@sambanis2009s]. As ethnic conflict
+intensifies, groups seek to become more quintessentially like the typical
+member of their ethnic group. This can manifest in a number of ways, including
+in behavior on social media. However, this may also include a general identification
+across ethnic groups in a membership of an opposition to an oppressive leader.
+
+The civil war literature has further explored the role of social cohesion in
+detail. Social homogeneity increases the likelihood of social conflict,
+especially when the society is polarized [@collier2004greed]; this is partly
+due to nationalist groups' strong identification with a collective identity
+[@cederman2007beyond] and their social solidarity [@sambanis2009s]. These
+same processes can be similarly important for rebels [@anyanwu2002economic].
+Referencing Gurr’s [-@gurr2000peoples] work on minorities at
+risk, Regan and Norton [-@regan2005greed] note that
+
+>a religious or linguistic minority
+might suffer disproportionately in a given society, and this form of
+aggrievement can lead to unrest across the social lines that distinguish the
+minority group. Therefore, while collective cohesion is a function of targeted
+maldistributions, it is individual penury that allows for this collective
+mobilization. [@regan2005greed]
+
+The body of previous work concurs that group cohesion matters to group
+mobilization. We build on this by providing a quantitative approach to
+understanding cohesion from multiple levels and by incorporating analytic tools
+that allow us to investigate the interconnectedness of those levels.
+
 ## Cohesion: A Multi-Leveled, Multi-Layered Concept
@@
 
-#### Cohesion in Social Movements and Civil Wars
-People join social and political resistance movements because they feel a sense
-of connection to the cause, and because they have been sufficiently convinced to
-participate. Given that people are generally risk averse, overcoming inertia
-requires a strong connection to the group identity, or against an individual,
-event, or political injustice [@Goldstone_1980; Goldstone_2011]. Political
-resistance offers participants the opportunity to “lose themselves” and
-relinquish their individual identity in favor of identification with a larger
-group identity, thus contributing to a cohesive group ready and mobilized for
-action [@Hoffer_2011. Previous research on social movements supports the idea
-that participants are likely to join movements when they know and have a
-personal connection to someone else already involved [@McAdam_1986. The type of
-collective contentious behavior that manifests in society is a function of the
-available political opportunity structures. The political opportunity structure,
-as defined by Kitschelt (1986) are “comprised of specific configuration of
-resources, institutional arrangements and historical precedents for social
-mobilization, which facilitate the development of protest movements in some
-instances and constrain them in others [@Kitschelt_1986].” What emerges as
-strategies and tactics in contentious politics is in essence, a function of what
-the system makes possible. This includes the number of people and their
-disposition, i.e. nonviolent or violent, as well as their internal structure.
-The more cohesive a group is, the greater threat they pose to the establishment.
-
-Cohesion is also a familiar concept in the study of civil conflicts as it
-pertains to group affiliation and the ability to overcome collective action
-problems. Olson’s (Olson, 1965) seminal work on collective action informs the
-theory of group behavior. Individuals must act in concert – cohesively – to
-accomplish the task of challenging the authority of the state. Building on
-Eisinger’s (1973) analysis of social protest movements [@Eisinger_1973, McAdam,
-Tilly and Tarrow [@Tilly_2004, and Francisco [@Francisco_1995 have provided
-foundational work on the dynamics of social movements and contentious behavior.
-More recently, Gates (2002) considers rebel recruitment for participation in
-civil conflicts as a function of internal cohesion [@Gates_2002]. He notes that
-rebel movement success is influenced by the degree of group cohesion, which
-itself is a function of geographic distance, ideology and ethnicity.
-
-There are multiple rebel groups within Syria, some with fighters sourced locally
-from the disaffected Syrian population, and an increasing number of foreign
-fighters from transnational terrorist organizations. Gates’ work helps us
-understand the intergroup competition for participation in the rebel movement,
-as well as the groups’ abilities to punish defectors for nonparticipation.
-Foreign fighters would appear to be amply motivated to fight, given their
-decision to relocate from their home country which is sometimes in the region
-but other times requires them to travel large distances.
-
-Similarly, Sambanis and Shayo (2013) find in their model that “intense ethnic
-conflict makes people care more about their ethnic group relative to other
-groups, and seek to resemble it more [@Sambanis_Shayo_2013].” As ethnic conflict
-intensifies, groups seeking to become more quintessentially like the typical
-member of their ethnic group, this should be manifested in their language on
-social media. Social medial should reflect this delineation amongst ethnic
-groups and between them. However, this may also include a general identification
-across ethnic groups in a membership of an opposition to an oppressive leader.
-
-It is this general identification with the larger opposition movement, not the
-individual identity groups within Syria, which we seek to understand in this
-paper. It is implausible to expect there to be one cohesive narrative from the
-multiple groups with disparate incentives. However, they do have important
-similarities, namely, they are all interested in opposing the current Syrian
-regime using largely violent means, although there are notable and regular
-instances of nonviolent protests on Fridays, following prayer services. Thus,
-what we are able to capture in this study is the degree to which all opposition
-movements to the Syrian government have a similar content and tone, with a
-similar ebb and flow. It should be increasingly threatening to the regime if the
-rebel movement across the disparate groups is growing stronger and more unified,
-represented by similar language used across groups.
-
-The civil war literature has further explored the role of social cohesion in
-detail. Collier and Hoeffler identified the role of social homogeneity as having
-an increased likelihood on social conflict, especially when the society is
-polarized [@Collier_Hoeffler_2004]. Cederman and Girardin  write that, “In
-general, nationalist groups derive their cohesion from collective-level
-identities that resonate deeply with the emotional needs of modern citizens.”
-Sambanis and Schulhofer-Wohl note that “group cohesion and solidarity (underlie)
-the offensive advantage (Sambanis & Schulhofer-Wohl, 2009).” Anyanwu (2002)
-writes, “Another source of rebel military opportunity is social cohesion…an
-ethnically diverse society may reduce the opportunity for rebellion by limiting
-the recruitment pool [@Anyanwu_2002].” Referencing Gurr’s work on minorities at
-risk, Regan and Norton (2005) note that “a religious or linguistic minority
-might suffer disproportionately in a given society, and this form of
-aggrievement can lead to unrest across the social lines that distinguish the
-minority group. Therefore, while collective cohesion is a function of targeted
-maldistributions, it is individual penury that allows for this collective
-mobilization [@Gurr_2000; @Regan_Norton_2005].” Thus scholarship concurs that
-group cohesion matters to group mobilization; we add to this concept by
-introducing the role of language in facilitating cohesion.
-
-## Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
-We tie the constructs of lexical, interlocutor, and social/physical cohesion
+### Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
+We tie the constructs of lexical, interlocutor, and social cohesion
 together in a theoretical framework called sociolinguistic cohesion, as shown in

### 2020-06-01 manuscript.Rmd
Finish editing Cohesion section

@@
 ## Social Media and Social Movements
+
+Massive online social cohesion can have real-world social
+manifestations. Social media platforms provide one way to enable this kind of
+online social cohesion by offering distributed information-gathering and
+real-time information dissemination. Given its accessibility and proficiency as
+an information exchange tool, Twitter has provided individuals involved in
+social movements an opportunity to complement or even replace real-world social
+mobilization. For example, during the 2012 Italian protests for global economic
+change, the riots in Rome were mirrored by Twitter activity both on the day of
+the protests and in the days following them [@vicari2013public]. Tweeting was
+determined to be more effective locally in discussing real-world, real-time
+events than traditional mainstream media platforms. As more and more individuals
+rely on social media to obtain local news and information, it becomes
+increasingly important to understand just how these micro-blogs reflect
+real-world action.
+
 During the Arab Spring, social media provided real-time information about the
@@
 
+Just as real-world social cohesion can be quantified, so can online cohesion.
+One kind of cohesion can be found in
+the similarity in language use on social media. This implicit or explicit
+similarity in language use can indicate shared beliefs, thoughts, and feelings,
+as has been studied in research on language style in psycholinguistics and
+social psychology [@gonzales2010language; @tausczik2010psychological;
+@brennan1996conceptual]. Although previous work on language style has often
+focused on individuals and small groups, this can be scaled up to examine
+massive social-level changes [@michel2011quantitative; @fusaroli2015timescales].
+
 The words that comprise social media posts are the first level of cohesion that
-we will consider. The concept of lexical, or semantic, cohesion has already been
-applied to the analysis of political speech (for example, the language of
-Margaret Thatcher) and non-political speech [@barzilay1999using;
-@morris1991lexical]. In Figure \@ref(fig:cohesion-in-tweets), we see four
+we will consider.  In Figure \@ref(fig:cohesion-in-tweets), we see four
 sequential tweets, each containing four words.
@@
 
-### Sociolinguistic cohesion: Connectedness of speakers, events, and ideas
-We tie the constructs of lexical, interlocutor, and social cohesion
-together in a theoretical framework called sociolinguistic cohesion, as shown in
-Figure \@ref(fig:theoretical-framework). We can measure the changes in cohesion
-preceding and in response to external stimuli by evaluating the messages and the
-context in which they occur. Several mechanisms are in motion here. Previous
-values of linguistic cohesion should influence future values of linguistic
-cohesion. They should also influence future actions in the real world space.
-Previous events influence future events, and also the future cohesiveness of the
-opposition.
+### Sociolinguistic Cohesion: Connectedness of Speakers, Ideas, and Events
+We tie the constructs of lexical, interlocutor, and social cohesion together in
+a theoretical framework called *sociolinguistic cohesion*, as shown in Figure
+\@ref(fig:theoretical-framework). Several interconnected mechanisms are in
+motion here. Previous values of linguistic cohesion should influence future
+values of linguistic cohesion and future actions in the real world space.
+Previous events influence future events and future linguistic cohesion in
+social media.
 
 Sociolinguistic cohesion is not a static concept. Just as social movements
-experience increased participation as well as setbacks – indicating dynamic
-relationships between participants, and participants and the sociopolitical
-environment – sociolinguistic cohesion is also dynamic, reflecting the changing
+experience increased participation and setbacks---indicating dynamic
+relationships among participants and between participants and the sociopolitical
+environment---sociolinguistic cohesion is also dynamic, reflecting the changing
 states of the political sphere. Other scholars have noted the diffusion of
 messages whereby they reach a critical mass, whereby “behaviors, beliefs, and
-preferences” spread within a population [@Barash_Cameron_Macy_2012].  Cohesion
+preferences” spread within a population [@barash2012critical].  Cohesion
 changes over time in response to external events and the internal dynamics of
-the social movement. Some may wonder whether social cohesion can diffuse among
-distant actors who do not interact face-to-face; Centola and Macy show that
-Internet weak ties extend over long distances and as such have spatially
-significant abilities to influence actors [@Centola_Macy_2007]. Fink et al. also
-explored diffusion of hashtags in viral contagion in Nigeria, a phenomenon
-similar to what we identify as sociolinguistic cohesion
-[@Fink_Schmidt_Barash_Cameron_Macy_2016]. The prevalence and rate of particular
-hashtags contribute to the overall sociolinguistic cohesion. he more that people
+the social movement. This can occur even if the social interaction occurs entirely 
+online [@centola2007complex].
+
+Related previous work has also explored diffusion of hashtags in viral contagion in
+Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
+[@fink2016complex]. The prevalence and rate of particular hashtags were
+contributed to the overall sociolinguistic cohesion. The more that people
 reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
 this phenomenon occurs during socially significant times like protests
-[@Adamic_others_2015]. Exogenous events, like intervention by another country or
-international organization like the United Nations, can affect sociolinguistic
-cohesion. Endogenous events, like the recruitment of new members to the rebel or
-resistance movement, can also affect the level of cohesion.
+[@state2015diffusion].
 
@@
 cohesion would be driven by real-world action, we would expect interaction
-between real-world and virtual dynamics: In this case, exposure to real-world
+between real-world and online dynamics: In this case, exposure to real-world
 violence could result in social cohesion in the virtual world. Increased social
 cohesion is thus potentially an indicator and a result of increased social
-organization and mobilization on the ground.
-
-Exploring how social media influences contentious behavior, Tilly notes that
-social media lowers coordination and transaction costs for participants, and
-that older versions of organizing social movements have become less effective,
-yielding to the new frontier of online organizing [@McAdam_Tarrow_Tilly_2003].
-Koopmans extends this further, writing that, “Authorities react to social
-movement activities if and as they are depicted in the mass media, and
-conversely movement activists become aware of political opportunities and
-constraints through the reactions (or non-reactions) that their actions provoke
-in the public sphere” [@Koopmans_2004].
-
-Lexical cohesion, then, should be a useful indicator of social cohesion in
+organization and mobilization on the ground. However, this occurs within a context
+that is affected by local and international events; both
+exogenous events (like intervention by another country or
+international organization like the United Nations) and 
+endogenous events (like the recruitment of new members to the rebel or
+resistance movement) can affect cohesion.
+
+From a dynamical systems perspective, online social cohesion and
+in-person action can be considered two complementary
+components of a single system, mutually constrained and constantly interacting
+and influencing one another [@mahner1997foundations]. Investigation of the
+coupling of real-world mobilization and social cohesion could provide new
+insight into the power of social media during mobilization and the ways in which
+individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social
+mobilization [@mcadam2003dynamics; @koopmans2004movements], 
+but the relationship between virtual and real-world mobilization
+is still largely unknown. The present work aims to understand how physical and
+virtual movements coexist and interact from a dynamical systems perspective.
+
+Lexical cohesion, then, is be a useful indicator of social cohesion in
 political crisis. Lexical cohesion happens at the word level. Interlocutor
@@
 action problem to mount sustained resistance to state authority.
-
-Social coordination has long been used both physically and virtually to start
-and carry out collective actions. These collective events bring individuals
-together and create emergent patterns of communication and action. Online
-communication has historically been used to document and communicate archival
-information about events, but it has been increasingly used to bring about
-social change. From a dynamical systems perspective, these different means of
-social coordination during times of turmoil can be considered two complementary
-components of a single system, mutually constrained and constantly interacting
-and influencing one another [@mahner1997foundations]. Investigation of the
-coupling of real-world mobilization and social cohesion could provide new
-insight into the power of social media during mobilization and the ways in which
-individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social
-mobilization, but the relationship between virtual and real-world mobilization
-is still largely unknown. The present work aims to understand how physical and
-virtual movements coexist and interact from a dynamical systems perspective.
-
-Just as real-world social cohesion can be quantified, so can online cohesion.
-While this can be quantified in many ways, one kind of cohesion can be found in
-the similarity in language use on social media. This implicit or explicit
-similarity in language use can indicate shared beliefs, thoughts, and feelings,
-as has been studied in research on language style in psycholinguistics and
-social psychology [@gonzales2010language; @tausczik2010psychological;
-@brennan1996conceptual]; although previous work on language style has often
-focused on individuals and small groups, this can be scaled up to examine
-massive social-level changes [@michel2011quantitative; @fusaroli2015timescales].
-This kind of widespread online social cohesion can lead to real-world social
-change.
-
-This kind of massive online social cohesion can lead to real-world social
-manifestations. Social media platforms provide one way to enable this kind of
-online social cohesion by offering distributed information-gathering and
-real-time information dissemination. Given its accessibility and proficiency as
-an information exchange tool, Twitter has provided individuals involved in
-social movements an opportunity to complement or even replace real-world social
-mobilization. For example, during the 2012 Italian protests for global economic
-change, the riots in Rome were mirrored by Twitter activity both on the day of
-the protests and in the days following them [@vicari2013public]. Tweeting was
-determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more individuals
-rely on social media to obtain local news and information, it becomes
-increasingly important to understand just how these micro-blogs reflect
-real-world action.
 

### 2020-06-01 manuscript.Rmd
Minor edits

@@
 were powerful tools in the events of the Arab Spring and are undeniably linked.
-This study aims to explore the dynamics of Syrian Twitter users, who used the
+This study aims to explore the dynamics of Twitter users in Syria, who used the
 social media platform to raise awareness about the Arab Spring and bring about

### 2020-06-01 manuscript.tex
Bring .tex current

--- 2020-06-01 manuscript.tex
@@
 found in Syrian tweets. Results indicate that virtual social cohesion is
-coupled with the counts of all and negative events each day but not with
-counts of positive events. This suggests that virtual mobilization does reflect
-real-world movements but only for salient, frequent and negative events. We
+coupled with the counts of all and negative events each day but shows a more
+nuanced connection to positive events, only visible when examining finer-grained
+data. This suggests that virtual mobilization does reflect
+real-world movements, with the strongest connections to the frequency of all
+events and the frequency of negative events. We
 conclude with a discussion of implications and applications of nonlinear
@@
 
-Social coordination has long been used both physically and virtually
-to start and carry out collective actions. These collective events
-bring individuals together and create emergent patterns of communication
-and action. Online communication has historically been used to document
-and communicate archival information about events, but it has been
-increasingly used to bring about social change. From a dynamical
-systems perspective, these different means of social coordination during
-times of turmoil can be considered two complementary components of a
-single system, mutually constrained and constantly interacting and
-influencing one another (Mahner \& Bunge, 1997). Investigation of the
-coupling of real-world mobilization and social cohesion could provide
-new insight into the power of social media during mobilization and the
-ways in which individuals utilize it to bring about, or respond to, social
-change. Increasingly, social media platforms are being utilized during
-social mobilization, but the relationship between virtual and real-world
-mobilization is still largely unknown. The present work aims to understand
-how physical and virtual movements coexist and interact from a dynamical
-systems perspective.
-
-\hypertarget{arab-spring}{%
-\subsection{Arab Spring}\label{arab-spring}}
+Prior to the advent of social media, people coordinated their protest behavior
+using phone tree calling sheets and mimeographed flyers,
+through in-person meetings of social organizations and churches, and through
+word of mouth. They gathered together and hand-made protest signs that reflected
+their agendas. As McAdam found, people were more likely to join movements when
+they had a personal connection (McAdam, 1986; McAdam \& Paulsen, 1993):
+Historically, strong ties have been
+strong predictors of involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements in the pre-Internet era could be
+operationalized by the number of people turning out to protest and through the
+political events that precipitated and resulted from social gatherings \emph{en masse}.
+The content of placards and protest
+signs provided the protest narrative in their own words. Cohesive
+social movements were reflected in their cohesive placards and posters. For
+example, the \enquote{I am a man} posters held by the men involved in the 1968
+sanitation workers' strike reflected their internal cohesion and unified,
+goal-oriented movement (Windsor, 2020).
+
+However, the rise of the Internet and its decentralized online networks
+has upended theories about recruitment to---and participation in---social
+movements. Strong interpersonal ties have yielded to weak impersonal ties that
+strongly predict involvement in social movements (Steinert-Threlkeld, 2017). Research
+methodologies for measuring social movements have similarly evolved from
+ethnographic interviews to \enquote{big data} analyses of language on social media.
+
+Today, social media replicates and amplifies
+this phenomenon during moments of social unrest. Amid the cacophony of messages
+during political upheaval---such as the Arab Spring---consistent themes emerge
+through hashtags, retweets, and the repeated mentions of concepts such as
+regime, security, demonstration, and human rights. The cohesiveness of these
+themes (i.e., whether movement participants are metaphorically singing in one voice)
+reflects the real-world events happening contemporaneously with collective action in
+social movements or civil conflicts.
+
+In the present research, we investigate the relationship between linguistic
+cohesion and social cohesion in times of social conflict and unrest. We tackle a
+question related to the one posed by Zeitzoff (2017): How does
+social media reflect on-the-ground realities during times of social conflict?
+To do so, we examine patterns of linguistic cohesion on Twitter and their
+connection to real-world events during
+the Arab Spring uprising in Syria between March and June 2012.
+
+Disentangling the complicated relationship between mass online mobilization---and
+social mobilization in person---continues to be relevant, even as our modes
+of communication change. The
+political processes that transpired during and after the Arab Spring are still
+in the process of being understood. As Zeitzoff (2017) recognizes,
+social media is changing conflict, but the mechanisms and relationships by
+which it does so are still being understood.
+
+\hypertarget{syria-in-context}{%
+\subsection{Syria in Context}\label{syria-in-context}}
+
+The decades preceding the Arab Spring in Syria were marked by
+social repression and fear. In 1971, Hafez al-Assad overthrew the previous
+leader and remained in power for thirty years, presiding during
+regional contentiousness and cooperation until his death in 2000. His son,
+Bashar al-Assad continued the regime of authoritarian leadership as he assumed
+his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
+in a multi-religious and multi-ethnic country comprising Christians, Sunni and
+Shia Muslims, Kurds, and Palestinian refugees.
 
@@
 unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian
-rule, ultimately leading to his death several days later. His actions served
-as a catalyst for the Tunisian Revolution, and one week after his death,
-Zine El Abidine Ben Ali---the longstanding authoritarian president---fled the
-country. The events of Tunisia rapidly spread to surrounding countries
-also subject to unjust authoritarian rule, including Yemen, Egypt, Libya,
-and Syria.
-
-These mass movements would not have been possible without
-efficient large-scale coordination, both physically on the ground and virtually
-on social media platforms. Along with Facebook, Twitter has been credited as
-essential to the Arab Spring---both for protesters (as a means to coordinate
-with one another and to communicate with the world) and for the government
-response (to monitor and track protestors to crack down on dissent)
-(Comninos, 2011). The events of Arab Spring have been thoroughly
-discussed within the political science literature
-(e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge,
-the direct \emph{coupling} between Syrian Twitter cohesion and international action
-coordination has not been investigated.
-
-\hypertarget{social-cohesion-and-social-mobilization}{%
-\subsection{Social Cohesion and Social Mobilization}\label{social-cohesion-and-social-mobilization}}
+humiliation led him to set himself on fire in protest to the authoritarian rule,
+ultimately leading to his death several days later. His actions served as a
+catalyst for the Tunisian Revolution, and one week after his death, Zine El
+Abidine Ben Ali---the longstanding authoritarian president---fled the country.
+The events of Tunisia rapidly spread to surrounding countries also subject to
+unjust authoritarian rule, including Yemen, Egypt, Libya, and Syria.
+
+Following a wave of democratization efforts across the Middle East and North
+Africa, modest Syrian protests began in March 2011. The regime responded
+harshly with imprisonments, detentions, censorship, and military operations as
+the resistance to Assad's regime grew and spread throughout the country. The
+fighting escalated dramatically in March 2012, after increased unrest in the
+western city of Homs. International actors---including the Red Cross/Red Crescent
+Society, the United Nations General Assembly, the Security Council, and
+individual world leaders---worked toward cease-fires, negotiations,
+and concessions without much success. While many high-level military and
+diplomatic officials defected from the regime, numerous loyal forces
+continued the regime's repression, and the Syrian people turned to social
+media to help coordinate their activism and communicate to the world. Between March and
+June 2012, more than 8 million tweets were sent within Syria, revealing the
+details of the conflict suppressed by the government.
+
+Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
+people make up between 10-15\% of the population, Alawites between 8-15\%,
+Christians about 10\%. There are also much smaller sects (e.g., Ismailis,
+Druze), but Sunni Muslims comprise the vast majority of society. Most people
+speak Arabic as their primary language. Most policy reports addressing the current
+conflict report on the cohesion of the ruling Alawite military elite, rather
+than on the cohesiveness of the opposition movement. However, the Sunni
+majority's disaffection with the Syrian government and their lack of political
+representation provide sufficient grievance and collective group identification
+to make them a cohesive force.
+
+\hypertarget{social-media-and-social-movements}{%
+\subsection{Social Media and Social Movements}\label{social-media-and-social-movements}}
+
+Massive online social cohesion can have real-world social
+manifestations. Social media platforms provide one way to enable this kind of
+online social cohesion by offering distributed information-gathering and
+real-time information dissemination. Given its accessibility and proficiency as
+an information exchange tool, Twitter has provided individuals involved in
+social movements an opportunity to complement or even replace real-world social
+mobilization. For example, during the 2012 Italian protests for global economic
+change, the riots in Rome were mirrored by Twitter activity both on the day of
+the protests and in the days following them (Vicari, 2013). Tweeting was
+determined to be more effective locally in discussing real-world, real-time
+events than traditional mainstream media platforms. As more and more individuals
+rely on social media to obtain local news and information, it becomes
+increasingly important to understand just how these micro-blogs reflect
+real-world action.
+
+During the Arab Spring, social media provided real-time information about the
+events transpiring in countries across the Middle East and North Africa. Our
+understanding about the role of social media in social movements is still
+evolving. Some argue that these mass movements would not have been possible
+without efficient large-scale coordination, both physically on the ground and
+virtually on social media platforms.
+
+Along with Facebook, Twitter has been
+credited as essential to the Arab Spring---both for protesters (as a means to
+coordinate with one another and to communicate with the world) and for the
+government response (to monitor and track protestors to crack down on dissent)
+(Comninos, 2011). The events of Arab Spring have been thoroughly discussed
+within the political science literature (e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge, the direct \emph{coupling} between
+Syrian Twitter cohesion and international action coordination has not been
+investigated. In fact, some have been skeptical about the effect of social media on
+collective action at all (Seay, 2014).
+
+This skepticism can be summarized in a quote by Lisa Anderson:
+
+\begin{quote}
+The important story about the 2011
+Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
+norms of civic engagement shaped the protesters' aspirations. Nor is it about
+how activists used technology to share ideas and tactics. Instead, the critical
+issue is how and why these ambitions and techniques resonated in their various
+local contexts. (Anderson, 2011)
+\end{quote}
+
+Others have similarly expressed hesitation about the role of online
+organizing. Some have argued that real-life strong ties outweigh online weak ties and
+that the power of the strong ties through in-person contact is critical
+to recruiting people for higher-risk activities
+(Gladwell, 2010; McAdam, 1986).
+
+Interestingly, these views may
+actually help to make the case for bridging the gap between social media and
+social mobilization. Such views suggest the strength of social ties in an online
+environment is inextricably linked to the \emph{context} and \emph{ambitions} of the actors.
+Moreover, research suggests that weak ties still retain considerable political
+power: While strong ties tend to bind smaller groups, weak ties
+tend to bind groups across distances (Granovetter, 1973).
+
+Social media generates critical information about events, including whether and how
+a demonstration will take place, how many
+people participate, and how those in power (e.g., state, military, security apparatus)
+respond. Similarly, these media platforms alert us to more global shifts within
+a conflict, such as when fighting moves to a new city or region, the number of
+casualties and wounded, and the types of weaponry used by parties to the
+conflict (Zeitzoff, 2017). Social media is not entirely event-driven, however.
+In monitoring social media channels, government forces may respond to the
+perception that citizens are gaining strength and sympathy. Governments have
+been shown to be quite tolerant of dissent so long as it does not metamorphose
+into collective action (King, Pan, \& Roberts, 2013).
+
+Citizens communicate with each other with increased transparency due to the
+ubiquitous availability of social media such as low-cost and egalitarian
+platforms like Twitter. Citizens are able to access these tools via mobile
+phones and computers with Internet connectivity, providing a stream of real-time
+shared information. Citizens can share the location of events like protests and military
+incursions, the degree of state repression, and the number of casualties. In
+turn, the government---interested in remaining in power---monitors social media
+platforms to ascertain emerging threats (Comninos, 2011),
+such as where new groups are forming
+and where existing groups are strengthening, where gatherings are held, and who
+the idea entrepreneurs are. An example of a leader
+expressing his interest in
+such public conversation is given by Bashar al-Assad in a speech on June 3, 2012:
+
+\begin{quote}
+I know that I have been away from the media for a long time, and I have missed
+having direct contact with the citizens, but I have always been following up
+with the daily occurrences and gathering the information so that my speech can
+be built on what is said by the street.
+\end{quote}
+
+With few exceptions, Assad chose to keep social media platforms up and running.
+Gohdes (2015) notes that regimes can attempt to thwart the growth of social
+protest online and in the streets by shutting down the Internet.
+During these times, however, she finds that military repression increases.
+However, government information about the citizens decreases; as such, many
+regimes have elected to maintain Internet connectivity as a means of monitoring
+and surveilling their citizens.
+
+At the same time, the insulation
+of online social platforms allows researchers to detail real-world social dynamics
+at unprecedented resolution and scale (Paxton \& Griffiths, 2017). The digital traces left by
+individuals and collectively as groups are regarded as a valuable source of
+information that can offer powerful insights into states of social
+disequilibrium, uprisings, and escalations into civil wars.
+By examining these conversations, researchers can study the degree of cohesion between
+speakers and the alignment between that cohesion and their collective political
+behavior.
+
+\hypertarget{the-role-of-cohesion-in-social-movements-and-civil-wars}{%
+\subsection{The Role of Cohesion in Social Movements and Civil Wars}\label{the-role-of-cohesion-in-social-movements-and-civil-wars}}
+
+People join social and political resistance movements because they feel a sense
+of connection to the cause and because they have been sufficiently convinced to
+participate. Given that people are generally risk-averse, overcoming inertia
+requires a strong connection to the group identity or a strong aversion to an individual,
+event, or political injustice (Goldstone, 1980, 2011).
+Political resistance offers participants the opportunity to \enquote{lose themselves} and
+relinquish their individual identity in favor of identification with a larger
+group identity, contributing to a cohesive group ready and mobilized for
+action (Hoffer, 2011).
+
+Previous research on social movements supports the idea that participants are
+likely to join movements when they know and have a personal connection to
+someone else already involved (McAdam, 1986). The type of collective
+contentious behavior that manifests in society is a function of the available
+political opportunity structures. The political opportunity structure are
+\enquote{comprised \emph{(sic)} of specific configuration of resources, institutional
+arrangements and historical precedents for social mobilization, which facilitate
+the development of protest movements in some instances and constrain them in
+others} ({\textbf{???}}). What emerges as strategies and tactics in contentious
+politics are, in essence, a function of what the system makes possible. This
+includes the number of people and their disposition (i.e.~nonviolent or
+violent), as well as their internal structure. The more cohesive a group is, the
+greater threat they pose to the establishment.
+
+Cohesion is also a familiar concept in the study of civil conflicts, as it
+pertains to group affiliation and the ability to overcome collective action
+problems. Individuals must act in concert---that is, cohesively---to
+accomplish the task of challenging the authority of the state (Eisinger, 1973; Francisco, 1995; Olson, 1965; Tilly, 2004).
+Recent work has considered rebel recruitment for participation in
+civil conflicts as a function of internal cohesion (Gates, 2002):
+Rebel movement success is influenced by the degree of group cohesion, which
+itself is a function of geographic distance, ideology, and ethnicity.
+Within Syria, multiple rebel groups within Syria exist, sourcing fighters locally
+from the disaffected Syrian population and internationally through
+fighters from transnational terrorist organizations. There is considerable
+intergroup competition for participation in the rebel movement and
+punishment for defectors for nonparticipation (Gates, 2002).
+Foreign fighters would appear to be amply motivated to fight, given their
+decision to relocate from a home country that may be located in the region
+or much farther away.
+
+Another factor influencing social cohesion during social movements and
+civil wars is ethnic identity and the degree of ethnic conflict associated with
+the movement. Greater degrees of ethnic conflict increase the salience of
+ethnic identity, leading people to identify more strongly with their own
+ethnic identity (Sambanis \& Schulhofer-Wohl, 2009). As ethnic conflict
+intensifies, groups seek to become more quintessentially like the typical
+member of their ethnic group. This can manifest in a number of ways, including
+in behavior on social media. However, this may also include a general identification
+across ethnic groups in a membership of an opposition to an oppressive leader.
+
+The civil war literature has further explored the role of social cohesion in
+detail. Social homogeneity increases the likelihood of social conflict,
+especially when the society is polarized (Collier \& Hoeffler, 2004); this is partly
+due to nationalist groups' strong identification with a collective identity
+(Cederman \& Girardin, 2007) and their social solidarity (Sambanis \& Schulhofer-Wohl, 2009). These
+same processes can be similarly important for rebels (Anyanwu, 2002).
+Referencing Gurr's (2000) work on minorities at
+risk, Regan and Norton (2005) note that
+
+\begin{quote}
+a religious or linguistic minority
+might suffer disproportionately in a given society, and this form of
+aggrievement can lead to unrest across the social lines that distinguish the
+minority group. Therefore, while collective cohesion is a function of targeted
+maldistributions, it is individual penury that allows for this collective
+mobilization. (Regan \& Norton, 2005)
+\end{quote}
+
+The body of previous work concurs that group cohesion matters to group
+mobilization. We build on this by providing a quantitative approach to
+understanding cohesion from multiple levels and by incorporating analytic tools
+that allow us to investigate the interconnectedness of those levels.
+
+\hypertarget{cohesion-a-multi-leveled-multi-layered-concept}{%
+\subsection{Cohesion: A Multi-Leveled, Multi-Layered Concept}\label{cohesion-a-multi-leveled-multi-layered-concept}}
+
+We contextualize linguistic cohesion with social mobilization and response to the relative
+intensity of the conflict. Cohesion is a multi-layered concept referring to the
+connectedness of speakers, actions, and societies. Cohesion reflects the
+continuity of language and expression, and it shows the connectivity of
+participants in a social movement. To address the relationship between language
+and discourse and social movements, we adopt an interdisciplinary approach that
+incorporates linguistics, psychology, and political science using nonlinear
+dynamical systems methodology to model the relationship between language and
+action.
+
+\hypertarget{lexical-and-interlocutor-cohesion}{%
+\subsubsection{Lexical and Interlocutor Cohesion}\label{lexical-and-interlocutor-cohesion}}
+
+Just as real-world social cohesion can be quantified, so can online cohesion.
+One kind of cohesion can be found in
+the similarity in language use on social media. This implicit or explicit
+similarity in language use can indicate shared beliefs, thoughts, and feelings,
+as has been studied in research on language style in psycholinguistics and
+social psychology (Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010). Although previous work on language style has often
+focused on individuals and small groups, this can be scaled up to examine
+massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
+
+The words that comprise social media posts are the first level of cohesion that
+we will consider. In Figure \ref{fig:cohesion-in-tweets}, we see four
+sequential tweets, each containing four words.
+Each sequential tweet contains some content included in the previous tweets. The
+linguistic construct of content word overlap measures the relationship across
+units of meaning---here, tweets---where identical and semantically similar words
+are repeated (Graesser, McNamara, Louwerse, \& Cai, 2004). These repeated lexical
+items constitute a theme; on Twitter, this might be a particular hashtag, a
+name, a location, or other nominal category. This localized cohesion is
+referential; words are repeated and co-referred across tweets, creating a sense
+of continuity and cohesiveness of meaning and message.
+
+Typically, these analyses focus on \emph{content words} (e.g., nouns, adjectives,
+verbs), which convey more meaningful semantic information than \emph{function words}
+(e.g., articles, conjunctions). While function words can provide important
+information about complexity and language structure
+(Tausczik \& Pennebaker, 2010), content words have more specialized meaning and
+are therefore more useful when researchers want to understand \emph{what} people are
+discussing, rather than \emph{how} they are discussing it (Graesser et al., 2004; McNamara, Graesser, McCarthy, \& Cai, 2014).
+
+In estimating cohesion in Twitter posts, tweets that share content words
+will yield higher cohesion values, even among speakers with opposing
+views on the subject matter. Repetition of terms and concepts is captured by
+reiteration, which is a type of lexical cohesion in which a subsequent item
+repeats a previous item, or refers to it through synonymous language
+(Halliday \& Hasan, 1976). In social media, we can conceive of retweets (i.e., reposts
+or forwards of previous messages) as a form of reiteration
+that increase message cohesion. Since retweets replicate verbatim some part of
+another tweet, these tweets would also have higher cohesion. Hashtags function
+similarly and are included in our analysis.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{./figs/cohesion-in-tweets} \caption{A visual representation of cohesion in tweets.
+Content word overlap indicates a shared relationship among tweets.
+The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring.}\label{fig:cohesion-in-tweets}
+\end{figure}
+
+The use of similar language can provide insight into \emph{interlocutor cohesion}, or
+the degree to which people are talking about similar things. This can---as noted
+earlier---include people who are talking about similar things from radically
+perspectives, as well as those who are talking about something from the same
+perspective. Previous research from political science has investigated these
+ideas (Windsor, 2020): The \enquote{Occupy Wall Street} movement has been held up as an
+example of a movement with low interlocutor and linguistic cohesion because of
+its wide range of signs and slogans, while the \enquote{I am a man} protest (captured by
+Ernest Withers during the 1968 sanitation workers' strike in Memphis, TN) or the
+\enquote{Black Lives Matter} placards (following the uprising in Ferguson, MO) have high
+lexical and interlocutor cohesion (Edgar \& Johnson, 2018).
+
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
+contextualized by variation in real world events. Interlocutor cohesion may
+increase preceding an in-person social mobilization event, alerting a repressive
+government that collective mobilization is happening. Interlocutor cohesion may
+also respond to exogenous events such as spontaneous, unprovoked militarized
+conflict. If government forces target a new location using military weapons,
+this can precipitate online mobilization and discussion of the event.
+
+Given the importance of lexical and interlocutor cohesion for messaging in
+political movements, lexical cohesion may be an important bit of trace data for
+researchers interested in leveraging social media data to analyze social
+movements. Similar to large-scale studies of sociocultural movements (sometimes
+referred to as \emph{culturomics}; e.g., Michel et al., 2011), political
+scientists can track the ways in which conversations on social media coalesce or
+diffuse around similar content words. In this way, it matters relatively little
+whether the interlocutors have precisely the same views: The point is to
+understand whether the society-level conversation is converging on similar
+language.
+
+\hypertarget{social-and-political-cohesion}{%
+\subsubsection{Social and Political Cohesion}\label{social-and-political-cohesion}}
 
 Real-world collective action is known to bring about a sense of togetherness,
-also known as \enquote{collective effervescence} (Durkheim, 1995). This
-feeling of being a part of something larger than oneself leads individuals
-to act in ways that would not have on their own. Being overcome with this
-feeling can lead to violence (Collins, 2009; Spaaij, 2014).
-Conversely, increased exposure
-to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
+also known as \enquote{collective effervescence} (Durkheim, 1995). This feeling
+of being a part of something larger than oneself leads individuals to act in
+ways that would not have on their own. Being overcome with this feeling can lead
+to violence (Collins, 2009; Spaaij, 2014). Conversely, increased
+exposure to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
 found that exposure to fatal wartime violence resulted in increased prosocial
@@
 
-Just as real-world social cohesion can be
-quantified, so can online cohesion. While this can be quantified in many ways,
-one kind of cohesion can be found in the similarity in language use on social media.
-This implicit or explicit similarity in language use can indicate shared
-beliefs, thoughts, and feelings, as has been studied in research on language style
-in psycholinguistics and social psychology
-(Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010);
-although previous work on language style
-has often focused on individuals and small groups, this can be scaled up to examine
-massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
-This kind of widespread online social cohesion can lead to real-world
-social change.
-
-Combining these separate threads, it is reasonable to expect that real-world actions
-and online social interactions would be enmeshed, driving and being driven by
-one another. Rather than expecting that only real-world social cohesion would be
-driven by real-world action, we would expect interaction between real-world and
-virtual dynamics: In this case, exposure to real-world violence could result in social
-cohesion in the virtual world. Increased social cohesion is thus potentially
-an indicator and a result of increased social organization and mobilization
-on the ground.
-
-Social media platforms provide one way to enable this kind of online social
-cohesion by offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements
-an opportunity to complement or even replace real-world social mobilization.
-For example, during the 2012 Italian protests for global economic change, the riots in
-Rome were mirrored by Twitter activity both on the day of the protests and in the
-days following them (Vicari, 2013). Tweeting was
-determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more
-individuals rely on social media to obtain local news and information, it
-becomes increasingly important to understand just how these micro-blogs
-reflect real-world action.
+At the same time, behavioral similarity in certain contexts has been
+connected to important psychological and social effects. For example, shared
+language is associated with rapport (both in face-to-face and computer-mediated
+conversations; Niederhoffer \& Pennebaker, 2002; Riordan, Dale, Kreuz, \& Olney, 2011) and
+can even be connected to better performance on shared tasks (as long as
+the language is relevant to the task at hand; Fusaroli et al., 2012). Shared
+movement is associated with greater group bonding and greater willingness
+to contribute to the group (Wiltermuth \& Heath, 2009), and shared identity
+is associated with a greater willingness to adopt the group's goals and
+motivations (Walton, Cohen, Cwir, \& Spencer, 2012).
+
+We should expect to see increased linguistic cohesion among people participating
+in online discussions about an idea, event, individual, or movement. Given that
+Syrian protesters are known to have coordinated their activity through Twitter
+by discussing their own events (e.g., planned protests, active demonstrations)
+and their reactions to events happening around them (e.g., government reactions,
+international action or inaction), the cohesion in social media should be
+expected to correlate with the social cohesion of the group (Zeitzoff, 2011).
+
+This social cohesion can have real and wide-ranging impacts on a political
+movement and the people in it. A socially cohesive group is inherently more
+threatening to the existing regime because it reflects collective opposition
+momentum and the professionalization of potential alternate leadership. Groups
+with high social cohesion are more difficult to divide and conquer, and more
+cohesive messages may also garner increased international support. Global
+insurgency movements exhibit similar patterns in their social structure
+(Bohorquez, Gourley, Dixon, Spagat, \& Johnson, 2009). Each violent group has a stable state. Exogenous events
+can create perturbations that push the group to become either more cohesive or
+more fragmented. Rather than frenetic, patchwork messages via Twitter, emergent
+or intentional cohesive online messaging---using similar language, paralleling
+in-person messaging (Windsor, 2020)---are a sign of increased organizational
+structure, inciting a government response.
+
+Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
+and political cohesion. Shared language in an online environment may lead to the
+development or expression of a shared identity (Wiltermuth \& Heath, 2009). This,
+in turn, may drive individuals' propensity to engage in similar coordinated
+behavior on behalf of the group (Walton et al., 2012; Wiltermuth \& Heath, 2009).
+Taken together, these two processes may grow movement participants' weak and
+strong ties (Gladwell, 2010; Granovetter, 1973; McAdam, 1986), strengthening the movement overall by expanding and
+deepening heterogenous ties. Therefore,
+in the context of social conflict, the linguistic cohesion
+of the online conversation should correspond to the degree of
+social cohesion on the ground.
+
+Steinert-Threlkeld (2017) modeled a similar relationship
+between social media and social mobilization alongside event data. This
+groundbreaking work demonstrates that participants on the fringe of a social
+movement contribute substantially to the overall level of protest. In addition
+to providing new methods to this growing field of study, we build on this
+previous work by demonstrating how sociolinguistic cohesion evolves in
+response to negative and positive exogenous events.
+
+Political and social cohesion in the world can be modeled using event data which
+encodes who does what to whom on a given day. This could include events such as
+the government imposing a blockade or fighting with artillery or tanks on
+a civilian group. CAMEO (Conflict and Mediation Event Observations) encode
+a set of activities with numerical values, rescaled to reflect a
+conflict-cooperation scale (Goldstein, 1992; Schrodt \& Hall, 2006). These event
+codes include a range of behaviors, from making public statements and appeals,
+to demanding, threatening, protesting, and using unconventional mass violence.
+
+\hypertarget{sociolinguistic-cohesion-connectedness-of-speakers-ideas-and-events}{%
+\subsubsection{Sociolinguistic Cohesion: Connectedness of Speakers, Ideas, and Events}\label{sociolinguistic-cohesion-connectedness-of-speakers-ideas-and-events}}
+
+We tie the constructs of lexical, interlocutor, and social cohesion together in
+a theoretical framework called \emph{sociolinguistic cohesion}, as shown in Figure
+\ref{fig:theoretical-framework}. Several interconnected mechanisms are in
+motion here. Previous values of linguistic cohesion should influence future
+values of linguistic cohesion and future actions in the real world space.
+Previous events influence future events and future linguistic cohesion in
+social media.
+
+Sociolinguistic cohesion is not a static concept. Just as social movements
+experience increased participation and setbacks---indicating dynamic
+relationships among participants and between participants and the sociopolitical
+environment---sociolinguistic cohesion is also dynamic, reflecting the changing
+states of the political sphere. Other scholars have noted the diffusion of
+messages whereby they reach a critical mass, whereby \enquote{behaviors, beliefs, and
+preferences} spread within a population (Barash, Cameron, \& Macy, 2012). Cohesion
+changes over time in response to external events and the internal dynamics of
+the social movement. This can occur even if the social interaction occurs entirely
+online (Centola \& Macy, 2007).
+
+Related previous work has also explored diffusion of hashtags in viral contagion in
+Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
+(Fink, Schmidt, Barash, Cameron, \& Macy, 2016). The prevalence and rate of particular hashtags were
+contributed to the overall sociolinguistic cohesion. The more that people
+reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
+this phenomenon occurs during socially significant times like protests
+(State \& Adamic, 2015).
+
+Combining these separate threads, it is reasonable to expect that real-world
+actions and online social interactions would be enmeshed, driving and being
+driven by one another. Rather than expecting that only real-world social
+cohesion would be driven by real-world action, we would expect interaction
+between real-world and online dynamics: In this case, exposure to real-world
+violence could result in social cohesion in the virtual world. Increased social
+cohesion is thus potentially an indicator and a result of increased social
+organization and mobilization on the ground. However, this occurs within a context
+that is affected by local and international events; both
+exogenous events (like intervention by another country or
+international organization like the United Nations) and
+endogenous events (like the recruitment of new members to the rebel or
+resistance movement) can affect cohesion.
+
+From a dynamical systems perspective, online social cohesion and
+in-person action can be considered two complementary
+components of a single system, mutually constrained and constantly interacting
+and influencing one another (Mahner \& Bunge, 1997). Investigation of the
+coupling of real-world mobilization and social cohesion could provide new
+insight into the power of social media during mobilization and the ways in which
+individuals utilize it to bring about, or respond to, social change.
+Increasingly, social media platforms are being utilized during social
+mobilization (Koopmans, 2004; McAdam, Tarrow, \& Tilly, 2003),
+but the relationship between virtual and real-world mobilization
+is still largely unknown. The present work aims to understand how physical and
+virtual movements coexist and interact from a dynamical systems perspective.
+
+Lexical cohesion, then, is be a useful indicator of social cohesion in
+political crisis. Lexical cohesion happens at the word level. Interlocutor
+cohesion happens between speakers. Political cohesion happens at the social
+level during moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion is comprised of lexical, interlocutor, and
+socio-political events, where the words and their context reveal the disposition
+of socially connected linguistic communities. Sociolinguistic cohesion combines
+the elements of lexical cohesion in that it captures the degree of similarity
+between what is said, and how it is said. It accounts for the cohesion between
+multiple speakers in an environment whose language evolves to become more
+aligned and similar. Sociolinguistic cohesion also addresses how groups involved
+in political rebellion must have internal cohesion to overcome the collective
+action problem to mount sustained resistance to state authority.
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{./figs/theoretical-framework} \caption{The theoretical framework for sociolinguistic cohesion.
+Real-world events and linguistic cohesion continually interact and influence one another throughout time.}\label{fig:theoretical-framework}
+\end{figure}
 
@@
 
-Given the hypothesized interrelationship between the real-world
-and online actions---and the notorious messiness of naturally occurring
-data---it is critical to find appropriate analysis tools that can
-identify the complex interconnections. Traditional linear analyses have led to
-many notable discoveries in the domains of psychology and political science,
-but time series data pose problems that are not easily overcome with these
-methods. Events have historically been conceptualized as linear chains of
-smaller, sequential events with one occurrence leading to the next.
-Certain kinds of data are relatively well-suited to these analyses,
-but messy, complex, variable data from real-world events can pose
-challenges, from overpowered samples to violation of underlying
+Given the hypothesized interrelationship between the real-world and online
+actions---and the notorious messiness of naturally occurring data---it is
+critical to find appropriate analysis tools that can identify the complex
+interconnections. Traditional linear analyses have led to many notable
+discoveries in the domains of psychology and political science, but time series
+data pose problems that are not easily overcome with these methods. Events have
+historically been conceptualized as linear chains of smaller, sequential events
+with one occurrence leading to the next. Certain kinds of data are relatively
+well-suited to these analyses, but messy, complex, variable data from real-world
+events can pose challenges, from overpowered samples to violation of underlying
 statistical assumptions (Paxton \& Griffiths, 2017).
 
-At the same time, the foundational theoretical assumptions of a
-linear world has been
-increasingly replaced by ideas from dynamical systems theory. Rather than
-a chain of events, time series data can be thought of as nested occurrences,
-where mutually constrained parts (e.g., citizens, governments, real-world
-events, social media platforms) are constantly interacting, leading to
-more global behaviors that are larger than the sum of the parts
-(Turvey, 2018). Linear analyses flatten time series data and ignore
-the variability that is fundamental to these systems and their evolution over
-time. However, when analyzed as dynamical systems, many phenomena
-exhibit new nonlinear patterns that were formerly overlooked.
-Nonlinear methods provide means for capturing the rich temporal
-dynamics and variability that unfold in time series data.
-
-Although a number of other nonlinear methods exist,
-the primary nonlinear method used in the current work is cross-recurrence
-quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot,
-windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005).
-CRQA has successfully been used to gain a better understanding of many
-complex human phenomena, including a variety of human social interactions
-(for a review, see Fusaroli, Konvalinka, \& Wallot, 2014).
-Much as it has for psychology, we argue that the use of nonlinear methods in
-the investigation of political science phenomena will lead to new insights
-and the development of more robust theories.
+At the same time, the foundational theoretical assumptions of a linear world has
+been increasingly replaced by ideas from dynamical systems theory. Rather than a
+chain of events, time series data can be thought of as nested occurrences, where
+mutually constrained parts (e.g., citizens, governments, real-world events,
+social media platforms) are constantly interacting, leading to more global
+behaviors that are larger than the sum of the parts (Turvey, 2018).
+Linear analyses flatten time series data and ignore the variability that is
+fundamental to these systems and their evolution over time. However, when
+analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
+that were formerly overlooked. Nonlinear methods provide means for capturing the
+rich temporal dynamics and variability that unfold in time series data.
+
+Although a number of other nonlinear methods exist, the primary nonlinear method
+used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot, windowed cross-recurrence quantification
+analysis (WCRQA; Webber Jr \& Zbilut, 2005). CRQA has successfully been used to gain
+a better understanding of many complex human phenomena, including a variety of
+human social interactions (for a review, see Fusaroli, Konvalinka, \& Wallot, 2014). Much as it
+has for psychology, we argue that the use of nonlinear methods in the
+investigation of political science phenomena will lead to new insights and the
+development of more robust theories.
 
@@
 
-Social media has become a primary platform for social movements and
-activism across the world, but the extent to which virtual activism
-reflects and drives real-world mobilization is still largely unknown.
-In the current work, we
-conceptualize the physical and virtual movements as a dynamical system,
-both constantly interacting and influencing the other. We aim to study
-this by analyzing the real-world events and online social cohesion
-during nearly three months of the Arab Spring. Both real- and
-virtual-world collective coordination were powerful tools in the events
-of the Arab Spring and are undeniably linked. This study aims to explore
-the dynamics of Syrian Twitter users, who used the social media platform to raise
-awareness about the Arab Spring and bring about mass mobilization.
-
-Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998)
-and windowed cross-recurrence quantification analysis
-(WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the co-evolution of social
-cohesion online and real-world events. Specifically, using heterogeneous
-data from March 30, 2012, to June 15, 2012, we compared the social cohesion
-of Syrian tweets with the counts
-of all, positive, and negative real-world events derived from gold-standard
-international event data (i.e., the Integrated Crisis Early Warning
-System; Boschee et al., 2015).
-
-We hypothesized that the count of all events and the count of negative
-events would show high levels of determinism, as this time period was
-marked by daily violence which often leads to increased salience. We also
-hypothesized that the count of positive events would not show patterns of
-determinism, as these events were likely overshadowed by the salient
-negative daily occurrences.
-After testing these hypotheses, we then conducted exploratory analyses
-to further examine the patterns identified with CRQA. Using WCRQA,
-we sought to identify shifts in the
-dynamics of the systems that could then be linked to real-world shifts in
-conflict frequency.
-Through these analyses, our two primary goals in the current work were to uncover
-(1) how different intensities during times of turmoil may enhance or deter
-social cohesion in social media communication and (2) how social mobilization
-may be evident in the dynamic coupling of cohesion and real-world events.
+Social media has become a primary platform for social movements and activism
+across the world, but the extent to which virtual activism reflects and drives
+real-world mobilization is still largely unknown. In the current work, we
+conceptualize the physical and virtual movements as a dynamical system, both
+constantly interacting and influencing the other. We aim to study this by
+analyzing the real-world events and online social cohesion during nearly three
+months of the Arab Spring. Both real- and virtual-world collective coordination
+were powerful tools in the events of the Arab Spring and are undeniably linked.
+This study aims to explore the dynamics of Twitter users in Syria, who used the
+social media platform to raise awareness about the Arab Spring and bring about
+mass mobilization.
+
+Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) and
+windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the co-evolution of social cohesion online
+and real-world events. Specifically, using heterogeneous data from March 30,
+2012, to June 15, 2012, we compared the social cohesion of Syrian tweets with
+the counts of all, positive, and negative real-world events derived from
+gold-standard international event data (i.e., the Integrated Crisis Early
+Warning System; Boschee et al., 2015).
+
+We hypothesized that the count of all events and the count of negative events
+would show high levels of determinism, as this time period was marked by daily
+violence which often leads to increased salience. We also hypothesized that the
+count of positive events would not show patterns of determinism, as these events
+were likely overshadowed by the salient negative daily occurrences. After
+testing these hypotheses, we then conducted exploratory analyses to further
+examine the patterns identified with CRQA. Using WCRQA, we sought to identify
+shifts in the dynamics of the systems that could then be linked to real-world
+shifts in conflict frequency. Through these analyses, our two primary goals in
+the current work were to uncover (1) how different intensities during times of
+turmoil may enhance or deter social cohesion in social media communication and
+(2) how social mobilization may be evident in the dynamic coupling of cohesion
+and real-world events.
 
 An additional focus of the current work is to introduce cross-recurrence
-quantification analysis---a longstanding method from physics that has
-since become influential in a variety of other fields---to political
-science. We do so by providing detailed descriptions of the methods and
-providing clear directions about interpretation and significance testing
-even with relatively small-\emph{n} or case studies. After demonstrating these
-methods' utility with this dataset, we close the paper with specific
-suggestions to political scientists interested in incorporating these
-methods into their work.
+quantification analysis---a longstanding method from physics that has since
+become influential in a variety of other fields---to political science. We do so
+by providing detailed descriptions of the methods and providing clear directions
+about interpretation and significance testing even with relatively small-\emph{n} or
+case studies. After demonstrating these methods' utility with this dataset, we
+close the paper with specific suggestions to political scientists interested in
+incorporating these methods into their work.
 
@@
 The corpus of tweets used included 697428 Syrian tweets
-occurring between March 30--June 15, 2012. Using the Twitter
-streaming API, servers at the University of Texas at Austin collected
-the tweets. The servers were run on a stable (LTS) version of Ubuntu
-Linus (v. 10.04) and were connected directly to the high-bandwidth UT network
-maintained by IT services.
-
-Tweets collected contained one or more of the following keywords:
-\enquote{syria,} \enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These
-keywords were chosen based on the most distinctive terms used in news
-articles covering the Arab Spring in Syria at the time. A node.js script
-was used to reinitialize the connection to Twitter's servers whenever the
-script timed out due to a period of silence. The script requested data from
-the API endpoint using basic HTTP authentication (OAuth was optional, at
-the time) at \url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored
-the data directly to the local hard disk. The tweets were then post-processed
-with a Python script to convert the JSON-formatted tweets to tab-separated
-files, which were then compressed to maximize storage efficiency.
-
-All scripts used for scrapping tweets and compressing data can be found at \url{https://github.com/chbrown/twilight}.
+occurring between March 30--June 15, 2012. Using the Twitter streaming API,
+servers at the University of Texas at Austin collected the tweets. The servers
+were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
+directly to the high-bandwidth UT network maintained by IT services.
+
+Tweets collected contained one or more of the following keywords: \enquote{syria,}
+\enquote{syrian,} \enquote{damascus,} \enquote{homs,} \enquote{al-assad,} and \enquote{sunni.} These keywords were
+chosen based on the most distinctive terms used in news articles covering the
+Arab Spring in Syria at the time. A node.js script was used to reinitialize the
+connection to Twitter's servers whenever the script timed out due to a period of
+silence. The script requested data from the API endpoint using basic HTTP
+authentication (OAuth was optional, at the time) at
+\url{https://stream.twitter.com/1.1/statuses/filter.json}, and stored the data
+directly to the local hard disk. The tweets were then post-processed with a
+Python script to convert the JSON-formatted tweets to tab-separated files, which
+were then compressed to maximize storage efficiency.
+
+All scripts used for scraping tweets and compressing data can be found at
+\url{https://github.com/chbrown/twilight}.
 
@@
 
-Event data were obtained from the 2012 Integrated Crisis Early Warning
-System (ICEWS; Boschee et al., 2015). The event data were first filtered to
-remove incomplete and incorrectly formatted data. They were then filtered
-to include only events that were directed at (i.e., \texttt{target}) Syria (\(n = 6300\)).
-To explore the impact of outwardly directed Syrian events, the data were
-filtered again to include events that were both directed at (i.e., \texttt{target})
-or directed by (i.e., \texttt{source}) Syria (\(n = 7990\)).
+Event data were obtained from the 2012 Integrated Crisis Early Warning System
+(ICEWS; Boschee et al., 2015). The event data were first filtered to remove
+incomplete and incorrectly formatted data. They were then filtered to include
+only events that were directed at (i.e., \texttt{target}) Syria (\(n = 6300\)). To
+explore the impact of outwardly directed Syrian events, the data were filtered
+again to include events that were both directed at (i.e., \texttt{target}) or directed
+by (i.e., \texttt{source}) Syria (\(n = 7990\)).
 
@@
 
-The social cohesion or linguistic similarity of daily tweets was calculated
-by quantifying the frequency of shared content words with respect to those
-words' frequencies in the entire tweet corpus. If a linguistic term has a
-high frequency in one tweet but has a low frequency in the whole tweet
-corpus, then it is more likely a content word and is thus given more weight
-in calculating social cohesion.
-This method is similar to inverse document frequency (IDF).
-For more information on IDF, see Jones (1972) and
+The social cohesion or linguistic similarity of daily tweets was calculated by
+quantifying the frequency of shared content words with respect to those words'
+frequencies in the entire tweet corpus. If a linguistic term has a high
+frequency in one tweet but has a low frequency in the whole tweet corpus, then
+it is more likely a content word and is thus given more weight in calculating
+social cohesion. This method is similar to inverse document frequency (IDF). For
+more information on IDF, see Jones (1972) and
 Robertson (2004).
 
-The tweets were first sorted into ascending order by timestamp. They were
-then grouped into successive sets of five tweets. Inverse frequency
-weighting for the overlap words and all words was conducted for each pair
-of two tweets in the group of five, then divided to get the social cohesion
-score for that pair (see Eq. 1-3). This resulted in ten social cohesion
-values for each group of five tweets; these values were then averaged to get
-a social cohesion score for the entire set of five tweets. Finally,
-the mean of all average cohesion values for all groups was taken to get
-a social cohesion score for each day.
+The tweets were first sorted into ascending order by timestamp. They were then
+grouped into successive sets of five tweets. Inverse frequency weighting for the
+overlap words and all words was conducted for each pair of two tweets in the
+group of five, then divided to get the social cohesion score for that pair (see
+Eq. 1-3). This resulted in ten social cohesion values for each group of five
+tweets; these values were then averaged to get a social cohesion score for the
+entire set of five tweets. Finally, the mean of all average cohesion values for
+all groups was taken to get a social cohesion score for each day.
 
 \begin{align}
-\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k \frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k
+\frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
 \end{align}
@@
 \begin{align}
-\text{Two tweets similarity =}\frac{\text{inverse frequency weighting of overlap words}}{\text{inverse frequency weighting of all words}}
+\text{Two tweets' similarity =}\frac{\text{inverse frequency weighting of overlap
+words}}{\text{inverse frequency weighting of all words}}
 \end{align}
 
-The social cohesion calculation was performed on the tweet corpus
-containing both English and Arabic tweets. All hashtags and URLs were included
-in the analysis.
+The social cohesion calculation was performed on the tweet corpus containing
+both English and Arabic tweets. All hashtags and URLs were included in the
+analysis.
 
@@
 Using the Integrated Crisis Early Warning System (ICEWS) developed at the
-Defense Advanced Research Project Agency, the daily events were
-scored with an intensity rating ranging from -10 to 10. Negative
-events---such as riots and attacks---are coded with low negative numbers, while
-positive or peaceful events are coded with high positive numbers. This
-well-validated coding scheme allows for numerical quantification of
-different event types.
-
-For both the target only and the target and source data described above, time series of
-the count of all events were generated by summing the total number of events
-on each day, irrespective of ICEWS score. Similarly, time series of count
-of positive events were generated by summing the number of ICEWS events
-for each day that had an intensity rating greater than zero. Lastly,
-time series of count of negative events were generated by summing the number
-of ICEWS events for each day that had an intensity rating less than zero.
+Defense Advanced Research Project Agency, the daily events were scored with an
+intensity rating ranging from -10 to 10. Negative events---such as riots and
+attacks---are coded with low negative numbers, while positive or peaceful events
+are coded with high positive numbers. This well-validated coding scheme allows
+for numerical quantification of different event types.
+
+For both the target-only and the target and source data described above, time
+series of the count of all events were generated by summing the total number of
+events on each day, irrespective of ICEWS score. Similarly, time series of count
+of positive events were generated by summing the number of ICEWS events for each
+day that had an intensity rating greater than zero. Lastly, time series of count
+of negative events were generated by summing the number of ICEWS events for each
+day that had an intensity rating less than zero.
 
@@
 
-We first used cross-recurrence quantification analysis
-(CRQA; Zbilut et al., 1998) to investigate the temporal patterns of
-social cohesion and real-world events in Syria during Arab Spring. CRQA
-is an extension of RQA, which captures the patterns of revisited states of
-a single time series (Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992). CRQA
-allows for two time series to be projected onto one another to investigate
-shared states and trajectories.
-In CRQA, we track these shared states by identifying \emph{recurrent points},
-or intersections of time during which two signals shared or revisited the same
-state. These shared states can be at the same time or at later points in
-the time series. We can further chart shared trajectories by examining
-the occurrences and patterns of multiple sequential recurrent points.
-
-To perform CRQA, the time series must be converted to the same
-scale, while still preserving a sampling rate that respects the native
-timescale of the system
-(cf.~Nyquist frequency in signal processing; Grenander, 1959).
-Because the social cohesion and event data have different scales and values,
-we converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles
-(e.g., Figure \ref{fig:deciled-ts}) to analyze the relative dynamics of different
-levels of social cohesion and counts of all, positive, and negative events
-on each day.
-We implemented CRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R (R Core Team, 2019).
+We first used cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of social cohesion
+and real-world events in Syria during Arab Spring. CRQA is an extension of RQA,
+which captures the patterns of revisited states of a single time series
+(Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992). CRQA allows for two time series
+to be projected onto one another to investigate shared states and trajectories.
+In CRQA, we track these shared states by identifying \emph{recurrent points}, or
+intersections of time during which two signals shared or revisited the same
+state. These shared states can be at the same time or at later points in the
+time series. We can further chart shared trajectories by examining the
+occurrences and patterns of multiple sequential recurrent points.
+
+To perform CRQA, the time series must be converted to the same scale, while
+still preserving a sampling rate that respects the native timescale of the
+system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
+Because the social cohesion and event data have different scales and values, we
+converted each time series (e.g., Figure \ref{fig:raw-ts}) into deciles (e.g.,
+Figure \ref{fig:deciled-ts}) to analyze the relative dynamics of different
+levels of social cohesion and counts of all, positive, and negative events on
+each day. We implemented CRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R
+(R Core Team, 2019).
 
@@
 a cross-recurrence plot, two time series are plotted against each other on the
-\(x\) and \(y\) axes. At every point where they share the same state, a point
-in placed on the plot to indicate recurrence. (For categorical CRQA, this process
+\(x\) and \(y\) axes. At every point where they share the same state, a point in
+placed on the plot to indicate recurrence. (For categorical CRQA, this process
 is similar to the Cartesian product.)
 
-We can visually analyze these plots
-to reveal patterns of structure and recurrence. The line \(y = x\) is known
-as the \emph{line of identity}. This line falls where the time series match
-temporally. A filled line would indicate perfect in-phase synchrony between the
-two time series. See
-Figures \ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg}
-for examples of RPs.
+We can visually analyze these plots to reveal patterns of structure and
+recurrence. The line \(y = x\) is known as the \emph{line of identity}. This line falls
+where the time series match temporally. A filled line would indicate perfect
+in-phase synchrony between the two time series. See Figures
+\ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg} for examples of
+RPs.
 
@@
 provides information into the patterns and dynamics of the new shared system.
-These metrics are also critical for inferential
-statistics. We will focus most directly on two of these metrics:
-\emph{recurrence rate} and \emph{determinism}.
-
-The percentage of recurrent points to total possible points is a metric
-called the \emph{recurrence rate} (\emph{RR}). This metrics gives a general description of
-how frequently the time series are sharing the same states. In the current
-study, a recurrent point would indicate that the level of social cohesion
-and frequency of events were at the same intensity.
-
-Recurrent points that occur in successive moments form line structures.
-These are conceptualized as shared trajectories, where the two time series
-are moving together across time in a shared state. The percentage of
-recurrent points on the plot that fall along diagonal line structures
-(i.e., two or more
-consecutive points) is a metric called \emph{percent determinism}
-(or simply \emph{determinism}; \emph{DET}). For the
-current project, a high DET would indicate that not only are the levels of
-social cohesion and frequency of events occurring at similar intensities,
-but they are doing so across consecutive days.
+These metrics are also critical for inferential statistics. We will focus most
+directly on two of these metrics: \emph{recurrence rate} and \emph{determinism}.
+
+The percentage of recurrent points to total possible points is a metric called
+the \emph{recurrence rate} (\emph{RR}). This metrics gives a general description of how
+frequently the time series are sharing the same states. In the current study, a
+recurrent point would indicate that the level of social cohesion and frequency
+of events were at the same intensity.
+
+Recurrent points that occur in successive moments form line structures. These
+are conceptualized as shared trajectories, where the two time series are moving
+together across time in a shared state. The percentage of recurrent points on
+the plot that fall along diagonal line structures (i.e., two or more consecutive
+points) is a metric called \emph{percent determinism} (or simply \emph{determinism};
+\emph{DET}). For the current project, a high DET would indicate that not only are the
+levels of social cohesion and frequency of events occurring at similar
+intensities, but they are doing so across consecutive days.
 
 A number of other metrics provide insight not only into the amount of structure
-between the systems but about the nature of this shared structure.
-The average length of the line structures is called \emph{mean line} (L), which can
-be conceptualized as the average amount of time that the two time series move
-together before one or both shift states. The longest line length is called
-\emph{max line} (\emph{maxL}); it indicates the longest instance of being \enquote{stuck} in a
-particular state together and is a measure of the stability of the system.
-The total \emph{number of lines} on the plot (\emph{NRLINE})
-scales with structure: The more lines that exist, the more coupled the two
-systems are. The complexity or variability of line lengths is captured by a
-metric called \emph{entropy} (\emph{ENTR})---which may also be normalized by the total
-number of lines (i.e., \emph{normalized entropy}; \emph{rENTR})---and indicates
-the stability and predictability of the system. When one of the signals gets
-\enquote{stuck} in a state and the other moves on to other states, this results in
-vertical line structures, which are quantified in \emph{laminarity} (\emph{LAM};
-i.e., the proportion of points forming vertical line structures)
-and \emph{trapping time} (\emph{TT}; i.e., the average length of the
-vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).
+between the systems but about the nature of this shared structure. The average
+length of the line structures is called \emph{mean line} (L), which can be
+conceptualized as the average amount of time that the two time series move
+together before one or both shift states. The longest line length is called \emph{max
+line} (\emph{maxL}); it indicates the longest instance of being \enquote{stuck} in a
+particular state together and is a measure of the stability of the system. The
+total \emph{number of lines} on the plot (\emph{NRLINE}) scales with structure: The more
+lines that exist, the more coupled the two systems are. The complexity or
+variability of line lengths is captured by a metric called \emph{entropy}
+(\emph{ENTR})---which may also be normalized by the total number of lines (i.e.,
+\emph{normalized entropy}; \emph{rENTR})---and indicates the stability and predictability
+of the system. When one of the signals gets \enquote{stuck} in a state and the other
+moves on to other states, this results in vertical line structures, which are
+quantified in \emph{laminarity} (\emph{LAM}; i.e., the proportion of points forming
+vertical line structures) and \emph{trapping time} (\emph{TT}; i.e., the average length of
+the vertical trajectories). For more detail on CRQA metrics, see Coco and Dale (2018).
 
@@
 
-Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not have
-inherently meaningful values. As a result, CRQA is best used as a relative
-metric---that is, comparing the CRQA values across conditions or subsets
-of the data. Typically, meaningful differences between values are determined with
+Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not
+have inherently meaningful values. As a result, CRQA is best used as a relative
+metric---that is, comparing the CRQA values across conditions or subsets of the
+data. Typically, meaningful differences between values are determined with
 traditional inferential statistics. While this may not be a problem for
@@
 
-For CRQA, this can be addressed using \emph{permutation tests}.
-Similar to more established methods of statistical significance in CRQA research
-(which create surrogate time series; e.g., Paxton \& Dale, 2017),
-the permutation test approach to significance testing allows the researcher
-to use a time series as its own baseline by testing whether the \emph{structure}
-of the unfolding events of the time series---rather than the \emph{raw frequency} of the
-events within the time series---cohere together more than would be expected
-by chance. A permutation test is similar to
-bootstrapping, except that the sampling of observations is done without
-replacement. In this approach, we simply create a large number of permutations
-of the original time series (i.e., breaking up the dependency across time points but
-preserving the frequencies of the events), conduct CRQA for each of those
-permutations, and then examine whether the real time series' CRQA metrics
-exceed those that we would expect to see by chance. The proportion of times that
-the real time series' values exceeds the surrogate time series' values can
-be interpreted as the alpha criterion to determine significance.
-For more information on permutation
-tests, see Good (2013).
-
-Using the real deciles of social cohesion, count of all events,
-count of positive events, and count of negative events, we conducted a series
-of permutation tests
-(one for the comparison between social cohesion and each type of event count)
-to determine statistical difference from chance for each CRQA metric.
-Using the \texttt{sample} function in base R (R Core Team, 2019), \(1000\) permuted time series were
-created for each of the real time series.\\
-CRQA was then run \(1000\) times for social cohesion and count of all
-events, social cohesion and count of positive events, and social cohesion and
-count of negative events using the permuted time series. This resulted in
-\(1000\) results for each of the CRQA metrics for each combination of time series.
-Statistical significance from chance was set at the 95th and 99th percentiles
-of the metrics from the permuted CRQ analyses. Given that a permutation test
-is similar to bootstrapping but does not include replacement, all points were
-included in each CRQA analysis, leaving RR constant across all permutations. Thus,
-RR is not included in the inferential tests.
+For CRQA, this can be addressed using \emph{permutation tests}. Similar to more
+established methods of statistical significance in CRQA research (which create
+surrogate time series; e.g., Paxton \& Dale, 2017), the permutation test
+approach to significance testing allows the researcher to use a time series as
+its own baseline by testing whether the \emph{structure} of the unfolding events of
+the time series---rather than the \emph{raw frequency} of the events within the time
+series---cohere together more than would be expected by chance. A permutation
+test is similar to bootstrapping, except that the sampling of observations is
+done without replacement. In this approach, we simply create a large number of
+permutations of the original time series (i.e., breaking up the dependency
+across time points but preserving the frequencies of the events), conduct CRQA
+for each of those permutations, and then examine whether the real time series'
+CRQA metrics exceed those that we would expect to see by chance. The proportion
+of times that the real time series' values exceeds the surrogate time series'
+values can be interpreted as the alpha criterion to determine significance. For
+more information on permutation tests, see Good (2013).
+
+Using the real deciles of social cohesion, count of all events, count of
+positive events, and count of negative events, we conducted a series of
+permutation tests (one for the comparison between social cohesion and each type
+of event count) to determine statistical difference from chance for each CRQA
+metric. Using the \texttt{sample} function in base R (R Core Team, 2019), \(1000\) permuted time
+series were created for each of the real time series. CRQA was then run \(1000\)
+times for social cohesion and count of all events, social cohesion and count of
+positive events, and social cohesion and count of negative events using the
+permuted time series. This resulted in \(1000\) results for each of the CRQA
+metrics for each combination of time series. Statistical significance from
+chance was set at the 95th and 99th percentiles of the metrics from the permuted
+CRQ analyses. Given that a permutation test is similar to bootstrapping but does
+not include replacement, all points were included in each CRQA analysis, leaving
+RR constant across all permutations. Thus, RR is not included in the inferential
+tests.
 
@@
 
-We used windowed cross-recurrence quantification analysis
-(WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the
-temporal dynamics of social cohesion and real-world events. In this analysis,
-a smaller \enquote{window} of time points is used to calculate CRQA and capture more
-fine-grained dynamics of two time series. The window remains the same size and
-\enquote{slides} diagonally up the line of identity. The changes in the CRQA metrics
-across the windows can reveal changes in dynamics that can then be linked to
-external, real-world events.
-We implemented WCRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R (R Core Team, 2019).
+We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal
+dynamics of social cohesion and real-world events. In this analysis, a smaller
+\enquote{window} of time points is used to calculate CRQA and capture more fine-grained
+dynamics of two time series. The window remains the same size and \enquote{slides}
+diagonally up the line of identity. The changes in the CRQA metrics across the
+windows can reveal changes in dynamics that can then be linked to external,
+real-world events. We implemented WCRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R
+(R Core Team, 2019).
 
@@
 
-Conducting WCRQA results in CRQA metrics (e.g., RR, DET, ENTR) for each
-respective window. For these analyses, we decided to focus on recurrence rate
-and determinism.
+For WCRQA analyses, we decided to focus on RR and DET.
 
@@
 In addition to the CRQA parameters, two other parameters are required when
-conducting WCRQA. First, the \emph{window size}
-will determine how many observations are used in each CRQA analysis. We
-conducted WCRQA with a window size of \(14\) to investigate the dynamics over
-two weeks and allow for the capture of more structure and thus a more
-meaningful interpretation of DET.
-
-The second parameter to be chosen is a \emph{window step size}.
-Window step size is how far the window moves up the line of identity
-before conducting CRQA again. We chose \(1\) for the step size to understand
-how the metrics evolve from day to day.
+conducting WCRQA. First, the \emph{window size} will determine how many observations
+are used in each CRQA analysis. We conducted WCRQA with a window size of \(14\) to
+investigate the dynamics over two weeks and allow for the capture of more
+structure and thus a more meaningful interpretation of DET.
+
+The second parameter to be chosen is a \emph{window step size}. Window step size is
+how far the window moves up the line of identity before conducting CRQA again.
+We chose \(1\) for the step size to understand how the metrics evolve from day to
+day.
 
@@
 
-To visualize WCRQA, the resulting metrics from each window can be plotted
-as a time series. This allows for visual interpretation of the pattern or
-fluctuation of the metrics across time. These dynamics can then be linked
-to other external events. See Figures \ref{fig:plot-wcrqa-targ-all} and
+To visualize WCRQA, the resulting metrics from each window can be plotted as a
+time series. This allows for visual interpretation of the pattern or fluctuation
+of the metrics across time. These dynamics can then be linked to other external
+events. See Figures \ref{fig:plot-wcrqa-targ-all} and
 \ref{fig:plot-wcrqa-source-targ-all} for examples.
@@
 
-To visualize the differences in the WCRQA metrics from those obtained by
-chance, a permutation test was done to set upper and lower bounds for the
-95th and 99th percentiles. Using a sample size of 14, \(1000\) permuted
-time series were generated without replacement for each real time series. The
-upper and lower 95th and 99th percentiles were set based on the distribution
-of the permuted WCRQA metrics.
+To visualize the differences in the WCRQA metrics from those obtained by chance,
+a permutation test was done to set upper and lower bounds for the 95th and 99th
+percentiles. Using a sample size of 14, \(1000\) permuted time series were
+generated without replacement for each real time series. The upper and lower
+95th and 99th percentiles were set based on the distribution of the permuted
+WCRQA metrics.
 
@@
 
-A permutation test for the CRQA of social cohesion and count of all events
-found a statistical difference from chance for DET, NRLINE, maxL, and LAM.
-All other metrics did not reach significance (Figure \ref{fig:plot-rp-targ-all};
+A permutation test for the CRQA of social cohesion and count of all events found
+a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
+metrics did not reach significance (Figure \ref{fig:plot-rp-targ-all};
 \autoref{table-1}).
 
-A permutation test for the CRQA of social cohesion and
-count of positive events found no statistically significant difference for any
-of the metrics other than TT (Figure \ref{fig:plot-rp-targ-pos};
-\autoref{table-1}).
-
-A permutation test for the CRQA of social cohesion and
-count of negative events found a statistically significant difference for DET,
-NRLINE, L, ENTR, LAM, and TT. All other metrics did not reach significance
-(Figure \ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
-
-A qualitative investigation of the recurrence plots suggests
-a shift in dynamics around the 36th observation,
-which corresponds to May 4th, 2012.
+A permutation test for the CRQA of social cohesion and count of positive events
+found no statistically significant difference from chance for any of the metrics
+other than TT (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found a statistically significant difference from chance for DET, NRLINE, L,
+ENTR, LAM, and TT. All other metrics did not reach significance (Figure
+\ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
+
+A qualitative investigation of the recurrence plots suggests a shift in dynamics
+around the 36th observation, which corresponds to May 4th, 2012.
 
 \begin{longtable}[]{@{}cccccccccc@{}}
-\caption{\label{table-1}CRQA results for target only data.}\tabularnewline
+\caption{\label{table-1}CRQA results for target-only data.}\tabularnewline
 \toprule
@@
 
-A permutation test for the CRQA of social cohesion and count of all
-events found a statistical difference from chance for DET, NRLINE, and
-LAM. All other metrics were non-significant (Figure
-\ref{fig:plot-rp-source-targ-all}; \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of positive
-events found a statistical difference from chance for maxL, ENTR, and LAM
-(Figure \ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of negative
-events found a statistical difference from chance for DET, NRLINE, and rENTR.
-All other metrics were non-significant (Figure
-\ref{fig:plot-rp-source-targ-neg}; \autoref{table-2}).
-
-Looking qualitatively at the recurrence plots, there again appeared
-to be a shift in dynamics around the 36th observation (May 4th, 2012).
+A permutation test for the CRQA of social cohesion and count of all events found
+a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
+were non-significant (Figure \ref{fig:plot-rp-source-targ-all};
+\autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of positive events
+found a statistical difference from chance for maxL, ENTR, and LAM (Figure
+\ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found a statistical difference from chance for DET, NRLINE, and rENTR. All other
+metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-neg};
+\autoref{table-2}).
+
+Looking qualitatively at the recurrence plots, there again appeared to be a
+shift in dynamics around the 36th observation (May 4th, 2012).
 
@@
 
-In the plots (see Figures \ref{fig:plot-wcrqa-targ-all} and
-\ref{fig:plot-wcrqa-source-targ-all}), the 95th percentiles are represented
-by horizontal red lines, and the 99th percentiles are
-represented by horizontal orange lines. The trend lines are plotted in blue.
+In the WCRQA plots (see Figures \ref{fig:plot-wcrqa-targ-all} and
+\ref{fig:plot-wcrqa-source-targ-all}), the 95th percentiles are represented by
+horizontal red lines, and the 99th percentiles are represented by horizontal
+orange lines. The trend lines are plotted in blue.
 
@@
 
-For social cohesion and count of all events, there was a consistent period
-of above-chance RR from the 7th-12th and 36th-47th window. DET was largely
-above chance from the 46th to the 61st window
-(Figure \ref{fig:plot-wcrqa-targ-all}).
-
-For social cohesion and count of positive events, there was a downward trend in RR
-as the window moves with largely above-chance RR from the 1st-18th and
-32nd-45th windows. DET was at or above chance for the 8th-17th,
-32nd-34th and at the 60th window (Figure \ref{fig:plot-wcrqa-targ-all}).
-
-For social cohesion and count of negative events, RR stayed above
-or almost above chance from the 4th-7th and 43rd-47th windows. DET
-was above or nearly above chance in the 1st and 2nd windows, with intermittent
-peaks in later windows (Figure \ref{fig:plot-wcrqa-targ-all}).
+For social cohesion and count of all events, there was a consistent period of
+above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
+one-week peaks at the beginning of the time period, DET was largely above chance
+from the 46th to the 61st window, with some exceptions (Figure
+\ref{fig:plot-wcrqa-targ-all}).
+
+For social cohesion and count of positive events, we saw a downward trend in RR
+as the window advances throughout the sample. Interestingly, we see largely
+above-chance RR until the 50th window, with some exceptions during window
+periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
+60th windows (Figure \ref{fig:plot-wcrqa-targ-all}).
+
+For social cohesion and count of negative events, RR stayed above or almost
+above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
+above chance in the 1st and 2nd windows, with intermittent peaks in later
+windows (Figure \ref{fig:plot-wcrqa-targ-all}).
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 7th-13th and 26th-47th
-windows. DET also showed above- or nearly above-chance values in windows 7
-through 17 and intermittent peaks between the 34th and 61st windows
-(Figure \ref{fig:plot-wcrqa-source-targ-all}).
-
-For social cohesion and count of
-positive events, there was a downward trend in RR as the window moved, with
-largely above-chance values in the first 20 windows and the 32nd-45th windows.
-DET stayed largely within chance, with the exception of windows 13
-through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
-
-For social cohesion
-and negative events, there was an extended period of time during which RR
-(32nd-47th windows) and DET (35th-39th windows) were above or nearly above
-chance (Figure \ref{fig:plot-wcrqa-source-targ-all}). These windows span from
-May 3rd--14th, 2012.
+above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
+also showed above- or nearly above-chance values in windows 7 through 17 and
+intermittent peaks between the 34th and 61st windows (Figure
+\ref{fig:plot-wcrqa-source-targ-all}).
+
+For social cohesion and count of positive events, there was a downward trend in
+RR as the window moved, with largely above-chance values in the first 20 windows
+and the 32nd--45th windows. DET stayed largely within chance, with the exception
+of windows 13 through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+
+For social cohesion and negative events, there was an extended, overlapping
+period of time during which RR (32nd--47th windows) and DET (35th--39th windows)
+were above or nearly above chance (Figure
+\ref{fig:plot-wcrqa-source-targ-all}). These windows span from May 3rd--14th,
+2012.
 
@@
 
-In the present study, we investigated the dynamics of real-world events
-and online communication on Twitter in Syria during Arab Spring.
-CRQA methodology allows us to model the relationship between sociolinguistic
-cohesion and exogenous political events. This work stands alongside the model
-of Palestinian-Israeli social media and events developed by Zeitzoff (2011),
-and the role of peripheral participants in the Syrian Arab Spring movement by
+In the present study, we investigated the dynamics of real-world events and
+online communication on Twitter in Syria during Arab Spring. CRQA methodology
+allows us to model the relationship between sociolinguistic cohesion and
+exogenous political events. This work stands alongside the model of
+Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
+the role of peripheral participants in the Syrian Arab Spring movement by
 Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
-demonstrate how language and social mobilization interact with events along
-the conflict-cooperation continuum in Syria. We have introduced a novel
-theoretical framework of sociolinguistic cohesion which we operationalize
-using a weighted measure of lexical relationships. We examined
-how social mobilization both virtually and physically evolve over time in
-tandem. Using nonlinear dynamical time series analyses, we investigated the
-theory that virtual mobilization is increasingly reflective of real-world
-events during times of strife.
+demonstrate how language and social mobilization interact with events along the
+conflict-cooperation continuum in Syria. We have introduced a novel theoretical
+framework of sociolinguistic cohesion which we operationalize using a weighted
+measure of lexical relationships. We examined how social mobilization both
+virtually and physically evolve over time in tandem. Using nonlinear dynamical
+time series analyses, we investigated the theory that virtual mobilization is
+increasingly reflective of real-world events during times of strife.
 
@@
 
-The significant result of DET for social cohesion with all and negative
-events supports our hypothesis that event salience is coupled with online
-social cohesion. The frequency of all and negative events are thus associated
-with greater shared trajectories with social cohesion that would be expected
-by chance. However, when we specifically target positive events, the connection
-to social cohesion fades, providing further support for our hypothesis.
+The significant result of DET for social cohesion with all and negative events
+supports our first hypothesis that event salience is coupled with online social
+cohesion. The frequency of all and negative events are thus associated with
+greater shared trajectories with social cohesion that would be expected by
+chance. However, when we specifically target positive events, the connection to
+social cohesion fades, providing further support for our second hypothesis.
 Positive events may be less coupled to social cohesion than more salient
@@
 
-By adding Syria as a source in the data filtering, the dataset increased
-in size by 1,690 samples. These additional observations are times where
-Syria initiated an event with another country. Events initiated by Syria
-but directed internally within the country were already captured by the
-target-only filtering. The increase in coupling between positive events
-and social cohesion can thus only be due to the externally
-directed events. Though the coupling between social cohesion with
-negative and all events were largely unchanged,
-positive events and social cohesion showed greater stability
-in their coupling (reflected in maxL); while TT was no longer
-significant in these analyses, LAM (related to TT) did
-reach statistical significance.
-
-While interesting, the underlying meaning or drivers of this change
-in results requires further investigation that incorporates the
-actual content of the tweets themselves. One possible reason (among
-many) may be that the finding was spurious. The positive external
-events from Syria may have been self-serving, aiming to prevent intervention
-by other countries or to cover up what was happening internally.
-During these moments, the increased cohesion may reflect a surge from
-the Syrian people trying to raise awareness of the situation or
-to decry the Syrian government's attempts to improve their international
-standing. In this case, the increased coupling of positive events would
-be coupled not with shared positive affect in social media but instead
-to shared negative affect in social media in response. However, we
-cannot test this hypothesis with the current data; future
-research should explore the semantic content of this tweet
-corpus to determine the nature of the socially cohered language.
+By adding Syria as a source in the data filtering, the dataset increased in size
+by 1,690 samples. These additional observations are times where Syria initiated
+an event with another country. Events initiated by Syria but directed internally
+within the country were already captured by the target-only filtering. The
+increase in coupling between positive events and social cohesion can thus only
+be due to the externally directed events. Though the coupling between social
+cohesion with negative and all events were largely unchanged, positive events
+and social cohesion showed greater stability in their coupling (reflected in
+maxL); while TT was no longer significant in these analyses, LAM (related to TT)
+did reach statistical significance.
+
+While interesting, the underlying meaning or drivers of this change in results
+requires further investigation that incorporates the actual content of the
+tweets themselves. One possible reason (among many) may be that the finding was
+spurious. The positive external events from Syria may have been self-serving,
+aiming to prevent intervention by other countries or to cover up what was
+happening internally. During these moments, the increased cohesion may reflect a
+surge from the Syrian people trying to raise awareness of the situation or to
+decry the Syrian government's attempts to improve their international standing.
+In this case, the increased coupling of positive events would be coupled not
+with shared positive affect in social media but instead to shared negative
+affect in social media in response. However, we cannot test this hypothesis with
+the current data; future research should explore the semantic content of this
+tweet corpus to determine the nature of the socially cohered language.
 
@@
 
-The time period of differing dynamics---from observation 38 through
-43---appears to be captured by the RR and DET values in
-WCRQA of social cohesion and count of negative
-events (Figure \ref{fig:plot-wcrqa-targ-all}). The
-amount of recurrence and determinism for these periods almost consistently
-lie above chance, suggesting that the intensity of negative events coincide
-with the degree of social cohesion found on Twitter and that these
-shared trajectories extend across multiple days.
-
-The above-chance levels of determinism and recurrence rate demonstrate
-the coupling of social cohesion to both total and negative events during
-times of strife. During this period,
-the modal ICEWS event for each day (Figure \ref{fig:plot-mode-event})
-during May 1st---15th was almost consistently -10, the most violent
-event category. These dates directly correlate with the above-chance RR and DET
-metrics for the WCRQA of social cohesion and count of negative events.
-Furthermore, for WCRQA of social cohesion and positive event count during
-this time period, DET was entirely within chance (Figure
-\ref{fig:plot-wcrqa-targ-all}). This supports our hypothesis, as the
-positive events are seemingly not coupled with the social cohesion on Twitter
-during civil uprisings during the Arab Spring.
+The time period of differing dynamics noted in the cross-recurrence plots---from
+observation 32 through 47---appears to be captured by the above-chance RR values
+in WCRQA of social cohesion and count of all events (Figure
+\ref{fig:plot-wcrqa-targ-all}). However, DET for these periods only
+intermittently rises above chance; it more consistently reaches statistical
+significance only at the end of the window through the end of the observation
+period, following a spike in the RR between negative event count and social
+cohesion. During this period, the modal ICEWS event for each day (Figure
+\ref{fig:plot-mode-event}) was almost consistently -10, the most violent event
+category. This supports our first hypothesis.
+
+Surprisingly---and contrary to our second hypothesis---we saw consistent
+coupling between positive event count and social cohesion. Although both had a
+downward trajectory throughout the time period under consideration, RR was at or
+above chance in nearly all windows, and DET showed much more consistent shared
+trajectories than negative events. This may suggest that Syrian Twitter
+community was reacting more cohesively to the positive events aimed at Syria
+from the international community; this interpretation is supported by the
+attenuation of the effect in the analyses that include Syria as both a source
+and a target.
 
@@
 
-WCRQA of recurrence rate on the source and target filtered data remained
-largely the same for count of all events and social cohesion, suggesting
-that large numbers on a given day will be reflective of increased levels
-of social cohesion. DET showed more frequent above-chance metrics
-for windows 39 and up, suggesting that the inclusion of externally
-directed events lead to higher event counts during these days and then
-was more reflective of the level of social cohesion on Twitter.
-
-WCRQA metrics for positive-only and negative-only event counts with
-social cohesion remained largely the same for
-RR and DET as the source-only data. This may support the ideas suggested
-in the CRQA section, but again, only future work including the \emph{content}
-of those tweets can directly speak to that explanation.
-
-\hypertarget{implications}{%
-\subsection{Implications}\label{implications}}
-
-\hypertarget{implications-for-methodology}{%
-\subsubsection{Implications for Methodology}\label{implications-for-methodology}}
-
-Nonlinear methods have been transformative for a variety of research
-areas (including psychology, Coco \& Dale, 2014). One of the goals in the
-present work was to introduce variants of one kind of nonlinear
-method---specifically, recurrence quantification analysis---to
-this research area. While a number of excellent guides can provide
-detailed explanations of the methods and their statistical underpinnings
-(e.g., Riley \& Van Orden, 2005; Webber Jr \& Zbilut, 1994, 2005),
-one of the most important considerations that should be briefly
-summarized here is about data.
-
-Nonlinear methods---including recurrence-based analyses---require
-time series data. This requires repeated observations of the behavior
-at interest, preferably at a frequency that provides information
-about timing at a temporal resolution that allows the researcher to
-make observations about interesting variations over time. While
-this is easily controlled by scientists who conduct experimental
-research, it can be more difficult for scientists who rely on
-trace data or naturally occurring data. However, where possible,
-we recommend political scientists work to expand efforts for
-improving the temporal granularity of the data. One possible
-means of achieving this may be through collaborative efforts
-like the Open Event Data Alliance (Schrodt, Beieler, \& Idris, 2014).
-
-\hypertarget{implications-for-theory}{%
-\subsubsection{Implications for Theory}\label{implications-for-theory}}
-
-This methodology should be of great interest to social scientists investigating social mobilization.
-It has potential applications for gender studies and the \#MeToo movement, and for the relationship between social protest and repression during the Black Lives Matter protests.
-Fundamentally, this methodological approach can help us better understand the mechanisms underlying social media, and its influence on human behavior in real life.
-Given that many governments enact repressive measures when they determine that collective action by citizens has become an imminent possibility this methodology should help to improve the predictive power of using social media data in estimating repressive behavior.
-If social media messages are increasing in cohesion, this may represent a threat to civil and political liberties of citizens engaging in collective action.
+WCRQA on the source-and-target-filtered data showed similar patterns of RR
+between the count of all events and social cohesion (as observed in the
+target-only data), though the values increased. This suggests that large numbers
+on a given day match increased levels of social cohesion online. However, the
+results for DET changed: While the majority of statistically significant DET
+windows occurred toward the end of the observation period for target-only data
+(creating a positive trendline), the source-and-target data showed a negative
+trendline for DET.
+
+The divergences in the all-event count data for these two datasets underscores
+the differences between RR and DET. As noted earlier, DET captures
+\emph{trajectories}---in this case, similar to the impact of actions and social
+cohesion carrying across time. The same number of points (RR) can fall in
+different patterns (DET), providing important information about the structure of
+the system in question.
+
+WCRQA metrics for positive-only event counts with social cohesion showed similar
+patterns in RR and DET as the target-only data, but the precise values of DET
+and RR were diminished. This may support the ideas suggested in the CRQA
+section, but again, only future work including the \emph{content} of those tweets can
+directly speak to that explanation.
+
+Finally, the coupling between negative-only event counts and social cohesion
+also remained relatively similar but demonstrated some important differences.
+First, we see a greater number of windows at above-chance levels for RR,
+including an interesting spike around window 32 that suggests a negative
+externally focused action taken by Syria prompted a sharp rise in social
+cohesion. (This would not have been captured by the target-only dataset.)
+Second---like with the all-event data---we see different structuring of the data
+through differences in the patterns of DET; above-chance DET only occurrs within
+the middle of the observation period, around a time of increased strive (as
+noted above).
+
+\hypertarget{implications-for-methodology-and-theory}{%
+\subsection{Implications for Methodology and Theory}\label{implications-for-methodology-and-theory}}
+
+Nonlinear methods have been transformative for a variety of research areas
+(including psychology, Coco \& Dale, 2014). One of the goals in the present work was
+to introduce variants of one kind of nonlinear method---specifically, recurrence
+quantification analysis---to this research area. While a number of excellent
+guides can provide detailed explanations of the methods and their statistical
+underpinnings (e.g., Riley \& Van Orden, 2005; Webber Jr \& Zbilut, 1994, 2005), one of the most important considerations that should be
+briefly summarized here is about data.
+
+Nonlinear methods---including recurrence-based analyses---require time series
+data. This requires repeated observations of the behavior at interest,
+preferably at a frequency that provides information about timing at a temporal
+resolution that allows the researcher to make observations about interesting
+variations over time. While this is easily controlled by scientists who conduct
+experimental research, it can be more difficult for scientists who rely on trace
+data or naturally occurring data. However, where possible, we recommend
+political scientists work to expand efforts for improving the temporal
+granularity of the data. One possible means of achieving this may be through
+collaborative efforts like the Open Event Data Alliance (Schrodt, Beieler, \& Idris, 2014).
+
+This methodology should be of great interest to social scientists investigating
+social mobilization. It has potential applications for gender studies and
+the \#MeToo movement and for the relationship between social protest and repression
+during the Black Lives Matter protests. Fundamentally, this methodological
+approach can help us better understand the human social mechanisms underlying
+social media and its influence on human behavior in real life. Given that many
+governments enact repressive measures when they determine that collective action
+by citizens is imminent, this methodology should help to improve the predictive
+power of using social media data in estimating repressive behavior. If social
+media messages are increasing in cohesion, this may represent a threat to civil
+and political liberties of citizens engaging in collective action.
 
@@
 
-Considering the pervasiveness of social media, it is unsurprising
-that social activists and protesters have
-utilized these platforms to support real-world mobilization.
-Here, we quantitatively explored the connection
-between online social cohesion and real-world events. In addition
-to introducing political scientists to a family of powerful nonlinear
-dynamics analyses, our results have serious implications for monitoring global
-movements in consistent across other social uprisings. While traditional,
-state-run media in regions of authoritarian rule are often biased and
-propaganda for the leader and central government, the
-self-organized nature of Twitter poses a new avenue to gain insight into
-truths about up-risings and social mobilization. By conceptualizing Twitter
-and real-world events as two elements of an inextricably linked dynamical
-system, the levels of social cohesion within social media platforms could be
-monitored for fluctuations indicating shifts in power and peace. Social media
-mobilization may thus help alert the world to citizens' actions and reactions
-that are suppressed by government regimes, providing insight into events that
-may not otherwise be broadcast and allowing for faster intervention.
+Considering the pervasiveness of social media, it is unsurprising that social
+activists and protesters have utilized these platforms to support real-world
+mobilization. Here, we quantitatively explored the connection between online
+social cohesion and real-world events. In addition to introducing political
+scientists to a family of powerful nonlinear dynamics analyses, our results have
+serious implications for monitoring global movements in consistent across other
+social uprisings. While state-run media in regions of authoritarian rule are
+often biased and serve as propaganda for the leader and central government, the
+self-organized nature of Twitter provides a new avenue to gain insight into
+truths about uprisings and social mobilization. By conceptualizing Twitter and
+real-world events as two elements of an inextricably linked dynamical system,
+the levels of social cohesion within social media platforms could be monitored
+for fluctuations indicating shifts in power and peace. Social media mobilization
+may thus help alert the world to citizens' actions and reactions that are
+suppressed by government regimes, providing insight into events that may not
+otherwise be broadcast and allowing for faster intervention.
 
 \hypertarget{acknowledgements}{%
-\subsubsection{Acknowledgements}\label{acknowledgements}}
+\section{Acknowledgements}\label{acknowledgements}}
+
+This work was completed in part as coursework done by lead author M. Chiovaro in
+the \enquote{Applications of Nonlinear Time Series Analysis} graduate course at the
+University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
+Harrison).
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-anderson2011demystifying}{}%
+Anderson, L. (2011). Demystifying the Arab Spring: Parsing the differences between Tunisia, Egypt, and Libya. \emph{Foreign Aff.}, \emph{90}, 2.
+
+\leavevmode\hypertarget{ref-anyanwu2002economic}{}%
+Anyanwu, J. C. (2002). \emph{Economic and political causes of civil wars in Africa: Some econometric results}. African Development Bank Abidjan, Côte d'Ivoire.
+
+\leavevmode\hypertarget{ref-barash2012critical}{}%
+Barash, V., Cameron, C., \& Macy, M. (2012). Critical phenomena in complex contagions. \emph{Social Networks}, \emph{34}(4), 451--461.
+
+\leavevmode\hypertarget{ref-bohorquez2009common}{}%
+Bohorquez, J. C., Gourley, S., Dixon, A. R., Spagat, M., \& Johnson, N. F. (2009). Common ecology quantifies human insurgency. \emph{Nature}, \emph{462}(7275), 911--914.
+
 \leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
@@
 
+\leavevmode\hypertarget{ref-cederman2007beyond}{}%
+Cederman, L.-E., \& Girardin, L. (2007). Beyond fractionalization: Mapping ethnicity onto nationalist insurgencies. \emph{American Political Science Review}, \emph{101}(1), 173--185.
+
+\leavevmode\hypertarget{ref-centola2007complex}{}%
+Centola, D., \& Macy, M. (2007). Complex contagions and the weakness of long ties. \emph{American Journal of Sociology}, \emph{113}(3), 702--734.
+
 \leavevmode\hypertarget{ref-coco2014cross}{}%
@@
 
+\leavevmode\hypertarget{ref-collier2004greed}{}%
+Collier, P., \& Hoeffler, A. (2004). Greed and grievance in civil war. \emph{Oxford Economic Papers}, \emph{56}(4), 563--595.
+
 \leavevmode\hypertarget{ref-collins2009violence}{}%
@@
 Durkheim, E. (1995). The elementary forms of religious life, terj. Karen e. Fields. \emph{New York: Free Press.}, \emph{42}, 651669.
+
+\leavevmode\hypertarget{ref-edgar2018struggle}{}%
+Edgar, A. N., \& Johnson, A. E. (2018). \emph{The struggle over black lives matter and all lives matter}. Rowman \& Littlefield.
+
+\leavevmode\hypertarget{ref-eisinger1973conditions}{}%
+Eisinger, P. K. (1973). The conditions of protest behavior in american cities. \emph{American Political Science Review}, \emph{67}(1), 11--28.
+
+\leavevmode\hypertarget{ref-fink2016complex}{}%
+Fink, C., Schmidt, A., Barash, V., Cameron, C., \& Macy, M.
+(2016).
+Complex contagions and the diffusion of popular twitter hashtags in nigeria.
+\emph{Social Network Analysis and Mining}, \emph{6}(1), 1.
+
+\leavevmode\hypertarget{ref-francisco1995relationship}{}%
+Francisco, R. A. (1995). The relationship between coercion and protest: An empirical evaluation in three coercive states. \emph{Journal of Conflict Resolution}, \emph{39}(2), 263--282.
+
+\leavevmode\hypertarget{ref-fusaroli2012coming}{}%
+Fusaroli, R., Bahrami, B., Olsen, K., Roepstorff, A., Rees, G., Frith, C., \& Tylén, K.
+(2012).
+Coming to terms: Quantifying the benefits of linguistic coordination.
+\emph{Psychological Science}, \emph{23}(8), 931--939.
 
@@
 
+\leavevmode\hypertarget{ref-gates2002recruitment}{}%
+Gates, S. (2002). Recruitment and allegiance: The microfoundations of rebellion. \emph{Journal of Conflict Resolution}, \emph{46}(1), 111--130.
+
 \leavevmode\hypertarget{ref-gilligan2014civil}{}%
@@
 
+\leavevmode\hypertarget{ref-gladwell2010revolution}{}%
+Gladwell, M. (2010). Why the revolution will not be tweeted. \emph{The New Yorker}, \emph{4}(2010), 42--49.
+
+\leavevmode\hypertarget{ref-gohdes2015pulling}{}%
+Gohdes, A. R. (2015). Pulling the plug: Network disruptions and violence in civil conflict. \emph{Journal of Peace Research}, \emph{52}(3), 352--367.
+
+\leavevmode\hypertarget{ref-goldstein1992conflict}{}%
+Goldstein, J. S. (1992). A conflict-cooperation scale for WEIS events data. \emph{Journal of Conflict Resolution}, \emph{36}(2), 369--385.
+
+\leavevmode\hypertarget{ref-goldstone1980theories}{}%
+Goldstone, J. A. (1980). Theories of revolution: The third generation. \emph{World Politics}, \emph{32}(3), 425--453.
+
+\leavevmode\hypertarget{ref-goldstone2011understanding}{}%
+Goldstone, J. A. (2011). Understanding the revolutions of 2011: Weakness and resilience in Middle Eastern autocracies. \emph{Foreign Affairs}, 8--16.
+
 \leavevmode\hypertarget{ref-gonzales2010language}{}%
@@
 
+\leavevmode\hypertarget{ref-graesser2004coh}{}%
+Graesser, A.
+C., McNamara, D.
+S., Louwerse, M.
+M., \& Cai, Z.
+(2004).
+Coh-Metrix: Analysis of text on cohesion and language.
+\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{36}(2), 193--202.
+
+\leavevmode\hypertarget{ref-granovetter1977strength}{}%
+Granovetter, M. S. (1973). The strength of weak ties. In \emph{American Journal of Sociology} (Vol. 78, pp. 1360--1380). JSTOR.
+
 \leavevmode\hypertarget{ref-grenander1959probability}{}%
@@
 
+\leavevmode\hypertarget{ref-gurr2000peoples}{}%
+Gurr, T. R. (2000). \emph{Peoples versus states: Minorities at risk in the new century}. US Institute of Peace Press.
+
+\leavevmode\hypertarget{ref-halliday1976cohesion}{}%
+Halliday, M. A. K., \& Hasan, R. (1976). \emph{Cohesion in English}. Longman, London.
+
+\leavevmode\hypertarget{ref-Hoffer2011true}{}%
+Hoffer, E. (2011). \emph{The true believer: Thoughts on the nature of mass movements}. Harper Collins.
+
 \leavevmode\hypertarget{ref-jones1972statistical}{}%
@@
 
+\leavevmode\hypertarget{ref-king2013censorship}{}%
+King, G., Pan, J., \& Roberts, M. E. (2013). How censorship in China allows government criticism but silences collective expression. \emph{American Political Science Review}, \emph{107}(2), 326--343.
+
 \leavevmode\hypertarget{ref-koehler2017political}{}%
@@
 
+\leavevmode\hypertarget{ref-koopmans2004movements}{}%
+Koopmans, R. (2004). Movements and media: Selection processes and evolutionary dynamics in the public sphere. \emph{Theory and Society}, \emph{33}(3-4), 367--391.
+
 \leavevmode\hypertarget{ref-lutterbeck2013arab}{}%
@@
 Mahner, M., \& Bunge, M. (1997). \emph{Foundations of biophilosophy}. Springer Science \& Business Media.
+
+\leavevmode\hypertarget{ref-mcadam1986recruitment}{}%
+McAdam, D. (1986). Recruitment to high-risk activism: The case of freedom summer. \emph{American Journal of Sociology}, \emph{92}(1), 64--90.
+
+\leavevmode\hypertarget{ref-mcadam1993specifying}{}%
+McAdam, D., \& Paulsen, R. (1993). Specifying the relationship between social ties and activism. \emph{American Journal of Sociology}, \emph{99}(3), 640--667.
+
+\leavevmode\hypertarget{ref-mcadam2003dynamics}{}%
+McAdam, D., Tarrow, S., \& Tilly, C. (2003). Dynamics of contention. \emph{Social Movement Studies}, \emph{2}(1), 99--102.
+
+\leavevmode\hypertarget{ref-mcnamara2014automated}{}%
+McNamara, D. S., Graesser, A. C., McCarthy, P. M., \& Cai, Z. (2014). \emph{Automated evaluation of text and discourse with Coh-Metrix}. Cambridge University Press.
 
@@
 
+\leavevmode\hypertarget{ref-niederhoffer2002linguistic}{}%
+Niederhoffer, K. G., \& Pennebaker, J. W. (2002). Linguistic style matching in social interaction. \emph{Journal of Language and Social Psychology}, \emph{21}(4), 337--360.
+
+\leavevmode\hypertarget{ref-olson1965logic}{}%
+Olson, M. (1965). \emph{The logic of collective action}. Harvard University Press.
+
 \leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
@@
 
+\leavevmode\hypertarget{ref-regan2005greed}{}%
+Regan, P. M., \& Norton, D. (2005). Greed, grievance, and mobilization in civil wars. \emph{Journal of Conflict Resolution}, \emph{49}(3), 319--336.
+
 \leavevmode\hypertarget{ref-riley2005tutorials}{}%
@@
 
+\leavevmode\hypertarget{ref-riordan2011evidence}{}%
+Riordan, M., Dale, R., Kreuz, R., \& Olney, A.
+(2011).
+Evidence for alignment in a computer-mediated text-only environment.
+In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol.
+33).
+
 \leavevmode\hypertarget{ref-robertson2004understanding}{}%
 Robertson, S. (2004). Understanding inverse document frequency: On theoretical arguments for idf. \emph{Journal of Documentation}.
+
+\leavevmode\hypertarget{ref-sambanis2009s}{}%
+Sambanis, N., \& Schulhofer-Wohl, J. (2009). What's in a line? Is partition a solution to civil war? \emph{International Security}, \emph{34}(2), 82--118.
 
@@
 
+\leavevmode\hypertarget{ref-schrodt2006twenty}{}%
+Schrodt, P. A., \& Hall, B. (2006). Twenty years of the Kansas event data system project. \emph{The Political Methodologist}, \emph{14}(1), 2--8.
+
+\leavevmode\hypertarget{ref-seay2014slacktivism}{}%
+Seay, L. (2014). Does slacktivism work? \emph{The Washington Post}, \emph{12}.
+
 \leavevmode\hypertarget{ref-spaaij2014sports}{}%
@@
 
+\leavevmode\hypertarget{ref-state2015diffusion}{}%
+State, B., \& Adamic, L.
+(2015).
+The diffusion of support in an online social movement: Evidence from the adoption of equal-sign profile pictures.
+In \emph{Proceedings of the 18th acm conference on computer supported cooperative work \& social computing} (pp.
+1741--1750).
+
+\leavevmode\hypertarget{ref-steinert2017spontaneous}{}%
+Steinert-Threlkeld, Z. C. (2017). Spontaneous collective action: Peripheral mobilization during the Arab Spring. \emph{American Political Science Review}, \emph{111}(2), 379--403.
+
 \leavevmode\hypertarget{ref-tausczik2010psychological}{}%
@@
 
+\leavevmode\hypertarget{ref-tilly2004contentious}{}%
+Tilly, C. (2004). Contentious choices. \emph{Theory and Society}, \emph{33}(3-4), 473--481.
+
 \leavevmode\hypertarget{ref-turvey2018lectures}{}%
@@
 Vicari, S. (2013). Public reasoning around social contention: A case study of Twitter use in the Italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
+
+\leavevmode\hypertarget{ref-walton2012mere}{}%
+Walton, G. M., Cohen, G. L., Cwir, D., \& Spencer, S. J. (2012). Mere belonging: The power of social connections. \emph{Journal of Personality and Social Psychology}, \emph{102}(3), 513.
 
@@
 
+\leavevmode\hypertarget{ref-wiltermuth2009synchrony}{}%
+Wiltermuth, S. S., \& Heath, C. (2009). Synchrony and cooperation. \emph{Psychological Science}, \emph{20}(1), 1--5.
+
+\leavevmode\hypertarget{ref-Windsor2020}{}%
+Windsor, L. (2020). Advancing interdisciplinary work in computational communication science. \emph{Political Communication}.
+
 \leavevmode\hypertarget{ref-zbilut1998detecting}{}%
@@
 
+\leavevmode\hypertarget{ref-zeitzoff2011using}{}%
+Zeitzoff, T. (2011). Using social media to measure conflict dynamics: An application to the 2008--2009 Gaza conflict. \emph{Journal of Conflict Resolution}, \emph{55}(6), 938--969.
+
+\leavevmode\hypertarget{ref-zeitzoff2017social}{}%
+Zeitzoff, T. (2017). How social media is changing conflict. \emph{Journal of Conflict Resolution}, \emph{61}(9), 1970--1991.
+
 \endgroup

### 2020-06-01 manuscript.Rmd
Fix wrapping
Fix reference

@@
   coupled with the counts of all and negative events each day but shows a more
-  nuanced connection to positive events, only visible when examining finer-grained
-  data. This suggests that virtual mobilization does reflect
+  nuanced connection to positive events, only visible when examining
+  finer-grained data. This suggests that virtual mobilization does reflect
   real-world movements, with the strongest connections to the frequency of all
-  events and the frequency of negative events. We
-  conclude with a discussion of implications and applications of nonlinear
-  methods in political science research.
+  events and the frequency of negative events. We conclude with a discussion of
+  implications and applications of nonlinear methods in political science
+  research.
   <!-- https://tinyurl.com/ybremelq -->
@@
 Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and mimeographed flyers,
-through in-person meetings of social organizations and churches, and through
-word of mouth. They gathered together and hand-made protest signs that reflected
-their agendas. As McAdam found, people were more likely to join movements when
-they had a personal connection [@mcadam1986recruitment; @mcadam1993specifying]:
-Historically, strong ties have been
-strong predictors of involvement in high-risk protest activity.
-
-The cohesiveness and strength of social movements in the pre-Internet era could be
-operationalized by the number of people turning out to protest and through the
-political events that precipitated and resulted from social gatherings *en masse*.
-The content of placards and protest
-signs provided the protest narrative in their own words. Cohesive
-social movements were reflected in their cohesive placards and posters. For
-example, the “I am a man” posters held by the men involved in the 1968
-sanitation workers' strike reflected their internal cohesion and unified,
-goal-oriented movement [@Windsor2020].
-
-However, the rise of the Internet and its decentralized online networks
-has upended theories about recruitment to---and participation in---social
-movements. Strong interpersonal ties have yielded to weak impersonal ties that
-strongly predict involvement in social movements [@steinert2017spontaneous]. Research
+using phone tree calling sheets and mimeographed flyers, through in-person
+meetings of social organizations and churches, and through word of mouth. They
+gathered together and hand-made protest signs that reflected their agendas. As
+McAdam found, people were more likely to join movements when they had a personal
+connection [@mcadam1986recruitment; @mcadam1993specifying]: Historically, strong
+ties have been strong predictors of involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements in the pre-Internet era could
+be operationalized by the number of people turning out to protest and through
+the political events that precipitated and resulted from social gatherings *en
+masse*. The content of placards and protest signs provided the protest narrative
+in their own words. Cohesive social movements were reflected in their cohesive
+placards and posters. For example, the “I am a man” posters held by the men
+involved in the 1968 sanitation workers' strike reflected their internal
+cohesion and unified, goal-oriented movement [@Windsor2020].
+
+However, the rise of the Internet and its decentralized online networks has
+upended theories about recruitment to---and participation in---social movements.
+Strong interpersonal ties have yielded to weak impersonal ties that strongly
+predict involvement in social movements [@steinert2017spontaneous]. Research
 methodologies for measuring social movements have similarly evolved from
@@
 
-Today, social media replicates and amplifies
-this phenomenon during moments of social unrest. Amid the cacophony of messages
-during political upheaval---such as the Arab Spring---consistent themes emerge
-through hashtags, retweets, and the repeated mentions of concepts such as
-regime, security, demonstration, and human rights. The cohesiveness of these
-themes (i.e., whether movement participants are metaphorically singing in one voice)
-reflects the real-world events happening contemporaneously with collective action in
-social movements or civil conflicts.
+Today, social media replicates and amplifies this phenomenon during moments of
+social unrest. Amid the cacophony of messages during political upheaval---such
+as the Arab Spring---consistent themes emerge through hashtags, retweets, and
+the repeated mentions of concepts such as regime, security, demonstration, and
+human rights. The cohesiveness of these themes (i.e., whether movement
+participants are metaphorically singing in one voice) reflects the real-world
+events happening contemporaneously with collective action in social movements or
+civil conflicts.
 
@@
 question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does
-social media reflect on-the-ground realities during times of social conflict?
-To do so, we examine patterns of linguistic cohesion on Twitter and their
-connection to real-world events during
-the Arab Spring uprising in Syria between March and June 2012.
-
-Disentangling the complicated relationship between mass online mobilization---and
-social mobilization in person---continues to be relevant, even as our modes
-of communication change. The
-political processes that transpired during and after the Arab Spring are still
-in the process of being understood. As Zeitzoff [-@zeitzoff2017social] recognizes,
-social media is changing conflict, but the mechanisms and relationships by
-which it does so are still being understood.
+social media reflect on-the-ground realities during times of social conflict? To
+do so, we examine patterns of linguistic cohesion on Twitter and their
+connection to real-world events during the Arab Spring uprising in Syria between
+March and June 2012.
+
+Disentangling the complicated relationship between mass online
+mobilization---and social mobilization in person---continues to be relevant,
+even as our modes of communication change. The political processes that
+transpired during and after the Arab Spring are still in the process of being
+understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
+changing conflict, but the mechanisms and relationships by which it does so are
+still being understood.
 
@@
 Following a wave of democratization efforts across the Middle East and North
-Africa, modest Syrian protests began in March 2011. The regime responded
-harshly with imprisonments, detentions, censorship, and military operations as
-the resistance to Assad’s regime grew and spread throughout the country. The
+Africa, modest Syrian protests began in March 2011. The regime responded harshly
+with imprisonments, detentions, censorship, and military operations as the
+resistance to Assad’s regime grew and spread throughout the country. The
 fighting escalated dramatically in March 2012, after increased unrest in the
-western city of Homs. International actors---including the Red Cross/Red Crescent
-Society, the United Nations General Assembly, the Security Council, and
-individual world leaders---worked toward cease-fires, negotiations,
-and concessions without much success. While many high-level military and
-diplomatic officials defected from the regime, numerous loyal forces
-continued the regime's repression, and the Syrian people turned to social
-media to help coordinate their activism and communicate to the world. Between March and
-June 2012, more than 8 million tweets were sent within Syria, revealing the
-details of the conflict suppressed by the government.
+western city of Homs. International actors---including the Red Cross/Red
+Crescent Society, the United Nations General Assembly, the Security Council, and
+individual world leaders---worked toward cease-fires, negotiations, and
+concessions without much success. While many high-level military and diplomatic
+officials defected from the regime, numerous loyal forces continued the regime's
+repression, and the Syrian people turned to social media to help coordinate
+their activism and communicate to the world. Between March and June 2012, more
+than 8 million tweets were sent within Syria, revealing the details of the
+conflict suppressed by the government.
 
@@
 people make up between 10-15% of the population, Alawites between 8-15%,
-Christians about 10%. There are also much smaller sects (e.g., Ismailis,
-Druze), but Sunni Muslims comprise the vast majority of society. Most people
-speak Arabic as their primary language. Most policy reports addressing the current
+Christians about 10%. There are also much smaller sects (e.g., Ismailis, Druze),
+but Sunni Muslims comprise the vast majority of society. Most people speak
+Arabic as their primary language. Most policy reports addressing the current
 conflict report on the cohesion of the ruling Alawite military elite, rather
@@
 
-Massive online social cohesion can have real-world social
-manifestations. Social media platforms provide one way to enable this kind of
-online social cohesion by offering distributed information-gathering and
-real-time information dissemination. Given its accessibility and proficiency as
-an information exchange tool, Twitter has provided individuals involved in
-social movements an opportunity to complement or even replace real-world social
-mobilization. For example, during the 2012 Italian protests for global economic
-change, the riots in Rome were mirrored by Twitter activity both on the day of
-the protests and in the days following them [@vicari2013public]. Tweeting was
-determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more individuals
-rely on social media to obtain local news and information, it becomes
-increasingly important to understand just how these micro-blogs reflect
-real-world action.
+Massive online social cohesion can have real-world social manifestations. Social
+media platforms provide one way to enable this kind of online social cohesion by
+offering distributed information-gathering and real-time information
+dissemination. Given its accessibility and proficiency as an information
+exchange tool, Twitter has provided individuals involved in social movements an
+opportunity to complement or even replace real-world social mobilization. For
+example, during the 2012 Italian protests for global economic change, the riots
+in Rome were mirrored by Twitter activity both on the day of the protests and in
+the days following them [@vicari2013public]. Tweeting was determined to be more
+effective locally in discussing real-world, real-time events than traditional
+mainstream media platforms. As more and more individuals rely on social media to
+obtain local news and information, it becomes increasingly important to
+understand just how these micro-blogs reflect real-world action.
 
@@
 
-Along with Facebook, Twitter has been
-credited as essential to the Arab Spring---both for protesters (as a means to
-coordinate with one another and to communicate with the world) and for the
-government response (to monitor and track protestors to crack down on dissent)
-[@comninos2011twitter]. The events of Arab Spring have been thoroughly discussed
-within the political science literature [e.g., @lutterbeck2013arab;
+Along with Facebook, Twitter has been credited as essential to the Arab
+Spring---both for protesters (as a means to coordinate with one another and to
+communicate with the world) and for the government response (to monitor and
+track protestors to crack down on dissent) [@comninos2011twitter]. The events of
+Arab Spring have been thoroughly discussed within the political science
+literature [e.g., @lutterbeck2013arab;
 @koehler2017political], but to our knowledge, the direct *coupling* between
 Syrian Twitter cohesion and international action coordination has not been
-investigated. In fact, some have been skeptical about the effect of social media on
-collective action at all [@seay2014slacktivism].
+investigated. In fact, some have been skeptical about the effect of social media
+on collective action at all [@seay2014slacktivism].
 
@@
 
-Social media generates critical information about events, including whether and how
-a demonstration will take place, how many
-people participate, and how those in power (e.g., state, military, security apparatus)
-respond. Similarly, these media platforms alert us to more global shifts within
-a conflict, such as when fighting moves to a new city or region, the number of
-casualties and wounded, and the types of weaponry used by parties to the
-conflict [@zeitzoff2017social]. Social media is not entirely event-driven, however.
-In monitoring social media channels, government forces may respond to the
-perception that citizens are gaining strength and sympathy. Governments have
-been shown to be quite tolerant of dissent so long as it does not metamorphose
-into collective action [@king2013censorship].
+Social media generates critical information about events, including whether and
+how a demonstration will take place, how many people participate, and how those
+in power (e.g., state, military, security apparatus) respond. Similarly, these
+media platforms alert us to more global shifts within a conflict, such as when
+fighting moves to a new city or region, the number of casualties and wounded,
+and the types of weaponry used by parties to the conflict [@zeitzoff2017social].
+Social media is not entirely event-driven, however. In monitoring social media
+channels, government forces may respond to the perception that citizens are
+gaining strength and sympathy. Governments have been shown to be quite tolerant
+of dissent so long as it does not metamorphose into collective action
+[@king2013censorship].
 
@@
 phones and computers with Internet connectivity, providing a stream of real-time
-shared information. Citizens can share the location of events like protests and military
-incursions, the degree of state repression, and the number of casualties. In
-turn, the government---interested in remaining in power---monitors social media
-platforms to ascertain emerging threats [@comninos2011twitter],
-such as where new groups are forming
-and where existing groups are strengthening, where gatherings are held, and who
-the idea entrepreneurs are. An example of a leader
-expressing his interest in
-such public conversation is given by Bashar al-Assad in a speech on June 3, 2012:
+shared information. Citizens can share the location of events like protests and
+military incursions, the degree of state repression, and the number of
+casualties. In turn, the government---interested in remaining in
+power---monitors social media platforms to ascertain emerging threats
+[@comninos2011twitter], such as where new groups are forming and where existing
+groups are strengthening, where gatherings are held, and who the idea
+entrepreneurs are. An example of a leader expressing his interest in such public
+conversation is given by Bashar al-Assad in a speech on June 3, 2012:
 
@@
 With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth of social
-protest online and in the streets by shutting down the Internet.
+Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
+of social protest online and in the streets by shutting down the Internet.
 During these times, however, she finds that military repression increases.
@@
 
-At the same time, the insulation
-of online social platforms allows researchers to detail real-world social dynamics
-at unprecedented resolution and scale [@paxton2017finding]. The digital traces left by
-individuals and collectively as groups are regarded as a valuable source of
-information that can offer powerful insights into states of social
-disequilibrium, uprisings, and escalations into civil wars.
-By examining these conversations, researchers can study the degree of cohesion between
-speakers and the alignment between that cohesion and their collective political
-behavior.
+At the same time, the insulation of online social platforms allows researchers
+to detail real-world social dynamics at unprecedented resolution and scale
+[@paxton2017finding]. The digital traces left by individuals and collectively as
+groups are regarded as a valuable source of information that can offer powerful
+insights into states of social disequilibrium, uprisings, and escalations into
+civil wars. By examining these conversations, researchers can study the degree
+of cohesion between speakers and the alignment between that cohesion and their
+collective political behavior.
 
@@
 the development of protest movements in some instances and constrain them in
-others” [@Kitschelt_1986]. What emerges as strategies and tactics in contentious
-politics are, in essence, a function of what the system makes possible. This
-includes the number of people and their disposition (i.e. nonviolent or
-violent), as well as their internal structure. The more cohesive a group is, the
-greater threat they pose to the establishment.
+others” [@kitschelt1986political]. What emerges as strategies and tactics in
+contentious politics are, in essence, a function of what the system makes
+possible. This includes the number of people and their disposition (i.e.
+nonviolent or violent), as well as their internal structure. The more cohesive a
+group is, the greater threat they pose to the establishment.
 
@@
 
-Another factor influencing social cohesion during social movements and
-civil wars is ethnic identity and the degree of ethnic conflict associated with
-the movement. Greater degrees of ethnic conflict increase the salience of
-ethnic identity, leading people to identify more strongly with their own
-ethnic identity [@sambanis2009s]. As ethnic conflict
-intensifies, groups seek to become more quintessentially like the typical
-member of their ethnic group. This can manifest in a number of ways, including
-in behavior on social media. However, this may also include a general identification
-across ethnic groups in a membership of an opposition to an oppressive leader.
+Another factor influencing social cohesion during social movements and civil
+wars is ethnic identity and the degree of ethnic conflict associated with the
+movement. Greater degrees of ethnic conflict increase the salience of ethnic
+identity, leading people to identify more strongly with their own ethnic
+identity [@sambanis2009s]. As ethnic conflict intensifies, groups seek to become
+more quintessentially like the typical member of their ethnic group. This can
+manifest in a number of ways, including in behavior on social media. However,
+this may also include a general identification across ethnic groups in a
+membership of an opposition to an oppressive leader.
 
@@
 
-We contextualize linguistic cohesion with social mobilization and response to the relative
-intensity of the conflict. Cohesion is a multi-layered concept referring to the
-connectedness of speakers, actions, and societies. Cohesion reflects the
-continuity of language and expression, and it shows the connectivity of
-participants in a social movement. To address the relationship between language
-and discourse and social movements, we adopt an interdisciplinary approach that
-incorporates linguistics, psychology, and political science using nonlinear
-dynamical systems methodology to model the relationship between language and
-action.
+We contextualize linguistic cohesion with social mobilization and response to
+the relative intensity of the conflict. Cohesion is a multi-layered concept
+referring to the connectedness of speakers, actions, and societies. Cohesion
+reflects the continuity of language and expression, and it shows the
+connectivity of participants in a social movement. To address the relationship
+between language and discourse and social movements, we adopt an
+interdisciplinary approach that incorporates linguistics, psychology, and
+political science using nonlinear dynamical systems methodology to model the
+relationship between language and action.
 
@@
 Just as real-world social cohesion can be quantified, so can online cohesion.
-One kind of cohesion can be found in
-the similarity in language use on social media. This implicit or explicit
-similarity in language use can indicate shared beliefs, thoughts, and feelings,
-as has been studied in research on language style in psycholinguistics and
-social psychology [@gonzales2010language; @tausczik2010psychological;
+One kind of cohesion can be found in the similarity in language use on social
+media. This implicit or explicit similarity in language use can indicate shared
+beliefs, thoughts, and feelings, as has been studied in research on language
+style in psycholinguistics and social psychology [@gonzales2010language;
+@tausczik2010psychological;
 @brennan1996conceptual]. Although previous work on language style has often
@@
 we will consider.  In Figure \@ref(fig:cohesion-in-tweets), we see four
-sequential tweets, each containing four words.
-Each sequential tweet contains some content included in the previous tweets. The
-linguistic construct of content word overlap measures the relationship across
-units of meaning---here, tweets---where identical and semantically similar words
-are repeated [@graesser2004coh]. These repeated lexical
-items constitute a theme; on Twitter, this might be a particular hashtag, a
-name, a location, or other nominal category. This localized cohesion is
-referential; words are repeated and co-referred across tweets, creating a sense
-of continuity and cohesiveness of meaning and message.
+sequential tweets, each containing four words. Each sequential tweet contains
+some content included in the previous tweets. The linguistic construct of
+content word overlap measures the relationship across units of meaning---here,
+tweets---where identical and semantically similar words are repeated
+[@graesser2004coh]. These repeated lexical items constitute a theme; on Twitter,
+this might be a particular hashtag, a name, a location, or other nominal
+category. This localized cohesion is referential; words are repeated and
+co-referred across tweets, creating a sense of continuity and cohesiveness of
+meaning and message.
 
@@
 @mcadam1986recruitment], strengthening the movement overall by expanding and
-deepening heterogenous ties. Therefore,
-in the context of social conflict, the linguistic cohesion
-of the online conversation should correspond to the degree of
-social cohesion on the ground.
+deepening heterogenous ties. Therefore, in the context of social conflict, the
+linguistic cohesion of the online conversation should correspond to the degree
+of social cohesion on the ground.
 
@@
 cohesion is thus potentially an indicator and a result of increased social
-organization and mobilization on the ground. However, this occurs within a context
-that is affected by local and international events; both
-exogenous events (like intervention by another country or
-international organization like the United Nations) and 
-endogenous events (like the recruitment of new members to the rebel or
-resistance movement) can affect cohesion.
-
-From a dynamical systems perspective, online social cohesion and
-in-person action can be considered two complementary
-components of a single system, mutually constrained and constantly interacting
-and influencing one another [@mahner1997foundations]. Investigation of the
-coupling of real-world mobilization and social cohesion could provide new
-insight into the power of social media during mobilization and the ways in which
-individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social
-mobilization [@mcadam2003dynamics; @koopmans2004movements], 
-but the relationship between virtual and real-world mobilization
-is still largely unknown. The present work aims to understand how physical and
-virtual movements coexist and interact from a dynamical systems perspective.
+organization and mobilization on the ground. However, this occurs within a
+context that is affected by local and international events; both exogenous
+events (like intervention by another country or international organization like
+the United Nations) and endogenous events (like the recruitment of new members
+to the rebel or resistance movement) can affect cohesion.
+
+From a dynamical systems perspective, online social cohesion and in-person
+action can be considered two complementary components of a single system,
+mutually constrained and constantly interacting and influencing one another
+[@mahner1997foundations]. Investigation of the coupling of real-world
+mobilization and social cohesion could provide new insight into the power of
+social media during mobilization and the ways in which individuals utilize it to
+bring about, or respond to, social change. Increasingly, social media platforms
+are being utilized during social mobilization [@mcadam2003dynamics;
+@koopmans2004movements], but the relationship between virtual and real-world
+mobilization is still largely unknown. The present work aims to understand how
+physical and virtual movements coexist and interact from a dynamical systems
+perspective.
 

### 2020-06-01 manuscript.Rmd
Add raw time series figure for social cohesion

@@
 participate. Given that people are generally risk-averse, overcoming inertia
-requires a strong connection to the group identity or a strong aversion to an individual,
-event, or political injustice [@goldstone1980theories; @goldstone2011understanding].
-Political resistance offers participants the opportunity to “lose themselves” and
-relinquish their individual identity in favor of identification with a larger
-group identity, contributing to a cohesive group ready and mobilized for
-action [@Hoffer2011true].
+requires a strong connection to the group identity or a strong aversion to an
+individual, event, or political injustice [@goldstone1980theories;
+@goldstone2011understanding]. Political resistance offers participants the
+opportunity to “lose themselves” and relinquish their individual identity in
+favor of identification with a larger group identity, contributing to a cohesive
+group ready and mobilized for action [@Hoffer2011true].
 
@@
 
-```{r tweet-count, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
-
-# read in social cohesion data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
-
-```
-
 The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
@@
 analysis.
+
+The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion).
+
+```{r raw-cohesion-ts, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw social cohesion metric time series."}
+
+# read in social cohesion data
+cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+
+# plot time series
+raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
+  geom_point() +
+  geom_line() +
+  xlab("Date") +
+  ylab("Mean Social Cohesion")
+ggsave("./results/primary/raw-cohesion-ts.png")
+
+# call the image
+knitr::include_graphics("./results/primary/raw-cohesion-ts.png")
+
+```
 
@@
 #### Metrics
-For WCRQA analyses, we decided to focus on RR and DET.
+For WCRQA analyses, we decided to focus on RR and DET, but WCRQA visualization can be done for any metric desired.
 

### 2020-06-02 manuscript.Rmd
Add raw event time series plots

@@
 
-The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion).
+The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
 
@@
 day that had an intensity rating less than zero.
+
+The raw event time series for target filtered data can be seen in Figure \@ref(fig:raw-event-ts-target).
+The The raw event time series for source and target filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).
+
+```{r raw-event-ts-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw event count time series for target filtered data."}
+
+# read in social cohesion data
+event_df <- read.csv("./data/formatted/primary/formatted_data.csv")
+
+# plot the time series
+ggplot() +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
+  scale_color_manual(values = c("red", "orange", "blue")) +
+  xlab("Date") +
+  ylab("Number of events") +
+  ylim(0, 360)
+
+ggsave("./results/primary/raw-event-ts-target.png")
+
+# call the image
+knitr::include_graphics("./results/primary/raw-event-ts-target.png")
+
+```
+
+```{r raw-event-ts-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw event count time series for source and target filtered data."}
+
+# plot the time series
+ggplot() +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
+  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
+  scale_color_manual(values = c("red", "orange", "blue")) +
+  xlab("Date") +
+  ylab("Number of events") +
+  ylim(0, 360)
+
+ggsave("./results/primary/raw-event-ts-source-target.png")
+
+# call the image
+knitr::include_graphics("./results/primary/raw-event-ts-source-target.png")
+
+```
 

### 2020-06-02 manuscript.Rmd
Trim abstract to 150 words

@@
 abstract: |
-  Social mobilization requires effective collective coordination. In recent
-  years, individuals involved in social movements have taken to social media
-  platforms to reach broader audiences at rapid speeds. Effective virtual
-  mobilization similarly requires social cohesion and coordination, yet the
-  degree to which virtual mobilization reflects or drives real-world movements
-  is unclear. Here, we explore the dynamics of real-world events and social
-  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear
-  methods cross-recurrence quantification analysis and windowed cross-recurrence
-  quantification analysis, we investigate if counts of all daily events, daily
-  positive events, and daily negative events are coupled with social cohesion
-  found in Syrian tweets. Results indicate that virtual social cohesion is
-  coupled with the counts of all and negative events each day but shows a more
-  nuanced connection to positive events, only visible when examining
-  finer-grained data. This suggests that virtual mobilization does reflect
-  real-world movements, with the strongest connections to the frequency of all
-  events and the frequency of negative events. We conclude with a discussion of
-  implications and applications of nonlinear methods in political science
-  research.
+  In recent years, individuals involved in social movements have taken to social
+  media platforms to reach broader audiences at rapid speeds. Although
+  micro-blogging has become a primary means of information dissemination during
+  times of turmoil, the degree to which virtual mobilization reflects or drives
+  real-world movements is unclear. Here, we explore the dynamics of real-world
+  events and Twitter social cohesion in Syria during the Arab Spring. Using the
+  nonlinear methods cross-recurrence quantification analysis and windowed
+  cross-recurrence quantification analysis, we investigate if frequency of
+  events of different intensities are coupled with social cohesion found in
+  Syrian tweets. Results indicate that virtual social cohesion is coupled with
+  the counts of all and negative events each day but shows a more nuanced
+  connection to positive events, suggesting that virtual mobilization does
+  reflect real-world movements. We conclude with a discussion of implications
+  and applications of nonlinear methods in political science research.
   <!-- https://tinyurl.com/ybremelq -->
@@
 # plot the time series
-ggplot() +
+raw_events_ts_target <- ggplot() +
   geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
@@
 # plot the time series
-ggplot() +
+raw_events_ts_source_target <- ggplot() +
   geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +

### 2020-06-02 manuscript.Rmd
Edits to intro

@@
 the political events that precipitated and resulted from social gatherings *en
-masse*. The content of placards and protest signs provided the protest narrative
-in their own words. Cohesive social movements were reflected in their cohesive
-placards and posters. For example, the “I am a man” posters held by the men
-involved in the 1968 sanitation workers' strike reflected their internal
-cohesion and unified, goal-oriented movement [@Windsor2020].
+masse*. Cohesive social movements were reflected in their cohesive placards and
+posters. For example, the “I am a man” posters held by the men involved in the
+1968 sanitation workers' strike reflected their internal cohesion and unified,
+goal-oriented movement [@Windsor2020].
 
@@
 mobilization---and social mobilization in person---continues to be relevant,
-even as our modes of communication change. The political processes that
+even as our modes of communication change. The political events that
 transpired during and after the Arab Spring are still in the process of being

### 2020-06-02 manuscript.Rmd
Slight phrasing edit
More formatting and typos

@@
 with imprisonments, detentions, censorship, and military operations as the
-resistance to Assad’s regime grew and spread throughout the country. The
+resistance to Assad's regime grew and spread throughout the country. The
 fighting escalated dramatically in March 2012, after increased unrest in the
@@
 
-Others have similarly expressed hesitation about the role of online
+\noindent Others have similarly expressed hesitation about the role of online
 organizing. Some have argued that real-life strong ties outweigh online weak ties and
@@
 groups are strengthening, where gatherings are held, and who the idea
-entrepreneurs are. An example of a leader expressing his interest in such public
+entrepreneurs are.
+
+An example of a leader expressing his interest in such public
 conversation is given by Bashar al-Assad in a speech on June 3, 2012:
@@
 
-With few exceptions, Assad chose to keep social media platforms up and running.
+\noindent With few exceptions, Assad chose to keep social media platforms up and running.
 Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
@@
 political opportunity structures. The political opportunity structure are
-“comprised *(sic)* of specific configuration of resources, institutional
+“comprised of *(sic)* specific configuration of resources, institutional
 arrangements and historical precedents for social mobilization, which facilitate
@@
 same processes can be similarly important for rebels [@anyanwu2002economic].
-Referencing Gurr’s [-@gurr2000peoples] work on minorities at
+Referencing Gurr's [-@gurr2000peoples] work on minorities at
 risk, Regan and Norton [-@regan2005greed] note that
@@
 development or expression of a shared identity [@wiltermuth2009synchrony]. This,
-in turn, may drive individuals’ propensity to engage in similar coordinated
+in turn, may drive individuals' propensity to engage in similar coordinated
 behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
@@
 Steinert-Threlkeld [-@steinert2017spontaneous] modeled a similar relationship
-between social media and social mobilization alongside event data. This
-groundbreaking work demonstrates that participants on the fringe of a social
+between social media and social mobilization alongside event data. That
+groundbreaking work demonstrated that participants on the fringe of a social
 movement contribute substantially to the overall level of protest. In addition
@@
 The social cohesion or linguistic similarity of daily tweets was calculated by
-quantifying the frequency of shared content words with respect to those words’
+quantifying the frequency of shared content words with respect to those words'
 frequencies in the entire tweet corpus. If a linguistic term has a high
@@
 
-The social cohesion calculation was performed on the tweet corpus containing
-both English and Arabic tweets. All hashtags and URLs were included in the
-analysis.
-
-The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
+\noindent The social cohesion calculation was performed on the tweet corpus
+containing both English and Arabic tweets. All hashtags and URLs were included
+in the analysis. The raw social cohesion time series can be seen in Figure
+\@ref(fig:raw-cohesion-ts).
 
@@
 
-The raw event time series for target filtered data can be seen in Figure \@ref(fig:raw-event-ts-target).
-The The raw event time series for source and target filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).
+The raw event time series for target filtered data can be seen in Figure
+\@ref(fig:raw-event-ts-target). The raw event time series for source and target
+filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).
 
@@
 #### Metrics
-For WCRQA analyses, we decided to focus on RR and DET, but WCRQA visualization can be done for any metric desired.
+For WCRQA analyses, we decided to focus on RR and DET, but similar analyses and
+visualizations can be performed for any RQA metric.
 

### 2020-06-02 manuscript.tex
More formatting and typos

@@
 \abstract{
-Social mobilization requires effective collective coordination. In recent
-years, individuals involved in social movements have taken to social media
-platforms to reach broader audiences at rapid speeds. Effective virtual
-mobilization similarly requires social cohesion and coordination, yet the
-degree to which virtual mobilization reflects or drives real-world movements
-is unclear. Here, we explore the dynamics of real-world events and social
-cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear
-methods cross-recurrence quantification analysis and windowed cross-recurrence
-quantification analysis, we investigate if counts of all daily events, daily
-positive events, and daily negative events are coupled with social cohesion
-found in Syrian tweets. Results indicate that virtual social cohesion is
-coupled with the counts of all and negative events each day but shows a more
-nuanced connection to positive events, only visible when examining finer-grained
-data. This suggests that virtual mobilization does reflect
-real-world movements, with the strongest connections to the frequency of all
-events and the frequency of negative events. We
-conclude with a discussion of implications and applications of nonlinear
-methods in political science research.
+In recent years, individuals involved in social movements have taken to social
+media platforms to reach broader audiences at rapid speeds. Although
+micro-blogging has become a primary means of information dissemination during
+times of turmoil, the degree to which virtual mobilization reflects or drives
+real-world movements is unclear. Here, we explore the dynamics of real-world
+events and Twitter social cohesion in Syria during the Arab Spring. Using the
+nonlinear methods cross-recurrence quantification analysis and windowed
+cross-recurrence quantification analysis, we investigate if frequency of
+events of different intensities are coupled with social cohesion found in
+Syrian tweets. Results indicate that virtual social cohesion is coupled with
+the counts of all and negative events each day but shows a more nuanced
+connection to positive events, suggesting that virtual mobilization does
+reflect real-world movements. We conclude with a discussion of implications
+and applications of nonlinear methods in political science research.
 }
@@
 Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and mimeographed flyers,
-through in-person meetings of social organizations and churches, and through
-word of mouth. They gathered together and hand-made protest signs that reflected
-their agendas. As McAdam found, people were more likely to join movements when
-they had a personal connection (McAdam, 1986; McAdam \& Paulsen, 1993):
-Historically, strong ties have been
-strong predictors of involvement in high-risk protest activity.
-
-The cohesiveness and strength of social movements in the pre-Internet era could be
-operationalized by the number of people turning out to protest and through the
-political events that precipitated and resulted from social gatherings \emph{en masse}.
-The content of placards and protest
-signs provided the protest narrative in their own words. Cohesive
-social movements were reflected in their cohesive placards and posters. For
-example, the \enquote{I am a man} posters held by the men involved in the 1968
-sanitation workers' strike reflected their internal cohesion and unified,
+using phone tree calling sheets and mimeographed flyers, through in-person
+meetings of social organizations and churches, and through word of mouth. They
+gathered together and hand-made protest signs that reflected their agendas. As
+McAdam found, people were more likely to join movements when they had a personal
+connection (McAdam, 1986; McAdam \& Paulsen, 1993): Historically, strong
+ties have been strong predictors of involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements in the pre-Internet era could
+be operationalized by the number of people turning out to protest and through
+the political events that precipitated and resulted from social gatherings \emph{en
+masse}. Cohesive social movements were reflected in their cohesive placards and
+posters. For example, the \enquote{I am a man} posters held by the men involved in the
+1968 sanitation workers' strike reflected their internal cohesion and unified,
 goal-oriented movement (Windsor, 2020).
 
-However, the rise of the Internet and its decentralized online networks
-has upended theories about recruitment to---and participation in---social
-movements. Strong interpersonal ties have yielded to weak impersonal ties that
-strongly predict involvement in social movements (Steinert-Threlkeld, 2017). Research
+However, the rise of the Internet and its decentralized online networks has
+upended theories about recruitment to---and participation in---social movements.
+Strong interpersonal ties have yielded to weak impersonal ties that strongly
+predict involvement in social movements (Steinert-Threlkeld, 2017). Research
 methodologies for measuring social movements have similarly evolved from
@@
 question related to the one posed by Zeitzoff (2017): How does
-social media reflect on-the-ground realities during times of social conflict?
-To do so, we examine patterns of linguistic cohesion on Twitter and their
-connection to real-world events during
-the Arab Spring uprising in Syria between March and June 2012.
-
-Disentangling the complicated relationship between mass online mobilization---and
-social mobilization in person---continues to be relevant, even as our modes
-of communication change. The
-political processes that transpired during and after the Arab Spring are still
-in the process of being understood. As Zeitzoff (2017) recognizes,
-social media is changing conflict, but the mechanisms and relationships by
-which it does so are still being understood.
+social media reflect on-the-ground realities during times of social conflict? To
+do so, we examine patterns of linguistic cohesion on Twitter and their
+connection to real-world events during the Arab Spring uprising in Syria between
+March and June 2012.
+
+Disentangling the complicated relationship between mass online
+mobilization---and social mobilization in person---continues to be relevant,
+even as our modes of communication change. The political events that
+transpired during and after the Arab Spring are still in the process of being
+understood. As Zeitzoff (2017) recognizes, social media is
+changing conflict, but the mechanisms and relationships by which it does so are
+still being understood.
 
@@
 Following a wave of democratization efforts across the Middle East and North
-Africa, modest Syrian protests began in March 2011. The regime responded
-harshly with imprisonments, detentions, censorship, and military operations as
-the resistance to Assad's regime grew and spread throughout the country. The
+Africa, modest Syrian protests began in March 2011. The regime responded harshly
+with imprisonments, detentions, censorship, and military operations as the
+resistance to Assad's regime grew and spread throughout the country. The
 fighting escalated dramatically in March 2012, after increased unrest in the
-western city of Homs. International actors---including the Red Cross/Red Crescent
-Society, the United Nations General Assembly, the Security Council, and
-individual world leaders---worked toward cease-fires, negotiations,
-and concessions without much success. While many high-level military and
-diplomatic officials defected from the regime, numerous loyal forces
-continued the regime's repression, and the Syrian people turned to social
-media to help coordinate their activism and communicate to the world. Between March and
-June 2012, more than 8 million tweets were sent within Syria, revealing the
-details of the conflict suppressed by the government.
+western city of Homs. International actors---including the Red Cross/Red
+Crescent Society, the United Nations General Assembly, the Security Council, and
+individual world leaders---worked toward cease-fires, negotiations, and
+concessions without much success. While many high-level military and diplomatic
+officials defected from the regime, numerous loyal forces continued the regime's
+repression, and the Syrian people turned to social media to help coordinate
+their activism and communicate to the world. Between March and June 2012, more
+than 8 million tweets were sent within Syria, revealing the details of the
+conflict suppressed by the government.
 
@@
 people make up between 10-15\% of the population, Alawites between 8-15\%,
-Christians about 10\%. There are also much smaller sects (e.g., Ismailis,
-Druze), but Sunni Muslims comprise the vast majority of society. Most people
-speak Arabic as their primary language. Most policy reports addressing the current
+Christians about 10\%. There are also much smaller sects (e.g., Ismailis, Druze),
+but Sunni Muslims comprise the vast majority of society. Most people speak
+Arabic as their primary language. Most policy reports addressing the current
 conflict report on the cohesion of the ruling Alawite military elite, rather
@@
 
-Massive online social cohesion can have real-world social
-manifestations. Social media platforms provide one way to enable this kind of
-online social cohesion by offering distributed information-gathering and
-real-time information dissemination. Given its accessibility and proficiency as
-an information exchange tool, Twitter has provided individuals involved in
-social movements an opportunity to complement or even replace real-world social
-mobilization. For example, during the 2012 Italian protests for global economic
-change, the riots in Rome were mirrored by Twitter activity both on the day of
-the protests and in the days following them (Vicari, 2013). Tweeting was
-determined to be more effective locally in discussing real-world, real-time
-events than traditional mainstream media platforms. As more and more individuals
-rely on social media to obtain local news and information, it becomes
-increasingly important to understand just how these micro-blogs reflect
-real-world action.
+Massive online social cohesion can have real-world social manifestations. Social
+media platforms provide one way to enable this kind of online social cohesion by
+offering distributed information-gathering and real-time information
+dissemination. Given its accessibility and proficiency as an information
+exchange tool, Twitter has provided individuals involved in social movements an
+opportunity to complement or even replace real-world social mobilization. For
+example, during the 2012 Italian protests for global economic change, the riots
+in Rome were mirrored by Twitter activity both on the day of the protests and in
+the days following them (Vicari, 2013). Tweeting was determined to be more
+effective locally in discussing real-world, real-time events than traditional
+mainstream media platforms. As more and more individuals rely on social media to
+obtain local news and information, it becomes increasingly important to
+understand just how these micro-blogs reflect real-world action.
 
@@
 
-Along with Facebook, Twitter has been
-credited as essential to the Arab Spring---both for protesters (as a means to
-coordinate with one another and to communicate with the world) and for the
-government response (to monitor and track protestors to crack down on dissent)
-(Comninos, 2011). The events of Arab Spring have been thoroughly discussed
-within the political science literature (e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge, the direct \emph{coupling} between
+Along with Facebook, Twitter has been credited as essential to the Arab
+Spring---both for protesters (as a means to coordinate with one another and to
+communicate with the world) and for the government response (to monitor and
+track protestors to crack down on dissent) (Comninos, 2011). The events of
+Arab Spring have been thoroughly discussed within the political science
+literature (e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge, the direct \emph{coupling} between
 Syrian Twitter cohesion and international action coordination has not been
-investigated. In fact, some have been skeptical about the effect of social media on
-collective action at all (Seay, 2014).
+investigated. In fact, some have been skeptical about the effect of social media
+on collective action at all (Seay, 2014).
 
@@
 
-Social media generates critical information about events, including whether and how
-a demonstration will take place, how many
-people participate, and how those in power (e.g., state, military, security apparatus)
-respond. Similarly, these media platforms alert us to more global shifts within
-a conflict, such as when fighting moves to a new city or region, the number of
-casualties and wounded, and the types of weaponry used by parties to the
-conflict (Zeitzoff, 2017). Social media is not entirely event-driven, however.
-In monitoring social media channels, government forces may respond to the
-perception that citizens are gaining strength and sympathy. Governments have
-been shown to be quite tolerant of dissent so long as it does not metamorphose
-into collective action (King, Pan, \& Roberts, 2013).
+Social media generates critical information about events, including whether and
+how a demonstration will take place, how many people participate, and how those
+in power (e.g., state, military, security apparatus) respond. Similarly, these
+media platforms alert us to more global shifts within a conflict, such as when
+fighting moves to a new city or region, the number of casualties and wounded,
+and the types of weaponry used by parties to the conflict (Zeitzoff, 2017).
+Social media is not entirely event-driven, however. In monitoring social media
+channels, government forces may respond to the perception that citizens are
+gaining strength and sympathy. Governments have been shown to be quite tolerant
+of dissent so long as it does not metamorphose into collective action
+(King, Pan, \& Roberts, 2013).
 
@@
 phones and computers with Internet connectivity, providing a stream of real-time
-shared information. Citizens can share the location of events like protests and military
-incursions, the degree of state repression, and the number of casualties. In
-turn, the government---interested in remaining in power---monitors social media
-platforms to ascertain emerging threats (Comninos, 2011),
-such as where new groups are forming
-and where existing groups are strengthening, where gatherings are held, and who
-the idea entrepreneurs are. An example of a leader
-expressing his interest in
-such public conversation is given by Bashar al-Assad in a speech on June 3, 2012:
+shared information. Citizens can share the location of events like protests and
+military incursions, the degree of state repression, and the number of
+casualties. In turn, the government---interested in remaining in
+power---monitors social media platforms to ascertain emerging threats
+(Comninos, 2011), such as where new groups are forming and where existing
+groups are strengthening, where gatherings are held, and who the idea
+entrepreneurs are.
+
+An example of a leader expressing his interest in such public
+conversation is given by Bashar al-Assad in a speech on June 3, 2012:
 
@@
 
-With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes (2015) notes that regimes can attempt to thwart the growth of social
-protest online and in the streets by shutting down the Internet.
+\noindent With few exceptions, Assad chose to keep social media platforms up and running.
+Gohdes (2015) notes that regimes can attempt to thwart the growth
+of social protest online and in the streets by shutting down the Internet.
 During these times, however, she finds that military repression increases.
@@
 
-At the same time, the insulation
-of online social platforms allows researchers to detail real-world social dynamics
-at unprecedented resolution and scale (Paxton \& Griffiths, 2017). The digital traces left by
-individuals and collectively as groups are regarded as a valuable source of
-information that can offer powerful insights into states of social
-disequilibrium, uprisings, and escalations into civil wars.
-By examining these conversations, researchers can study the degree of cohesion between
-speakers and the alignment between that cohesion and their collective political
-behavior.
+At the same time, the insulation of online social platforms allows researchers
+to detail real-world social dynamics at unprecedented resolution and scale
+(Paxton \& Griffiths, 2017). The digital traces left by individuals and collectively as
+groups are regarded as a valuable source of information that can offer powerful
+insights into states of social disequilibrium, uprisings, and escalations into
+civil wars. By examining these conversations, researchers can study the degree
+of cohesion between speakers and the alignment between that cohesion and their
+collective political behavior.
 
@@
 participate. Given that people are generally risk-averse, overcoming inertia
-requires a strong connection to the group identity or a strong aversion to an individual,
-event, or political injustice (Goldstone, 1980, 2011).
-Political resistance offers participants the opportunity to \enquote{lose themselves} and
-relinquish their individual identity in favor of identification with a larger
-group identity, contributing to a cohesive group ready and mobilized for
-action (Hoffer, 2011).
+requires a strong connection to the group identity or a strong aversion to an
+individual, event, or political injustice (Goldstone, 1980, 2011). Political resistance offers participants the
+opportunity to \enquote{lose themselves} and relinquish their individual identity in
+favor of identification with a larger group identity, contributing to a cohesive
+group ready and mobilized for action (Hoffer, 2011).
 
@@
 political opportunity structures. The political opportunity structure are
-\enquote{comprised \emph{(sic)} of specific configuration of resources, institutional
+\enquote{comprised of \emph{(sic)} specific configuration of resources, institutional
 arrangements and historical precedents for social mobilization, which facilitate
 the development of protest movements in some instances and constrain them in
-others} ({\textbf{???}}). What emerges as strategies and tactics in contentious
-politics are, in essence, a function of what the system makes possible. This
-includes the number of people and their disposition (i.e.~nonviolent or
-violent), as well as their internal structure. The more cohesive a group is, the
-greater threat they pose to the establishment.
+others} (Kitschelt, 1986). What emerges as strategies and tactics in
+contentious politics are, in essence, a function of what the system makes
+possible. This includes the number of people and their disposition (i.e.
+nonviolent or violent), as well as their internal structure. The more cohesive a
+group is, the greater threat they pose to the establishment.
 
@@
 
-Another factor influencing social cohesion during social movements and
-civil wars is ethnic identity and the degree of ethnic conflict associated with
-the movement. Greater degrees of ethnic conflict increase the salience of
-ethnic identity, leading people to identify more strongly with their own
-ethnic identity (Sambanis \& Schulhofer-Wohl, 2009). As ethnic conflict
-intensifies, groups seek to become more quintessentially like the typical
-member of their ethnic group. This can manifest in a number of ways, including
-in behavior on social media. However, this may also include a general identification
-across ethnic groups in a membership of an opposition to an oppressive leader.
+Another factor influencing social cohesion during social movements and civil
+wars is ethnic identity and the degree of ethnic conflict associated with the
+movement. Greater degrees of ethnic conflict increase the salience of ethnic
+identity, leading people to identify more strongly with their own ethnic
+identity (Sambanis \& Schulhofer-Wohl, 2009). As ethnic conflict intensifies, groups seek to become
+more quintessentially like the typical member of their ethnic group. This can
+manifest in a number of ways, including in behavior on social media. However,
+this may also include a general identification across ethnic groups in a
+membership of an opposition to an oppressive leader.
 
@@
 Just as real-world social cohesion can be quantified, so can online cohesion.
-One kind of cohesion can be found in
-the similarity in language use on social media. This implicit or explicit
-similarity in language use can indicate shared beliefs, thoughts, and feelings,
-as has been studied in research on language style in psycholinguistics and
-social psychology (Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010). Although previous work on language style has often
+One kind of cohesion can be found in the similarity in language use on social
+media. This implicit or explicit similarity in language use can indicate shared
+beliefs, thoughts, and feelings, as has been studied in research on language
+style in psycholinguistics and social psychology (Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010). Although previous work on language style has often
 focused on individuals and small groups, this can be scaled up to examine
@@
 we will consider. In Figure \ref{fig:cohesion-in-tweets}, we see four
-sequential tweets, each containing four words.
-Each sequential tweet contains some content included in the previous tweets. The
-linguistic construct of content word overlap measures the relationship across
-units of meaning---here, tweets---where identical and semantically similar words
-are repeated (Graesser, McNamara, Louwerse, \& Cai, 2004). These repeated lexical
-items constitute a theme; on Twitter, this might be a particular hashtag, a
-name, a location, or other nominal category. This localized cohesion is
-referential; words are repeated and co-referred across tweets, creating a sense
-of continuity and cohesiveness of meaning and message.
+sequential tweets, each containing four words. Each sequential tweet contains
+some content included in the previous tweets. The linguistic construct of
+content word overlap measures the relationship across units of meaning---here,
+tweets---where identical and semantically similar words are repeated
+(Graesser, McNamara, Louwerse, \& Cai, 2004). These repeated lexical items constitute a theme; on Twitter,
+this might be a particular hashtag, a name, a location, or other nominal
+category. This localized cohesion is referential; words are repeated and
+co-referred across tweets, creating a sense of continuity and cohesiveness of
+meaning and message.
 
@@
 strong ties (Gladwell, 2010; Granovetter, 1973; McAdam, 1986), strengthening the movement overall by expanding and
-deepening heterogenous ties. Therefore,
-in the context of social conflict, the linguistic cohesion
-of the online conversation should correspond to the degree of
-social cohesion on the ground.
+deepening heterogenous ties. Therefore, in the context of social conflict, the
+linguistic cohesion of the online conversation should correspond to the degree
+of social cohesion on the ground.
 
 Steinert-Threlkeld (2017) modeled a similar relationship
-between social media and social mobilization alongside event data. This
-groundbreaking work demonstrates that participants on the fringe of a social
+between social media and social mobilization alongside event data. That
+groundbreaking work demonstrated that participants on the fringe of a social
 movement contribute substantially to the overall level of protest. In addition
@@
 cohesion is thus potentially an indicator and a result of increased social
-organization and mobilization on the ground. However, this occurs within a context
-that is affected by local and international events; both
-exogenous events (like intervention by another country or
-international organization like the United Nations) and
-endogenous events (like the recruitment of new members to the rebel or
-resistance movement) can affect cohesion.
-
-From a dynamical systems perspective, online social cohesion and
-in-person action can be considered two complementary
-components of a single system, mutually constrained and constantly interacting
-and influencing one another (Mahner \& Bunge, 1997). Investigation of the
-coupling of real-world mobilization and social cohesion could provide new
-insight into the power of social media during mobilization and the ways in which
-individuals utilize it to bring about, or respond to, social change.
-Increasingly, social media platforms are being utilized during social
-mobilization (Koopmans, 2004; McAdam, Tarrow, \& Tilly, 2003),
-but the relationship between virtual and real-world mobilization
-is still largely unknown. The present work aims to understand how physical and
-virtual movements coexist and interact from a dynamical systems perspective.
+organization and mobilization on the ground. However, this occurs within a
+context that is affected by local and international events; both exogenous
+events (like intervention by another country or international organization like
+the United Nations) and endogenous events (like the recruitment of new members
+to the rebel or resistance movement) can affect cohesion.
+
+From a dynamical systems perspective, online social cohesion and in-person
+action can be considered two complementary components of a single system,
+mutually constrained and constantly interacting and influencing one another
+(Mahner \& Bunge, 1997). Investigation of the coupling of real-world
+mobilization and social cohesion could provide new insight into the power of
+social media during mobilization and the ways in which individuals utilize it to
+bring about, or respond to, social change. Increasingly, social media platforms
+are being utilized during social mobilization (Koopmans, 2004; McAdam, Tarrow, \& Tilly, 2003), but the relationship between virtual and real-world
+mobilization is still largely unknown. The present work aims to understand how
+physical and virtual movements coexist and interact from a dynamical systems
+perspective.
 
@@
 
-The corpus of tweets used included 697428 Syrian tweets
+The corpus of tweets used included 0 Syrian tweets
 occurring between March 30--June 15, 2012. Using the Twitter streaming API,
@@
 
-The social cohesion calculation was performed on the tweet corpus containing
-both English and Arabic tweets. All hashtags and URLs were included in the
-analysis.
+\noindent The social cohesion calculation was performed on the tweet corpus
+containing both English and Arabic tweets. All hashtags and URLs were included
+in the analysis. The raw social cohesion time series can be seen in Figure
+\ref{fig:raw-cohesion-ts}.
+
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/raw-cohesion-ts} \caption{Raw social cohesion metric time series.}\label{fig:raw-cohesion-ts}
+\end{figure}
 
@@
 day that had an intensity rating less than zero.
+
+The raw event time series for target filtered data can be seen in Figure
+\ref{fig:raw-event-ts-target}. The raw event time series for source and target
+filtered data can be seen in Figure \ref{fig:raw-event-ts-source-target}.
+
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/raw-event-ts-target} \caption{Raw event count time series for target filtered data.}\label{fig:raw-event-ts-target}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/raw-event-ts-source-target} \caption{Raw event count time series for source and target filtered data.}\label{fig:raw-event-ts-source-target}
+\end{figure}
 
@@
 
-For WCRQA analyses, we decided to focus on RR and DET.
+For WCRQA analyses, we decided to focus on RR and DET, but similar analyses and
+visualizations can be performed for any RQA metric.
 
@@
 
+\leavevmode\hypertarget{ref-kitschelt1986political}{}%
+Kitschelt, H. P. (1986). Political opportunity structures and political protest: Anti-nuclear movements in four democracies. \emph{British Journal of Political Science}, \emph{16}(1), 57--85.
+
 \leavevmode\hypertarget{ref-koehler2017political}{}%

### 2020-06-02 manuscript.Rmd
Updates to raw event plots

@@
 
+# specify global plotting variables for easier testing
+all_event_color = "#CC79A7"
+positive_event_color = "#0072B2"
+negative_event_color = "#D55E00"
+line_thickness = 2
+
 # read in social cohesion data
@@
 raw_events_ts_target <- ggplot() +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
-  scale_color_manual(values = c("red", "orange", "blue")) +
+  geom_line(event_df, 
+            mapping = aes(x= as.Date(Date), 
+                          y=all_events_target, 
+                          colour = 'all events')) +
+  geom_line(event_df, 
+            mapping = aes(x= as.Date(Date), 
+                          y=pos_events_target, 
+                          colour = 'positive events')) +
+  geom_line(event_df, 
+            mapping = aes(x= as.Date(Date),
+                          y=neg_events_target, 
+                          colour = 'negative events')) +
+  scale_color_manual(values = c(all_event_color, # all
+                                positive_event_color, # positive
+                                negative_event_color)) + # negative
+  scale_size_manual(values=line_thickness) +
   xlab("Date") +
@@
 raw_events_ts_source_target <- ggplot() +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
-  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
-  scale_color_manual(values = c("red", "orange", "blue")) +
+  geom_line(event_df, 
+            mapping = aes(x = as.Date(Date), 
+                          y=all_events_source_target, 
+                          colour = 'all events')) +
+  geom_line(event_df, 
+            mapping = aes(x = as.Date(Date),
+                          y=pos_events_source_target, 
+                          colour = 'positive events')) +
+  geom_line(event_df, 
+            mapping = aes(x = as.Date(Date), 
+                          y=neg_events_source_target, 
+                          colour = 'negative events')) +
+  scale_color_manual(values = c(all_event_color, # all
+                                positive_event_color, # positive
+                                negative_event_color)) + # negative
+  scale_size_manual(values=line_thickness) +
   xlab("Date") +

### 2020-06-02 manuscript.Rmd
Update CRPs to have event-specific coloring

@@
 
-# specify global plotting variables for easier testing
+# specify global plotting variables
 all_event_color = "#CC79A7"

### 2020-06-02 scripts/primary-analyses/02_crqa.R

@@ -13,6 +13,11 @@
 # clear environment
 rm(list=ls())
 
+# specify global plotting variables
+all_event_color = "#CC79A7"
+positive_event_color = "#0072B2"
+negative_event_color = "#D55E00"
+
 # read in data 
 data <- read.csv("./data/formatted/primary/formatted_data.csv")
 shuffled_full <- read.csv("./data/formatted/primary/shuffled_data_full.csv")
@@ -54,7 +59,7 @@ png("./results/primary/crqa/source_target-rp-all_events.png", width = 4, height 
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of all events", 
-           cols = "blue", 
+           cols = all_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
@@ -83,7 +88,7 @@ png("./results/primary/crqa/source_target-rp-pos_events.png", width = 4, height 
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of positive events", 
-           cols = "blue", 
+           cols = positive_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
@@ -112,7 +117,7 @@ png("./results/primary/crqa/source_target-rp-neg_events.png", width = 4, height 
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of negative events", 
-           cols = "blue", 
+           cols = negative_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
@@ -143,7 +148,7 @@ png("./results/primary/crqa/target-rp-all_events.png", width = 4, height = 4, un
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of all events", 
-           cols = "blue", 
+           cols = all_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
@@ -172,7 +177,7 @@ png("./results/primary/crqa/target-rp-pos_events.png", width = 4, height = 4, un
 par = list(unit = 2, 
            labelx = "Social cohesion", 
            labely = "Count of positive events", 
-           cols = "blue", 
+           cols = positive_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
[…]

### 2020-06-02 scripts/primary-analyses/02_crqa.R
Join CRPs

@@ -122,6 +122,18 @@ par = list(unit = 2,
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
 
+## join source-target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/primary/crqa/source_target-rp-all_events.png')
+crp_2 <- readPNG('./results/primary/crqa/source_target-rp-pos_events.png')
+crp_3 <- readPNG('./results/primary/crqa/source_target-rp-neg_events.png')
+
+# join images and save
+png("./results/primary/crqa/source_target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
+dev.off()
+
 ### target filtered data ###
 
 ## count of all events and social cohesion ##
@@ -209,6 +221,18 @@ par = list(unit = 2,
            cols = negative_event_color, 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
+dev.off()
+
+## join source-target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/primary/crqa/target-rp-all_events.png')
+crp_2 <- readPNG('./results/primary/crqa/target-rp-pos_events.png')
+crp_3 <- readPNG('./results/primary/crqa/target-rp-neg_events.png')
+
+# join images and save
+png("./results/primary/crqa/target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 
 #### 3. Conduct permutation tests ####

### 2020-06-02 scripts/libraries_and_functions.r
Update necessary packages for joining images

@@ -16,7 +16,8 @@ required_packages = c(
   'gtools',
   'knitr',
   'statip',
-  'gridExtra'
+  'gridExtra',
+  'png'
 )
 
 # load required packages

### 2020-06-02 scripts/required_packages.r

@@ -16,7 +16,8 @@ required_packages = c(
   'gtools',
   'knitr',
   'statip',
-  'gridExtra'
+  'gridExtra',
+  'png'
 )
 
 # install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)

### 2020-06-02 scripts/primary-analyses/02_crqa.R
Fix header

@@ -223,7 +223,7 @@ par = list(unit = 2,
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
 
-## join source-target plots ##
+## join target plots ##
 
 # read in CRPs
 crp_1 <- readPNG('./results/primary/crqa/target-rp-all_events.png')

### 2020-06-02 scripts/secondary-analyses/icews/02_crqa.R
Join CRPs for secondary ICEWS analyses

@@ -117,6 +117,18 @@ par = list(unit = 2,
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
 
+## join source-target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/secondary/icews/crqa/source_target-rp-all_events.png')
+crp_2 <- readPNG('./results/secondary/icews/crqa/source_target-rp-pos_events.png')
+crp_3 <- readPNG('./results/secondary/icews/crqa/source_target-rp-neg_events.png')
+
+# join images and save
+png("./results/secondary/icews/crqa/source_target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
+dev.off()
+
 ### target filtered data ###
 
 ## count of all events and social cohesion ##
@@ -204,6 +216,18 @@ par = list(unit = 2,
            cols = "blue", 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
+dev.off()
+
+## join target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/secondary/icews/crqa/target-rp-all_events.png')
+crp_2 <- readPNG('./results/secondary/icews/crqa/target-rp-pos_events.png')
+crp_3 <- readPNG('./results/secondary/icews/crqa/target-rp-neg_events.png')
+
+# join images and save
+png("./results/secondary/icews/crqa/target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 
 #### 3. Conduct permutation tests ####

### 2020-06-02 scripts/secondary-analyses/phoenix/02_crqa.R
Join CRPs for secondary Phoenix analyses

@@ -117,6 +117,18 @@ par = list(unit = 2,
 plotRP(cross_recurrence_analysis$RP, par)
 dev.off()
 
+## join source-target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/secondary/phoenix/crqa/source_target-rp-all_events.png')
+crp_2 <- readPNG('./results/secondary/phoenix/crqa/source_target-rp-pos_events.png')
+crp_3 <- readPNG('./results/secondary/phoenix/crqa/source_target-rp-neg_events.png')
+
+# join images and save
+png("./results/secondary/phoenix/crqa/source_target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
+dev.off()
+
 ### target filtered data ###
 
 ## count of all events and social cohesion ##
@@ -204,6 +216,18 @@ par = list(unit = 2,
            cols = "blue", 
            pcex = .5)
 plotRP(cross_recurrence_analysis$RP, par)
+dev.off()
+
+## join target plots ##
+
+# read in CRPs
+crp_1 <- readPNG('./results/primary/crqa/target-rp-all_events.png')
+crp_2 <- readPNG('./results/primary/crqa/target-rp-pos_events.png')
+crp_3 <- readPNG('./results/primary/crqa/target-rp-neg_events.png')
+
+# join images and save
+png("./results/primary/crqa/target-rp-joined.png")
+grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 
 #### 3. Conduct permutation tests ####

### 2020-06-02 manuscript.Rmd
Call joined CRPs

@@
 
-```{r plot-rp-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}
+```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}
 
 # call image
-knitr::include_graphics("./results/primary/crqa/target-rp-all_events.png")
-
-```
-
-```{r plot-rp-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/crqa/target-rp-pos_events.png")
-
-```
-
-```{r plot-rp-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/crqa/target-rp-neg_events.png")
+knitr::include_graphics("./results/primary/crqa/target-rp-joined.png")
 
@@
 
-```{r plot-rp-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}
 
 # call image
-knitr::include_graphics("./results/primary/crqa/source_target-rp-all_events.png")
-
-```
-
-```{r plot-rp-source-targ-pos, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/crqa/source_target-rp-pos_events.png")
-
-```
-
-```{r plot-rp-source-targ-neg, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.'}
-
-# call image
-knitr::include_graphics("./results/primary/crqa/source_target-rp-neg_events.png")
+knitr::include_graphics("./results/primary/crqa/source_target-rp-joined.png")
 

### 2020-06-03 scripts/primary-analyses/02_crqa.R
Fix spacing in joined plots

@@ -130,8 +130,8 @@ crp_2 <- readPNG('./results/primary/crqa/source_target-rp-pos_events.png')
 crp_3 <- readPNG('./results/primary/crqa/source_target-rp-neg_events.png')
 
 # join images and save
-png("./results/primary/crqa/source_target-rp-joined.png")
-grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
+png("./results/primary/crqa/source_target-rp-joined.png", width=720,height=325)
+grid.arrange(rasterGrob(crp_1), rasterGrob(crp_2), rasterGrob(crp_3), nrow=1)
 dev.off()
 
 ### target filtered data ###
@@ -230,9 +230,9 @@ crp_1 <- readPNG('./results/primary/crqa/target-rp-all_events.png')
 crp_2 <- readPNG('./results/primary/crqa/target-rp-pos_events.png')
 crp_3 <- readPNG('./results/primary/crqa/target-rp-neg_events.png')
 
-# join images and save
-png("./results/primary/crqa/target-rp-joined.png")
-grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
+# join and save
+png("./results/primary/crqa/target-rp-joined.png", width=720,height=325)
+grid.arrange(rasterGrob(crp_1), rasterGrob(crp_2), rasterGrob(crp_3), nrow=1)
 dev.off()
 
 #### 3. Conduct permutation tests ####

### 2020-06-03 scripts/secondary-analyses/icews/02_crqa.R
Fix spacing in secondary joined CRP plots

@@ -125,7 +125,7 @@ crp_2 <- readPNG('./results/secondary/icews/crqa/source_target-rp-pos_events.png
 crp_3 <- readPNG('./results/secondary/icews/crqa/source_target-rp-neg_events.png')
 
 # join images and save
-png("./results/secondary/icews/crqa/source_target-rp-joined.png")
+png("./results/secondary/icews/crqa/source_target-rp-joined.png", width=720, height=325)
 grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 
@@ -226,7 +226,7 @@ crp_2 <- readPNG('./results/secondary/icews/crqa/target-rp-pos_events.png')
 crp_3 <- readPNG('./results/secondary/icews/crqa/target-rp-neg_events.png')
 
 # join images and save
-png("./results/secondary/icews/crqa/target-rp-joined.png")
+png("./results/secondary/icews/crqa/target-rp-joined.png", width=720, height=325)
 grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 

### 2020-06-03 scripts/secondary-analyses/phoenix/02_crqa.R

@@ -125,7 +125,7 @@ crp_2 <- readPNG('./results/secondary/phoenix/crqa/source_target-rp-pos_events.p
 crp_3 <- readPNG('./results/secondary/phoenix/crqa/source_target-rp-neg_events.png')
 
 # join images and save
-png("./results/secondary/phoenix/crqa/source_target-rp-joined.png")
+png("./results/secondary/phoenix/crqa/source_target-rp-joined.png", width=720, height=325)
 grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 
@@ -226,7 +226,7 @@ crp_2 <- readPNG('./results/primary/crqa/target-rp-pos_events.png')
 crp_3 <- readPNG('./results/primary/crqa/target-rp-neg_events.png')
 
 # join images and save
-png("./results/primary/crqa/target-rp-joined.png")
+png("./results/primary/crqa/target-rp-joined.png", width=720, height=325)
 grid.arrange(rasterGrob(crp_1),rasterGrob(crp_2), rasterGrob(crp_3), ncol=3)
 dev.off()
 

### 2020-06-03 manuscript.Rmd
Increase joined CRP image size

@@
 in-phase synchrony between the two time series. See Figures
-\@ref(fig:plot-rp-targ-all)-\@ref(fig:plot-rp-source-targ-neg) for examples of
+\@ref(fig:plot-rp-targ)-\@ref(fig:plot-rp-source-targ) for examples of
 RPs.
@@
 a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
-metrics did not reach significance (Figure \@ref(fig:plot-rp-targ-all);
+metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
 \autoref{table-1}).
@@
 found no statistically significant difference from chance for any of the metrics
-other than TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).
+other than TT (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
 
@@
 ENTR, LAM, and TT. All other metrics did not reach significance (Figure
-\@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
+\@ref(fig:plot-rp-targ); \autoref{table-1}).
 
@@
 
-```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.'}
+```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.', out.width='100%'}
 
@@
 a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
-were non-significant (Figure \@ref(fig:plot-rp-source-targ-all);
+were non-significant (Figure \@ref(fig:plot-rp-source-targ);
 \autoref{table-2}).
@@
 found a statistical difference from chance for maxL, ENTR, and LAM (Figure
-\@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).
+\@ref(fig:plot-rp-source-targ); \autoref{table-2}).
 
@@
 found a statistical difference from chance for DET, NRLINE, and rENTR. All other
-metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg);
+metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
 \autoref{table-2}).
@@
 
-```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.'}
+```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.', out.width='100%'}
 

### 2020-06-03 manuscript.Rmd
Edits to intro

@@
 changing conflict, but the mechanisms and relationships by which it does so are
-still being understood.
+still largely unknown.
 
@@
 power---monitors social media platforms to ascertain emerging threats
-[@comninos2011twitter], such as where new groups are forming and where existing
+[@comninos2011twitter], such as where new groups are forming, where existing
 groups are strengthening, where gatherings are held, and who the idea
@@
 People join social and political resistance movements because they feel a sense
-of connection to the cause and because they have been sufficiently convinced to
-participate. Given that people are generally risk-averse, overcoming inertia
+of connection to the cause. Given that people are generally risk-averse, overcoming inertia
 requires a strong connection to the group identity or a strong aversion to an
@@
 opportunity to “lose themselves” and relinquish their individual identity in
-favor of identification with a larger group identity, contributing to a cohesive
+favor of identification with a larger group, contributing to a cohesive
 group ready and mobilized for action [@Hoffer2011true].
@@
 Previous research on social movements supports the idea that participants are
-likely to join movements when they know and have a personal connection to
+more likely to join movements when they know and have a personal connection to
 someone else already involved [@mcadam1986recruitment]. The type of collective
@@
 political opportunity structures. The political opportunity structure are
-“comprised of *(sic)* specific configuration of resources, institutional
+“comprised of *(sic)* specific configurations of resources, institutional
 arrangements and historical precedents for social mobilization, which facilitate
@@
 itself is a function of geographic distance, ideology, and ethnicity.
-Within Syria, multiple rebel groups within Syria exist, sourcing fighters locally
+Within Syria, multiple rebel groups exist, sourcing fighters locally
 from the disaffected Syrian population and internationally through

### 2020-06-03 manuscript.Rmd
More edits to intro

@@
 the relative intensity of the conflict. Cohesion is a multi-layered concept
-referring to the connectedness of speakers, actions, and societies. Cohesion
-reflects the continuity of language and expression, and it shows the
+referring to the connectedness of speakers, actions, and societies. It
+reflects the continuity of language and expression, and shows the
 connectivity of participants in a social movement. To address the relationship
@@
 interdisciplinary approach that incorporates linguistics, psychology, and
-political science using nonlinear dynamical systems methodology to model the
+political science using nonlinear dynamical systems methodology to disentangle the
 relationship between language and action.
@@
 Just as real-world social cohesion can be quantified, so can online cohesion.
-One kind of cohesion can be found in the similarity in language use on social
-media. This implicit or explicit similarity in language use can indicate shared
+One kind of cohesion is the similarity in language use on social
+media. This implicit or explicit similarity can indicate shared
 beliefs, thoughts, and feelings, as has been studied in research on language
@@
 behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
-Taken together, these two processes may grow movement participants' weak and
+Taken together, these two processes may increase movement participants' weak and
 strong ties [@granovetter1977strength; @gladwell2010revolution;
@@
 previous work by demonstrating how sociolinguistic cohesion evolves in
-response to negative and positive exogenous events.
+tandem with negative and positive exogenous events.
 

### 2020-06-03 manuscript.tex
Specify Chicago citation/reference style

@@
 McAdam found, people were more likely to join movements when they had a personal
-connection (McAdam, 1986; McAdam \& Paulsen, 1993): Historically, strong
+connection (McAdam 1986; McAdam and Paulsen 1993): Historically, strong
 ties have been strong predictors of involvement in high-risk protest activity.
@@
 1968 sanitation workers' strike reflected their internal cohesion and unified,
-goal-oriented movement (Windsor, 2020).
+goal-oriented movement (Windsor 2020).
 
@@
 Strong interpersonal ties have yielded to weak impersonal ties that strongly
-predict involvement in social movements (Steinert-Threlkeld, 2017). Research
+predict involvement in social movements (Steinert-Threlkeld 2017). Research
 methodologies for measuring social movements have similarly evolved from
@@
 in Rome were mirrored by Twitter activity both on the day of the protests and in
-the days following them (Vicari, 2013). Tweeting was determined to be more
+the days following them (Vicari 2013). Tweeting was determined to be more
 effective locally in discussing real-world, real-time events than traditional
@@
 communicate with the world) and for the government response (to monitor and
-track protestors to crack down on dissent) (Comninos, 2011). The events of
+track protestors to crack down on dissent) (Comninos 2011). The events of
 Arab Spring have been thoroughly discussed within the political science
-literature (e.g., Lutterbeck, 2013; Koehler, 2017), but to our knowledge, the direct \emph{coupling} between
+literature (e.g., Lutterbeck 2013; Koehler 2017), but to our knowledge, the direct \emph{coupling} between
 Syrian Twitter cohesion and international action coordination has not been
 investigated. In fact, some have been skeptical about the effect of social media
-on collective action at all (Seay, 2014).
+on collective action at all (Seay 2014).
 
@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts. (Anderson, 2011)
+local contexts. (Anderson 2011)
 \end{quote}
@@
 to recruiting people for higher-risk activities
-(Gladwell, 2010; McAdam, 1986).
+(Gladwell 2010; McAdam 1986).
 
@@
 power: While strong ties tend to bind smaller groups, weak ties
-tend to bind groups across distances (Granovetter, 1973).
+tend to bind groups across distances (Granovetter 1973).
 
@@
 fighting moves to a new city or region, the number of casualties and wounded,
-and the types of weaponry used by parties to the conflict (Zeitzoff, 2017).
+and the types of weaponry used by parties to the conflict (Zeitzoff 2017).
 Social media is not entirely event-driven, however. In monitoring social media
@@
 of dissent so long as it does not metamorphose into collective action
-(King, Pan, \& Roberts, 2013).
+(King, Pan, and Roberts 2013).
 
@@
 power---monitors social media platforms to ascertain emerging threats
-(Comninos, 2011), such as where new groups are forming and where existing
+(Comninos 2011), such as where new groups are forming, where existing
 groups are strengthening, where gatherings are held, and who the idea
@@
 to detail real-world social dynamics at unprecedented resolution and scale
-(Paxton \& Griffiths, 2017). The digital traces left by individuals and collectively as
+(Paxton and Griffiths 2017). The digital traces left by individuals and collectively as
 groups are regarded as a valuable source of information that can offer powerful
@@
 People join social and political resistance movements because they feel a sense
-of connection to the cause and because they have been sufficiently convinced to
-participate. Given that people are generally risk-averse, overcoming inertia
+of connection to the cause. Given that people are generally risk-averse, overcoming inertia
 requires a strong connection to the group identity or a strong aversion to an
-individual, event, or political injustice (Goldstone, 1980, 2011). Political resistance offers participants the
+individual, event, or political injustice (Goldstone 1980, 2011). Political resistance offers participants the
 opportunity to \enquote{lose themselves} and relinquish their individual identity in
-favor of identification with a larger group identity, contributing to a cohesive
-group ready and mobilized for action (Hoffer, 2011).
+favor of identification with a larger group, contributing to a cohesive
+group ready and mobilized for action (Hoffer 2011).
 
 Previous research on social movements supports the idea that participants are
-likely to join movements when they know and have a personal connection to
-someone else already involved (McAdam, 1986). The type of collective
+more likely to join movements when they know and have a personal connection to
+someone else already involved (McAdam 1986). The type of collective
 contentious behavior that manifests in society is a function of the available
 political opportunity structures. The political opportunity structure are
-\enquote{comprised of \emph{(sic)} specific configuration of resources, institutional
+\enquote{comprised of \emph{(sic)} specific configurations of resources, institutional
 arrangements and historical precedents for social mobilization, which facilitate
 the development of protest movements in some instances and constrain them in
-others} (Kitschelt, 1986). What emerges as strategies and tactics in
+others} (Kitschelt 1986). What emerges as strategies and tactics in
 contentious politics are, in essence, a function of what the system makes
@@
 problems. Individuals must act in concert---that is, cohesively---to
-accomplish the task of challenging the authority of the state (Eisinger, 1973; Francisco, 1995; Olson, 1965; Tilly, 2004).
+accomplish the task of challenging the authority of the state (Olson 1965; Eisinger 1973; Tilly 2004; Francisco 1995).
 Recent work has considered rebel recruitment for participation in
-civil conflicts as a function of internal cohesion (Gates, 2002):
+civil conflicts as a function of internal cohesion (Gates 2002):
 Rebel movement success is influenced by the degree of group cohesion, which
 itself is a function of geographic distance, ideology, and ethnicity.
-Within Syria, multiple rebel groups within Syria exist, sourcing fighters locally
+Within Syria, multiple rebel groups exist, sourcing fighters locally
 from the disaffected Syrian population and internationally through
@@
 intergroup competition for participation in the rebel movement and
-punishment for defectors for nonparticipation (Gates, 2002).
+punishment for defectors for nonparticipation (Gates 2002).
 Foreign fighters would appear to be amply motivated to fight, given their
@@
 identity, leading people to identify more strongly with their own ethnic
-identity (Sambanis \& Schulhofer-Wohl, 2009). As ethnic conflict intensifies, groups seek to become
+identity (Sambanis and Schulhofer-Wohl 2009). As ethnic conflict intensifies, groups seek to become
 more quintessentially like the typical member of their ethnic group. This can
@@
 detail. Social homogeneity increases the likelihood of social conflict,
-especially when the society is polarized (Collier \& Hoeffler, 2004); this is partly
+especially when the society is polarized (Collier and Hoeffler 2004); this is partly
 due to nationalist groups' strong identification with a collective identity
-(Cederman \& Girardin, 2007) and their social solidarity (Sambanis \& Schulhofer-Wohl, 2009). These
-same processes can be similarly important for rebels (Anyanwu, 2002).
+(Cederman and Girardin 2007) and their social solidarity (Sambanis and Schulhofer-Wohl 2009). These
+same processes can be similarly important for rebels (Anyanwu 2002).
 Referencing Gurr's (2000) work on minorities at
@@
 maldistributions, it is individual penury that allows for this collective
-mobilization. (Regan \& Norton, 2005)
+mobilization. (Regan and Norton 2005)
 \end{quote}
@@
 Just as real-world social cohesion can be quantified, so can online cohesion.
-One kind of cohesion can be found in the similarity in language use on social
-media. This implicit or explicit similarity in language use can indicate shared
+One kind of cohesion is the similarity in language use on social
+media. This implicit or explicit similarity can indicate shared
 beliefs, thoughts, and feelings, as has been studied in research on language
-style in psycholinguistics and social psychology (Brennan \& Clark, 1996; Gonzales, Hancock, \& Pennebaker, 2010; Tausczik \& Pennebaker, 2010). Although previous work on language style has often
+style in psycholinguistics and social psychology (Gonzales, Hancock, and Pennebaker 2010; Tausczik and Pennebaker 2010; Brennan and Clark 1996). Although previous work on language style has often
 focused on individuals and small groups, this can be scaled up to examine
-massive social-level changes (Fusaroli et al., 2015; Michel et al., 2011).
+massive social-level changes (Michel et al. 2011; Fusaroli et al. 2015).
 
@@
 tweets---where identical and semantically similar words are repeated
-(Graesser, McNamara, Louwerse, \& Cai, 2004). These repeated lexical items constitute a theme; on Twitter,
+(Graesser et al. 2004). These repeated lexical items constitute a theme; on Twitter,
 this might be a particular hashtag, a name, a location, or other nominal
@@
 information about complexity and language structure
-(Tausczik \& Pennebaker, 2010), content words have more specialized meaning and
+(Tausczik and Pennebaker 2010), content words have more specialized meaning and
 are therefore more useful when researchers want to understand \emph{what} people are
-discussing, rather than \emph{how} they are discussing it (Graesser et al., 2004; McNamara, Graesser, McCarthy, \& Cai, 2014).
+discussing, rather than \emph{how} they are discussing it (Graesser et al. 2004; McNamara et al. 2014).
 
@@
 repeats a previous item, or refers to it through synonymous language
-(Halliday \& Hasan, 1976). In social media, we can conceive of retweets (i.e., reposts
+(Halliday and Hasan 1976). In social media, we can conceive of retweets (i.e., reposts
 or forwards of previous messages) as a form of reiteration
@@
 perspective. Previous research from political science has investigated these
-ideas (Windsor, 2020): The \enquote{Occupy Wall Street} movement has been held up as an
+ideas (Windsor 2020): The \enquote{Occupy Wall Street} movement has been held up as an
 example of a movement with low interlocutor and linguistic cohesion because of
@@
 \enquote{Black Lives Matter} placards (following the uprising in Ferguson, MO) have high
-lexical and interlocutor cohesion (Edgar \& Johnson, 2018).
+lexical and interlocutor cohesion (Edgar and Johnson 2018).
 
@@
 movements. Similar to large-scale studies of sociocultural movements (sometimes
-referred to as \emph{culturomics}; e.g., Michel et al., 2011), political
+referred to as \emph{culturomics}; e.g., Michel et al. 2011), political
 scientists can track the ways in which conversations on social media coalesce or
@@
 Real-world collective action is known to bring about a sense of togetherness,
-also known as \enquote{collective effervescence} (Durkheim, 1995). This feeling
+also known as \enquote{collective effervescence} (Durkheim 1995). This feeling
 of being a part of something larger than oneself leads individuals to act in
 ways that would not have on their own. Being overcome with this feeling can lead
-to violence (Collins, 2009; Spaaij, 2014). Conversely, increased
+to violence (Collins 2009; Spaaij 2014). Conversely, increased
 exposure to violence can result in positive social cohesion. Gilligan, Pasquale, and Samii (2014)
@@
 language is associated with rapport (both in face-to-face and computer-mediated
-conversations; Niederhoffer \& Pennebaker, 2002; Riordan, Dale, Kreuz, \& Olney, 2011) and
+conversations; Niederhoffer and Pennebaker 2002; Riordan et al. 2011) and
 can even be connected to better performance on shared tasks (as long as
-the language is relevant to the task at hand; Fusaroli et al., 2012). Shared
+the language is relevant to the task at hand; Fusaroli et al. 2012). Shared
 movement is associated with greater group bonding and greater willingness
-to contribute to the group (Wiltermuth \& Heath, 2009), and shared identity
+to contribute to the group (Wiltermuth and Heath 2009), and shared identity
 is associated with a greater willingness to adopt the group's goals and
-motivations (Walton, Cohen, Cwir, \& Spencer, 2012).
+motivations (Walton et al. 2012).
 
@@
 international action or inaction), the cohesion in social media should be
-expected to correlate with the social cohesion of the group (Zeitzoff, 2011).
+expected to correlate with the social cohesion of the group (Zeitzoff 2011).
 
@@
 insurgency movements exhibit similar patterns in their social structure
-(Bohorquez, Gourley, Dixon, Spagat, \& Johnson, 2009). Each violent group has a stable state. Exogenous events
+(Bohorquez et al. 2009). Each violent group has a stable state. Exogenous events
 can create perturbations that push the group to become either more cohesive or
@@
 or intentional cohesive online messaging---using similar language, paralleling
-in-person messaging (Windsor, 2020)---are a sign of increased organizational
+in-person messaging (Windsor 2020)---are a sign of increased organizational
 structure, inciting a government response.
@@
 and political cohesion. Shared language in an online environment may lead to the
-development or expression of a shared identity (Wiltermuth \& Heath, 2009). This,
+development or expression of a shared identity (Wiltermuth and Heath 2009). This,
 in turn, may drive individuals' propensity to engage in similar coordinated
-behavior on behalf of the group (Walton et al., 2012; Wiltermuth \& Heath, 2009).
-Taken together, these two processes may grow movement participants' weak and
-strong ties (Gladwell, 2010; Granovetter, 1973; McAdam, 1986), strengthening the movement overall by expanding and
+behavior on behalf of the group (Wiltermuth and Heath 2009; Walton et al. 2012).
+Taken together, these two processes may increase movement participants' weak and
+strong ties (Granovetter 1973; Gladwell 2010; McAdam 1986), strengthening the movement overall by expanding and
 deepening heterogenous ties. Therefore, in the context of social conflict, the
@@
 a set of activities with numerical values, rescaled to reflect a
-conflict-cooperation scale (Goldstein, 1992; Schrodt \& Hall, 2006). These event
+conflict-cooperation scale (Schrodt and Hall 2006; Goldstein 1992). These event
 codes include a range of behaviors, from making public statements and appeals,
@@
 messages whereby they reach a critical mass, whereby \enquote{behaviors, beliefs, and
-preferences} spread within a population (Barash, Cameron, \& Macy, 2012). Cohesion
+preferences} spread within a population (Barash, Cameron, and Macy 2012). Cohesion
 changes over time in response to external events and the internal dynamics of
 the social movement. This can occur even if the social interaction occurs entirely
-online (Centola \& Macy, 2007).
+online (Centola and Macy 2007).
 
@@
 Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
-(Fink, Schmidt, Barash, Cameron, \& Macy, 2016). The prevalence and rate of particular hashtags were
+(Fink et al. 2016). The prevalence and rate of particular hashtags were
 contributed to the overall sociolinguistic cohesion. The more that people
@@
 this phenomenon occurs during socially significant times like protests
-(State \& Adamic, 2015).
+(State and Adamic 2015).
 
@@
 mutually constrained and constantly interacting and influencing one another
-(Mahner \& Bunge, 1997). Investigation of the coupling of real-world
+(Mahner and Bunge 1997). Investigation of the coupling of real-world
 mobilization and social cohesion could provide new insight into the power of
@@
 bring about, or respond to, social change. Increasingly, social media platforms
-are being utilized during social mobilization (Koopmans, 2004; McAdam, Tarrow, \& Tilly, 2003), but the relationship between virtual and real-world
+are being utilized during social mobilization (McAdam, Tarrow, and Tilly 2003; Koopmans 2004), but the relationship between virtual and real-world
 mobilization is still largely unknown. The present work aims to understand how
@@
 events can pose challenges, from overpowered samples to violation of underlying
-statistical assumptions (Paxton \& Griffiths, 2017).
+statistical assumptions (Paxton and Griffiths 2017).
 
@@
 social media platforms) are constantly interacting, leading to more global
-behaviors that are larger than the sum of the parts (Turvey, 2018).
+behaviors that are larger than the sum of the parts (Turvey 2018).
 Linear analyses flatten time series data and ignore the variability that is
@@
 Although a number of other nonlinear methods exist, the primary nonlinear method
-used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, \& Webber Jr, 1998) and its offshoot, windowed cross-recurrence quantification
-analysis (WCRQA; Webber Jr \& Zbilut, 2005). CRQA has successfully been used to gain
+used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, and Webber Jr 1998) and its offshoot, windowed cross-recurrence quantification
+analysis (WCRQA; Webber Jr and Zbilut 2005). CRQA has successfully been used to gain
 a better understanding of many complex human phenomena, including a variety of
-human social interactions (for a review, see Fusaroli, Konvalinka, \& Wallot, 2014). Much as it
+human social interactions (for a review, see Fusaroli, Konvalinka, and Wallot 2014). Much as it
 has for psychology, we argue that the use of nonlinear methods in the
@@
 
-Using cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) and
-windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005), we analyzed the co-evolution of social cohesion online
+Using cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, and Webber Jr 1998) and
+windowed cross-recurrence quantification analysis (WCRQA; Webber Jr and Zbilut 2005), we analyzed the co-evolution of social cohesion online
 and real-world events. Specifically, using heterogeneous data from March 30,
@@
 gold-standard international event data (i.e., the Integrated Crisis Early
-Warning System; Boschee et al., 2015).
+Warning System; Boschee et al. 2015).
 
@@
 Event data were obtained from the 2012 Integrated Crisis Early Warning System
-(ICEWS; Boschee et al., 2015). The event data were first filtered to remove
+(ICEWS; Boschee et al. 2015). The event data were first filtered to remove
 incomplete and incorrectly formatted data. They were then filtered to include
@@
 
-We first used cross-recurrence quantification analysis (CRQA; Zbilut et al., 1998) to investigate the temporal patterns of social cohesion
+We first used cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, and Webber Jr 1998) to investigate the temporal patterns of social cohesion
 and real-world events in Syria during Arab Spring. CRQA is an extension of RQA,
 which captures the patterns of revisited states of a single time series
-(Webber Jr \& Zbilut, 1994; Zbilut \& Webber Jr, 1992). CRQA allows for two time series
+(Zbilut and Webber Jr 1992; Webber Jr and Zbilut 1994). CRQA allows for two time series
 to be projected onto one another to investigate shared states and trajectories.
@@
 still preserving a sampling rate that respects the native timescale of the
-system (cf.~Nyquist frequency in signal processing; Grenander, 1959).
+system (cf.~Nyquist frequency in signal processing; Grenander 1959).
 Because the social cohesion and event data have different scales and values, we
@@
 levels of social cohesion and counts of all, positive, and negative events on
-each day. We implemented CRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R
-(R Core Team, 2019).
+each day. We implemented CRQA using the \texttt{crqa} package (Coco and Dale 2018) for R
+(R Core Team 2019).
 
@@
 in-phase synchrony between the two time series. See Figures
-\ref{fig:plot-rp-targ-all}-\ref{fig:plot-rp-source-targ-neg} for examples of
+\ref{fig:plot-rp-targ}-\ref{fig:plot-rp-source-targ} for examples of
 RPs.
@@
 established methods of statistical significance in CRQA research (which create
-surrogate time series; e.g., Paxton \& Dale, 2017), the permutation test
+surrogate time series; e.g., Paxton and Dale 2017), the permutation test
 approach to significance testing allows the researcher to use a time series as
@@
 of event count) to determine statistical difference from chance for each CRQA
-metric. Using the \texttt{sample} function in base R (R Core Team, 2019), \(1000\) permuted time
+metric. Using the \texttt{sample} function in base R (R Core Team 2019), \(1000\) permuted time
 series were created for each of the real time series. CRQA was then run \(1000\)
@@
 
-We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr \& Zbilut, 2005) to further investigate the evolution of the temporal
+We used windowed cross-recurrence quantification analysis (WCRQA; Webber Jr and Zbilut 2005) to further investigate the evolution of the temporal
 dynamics of social cohesion and real-world events. In this analysis, a smaller
@@
 windows can reveal changes in dynamics that can then be linked to external,
-real-world events. We implemented WCRQA using the \texttt{crqa} package (Coco \& Dale, 2018) for R
-(R Core Team, 2019).
+real-world events. We implemented WCRQA using the \texttt{crqa} package (Coco and Dale 2018) for R
+(R Core Team 2019).
 
@@
 a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
-metrics did not reach significance (Figure \ref{fig:plot-rp-targ-all};
+metrics did not reach significance (Figure \ref{fig:plot-rp-targ};
 \autoref{table-1}).
@@
 found no statistically significant difference from chance for any of the metrics
-other than TT (Figure \ref{fig:plot-rp-targ-pos}; \autoref{table-1}).
+other than TT (Figure \ref{fig:plot-rp-targ}; \autoref{table-1}).
 
@@
 ENTR, LAM, and TT. All other metrics did not reach significance (Figure
-\ref{fig:plot-rp-targ-neg}; \autoref{table-1}).
+\ref{fig:plot-rp-targ}; \autoref{table-1}).
 
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target-rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target-rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from target filtered data.}\label{fig:plot-rp-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/target-rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from target filtered data.}\label{fig:plot-rp-targ-neg}
+\includegraphics[width=1\linewidth]{./results/primary/crqa/target-rp-joined} \caption{Recurrence plot (RP) for social cohesion and count of all events from target filtered data.}\label{fig:plot-rp-targ}
 \end{figure}
@@
 a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
-were non-significant (Figure \ref{fig:plot-rp-source-targ-all};
+were non-significant (Figure \ref{fig:plot-rp-source-targ};
 \autoref{table-2}).
@@
 found a statistical difference from chance for maxL, ENTR, and LAM (Figure
-\ref{fig:plot-rp-source-targ-pos}; \autoref{table-2}).
+\ref{fig:plot-rp-source-targ}; \autoref{table-2}).
 
@@
 found a statistical difference from chance for DET, NRLINE, and rENTR. All other
-metrics were non-significant (Figure \ref{fig:plot-rp-source-targ-neg};
+metrics were non-significant (Figure \ref{fig:plot-rp-source-targ};
 \autoref{table-2}).
@@
 \begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-all_events} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ-all}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-pos_events} \caption{Recurrence plot (RP) for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-rp-source-targ-pos}
-\end{figure}
-
-\begin{figure}
-\includegraphics[width=4in]{./results/primary/crqa/source_target-rp-neg_events} \caption{Recurrence plot (RP) for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-rp-source-targ-neg}
+\includegraphics[width=1\linewidth]{./results/primary/crqa/source_target-rp-joined} \caption{Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-rp-source-targ}
 \end{figure}
@@
 Nonlinear methods have been transformative for a variety of research areas
-(including psychology, Coco \& Dale, 2014). One of the goals in the present work was
+(including psychology, Coco and Dale 2014). One of the goals in the present work was
 to introduce variants of one kind of nonlinear method---specifically, recurrence
@@
 guides can provide detailed explanations of the methods and their statistical
-underpinnings (e.g., Riley \& Van Orden, 2005; Webber Jr \& Zbilut, 1994, 2005), one of the most important considerations that should be
+underpinnings (e.g., Riley and Van Orden 2005; Webber Jr and Zbilut 1994, 2005), one of the most important considerations that should be
 briefly summarized here is about data.
@@
 granularity of the data. One possible means of achieving this may be through
-collaborative efforts like the Open Event Data Alliance (Schrodt, Beieler, \& Idris, 2014).
+collaborative efforts like the Open Event Data Alliance (Schrodt, Beieler, and Idris 2014).
 
@@
 \leavevmode\hypertarget{ref-anderson2011demystifying}{}%
-Anderson, L. (2011). Demystifying the Arab Spring: Parsing the differences between Tunisia, Egypt, and Libya. \emph{Foreign Aff.}, \emph{90}, 2.
+Anderson, Lisa. 2011. ``Demystifying the Arab Spring: Parsing the Differences Between Tunisia, Egypt, and Libya.'' \emph{Foreign Aff.} 90: 2.
 
 \leavevmode\hypertarget{ref-anyanwu2002economic}{}%
-Anyanwu, J. C. (2002). \emph{Economic and political causes of civil wars in Africa: Some econometric results}. African Development Bank Abidjan, Côte d'Ivoire.
+Anyanwu, John C. 2002. \emph{Economic and Political Causes of Civil Wars in Africa: Some Econometric Results}. African Development Bank Abidjan, Côte d'Ivoire.
 
 \leavevmode\hypertarget{ref-barash2012critical}{}%
-Barash, V., Cameron, C., \& Macy, M. (2012). Critical phenomena in complex contagions. \emph{Social Networks}, \emph{34}(4), 451--461.
+Barash, Vladimir, Christopher Cameron, and Michael Macy. 2012. ``Critical Phenomena in Complex Contagions.'' \emph{Social Networks} 34 (4): 451--61.
 
 \leavevmode\hypertarget{ref-bohorquez2009common}{}%
-Bohorquez, J. C., Gourley, S., Dixon, A. R., Spagat, M., \& Johnson, N. F. (2009). Common ecology quantifies human insurgency. \emph{Nature}, \emph{462}(7275), 911--914.
+Bohorquez, Juan Camilo, Sean Gourley, Alexander R Dixon, Michael Spagat, and Neil F Johnson. 2009. ``Common Ecology Quantifies Human Insurgency.'' \emph{Nature} 462 (7275): 911--14.
 
 \leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
-Boschee, E., Lautenschlager, J., O'Brien, S., Shellman, S., Starz, J., \& Ward, M.
-(2015).
-\emph{ICEWS Coded Event Data} (Version V27) {[}Data set{]}.
-Harvard Dataverse.
-\url{https://doi.org/10.7910/DVN/28075}
+Boschee, Elizabeth, Jennifer Lautenschlager, Sean O'Brien, Steve Shellman, James Starz, and Michael Ward. 2015. ``ICEWS Coded Event Data.'' Harvard Dataverse. \url{https://doi.org/10.7910/DVN/28075}.
 
 \leavevmode\hypertarget{ref-brennan1996conceptual}{}%
-Brennan, S. E., \& Clark, H. H. (1996). Conceptual pacts and lexical choice in conversation. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{22}(6), 1482.
+Brennan, Susan E, and Herbert H Clark. 1996. ``Conceptual Pacts and Lexical Choice in Conversation.'' \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition} 22 (6): 1482.
 
 \leavevmode\hypertarget{ref-cederman2007beyond}{}%
-Cederman, L.-E., \& Girardin, L. (2007). Beyond fractionalization: Mapping ethnicity onto nationalist insurgencies. \emph{American Political Science Review}, \emph{101}(1), 173--185.
+Cederman, Lars-Erik, and Luc Girardin. 2007. ``Beyond Fractionalization: Mapping Ethnicity onto Nationalist Insurgencies.'' \emph{American Political Science Review} 101 (1): 173--85.
 
 \leavevmode\hypertarget{ref-centola2007complex}{}%
-Centola, D., \& Macy, M. (2007). Complex contagions and the weakness of long ties. \emph{American Journal of Sociology}, \emph{113}(3), 702--734.
+Centola, Damon, and Michael Macy. 2007. ``Complex Contagions and the Weakness of Long Ties.'' \emph{American Journal of Sociology} 113 (3): 702--34.
+
+\leavevmode\hypertarget{ref-R-crqa}{}%
+Coco, Moreno I., and Rick Dale. 2018. \emph{Crqa: Cross-Recurrence Quantification Analysis for Categorical and Continuous Time-Series}. \url{https://CRAN.R-project.org/package=crqa}.
 
 \leavevmode\hypertarget{ref-coco2014cross}{}%
-Coco, M. I., \& Dale, R. (2014). Cross-recurrence quantification analysis of categorical and continuous time series: An r package. \emph{Frontiers in Psychology}, \emph{5}, 510.
-
-\leavevmode\hypertarget{ref-R-crqa}{}%
-Coco, M. I., \& Dale, R. (2018). \emph{Crqa: Cross-recurrence quantification analysis for categorical and continuous time-series}. Retrieved from \url{https://CRAN.R-project.org/package=crqa}
+Coco, Moreno I, and Rick Dale. 2014. ``Cross-Recurrence Quantification Analysis of Categorical and Continuous Time Series: An R Package.'' \emph{Frontiers in Psychology} 5: 510.
 
 \leavevmode\hypertarget{ref-collier2004greed}{}%
-Collier, P., \& Hoeffler, A. (2004). Greed and grievance in civil war. \emph{Oxford Economic Papers}, \emph{56}(4), 563--595.
+Collier, Paul, and Anke Hoeffler. 2004. ``Greed and Grievance in Civil War.'' \emph{Oxford Economic Papers} 56 (4): 563--95.
 
 \leavevmode\hypertarget{ref-collins2009violence}{}%
-Collins, R. (2009). \emph{Violence: A micro-sociological theory}. Princeton University Press.
+Collins, Randall. 2009. \emph{Violence: A Micro-Sociological Theory}. Princeton University Press.
 
 \leavevmode\hypertarget{ref-comninos2011twitter}{}%
-Comninos, A. (2011). \emph{Twitter revolutions and cyber crackdowns}. Association for Progressive Communications.
+Comninos, Alex. 2011. \emph{Twitter Revolutions and Cyber Crackdowns}. Association for Progressive Communications.
 
 \leavevmode\hypertarget{ref-durkheim1995elementary}{}%
-Durkheim, E. (1995). The elementary forms of religious life, terj. Karen e. Fields. \emph{New York: Free Press.}, \emph{42}, 651669.
+Durkheim, Emile. 1995. ``The Elementary Forms of Religious Life, Terj. Karen E. Fields.'' \emph{New York: Free Press.} 42: 651669.
 
 \leavevmode\hypertarget{ref-edgar2018struggle}{}%
-Edgar, A. N., \& Johnson, A. E. (2018). \emph{The struggle over black lives matter and all lives matter}. Rowman \& Littlefield.
+Edgar, Amanda Nell, and Andre E Johnson. 2018. \emph{The Struggle over Black Lives Matter and All Lives Matter}. Rowman \& Littlefield.
 
 \leavevmode\hypertarget{ref-eisinger1973conditions}{}%
-Eisinger, P. K. (1973). The conditions of protest behavior in american cities. \emph{American Political Science Review}, \emph{67}(1), 11--28.
+Eisinger, Peter K. 1973. ``The Conditions of Protest Behavior in American Cities.'' \emph{American Political Science Review} 67 (1): 11--28.
 
 \leavevmode\hypertarget{ref-fink2016complex}{}%
-Fink, C., Schmidt, A., Barash, V., Cameron, C., \& Macy, M.
-(2016).
-Complex contagions and the diffusion of popular twitter hashtags in nigeria.
-\emph{Social Network Analysis and Mining}, \emph{6}(1), 1.
+Fink, Clay, Aurora Schmidt, Vladimir Barash, Christopher Cameron, and Michael Macy.
+2016.
+``Complex Contagions and the Diffusion of Popular Twitter Hashtags in Nigeria.'' \emph{Social Network Analysis and Mining} 6 (1): 1.
 
 \leavevmode\hypertarget{ref-francisco1995relationship}{}%
-Francisco, R. A. (1995). The relationship between coercion and protest: An empirical evaluation in three coercive states. \emph{Journal of Conflict Resolution}, \emph{39}(2), 263--282.
+Francisco, Ronald A. 1995. ``The Relationship Between Coercion and Protest: An Empirical Evaluation in Three Coercive States.'' \emph{Journal of Conflict Resolution} 39 (2): 263--82.
 
 \leavevmode\hypertarget{ref-fusaroli2012coming}{}%
-Fusaroli, R., Bahrami, B., Olsen, K., Roepstorff, A., Rees, G., Frith, C., \& Tylén, K.
-(2012).
-Coming to terms: Quantifying the benefits of linguistic coordination.
-\emph{Psychological Science}, \emph{23}(8), 931--939.
+Fusaroli, Riccardo, Bahador Bahrami, Karsten Olsen, Andreas Roepstorff, Geraint Rees, Chris Frith, and Kristian Tylén.
+2012.
+``Coming to Terms: Quantifying the Benefits of Linguistic Coordination.'' \emph{Psychological Science} 23 (8): 931--39.
 
 \leavevmode\hypertarget{ref-fusaroli2014analyzing}{}%
-Fusaroli, R., Konvalinka, I., \& Wallot, S.
-(2014).
-Analyzing social interactions: The promises and challenges of using cross recurrence quantification analysis.
-In \emph{Translational recurrences} (pp.
-137--155).
+Fusaroli, Riccardo, Ivana Konvalinka, and Sebastian Wallot.
+2014.
+``Analyzing Social Interactions: The Promises and Challenges of Using Cross Recurrence Quantification Analysis.'' In \emph{Translational Recurrences}, 137--55.
 Springer.
@@
 \leavevmode\hypertarget{ref-fusaroli2015timescales}{}%
-Fusaroli, R., Perlman, M., Mislove, A., Paxton, A., Matlock, T., \& Dale, R. (2015). Timescales of massive human entrainment. \emph{PloS ONE}, \emph{10}(4).
+Fusaroli, Riccardo, Marcus Perlman, Alan Mislove, Alexandra Paxton, Teenie Matlock, and Rick Dale. 2015. ``Timescales of Massive Human Entrainment.'' \emph{PloS ONE} 10 (4).
 
 \leavevmode\hypertarget{ref-gates2002recruitment}{}%
-Gates, S. (2002). Recruitment and allegiance: The microfoundations of rebellion. \emph{Journal of Conflict Resolution}, \emph{46}(1), 111--130.
+Gates, Scott. 2002. ``Recruitment and Allegiance: The Microfoundations of Rebellion.'' \emph{Journal of Conflict Resolution} 46 (1): 111--30.
 
 \leavevmode\hypertarget{ref-gilligan2014civil}{}%
-Gilligan, M. J., Pasquale, B. J., \& Samii, C. (2014). Civil war and social cohesion: Lab-in-the-field evidence from nepal. \emph{American Journal of Political Science}, \emph{58}(3), 604--619.
+Gilligan, Michael J, Benjamin J Pasquale, and Cyrus Samii. 2014. ``Civil War and Social Cohesion: Lab-in-the-Field Evidence from Nepal.'' \emph{American Journal of Political Science} 58 (3): 604--19.
 
 \leavevmode\hypertarget{ref-gladwell2010revolution}{}%
-Gladwell, M. (2010). Why the revolution will not be tweeted. \emph{The New Yorker}, \emph{4}(2010), 42--49.
+Gladwell, Malcolm. 2010. ``Why the Revolution Will Not Be Tweeted.'' \emph{The New Yorker} 4 (2010): 42--49.
 
 \leavevmode\hypertarget{ref-gohdes2015pulling}{}%
-Gohdes, A. R. (2015). Pulling the plug: Network disruptions and violence in civil conflict. \emph{Journal of Peace Research}, \emph{52}(3), 352--367.
+Gohdes, Anita R. 2015. ``Pulling the Plug: Network Disruptions and Violence in Civil Conflict.'' \emph{Journal of Peace Research} 52 (3): 352--67.
 
 \leavevmode\hypertarget{ref-goldstein1992conflict}{}%
-Goldstein, J. S. (1992). A conflict-cooperation scale for WEIS events data. \emph{Journal of Conflict Resolution}, \emph{36}(2), 369--385.
+Goldstein, Joshua S. 1992. ``A Conflict-Cooperation Scale for WEIS Events Data.'' \emph{Journal of Conflict Resolution} 36 (2): 369--85.
 
 \leavevmode\hypertarget{ref-goldstone1980theories}{}%
-Goldstone, J. A. (1980). Theories of revolution: The third generation. \emph{World Politics}, \emph{32}(3), 425--453.
+Goldstone, Jack A. 1980. ``Theories of Revolution: The Third Generation.'' \emph{World Politics} 32 (3): 425--53.
 
 \leavevmode\hypertarget{ref-goldstone2011understanding}{}%
-Goldstone, J. A. (2011). Understanding the revolutions of 2011: Weakness and resilience in Middle Eastern autocracies. \emph{Foreign Affairs}, 8--16.
+---------. 2011. ``Understanding the Revolutions of 2011: Weakness and Resilience in Middle Eastern Autocracies.'' \emph{Foreign Affairs}, 8--16.
 
 \leavevmode\hypertarget{ref-gonzales2010language}{}%
-Gonzales, A. L., Hancock, J. T., \& Pennebaker, J. W. (2010). Language style matching as a predictor of social dynamics in small groups. \emph{Communication Research}, \emph{37}(1), 3--19.
+Gonzales, Amy L, Jeffrey T Hancock, and James W Pennebaker. 2010. ``Language Style Matching as a Predictor of Social Dynamics in Small Groups.'' \emph{Communication Research} 37 (1): 3--19.
 
 \leavevmode\hypertarget{ref-good2013permutation}{}%
-Good, P. (2013). \emph{Permutation tests: A practical guide to resampling methods for testing hypotheses}. Springer Science \& Business Media.
+Good, Phillip. 2013. \emph{Permutation Tests: A Practical Guide to Resampling Methods for Testing Hypotheses}. Springer Science \& Business Media.
 
 \leavevmode\hypertarget{ref-graesser2004coh}{}%
-Graesser, A.
-C., McNamara, D.
-S., Louwerse, M.
-M., \& Cai, Z.
-(2004).
-Coh-Metrix: Analysis of text on cohesion and language.
-\emph{Behavior Research Methods, Instruments, \& Computers}, \emph{36}(2), 193--202.
+Graesser, Arthur C, Danielle S McNamara, Max M Louwerse, and Zhiqiang Cai.
+2004.
+``Coh-Metrix: Analysis of Text on Cohesion and Language.'' \emph{Behavior Research Methods, Instruments, \& Computers} 36 (2): 193--202.
 
 \leavevmode\hypertarget{ref-granovetter1977strength}{}%
-Granovetter, M. S. (1973). The strength of weak ties. In \emph{American Journal of Sociology} (Vol. 78, pp. 1360--1380). JSTOR.
+Granovetter, Mark S. 1973. ``The Strength of Weak Ties.'' In \emph{American Journal of Sociology}, 78:1360--80. JSTOR.
 
 \leavevmode\hypertarget{ref-grenander1959probability}{}%
-Grenander, U. (1959). \emph{Probability and statistics: The harald cramer volume}. Alqvist \& Wiksell.
+Grenander, Ulf. 1959. \emph{Probability and Statistics: The Harald Cramer Volume}. Alqvist \& Wiksell.
 
 \leavevmode\hypertarget{ref-gurr2000peoples}{}%
-Gurr, T. R. (2000). \emph{Peoples versus states: Minorities at risk in the new century}. US Institute of Peace Press.
+Gurr, Ted Robert. 2000. \emph{Peoples Versus States: Minorities at Risk in the New Century}. US Institute of Peace Press.
 
 \leavevmode\hypertarget{ref-halliday1976cohesion}{}%
-Halliday, M. A. K., \& Hasan, R. (1976). \emph{Cohesion in English}. Longman, London.
+Halliday, Michael Alexander Kirkwood, and Ruqaiya Hasan. 1976. \emph{Cohesion in English}. Longman, London.
 
 \leavevmode\hypertarget{ref-Hoffer2011true}{}%
-Hoffer, E. (2011). \emph{The true believer: Thoughts on the nature of mass movements}. Harper Collins.
+Hoffer, Eric. 2011. \emph{The True Believer: Thoughts on the Nature of Mass Movements}. Harper Collins.
 
 \leavevmode\hypertarget{ref-jones1972statistical}{}%
-Jones, K. S. (1972). A statistical interpretation of term specificity and its application in retrieval. \emph{Journal of Documentation}.
+Jones, Karen Sparck. 1972. ``A Statistical Interpretation of Term Specificity and Its Application in Retrieval.'' \emph{Journal of Documentation}.
 
 \leavevmode\hypertarget{ref-king2013censorship}{}%
-King, G., Pan, J., \& Roberts, M. E. (2013). How censorship in China allows government criticism but silences collective expression. \emph{American Political Science Review}, \emph{107}(2), 326--343.
+King, Gary, Jennifer Pan, and Margaret E Roberts.
+2013.
+``How Censorship in China Allows Government Criticism but Silences Collective Expression.'' \emph{American Political Science Review} 107 (2): 326--43.
 
 \leavevmode\hypertarget{ref-kitschelt1986political}{}%
-Kitschelt, H. P. (1986). Political opportunity structures and political protest: Anti-nuclear movements in four democracies. \emph{British Journal of Political Science}, \emph{16}(1), 57--85.
+Kitschelt, Herbert P. 1986. ``Political Opportunity Structures and Political Protest: Anti-Nuclear Movements in Four Democracies.'' \emph{British Journal of Political Science} 16 (1): 57--85.
 
 \leavevmode\hypertarget{ref-koehler2017political}{}%
-Koehler, K. (2017). Political militaries in popular uprisings: A comparative perspective on the arab spring. \emph{International Political Science Review}, \emph{38}(3), 363--377.
+Koehler, Kevin. 2017. ``Political Militaries in Popular Uprisings: A Comparative Perspective on the Arab Spring.'' \emph{International Political Science Review} 38 (3): 363--77.
 
 \leavevmode\hypertarget{ref-koopmans2004movements}{}%
-Koopmans, R. (2004). Movements and media: Selection processes and evolutionary dynamics in the public sphere. \emph{Theory and Society}, \emph{33}(3-4), 367--391.
+Koopmans, Ruud. 2004. ``Movements and Media: Selection Processes and Evolutionary Dynamics in the Public Sphere.'' \emph{Theory and Society} 33 (3-4): 367--91.
 
 \leavevmode\hypertarget{ref-lutterbeck2013arab}{}%
-Lutterbeck, D. (2013). Arab uprisings, armed forces, and civil--military relations. \emph{Armed Forces \& Society}, \emph{39}(1), 28--52.
+Lutterbeck, Derek. 2013. ``Arab Uprisings, Armed Forces, and Civil--Military Relations.'' \emph{Armed Forces \& Society} 39 (1): 28--52.
 
 \leavevmode\hypertarget{ref-mahner1997foundations}{}%
-Mahner, M., \& Bunge, M. (1997). \emph{Foundations of biophilosophy}. Springer Science \& Business Media.
+Mahner, Martin, and Mario Bunge. 1997. \emph{Foundations of Biophilosophy}. Springer Science \& Business Media.
 
 \leavevmode\hypertarget{ref-mcadam1986recruitment}{}%
-McAdam, D. (1986). Recruitment to high-risk activism: The case of freedom summer. \emph{American Journal of Sociology}, \emph{92}(1), 64--90.
+McAdam, Doug. 1986. ``Recruitment to High-Risk Activism: The Case of Freedom Summer.'' \emph{American Journal of Sociology} 92 (1): 64--90.
 
 \leavevmode\hypertarget{ref-mcadam1993specifying}{}%
-McAdam, D., \& Paulsen, R. (1993). Specifying the relationship between social ties and activism. \emph{American Journal of Sociology}, \emph{99}(3), 640--667.
+McAdam, Doug, and Ronnelle Paulsen. 1993. ``Specifying the Relationship Between Social Ties and Activism.'' \emph{American Journal of Sociology} 99 (3): 640--67.
 
 \leavevmode\hypertarget{ref-mcadam2003dynamics}{}%
-McAdam, D., Tarrow, S., \& Tilly, C. (2003). Dynamics of contention. \emph{Social Movement Studies}, \emph{2}(1), 99--102.
+McAdam, Doug, Sidney Tarrow, and Charles Tilly. 2003. ``Dynamics of Contention.'' \emph{Social Movement Studies} 2 (1): 99--102.
 
 \leavevmode\hypertarget{ref-mcnamara2014automated}{}%
-McNamara, D. S., Graesser, A. C., McCarthy, P. M., \& Cai, Z. (2014). \emph{Automated evaluation of text and discourse with Coh-Metrix}. Cambridge University Press.
+McNamara, Danielle S, Arthur C Graesser, Philip M McCarthy, and Zhiqiang Cai. 2014. \emph{Automated Evaluation of Text and Discourse with Coh-Metrix}. Cambridge University Press.
 
 \leavevmode\hypertarget{ref-michel2011quantitative}{}%
-Michel, J.-B., Shen, Y.
-K., Aiden, A.
-P., Veres, A., Gray, M.
-K., Pickett, J.
-P., \ldots{} others.
-(2011).
-Quantitative analysis of culture using millions of digitized books.
-\emph{Science}, \emph{331}(6014), 176--182.
+Michel, Jean-Baptiste, Yuan Kui Shen, Aviva Presser Aiden, Adrian Veres, Matthew K Gray, Joseph P Pickett, Dale Hoiberg, et al.
+2011.
+``Quantitative Analysis of Culture Using Millions of Digitized Books.'' \emph{Science} 331 (6014): 176--82.
 
 \leavevmode\hypertarget{ref-niederhoffer2002linguistic}{}%
-Niederhoffer, K. G., \& Pennebaker, J. W. (2002). Linguistic style matching in social interaction. \emph{Journal of Language and Social Psychology}, \emph{21}(4), 337--360.
+Niederhoffer, Kate G, and James W Pennebaker. 2002. ``Linguistic Style Matching in Social Interaction.'' \emph{Journal of Language and Social Psychology} 21 (4): 337--60.
 
 \leavevmode\hypertarget{ref-olson1965logic}{}%
-Olson, M. (1965). \emph{The logic of collective action}. Harvard University Press.
+Olson, Mancur. 1965. \emph{The Logic of Collective Action}. Harvard University Press.
 
 \leavevmode\hypertarget{ref-paxton2017interpersonal}{}%
-Paxton, A., \& Dale, R. (2017). Interpersonal movement synchrony responds to high-and low-level conversational constraints. \emph{Frontiers in Psychology}, \emph{8}, 1135.
+Paxton, Alexandra, and Rick Dale. 2017. ``Interpersonal Movement Synchrony Responds to High-and Low-Level Conversational Constraints.'' \emph{Frontiers in Psychology} 8: 1135.
 
 \leavevmode\hypertarget{ref-paxton2017finding}{}%
-Paxton, A., \& Griffiths, T.
-L.
-(2017).
-Finding the traces of behavioral and cognitive processes in big data and naturally occurring datasets.
-\emph{Behavior Research Methods}, \emph{49}(5), 1630--1638.
+Paxton, Alexandra, and Thomas L Griffiths.
+2017.
+``Finding the Traces of Behavioral and Cognitive Processes in Big Data and Naturally Occurring Datasets.'' \emph{Behavior Research Methods} 49 (5): 1630--8.
 
 \leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+R Core Team. 2019. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.
 
 \leavevmode\hypertarget{ref-regan2005greed}{}%
-Regan, P. M., \& Norton, D. (2005). Greed, grievance, and mobilization in civil wars. \emph{Journal of Conflict Resolution}, \emph{49}(3), 319--336.
+Regan, Patrick M, and Daniel Norton. 2005. ``Greed, Grievance, and Mobilization in Civil Wars.'' \emph{Journal of Conflict Resolution} 49 (3): 319--36.
 
 \leavevmode\hypertarget{ref-riley2005tutorials}{}%
-Riley, M. A., \& Van Orden, G. C. (Eds.). (2005). \emph{Tutorials in contemporary nonlinear methods for the behavioral sciences}. National Science Foundation.
+Riley, Michael A, and Guy C Van Orden, eds. 2005. \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences}. National Science Foundation.
 
 \leavevmode\hypertarget{ref-riordan2011evidence}{}%
-Riordan, M., Dale, R., Kreuz, R., \& Olney, A.
-(2011).
-Evidence for alignment in a computer-mediated text-only environment.
-In \emph{Proceedings of the annual meeting of the cognitive science society} (Vol.
-33).
+Riordan, Monica, Rick Dale, Roger Kreuz, and Andrew Olney.
+2011.
+``Evidence for Alignment in a Computer-Mediated Text-Only Environment.'' In \emph{Proceedings of the Annual Meeting of the Cognitive Science Society}.
+Vol.
+33.
+33.
 
 \leavevmode\hypertarget{ref-robertson2004understanding}{}%
-Robertson, S. (2004). Understanding inverse document frequency: On theoretical arguments for idf. \emph{Journal of Documentation}.
+Robertson, Stephen. 2004. ``Understanding Inverse Document Frequency: On Theoretical Arguments for Idf.'' \emph{Journal of Documentation}.
 
 \leavevmode\hypertarget{ref-sambanis2009s}{}%
-Sambanis, N., \& Schulhofer-Wohl, J. (2009). What's in a line? Is partition a solution to civil war? \emph{International Security}, \emph{34}(2), 82--118.
+Sambanis, Nicholas, and Jonah Schulhofer-Wohl. 2009. ``What's in a Line? Is Partition a Solution to Civil War?'' \emph{International Security} 34 (2): 82--118.
 
 \leavevmode\hypertarget{ref-schrodt2014three}{}%
-Schrodt, P.
-A., Beieler, J., \& Idris, M.
-(2014).
-Three's a charm?: Open event data coding with EL:DIABLO, PETRARCH, and the Open Event Data Alliance.
-In \emph{International studies association annual convention}.
+Schrodt, Philip A, John Beieler, and Muhammed Idris.
+2014.
+``Three's a Charm?: Open Event Data Coding with EL:DIABLO, PETRARCH, and the Open Event Data Alliance.'' In \emph{International Studies Association Annual Convention}.
 
 \leavevmode\hypertarget{ref-schrodt2006twenty}{}%
-Schrodt, P. A., \& Hall, B. (2006). Twenty years of the Kansas event data system project. \emph{The Political Methodologist}, \emph{14}(1), 2--8.
+Schrodt, Philip A, and Blake Hall. 2006. ``Twenty Years of the Kansas Event Data System Project.'' \emph{The Political Methodologist} 14 (1): 2--8.
 
 \leavevmode\hypertarget{ref-seay2014slacktivism}{}%
-Seay, L. (2014). Does slacktivism work? \emph{The Washington Post}, \emph{12}.
+Seay, Laura. 2014. ``Does Slacktivism Work?'' \emph{The Washington Post} 12.
 
 \leavevmode\hypertarget{ref-spaaij2014sports}{}%
-Spaaij, R. (2014). Sports crowd violence: An interdisciplinary synthesis. \emph{Aggression and Violent Behavior}, \emph{19}(2), 146--155.
+Spaaij, Ramón. 2014. ``Sports Crowd Violence: An Interdisciplinary Synthesis.'' \emph{Aggression and Violent Behavior} 19 (2): 146--55.
 
 \leavevmode\hypertarget{ref-state2015diffusion}{}%
-State, B., \& Adamic, L.
-(2015).
-The diffusion of support in an online social movement: Evidence from the adoption of equal-sign profile pictures.
-In \emph{Proceedings of the 18th acm conference on computer supported cooperative work \& social computing} (pp.
-1741--1750).
+State, Bogdan, and Lada Adamic.
+2015.
+``The Diffusion of Support in an Online Social Movement: Evidence from the Adoption of Equal-Sign Profile Pictures.'' In \emph{Proceedings of the 18th Acm Conference on Computer Supported Cooperative Work \& Social Computing}, 1741--50.
 
 \leavevmode\hypertarget{ref-steinert2017spontaneous}{}%
-Steinert-Threlkeld, Z. C. (2017). Spontaneous collective action: Peripheral mobilization during the Arab Spring. \emph{American Political Science Review}, \emph{111}(2), 379--403.
+Steinert-Threlkeld, Zachary C. 2017. ``Spontaneous Collective Action: Peripheral Mobilization During the Arab Spring.'' \emph{American Political Science Review} 111 (2): 379--403.
 
 \leavevmode\hypertarget{ref-tausczik2010psychological}{}%
-Tausczik, Y. R., \& Pennebaker, J. W. (2010). The psychological meaning of words: LIWC and computerized text analysis methods. \emph{Journal of Language and Social Psychology}, \emph{29}(1), 24--54.
+Tausczik, Yla R, and James W Pennebaker. 2010. ``The Psychological Meaning of Words: LIWC and Computerized Text Analysis Methods.'' \emph{Journal of Language and Social Psychology} 29 (1): 24--54.
 
 \leavevmode\hypertarget{ref-tilly2004contentious}{}%
-Tilly, C. (2004). Contentious choices. \emph{Theory and Society}, \emph{33}(3-4), 473--481.
+Tilly, Charles. 2004. ``Contentious Choices.'' \emph{Theory and Society} 33 (3-4): 473--81.
 
 \leavevmode\hypertarget{ref-turvey2018lectures}{}%
-Turvey, M. T. (2018). \emph{Lectures on perception: An ecological perspective}. Routledge.
+Turvey, Michael T. 2018. \emph{Lectures on Perception: An Ecological Perspective}. Routledge.
 
 \leavevmode\hypertarget{ref-vicari2013public}{}%
-Vicari, S. (2013). Public reasoning around social contention: A case study of Twitter use in the Italian mobilization for global change. \emph{Current Sociology}, \emph{61}(4), 474--490.
+Vicari, Stefania. 2013. ``Public Reasoning Around Social Contention: A Case Study of Twitter Use in the Italian Mobilization for Global Change.'' \emph{Current Sociology} 61 (4): 474--90.
 
 \leavevmode\hypertarget{ref-walton2012mere}{}%
-Walton, G. M., Cohen, G. L., Cwir, D., \& Spencer, S. J. (2012). Mere belonging: The power of social connections. \emph{Journal of Personality and Social Psychology}, \emph{102}(3), 513.
+Walton, Gregory M, Geoffrey L Cohen, David Cwir, and Steven J Spencer. 2012. ``Mere Belonging: The Power of Social Connections.'' \emph{Journal of Personality and Social Psychology} 102 (3): 513.
 
 \leavevmode\hypertarget{ref-webber1994dynamical}{}%
-Webber Jr, C. L., \& Zbilut, J. P. (1994). Dynamical assessment of physiological systems and states using recurrence plot strategies. \emph{Journal of Applied Physiology}, \emph{76}(2), 965--973.
+Webber Jr, Charles L, and Joseph P Zbilut. 1994. ``Dynamical Assessment of Physiological Systems and States Using Recurrence Plot Strategies.'' \emph{Journal of Applied Physiology} 76 (2): 965--73.
 
 \leavevmode\hypertarget{ref-webber2005recurrence}{}%
-Webber Jr, C.
-L., \& Zbilut, J.
-P.
-(2005).
-Recurrence quantification analysis of nonlinear dynamical systems.
-\emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences}, \emph{94}(2005), 26--94.
+---------. 2005. ``Recurrence Quantification Analysis of Nonlinear Dynamical Systems.'' \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences} 94 (2005): 26--94.
 
 \leavevmode\hypertarget{ref-wiltermuth2009synchrony}{}%
-Wiltermuth, S. S., \& Heath, C. (2009). Synchrony and cooperation. \emph{Psychological Science}, \emph{20}(1), 1--5.
+Wiltermuth, Scott S, and Chip Heath. 2009. ``Synchrony and Cooperation.'' \emph{Psychological Science} 20 (1): 1--5.
 
 \leavevmode\hypertarget{ref-Windsor2020}{}%
-Windsor, L. (2020). Advancing interdisciplinary work in computational communication science. \emph{Political Communication}.
+Windsor, Leah. 2020. ``Advancing Interdisciplinary Work in Computational Communication Science.'' \emph{Political Communication}.
 
 \leavevmode\hypertarget{ref-zbilut1998detecting}{}%
-Zbilut, J.
-P., Giuliani, A., \& Webber Jr, C.
-L.
-(1998).
-Detecting deterministic signals in exceptionally noisy environments using cross-recurrence quantification.
-\emph{Physics Letters A}, \emph{246}(1-2), 122--128.
+Zbilut, Joseph P, Alessandro Giuliani, and Charles L Webber Jr.
+1998.
+``Detecting Deterministic Signals in Exceptionally Noisy Environments Using Cross-Recurrence Quantification.'' \emph{Physics Letters A} 246 (1-2): 122--28.
 
 \leavevmode\hypertarget{ref-zbilut1992embeddings}{}%
-Zbilut, J. P., \& Webber Jr, C. L. (1992). Embeddings and delays as derived from quantification of recurrence plots. \emph{Physics Letters A}, \emph{171}(3-4), 199--203.
+Zbilut, Joseph P, and Charles L Webber Jr. 1992. ``Embeddings and Delays as Derived from Quantification of Recurrence Plots.'' \emph{Physics Letters A} 171 (3-4): 199--203.
 
 \leavevmode\hypertarget{ref-zeitzoff2011using}{}%
-Zeitzoff, T. (2011). Using social media to measure conflict dynamics: An application to the 2008--2009 Gaza conflict. \emph{Journal of Conflict Resolution}, \emph{55}(6), 938--969.
+Zeitzoff, Thomas. 2011. ``Using Social Media to Measure Conflict Dynamics: An Application to the 2008--2009 Gaza Conflict.'' \emph{Journal of Conflict Resolution} 55 (6): 938--69.
 
 \leavevmode\hypertarget{ref-zeitzoff2017social}{}%
-Zeitzoff, T. (2017). How social media is changing conflict. \emph{Journal of Conflict Resolution}, \emph{61}(9), 1970--1991.
+---------. 2017. ``How Social Media Is Changing Conflict.'' \emph{Journal of Conflict Resolution} 61 (9): 1970--91.
 

### 2020-06-03 manuscript-chicago.Rmd
Add introduction header and small edits

--- 2020-06-03 manuscript.Rmd
@@
 bibliography      : ["references.bib"]
+csl               : chicago.csl
 
@@
 classoption       : "man"
-header-includes   :
-  - "\\usepackage{float}"
 output            : papaja::apa6_pdf
@@
 
+## Introduction
 Prior to the advent of social media, people coordinated their protest behavior

### 2020-06-03 manuscript.tex
Bring .tex up to speed

--- 2020-06-02 manuscript.tex
@@
 \usepackage{csquotes}
-\usepackage{float}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
-\else
-  \usepackage[shorthands=off,main=english]{babel}
 \fi
@@
 power---monitors social media platforms to ascertain emerging threats
-(Comninos, 2011), such as where new groups are forming and where existing
+(Comninos, 2011), such as where new groups are forming, where existing
 groups are strengthening, where gatherings are held, and who the idea
@@
 opportunity to \enquote{lose themselves} and relinquish their individual identity in
-favor of identification with a larger group identity, contributing to a cohesive
+favor of identification with a larger group, contributing to a cohesive
 group ready and mobilized for action (Hoffer, 2011).
@@
 Previous research on social movements supports the idea that participants are
-likely to join movements when they know and have a personal connection to
+more likely to join movements when they know and have a personal connection to
 someone else already involved (McAdam, 1986). The type of collective
@@
 political opportunity structures. The political opportunity structure are
-\enquote{comprised of \emph{(sic)} specific configuration of resources, institutional
+\enquote{comprised of \emph{(sic)} specific configurations of resources, institutional
 arrangements and historical precedents for social mobilization, which facilitate
@@
 contentious politics are, in essence, a function of what the system makes
-possible. This includes the number of people and their disposition (i.e.
-nonviolent or violent), as well as their internal structure. The more cohesive a
+possible. This includes the number of people and their disposition (
+i.e.~nonviolent or violent), as well as their internal structure. The more cohesive a
 group is, the greater threat they pose to the establishment.
@@
 behavior on behalf of the group (Walton et al., 2012; Wiltermuth \& Heath, 2009).
-Taken together, these two processes may grow movement participants' weak and
+Taken together, these two processes may increase movement participants' weak and
 strong ties (Gladwell, 2010; Granovetter, 1973; McAdam, 1986), strengthening the movement overall by expanding and

### 2020-06-03 manuscript-chicago.Rmd
Format quotes

--- 2020-06-03 manuscript.Rmd
@@
 header-includes   :
-  - "\\usepackage{float}"
+  - "\\usepackage{setspace}"
 output            : papaja::apa6_pdf
@@
 
-This skepticism can be summarized in a quote by Lisa Anderson:
-
-> The important story about the 2011
+This skepticism can be summarized in a quote by Lisa @anderson2011demystifying:
+
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent The important story about the 2011
 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts. [@anderson2011demystifying]
+local contexts.
+
+\setlength{\leftskip}{0pt}
+\end{singlespace}
 
@@
 
->I know that I have been away from the media for a long time, and I have missed
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent I know that I have been away from the media for a long time, and I have missed
 having direct contact with the citizens, but I have always been following up
@@
 
+\setlength{\leftskip}{0pt}
+\end{singlespace}
 \noindent With few exceptions, Assad chose to keep social media platforms up and running.

### 2020-06-03 manuscript-chicago.Rmd
More quote formatting

@@
 
->a religious or linguistic minority
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent a religious or linguistic minority
 might suffer disproportionately in a given society, and this form of
@@
 maldistributions, it is individual penury that allows for this collective
-mobilization. [@regan2005greed]
+mobilization.
+
+\setlength{\leftskip}{0pt}
+\end{singlespace}
 

### 2020-06-04 manuscript-chicago.Rmd
Add page numbers for quotes
Small Chicago style edit
Edits to discussion

@@
 online communication on Twitter in Syria during Arab Spring. CRQA methodology
-allows us to model the relationship between sociolinguistic cohesion and
+allows us to disentangle the relationship between sociolinguistic cohesion and
 exogenous political events. This work stands alongside the model of
@@
 framework of sociolinguistic cohesion which we operationalize using a weighted
-measure of lexical relationships. We examined how social mobilization both
-virtually and physically evolve over time in tandem. Using nonlinear dynamical
-time series analyses, we investigated the theory that virtual mobilization is
-increasingly reflective of real-world events during times of strife.
+measure of lexical relationships. We examined how virtual and physical social
+mobilization evolve over time in tandem. Using nonlinear dynamical time series
+analyses, we investigated the theory that virtual mobilization is increasingly
+reflective of real-world events during times of strife.
 
@@
 cohesion. The frequency of all and negative events are thus associated with
-greater shared trajectories with social cohesion that would be expected by
+greater shared trajectories with social cohesion than would be expected by
 chance. However, when we specifically target positive events, the connection to
@@
 affect in social media in response. However, we cannot test this hypothesis with
-the current data; future research should explore the semantic content of this
-tweet corpus to determine the nature of the socially cohered language.
+the current time series data; future research should explore the semantic
+content of this tweet corpus to determine the nature of the socially cohered
+language.
 
@@
 
-# References
+# Bibliography
 

### 2020-06-04 manuscript-chicago.Rmd
More edits to discussion

@@
 through differences in the patterns of DET; above-chance DET only occurrs within
-the middle of the observation period, around a time of increased strive (as
+the middle of the observation period, around a time of increased strife (as
 noted above).
@@
 Nonlinear methods have been transformative for a variety of research areas
-[including psychology, @coco2014cross]. One of the goals in the present work was
+[including psychology, @coco2014cross]. One of the goals of the present work was
 to introduce variants of one kind of nonlinear method---specifically, recurrence
@@
 scientists to a family of powerful nonlinear dynamics analyses, our results have
-serious implications for monitoring global movements in consistent across other
-social uprisings. While state-run media in regions of authoritarian rule are
-often biased and serve as propaganda for the leader and central government, the
+serious implications for monitoring global movements across other social
+uprisings. While state-run media in regions of authoritarian rule are often
+biased and serve as propaganda for the leader and central government, the
 self-organized nature of Twitter provides a new avenue to gain insight into

### 2020-06-04 manuscript-chicago.Rmd
Small edits

@@
 scientists to a family of powerful nonlinear dynamics analyses, our results have
-serious implications for monitoring global movements across other social
-uprisings. While state-run media in regions of authoritarian rule are often
-biased and serve as propaganda for the leader and central government, the
-self-organized nature of Twitter provides a new avenue to gain insight into
-truths about uprisings and social mobilization. By conceptualizing Twitter and
-real-world events as two elements of an inextricably linked dynamical system,
-the levels of social cohesion within social media platforms could be monitored
-for fluctuations indicating shifts in power and peace. Social media mobilization
-may thus help alert the world to citizens' actions and reactions that are
-suppressed by government regimes, providing insight into events that may not
-otherwise be broadcast and allowing for faster intervention.
+serious implications for monitoring global movements. While state-run media in
+regions of authoritarian rule are often biased and serve as propaganda for the
+leader and central government, the self-organized nature of Twitter provides a
+new avenue to gain insight into truths about uprisings and social mobilization.
+By conceptualizing Twitter and real-world events as two elements of an
+inextricably linked dynamical system, the levels of social cohesion within
+social media platforms could be monitored for fluctuations indicating shifts in
+power and peace. Social media mobilization may thus help alert the world to
+citizens' actions and reactions that are suppressed by government regimes,
+providing insight into events that may not otherwise be broadcast and allowing
+for faster intervention.
 

### 2020-06-04 manuscript-chicago.Rmd
Add references to approx. figure and table locations

@@
 
+[Figure \@ref(fig:cohesion-in-tweets) about here]
+
 Typically, these analyses focus on *content words* (e.g., nouns, adjectives,
@@
 
+[Figure \@ref(fig:theoretical-framework) about here]
+
 Sociolinguistic cohesion is not a static concept. Just as social movements
@@
 ```
+
+[Figure \@ref(fig:raw-cohesion-ts) about here]
 
@@
 ```
+[Figures \@ref(fig:raw-event-ts-target) and \@ref(fig:raw-event-ts-source-target) about here]
 
@@
 [@R-base].
+
+[Figures \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]
 
@@
 
+[Figure \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]
+
 A qualitative investigation of the recurrence plots suggests a shift in dynamics
@@
 
+[Figure \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]
+
 Looking qualitatively at the recurrence plots, there again appeared to be a
@@
 
+For social cohesion and count of all events, there was a consistent period of
+above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
+one-week peaks at the beginning of the time period, DET was largely above chance
+from the 46th to the 61st window, with some exceptions (Figure
+\@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of positive events, we saw a downward trend in RR
+as the window advances throughout the sample. Interestingly, we see largely
+above-chance RR until the 50th window, with some exceptions during window
+periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
+60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of negative events, RR stayed above or almost
+above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
+above chance in the 1st and 2nd windows, with intermittent peaks in later
+windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+[Figure \@ref(fig:plot-wcrqa-targ-all) about here]
+
+### Syria as Source and Target
+
+```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
+
+```
+
 ```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Mode ICEWS event per day.'}
@@
 For social cohesion and count of all events, there was a consistent period of
-above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
-one-week peaks at the beginning of the time period, DET was largely above chance
-from the 46th to the 61st window, with some exceptions (Figure
-\@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of positive events, we saw a downward trend in RR
-as the window advances throughout the sample. Interestingly, we see largely
-above-chance RR until the 50th window, with some exceptions during window
-periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
-60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
-above chance in the 1st and 2nd windows, with intermittent peaks in later
-windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-### Syria as Source and Target
-
-```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
-
-```
-
-For social cohesion and count of all events, there was a consistent period of
 above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
@@
 2012.
+
+[Figure \@ref(fig:plot-wcrqa-source-targ-all) about here]
 
@@
 category. This supports our first hypothesis.
+
+[Figure \@ref(fig:plot-mode-event) about here]
 

### 2020-06-04 manuscript-chicago.Rmd
Fix references

@@
 exogenous political events. This work stands alongside the model of
-Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
+Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
 the role of peripheral participants in the Syrian Arab Spring movement by
-Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
+@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
 demonstrate how language and social mobilization interact with events along the

### 2020-06-05 manuscript-chicago.Rmd
Removing language for word count

@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 as the Arab Spring---consistent themes emerge through hashtags, retweets, and
-the repeated mentions of concepts such as regime, security, demonstration, and
+the repeated mentions of concepts such as regime, demonstration, and
 human rights. The cohesiveness of these themes (i.e., whether movement
@@
 
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian rule,
-ultimately leading to his death several days later. His actions served as a
-catalyst for the Tunisian Revolution, and one week after his death, Zine El
-Abidine Ben Ali---the longstanding authoritarian president---fled the country.
-The events of Tunisia rapidly spread to surrounding countries also subject to
-unjust authoritarian rule, including Yemen, Egypt, Libya, and Syria.
+In December 2010, a Tunisian man named Mohamed Bouazizi was unjustifiably
+stripped of his vendor cart by municipal officials. His humiliation led him to
+set himself on fire in protest to the authoritarian rule, leading to his death
+several days later. His actions served as a catalyst for the Tunisian
+Revolution, and one week after his death, Zine El Abidine Ben Ali---the
+longstanding authoritarian president---fled the country. The events of Tunisia
+rapidly spread to surrounding countries also subject to unjust authoritarian
+rule, including Egypt, Libya, and Syria.
 
@@
 obtain local news and information, it becomes increasingly important to
-understand just how these micro-blogs reflect real-world action.
-
-During the Arab Spring, social media provided real-time information about the
-events transpiring in countries across the Middle East and North Africa. Our
-understanding about the role of social media in social movements is still
-evolving. Some argue that these mass movements would not have been possible
-without efficient large-scale coordination, both physically on the ground and
-virtually on social media platforms.
+understand just how these micro-blogs reflect real-world action. Some argue that
+these mass movements would not have been possible without efficient large-scale
+coordination, both physically on the ground and virtually on social media
+platforms.
 
@@
 fighting moves to a new city or region, the number of casualties and wounded,
-and the types of weaponry used by parties to the conflict [@zeitzoff2017social].
-Social media is not entirely event-driven, however. In monitoring social media
-channels, government forces may respond to the perception that citizens are
-gaining strength and sympathy. Governments have been shown to be quite tolerant
-of dissent so long as it does not metamorphose into collective action
-[@king2013censorship].
+and the types of weaponry used by parties [@zeitzoff2017social]. In monitoring
+social media channels, government forces may respond to the perception that
+citizens are gaining strength and sympathy. Governments have been shown to be
+quite tolerant of dissent so long as it does not metamorphose into collective
+action [@king2013censorship].
 
@@
 
-\noindent I know that I have been away from the media for a long time, and I have missed
-having direct contact with the citizens, but I have always been following up
-with the daily occurrences and gathering the information so that my speech can
-be built on what is said by the street.
+\noindent I know that I have been away from the media for a long time, and I
+have missed having direct contact with the citizens, but I have always been
+following up with the daily occurrences and gathering the information so that my
+speech can be built on what is said by the street.
 
@@
 of social protest online and in the streets by shutting down the Internet.
-During these times, however, she finds that military repression increases.
+During these times, however, they find that military repression increases.
 However, government information about the citizens decreases; as such, many
@@
 People join social and political resistance movements because they feel a sense
-of connection to the cause. Given that people are generally risk-averse, overcoming inertia
-requires a strong connection to the group identity or a strong aversion to an
-individual, event, or political injustice [@goldstone1980theories;
+of connection to the cause. Given that people are generally risk-averse,
+overcoming inertia requires a strong connection to the group identity or a
+strong aversion to an individual, event, or political injustice
+[@goldstone1980theories;
 @goldstone2011understanding]. Political resistance offers participants the
 opportunity to “lose themselves” and relinquish their individual identity in
-favor of identification with a larger group, contributing to a cohesive
-group ready and mobilized for action [@Hoffer2011true].
-
-Previous research on social movements supports the idea that participants are
-more likely to join movements when they know and have a personal connection to
-someone else already involved [@mcadam1986recruitment]. The type of collective
-contentious behavior that manifests in society is a function of the available
-political opportunity structures. The political opportunity structure are
-“comprised of *(sic)* specific configurations of resources, institutional
-arrangements and historical precedents for social mobilization, which facilitate
-the development of protest movements in some instances and constrain them in
-others” [@kitschelt1986political]. What emerges as strategies and tactics in
-contentious politics are, in essence, a function of what the system makes
-possible. This includes the number of people and their disposition (i.e.
-nonviolent or violent), as well as their internal structure. The more cohesive a
-group is, the greater threat they pose to the establishment.
+favor of identification with a larger group, contributing to a cohesive group
+ready and mobilized for action [@Hoffer2011true].
+
+The type of collective contentious behavior that manifests in society is a
+function of the available political opportunity structures. The political
+opportunity structure are “comprised of *(sic)* specific configurations of
+resources, institutional arrangements and historical precedents for social
+mobilization, which facilitate the development of protest movements in some
+instances and constrain them in others” [@kitschelt1986political]. What emerges
+as strategies and tactics in contentious politics are, in essence, a function of
+what the system makes possible. This includes the number of people and their
+disposition (i.e. nonviolent or violent), as well as their internal structure.
+The more cohesive a group is, the greater threat they pose to the establishment.
 
@@
 ```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets.
-Content word overlap indicates a shared relationship among tweets.
-The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}
+The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}
 
@@
 close the paper with specific suggestions to political scientists interested in
-incorporating these methods into their work.
+these methods.
 

### 2020-06-05 manuscript-chicago.Rmd
Removing more language

@@
 The use of similar language can provide insight into *interlocutor cohesion*, or
-the degree to which people are talking about similar things. This can---as noted
-earlier---include people who are talking about similar things from radically
-perspectives, as well as those who are talking about something from the same
-perspective. Previous research from political science has investigated these
-ideas [@Windsor2020]: The “Occupy Wall Street” movement has been held up as an
-example of a movement with low interlocutor and linguistic cohesion because of
-its wide range of signs and slogans, while the “I am a man” protest (captured by
-Ernest Withers during the 1968 sanitation workers' strike in Memphis, TN) or the
-“Black Lives Matter” placards (following the uprising in Ferguson, MO) have high
-lexical and interlocutor cohesion [@edgar2018struggle].
+the degree to which people are talking about similar things. This can include
+people who are talking about similar things from radically perspectives, as well
+as those who are talking about something from the same perspective. Previous
+research from political science has investigated these ideas [@Windsor2020]: The
+“Occupy Wall Street” movement has been held up as an example of a movement with
+low interlocutor and linguistic cohesion because of its wide range of signs and
+slogans, while the “I am a man” protest (captured by Ernest Withers during the
+1968 sanitation workers' strike in Memphis, TN) or the “Black Lives Matter”
+placards (following the uprising in Ferguson, MO) have high lexical and
+interlocutor cohesion [@edgar2018struggle].
 
@@
 also respond to exogenous events such as spontaneous, unprovoked militarized
-conflict. If government forces target a new location using military weapons,
-this can precipitate online mobilization and discussion of the event.
+conflict.
 
 Given the importance of lexical and interlocutor cohesion for messaging in
-political movements, lexical cohesion may be an important bit of trace data for
+political movements, lexical cohesion may be important trace data for
 researchers interested in leveraging social media data to analyze social
@@
 threatening to the existing regime because it reflects collective opposition
-momentum and the professionalization of potential alternate leadership. Groups
-with high social cohesion are more difficult to divide and conquer, and more
-cohesive messages may also garner increased international support. Global
+momentum and the professionalization of potential alternate leadership. Global
 insurgency movements exhibit similar patterns in their social structure
-[@bohorquez2009common]. Each violent group has a stable state. Exogenous events
-can create perturbations that push the group to become either more cohesive or
-more fragmented. Rather than frenetic, patchwork messages via Twitter, emergent
-or intentional cohesive online messaging---using similar language, paralleling
-in-person messaging [@Windsor2020]---are a sign of increased organizational
-structure, inciting a government response.
+[@bohorquez2009common]. Rather than frenetic, patchwork messages via Twitter,
+emergent or intentional cohesive online messaging---using similar language,
+paralleling in-person messaging [@Windsor2020]---are a sign of increased
+organizational structure, inciting a government response.
 
@@
 Political and social cohesion in the world can be modeled using event data which
-encodes who does what to whom on a given day. This could include events such as
-the government imposing a blockade or fighting with artillery or tanks on
-a civilian group. CAMEO (Conflict and Mediation Event Observations) encode
-a set of activities with numerical values, rescaled to reflect a
-conflict-cooperation scale [@schrodt2006twenty; @goldstein1992conflict]. These event
-codes include a range of behaviors, from making public statements and appeals,
-to demanding, threatening, protesting, and using unconventional mass violence.
+encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
+Event Observations) encode a set of activities with numerical values, rescaled
+to reflect a conflict-cooperation scale [@schrodt2006twenty;
+@goldstein1992conflict]. These event codes include a range of behaviors, from
+making public statements and appeals, to demanding, threatening, protesting, and
+using unconventional mass violence.
 
@@
 a theoretical framework called *sociolinguistic cohesion*, as shown in Figure
-\@ref(fig:theoretical-framework). Several interconnected mechanisms are in
-motion here. Previous values of linguistic cohesion should influence future
-values of linguistic cohesion and future actions in the real world space.
+\@ref(fig:theoretical-framework). Previous values of linguistic cohesion should influence future values of linguistic cohesion and future actions in the real world space.
 Previous events influence future events and future linguistic cohesion in
@@
 states of the political sphere. Other scholars have noted the diffusion of
-messages whereby they reach a critical mass, whereby “behaviors, beliefs, and
-preferences” spread within a population [@barash2012critical].  Cohesion
+messages whereby they reach a critical mass, allowing for “behaviors, beliefs, and
+preferences” to spread within a population [@barash2012critical]. Cohesion
 changes over time in response to external events and the internal dynamics of
-the social movement. This can occur even if the social interaction occurs entirely 
+the social movement, even if the social interaction occurs entirely 
 online [@centola2007complex].
@@
 actions and online social interactions would be enmeshed, driving and being
-driven by one another. Rather than expecting that only real-world social
-cohesion would be driven by real-world action, we would expect interaction
-between real-world and online dynamics: In this case, exposure to real-world
-violence could result in social cohesion in the virtual world. Increased social
-cohesion is thus potentially an indicator and a result of increased social
-organization and mobilization on the ground. However, this occurs within a
-context that is affected by local and international events; both exogenous
-events (like intervention by another country or international organization like
-the United Nations) and endogenous events (like the recruitment of new members
-to the rebel or resistance movement) can affect cohesion.
-
-From a dynamical systems perspective, online social cohesion and in-person
-action can be considered two complementary components of a single system,
-mutually constrained and constantly interacting and influencing one another
-[@mahner1997foundations]. Investigation of the coupling of real-world
-mobilization and social cohesion could provide new insight into the power of
-social media during mobilization and the ways in which individuals utilize it to
-bring about, or respond to, social change. Increasingly, social media platforms
-are being utilized during social mobilization [@mcadam2003dynamics;
+driven by one another. From a dynamical systems perspective, online social
+cohesion and in-person action can be considered two complementary components of
+a single system, mutually constrained and constantly interacting and influencing
+one another [@mahner1997foundations]. Investigation of the coupling of
+real-world mobilization and social cohesion could provide new insight into the
+power of social media during mobilization and the ways in which individuals
+utilize it to bring about, or respond to, social change. Increasingly, social
+media platforms are being utilized during social mobilization
+[@mcadam2003dynamics;
 @koopmans2004movements], but the relationship between virtual and real-world
@@
 
-Lexical cohesion, then, is be a useful indicator of social cohesion in
+Lexical cohesion, then, is a useful indicator of social cohesion in
 political crisis. Lexical cohesion happens at the word level. Interlocutor

### 2020-06-05 manuscript-chicago.Rmd
More removing

@@
 
+Lexical cohesion, then, is a useful indicator of social cohesion in
+political crisis. Lexical cohesion happens at the word level. Interlocutor
+cohesion happens between speakers. Political cohesion happens at the social
+level during moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion is comprised of lexical, interlocutor, and
+socio-political events, where the words and their context reveal the disposition
+of socially connected linguistic communities. It accounts for the cohesion between
+multiple speakers in an environment whose language evolves to become more
+aligned and similar. Sociolinguistic cohesion also addresses how groups involved
+in political rebellion must have internal cohesion to overcome the collective
+action problem to mount sustained resistance to state authority.
+
 Related previous work has also explored diffusion of hashtags in viral contagion in
@@
 
-Lexical cohesion, then, is a useful indicator of social cohesion in
-political crisis. Lexical cohesion happens at the word level. Interlocutor
-cohesion happens between speakers. Political cohesion happens at the social
-level during moments of political crisis, like civil wars and social movements.
-Sociolinguistic cohesion is comprised of lexical, interlocutor, and
-socio-political events, where the words and their context reveal the disposition
-of socially connected linguistic communities. Sociolinguistic cohesion combines
-the elements of lexical cohesion in that it captures the degree of similarity
-between what is said, and how it is said. It accounts for the cohesion between
-multiple speakers in an environment whose language evolves to become more
-aligned and similar. Sociolinguistic cohesion also addresses how groups involved
-in political rebellion must have internal cohesion to overcome the collective
-action problem to mount sustained resistance to state authority.
-
 ```{r theoretical-framework, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "The theoretical framework for sociolinguistic cohesion.
@@
 social media platforms) are constantly interacting, leading to more global
-behaviors that are larger than the sum of the parts [@turvey2018lectures].
-Linear analyses flatten time series data and ignore the variability that is
-fundamental to these systems and their evolution over time. However, when
+behaviors that are larger than the sum of the parts [@turvey2018lectures]. When
 analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
@@
 
-Although a number of other nonlinear methods exist, the primary nonlinear method
-used in the current work is cross-recurrence quantification analysis [CRQA;
+Although a number of other nonlinear methods exist, the primary nonlinear methods
+used in the current work are cross-recurrence quantification analysis [CRQA;
 @zbilut1998detecting] and its offshoot, windowed cross-recurrence quantification
@@
 the counts of all, positive, and negative real-world events derived from
-gold-standard international event data [i.e., the Integrated Crisis Early
-Warning System; @DVN/28075_2015].
+international event data [i.e., the Integrated Crisis Early Warning System;
+@DVN/28075_2015].
 

### 2020-06-05 manuscript-chicago.Rmd
Remove in-line figure placement references

@@
 
-[Figure \@ref(fig:cohesion-in-tweets) about here]
-
 Typically, these analyses focus on *content words* (e.g., nouns, adjectives,
@@
 social media.
-
-[Figure \@ref(fig:theoretical-framework) about here]
 
@@
 ```
-
-[Figure \@ref(fig:raw-cohesion-ts) about here]
 
@@
 ```
-[Figures \@ref(fig:raw-event-ts-target) and \@ref(fig:raw-event-ts-source-target) about here]
 
@@
 [@R-base].
-
-[Figures \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]
 
@@
 
-[Figure \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]
-
 A qualitative investigation of the recurrence plots suggests a shift in dynamics
@@
 
-[Figure \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]
-
 Looking qualitatively at the recurrence plots, there again appeared to be a
@@
 
-[Figure \@ref(fig:plot-wcrqa-targ-all) about here]
-
 ### Syria as Source and Target
@@
 2012.
-
-[Figure \@ref(fig:plot-wcrqa-source-targ-all) about here]
 
@@
 category. This supports our first hypothesis.
-
-[Figure \@ref(fig:plot-mode-event) about here]
 

### 2020-06-05 manuscript-chicago.Rmd
Snipping words

@@
 abstract: |
-  In recent years, individuals involved in social movements have taken to social
-  media platforms to reach broader audiences at rapid speeds. Although
-  micro-blogging has become a primary means of information dissemination during
-  times of turmoil, the degree to which virtual mobilization reflects or drives
-  real-world movements is unclear. Here, we explore the dynamics of real-world
-  events and Twitter social cohesion in Syria during the Arab Spring. Using the
-  nonlinear methods cross-recurrence quantification analysis and windowed
-  cross-recurrence quantification analysis, we investigate if frequency of
-  events of different intensities are coupled with social cohesion found in
-  Syrian tweets. Results indicate that virtual social cohesion is coupled with
-  the counts of all and negative events each day but shows a more nuanced
-  connection to positive events, suggesting that virtual mobilization does
-  reflect real-world movements. We conclude with a discussion of implications
-  and applications of nonlinear methods in political science research.
+  In recent years, political activists have taken to social media platforms to
+  rapidly reach broad audiences. Despite the prevalence of micro-blogging in
+  these sociopolitical movements, the degree to which virtual mobilization
+  reflects or drives real-world movements is unclear. Here, we explore the
+  dynamics of real-world events and Twitter social cohesion in Syria during the
+  Arab Spring. Using the nonlinear methods cross-recurrence quantification
+  analysis and windowed cross-recurrence quantification analysis, we investigate
+  if frequency of events of different intensities are coupled with social
+  cohesion found in Syrian tweets. Results indicate that virtual social cohesion
+  is coupled with the counts of all and negative events each day but shows a
+  more nuanced connection to positive events, suggesting that virtual
+  mobilization does reflect real-world movements. We conclude with a discussion
+  of implications and applications of nonlinear methods in political science
+  research.
   <!-- https://tinyurl.com/ybremelq -->
@@
 
-Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and mimeographed flyers, through in-person
-meetings of social organizations and churches, and through word of mouth. They
-gathered together and hand-made protest signs that reflected their agendas. As
-McAdam found, people were more likely to join movements when they had a personal
-connection [@mcadam1986recruitment; @mcadam1993specifying]: Historically, strong
-ties have been strong predictors of involvement in high-risk protest activity.
-
-The cohesiveness and strength of social movements in the pre-Internet era could
-be operationalized by the number of people turning out to protest and through
-the political events that precipitated and resulted from social gatherings *en
-masse*. Cohesive social movements were reflected in their cohesive placards and
-posters. For example, the “I am a man” posters held by the men involved in the
-1968 sanitation workers' strike reflected their internal cohesion and unified,
-goal-oriented movement [@Windsor2020].
-
-However, the rise of the Internet and its decentralized online networks has
+Before social media, people coordinated protests using phone tree calling sheets
+and mimeographed flyers, through in-person meetings of social organizations and
+churches, and by word of mouth. They gathered together and hand-made protest
+signs that reflected their agendas. As McAdam found, people were more likely to
+join movements when they had a personal connection [@mcadam1986recruitment;
+@mcadam1993specifying]: Historically, strong ties have been strong predictors of
+involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements before the Internet were
+operationalized by the number of people present and through the political events
+that precipitated and resulted from social gatherings *en masse*. Cohesive
+social movements were reflected in their cohesive placards and posters. For
+example, the pervasive “I am a man” posters during the 1968 sanitation workers'
+strike reflected their internal cohesion and unified, goal-oriented movement
+[@Windsor2020].
+
+However, the rise of the Internet and its decentralized online networks have
 upended theories about recruitment to---and participation in---social movements.
 Strong interpersonal ties have yielded to weak impersonal ties that strongly
-predict involvement in social movements [@steinert2017spontaneous]. Research
-methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to “big data” analyses of language on social media.
-
-Today, social media replicates and amplifies this phenomenon during moments of
-social unrest. Amid the cacophony of messages during political upheaval---such
+predict involvement in social movements [@steinert2017spontaneous]. Measurements
+of social movements have similarly evolved from ethnographic interviews to “big
+data” analyses of social media.
+
+Amid the cacophony of messages during political upheaval---such
 as the Arab Spring---consistent themes emerge through hashtags, retweets, and
@@
 mobilization---and social mobilization in person---continues to be relevant,
-even as our modes of communication change. The political events that
-transpired during and after the Arab Spring are still in the process of being
-understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
-changing conflict, but the mechanisms and relationships by which it does so are
-still largely unknown.
+even as our modes of communication change. Accordingly, the political events
+around the Arab Spring are still being understood. As Zeitzoff
+[-@zeitzoff2017social] recognizes, social media is changing conflict, but the
+mechanisms and relationships by which it does so are still largely unknown.
 
 ## Syria in Context
-The decades preceding the Arab Spring in Syria were marked by
-social repression and fear. In 1971, Hafez al-Assad overthrew the previous
-leader and remained in power for thirty years, presiding during
-regional contentiousness and cooperation until his death in 2000. His son,
-Bashar al-Assad continued the regime of authoritarian leadership as he assumed
-his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
-in a multi-religious and multi-ethnic country comprising Christians, Sunni and
-Shia Muslims, Kurds, and Palestinian refugees.
+The decades preceding the Arab Spring in Syria were marked by repression and
+fear. In 1971, Hafez al-Assad overthrew the previous leader and remained in
+power for thirty years, presiding during regional contentiousness and
+cooperation until his death in 2000. His son, Bashar al-Assad, continued the
+regime of authoritarian leadership after assuming his office. The Assad lineage
+hails from a minority Islamic sect (the Alawites) in a multi-religious and
+multi-ethnic country comprising Christians, Sunni and Shia Muslims, Kurds, and
+Palestinian refugees.
 
@@
 with imprisonments, detentions, censorship, and military operations as the
-resistance to Assad's regime grew and spread throughout the country. The
-fighting escalated dramatically in March 2012, after increased unrest in the
-western city of Homs. International actors---including the Red Cross/Red
-Crescent Society, the United Nations General Assembly, the Security Council, and
-individual world leaders---worked toward cease-fires, negotiations, and
-concessions without much success. While many high-level military and diplomatic
-officials defected from the regime, numerous loyal forces continued the regime's
-repression, and the Syrian people turned to social media to help coordinate
-their activism and communicate to the world. Between March and June 2012, more
-than 8 million tweets were sent within Syria, revealing the details of the
-conflict suppressed by the government.
+resistance to Assad's regime spread. The fighting escalated dramatically in
+March 2012, after increased unrest in the western city of Homs. International
+actors---including the Red Cross/Red Crescent Society, the United Nations
+General Assembly, the U.N. Security Council, and individual world
+leaders---worked toward cease-fires, negotiations, and concessions without much
+success. While many high-level military and diplomatic officials defected,
+numerous loyal forces continued the regime's repression, and the Syrian people
+turned to social media to coordinate their activism and communicate to the
+world. Between March and June 2012, more than 8 million tweets were sent within
+Syria, revealing the details of the conflict suppressed by the government.
 
 Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
-people make up between 10-15% of the population, Alawites between 8-15%,
+people make up between 10-15% of the population, Alawites between 8-15%, and
 Christians about 10%. There are also much smaller sects (e.g., Ismailis, Druze),
@@
 
-Massive online social cohesion can have real-world social manifestations. Social
-media platforms provide one way to enable this kind of online social cohesion by
-offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements an
-opportunity to complement or even replace real-world social mobilization. For
-example, during the 2012 Italian protests for global economic change, the riots
-in Rome were mirrored by Twitter activity both on the day of the protests and in
-the days following them [@vicari2013public]. Tweeting was determined to be more
-effective locally in discussing real-world, real-time events than traditional
-mainstream media platforms. As more and more individuals rely on social media to
-obtain local news and information, it becomes increasingly important to
-understand just how these micro-blogs reflect real-world action. Some argue that
-these mass movements would not have been possible without efficient large-scale
-coordination, both physically on the ground and virtually on social media
-platforms.
+Massive online social cohesion can manifest in real-world social behavior.
+Social media platforms enable online social cohesion by offering distributed
+information-gathering and real-time information dissemination. Given its
+accessibility and proficiency as an information exchange tool, Twitter has
+provided social and political activists an opportunity to complement or even
+replace real-world social mobilization. For example, during the 2012 Italian
+protests for global economic change, the riots in Rome were mirrored by Twitter
+activity both on the day of the protests and in the days following them
+[@vicari2013public]. Tweeting was determined to be more effective locally in
+discussing real-world, real-time events than traditional mainstream media
+platforms. As people increasingly rely on social media for local news and
+information, we must understand exactly how these micro-blogs connect to and
+reflect real-world action. Some argue that these mass movements would not have
+been possible without efficient large-scale coordination, both physically on the
+ground and virtually on social media platforms.
 
 Along with Facebook, Twitter has been credited as essential to the Arab
-Spring---both for protesters (as a means to coordinate with one another and to
-communicate with the world) and for the government response (to monitor and
-track protestors to crack down on dissent) [@comninos2011twitter]. The events of
-Arab Spring have been thoroughly discussed within the political science
-literature [e.g., @lutterbeck2013arab;
+Spring---both for protesters and for the government's response to them
+[@comninos2011twitter]. The Arab Spring has been deeply examined within the
+political science literature [e.g., @lutterbeck2013arab;
 @koehler2017political], but to our knowledge, the direct *coupling* between
-Syrian Twitter cohesion and international action coordination has not been
-investigated. In fact, some have been skeptical about the effect of social media
-on collective action at all [@seay2014slacktivism].
-
-This skepticism can be summarized in a quote by Lisa @anderson2011demystifying:
+Syrian Twitter cohesion and international action has not been investigated. In
+fact, some have been skeptical about the effect of social media on collective
+action at all [@seay2014slacktivism].
+
+This skepticism is summarized in a quote by Lisa @anderson2011demystifying:
 
@@
 \noindent Others have similarly expressed hesitation about the role of online
-organizing. Some have argued that real-life strong ties outweigh online weak ties and
-that the power of the strong ties through in-person contact is critical
-to recruiting people for higher-risk activities
-[@gladwell2010revolution; @mcadam1986recruitment].
-
-Interestingly, these views may
-actually help to make the case for bridging the gap between social media and
-social mobilization. Such views suggest the strength of social ties in an online
-environment is inextricably linked to the *context* and *ambitions* of the actors.
-Moreover, research suggests that weak ties still retain considerable political
-power: While strong ties tend to bind smaller groups, weak ties
-tend to bind groups across distances [@granovetter1977strength].
+organizing. Some have argued that real-life strong ties outweigh online weak
+ties and that the power of the strong ties through in-person contact is critical
+to recruiting people for higher-risk activities [@gladwell2010revolution;
+@mcadam1986recruitment].
+
+Interestingly, these views may help make the case for bridging social media and
+social mobilization. Such views suggest the strength of online social ties is
+inextricably linked to the *context* and *ambitions* of the actors. Moreover,
+research suggests that weak ties still retain considerable political power:
+While strong ties tend to bind smaller groups, weak ties tend to bind groups
+across distances [@granovetter1977strength].
 
@@
 how a demonstration will take place, how many people participate, and how those
-in power (e.g., state, military, security apparatus) respond. Similarly, these
-media platforms alert us to more global shifts within a conflict, such as when
-fighting moves to a new city or region, the number of casualties and wounded,
-and the types of weaponry used by parties [@zeitzoff2017social]. In monitoring
-social media channels, government forces may respond to the perception that
-citizens are gaining strength and sympathy. Governments have been shown to be
-quite tolerant of dissent so long as it does not metamorphose into collective
-action [@king2013censorship].
+in power (e.g., state, military) respond. Similarly, these media platforms alert
+us to more global shifts within a conflict, such as when fighting moves to a new
+city or region, the number of casualties and wounded, and the types of weaponry
+used by parties [@zeitzoff2017social]. In monitoring social media channels,
+government forces may respond to the perception that citizens are gaining
+strength and sympathy. Governments have been shown to be quite tolerant of
+dissent so long as it does not metamorphose into collective action
+[@king2013censorship].
 
@@
 [@comninos2011twitter], such as where new groups are forming, where existing
-groups are strengthening, where gatherings are held, and who the idea
-entrepreneurs are.
+groups are strengthening, where gatherings are held, and who the leaders are.
 
@@
 \end{singlespace}
-\noindent With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
-of social protest online and in the streets by shutting down the Internet.
-During these times, however, they find that military repression increases.
-However, government information about the citizens decreases; as such, many
-regimes have elected to maintain Internet connectivity as a means of monitoring
-and surveilling their citizens.
+\noindent With few exceptions, Assad chose to keep social media platforms up and
+running. Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart
+the growth of social protest online and in the streets by shutting down the
+Internet. During these times, military repression increases, but government
+information about the citizens decreases. As a result, regimes may elect to
+maintain Internet connectivity to monitor and surveil their citizens.
 
@@
 function of the available political opportunity structures. The political
-opportunity structure are “comprised of *(sic)* specific configurations of
+opportunity structure is “comprised of *(sic)* specific configurations of
 resources, institutional arrangements and historical precedents for social
@@
 instances and constrain them in others” [@kitschelt1986political]. What emerges
-as strategies and tactics in contentious politics are, in essence, a function of
+as strategies and tactics in contentious politics are a function of
 what the system makes possible. This includes the number of people and their
@@
 
-Cohesion is also a familiar concept in the study of civil conflicts, as it
-pertains to group affiliation and the ability to overcome collective action
-problems. Individuals must act in concert---that is, cohesively---to
-accomplish the task of challenging the authority of the state [@olson1965logic;
+Cohesion is a familiar concept in the study of civil conflicts, as it pertains
+to group affiliation and the ability to overcome collective action problems.
+Individuals must act in concert---that is, cohesively---to accomplish the task
+of challenging state authority [@olson1965logic;
 @eisinger1973conditions; @tilly2004contentious; @francisco1995relationship].
-Recent work has considered rebel recruitment for participation in
-civil conflicts as a function of internal cohesion [@gates2002recruitment]:
-Rebel movement success is influenced by the degree of group cohesion, which
-itself is a function of geographic distance, ideology, and ethnicity.
-Within Syria, multiple rebel groups exist, sourcing fighters locally
-from the disaffected Syrian population and internationally through
-fighters from transnational terrorist organizations. There is considerable
-intergroup competition for participation in the rebel movement and
-punishment for defectors for nonparticipation [@gates2002recruitment].
-Foreign fighters would appear to be amply motivated to fight, given their
-decision to relocate from a home country that may be located in the region
-or much farther away.
+Viewing rebel recruitment during civil conflicts as a function of internal
+cohesion, rebel movement success is influenced by the degree of group cohesion,
+which itself is a function of geographic distance, ideology, and ethnicity
+[@gates2002recruitment]. Within Syria, multiple rebel groups exist, sourcing
+fighters locally (from the disaffected Syrian population) and internationally
+(from transnational terrorist organizations). Groups compete intensely with one
+another for recruitment in the rebel movement and often punish defectors for
+nonparticipation [@gates2002recruitment].
 
@@
 
-The civil war literature has further explored the role of social cohesion in
-detail. Social homogeneity increases the likelihood of social conflict,
-especially when the society is polarized [@collier2004greed]; this is partly
-due to nationalist groups' strong identification with a collective identity
-[@cederman2007beyond] and their social solidarity [@sambanis2009s]. These
-same processes can be similarly important for rebels [@anyanwu2002economic].
-Referencing Gurr's [-@gurr2000peoples] work on minorities at
-risk, Regan and Norton [-@regan2005greed] note that
+The civil war literature has also explored the role of social cohesion. Social
+homogeneity increases the likelihood of social conflict, especially when the
+society is polarized [@collier2004greed]; this is partly due to nationalist
+groups' strong identification with a collective identity [@cederman2007beyond]
+and their social solidarity [@sambanis2009s]. These same processes can be
+similarly important for rebels [@anyanwu2002economic]. Referencing Gurr's
+[-@gurr2000peoples] work on minorities at risk, Regan and Norton
+[-@regan2005greed] note that
 
@@
 referring to the connectedness of speakers, actions, and societies. It
-reflects the continuity of language and expression, and shows the
+reflects the continuity of language and expression and shows the
 connectivity of participants in a social movement. To address the relationship
@@
 
-The words that comprise social media posts are the first level of cohesion that
-we will consider.  In Figure \@ref(fig:cohesion-in-tweets), we see four
-sequential tweets, each containing four words. Each sequential tweet contains
-some content included in the previous tweets. The linguistic construct of
-content word overlap measures the relationship across units of meaning---here,
-tweets---where identical and semantically similar words are repeated
-[@graesser2004coh]. These repeated lexical items constitute a theme; on Twitter,
-this might be a particular hashtag, a name, a location, or other nominal
-category. This localized cohesion is referential; words are repeated and
-co-referred across tweets, creating a sense of continuity and cohesiveness of
-meaning and message.
+The first level of cohesion that we will consider are the words within social
+media posts.  In Figure \@ref(fig:cohesion-in-tweets), we see four sequential
+tweets of four words each. Each sequential tweet contains some content
+included in the previous tweets. The linguistic construct of content word
+overlap measures the relationship across units of meaning---here, tweets---where
+identical and semantically similar words are repeated [@graesser2004coh]. These
+repeated lexical items constitute a theme; on Twitter, this might be a
+particular hashtag, a name, a location, or another nominal category. This
+localized cohesion is referential; words are repeated and co-referred across
+tweets, creating a sense of continuity and cohesiveness.
 
@@
 In estimating cohesion in Twitter posts, tweets that share content words
-will yield higher cohesion values, even among speakers with opposing
+yield higher cohesion values, even among speakers with opposing
 views on the subject matter. Repetition of terms and concepts is captured by
@@
 low interlocutor and linguistic cohesion because of its wide range of signs and
-slogans, while the “I am a man” protest (captured by Ernest Withers during the
-1968 sanitation workers' strike in Memphis, TN) or the “Black Lives Matter”
-placards (following the uprising in Ferguson, MO) have high lexical and
-interlocutor cohesion [@edgar2018struggle].
-
-Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
-contextualized by variation in real world events. Interlocutor cohesion may
-increase preceding an in-person social mobilization event, alerting a repressive
-government that collective mobilization is happening. Interlocutor cohesion may
-also respond to exogenous events such as spontaneous, unprovoked militarized
-conflict.
+slogans, while the “I am a man” protest (during the 1968 sanitation workers'
+strike in Memphis, TN) or the “Black Lives Matter” placards (following the
+uprising in Ferguson, MO) have high lexical and interlocutor cohesion
+[@edgar2018struggle].
+
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows, contextualized by
+changing real world events. Interlocutor cohesion may increase preceding an
+in-person social mobilization event, alerting a repressive government that
+collective mobilization is happening. Interlocutor cohesion may also respond to
+exogenous events such as spontaneous, unprovoked militarized conflict.
 
@@
 understand whether the society-level conversation is converging on similar
-language.
+themes.
 
@@
 to contribute to the group [@wiltermuth2009synchrony], and shared identity
-is associated with a greater willingness to adopt the group's goals and
+leads to a greater willingness to adopt the group's goals and
 motivations [@walton2012mere].
 
-We should expect to see increased linguistic cohesion among people participating
-in online discussions about an idea, event, individual, or movement. Given that
-Syrian protesters are known to have coordinated their activity through Twitter
-by discussing their own events (e.g., planned protests, active demonstrations)
-and their reactions to events happening around them (e.g., government reactions,
-international action or inaction), the cohesion in social media should be
-expected to correlate with the social cohesion of the group [@zeitzoff2011using].
-
-This social cohesion can have real and wide-ranging impacts on a political
-movement and the people in it. A socially cohesive group is inherently more
-threatening to the existing regime because it reflects collective opposition
-momentum and the professionalization of potential alternate leadership. Global
-insurgency movements exhibit similar patterns in their social structure
-[@bohorquez2009common]. Rather than frenetic, patchwork messages via Twitter,
-emergent or intentional cohesive online messaging---using similar language,
-paralleling in-person messaging [@Windsor2020]---are a sign of increased
-organizational structure, inciting a government response.
+We expect to see increased linguistic cohesion among people participating in
+online discussions about an idea, event, individual, or movement. Given that
+Syrian protesters coordinated their activity through Twitter by discussing their
+own events (e.g., planned protests, active demonstrations) and their reactions
+to events happening around them (e.g., government reactions, international
+action or inaction), the cohesion in social media should correlate with the
+social cohesion of the group [@zeitzoff2011using].
+
+Social cohesion can have real and wide-ranging impacts on a political movement
+and the people in it. A socially cohesive group is inherently more threatening
+to the existing regime because it reflects momentum in collective opposition and
+the professionalization of alternate leadership. Global insurgency movements
+exhibit similar patterns in their social structure [@bohorquez2009common].
+Rather than patchwork messages via Twitter, emergent or intentional cohesive
+online messaging---using similar language, paralleling in-person messaging
+[@Windsor2020]---demonstrates increased organizational structure, inciting a
+government response.
 

### 2020-06-05 manuscript-chicago.Rmd
More snipping

@@
 ## Social Media and Social Movements
-
 Massive online social cohesion can manifest in real-world social behavior.
@@
 provided social and political activists an opportunity to complement or even
-replace real-world social mobilization. For example, during the 2012 Italian
-protests for global economic change, the riots in Rome were mirrored by Twitter
-activity both on the day of the protests and in the days following them
-[@vicari2013public]. Tweeting was determined to be more effective locally in
+replace real-world social mobilization. During the 2012 Italian protests for
+global economic change, tweeting was determined to be more effective locally in
 discussing real-world, real-time events than traditional mainstream media
-platforms. As people increasingly rely on social media for local news and
-information, we must understand exactly how these micro-blogs connect to and
-reflect real-world action. Some argue that these mass movements would not have
-been possible without efficient large-scale coordination, both physically on the
-ground and virtually on social media platforms.
+platforms [@vicari2013public]. As people increasingly rely on social media for
+local news and information, we must understand exactly how these micro-blogs
+connect to and reflect real-world action.
 
@@
 above-chance RR until the 50th window, with some exceptions during window
-periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
+periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
 60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
@@
 For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
+above chance from the 4th--7th and 43rd--47th windows. DET was above or nearly
 above chance in the 1st and 2nd windows, with intermittent peaks in later
@@
 above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
-also showed above- or nearly above-chance values in windows 7 through 17 and
+also showed above- or nearly above-chance values in windows 7--17 and
 intermittent peaks between the 34th and 61st windows (Figure
@@
 and the 32nd--45th windows. DET stayed largely within chance, with the exception
-of windows 13 through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+of windows 13--19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
 
@@
 framework of sociolinguistic cohesion which we operationalize using a weighted
-measure of lexical relationships. We examined how virtual and physical social
-mobilization evolve over time in tandem. Using nonlinear dynamical time series
+measure of lexical relationships. Using nonlinear dynamical time series
 analyses, we investigated the theory that virtual mobilization is increasingly

### 2020-06-05 manuscript-chicago.tex
Submitted version

--- 2020-06-03 manuscript.tex
@@
 \makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
-\usepackage{float}
+\usepackage{setspace}
 \ifxetex
@@
 \abstract{
-In recent years, individuals involved in social movements have taken to social
-media platforms to reach broader audiences at rapid speeds. Although
-micro-blogging has become a primary means of information dissemination during
-times of turmoil, the degree to which virtual mobilization reflects or drives
-real-world movements is unclear. Here, we explore the dynamics of real-world
-events and Twitter social cohesion in Syria during the Arab Spring. Using the
-nonlinear methods cross-recurrence quantification analysis and windowed
-cross-recurrence quantification analysis, we investigate if frequency of
-events of different intensities are coupled with social cohesion found in
-Syrian tweets. Results indicate that virtual social cohesion is coupled with
-the counts of all and negative events each day but shows a more nuanced
-connection to positive events, suggesting that virtual mobilization does
-reflect real-world movements. We conclude with a discussion of implications
-and applications of nonlinear methods in political science research.
+In recent years, political activists have taken to social media platforms to
+rapidly reach broad audiences. Despite the prevalence of micro-blogging in
+these sociopolitical movements, the degree to which virtual mobilization
+reflects or drives real-world movements is unclear. Here, we explore the
+dynamics of real-world events and Twitter social cohesion in Syria during the
+Arab Spring. Using the nonlinear methods cross-recurrence quantification
+analysis and windowed cross-recurrence quantification analysis, we investigate
+if frequency of events of different intensities are coupled with social
+cohesion found in Syrian tweets. Results indicate that virtual social cohesion
+is coupled with the counts of all and negative events each day but shows a
+more nuanced connection to positive events, suggesting that virtual
+mobilization does reflect real-world movements. We conclude with a discussion
+of implications and applications of nonlinear methods in political science
+research.
 }
@@
 
-Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and mimeographed flyers, through in-person
-meetings of social organizations and churches, and through word of mouth. They
-gathered together and hand-made protest signs that reflected their agendas. As
-McAdam found, people were more likely to join movements when they had a personal
-connection (McAdam 1986; McAdam and Paulsen 1993): Historically, strong
-ties have been strong predictors of involvement in high-risk protest activity.
-
-The cohesiveness and strength of social movements in the pre-Internet era could
-be operationalized by the number of people turning out to protest and through
-the political events that precipitated and resulted from social gatherings \emph{en
-masse}. Cohesive social movements were reflected in their cohesive placards and
-posters. For example, the \enquote{I am a man} posters held by the men involved in the
-1968 sanitation workers' strike reflected their internal cohesion and unified,
-goal-oriented movement (Windsor 2020).
-
-However, the rise of the Internet and its decentralized online networks has
+Before social media, people coordinated protests using phone tree calling sheets
+and mimeographed flyers, through in-person meetings of social organizations and
+churches, and by word of mouth. They gathered together and hand-made protest
+signs that reflected their agendas. As McAdam found, people were more likely to
+join movements when they had a personal connection (McAdam 1986; McAdam and Paulsen 1993): Historically, strong ties have been strong predictors of
+involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements before the Internet were
+operationalized by the number of people present and through the political events
+that precipitated and resulted from social gatherings \emph{en masse}. Cohesive
+social movements were reflected in their cohesive placards and posters. For
+example, the pervasive \enquote{I am a man} posters during the 1968 sanitation workers'
+strike reflected their internal cohesion and unified, goal-oriented movement
+(Windsor 2020).
+
+However, the rise of the Internet and its decentralized online networks have
 upended theories about recruitment to---and participation in---social movements.
 Strong interpersonal ties have yielded to weak impersonal ties that strongly
-predict involvement in social movements (Steinert-Threlkeld 2017). Research
-methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to \enquote{big data} analyses of language on social media.
-
-Today, social media replicates and amplifies this phenomenon during moments of
-social unrest. Amid the cacophony of messages during political upheaval---such
+predict involvement in social movements (Steinert-Threlkeld 2017). Measurements
+of social movements have similarly evolved from ethnographic interviews to \enquote{big
+data} analyses of social media.
+
+Amid the cacophony of messages during political upheaval---such
 as the Arab Spring---consistent themes emerge through hashtags, retweets, and
-the repeated mentions of concepts such as regime, security, demonstration, and
+the repeated mentions of concepts such as regime, demonstration, and
 human rights. The cohesiveness of these themes (i.e., whether movement
@@
 mobilization---and social mobilization in person---continues to be relevant,
-even as our modes of communication change. The political events that
-transpired during and after the Arab Spring are still in the process of being
-understood. As Zeitzoff (2017) recognizes, social media is
-changing conflict, but the mechanisms and relationships by which it does so are
-still largely unknown.
+even as our modes of communication change. Accordingly, the political events
+around the Arab Spring are still being understood. As Zeitzoff
+(2017) recognizes, social media is changing conflict, but the
+mechanisms and relationships by which it does so are still largely unknown.
 
@@
 
-The decades preceding the Arab Spring in Syria were marked by
-social repression and fear. In 1971, Hafez al-Assad overthrew the previous
-leader and remained in power for thirty years, presiding during
-regional contentiousness and cooperation until his death in 2000. His son,
-Bashar al-Assad continued the regime of authoritarian leadership as he assumed
-his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
-in a multi-religious and multi-ethnic country comprising Christians, Sunni and
-Shia Muslims, Kurds, and Palestinian refugees.
-
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian rule,
-ultimately leading to his death several days later. His actions served as a
-catalyst for the Tunisian Revolution, and one week after his death, Zine El
-Abidine Ben Ali---the longstanding authoritarian president---fled the country.
-The events of Tunisia rapidly spread to surrounding countries also subject to
-unjust authoritarian rule, including Yemen, Egypt, Libya, and Syria.
+The decades preceding the Arab Spring in Syria were marked by repression and
+fear. In 1971, Hafez al-Assad overthrew the previous leader and remained in
+power for thirty years, presiding during regional contentiousness and
+cooperation until his death in 2000. His son, Bashar al-Assad, continued the
+regime of authoritarian leadership after assuming his office. The Assad lineage
+hails from a minority Islamic sect (the Alawites) in a multi-religious and
+multi-ethnic country comprising Christians, Sunni and Shia Muslims, Kurds, and
+Palestinian refugees.
+
+In December 2010, a Tunisian man named Mohamed Bouazizi was unjustifiably
+stripped of his vendor cart by municipal officials. His humiliation led him to
+set himself on fire in protest to the authoritarian rule, leading to his death
+several days later. His actions served as a catalyst for the Tunisian
+Revolution, and one week after his death, Zine El Abidine Ben Ali---the
+longstanding authoritarian president---fled the country. The events of Tunisia
+rapidly spread to surrounding countries also subject to unjust authoritarian
+rule, including Egypt, Libya, and Syria.
 
@@
 with imprisonments, detentions, censorship, and military operations as the
-resistance to Assad's regime grew and spread throughout the country. The
-fighting escalated dramatically in March 2012, after increased unrest in the
-western city of Homs. International actors---including the Red Cross/Red
-Crescent Society, the United Nations General Assembly, the Security Council, and
-individual world leaders---worked toward cease-fires, negotiations, and
-concessions without much success. While many high-level military and diplomatic
-officials defected from the regime, numerous loyal forces continued the regime's
-repression, and the Syrian people turned to social media to help coordinate
-their activism and communicate to the world. Between March and June 2012, more
-than 8 million tweets were sent within Syria, revealing the details of the
-conflict suppressed by the government.
+resistance to Assad's regime spread. The fighting escalated dramatically in
+March 2012, after increased unrest in the western city of Homs. International
+actors---including the Red Cross/Red Crescent Society, the United Nations
+General Assembly, the U.N. Security Council, and individual world
+leaders---worked toward cease-fires, negotiations, and concessions without much
+success. While many high-level military and diplomatic officials defected,
+numerous loyal forces continued the regime's repression, and the Syrian people
+turned to social media to coordinate their activism and communicate to the
+world. Between March and June 2012, more than 8 million tweets were sent within
+Syria, revealing the details of the conflict suppressed by the government.
 
 Syria is a multi-ethnic, multi-lingual, and multi-religious state. Kurdish
-people make up between 10-15\% of the population, Alawites between 8-15\%,
+people make up between 10-15\% of the population, Alawites between 8-15\%, and
 Christians about 10\%. There are also much smaller sects (e.g., Ismailis, Druze),
@@
 
-Massive online social cohesion can have real-world social manifestations. Social
-media platforms provide one way to enable this kind of online social cohesion by
-offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements an
-opportunity to complement or even replace real-world social mobilization. For
-example, during the 2012 Italian protests for global economic change, the riots
-in Rome were mirrored by Twitter activity both on the day of the protests and in
-the days following them (Vicari 2013). Tweeting was determined to be more
-effective locally in discussing real-world, real-time events than traditional
-mainstream media platforms. As more and more individuals rely on social media to
-obtain local news and information, it becomes increasingly important to
-understand just how these micro-blogs reflect real-world action.
-
-During the Arab Spring, social media provided real-time information about the
-events transpiring in countries across the Middle East and North Africa. Our
-understanding about the role of social media in social movements is still
-evolving. Some argue that these mass movements would not have been possible
-without efficient large-scale coordination, both physically on the ground and
-virtually on social media platforms.
+Massive online social cohesion can manifest in real-world social behavior.
+Social media platforms enable online social cohesion by offering distributed
+information-gathering and real-time information dissemination. Given its
+accessibility and proficiency as an information exchange tool, Twitter has
+provided social and political activists an opportunity to complement or even
+replace real-world social mobilization. During the 2012 Italian protests for
+global economic change, tweeting was determined to be more effective locally in
+discussing real-world, real-time events than traditional mainstream media
+platforms (Vicari 2013). As people increasingly rely on social media for
+local news and information, we must understand exactly how these micro-blogs
+connect to and reflect real-world action.
 
 Along with Facebook, Twitter has been credited as essential to the Arab
-Spring---both for protesters (as a means to coordinate with one another and to
-communicate with the world) and for the government response (to monitor and
-track protestors to crack down on dissent) (Comninos 2011). The events of
-Arab Spring have been thoroughly discussed within the political science
-literature (e.g., Lutterbeck 2013; Koehler 2017), but to our knowledge, the direct \emph{coupling} between
-Syrian Twitter cohesion and international action coordination has not been
-investigated. In fact, some have been skeptical about the effect of social media
-on collective action at all (Seay 2014).
-
-This skepticism can be summarized in a quote by Lisa Anderson:
-
-\begin{quote}
-The important story about the 2011
+Spring---both for protesters and for the government's response to them
+(Comninos 2011). The Arab Spring has been deeply examined within the
+political science literature (e.g., Lutterbeck 2013; Koehler 2017), but to our knowledge, the direct \emph{coupling} between
+Syrian Twitter cohesion and international action has not been investigated. In
+fact, some have been skeptical about the effect of social media on collective
+action at all (Seay 2014).
+
+This skepticism is summarized in a quote by Lisa Anderson (2011):
+
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent The important story about the 2011
 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts. (Anderson 2011)
-\end{quote}
+local contexts.
+
+\setlength{\leftskip}{0pt}
+\end{singlespace}
 
 \noindent Others have similarly expressed hesitation about the role of online
-organizing. Some have argued that real-life strong ties outweigh online weak ties and
-that the power of the strong ties through in-person contact is critical
-to recruiting people for higher-risk activities
-(Gladwell 2010; McAdam 1986).
-
-Interestingly, these views may
-actually help to make the case for bridging the gap between social media and
-social mobilization. Such views suggest the strength of social ties in an online
-environment is inextricably linked to the \emph{context} and \emph{ambitions} of the actors.
-Moreover, research suggests that weak ties still retain considerable political
-power: While strong ties tend to bind smaller groups, weak ties
-tend to bind groups across distances (Granovetter 1973).
+organizing. Some have argued that real-life strong ties outweigh online weak
+ties and that the power of the strong ties through in-person contact is critical
+to recruiting people for higher-risk activities (Gladwell 2010; McAdam 1986).
+
+Interestingly, these views may help make the case for bridging social media and
+social mobilization. Such views suggest the strength of online social ties is
+inextricably linked to the \emph{context} and \emph{ambitions} of the actors. Moreover,
+research suggests that weak ties still retain considerable political power:
+While strong ties tend to bind smaller groups, weak ties tend to bind groups
+across distances (Granovetter 1973).
 
@@
 how a demonstration will take place, how many people participate, and how those
-in power (e.g., state, military, security apparatus) respond. Similarly, these
-media platforms alert us to more global shifts within a conflict, such as when
-fighting moves to a new city or region, the number of casualties and wounded,
-and the types of weaponry used by parties to the conflict (Zeitzoff 2017).
-Social media is not entirely event-driven, however. In monitoring social media
-channels, government forces may respond to the perception that citizens are
-gaining strength and sympathy. Governments have been shown to be quite tolerant
-of dissent so long as it does not metamorphose into collective action
+in power (e.g., state, military) respond. Similarly, these media platforms alert
+us to more global shifts within a conflict, such as when fighting moves to a new
+city or region, the number of casualties and wounded, and the types of weaponry
+used by parties (Zeitzoff 2017). In monitoring social media channels,
+government forces may respond to the perception that citizens are gaining
+strength and sympathy. Governments have been shown to be quite tolerant of
+dissent so long as it does not metamorphose into collective action
 (King, Pan, and Roberts 2013).
@@
 (Comninos 2011), such as where new groups are forming, where existing
-groups are strengthening, where gatherings are held, and who the idea
-entrepreneurs are.
+groups are strengthening, where gatherings are held, and who the leaders are.
 
@@
 
-\begin{quote}
-I know that I have been away from the media for a long time, and I have missed
-having direct contact with the citizens, but I have always been following up
-with the daily occurrences and gathering the information so that my speech can
-be built on what is said by the street.
-\end{quote}
-
-\noindent With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes (2015) notes that regimes can attempt to thwart the growth
-of social protest online and in the streets by shutting down the Internet.
-During these times, however, she finds that military repression increases.
-However, government information about the citizens decreases; as such, many
-regimes have elected to maintain Internet connectivity as a means of monitoring
-and surveilling their citizens.
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent I know that I have been away from the media for a long time, and I
+have missed having direct contact with the citizens, but I have always been
+following up with the daily occurrences and gathering the information so that my
+speech can be built on what is said by the street.
+
+\setlength{\leftskip}{0pt}
+\end{singlespace}
+
+\noindent With few exceptions, Assad chose to keep social media platforms up and
+running. Gohdes (2015) notes that regimes can attempt to thwart
+the growth of social protest online and in the streets by shutting down the
+Internet. During these times, military repression increases, but government
+information about the citizens decreases. As a result, regimes may elect to
+maintain Internet connectivity to monitor and surveil their citizens.
 
@@
 People join social and political resistance movements because they feel a sense
-of connection to the cause. Given that people are generally risk-averse, overcoming inertia
-requires a strong connection to the group identity or a strong aversion to an
-individual, event, or political injustice (Goldstone 1980, 2011). Political resistance offers participants the
+of connection to the cause. Given that people are generally risk-averse,
+overcoming inertia requires a strong connection to the group identity or a
+strong aversion to an individual, event, or political injustice
+(Goldstone 1980, 2011). Political resistance offers participants the
 opportunity to \enquote{lose themselves} and relinquish their individual identity in
-favor of identification with a larger group, contributing to a cohesive
-group ready and mobilized for action (Hoffer 2011).
-
-Previous research on social movements supports the idea that participants are
-more likely to join movements when they know and have a personal connection to
-someone else already involved (McAdam 1986). The type of collective
-contentious behavior that manifests in society is a function of the available
-political opportunity structures. The political opportunity structure are
-\enquote{comprised of \emph{(sic)} specific configurations of resources, institutional
-arrangements and historical precedents for social mobilization, which facilitate
-the development of protest movements in some instances and constrain them in
-others} (Kitschelt 1986). What emerges as strategies and tactics in
-contentious politics are, in essence, a function of what the system makes
-possible. This includes the number of people and their disposition (i.e.
-nonviolent or violent), as well as their internal structure. The more cohesive a
-group is, the greater threat they pose to the establishment.
-
-Cohesion is also a familiar concept in the study of civil conflicts, as it
-pertains to group affiliation and the ability to overcome collective action
-problems. Individuals must act in concert---that is, cohesively---to
-accomplish the task of challenging the authority of the state (Olson 1965; Eisinger 1973; Tilly 2004; Francisco 1995).
-Recent work has considered rebel recruitment for participation in
-civil conflicts as a function of internal cohesion (Gates 2002):
-Rebel movement success is influenced by the degree of group cohesion, which
-itself is a function of geographic distance, ideology, and ethnicity.
-Within Syria, multiple rebel groups exist, sourcing fighters locally
-from the disaffected Syrian population and internationally through
-fighters from transnational terrorist organizations. There is considerable
-intergroup competition for participation in the rebel movement and
-punishment for defectors for nonparticipation (Gates 2002).
-Foreign fighters would appear to be amply motivated to fight, given their
-decision to relocate from a home country that may be located in the region
-or much farther away.
+favor of identification with a larger group, contributing to a cohesive group
+ready and mobilized for action (Hoffer 2011).
+
+The type of collective contentious behavior that manifests in society is a
+function of the available political opportunity structures. The political
+opportunity structure is \enquote{comprised of \emph{(sic)} specific configurations of
+resources, institutional arrangements and historical precedents for social
+mobilization, which facilitate the development of protest movements in some
+instances and constrain them in others} (Kitschelt 1986). What emerges
+as strategies and tactics in contentious politics are a function of
+what the system makes possible. This includes the number of people and their
+disposition (i.e.~nonviolent or violent), as well as their internal structure.
+The more cohesive a group is, the greater threat they pose to the establishment.
+
+Cohesion is a familiar concept in the study of civil conflicts, as it pertains
+to group affiliation and the ability to overcome collective action problems.
+Individuals must act in concert---that is, cohesively---to accomplish the task
+of challenging state authority (Olson 1965; Eisinger 1973; Tilly 2004; Francisco 1995).
+Viewing rebel recruitment during civil conflicts as a function of internal
+cohesion, rebel movement success is influenced by the degree of group cohesion,
+which itself is a function of geographic distance, ideology, and ethnicity
+(Gates 2002). Within Syria, multiple rebel groups exist, sourcing
+fighters locally (from the disaffected Syrian population) and internationally
+(from transnational terrorist organizations). Groups compete intensely with one
+another for recruitment in the rebel movement and often punish defectors for
+nonparticipation (Gates 2002).
 
@@
 
-The civil war literature has further explored the role of social cohesion in
-detail. Social homogeneity increases the likelihood of social conflict,
-especially when the society is polarized (Collier and Hoeffler 2004); this is partly
-due to nationalist groups' strong identification with a collective identity
-(Cederman and Girardin 2007) and their social solidarity (Sambanis and Schulhofer-Wohl 2009). These
-same processes can be similarly important for rebels (Anyanwu 2002).
-Referencing Gurr's (2000) work on minorities at
-risk, Regan and Norton (2005) note that
-
-\begin{quote}
-a religious or linguistic minority
+The civil war literature has also explored the role of social cohesion. Social
+homogeneity increases the likelihood of social conflict, especially when the
+society is polarized (Collier and Hoeffler 2004); this is partly due to nationalist
+groups' strong identification with a collective identity (Cederman and Girardin 2007)
+and their social solidarity (Sambanis and Schulhofer-Wohl 2009). These same processes can be
+similarly important for rebels (Anyanwu 2002). Referencing Gurr's
+(2000) work on minorities at risk, Regan and Norton
+(2005) note that
+
+\begin{singlespace}
+\setlength{\leftskip}{1cm}
+
+\noindent a religious or linguistic minority
 might suffer disproportionately in a given society, and this form of
@@
 maldistributions, it is individual penury that allows for this collective
-mobilization. (Regan and Norton 2005)
-\end{quote}
+mobilization.
+
+\setlength{\leftskip}{0pt}
+\end{singlespace}
 
@@
 
-The words that comprise social media posts are the first level of cohesion that
-we will consider. In Figure \ref{fig:cohesion-in-tweets}, we see four
-sequential tweets, each containing four words. Each sequential tweet contains
-some content included in the previous tweets. The linguistic construct of
-content word overlap measures the relationship across units of meaning---here,
-tweets---where identical and semantically similar words are repeated
-(Graesser et al. 2004). These repeated lexical items constitute a theme; on Twitter,
-this might be a particular hashtag, a name, a location, or other nominal
-category. This localized cohesion is referential; words are repeated and
-co-referred across tweets, creating a sense of continuity and cohesiveness of
-meaning and message.
+The first level of cohesion that we will consider are the words within social
+media posts. In Figure \ref{fig:cohesion-in-tweets}, we see four sequential
+tweets of four words each. Each sequential tweet contains some content
+included in the previous tweets. The linguistic construct of content word
+overlap measures the relationship across units of meaning---here, tweets---where
+identical and semantically similar words are repeated (Graesser et al. 2004). These
+repeated lexical items constitute a theme; on Twitter, this might be a
+particular hashtag, a name, a location, or another nominal category. This
+localized cohesion is referential; words are repeated and co-referred across
+tweets, creating a sense of continuity and cohesiveness.
 
@@
 \includegraphics[width=1\linewidth]{./figs/cohesion-in-tweets} \caption{A visual representation of cohesion in tweets.
-Content word overlap indicates a shared relationship among tweets.
-The shared words--either identical or semantically similar--constitute a theme around which cohesion is occuring.}\label{fig:cohesion-in-tweets}
+The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occuring.}\label{fig:cohesion-in-tweets}
 \end{figure}
@@
 The use of similar language can provide insight into \emph{interlocutor cohesion}, or
-the degree to which people are talking about similar things. This can---as noted
-earlier---include people who are talking about similar things from radically
-perspectives, as well as those who are talking about something from the same
-perspective. Previous research from political science has investigated these
-ideas (Windsor 2020): The \enquote{Occupy Wall Street} movement has been held up as an
-example of a movement with low interlocutor and linguistic cohesion because of
-its wide range of signs and slogans, while the \enquote{I am a man} protest (captured by
-Ernest Withers during the 1968 sanitation workers' strike in Memphis, TN) or the
-\enquote{Black Lives Matter} placards (following the uprising in Ferguson, MO) have high
-lexical and interlocutor cohesion (Edgar and Johnson 2018).
-
-Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
-contextualized by variation in real world events. Interlocutor cohesion may
-increase preceding an in-person social mobilization event, alerting a repressive
-government that collective mobilization is happening. Interlocutor cohesion may
-also respond to exogenous events such as spontaneous, unprovoked militarized
-conflict. If government forces target a new location using military weapons,
-this can precipitate online mobilization and discussion of the event.
+the degree to which people are talking about similar things. This can include
+people who are talking about similar things from radically perspectives, as well
+as those who are talking about something from the same perspective. Previous
+research from political science has investigated these ideas (Windsor 2020): The
+\enquote{Occupy Wall Street} movement has been held up as an example of a movement with
+low interlocutor and linguistic cohesion because of its wide range of signs and
+slogans, while the \enquote{I am a man} protest (during the 1968 sanitation workers'
+strike in Memphis, TN) or the \enquote{Black Lives Matter} placards (following the
+uprising in Ferguson, MO) have high lexical and interlocutor cohesion
+(Edgar and Johnson 2018).
+
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows, contextualized by
+changing real world events. Interlocutor cohesion may increase preceding an
+in-person social mobilization event, alerting a repressive government that
+collective mobilization is happening. Interlocutor cohesion may also respond to
+exogenous events such as spontaneous, unprovoked militarized conflict.
 
 Given the importance of lexical and interlocutor cohesion for messaging in
-political movements, lexical cohesion may be an important bit of trace data for
+political movements, lexical cohesion may be important trace data for
 researchers interested in leveraging social media data to analyze social
@@
 to contribute to the group (Wiltermuth and Heath 2009), and shared identity
-is associated with a greater willingness to adopt the group's goals and
+leads to a greater willingness to adopt the group's goals and
 motivations (Walton et al. 2012).
 
-We should expect to see increased linguistic cohesion among people participating
-in online discussions about an idea, event, individual, or movement. Given that
-Syrian protesters are known to have coordinated their activity through Twitter
-by discussing their own events (e.g., planned protests, active demonstrations)
-and their reactions to events happening around them (e.g., government reactions,
-international action or inaction), the cohesion in social media should be
-expected to correlate with the social cohesion of the group (Zeitzoff 2011).
-
-This social cohesion can have real and wide-ranging impacts on a political
-movement and the people in it. A socially cohesive group is inherently more
-threatening to the existing regime because it reflects collective opposition
-momentum and the professionalization of potential alternate leadership. Groups
-with high social cohesion are more difficult to divide and conquer, and more
-cohesive messages may also garner increased international support. Global
-insurgency movements exhibit similar patterns in their social structure
-(Bohorquez et al. 2009). Each violent group has a stable state. Exogenous events
-can create perturbations that push the group to become either more cohesive or
-more fragmented. Rather than frenetic, patchwork messages via Twitter, emergent
-or intentional cohesive online messaging---using similar language, paralleling
-in-person messaging (Windsor 2020)---are a sign of increased organizational
-structure, inciting a government response.
+We expect to see increased linguistic cohesion among people participating in
+online discussions about an idea, event, individual, or movement. Given that
+Syrian protesters coordinated their activity through Twitter by discussing their
+own events (e.g., planned protests, active demonstrations) and their reactions
+to events happening around them (e.g., government reactions, international
+action or inaction), the cohesion in social media should correlate with the
+social cohesion of the group (Zeitzoff 2011).
+
+Political and social cohesion in the world can be modeled using event data which
+encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
+Event Observations) encode a set of activities with numerical values, rescaled
+to reflect a conflict-cooperation scale (Schrodt and Hall 2006; Goldstein 1992). These event codes include a range of behaviors, from
+making public statements and appeals, to demanding, threatening, protesting, and
+using unconventional mass violence.
+
+Social cohesion can have real and wide-ranging impacts on a political movement
+and the people in it. A socially cohesive group is inherently more threatening
+to the existing regime because it reflects momentum in collective opposition and
+the professionalization of alternate leadership. Global insurgency movements
+exhibit similar patterns in their social structure (Bohorquez et al. 2009).
+Rather than patchwork messages via Twitter, emergent or intentional cohesive
+online messaging---using similar language, paralleling in-person messaging
+(Windsor 2020)---demonstrates increased organizational structure, inciting a
+government response.
 
 Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
-and political cohesion. Shared language in an online environment may lead to the
-development or expression of a shared identity (Wiltermuth and Heath 2009). This,
-in turn, may drive individuals' propensity to engage in similar coordinated
-behavior on behalf of the group (Wiltermuth and Heath 2009; Walton et al. 2012).
-Taken together, these two processes may increase movement participants' weak and
-strong ties (Granovetter 1973; Gladwell 2010; McAdam 1986), strengthening the movement overall by expanding and
-deepening heterogenous ties. Therefore, in the context of social conflict, the
-linguistic cohesion of the online conversation should correspond to the degree
-of social cohesion on the ground.
+and political cohesion. Shared online language may lead to the development or
+expression of shared identity (Wiltermuth and Heath 2009). This, in turn, may
+drive individuals' propensity to engage in coordinated behavior for the group
+(Wiltermuth and Heath 2009; Walton et al. 2012). Taken together, these processes may
+increase movement participants' weak and strong ties (Granovetter 1973; Gladwell 2010; McAdam 1986), building the movement by expanding and deepening
+heterogenous ties. Therefore, during social conflict, the linguistic cohesion
+of the online conversation should correspond to the degree of social cohesion on
+the ground.
 
@@
 groundbreaking work demonstrated that participants on the fringe of a social
-movement contribute substantially to the overall level of protest. In addition
-to providing new methods to this growing field of study, we build on this
-previous work by demonstrating how sociolinguistic cohesion evolves in
-tandem with negative and positive exogenous events.
-
-Political and social cohesion in the world can be modeled using event data which
-encodes who does what to whom on a given day. This could include events such as
-the government imposing a blockade or fighting with artillery or tanks on
-a civilian group. CAMEO (Conflict and Mediation Event Observations) encode
-a set of activities with numerical values, rescaled to reflect a
-conflict-cooperation scale (Schrodt and Hall 2006; Goldstein 1992). These event
-codes include a range of behaviors, from making public statements and appeals,
-to demanding, threatening, protesting, and using unconventional mass violence.
+movement contribute substantially to the overall level of protest. Here, in
+addition to providing new methods to this area, we build on this work by
+demonstrating how sociolinguistic cohesion evolves in tandem with negative and
+positive exogenous events.
 
@@
 a theoretical framework called \emph{sociolinguistic cohesion}, as shown in Figure
-\ref{fig:theoretical-framework}. Several interconnected mechanisms are in
-motion here. Previous values of linguistic cohesion should influence future
-values of linguistic cohesion and future actions in the real world space.
+\ref{fig:theoretical-framework}. Previous values of linguistic cohesion should influence future values of linguistic cohesion and future actions in the real world space.
 Previous events influence future events and future linguistic cohesion in
@@
 states of the political sphere. Other scholars have noted the diffusion of
-messages whereby they reach a critical mass, whereby \enquote{behaviors, beliefs, and
-preferences} spread within a population (Barash, Cameron, and Macy 2012). Cohesion
+messages that reach critical mass, allowing for \enquote{behaviors, beliefs, and
+preferences} to spread within a population (Barash, Cameron, and Macy 2012). Cohesion
 changes over time in response to external events and the internal dynamics of
-the social movement. This can occur even if the social interaction occurs entirely
+the social movement, even if the social interaction occurs entirely
 online (Centola and Macy 2007).
+
+Lexical cohesion, then, is a useful indicator of social cohesion in political
+crisis. Lexical cohesion happens at the word level. Interlocutor cohesion
+happens between speakers. Political cohesion happens at the social level during
+moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion comprises lexical, interlocutor, and sociopolitical
+events, in which the words and their context reveal the disposition of socially
+connected linguistic communities. It accounts for the cohesion between multiple
+speakers in an environment as their language becomes more similar.
+Sociolinguistic cohesion also addresses how groups involved in political
+rebellion converge to mount sustained resistance to state authority.
 
@@
 actions and online social interactions would be enmeshed, driving and being
-driven by one another. Rather than expecting that only real-world social
-cohesion would be driven by real-world action, we would expect interaction
-between real-world and online dynamics: In this case, exposure to real-world
-violence could result in social cohesion in the virtual world. Increased social
-cohesion is thus potentially an indicator and a result of increased social
-organization and mobilization on the ground. However, this occurs within a
-context that is affected by local and international events; both exogenous
-events (like intervention by another country or international organization like
-the United Nations) and endogenous events (like the recruitment of new members
-to the rebel or resistance movement) can affect cohesion.
-
-From a dynamical systems perspective, online social cohesion and in-person
-action can be considered two complementary components of a single system,
-mutually constrained and constantly interacting and influencing one another
-(Mahner and Bunge 1997). Investigation of the coupling of real-world
-mobilization and social cohesion could provide new insight into the power of
-social media during mobilization and the ways in which individuals utilize it to
-bring about, or respond to, social change. Increasingly, social media platforms
-are being utilized during social mobilization (McAdam, Tarrow, and Tilly 2003; Koopmans 2004), but the relationship between virtual and real-world
+driven by one another. From a dynamical systems perspective, online social
+cohesion and in-person action can be considered two complementary components of
+a single system, mutually constrained and constantly interacting and influencing
+one another (Mahner and Bunge 1997). Investigation of the coupling of
+real-world mobilization and social cohesion could provide new insight into the
+power of social media during mobilization and the ways in which individuals
+utilize it to bring about, or respond to, social change. Increasingly, social
+media platforms are being utilized during social mobilization
+(McAdam, Tarrow, and Tilly 2003; Koopmans 2004), but the relationship between virtual and real-world
 mobilization is still largely unknown. The present work aims to understand how
@@
 perspective.
-
-Lexical cohesion, then, is be a useful indicator of social cohesion in
-political crisis. Lexical cohesion happens at the word level. Interlocutor
-cohesion happens between speakers. Political cohesion happens at the social
-level during moments of political crisis, like civil wars and social movements.
-Sociolinguistic cohesion is comprised of lexical, interlocutor, and
-socio-political events, where the words and their context reveal the disposition
-of socially connected linguistic communities. Sociolinguistic cohesion combines
-the elements of lexical cohesion in that it captures the degree of similarity
-between what is said, and how it is said. It accounts for the cohesion between
-multiple speakers in an environment whose language evolves to become more
-aligned and similar. Sociolinguistic cohesion also addresses how groups involved
-in political rebellion must have internal cohesion to overcome the collective
-action problem to mount sustained resistance to state authority.
 
@@
 social media platforms) are constantly interacting, leading to more global
-behaviors that are larger than the sum of the parts (Turvey 2018).
-Linear analyses flatten time series data and ignore the variability that is
-fundamental to these systems and their evolution over time. However, when
+behaviors that are larger than the sum of the parts (Turvey 2018). When
 analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
@@
 
-Although a number of other nonlinear methods exist, the primary nonlinear method
-used in the current work is cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, and Webber Jr 1998) and its offshoot, windowed cross-recurrence quantification
+Although a number of other nonlinear methods exist, the primary nonlinear methods
+used in the current work are cross-recurrence quantification analysis (CRQA; Zbilut, Giuliani, and Webber Jr 1998) and its offshoot, windowed cross-recurrence quantification
 analysis (WCRQA; Webber Jr and Zbilut 2005). CRQA has successfully been used to gain
@@
 the counts of all, positive, and negative real-world events derived from
-gold-standard international event data (i.e., the Integrated Crisis Early
-Warning System; Boschee et al. 2015).
+international event data (i.e., the Integrated Crisis Early Warning System; Boschee et al. 2015).
 
@@
 
-\begin{figure}
-\includegraphics[width=6.5in]{./results/primary/mode_ts_plot} \caption{Mode ICEWS event per day.}\label{fig:plot-mode-event}
-\end{figure}
-
 For social cohesion and count of all events, there was a consistent period of
@@
 above-chance RR until the 50th window, with some exceptions during window
-periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
+periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
 60th windows (Figure \ref{fig:plot-wcrqa-targ-all}).
@@
 
+\begin{figure}
+\includegraphics[width=6.5in]{./results/primary/mode_ts_plot} \caption{Mode ICEWS event per day.}\label{fig:plot-mode-event}
+\end{figure}
+
 For social cohesion and count of all events, there was a consistent period of
 above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
-also showed above- or nearly above-chance values in windows 7 through 17 and
+also showed above- or nearly above-chance values in windows 7--17 and
 intermittent peaks between the 34th and 61st windows (Figure
@@
 and the 32nd--45th windows. DET stayed largely within chance, with the exception
-of windows 13 through 19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
+of windows 13--19 (Figure \ref{fig:plot-wcrqa-source-targ-all}).
 
@@
 online communication on Twitter in Syria during Arab Spring. CRQA methodology
-allows us to model the relationship between sociolinguistic cohesion and
+allows us to disentangle the relationship between sociolinguistic cohesion and
 exogenous political events. This work stands alongside the model of
-Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
+Palestinian-Israeli social media and events developed by Zeitzoff (2017), and
 the role of peripheral participants in the Syrian Arab Spring movement by
@@
 framework of sociolinguistic cohesion which we operationalize using a weighted
-measure of lexical relationships. We examined how social mobilization both
-virtually and physically evolve over time in tandem. Using nonlinear dynamical
-time series analyses, we investigated the theory that virtual mobilization is
-increasingly reflective of real-world events during times of strife.
+measure of lexical relationships. Using nonlinear dynamical time series
+analyses, we investigated the theory that virtual mobilization is increasingly
+reflective of real-world events during times of strife.
 
@@
 Nonlinear methods have been transformative for a variety of research areas
-(including psychology, Coco and Dale 2014). One of the goals in the present work was
+(including psychology, Coco and Dale 2014). One of the goals of the present work was
 to introduce variants of one kind of nonlinear method---specifically, recurrence
@@
 scientists to a family of powerful nonlinear dynamics analyses, our results have
-serious implications for monitoring global movements in consistent across other
-social uprisings. While state-run media in regions of authoritarian rule are
-often biased and serve as propaganda for the leader and central government, the
-self-organized nature of Twitter provides a new avenue to gain insight into
-truths about uprisings and social mobilization. By conceptualizing Twitter and
-real-world events as two elements of an inextricably linked dynamical system,
-the levels of social cohesion within social media platforms could be monitored
-for fluctuations indicating shifts in power and peace. Social media mobilization
-may thus help alert the world to citizens' actions and reactions that are
-suppressed by government regimes, providing insight into events that may not
-otherwise be broadcast and allowing for faster intervention.
+serious implications for monitoring global movements. While state-run media in
+regions of authoritarian rule are often biased and serve as propaganda for the
+leader and central government, the self-organized nature of Twitter provides a
+new avenue to gain insight into truths about uprisings and social mobilization.
+By conceptualizing Twitter and real-world events as two elements of an
+inextricably linked dynamical system, the levels of social cohesion within
+social media platforms could be monitored for fluctuations indicating shifts in
+power and peace. Social media mobilization may thus help alert the world to
+citizens' actions and reactions that are suppressed by government regimes,
+providing insight into events that may not otherwise be broadcast and allowing
+for faster intervention.
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
+\hypertarget{bibliography}{%
+\section{Bibliography}\label{bibliography}}
 

### 2020-06-05 manuscript-chicago.Rmd
Final version (pre-redaction)

@@
 
+Political and social cohesion in the world can be modeled using event data which
+encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
+Event Observations) encode a set of activities with numerical values, rescaled
+to reflect a conflict-cooperation scale [@schrodt2006twenty;
+@goldstein1992conflict]. These event codes include a range of behaviors, from
+making public statements and appeals, to demanding, threatening, protesting, and
+using unconventional mass violence.
+
 Social cohesion can have real and wide-ranging impacts on a political movement
@@
 Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
-and political cohesion. Shared language in an online environment may lead to the
-development or expression of a shared identity [@wiltermuth2009synchrony]. This,
-in turn, may drive individuals' propensity to engage in similar coordinated
-behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
-Taken together, these two processes may increase movement participants' weak and
-strong ties [@granovetter1977strength; @gladwell2010revolution;
-@mcadam1986recruitment], strengthening the movement overall by expanding and
-deepening heterogenous ties. Therefore, in the context of social conflict, the
-linguistic cohesion of the online conversation should correspond to the degree
-of social cohesion on the ground.
+and political cohesion. Shared online language may lead to the development or
+expression of shared identity [@wiltermuth2009synchrony]. This, in turn, may
+drive individuals' propensity to engage in coordinated behavior for the group
+[@wiltermuth2009synchrony; @walton2012mere]. Taken together, these processes may
+increase movement participants' weak and strong ties [@granovetter1977strength;
+@gladwell2010revolution;
+@mcadam1986recruitment], building the movement by expanding and deepening
+heterogenous ties. Therefore, during social conflict, the linguistic cohesion
+of the online conversation should correspond to the degree of social cohesion on
+the ground.
 
@@
 groundbreaking work demonstrated that participants on the fringe of a social
-movement contribute substantially to the overall level of protest. In addition
-to providing new methods to this growing field of study, we build on this
-previous work by demonstrating how sociolinguistic cohesion evolves in
-tandem with negative and positive exogenous events.
-
-Political and social cohesion in the world can be modeled using event data which
-encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
-Event Observations) encode a set of activities with numerical values, rescaled
-to reflect a conflict-cooperation scale [@schrodt2006twenty;
-@goldstein1992conflict]. These event codes include a range of behaviors, from
-making public statements and appeals, to demanding, threatening, protesting, and
-using unconventional mass violence.
+movement contribute substantially to the overall level of protest. Here, in
+addition to providing new methods to this area, we build on this work by
+demonstrating how sociolinguistic cohesion evolves in tandem with negative and
+positive exogenous events.
 
@@
 states of the political sphere. Other scholars have noted the diffusion of
-messages whereby they reach a critical mass, allowing for “behaviors, beliefs, and
+messages that reach critical mass, allowing for “behaviors, beliefs, and
 preferences” to spread within a population [@barash2012critical]. Cohesion
@@
 
-Lexical cohesion, then, is a useful indicator of social cohesion in
-political crisis. Lexical cohesion happens at the word level. Interlocutor
-cohesion happens between speakers. Political cohesion happens at the social
-level during moments of political crisis, like civil wars and social movements.
-Sociolinguistic cohesion is comprised of lexical, interlocutor, and
-socio-political events, where the words and their context reveal the disposition
-of socially connected linguistic communities. It accounts for the cohesion between
-multiple speakers in an environment whose language evolves to become more
-aligned and similar. Sociolinguistic cohesion also addresses how groups involved
-in political rebellion must have internal cohesion to overcome the collective
-action problem to mount sustained resistance to state authority.
+Lexical cohesion, then, is a useful indicator of social cohesion in political
+crisis. Lexical cohesion happens at the word level. Interlocutor cohesion
+happens between speakers. Political cohesion happens at the social level during
+moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion comprises lexical, interlocutor, and sociopolitical
+events, in which the words and their context reveal the disposition of socially
+connected linguistic communities. It accounts for the cohesion between multiple
+speakers in an environment as their language becomes more similar.
+Sociolinguistic cohesion also addresses how groups involved in political
+rebellion converge to mount sustained resistance to state authority.
 
@@
 it is more likely a content word and is thus given more weight in calculating
-social cohesion. This method is similar to inverse document frequency (IDF). For
-more information on IDF, see @jones1972statistical and
-@robertson2004understanding.
+social cohesion. This method is similar to *term frequency-inverse document
+frequency* [tf-idf; see also @jones1972statistical;
+@robertson2004understanding].
 

### 2020-06-05 manuscript-chicago.Rmd
Redacting

@@
 author:
-  - name          : "Megan Chiovaro"
-    affiliation   : "1, 2"
-    corresponding : yes    # Define only one corresponding author
-    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
-    email         : "megan.chiovaro@uconn.edu"
-  - name          : "Alexandra Paxton"
-    affiliation   : "1,2,*"
-  - name          : "Leah C. Windsor"
-    affiliation   : "3,*"
-
-affiliation:
-  - id            : "1"
-    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
-  - id            : "2"
-    institution   : "Department of Psychological Sciences, University of Connecticut"
-  - id            : "3"
-    institution   : "University of Memphis"
-  - id            : "*"
-    institution   : "Equal author contributions"
+    - name          : "[author names redacted for blind review]"
+#   - name          : "Megan Chiovaro"
+#     affiliation   : "1, 2"
+#     corresponding : yes    # Define only one corresponding author
+#     address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
+#     email         : "megan.chiovaro@uconn.edu"
+#   - name          : "Alexandra Paxton"
+#     affiliation   : "1,2,*"
+#   - name          : "Leah C. Windsor"
+#     affiliation   : "3,*"
+# 
+# affiliation:
+#   - id            : "1"
+#     institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
+#   - id            : "2"
+#     institution   : "Department of Psychological Sciences, University of Connecticut"
+#   - id            : "3"
+#     institution   : "University of Memphis"
+#   - id            : "*"
+#     institution   : "Equal author contributions"
 
@@
 keywords          : "social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring"
-wordcount         : "X"
+wordcount         : "10981"
 
@@
 a theoretical framework called *sociolinguistic cohesion*, as shown in Figure
-\@ref(fig:theoretical-framework). Previous values of linguistic cohesion should influence future values of linguistic cohesion and future actions in the real world space.
-Previous events influence future events and future linguistic cohesion in
-social media.
+\@ref(fig:theoretical-framework). Previous values of linguistic cohesion should
+influence future values of linguistic cohesion and future actions in the real
+world space. Previous events influence future events and future linguistic
+cohesion in social media.
 
@@
 these methods.
+
+This work is a reproducible manuscript. All code and analyses can be found at:
+[redacted for blind review].
 
@@
 
-This work was completed in part as coursework done by lead author M. Chiovaro in
-the “Applications of Nonlinear Time Series Analysis” graduate course at the
-University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
-Harrison).
+[redacted for blind review]
+
+<!-- This work was completed in part as coursework done by lead author M. Chiovaro in -->
+<!-- the “Applications of Nonlinear Time Series Analysis” graduate course at the -->
+<!-- University of Connecticut (co-taught by coauthor A. Paxton and Steven J. -->
+<!-- Harrison). -->
 

### 2020-06-05 manuscript-chicago-edited.tex
Add .tex version for submission

--- 2020-06-05 manuscript-chicago.tex
@@
 \shorttitle{Arab Spring}
-\author{Megan Chiovaro\textsuperscript{1, 2}, Alexandra Paxton\textsuperscript{1,2,*}, \& Leah C. Windsor\textsuperscript{3,*}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Center for the Ecological Study of Perception and Action, University of Connecticut\\\textsuperscript{2} Department of Psychological Sciences, University of Connecticut\\\textsuperscript{3} University of Memphis\\\textsuperscript{*} Equal author contributions}
-\authornote{
-
-Correspondence concerning this article should be addressed to Megan Chiovaro, 406 Babbidge Road, Unit 1020, Storrs, CT 06269. E-mail: megan.chiovaro@uconn.edu}
-\keywords{social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring\newline\indent Word count: X}
+\author{[author names redacted for blind review]\\ Word count : 10981}
+\affiliation{\phantom{a}}
+\keywords{social cohesion, recurrence quantification analysis, complex systems, Twitter, Arab Spring}
 \DeclareDelayedFloatFlavor{ThreePartTable}{table}
@@
 \usepackage{setspace}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[shorthands=off,main=english]{babel}
+\else
+  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
   \usepackage{polyglossia}
   \setmainlanguage[]{english}
-\else
-  \usepackage[shorthands=off,main=english]{babel}
 \fi
@@
 
-\abstract{
-In recent years, political activists have taken to social media platforms to
+\abstract{In recent years, political activists have taken to social media platforms to
 rapidly reach broad audiences. Despite the prevalence of micro-blogging in
@@
 a theoretical framework called \emph{sociolinguistic cohesion}, as shown in Figure
-\ref{fig:theoretical-framework}. Previous values of linguistic cohesion should influence future values of linguistic cohesion and future actions in the real world space.
-Previous events influence future events and future linguistic cohesion in
-social media.
+\ref{fig:theoretical-framework}. Previous values of linguistic cohesion should
+influence future values of linguistic cohesion and future actions in the real
+world space. Previous events influence future events and future linguistic
+cohesion in social media.
 
@@
 
+This work is a reproducible manuscript. All code and analyses can be found at:
+{[}redacted for blind review{]}.
+
 \hypertarget{method}{%
@@
 it is more likely a content word and is thus given more weight in calculating
-social cohesion. This method is similar to inverse document frequency (IDF). For
-more information on IDF, see Jones (1972) and
-Robertson (2004).
+social cohesion. This method is similar to \emph{term frequency-inverse document
+frequency} (tf-idf; see also Jones 1972; Robertson 2004).
 
@@
 
-This work was completed in part as coursework done by lead author M. Chiovaro in
-the \enquote{Applications of Nonlinear Time Series Analysis} graduate course at the
-University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
-Harrison).
+\noindent{[}redacted for blind review{]}
 
@@
 \leavevmode\hypertarget{ref-webber2005recurrence}{}%
----------. 2005. ``Recurrence Quantification Analysis of Nonlinear Dynamical Systems.'' \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences} 94 (2005): 26--94.
+Webber Jr, Charles L and Zbilut, Joseph P.
+2005.
+``Recurrence Quantification Analysis of Nonlinear Dynamical Systems.'' \emph{Tutorials in Contemporary Nonlinear Methods for the Behavioral Sciences} 94 (2005): 26--94.
 
@@
 \leavevmode\hypertarget{ref-zeitzoff2017social}{}%
----------. 2017. ``How Social Media Is Changing Conflict.'' \emph{Journal of Conflict Resolution} 61 (9): 1970--91.
+Zeitzoff, Thomas. 2017. ``How Social Media Is Changing Conflict.'' \emph{Journal of Conflict Resolution} 61 (9): 1970--91.
 

### 2020-07-06 manuscript.Rmd
Specify Chicago citation/reference style
Revert back to APA format
Bring APA manuscript up to speed

@@
 
-Prior to the advent of social media, people coordinated their protest behavior
-using phone tree calling sheets and mimeographed flyers, through in-person
-meetings of social organizations and churches, and through word of mouth. They
-gathered together and hand-made protest signs that reflected their agendas. As
-McAdam found, people were more likely to join movements when they had a personal
-connection [@mcadam1986recruitment; @mcadam1993specifying]: Historically, strong
-ties have been strong predictors of involvement in high-risk protest activity.
-
-The cohesiveness and strength of social movements in the pre-Internet era could
-be operationalized by the number of people turning out to protest and through
-the political events that precipitated and resulted from social gatherings *en
-masse*. Cohesive social movements were reflected in their cohesive placards and
-posters. For example, the “I am a man” posters held by the men involved in the
-1968 sanitation workers' strike reflected their internal cohesion and unified,
-goal-oriented movement [@Windsor2020].
-
-However, the rise of the Internet and its decentralized online networks has
+Before social media, people coordinated protests using phone tree calling sheets
+and mimeographed flyers, through in-person meetings of social organizations and
+churches, and by word of mouth. They gathered together and hand-made protest
+signs that reflected their agendas. As McAdam found, people were more likely to
+join movements when they had a personal connection [@mcadam1986recruitment;
+@mcadam1993specifying]: Historically, strong ties have been strong predictors of
+involvement in high-risk protest activity.
+
+The cohesiveness and strength of social movements before the Internet were
+operationalized by the number of people present and through the political events
+that precipitated and resulted from social gatherings *en masse*. Cohesive
+social movements were reflected in their cohesive placards and posters. For
+example, the pervasive “I am a man” posters during the 1968 sanitation workers'
+strike reflected their internal cohesion and unified, goal-oriented movement
+[@Windsor2020].
+
+However, the rise of the Internet and its decentralized online networks have
 upended theories about recruitment to---and participation in---social movements.
 Strong interpersonal ties have yielded to weak impersonal ties that strongly
-predict involvement in social movements [@steinert2017spontaneous]. Research
-methodologies for measuring social movements have similarly evolved from
-ethnographic interviews to “big data” analyses of language on social media.
-
-Today, social media replicates and amplifies this phenomenon during moments of
-social unrest. Amid the cacophony of messages during political upheaval---such
+predict involvement in social movements [@steinert2017spontaneous]. Measurements
+of social movements have similarly evolved from ethnographic interviews to “big
+data” analyses of social media.
+
+Amid the cacophony of messages during political upheaval---such
 as the Arab Spring---consistent themes emerge through hashtags, retweets, and
-the repeated mentions of concepts such as regime, security, demonstration, and
+the repeated mentions of concepts such as regime, demonstration, and
 human rights. The cohesiveness of these themes (i.e., whether movement
@@
 mobilization---and social mobilization in person---continues to be relevant,
-even as our modes of communication change. The political events that
-transpired during and after the Arab Spring are still in the process of being
-understood. As Zeitzoff [-@zeitzoff2017social] recognizes, social media is
-changing conflict, but the mechanisms and relationships by which it does so are
-still largely unknown.
+even as our modes of communication change. Accordingly, the political events
+around the Arab Spring are still being understood. As Zeitzoff
+[-@zeitzoff2017social] recognizes, social media is changing conflict, but the
+mechanisms and relationships by which it does so are still largely unknown.
 
 ## Syria in Context
-The decades preceding the Arab Spring in Syria were marked by
-social repression and fear. In 1971, Hafez al-Assad overthrew the previous
-leader and remained in power for thirty years, presiding during
-regional contentiousness and cooperation until his death in 2000. His son,
-Bashar al-Assad continued the regime of authoritarian leadership as he assumed
-his office. The Assad lineage hails from a minority Islamic sect (the Alawites)
-in a multi-religious and multi-ethnic country comprising Christians, Sunni and
-Shia Muslims, Kurds, and Palestinian refugees.
-
-In December 2010, a Tunisian man named Mohamed Bouazizi was harassed and
-unjustifiably stripped of his vendor cart by municipal officials. His
-humiliation led him to set himself on fire in protest to the authoritarian rule,
-ultimately leading to his death several days later. His actions served as a
-catalyst for the Tunisian Revolution, and one week after his death, Zine El
-Abidine Ben Ali---the longstanding authoritarian president---fled the country.
-The events of Tunisia rapidly spread to surrounding countries also subject to
-unjust authoritarian rule, including Yemen, Egypt, Libya, and Syria.
+The decades preceding the Arab Spring in Syria were marked by repression and
+fear. In 1971, Hafez al-Assad overthrew the previous leader and remained in
+power for thirty years, presiding during regional contentiousness and
+cooperation until his death in 2000. His son, Bashar al-Assad, continued the
+regime of authoritarian leadership after assuming his office. The Assad lineage
+hails from a minority Islamic sect (the Alawites) in a multi-religious and
+multi-ethnic country comprising Christians, Sunni and Shia Muslims, Kurds, and
+Palestinian refugees.
+
+In December 2010, a Tunisian man named Mohamed Bouazizi was unjustifiably
+stripped of his vendor cart by municipal officials. His humiliation led him to
+set himself on fire in protest to the authoritarian rule, leading to his death
+several days later. His actions served as a catalyst for the Tunisian
+Revolution, and one week after his death, Zine El Abidine Ben Ali---the
+longstanding authoritarian president---fled the country. The events of Tunisia
+rapidly spread to surrounding countries also subject to unjust authoritarian
+rule, including Egypt, Libya, and Syria.
 
@@
 ## Social Media and Social Movements
-
-Massive online social cohesion can have real-world social manifestations. Social
-media platforms provide one way to enable this kind of online social cohesion by
-offering distributed information-gathering and real-time information
-dissemination. Given its accessibility and proficiency as an information
-exchange tool, Twitter has provided individuals involved in social movements an
-opportunity to complement or even replace real-world social mobilization. For
-example, during the 2012 Italian protests for global economic change, the riots
-in Rome were mirrored by Twitter activity both on the day of the protests and in
-the days following them [@vicari2013public]. Tweeting was determined to be more
-effective locally in discussing real-world, real-time events than traditional
-mainstream media platforms. As more and more individuals rely on social media to
-obtain local news and information, it becomes increasingly important to
-understand just how these micro-blogs reflect real-world action.
-
-During the Arab Spring, social media provided real-time information about the
-events transpiring in countries across the Middle East and North Africa. Our
-understanding about the role of social media in social movements is still
-evolving. Some argue that these mass movements would not have been possible
-without efficient large-scale coordination, both physically on the ground and
-virtually on social media platforms.
+Massive online social cohesion can manifest in real-world social behavior.
+Social media platforms enable online social cohesion by offering distributed
+information-gathering and real-time information dissemination. Given its
+accessibility and proficiency as an information exchange tool, Twitter has
+provided social and political activists an opportunity to complement or even
+replace real-world social mobilization. During the 2012 Italian protests for
+global economic change, tweeting was determined to be more effective locally in
+discussing real-world, real-time events than traditional mainstream media
+platforms [@vicari2013public]. As people increasingly rely on social media for
+local news and information, we must understand exactly how these micro-blogs
+connect to and reflect real-world action.
 
 Along with Facebook, Twitter has been credited as essential to the Arab
-Spring---both for protesters (as a means to coordinate with one another and to
-communicate with the world) and for the government response (to monitor and
-track protestors to crack down on dissent) [@comninos2011twitter]. The events of
-Arab Spring have been thoroughly discussed within the political science
-literature [e.g., @lutterbeck2013arab;
+Spring---both for protesters and for the government's response to them
+[@comninos2011twitter]. The Arab Spring has been deeply examined within the
+political science literature [e.g., @lutterbeck2013arab;
 @koehler2017political], but to our knowledge, the direct *coupling* between
-Syrian Twitter cohesion and international action coordination has not been
-investigated. In fact, some have been skeptical about the effect of social media
-on collective action at all [@seay2014slacktivism].
-
-This skepticism can be summarized in a quote by Lisa Anderson:
-
-> The important story about the 2011
+Syrian Twitter cohesion and international action has not been investigated. In
+fact, some have been skeptical about the effect of social media on collective
+action at all [@seay2014slacktivism].
+
+This skepticism is summarized in a quote by Lisa @anderson2011demystifying:
+
+\setlength{\leftskip}{1cm}
+
+\noindent The important story about the 2011
 Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts. [@anderson2011demystifying]
+local contexts.
+
+\setlength{\leftskip}{0pt}
 
 \noindent Others have similarly expressed hesitation about the role of online
-organizing. Some have argued that real-life strong ties outweigh online weak ties and
-that the power of the strong ties through in-person contact is critical
-to recruiting people for higher-risk activities
-[@gladwell2010revolution; @mcadam1986recruitment].
-
-Interestingly, these views may
-actually help to make the case for bridging the gap between social media and
-social mobilization. Such views suggest the strength of social ties in an online
-environment is inextricably linked to the *context* and *ambitions* of the actors.
-Moreover, research suggests that weak ties still retain considerable political
-power: While strong ties tend to bind smaller groups, weak ties
-tend to bind groups across distances [@granovetter1977strength].
+organizing. Some have argued that real-life strong ties outweigh online weak
+ties and that the power of the strong ties through in-person contact is critical
+to recruiting people for higher-risk activities [@gladwell2010revolution;
+@mcadam1986recruitment].
+
+Interestingly, these views may help make the case for bridging social media and
+social mobilization. Such views suggest the strength of online social ties is
+inextricably linked to the *context* and *ambitions* of the actors. Moreover,
+research suggests that weak ties still retain considerable political power:
+While strong ties tend to bind smaller groups, weak ties tend to bind groups
+across distances [@granovetter1977strength].
 
@@
 how a demonstration will take place, how many people participate, and how those
-in power (e.g., state, military, security apparatus) respond. Similarly, these
-media platforms alert us to more global shifts within a conflict, such as when
-fighting moves to a new city or region, the number of casualties and wounded,
-and the types of weaponry used by parties to the conflict [@zeitzoff2017social].
-Social media is not entirely event-driven, however. In monitoring social media
-channels, government forces may respond to the perception that citizens are
-gaining strength and sympathy. Governments have been shown to be quite tolerant
-of dissent so long as it does not metamorphose into collective action
+in power (e.g., state, military) respond. Similarly, these media platforms alert
+us to more global shifts within a conflict, such as when fighting moves to a new
+city or region, the number of casualties and wounded, and the types of weaponry
+used by parties [@zeitzoff2017social]. In monitoring social media channels,
+government forces may respond to the perception that citizens are gaining
+strength and sympathy. Governments have been shown to be quite tolerant of
+dissent so long as it does not metamorphose into collective action
 [@king2013censorship].
@@
 
->I know that I have been away from the media for a long time, and I have missed
-having direct contact with the citizens, but I have always been following up
-with the daily occurrences and gathering the information so that my speech can
-be built on what is said by the street.
-
-\noindent With few exceptions, Assad chose to keep social media platforms up and running.
-Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth
-of social protest online and in the streets by shutting down the Internet.
-During these times, however, she finds that military repression increases.
-However, government information about the citizens decreases; as such, many
-regimes have elected to maintain Internet connectivity as a means of monitoring
-and surveilling their citizens.
+\setlength{\leftskip}{1cm}
+
+\noindent I know that I have been away from the media for a long time, and I
+have missed having direct contact with the citizens, but I have always been
+following up with the daily occurrences and gathering the information so that my
+speech can be built on what is said by the street.
+
+\setlength{\leftskip}{0pt}
+
+\noindent With few exceptions, Assad chose to keep social media platforms up and
+running. Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart
+the growth of social protest online and in the streets by shutting down the
+Internet. During these times, military repression increases, but government
+information about the citizens decreases. As a result, regimes may elect to
+maintain Internet connectivity to monitor and surveil their citizens.
 
@@
 People join social and political resistance movements because they feel a sense
-of connection to the cause. Given that people are generally risk-averse, overcoming inertia
-requires a strong connection to the group identity or a strong aversion to an
-individual, event, or political injustice [@goldstone1980theories;
+of connection to the cause. Given that people are generally risk-averse,
+overcoming inertia requires a strong connection to the group identity or a
+strong aversion to an individual, event, or political injustice
+[@goldstone1980theories;
 @goldstone2011understanding]. Political resistance offers participants the
 opportunity to “lose themselves” and relinquish their individual identity in
-favor of identification with a larger group, contributing to a cohesive
-group ready and mobilized for action [@Hoffer2011true].
-
-Previous research on social movements supports the idea that participants are
-more likely to join movements when they know and have a personal connection to
-someone else already involved [@mcadam1986recruitment]. The type of collective
-contentious behavior that manifests in society is a function of the available
-political opportunity structures. The political opportunity structure are
-“comprised of *(sic)* specific configurations of resources, institutional
-arrangements and historical precedents for social mobilization, which facilitate
-the development of protest movements in some instances and constrain them in
-others” [@kitschelt1986political]. What emerges as strategies and tactics in
-contentious politics are, in essence, a function of what the system makes
-possible. This includes the number of people and their disposition (i.e.
-nonviolent or violent), as well as their internal structure. The more cohesive a
-group is, the greater threat they pose to the establishment.
-
-Cohesion is also a familiar concept in the study of civil conflicts, as it
-pertains to group affiliation and the ability to overcome collective action
-problems. Individuals must act in concert---that is, cohesively---to
-accomplish the task of challenging the authority of the state [@olson1965logic;
+favor of identification with a larger group, contributing to a cohesive group
+ready and mobilized for action [@Hoffer2011true].
+
+The type of collective contentious behavior that manifests in society is a
+function of the available political opportunity structures. The political
+opportunity structure is “comprised of *(sic)* specific configurations of
+resources, institutional arrangements and historical precedents for social
+mobilization, which facilitate the development of protest movements in some
+instances and constrain them in others” [@kitschelt1986political]. What emerges
+as strategies and tactics in contentious politics are a function of
+what the system makes possible. This includes the number of people and their
+disposition (i.e. nonviolent or violent), as well as their internal structure.
+The more cohesive a group is, the greater threat they pose to the establishment.
+
+Cohesion is a familiar concept in the study of civil conflicts, as it pertains
+to group affiliation and the ability to overcome collective action problems.
+Individuals must act in concert---that is, cohesively---to accomplish the task
+of challenging state authority [@olson1965logic;
 @eisinger1973conditions; @tilly2004contentious; @francisco1995relationship].
-Recent work has considered rebel recruitment for participation in
-civil conflicts as a function of internal cohesion [@gates2002recruitment]:
-Rebel movement success is influenced by the degree of group cohesion, which
-itself is a function of geographic distance, ideology, and ethnicity.
-Within Syria, multiple rebel groups exist, sourcing fighters locally
-from the disaffected Syrian population and internationally through
-fighters from transnational terrorist organizations. There is considerable
-intergroup competition for participation in the rebel movement and
-punishment for defectors for nonparticipation [@gates2002recruitment].
-Foreign fighters would appear to be amply motivated to fight, given their
-decision to relocate from a home country that may be located in the region
-or much farther away.
+Viewing rebel recruitment during civil conflicts as a function of internal
+cohesion, rebel movement success is influenced by the degree of group cohesion,
+which itself is a function of geographic distance, ideology, and ethnicity
+[@gates2002recruitment]. Within Syria, multiple rebel groups exist, sourcing
+fighters locally (from the disaffected Syrian population) and internationally
+(from transnational terrorist organizations). Groups compete intensely with one
+another for recruitment in the rebel movement and often punish defectors for
+nonparticipation [@gates2002recruitment].
 
@@
 
-The civil war literature has further explored the role of social cohesion in
-detail. Social homogeneity increases the likelihood of social conflict,
-especially when the society is polarized [@collier2004greed]; this is partly
-due to nationalist groups' strong identification with a collective identity
-[@cederman2007beyond] and their social solidarity [@sambanis2009s]. These
-same processes can be similarly important for rebels [@anyanwu2002economic].
-Referencing Gurr's [-@gurr2000peoples] work on minorities at
-risk, Regan and Norton [-@regan2005greed] note that
-
->a religious or linguistic minority
+The civil war literature has also explored the role of social cohesion. Social
+homogeneity increases the likelihood of social conflict, especially when the
+society is polarized [@collier2004greed]; this is partly due to nationalist
+groups' strong identification with a collective identity [@cederman2007beyond]
+and their social solidarity [@sambanis2009s]. These same processes can be
+similarly important for rebels [@anyanwu2002economic]. Referencing Gurr's
+[-@gurr2000peoples] work on minorities at risk, Regan and Norton
+[-@regan2005greed] note that
+
+\setlength{\leftskip}{1cm}
+
+\noindent a religious or linguistic minority
 might suffer disproportionately in a given society, and this form of
@@
 maldistributions, it is individual penury that allows for this collective
-mobilization. [@regan2005greed]
+mobilization.
+
+\setlength{\leftskip}{0pt}
 
@@
 
-The words that comprise social media posts are the first level of cohesion that
-we will consider.  In Figure \@ref(fig:cohesion-in-tweets), we see four
-sequential tweets, each containing four words. Each sequential tweet contains
-some content included in the previous tweets. The linguistic construct of
-content word overlap measures the relationship across units of meaning---here,
-tweets---where identical and semantically similar words are repeated
-[@graesser2004coh]. These repeated lexical items constitute a theme; on Twitter,
-this might be a particular hashtag, a name, a location, or other nominal
-category. This localized cohesion is referential; words are repeated and
-co-referred across tweets, creating a sense of continuity and cohesiveness of
-meaning and message.
+The first level of cohesion that we will consider are the words within social
+media posts.  In Figure \@ref(fig:cohesion-in-tweets), we see four sequential
+tweets of four words each. Each sequential tweet contains some content
+included in the previous tweets. The linguistic construct of content word
+overlap measures the relationship across units of meaning---here, tweets---where
+identical and semantically similar words are repeated [@graesser2004coh]. These
+repeated lexical items constitute a theme; on Twitter, this might be a
+particular hashtag, a name, a location, or another nominal category. This
+localized cohesion is referential; words are repeated and co-referred across
+tweets, creating a sense of continuity and cohesiveness.
+
+[Figure \@ref(fig:cohesion-in-tweets) about here]
 
@@
 The use of similar language can provide insight into *interlocutor cohesion*, or
-the degree to which people are talking about similar things. This can---as noted
-earlier---include people who are talking about similar things from radically
-perspectives, as well as those who are talking about something from the same
-perspective. Previous research from political science has investigated these
-ideas [@Windsor2020]: The “Occupy Wall Street” movement has been held up as an
-example of a movement with low interlocutor and linguistic cohesion because of
-its wide range of signs and slogans, while the “I am a man” protest (captured by
-Ernest Withers during the 1968 sanitation workers' strike in Memphis, TN) or the
-“Black Lives Matter” placards (following the uprising in Ferguson, MO) have high
-lexical and interlocutor cohesion [@edgar2018struggle].
-
-Fed by lexical cohesion, interlocutor cohesion ebbs and flows along a timeline
-contextualized by variation in real world events. Interlocutor cohesion may
-increase preceding an in-person social mobilization event, alerting a repressive
-government that collective mobilization is happening. Interlocutor cohesion may
-also respond to exogenous events such as spontaneous, unprovoked militarized
-conflict. If government forces target a new location using military weapons,
-this can precipitate online mobilization and discussion of the event.
+the degree to which people are talking about similar things. This can include
+people who are talking about similar things from radically perspectives, as well
+as those who are talking about something from the same perspective. Previous
+research from political science has investigated these ideas [@Windsor2020]: The
+“Occupy Wall Street” movement has been held up as an example of a movement with
+low interlocutor and linguistic cohesion because of its wide range of signs and
+slogans, while the “I am a man” protest (during the 1968 sanitation workers'
+strike in Memphis, TN) or the “Black Lives Matter” placards (following the
+uprising in Ferguson, MO) have high lexical and interlocutor cohesion
+[@edgar2018struggle].
+
+Fed by lexical cohesion, interlocutor cohesion ebbs and flows, contextualized by
+changing real world events. Interlocutor cohesion may increase preceding an
+in-person social mobilization event, alerting a repressive government that
+collective mobilization is happening. Interlocutor cohesion may also respond to
+exogenous events such as spontaneous, unprovoked militarized conflict.
 
 Given the importance of lexical and interlocutor cohesion for messaging in
-political movements, lexical cohesion may be an important bit of trace data for
+political movements, lexical cohesion may be important trace data for
 researchers interested in leveraging social media data to analyze social
@@
 to contribute to the group [@wiltermuth2009synchrony], and shared identity
-is associated with a greater willingness to adopt the group's goals and
+leads to a greater willingness to adopt the group's goals and
 motivations [@walton2012mere].
 
-We should expect to see increased linguistic cohesion among people participating
-in online discussions about an idea, event, individual, or movement. Given that
-Syrian protesters are known to have coordinated their activity through Twitter
-by discussing their own events (e.g., planned protests, active demonstrations)
-and their reactions to events happening around them (e.g., government reactions,
-international action or inaction), the cohesion in social media should be
-expected to correlate with the social cohesion of the group [@zeitzoff2011using].
-
-This social cohesion can have real and wide-ranging impacts on a political
-movement and the people in it. A socially cohesive group is inherently more
-threatening to the existing regime because it reflects collective opposition
-momentum and the professionalization of potential alternate leadership. Groups
-with high social cohesion are more difficult to divide and conquer, and more
-cohesive messages may also garner increased international support. Global
-insurgency movements exhibit similar patterns in their social structure
-[@bohorquez2009common]. Each violent group has a stable state. Exogenous events
-can create perturbations that push the group to become either more cohesive or
-more fragmented. Rather than frenetic, patchwork messages via Twitter, emergent
-or intentional cohesive online messaging---using similar language, paralleling
-in-person messaging [@Windsor2020]---are a sign of increased organizational
-structure, inciting a government response.
+We expect to see increased linguistic cohesion among people participating in
+online discussions about an idea, event, individual, or movement. Given that
+Syrian protesters coordinated their activity through Twitter by discussing their
+own events (e.g., planned protests, active demonstrations) and their reactions
+to events happening around them (e.g., government reactions, international
+action or inaction), the cohesion in social media should correlate with the
+social cohesion of the group [@zeitzoff2011using].
+
+Political and social cohesion in the world can be modeled using event data which
+encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
+Event Observations) encode a set of activities with numerical values, rescaled
+to reflect a conflict-cooperation scale [@schrodt2006twenty;
+@goldstein1992conflict]. These event codes include a range of behaviors, from
+making public statements and appeals, to demanding, threatening, protesting, and
+using unconventional mass violence.
+
+Social cohesion can have real and wide-ranging impacts on a political movement
+and the people in it. A socially cohesive group is inherently more threatening
+to the existing regime because it reflects momentum in collective opposition and
+the professionalization of alternate leadership. Global insurgency movements
+exhibit similar patterns in their social structure [@bohorquez2009common].
+Rather than patchwork messages via Twitter, emergent or intentional cohesive
+online messaging---using similar language, paralleling in-person messaging
+[@Windsor2020]---demonstrates increased organizational structure, inciting a
+government response.
 
 Thus, lexical and interpersonal cohesion are hypothesized to be tied to social
-and political cohesion. Shared language in an online environment may lead to the
-development or expression of a shared identity [@wiltermuth2009synchrony]. This,
-in turn, may drive individuals' propensity to engage in similar coordinated
-behavior on behalf of the group [@wiltermuth2009synchrony; @walton2012mere].
-Taken together, these two processes may increase movement participants' weak and
-strong ties [@granovetter1977strength; @gladwell2010revolution;
-@mcadam1986recruitment], strengthening the movement overall by expanding and
-deepening heterogenous ties. Therefore, in the context of social conflict, the
-linguistic cohesion of the online conversation should correspond to the degree
-of social cohesion on the ground.
+and political cohesion. Shared online language may lead to the development or
+expression of shared identity [@wiltermuth2009synchrony]. This, in turn, may
+drive individuals' propensity to engage in coordinated behavior for the group
+[@wiltermuth2009synchrony; @walton2012mere]. Taken together, these processes may
+increase movement participants' weak and strong ties [@granovetter1977strength;
+@gladwell2010revolution;
+@mcadam1986recruitment], building the movement by expanding and deepening
+heterogenous ties. Therefore, during social conflict, the linguistic cohesion
+of the online conversation should correspond to the degree of social cohesion on
+the ground.
 
@@
 groundbreaking work demonstrated that participants on the fringe of a social
-movement contribute substantially to the overall level of protest. In addition
-to providing new methods to this growing field of study, we build on this
-previous work by demonstrating how sociolinguistic cohesion evolves in
-tandem with negative and positive exogenous events.
-
-Political and social cohesion in the world can be modeled using event data which
-encodes who does what to whom on a given day. This could include events such as
-the government imposing a blockade or fighting with artillery or tanks on
-a civilian group. CAMEO (Conflict and Mediation Event Observations) encode
-a set of activities with numerical values, rescaled to reflect a
-conflict-cooperation scale [@schrodt2006twenty; @goldstein1992conflict]. These event
-codes include a range of behaviors, from making public statements and appeals,
-to demanding, threatening, protesting, and using unconventional mass violence.
+movement contribute substantially to the overall level of protest. Here, in
+addition to providing new methods to this area, we build on this work by
+demonstrating how sociolinguistic cohesion evolves in tandem with negative and
+positive exogenous events.
 
@@
 a theoretical framework called *sociolinguistic cohesion*, as shown in Figure
-\@ref(fig:theoretical-framework). Several interconnected mechanisms are in
-motion here. Previous values of linguistic cohesion should influence future
-values of linguistic cohesion and future actions in the real world space.
-Previous events influence future events and future linguistic cohesion in
-social media.
+\@ref(fig:theoretical-framework). Previous values of linguistic cohesion should
+influence future values of linguistic cohesion and future actions in the real
+world space. Previous events influence future events and future linguistic
+cohesion in social media.
+
+[Figure \@ref(fig:theoretical-framework) about here]
 
@@
 states of the political sphere. Other scholars have noted the diffusion of
-messages whereby they reach a critical mass, whereby “behaviors, beliefs, and
-preferences” spread within a population [@barash2012critical].  Cohesion
+messages that reach critical mass, allowing for “behaviors, beliefs, and
+preferences” to spread within a population [@barash2012critical]. Cohesion
 changes over time in response to external events and the internal dynamics of
-the social movement. This can occur even if the social interaction occurs entirely 
+the social movement, even if the social interaction occurs entirely 
 online [@centola2007complex].
+
+Lexical cohesion, then, is a useful indicator of social cohesion in political
+crisis. Lexical cohesion happens at the word level. Interlocutor cohesion
+happens between speakers. Political cohesion happens at the social level during
+moments of political crisis, like civil wars and social movements.
+Sociolinguistic cohesion comprises lexical, interlocutor, and sociopolitical
+events, in which the words and their context reveal the disposition of socially
+connected linguistic communities. It accounts for the cohesion between multiple
+speakers in an environment as their language becomes more similar.
+Sociolinguistic cohesion also addresses how groups involved in political
+rebellion converge to mount sustained resistance to state authority.
 
@@
 close the paper with specific suggestions to political scientists interested in
-incorporating these methods into their work.
+these methods.
+
+This work is a reproducible manuscript. All code and analyses can be found at:
+[redacted for blind review].
 
@@
 
+[Figure \@ref(fig:raw-cohesion-ts) about here]
+
 ```{r raw-cohesion-ts, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap="Raw social cohesion metric time series."}
@@
 filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).
+
+[Figures \@ref(fig:raw-event-ts-target) and \@ref(fig:raw-event-ts-source-target) about here]
 
@@
 
+[Figures \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]
+
 #### Visualization
@@
 
+For social cohesion and count of all events, there was a consistent period of
+above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
+one-week peaks at the beginning of the time period, DET was largely above chance
+from the 46th to the 61st window, with some exceptions (Figure
+\@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of positive events, we saw a downward trend in RR
+as the window advances throughout the sample. Interestingly, we see largely
+above-chance RR until the 50th window, with some exceptions during window
+periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
+60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+For social cohesion and count of negative events, RR stayed above or almost
+above chance from the 4th--7th and 43rd--47th windows. DET was above or nearly
+above chance in the 1st and 2nd windows, with intermittent peaks in later
+windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+
+[Figure \@ref(fig:plot-wcrqa-targ-all) about here]
+
+### Syria as Source and Target
+
+```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
+
+# call image
+knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
+
+```
+
 ```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Mode ICEWS event per day.'}
@@
                     ylab("Mode ICEWS event")
-ggsave("./results/primary/mode_ts_plot.png")
+ggsave("./results/primary/mode_ts_plot.png", dpi=200)
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
-one-week peaks at the beginning of the time period, DET was largely above chance
-from the 46th to the 61st window, with some exceptions (Figure
-\@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of positive events, we saw a downward trend in RR
-as the window advances throughout the sample. Interestingly, we see largely
-above-chance RR until the 50th window, with some exceptions during window
-periods 19-30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
-60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 43rd-47th windows. DET was above or nearly
-above chance in the 1st and 2nd windows, with intermittent peaks in later
-windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
-
-### Syria as Source and Target
-
-```{r plot-wcrqa-source-targ-all, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Windowed CRQA for social cohesion and event counts from source and target filtered data.', out.extra='angle=90'}
-
-# call image
-knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")
-
-```
-
-For social cohesion and count of all events, there was a consistent period of
 above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
-also showed above- or nearly above-chance values in windows 7 through 17 and
+also showed above- or nearly above-chance values in windows 7--17 and
 intermittent peaks between the 34th and 61st windows (Figure
@@
 
+[Figure \@ref(fig:plot-wcrqa-source-targ-all) about here]
+
 # Discussion
@@
 online communication on Twitter in Syria during Arab Spring. CRQA methodology
-allows us to model the relationship between sociolinguistic cohesion and
+allows us to disentangle the relationship between sociolinguistic cohesion and
 exogenous political events. This work stands alongside the model of
-Palestinian-Israeli social media and events developed by Zeitzoff (2011), and
+Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
 the role of peripheral participants in the Syrian Arab Spring movement by
-Steinert-Threlkeld (2017). By introducing the CRQA and WCRQA methods, we
+@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
 demonstrate how language and social mobilization interact with events along the
@@
 
+[Figure \@ref(fig:plot-mode-event) about here]
+
 Surprisingly---and contrary to our second hypothesis---we saw consistent
@@
 
-This work was completed in part as coursework done by lead author M. Chiovaro in
-the “Applications of Nonlinear Time Series Analysis” graduate course at the
-University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
-Harrison).
+\noindent[redacted for blind review]
+
+<!-- This work was completed in part as coursework done by lead author M. Chiovaro in -->
+<!-- the “Applications of Nonlinear Time Series Analysis” graduate course at the -->
+<!-- University of Connecticut (co-taught by coauthor A. Paxton and Steven J. -->
+<!-- Harrison). -->
 

### 2020-07-06 manuscript.Rmd
Remove redactions

@@
 This work is a reproducible manuscript. All code and analyses can be found at:
-[redacted for blind review].
+www.github.com/mchiovaro/arab-spring.
 
@@
 
-\noindent[redacted for blind review]
-
-<!-- This work was completed in part as coursework done by lead author M. Chiovaro in -->
-<!-- the “Applications of Nonlinear Time Series Analysis” graduate course at the -->
-<!-- University of Connecticut (co-taught by coauthor A. Paxton and Steven J. -->
-<!-- Harrison). -->
+This work was completed in part as coursework done by lead author M. Chiovaro in
+the “Applications of Nonlinear Time Series Analysis” graduate course at the
+University of Connecticut (co-taught by coauthor A. Paxton and Steven J.
+Harrison).
 

### 2020-07-07 manuscript.Rmd
Add page numbers for block quotes
Fix typos and tweet counter

@@
 issue is how and why these ambitions and techniques resonated in their various
-local contexts.
+local contexts. (p. 2)
 
@@
 maldistributions, it is individual penury that allows for this collective
-mobilization.
+mobilization. (p. 323)
 
@@
 ```{r cohesion-in-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = "A visual representation of cohesion in tweets.
-The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occuring.", out.width='100%'}
+The shared content words--either identical or semantically similar--constitute a theme around which cohesion is occurring.", out.width='100%'}
 
@@
 
-At the same time, the foundational theoretical assumptions of a linear world has
+At the same time, the foundational theoretical assumptions of a linear world have
 been increasingly replaced by ideas from dynamical systems theory. Rather than a
@@
 
-The corpus of tweets used included `r sum(cohesion_df$n)` Syrian tweets
+```{r num-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")
+
+```
+
+The corpus of tweets used included `r sum(num_tweets$n)` Syrian tweets
 occurring between March 30--June 15, 2012. Using the Twitter streaming API,
@@
 
-```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from target filtered data.', out.width='100%'}
+```{r plot-rp-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from target filtered data.', out.width='100%'}
 
@@
 
-```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and count of all events from source and target filtered data.', out.width='100%'}
+```{r plot-rp-source-targ, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from source and target filtered data.', out.width='100%'}
 

### 2020-08-03 scripts/secondary-analyses/terrier/02_crqa.R
Update Terrier CRQA

@@ -1,0 +1,530 @@
+######## Cross-Recurrence Quantification Analysis (Terrier) ########
+#
+# This script runs cross-recurrence quantification analysis
+# the real-world events and Twitter social cohesion of 
+# Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_08_03
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# specify global plotting variables
+all_event_color = "#CC79A7"
+positive_event_color = "#0072B2"
+negative_event_color = "#D55E00"
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/terrier/formatted_data.csv")
+shuffled_full <- read.csv("./data/formatted/secondary/terrier/shuffled_data_full.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_full[,c(1:1000)]
+shuffled_all_source_target <- shuffled_full[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_full[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_full[,c(3001:4000)]
+shuffled_all_target <- shuffled_full[,c(4001:5000)]
+shuffled_pos_target <- shuffled_full[,c(5001:6000)]
+shuffled_neg_target <- shuffled_full[,c(6001:7000)]
+
+#### 2. Run CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# run cross recurrence
+cross_recurrence_analysis = crqa(ts1=data$coh_deciles,
+                                 ts2=data$all_deciles_source_target,
+                                 delay=0,
+                                 embed=1,
+                                 rescale=0,
+                                 radius=.001,
+                                 normalize=0,
+                                 mindiagline=2,
+                                 minvertline=2,
+                                 tw=0) 
+
+# save the crqa results
+rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
+write.table(rqa_results_all_source_target,'./results/secondary/terrier/crqa/source_target-crqa_results-all_events.csv',
+            sep=",", row.names=FALSE)
+
+# build the CRP using 'crqa' package function: plotRP
+png("./results/secondary/terrier/crqa/source_target-rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
+par = list(unit = 2, 
[…]

### 2020-08-03 scripts/secondary-analyses/phoenix/03_windowed_crqa.R
Update Phoenix WCRQA

@@ -6,7 +6,7 @@
 #
 # Code by: M. Chiovaro (@mchiovaro)
 # University of Connecticut
-# Last updated: 2020_05_21
+# Last updated: 2020_07_29
 
 #### 1. Set up ####
 
@@ -295,10 +295,9 @@ for (i in 1:9){
 
 # rename variables
 names(significance_pos_source_target) <- c("RR", "DET", 
-                                           "NRLINE", "maxL", 
-                                           "L", "ENTR", 
-                                           "rENTR", "LAM", 
-                                           "TT")
+                                           "NRLINE", "maxL", "L", 
+                                           "ENTR", "rENTR", 
+                                           "LAM", "TT")
 
 ## count of negative events and social cohesion ##
 
@@ -377,8 +376,7 @@ for (i in 1:1000) {
   rqa_results <- data.frame(c(cross_recurrence_analysis[1:9]))
   
   # bind to dataframe
-  rqa_shuffled_all_target <- rbind(rqa_shuffled_all_target, 
-                                   rqa_results)
+  rqa_shuffled_all_target <- rbind(rqa_shuffled_all_target, rqa_results)
   
 }
 
@@ -429,8 +427,7 @@ for (i in 1:1000) {
   rqa_results <- data.frame(c(cross_recurrence_analysis[1:9]))
   
   # bind to dataframe
-  rqa_shuffled_pos_target <- rbind(rqa_shuffled_pos_target, 
-                                   rqa_results)
+  rqa_shuffled_pos_target <- rbind(rqa_shuffled_pos_target, rqa_results)
   
 }
 
@@ -481,8 +478,7 @@ for (i in 1:1000) {
   rqa_results <- data.frame(c(cross_recurrence_analysis[1:9]))
   
   # bind to dataframe
-  rqa_shuffled_neg_target <- rbind(rqa_shuffled_neg_target, 
-                                   rqa_results)
+  rqa_shuffled_neg_target <- rbind(rqa_shuffled_neg_target, rqa_results)
   
 }
 
@@ -751,6 +747,7 @@ plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "with event count data",
+                       "with source and target filtering",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -1001,7 +998,8 @@ plot_target_windowed_neg_DET = ggplot(data = wincrqa_neg_df_target,
[…]

### 2020-08-03 scripts/secondary-analyses/terrier/03_windowed_crqa.R
Update Terrier WCRQA

@@ -1,0 +1,1019 @@
+######## Windowed Cross-Recurrence Quantification Analysis (Terrier) ########
+#
+# This script runs windowed cross-recurrence quantification 
+# analysis the real-world events and Twitter social cohesion 
+# of Arab Spring.
+#
+# Code by: M. Chiovaro (@mchiovaro)
+# University of Connecticut
+# Last updated: 2020_08_03
+
+#### 1. Set up ####
+
+# clear environment
+rm(list=ls())
+
+# read in data 
+data <- read.csv("./data/formatted/secondary/terrier/formatted_data.csv")
+shuffled_windowed <- read.csv("./data/formatted/secondary/terrier/shuffled_data_windowed.csv")
+
+# split shuffled data into their own dataframes
+shuffled_coh <- shuffled_windowed[,c(1:1000)]
+shuffled_all_source_target <- shuffled_windowed[,c(1001:2000)]
+shuffled_pos_source_target <- shuffled_windowed[,c(2001:3000)]
+shuffled_neg_source_target <- shuffled_windowed[,c(3001:4000)]
+shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
+shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
+shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
+
+#### 2. Run Windowed CRQA ####
+
+### source and target filtered data ###
+
+## count of all events and social cohesion ##
+
+# calculate windowed rqa
+windowed_all_source_target = wincrqa(ts1 = data$coh_deciles, 
+                                     ts2 = data$all_deciles_source_target, 
+                                     windowstep = 1, 
+                                     windowsize = 14,
+                                     radius = .001,  
+                                     delay = 1,       
+                                     embed = 1, 
+                                     rescale = 0, 
+                                     normalize = 0,  
+                                     mindiagline = 2, 
+                                     minvertline = 2, 
+                                     tw = 0,
+                                     whiteline = FALSE,
+                                     trend = TRUE) 
+
+# tranform into a dataframe for easier plotting 
+wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
+colnames(wincrqa_all_df_source_target) <- c("RR", "DET", 
+                                            "NRLINE", "maxL", "L", 
+                                            "ENTR", "rENTR", 
+                                            "LAM", "TT", 
+                                            "window")
+
[…]

### 2020-08-04 scripts/secondary-analyses/icews/01_formatting_data.R
Remove primary files from secondary scripts

@@ -1,603 +1,0 @@
-######## Secondary Analysis: Formatting ICEWS Arab Spring Data ########
-#
-# This script formats data related to the Arab Spring.
-# Daily Twitter social cohesion and event data are processed
-# and transformed into *sextiles* for CRQA and windowed CRQA
-# analyses.
-#
-# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
-# University of Connecticut
-# Last updated: 2020_05_27
-
-#### 1. Set up ####
-
-# clear environment
-rm(list=ls())
-
-# read in the data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
-ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab",
-                       header = TRUE, sep = "\t", quote = "")
-
-#### 2. Filter and format the time series ####
-
-### filter for source and target ###
-
-# filter full 2012 ICEWS data for correct dates and parameters
-ICEWS_filtered <- ICEWS_df %>%
-  
-  # fill blanks with NAs
-  na_if("") %>%
-  
-  # turn factor to character for using grepl
-  mutate(Event.Date = as.character(Event.Date)) %>%
-  
-  # filter out unusable dates
-  filter(grepl("^(2012)[-](0[1-9]|1[012])[-](0[1-9]|[12][0-9]|3[01])$",
-               Event.Date)) %>%
-  
-  # turn to date format to use select for date range
-  mutate_at(vars(Event.Date), as.Date, format = "%Y-%m-%d") %>%
-  
-  # grab the dates that align with old data
-  filter(Event.Date >= as.Date("2012-03-30")
-         & Event.Date <= as.Date("2012-06-15")) %>%
-  
-  # change search params to characters for searching
-  mutate_if(is.factor, as.character)  %>%
-  
-  # grab observations where either source or target is Syria
-  filter(grepl("Syria", Source.Country) |
-           grepl("Syria", Target.Country)) %>%
-  
-  # filter out invalid intensity formats
-  filter(grepl("\\-*\\d+\\.*\\d*", Intensity)) %>%
-  
-  # convert intensity to numeric
-  mutate(Intensity = as.numeric(Intensity)) %>%
-  
-  # filter out invalid intensity values
-  filter(Intensity >= -10 & Intensity <= 10)
-
-### prep the event count time series ###
-
-# create new dataframe with counts of different events
[…]

### 2020-08-04 scripts/secondary-analyses/icews/02_crqa.R

@@ -1,525 +1,0 @@
-######## Cross-Recurrence Quantification Analysis ########
-#
-# This script runs cross-recurrence quantification analysis
-# the real-world events and Twitter social cohesion of 
-# Arab Spring.
-#
-# Code by: M. Chiovaro (@mchiovaro)
-# University of Connecticut
-# Last updated: 2020_05_21
-
-#### 1. Set up ####
-
-# clear environment
-rm(list=ls())
-
-# read in data 
-data <- read.csv("./data/formatted/secondary/icews/formatted_data.csv")
-shuffled_full <- read.csv("./data/formatted/secondary/icews/shuffled_data_full.csv")
-
-# split shuffled data into their own dataframes
-shuffled_coh <- shuffled_full[,c(1:1000)]
-shuffled_all_source_target <- shuffled_full[,c(1001:2000)]
-shuffled_pos_source_target <- shuffled_full[,c(2001:3000)]
-shuffled_neg_source_target <- shuffled_full[,c(3001:4000)]
-shuffled_all_target <- shuffled_full[,c(4001:5000)]
-shuffled_pos_target <- shuffled_full[,c(5001:6000)]
-shuffled_neg_target <- shuffled_full[,c(6001:7000)]
-
-#### 2. Run CRQA ####
-
-### source and target filtered data ###
-
-## count of all events and social cohesion ##
-
-# run cross recurrence
-cross_recurrence_analysis = crqa(ts1=data$coh_sextiles,
-                                 ts2=data$all_sextiles_source_target,
-                                 delay=0,
-                                 embed=1,
-                                 rescale=0,
-                                 radius=.001,
-                                 normalize=0,
-                                 mindiagline=2,
-                                 minvertline=2,
-                                 tw=0) 
-
-# save the crqa results
-rqa_results_all_source_target <- data.frame(c(cross_recurrence_analysis[1:9]))
-write.table(rqa_results_all_source_target,'./results/secondary/icews/crqa/source_target-crqa_results-all_events.csv',
-            sep=",", row.names=FALSE)
-
-# build the CRP using 'crqa' package function: plotRP
-png("./results/secondary/icews/crqa/source_target-rp-all_events.png", width = 4, height = 4, units = 'in', res = 300)
-par = list(unit = 2, 
-           labelx = "Social cohesion", 
-           labely = "Count of all events", 
-           cols = "blue", 
-           pcex = .5)
[…]

### 2020-08-04 scripts/secondary-analyses/icews/03_windowed_crqa.R

@@ -1,1020 +1,0 @@
-######## Windowed Cross-Recurrence Quantification Analysis (ICEWS) ########
-#
-# This script runs windowed cross-recurrence quantification 
-# analysis the real-world events and Twitter social cohesion 
-# of Arab Spring.
-#
-# Code by: M. Chiovaro (@mchiovaro)
-# University of Connecticut
-# Last updated: 2020_05_21 
-
-#### 1. Set up ####
-
-# clear environment
-rm(list=ls())
-
-# read in data 
-data <- read.csv("./data/formatted/secondary/icews/formatted_data.csv")
-shuffled_windowed <- read.csv("./data/formatted/secondary/icews/shuffled_data_windowed.csv")
-
-# split shuffled data into their own dataframes
-shuffled_coh <- shuffled_windowed[,c(1:1000)]
-shuffled_all_source_target <- shuffled_windowed[,c(1001:2000)]
-shuffled_pos_source_target <- shuffled_windowed[,c(2001:3000)]
-shuffled_neg_source_target <- shuffled_windowed[,c(3001:4000)]
-shuffled_all_target <- shuffled_windowed[,c(4001:5000)]
-shuffled_pos_target <- shuffled_windowed[,c(5001:6000)]
-shuffled_neg_target <- shuffled_windowed[,c(6001:7000)]
-
-#### 2. Run Windowed CRQA ####
-
-### source and target filtered data ###
-
-## count of all events and social cohesion ##
-
-# calculate windowed rqa
-windowed_all_source_target = wincrqa(ts1 = data$coh_sextiles, 
-                                       ts2 = data$all_sextiles_source_target, 
-                                       windowstep = 1, 
-                                       windowsize = 14,
-                                       radius = .001,  
-                                       delay = 1,       
-                                       embed = 1, 
-                                       rescale = 0, 
-                                       normalize = 0,  
-                                       mindiagline = 2, 
-                                       minvertline = 2, 
-                                       tw = 0,
-                                       whiteline = FALSE,
-                                       trend = TRUE) 
-
-# tranform into a dataframe for easier plotting 
-wincrqa_all_df_source_target <- as.data.frame(windowed_all_source_target$crqwin)
-colnames(wincrqa_all_df_source_target) <- c("RR", "DET", 
-                                            "NRLINE", "maxL", "L", 
-                                            "ENTR", "rENTR", 
-                                            "LAM", "TT", 
-                                            "window")
-
[…]

### 2020-08-04 scripts/secondary-analyses/icews/04_cross_wavelet.R

@@ -1,71 +1,0 @@
-######## Cross Wavelet Analysis (ICEWS) ########
-#
-# This script runs cross wavelet analysis on the
-# real-world events and Twitter social cohesion of 
-# Arab Spring.
-#
-# Code by: M. Chiovaro (@mchiovaro)
-# University of Connecticut
-# Last updated: 2020_05_15
-
-# clear environment
-rm(list=ls())
-
-# set working directory
-setwd("./arab-spring/")
-
-# load the required packages
-library(dplyr)
-library(biwavelet)
-
-# read in truncated data 
-data <- read.csv("./data/formatted/formatted_data.csv")
-
-# make date into a number for the analysis
-data$date_num <- seq(from =1, to = nrow(data))
-
-t1 <- data[,c("date_num", "coh_dec")]
-t2 <- data[,c("date_num", "all_dec")]
-
-##### Coherence #####
-
-# Specify the number of iterations. The more, the better (>1000)
-nrands = 1000
-
-# compute coherence
-wtc.AB = wtc(t1, t2, nrands = nrands)
-
-# make room for the color bar on the right
-par(oma = c(0, 0, 0, 1), mar = c(5, 4, 5, 5) + 0.1)
-
-# plot the graph
-plot(wtc.AB, 
-     plot.phase = TRUE, 
-     lty.coi = 1, 
-     col.coi = "grey", 
-     lwd.coi = 2, 
-     lwd.sig = 2, 
-     arrow.lwd = 0.03, 
-     arrow.len = 0.12, 
-     ylab = "Scale", 
-     xlab = "Period (days)", 
-     plot.cb = TRUE, 
-     main = "Wavelet Coherence\nMean social coherence and Count of events (deciles)")
-
-# Adding grid lines
-n = length(t1[, 1])
-abline(v = seq(5, n, 5), h = 1:16, col = "brown", lty = 1, lwd = 1)
-
-# Defining x labels
-#axis(side = 3, at = c(seq(5, n, 5)), labels = c(seq(5, 75, 5)))
-
-##### Cross Wavelet #####
-
-# Compute cross-wavelet
-xwt <- xwt(t1, t2)
-
-# make room for the color bar on the right
-par(oma=c(0, 0, 0, 1), mar=c(5, 4, 4, 5) + 0.1) 
-
-# Plot cross wavelet power and phase difference (arrows)
-plot(xwt, plot.cb=TRUE)

### 2020-08-04 scripts/secondary-analyses/phoenix/03_windowed_crqa.R
Update labels for Phoenix wcrqa plots

@@ -747,7 +747,7 @@ plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "with event count data",
-                       "with source and target filtering",
+                       "with source and target filtering (Phoenix)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -999,7 +999,7 @@ plot_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with target-only filtering",
+                       "with target-only filtering (Pheonix)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_target_windowed_all_RR,

### 2020-08-04 scripts/secondary-analyses/terrier/03_windowed_crqa.R
Update labels for Terrier wcrqa plots

@@ -747,7 +747,7 @@ plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "with event count data",
-                       "with source and target filtering",
+                       "with source and target filtering (Terrier)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -999,7 +999,7 @@ plot_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with target-only filtering",
+                       "with target-only filtering (Terrier)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_target_windowed_all_RR,

### 2020-08-04 dataset_comparison.Rmd
Start multi dataset comparison Rmd with analyses, figures, and tables

---
title             : ""
shorttitle        : ""

author:
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Leah C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
  - id            : "2"
    institution   : "Department of Psychological Sciences, University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

abstract: |
  <!-- https://tinyurl.com/ybremelq -->

keywords          : ""
wordcount         : ""

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
appendix          :

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}

# clear the workspace
rm(list=ls())

# install and load required packages
source('./scripts/required_packages.r')
source('./scripts/libraries_and_functions.r')

# turn on caching
knitr::opts_chunk$set(cache=TRUE, autodep=TRUE, cache.lazy=FALSE)

# create subdirectories
dir.create("./data/raw") # load three data files here
dir.create("./data/formatted/primary", recursive = TRUE)
dir.create("./data/formatted/secondary/phoenix", recursive = TRUE)
dir.create("./data/formatted/secondary/terrier", recursive = TRUE)
dir.create("./results/primary/crqa", recursive = TRUE)
dir.create("./results/primary/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/terrier/crqa", recursive = TRUE)
dir.create("./results/secondary/terrier/windowed-crqa", recursive = TRUE)

```

```{r data-prep, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# format the data
source('./scripts/primary-analyses/01_formatting_data.R')
source('./scripts/secondary-analyses/phoenix/01_formatting_data.R')
source('./scripts/secondary-analyses/terrier/01_formatting_data.R')

```

# Method

# Results

## CRQA

```{r icews-crqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run primary crqa analysis
source('./scripts/primary-analyses/02_crqa.R')

# read in metric names
metrics <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv",
                      header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
metrics_all_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-all_events.csv",
                               header = FALSE)[-1,-1])
metrics_pos_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-pos_events.csv",
                               header = FALSE)[-1,-1])
metrics_neg_targ <- t(read.csv("./results/primary/crqa/target-crqa_results-neg_events.csv",
                               header = FALSE)[-1,-1])

# read in significance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_all.csv",
                           header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_pos.csv",
                           header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/primary/crqa/target-metric_signif_neg.csv",
                           header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
metrics_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-all_events.csv",
                                      header = FALSE)[-1,-1])
metrics_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-pos_events.csv",
                                      header = FALSE)[-1,-1])
metrics_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-crqa_results-neg_events.csv",
                                      header = FALSE)[-1,-1])

# read in significance from permutation tests (source and target filtered)
sig_all_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_all.csv",
                                  header = FALSE)[-1,-1])
sig_pos_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_pos.csv",
                                  header = FALSE)[-1,-1])
sig_neg_source_targ <- t(read.csv("./results/primary/crqa/source_target-metric_signif_neg.csv",
                                  header = FALSE)[-1,-1])

```

```{r icews-crqa-table-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_targ,
                                      sig_all_targ,
                                      metrics_pos_targ,
                                      sig_pos_targ,
                                      metrics_neg_targ,
                                      sig_neg_targ), stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
target_results[,numerics] <- sapply(target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(target_results[,3]))
stars_pos <- as.data.frame(stars.pval(target_results[,5]))
stars_neg <- as.data.frame(stars.pval(target_results[,7]))

target_results <- cbind(target_results, stars_all, stars_pos, stars_neg)
target_results <- target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(target_results) <- c("metric",
                              "all events", "p", "sig.",
                              "positive events", "p", "sig.",
                              "negative events", "p", "sig.")

# exclude row names
rownames(target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data (ICEWS).")

```

```{r icews-rp-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from target filtered data (ICEWS).', out.width='100%'}

# call image
knitr::include_graphics("./results/primary/crqa/target-rp-joined.png")

```

```{r icews-table-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
source_target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_source_targ,
                                      sig_all_source_targ,
                                      metrics_pos_source_targ,
                                      sig_pos_source_targ,
                                      metrics_neg_source_targ,
                                      sig_neg_source_targ), stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
source_target_results[,numerics] <- sapply(source_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(source_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(source_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(source_target_results[,7]))

source_target_results <- cbind(source_target_results, stars_all, stars_pos, stars_neg)
source_target_results <- source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(source_target_results) <- c("metric",
                                     "all events", "p", "sig.",
                                     "positive events", "p", "sig.",
                                     "negative events", "p", "sig.")

# exclude row names
rownames(source_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data (ICEWS).")

```

```{r icews-rp-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from source and target filtered data (ICEWS).', out.width='100%'}

# call image
knitr::include_graphics("./results/primary/crqa/source_target-rp-joined.png")

```

```{r phoenix-crqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run primary crqa analysis
source('./scripts/secondary-analyses/phoenix/02_crqa.R')

# read in metric names
metrics <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv",
                      header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
metrics_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-all_events.csv",
                               header = FALSE)[-1,-1])
metrics_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-pos_events.csv",
                               header = FALSE)[-1,-1])
metrics_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-crqa_results-neg_events.csv",
                               header = FALSE)[-1,-1])

# read in significance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_all.csv",
                           header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_pos.csv",
                           header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/secondary/phoenix/crqa/target-metric_signif_neg.csv",
                           header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
metrics_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-all_events.csv",
                                      header = FALSE)[-1,-1])
metrics_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-pos_events.csv",
                                      header = FALSE)[-1,-1])
metrics_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-crqa_results-neg_events.csv",
                                      header = FALSE)[-1,-1])

# read in significance from permutation tests (source and target filtered)
sig_all_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_all.csv",
                                  header = FALSE)[-1,-1])
sig_pos_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_pos.csv",
                                  header = FALSE)[-1,-1])
sig_neg_source_targ <- t(read.csv("./results/secondary/phoenix/crqa/source_target-metric_signif_neg.csv",
                                  header = FALSE)[-1,-1])

```

```{r phoenix-crqa-table-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_targ,
                                      sig_all_targ,
                                      metrics_pos_targ,
                                      sig_pos_targ,
                                      metrics_neg_targ,
                                      sig_neg_targ), stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
target_results[,numerics] <- sapply(target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(target_results[,3]))
stars_pos <- as.data.frame(stars.pval(target_results[,5]))
stars_neg <- as.data.frame(stars.pval(target_results[,7]))

target_results <- cbind(target_results, stars_all, stars_pos, stars_neg)
target_results <- target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(target_results) <- c("metric",
                              "all events", "p", "sig.",
                              "positive events", "p", "sig.",
                              "negative events", "p", "sig.")

# exclude row names
rownames(target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data (Phoenix).")

```

```{r phoenix-rp-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from target filtered data (Phoenix).', out.width='100%'}

# call image
knitr::include_graphics("./results/secondary/phoenix/crqa/target-rp-joined.png")

```

```{r phoenix-table-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
source_target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_source_targ,
                                      sig_all_source_targ,
                                      metrics_pos_source_targ,
                                      sig_pos_source_targ,
                                      metrics_neg_source_targ,
                                      sig_neg_source_targ), 
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
source_target_results[,numerics] <- sapply(source_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(source_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(source_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(source_target_results[,7]))

source_target_results <- cbind(source_target_results, stars_all, stars_pos, stars_neg)
source_target_results <- source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(source_target_results) <- c("metric",
                                     "all events", "p", "sig.",
                                     "positive events", "p", "sig.",
                                     "negative events", "p", "sig.")

# exclude row names
rownames(source_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data (Phoenix).")

```

```{r phoenix-rp-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from source and target filtered data (Phoenix).', out.width='100%'}

# call image
knitr::include_graphics("./results/secondary/phoenix/crqa/source_target-rp-joined.png")

```

```{r terrier-crqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# run primary crqa analysis
source('./scripts/secondary-analyses/terrier/02_crqa.R')

# read in metric names
metrics <- t(read.csv("./results/secondary/terrier/crqa/target-crqa_results-all_events.csv",
                      header = FALSE)[-2,-1])

# read in metrics from crq analyses (target filtered)
metrics_all_targ <- t(read.csv("./results/secondary/terrier/crqa/target-crqa_results-all_events.csv",
                               header = FALSE)[-1,-1])
metrics_pos_targ <- t(read.csv("./results/secondary/terrier/crqa/target-crqa_results-pos_events.csv",
                               header = FALSE)[-1,-1])
metrics_neg_targ <- t(read.csv("./results/secondary/terrier/crqa/target-crqa_results-neg_events.csv",
                               header = FALSE)[-1,-1])

# read in significance from permutation tests (target filtered)
sig_all_targ <- t(read.csv("./results/secondary/terrier/crqa/target-metric_signif_all.csv",
                           header = FALSE)[-1,-1])
sig_pos_targ <- t(read.csv("./results/secondary/terrier/crqa/target-metric_signif_pos.csv",
                           header = FALSE)[-1,-1])
sig_neg_targ <- t(read.csv("./results/secondary/terrier/crqa/target-metric_signif_neg.csv",
                           header = FALSE)[-1,-1])

# read in metrics from crq analyses (source and target filtered)
metrics_all_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-crqa_results-all_events.csv",
                                      header = FALSE)[-1,-1])
metrics_pos_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-crqa_results-pos_events.csv",
                                      header = FALSE)[-1,-1])
metrics_neg_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-crqa_results-neg_events.csv",
                                      header = FALSE)[-1,-1])

# read in significance from permutation tests (source and target filtered)
sig_all_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-metric_signif_all.csv",
                                  header = FALSE)[-1,-1])
sig_pos_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-metric_signif_pos.csv",
                                  header = FALSE)[-1,-1])
sig_neg_source_targ <- t(read.csv("./results/secondary/terrier/crqa/source_target-metric_signif_neg.csv",
                                  header = FALSE)[-1,-1])

```

```{r terrier-crqa-table-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_targ,
                                      sig_all_targ,
                                      metrics_pos_targ,
                                      sig_pos_targ,
                                      metrics_neg_targ,
                                      sig_neg_targ), stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
target_results[,numerics] <- sapply(target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(target_results[,3]))
stars_pos <- as.data.frame(stars.pval(target_results[,5]))
stars_neg <- as.data.frame(stars.pval(target_results[,7]))

target_results <- cbind(target_results, stars_all, stars_pos, stars_neg)
target_results <- target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(target_results) <- c("metric",
                              "all events", "p", "sig.",
                              "positive events", "p", "sig.",
                              "negative events", "p", "sig.")

# exclude row names
rownames(target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(target_results, caption = "\\label{table-1}CRQA results for target-only data (Terrier).")

```

```{r terrier-rp-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from target filtered data (Terrier).', out.width='100%'}

# call image
knitr::include_graphics("./results/secondary/terrier/crqa/target-rp-joined.png")

```

```{r terrier-table-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}

# bind metrics and significance results
source_target_results <- as.data.frame(cbind(metrics,
                                      metrics_all_source_targ,
                                      sig_all_source_targ,
                                      metrics_pos_source_targ,
                                      sig_pos_source_targ,
                                      metrics_neg_source_targ,
                                      sig_neg_source_targ), 
                                      stringsAsFactors = FALSE)

# covert to numerics for rounding
numerics <- c(2:7)
source_target_results[,numerics] <- sapply(source_target_results[,numerics],as.numeric)

# add significance stars
stars_all <- as.data.frame(stars.pval(source_target_results[,3]))
stars_pos <- as.data.frame(stars.pval(source_target_results[,5]))
stars_neg <- as.data.frame(stars.pval(source_target_results[,7]))

source_target_results <- cbind(source_target_results, stars_all, stars_pos, stars_neg)
source_target_results <- source_target_results[,c(1,2,3,8,4,5,9,6,7,10)]

# give intuitive names
colnames(source_target_results) <- c("metric",
                                     "all events", "p", "sig.",
                                     "positive events", "p", "sig.",
                                     "negative events", "p", "sig.")

# exclude row names
rownames(source_target_results) <- NULL

# set to not split table and round to two decimal places
panderOptions("table.split.table", Inf)
panderOptions('round', 3)
panderOptions('keep.trailing.zeros', TRUE)

# style for Rmd
panderOptions("table.style", "rmarkdown")

# build table
pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data (Terrier).")

```

```{r terrier-rp-source-target, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Recurrence plot (RP) for social cohesion and counts of events from source and target filtered data (Terrier).', out.width='100%'}

# call image
knitr::include_graphics("./results/secondary/terrier/crqa/source_target-rp-joined.png")

```

## Windowed CRQA
```{r run-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide', include = FALSE}

# run windowed crqa
source('./scripts/primary-analyses/03_windowed_crqa.R')
source('./scripts/secondary-analyses/phoenix/03_windowed_crqa.R')
source('./scripts/secondary-analyses/terrier/03_windowed_crqa.R')

```

```{r plot-wcrqa, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, out.extra='angle=90'}

# call ICEWS plots
knitr::include_graphics("./results/primary/windowed-crqa/target-windowed_all.png")
knitr::include_graphics("./results/primary/windowed-crqa/source_target-windowed_all.png")

# call Phoenix plots
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/target-windowed_all.png")
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all.png")

# call Terrier plots
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/target-windowed_all.png")
knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all.png")

```

## Cross-Wavelet Analysis
```{r cross-wavelet, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, results='hide'}

# format the data
# source('./scripts/primary-analyses/04_cross_wavelet.R')
# source('./scripts/secondary-analyses/phoenix/04_cross_wavelet.R')
# source('./scripts/secondary-analyses/terrier/04_cross_wavelet.R')

```

# Discussion

# Acknowledgements

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-08-04 scripts/libraries_and_functions.r
Update required packages

@@ -17,7 +17,8 @@ required_packages = c(
   'knitr',
   'statip',
   'gridExtra',
-  'png'
+  'png',
+  'data.table'
 )
 
 # load required packages

### 2020-08-04 scripts/required_packages.r

@@ -17,7 +17,8 @@ required_packages = c(
   'knitr',
   'statip',
   'gridExtra',
-  'png'
+  'png',
+  'data.table'
 )
 
 # install missing packages (adapted from <http://stackoverflow.com/a/4090208> and a-paxton/perception-memory-coordination)

### 2020-08-04 scripts/secondary-analyses/phoenix/03_windowed_crqa.R
Fix line endings

@@ -746,7 +746,7 @@ plot_source_target_windowed_neg_DET = ggplot(data = wincrqa_neg_df_source_target
 plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
-                       "with event count data",
+                       "\nwith event count data",
                        "with source and target filtering (Phoenix)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 

### 2020-08-04 scripts/secondary-analyses/terrier/03_windowed_crqa.R

@@ -746,7 +746,7 @@ plot_source_target_windowed_neg_DET = ggplot(data = wincrqa_neg_df_source_target
 plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
-                       "with event count data",
+                       "\nwith event count data",
                        "with source and target filtering (Terrier)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 

### 2020-08-04 scripts/primary-analyses/03_windowed_crqa.R
Add dataset type for plots

@@ -747,7 +747,7 @@ plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with source and target filtering",
+                       "with source and target filtering (ICEWS)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -999,7 +999,7 @@ plot_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with target-only filtering",
+                       "with target-only filtering (ICEWS)",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_target_windowed_all_RR,

### 2020-08-04 dataset_comparison.Rmd
Fix call for Terrier plots

@@
 # call Terrier plots
-knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/target-windowed_all.png")
-knitr::include_graphics("./results/secondary/phoenix/windowed-crqa/source_target-windowed_all.png")
+knitr::include_graphics("./results/secondary/terrier/windowed-crqa/target-windowed_all.png")
+knitr::include_graphics("./results/secondary/terrier/windowed-crqa/source_target-windowed_all.png")
 

### 2020-11-13 scripts/primary-analyses/01_formatting_data.R
Update cohesion dataset formatting with new code

@@ -15,11 +15,31 @@
 rm(list=ls())
 
 # read in the data 
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+cohesion_df <- read.csv("./data/raw/syria_cohesion.csv")
 ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab", 
                        header = TRUE, sep = "\t", quote = "")
 
 #### 2. Filter and format the time series ####
+
+### prep cohesion data ###
+cohesion_df <- cohesion_df %>%
+  
+  mutate(Start.Year = 2012) %>%
+  
+  mutate(date <- paste(Start.Year, 
+                       Start.Month, 
+                       Start.Day, 
+                       sep="-") 
+         %>% ymd() 
+         %>% as.Date()) %>%
+  
+  rename(full_date=19) %>%
+  
+  group_by(full_date) %>%
+  
+  summarise(
+    n = n(),
+    daily_avg = mean(Cohesion_avg, na.rm=T))
 
 ### filter for source and target ###
 

### 2020-11-13 scripts/primary-analyses/01_formatting_data.R
Update variable name

@@ -26,20 +26,19 @@ cohesion_df <- cohesion_df %>%
   
   mutate(Start.Year = 2012) %>%
   
-  mutate(date <- paste(Start.Year, 
+  mutate(full_date <- paste(Start.Year, 
                        Start.Month, 
                        Start.Day, 
                        sep="-") 
          %>% ymd() 
          %>% as.Date()) %>%
   
-  rename(full_date=19) %>%
+  rename(Date=19) %>%
   
-  group_by(full_date) %>%
+  group_by(Date) %>%
   
-  summarise(
-    n = n(),
-    daily_avg = mean(Cohesion_avg, na.rm=T))
+  summarise(n = n(),
+            MeanCohesion = mean(Cohesion_avg, na.rm=T))
 
 ### filter for source and target ###
 
@@ -154,16 +153,6 @@ ICEWS_formatted_target <- ICEWS_filtered %>%
   # undo grouping by date
   ungroup()
 
-### prepare cohesion dataframe for merging ###
-
-cohesion_df <- cohesion_df %>%
-  
-  # format dates
-  mutate(Date = as.Date(Date)) %>%
-  
-  # only keep variables we need
-  select(Date, MeanCohesion)
-
 ### combine all dataframes ###
 
 # bind the event and social cohesion data frames
@@ -171,7 +160,10 @@ ICEWS_df_formatted <- dplyr::full_join(ICEWS_formatted_source_target,
                                        ICEWS_formatted_target,
                                        by=c("Date")) %>%
   dplyr::full_join(., cohesion_df,
-                   by=c("Date"))
+                   by=c("Date")) %>%
+  
+  # remove 2020_03_30 for incomplete twitter data
+  slice(2:n())
 
 #### 3. Create the deciles for analyses ####
 

### 2020-11-13 scripts/secondary-analyses/phoenix/01_formatting_data.R
Update cohesion processing

@@ -19,10 +19,17 @@
 rm(list=ls())
 
 # read in data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
 phoenix_df <- read.csv("./data/raw/PhoenixBLN-SWB_1979-2019.csv", header = TRUE, sep = ",")
 
 #### 2. Filter and format the time series ####
+
+### drop unnecessary columns and keep cohesion data
+cohesion_df <- cohesion_df %>%
+  
+  select(Date, MeanCohesion, n) %>%
+  
+  mutate(Date = as.Date(Date))
 
 ### filter for source and target ###
 
@@ -144,16 +151,6 @@ phoenix_formatted_target <- phoenix_df_filtered %>%
   # fill NAs with zeros
   replace(is.na(.), 0)
 
-### prepare cohesion dataframe for merging ###
-
-cohesion_df <- cohesion_df %>%
-  
-  # format dates
-  mutate(Date = as.Date(Date)) %>%
-  
-  # only keep variables we need
-  select(Date, MeanCohesion)
-
 ### combine all dataframes ###
 
 # bind the event and social cohesion data frames
@@ -161,7 +158,10 @@ phoenix_df_formatted <- dplyr::full_join(phoenix_formatted_source_target,
                                          phoenix_formatted_target,
                                          by = c("Date")) %>%
   dplyr::full_join(., cohesion_df,
-                   by = c("Date"))
+                   by = c("Date")) %>%
+  
+  # remove 2020_03_30 for incomplete twitter data
+  slice(2:n())
 
 #### 3. Create the sextiles for analyses ####
 

### 2020-11-13 scripts/secondary-analyses/terrier/01_formatting_data.R
Update cohesion processing

@@ -17,7 +17,7 @@
 rm(list=ls())
 
 # read in data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
 terrier_df <- as.data.frame(fread("./data/raw/terrier-no-location-source-complete-2012.json.gz.tsv"))
 
 # assign variable names
@@ -30,6 +30,13 @@ colnames(terrier_df) <- c('code', 'root_code','quad_class', 'goldstein',
                           'doc_id', 'mongo_id')  
 
 #### 2. Filter and format the time series ####
+
+### drop unnecessary columns and keep cohesion data
+cohesion_df <- cohesion_df %>%
+  
+  select(Date, MeanCohesion, n) %>%
+  
+  mutate(Date = as.Date(Date))
 
 ### filter for source and target ###
 
@@ -168,7 +175,10 @@ terrier_df_formatted <- dplyr::full_join(terrier_formatted_source_target,
                                          terrier_formatted_target,
                                          by = c("Date")) %>%
   dplyr::full_join(., cohesion_df,
-                   by = c("Date"))
+                   by = c("Date")) %>%
+  
+  # remove 2020_03_30 for incomplete twitter data
+  slice(2:n())
 
 #### 3. Create the deciles for analyses ####
 

### 2020-11-13 manuscript.Rmd
Update results

@@
 source('./scripts/primary-analyses/01_formatting_data.R')
-source('./scripts/secondary-analyses/icews/01_formatting_data.R')
-source('./scripts/secondary-analyses/phoenix/01_formatting_data.R')
 
@@
 
-num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")
-
-```
-
-The corpus of tweets used included `r sum(num_tweets$n)` Syrian tweets
+#num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")
+
+```
+
+The corpus of tweets used included r sum(num_tweets$n) (ADD TICKS) Syrian tweets
 occurring between March 30--June 15, 2012. Using the Twitter streaming API,
@@
 # read in social cohesion data
-cohesion_df <- read.csv("./data/raw/Syria-social_cohesion.csv")
+cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
 
@@
   geom_line() +
+  #geom_errorbar(aes(ymin=len-ci, ymax=len+ci), colour="black", width=.1, position=pd) +
   xlab("Date") +
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for DET, NRLINE, maxL, and LAM. All other
+a statistical difference from chance for DET, NRLINE, and LAM. All other
 metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
@@
 A permutation test for the CRQA of social cohesion and count of positive events
-found no statistically significant difference from chance for any of the metrics
-other than TT (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
+found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT. All other
+metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
 
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistically significant difference from chance for DET, NRLINE, L,
-ENTR, LAM, and TT. All other metrics did not reach significance (Figure
-\@ref(fig:plot-rp-targ); \autoref{table-1}).
+found a statistically significant difference from chance for maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
 
 [Figure \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]
-
-A qualitative investigation of the recurrence plots suggests a shift in dynamics
-around the 36th observation, which corresponds to May 4th, 2012.
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
+a statistical difference from chance for maxL and LAM. All other metrics
 were non-significant (Figure \@ref(fig:plot-rp-source-targ);
@@
 A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for maxL, ENTR, and LAM (Figure
+found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and LAM (Figure
 \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
@@
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistical difference from chance for DET, NRLINE, and rENTR. All other
+found a statistical difference from chance for rENTR. All other
 metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
@@
 [Figure \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]
-
-Looking qualitatively at the recurrence plots, there again appeared to be a
-shift in dynamics around the 36th observation (May 4th, 2012).
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above-chance RR from the 7th--12th and 32nd--47th window. In addition to some
-one-week peaks at the beginning of the time period, DET was largely above chance
-from the 46th to the 61st window, with some exceptions (Figure
+above-chance RR from the 2nd--12th and 44th--50th window. DET was largely above chance
+from the 47th to the 52nd window, with some exceptions (Figure
 \@ref(fig:plot-wcrqa-targ-all)).
@@
 as the window advances throughout the sample. Interestingly, we see largely
-above-chance RR until the 50th window, with some exceptions during window
-periods 19--30. DET was at or above chance for the 8th--17th, 32nd--33rd, and
-60th windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+above-chance RR until the 18th window, with an exception for window 17.
+A peak also appeared for the 40th--42nd windows.
+DET was intermitently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
 For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 43rd--47th windows. DET was above or nearly
-above chance in the 1st and 2nd windows, with intermittent peaks in later
-windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+above chance from the 4th--7th and 46th--49th windows and was below chance for extneded period from the 56th--62nd window.
+DET bottomed out at zero for the 15th--23rd and 34th--39th windows.
+The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 7th--13th and 26th--47th windows. DET
-also showed above- or nearly above-chance values in windows 7--17 and
-intermittent peaks between the 34th and 61st windows (Figure
+above- or nearly above-chance DET from the 2nd--18th and 44th--52nd windows. DET
+also showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
 \@ref(fig:plot-wcrqa-source-targ-all)).
@@
 For social cohesion and count of positive events, there was a downward trend in
-RR as the window moved, with largely above-chance values in the first 20 windows
-and the 32nd--45th windows. DET stayed largely within chance, with the exception
-of windows 13--19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-For social cohesion and negative events, there was an extended, overlapping
-period of time during which RR (32nd--47th windows) and DET (35th--39th windows)
-were above or nearly above chance (Figure
-\@ref(fig:plot-wcrqa-source-targ-all)). These windows span from May 3rd--14th,
-2012.
+RR as the window moved, with above-chance values in the first 23 windows
+and the 57th--62nd windows. DET stayed largely within chance, with the exception
+of windows 1 and 4 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and negative events, RR was aboce chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows.
+DET showed a upward trend as the windows moved.
+It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows.
+(Figure
+\@ref(fig:plot-wcrqa-source-targ-all)).
 

### 2020-11-13 manuscript.Rmd
Update CRQA discussion

@@
 ### Syria as Target
-The significant result of DET for social cohesion with all and negative events
-supports our first hypothesis that event salience is coupled with online social
-cohesion. The frequency of all and negative events are thus associated with
+The significant result of DET and NRLINE for social cohesion with all events
+supports our first hypothesis that event activity is coupled with online social
+cohesion. The frequency of all events are thus associated with
 greater shared trajectories with social cohesion than would be expected by
-chance. However, when we specifically target positive events, the connection to
-social cohesion fades, providing further support for our second hypothesis.
-Positive events may be less coupled to social cohesion than more salient
-negative events during times of turmoil; by contrast, overall event frequency
-and negative event frequency are coupled with Twitter social cohesion.
+chance.
+This could be due to a conflation of the different kinds of events.
+However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis.
+In addition to the significant DET and NRLINE metrics seen in the all events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
+This may be a reflection of citizens' reaction to events that are positively influential to their cause.
+An act of concession by the government or aid from another country may have led to an increase in moral or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale.
+By contrast, negative event frequency showed weak coupling, counter to our third hypothesis.
+Although the significant reuslt for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time.
+Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter in the following days to report post-hoc what had happened.
+Further text analysis should be conducted to decipher the underlying tone of the tweets.
 
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the dataset increased in size
+By adding Syria as a source in the data filtering, the event dataset increased in size
 by 1,690 samples. These additional observations are times where Syria initiated
 an event with another country. Events initiated by Syria but directed internally
-within the country were already captured by the target-only filtering. The
-increase in coupling between positive events and social cohesion can thus only
-be due to the externally directed events. Though the coupling between social
-cohesion with negative and all events were largely unchanged, positive events
-and social cohesion showed greater stability in their coupling (reflected in
-maxL); while TT was no longer significant in these analyses, LAM (related to TT)
-did reach statistical significance.
-
-While interesting, the underlying meaning or drivers of this change in results
-requires further investigation that incorporates the actual content of the
-tweets themselves. One possible reason (among many) may be that the finding was
-spurious. The positive external events from Syria may have been self-serving,
-aiming to prevent intervention by other countries or to cover up what was
-happening internally. During these moments, the increased cohesion may reflect a
-surge from the Syrian people trying to raise awareness of the situation or to
-decry the Syrian government's attempts to improve their international standing.
-In this case, the increased coupling of positive events would be coupled not
-with shared positive affect in social media but instead to shared negative
-affect in social media in response. However, we cannot test this hypothesis with
-the current time series data; future research should explore the semantic
+within the country were already captured by the target-only filtering.
+Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion.
+There are no longer a signficant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequncy of overall daily events.
+Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social coheison online.
+In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events.
+These two time series showed greater stability in their coupling (reflected in L).
+But the significant ENTR metric suggests that there is more variablity in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events.
+Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR).
+Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.
+
+While interesting, the underlying meaning or drivers of these changes in CRQA results requires further investigation that incorporates the actual content of the tweets themselves.
+One possible reason (among many) may be that the findings were spurious.
+The source events may be covering up the relationship between different kinds of target events and Twitter social cohesion.
+However, we cannot test this hypothesis with the current time series data; future research should explore the semantic
 content of this tweet corpus to determine the nature of the socially cohered

### 2020-11-13 manuscript.Rmd
Fix typos

@@
 This may be a reflection of citizens' reaction to events that are positively influential to their cause.
-An act of concession by the government or aid from another country may have led to an increase in moral or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale.
+An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale.
 By contrast, negative event frequency showed weak coupling, counter to our third hypothesis.
-Although the significant reuslt for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time.
+Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time.
 Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter in the following days to report post-hoc what had happened.
@@
 Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion.
-There are no longer a signficant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequncy of overall daily events.
-Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social coheison online.
+There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events.
+Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social cohesion online.
 In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events.
 These two time series showed greater stability in their coupling (reflected in L).
-But the significant ENTR metric suggests that there is more variablity in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events.
+But the significant ENTR metric suggests that there is more variability in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events.
 Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR).

### 2020-11-13 manuscript.Rmd
Fix typos

@@
 A peak also appeared for the 40th--42nd windows.
-DET was intermitently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+DET was intermittently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
 
 For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 46th--49th windows and was below chance for extneded period from the 56th--62nd window.
+above chance from the 4th--7th and 46th--49th windows and was below chance for extended period from the 56th--62nd window.
 DET bottomed out at zero for the 15th--23rd and 34th--39th windows.
@@
 
-For social cohesion and negative events, RR was aboce chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows.
+For social cohesion and negative events, RR was above chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows.
 DET showed a upward trend as the windows moved.

### 2020-12-22 scripts/primary-analyses/00_tweet_stats.R
Update tweet corpus description script

@@ -5,52 +5,42 @@
 #
 # Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_09_02
+# Last updated: 2020_12_22
 
 #### 1. Set up ####
 
 setwd("./Documents/_github/arab-spring/")
 
+library(data.table)
+library(readxl)
+
 # clear environment
 rm(list=ls())
 
 # read in the data 
-raw_tweets <- data.table::fread("./data/raw/syria_tweets_en.txt", 
-                         header = FALSE, 
-                         sep = "\r", # just read it as one variable for now
-                         stringsAsFactors = FALSE,
-                         encoding='UTF-8')
+raw_tweets <- read_excel("./data/raw/syria_merge.xlsx")
+coh_data <- read.csv("./data/raw/syria_cohesion.csv",
+                     header = TRUE,
+                     sep = ',')
 
-#### 2. Parse data ####
+#### 2. Format date-time ####
 formatted_tweets <- raw_tweets %>%
-
-  # separate into multiple variables
-  separate(V1, c("datestamp","tweet"), sep=",", extra="merge")
-  
-# fix encoding
-Encoding(formatted_tweets$tweet) <- "latin1"
-
-# filter for dates and times
-formatted_tweets <- formatted_tweets %>%
-
-  # remove whitespace from beginning of tweet
-  mutate(tweet = str_trim(tweet)) %>%
   
   # parse day level
-  mutate(date = (stri_extract_first_regex(datestamp, "[0-9]{8}+"))) %>%
+  mutate(date = (stri_extract_first_regex(created_at, "[0-9]{8}+"))) %>%
   
   # convert to date format
   mutate(date = anytime::anydate(date, "%Y%m%d")) %>%
   
   # truncate to date range used
-  filter(date >= as.Date("2012-03-30") 
+  filter(date >= as.Date("2012-03-31") 
          & date <= as.Date("2012-06-15")) %>%
   
   # number of days since new year
   mutate(num_days = yday(date)) %>%
   
   # parse time
-  mutate(time = str_sub(datestamp,9,14)) %>%
+  mutate(time = str_sub(created_at, 10, 15)) %>%
   
   # subset hour
   mutate(hour = as.integer(str_sub(time,1,2))) %>%
@@ -63,17 +53,128 @@ formatted_tweets <- formatted_tweets %>%
   
   # calculate total seconds for later analyses
[…]

### 2020-12-22 manuscript.Rmd
Update corpus stats

@@
     email         : "megan.chiovaro@uconn.edu"
+  - name          : "Leah C. Windsor"
+    affiliation   : "3,*"
+  - name          : "Alistair Windsor"
+    affiliation   : "4"
   - name          : "Alexandra Paxton"
     affiliation   : "1,2,*"
-  - name          : "Leah C. Windsor"
-    affiliation   : "3,*"
 
@@
   - id            : "3"
-    institution   : "University of Memphis"
+    institution   : "Institute for Intelligent Systems, University of Memphis"
+  - id            : "4"
+    institution   : "Department of Mathematical Sciences, University of Memphis"
   - id            : "*"
@@
 
-```{r num-tweets, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
-
-#num_tweets <- read.csv("./data/raw/Syria-social_cohesion.csv")
-
-```
-
-The corpus of tweets used included r sum(num_tweets$n) (ADD TICKS) Syrian tweets
+```{r corpus_stats, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
+
+tweet_stats <- read.csv("./data/formatted/primary/stats.csv")
+
+```
+
+The corpus of tweets used included `r tweet_stats$total_tweets` Syrian tweets
 occurring between March 30--June 15, 2012. Using the Twitter streaming API,
@@
 
-All scripts used for scraping tweets and compressing data can be found at
+The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets and `r tweet_stats$percent_retweets_all`% retweets.
+There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.
+
+Scripts used for scraping tweets and compressing data can be found at
 https://github.com/chbrown/twilight.
@@
 incomplete and incorrectly formatted data. They were then filtered to include
-only events that were directed at (i.e., `target`) Syria ($n = 6300$). To
+only events that were directed at (i.e., `target`) Syria ($n = INSERT NUMBER HERE$). To
 explore the impact of outwardly directed Syrian events, the data were filtered
 again to include events that were both directed at (i.e., `target`) or directed
-by (i.e., `source`) Syria ($n = 7990$).
+by (i.e., `source`) Syria ($n = INSERT NUMBER HERE$).
 

### 2020-12-23 scripts/primary-analyses/00_tweet_stats.R
Update retweet filter

@@ -76,7 +76,7 @@ colnames(stats) <- c("avg_time_to_tweet",
                      "min_daily_tweets",
                      "total_retweets_beginning",
                      "total_retweets_all",
-                     "percent_retweets_all",
+                     "percent_retweets_beginning",
                      "num_users",
                      "total_replies_mentions",
                      "percent_replies_mentions",
@@ -124,10 +124,11 @@ replies_mentions <- formatted_tweets %>%
 # create corpus of original tweets
 original_tweets <- formatted_tweets %>% 
   
-  #filter(!str_detect(text, "^RT")) %>%
+  # tweets where RT appears in the beginning of the text
+  filter(!str_detect(text, "^RT")) %>%
 
   # tweets where RT appears anywhere in the text
-  filter(!str_detect(text, "RT")) %>%
+  #filter(!str_detect(text, "RT")) %>%
 
   # create corpus of replies and mentions
   filter(!str_detect(text, "@[[:alnum:]]"))
@@ -135,7 +136,7 @@ original_tweets <- formatted_tweets %>%
 # count retweets
 stats$total_retweets_beginning <- nrow(retweets_beginning)
 stats$total_retweets_all <- nrow(retweets_all)
-stats$percent_retweets_all <- nrow(retweets_all)/nrow(formatted_tweets)*100
+stats$percent_retweets_beginning <- nrow(retweets_beginning)/nrow(formatted_tweets)*100
 
 # count replies/mentions
 stats$total_replies_mentions <- nrow(replies_mentions)
@@ -177,4 +178,3 @@ write.table(x = stats,
             sep=",",
             col.names=TRUE,
             row.names=FALSE)
-

### 2020-12-23 scripts/primary-analyses/01_formatting_data.R
Update percentages

@@ -78,6 +78,12 @@ ICEWS_filtered <- ICEWS_df %>%
   # filter out invalid intensity values
   filter(Intensity >= -10 & Intensity <= 10)
 
+# look at the event types percentages for source and target
+source_targ_positives <- sum(ICEWS_filtered$Intensity > 0)
+source_targ_positives_perc <- sum(ICEWS_filtered$Intensity > 0)/nrow(ICEWS_filtered)
+source_targ_negatives <- sum(ICEWS_filtered$Intensity < 0)
+source_targ_negatives_perc <- sum(ICEWS_filtered$Intensity < 0)/nrow(ICEWS_filtered)
+
 ### prep the event count time series ###
 
 # create new dataframe with counts of different events
@@ -120,7 +126,16 @@ ICEWS_formatted_source_target <- ICEWS_filtered %>%
 ICEWS_formatted_target <- ICEWS_filtered %>% 
   
   # filter to just target (removing source)
-  filter(grepl("Syria", Target.Country)) %>%
+  filter(grepl("Syria", Target.Country)) 
+
+# look at the event types percentages for source and target
+targ_positives <- sum(ICEWS_formatted_target$Intensity > 0)
+targ_positives_perc <- sum(ICEWS_formatted_target$Intensity > 0)/nrow(ICEWS_formatted_target)
+targ_negatives <- sum(ICEWS_formatted_target$Intensity < 0)
+targ_negatives_perc <- sum(ICEWS_formatted_target$Intensity < 0)/nrow(ICEWS_formatted_target)
+
+# grab observations where target is Syria
+ICEWS_formatted_target <- ICEWS_formatted_target %>%
   
   # group by date
   group_by(Event.Date) %>%

### 2020-12-23 manuscript.Rmd
Update intro pt. 1

@@
 abstract: |
-  In recent years, political activists have taken to social media platforms to
-  rapidly reach broad audiences. Despite the prevalence of micro-blogging in
-  these sociopolitical movements, the degree to which virtual mobilization
-  reflects or drives real-world movements is unclear. Here, we explore the
-  dynamics of real-world events and Twitter social cohesion in Syria during the
-  Arab Spring. Using the nonlinear methods cross-recurrence quantification
-  analysis and windowed cross-recurrence quantification analysis, we investigate
-  if frequency of events of different intensities are coupled with social
-  cohesion found in Syrian tweets. Results indicate that virtual social cohesion
-  is coupled with the counts of all and negative events each day but shows a
-  more nuanced connection to positive events, suggesting that virtual
-  mobilization does reflect real-world movements. We conclude with a discussion
-  of implications and applications of nonlinear methods in political science
-  research.
+  In recent years, political activists have taken to social media platforms to rapidly reach broad audiences.
+Despite the prevalence of micro-blogging in these sociopolitical movements, the degree to which virtual mobilization reflects or drives real-world movements is unclear.
+Here, we explore the dynamics of real-world events and Twitter social cohesion in Syria during the Arab Spring.
+Using the nonlinear methods cross-recurrence quantification analysis and windowed cross-recurrence quantification analysis, we investigate if frequency of events of different intensities are coupled with social cohesion found in Syrian tweets.
+Results indicate that online social cohesion is coupled with the counts of all and negative events each day but shows a more nuanced connection to positive events, suggesting that online mobilization does reflect real-world movements.
+We conclude with a discussion of implications and applications of nonlinear methods in political science research.
   <!-- https://tinyurl.com/ybremelq -->
@@
 classoption       : "man"
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
+#output            : papaja::apa6_pdf
 ---
@@
 
-In December 2010, a Tunisian man named Mohamed Bouazizi was unjustifiably
-stripped of his vendor cart by municipal officials. His humiliation led him to
-set himself on fire in protest to the authoritarian rule, leading to his death
-several days later. His actions served as a catalyst for the Tunisian
-Revolution, and one week after his death, Zine El Abidine Ben Ali---the
-longstanding authoritarian president---fled the country. The events of Tunisia
-rapidly spread to surrounding countries also subject to unjust authoritarian
-rule, including Egypt, Libya, and Syria.
+In December 2010, a Tunisian man named Mohamed Bouazizi died after setting himself on fire to protest the authoritarian government’s unjustifiable confiscation of his vendor cart by municipal officials.
+His actions served as a catalyst for the Tunisian Revolution, which rapidly spread to surrounding countries also subject to unjust authoritarian rule, including Egypt, Libya, and Syria.
 
@@
 turned to social media to coordinate their activism and communicate to the
-world. Between March and June 2012, more than 8 million tweets were sent within
+world. Between March and June 2012, millions of tweets were sent within
 Syria, revealing the details of the conflict suppressed by the government.
+A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in Brownlee (2013) [fix bib] and Lynch (2016) [fix bib].
 
@@
 accessibility and proficiency as an information exchange tool, Twitter has
-provided social and political activists an opportunity to complement or even
-replace real-world social mobilization. During the 2012 Italian protests for
-global economic change, tweeting was determined to be more effective locally in
-discussing real-world, real-time events than traditional mainstream media
-platforms [@vicari2013public]. As people increasingly rely on social media for
-local news and information, we must understand exactly how these micro-blogs
-connect to and reflect real-world action.
+provided social and political activists an opportunity to complement (Greijdanus et al., 2020) [fix bib] and not hinder participation in (Harlow & Harp, 2012; Milošević-Đorđević & Žeželj, 2017) [fix bib] real-world social mobilization.
+During the 2012 Italian protests for global economic change, tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms [@vicari2013public].
+As people increasingly rely on social media for local news and information, we must understand exactly how these micro-blogs connect to and reflect real-world action.
 
@@
 @koehler2017political], but to our knowledge, the direct *coupling* between
-Syrian Twitter cohesion and international action has not been investigated. In
-fact, some have been skeptical about the effect of social media on collective
-action at all [@seay2014slacktivism].
+Syrian Twitter cohesion and international action has not been investigated  (though hashtag usage has been linked to next-day protests; Steinert-Threlkeld et al., 2015) [fix bib].
+In fact, some have been skeptical about the effect of social media on collective action at all [@seay2014slacktivism].
 
@@
 
-Citizens communicate with each other with increased transparency due to the
-ubiquitous availability of social media such as low-cost and egalitarian
-platforms like Twitter. Citizens are able to access these tools via mobile
+Protestors and social activists communicate with each other with increased transparency due to the ubiquitous availability of social media like Twitter.
+Activists are able to access these tools via mobile
 phones and computers with Internet connectivity, providing a stream of real-time
@@
 
-An example of a leader expressing his interest in such public
-conversation is given by Bashar al-Assad in a speech on June 3, 2012:
-
-\setlength{\leftskip}{1cm}
-
-\noindent I know that I have been away from the media for a long time, and I
-have missed having direct contact with the citizens, but I have always been
-following up with the daily occurrences and gathering the information so that my
-speech can be built on what is said by the street.
-
-\setlength{\leftskip}{0pt}
-
-\noindent With few exceptions, Assad chose to keep social media platforms up and
-running. Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart
-the growth of social protest online and in the streets by shutting down the
-Internet. During these times, military repression increases, but government
-information about the citizens decreases. As a result, regimes may elect to
-maintain Internet connectivity to monitor and surveil their citizens.
+With few exceptions, leader Bashar al-Assad chose to keep social media platforms up and running.
+Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth of social protest online and in the streets by shutting down the Internet.
+During these times, military repression increases, but government information about the citizens decreases.
+As a result, regimes may elect to maintain Internet connectivity to monitor and surveil their citizens.
 
@@
 of cohesion between speakers and the alignment between that cohesion and their
-collective political behavior.
+collective political behavior, just as the degree of cohesion among real-world protestors in past movements has been captured in their shared sign messaging (Windsor, 2020) [fix bib].
 
@@
 strong aversion to an individual, event, or political injustice
-[@goldstone1980theories;
-@goldstone2011understanding]. Political resistance offers participants the
+[@goldstone1980theories; @goldstone2011understanding]. Political resistance offers participants the
 opportunity to “lose themselves” and relinquish their individual identity in
@@
 mobilization, which facilitate the development of protest movements in some
-instances and constrain them in others” [@kitschelt1986political]. What emerges
-as strategies and tactics in contentious politics are a function of
+instances and constrain them in others” [@kitschelt1986political]. Emergent strategies and tactics in contentious politics are a function of
 what the system makes possible. This includes the number of people and their
@@
 The source events may be covering up the relationship between different kinds of target events and Twitter social cohesion.
-However, we cannot test this hypothesis with the current time series data; future research should explore the semantic
-content of this tweet corpus to determine the nature of the socially cohered
+However, we cannot test this hypothesis with the current time series data; future research should explore the semantic content of this tweet corpus to determine the nature of the socially cohered
 language.

### 2020-12-23 manuscript.Rmd
Update intro pt. 2

@@
 interdisciplinary approach that incorporates linguistics, psychology, and
-political science using nonlinear dynamical systems methodology to disentangle the
-relationship between language and action.
+political science using nonlinear dynamical systems methodology to disentangle the relationship between language and action.
 
@@
 repeats a previous item, or refers to it through synonymous language
-[@halliday1976cohesion]. In social media, we can conceive of retweets (i.e., reposts
-or forwards of previous messages) as a form of reiteration
-that increase message cohesion. Since retweets replicate verbatim some part of
-another tweet, these tweets would also have higher cohesion. Hashtags function
-similarly and are included in our analysis.
+[@halliday1976cohesion].
+We include retweets (i.e., reposts or forwards of previous messages) because they are a form of reiteration that increases message cohesion.
+They indicate that individuals are “singing to the same tune” by amplifying the original message.
+Since retweets replicate verbatim another tweet (sometimes with the addition of commentary or supplementary messages), these tweets would also have higher cohesion.
 
@@
 ```
+
+We also include hashtags in our analyses.
+Hashtags are a way of identifying similar topics (e.g., people, events, places, themes) across users and across tweets by typing a string of characters preceded by a “#” symbol.
+Users may choose to include as many hashtags (up to the total character limit of the tweet) as they would like, and they may choose to create their own or adopt hashtags from other users or groups.
+The use of the same hashtags would increase cohesion; however, because hashtags are often included or embedded within longer messages, simply using the same hashtags would not be a guarantee of higher cohesion if the rest of the words in the tweets do not overlap.
 
@@
 in-person social mobilization event, alerting a repressive government that
-collective mobilization is happening. Interlocutor cohesion may also respond to
+collective mobilization is happening. It may also respond to
 exogenous events such as spontaneous, unprovoked militarized conflict.
@@
 We expect to see increased linguistic cohesion among people participating in
-online discussions about an idea, event, individual, or movement. Given that
+online discussions about an idea, event, individual, or movement.
+While the overall frequency of social media messages related to the event may increase as a result of the event, their linguistic cohesion helps us understand if denizens are using the platforms in a coordinated way that amplifies their messages or goals and creates a virtual protest space.
+Given that
 Syrian protesters coordinated their activity through Twitter by discussing their
@@
 This study aims to explore the dynamics of Twitter users in Syria, who used the
-social media platform to raise awareness about the Arab Spring and bring about
-mass mobilization.
+social media platform to raise awareness about the Arab Spring and the relationship of those messages to mass mobilization in the real world.
 
@@
 
-This work is a reproducible manuscript. All code and analyses can be found at:
+This work is a reproducible manuscript. Code and analyses can be found at:
 www.github.com/mchiovaro/arab-spring.

### 2020-12-23 manuscript.Rmd
Update methods pt. 1

@@
 The corpus of tweets used included `r tweet_stats$total_tweets` Syrian tweets
-occurring between March 30--June 15, 2012. Using the Twitter streaming API,
+occurring between March 31--June 15, 2012. Using the Twitter streaming API,
 servers at the University of Texas at Austin collected the tweets. The servers
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated by
-quantifying the frequency of shared content words with respect to those words'
-frequencies in the entire tweet corpus. If a linguistic term has a high
-frequency in one tweet but has a low frequency in the whole tweet corpus, then
-it is more likely a content word and is thus given more weight in calculating
-social cohesion. This method is similar to *term frequency-inverse document
-frequency* [tf-idf; see also @jones1972statistical;
-@robertson2004understanding].
-
-The tweets were first sorted into ascending order by timestamp. They were then
-grouped into successive sets of five tweets. Inverse frequency weighting for the
-overlap words and all words was conducted for each pair of two tweets in the
-group of five, then divided to get the social cohesion score for that pair (see
-Eq. 1-3). This resulted in ten social cohesion values for each group of five
-tweets; these values were then averaged to get a social cohesion score for the
-entire set of five tweets. Finally, the mean of all average cohesion values for
-all groups was taken to get a social cohesion score for each day.
+The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
+Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message.
+Stop words, punctuations, and duplicate words were not removed from the tweets.
+
+The tweets were first sorted into ascending order by timestamp.
+They were then grouped into successive sets of five tweets.
+Groups of five were chosen to allow for manageability and efficiency of the analyses.
+Linguistic cohesion was quantified for all possible pairs of tweets in the group of five, resulting in 10 pairs per group of tweets; all 10 cohesion values for the group were averaged for a single group cohesion value.
+The cohesion value for each day was quantified as the average cohesion values for all groups in that day.
+Each pair’s cohesion value was calculated in three parts:
 
@@
 
+Equation 1 identifies the inverse frequency weighting of each overlapping word ti between two tweets d1 and d2, relative to the word’s frequency in the corpus  D, for all overlapping words t1...k between the two tweets.
+
 \begin{align}
@@
 
+Equation 2 then calculates the inverse frequency of each word ti  in tweets d1 and d2, relative to the word’s frequency in the corpus D, for all words t1...n that appear in either tweet.
+
 \begin{align}
@@
 
-\noindent The social cohesion calculation was performed on the tweet corpus
-containing both English and Arabic tweets. All hashtags and URLs were included
-in the analysis. The raw social cohesion time series can be seen in Figure
-\@ref(fig:raw-cohesion-ts).
+Finally, Equation 3 identifies their linguistic cohesion by taking the ratio of the results of Equations 1 and 2.
+Through this process, we are able to naturally account for the frequencies of natural language generally and of online language specifically: Words that occur many times in the corpus (which we can operationalize as function words; e.g., prepositions, pronouns) influence the similarity scores between two tweets much less than words that occur rarely in the corpus (which we can operationalize as content words; e.g., names, hashtags).
+
+This linguistic cohesion metric is similar to *term frequency-inverse document
+frequency* [tf-idf; see also @jones1972statistical;
+@robertson2004understanding].
+However, this method focuses more squarely on terms (i.e., agnostic to the number of documents in the corpus), aggregates at a higher semantic level (i.e., summing across words), and accounts for linguistic novelty relative to the pair and the corpus (i.e., ratio of Eq.
+1 to Eq.
+2).
+The social cohesion calculation was performed on the tweet corpus containing both English and Arabic tweets.
+All hashtags and URLs were included in the analysis.
+The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
 

### 2020-12-23 manuscript.Rmd
Update discussion

@@
 \text{Inverse frequency weighting of overlap words = }\sum_{i=1}^k
-\frac{log(f(t_i, d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+\frac{log(f(t_i, d_1) + f(t_i, d_2) + 1)}{log(f(t_i) + 1)}
 \end{align}
 
-Equation 1 identifies the inverse frequency weighting of each overlapping word ti between two tweets d1 and d2, relative to the word’s frequency in the corpus  D, for all overlapping words t1...k between the two tweets.
+Equation 1 identifies the inverse frequency weighting of each overlapping word ti between two tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all overlapping words t1...k between the two tweets.
 
@@
 \text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i,
-d1) + f(t_i, d2) + 1)}{log(f(t_i) + 1)}
+d_1) + f(t_i, d_2) + 1)}{log(f(t_i) + 1)}
 \end{align}
 
-Equation 2 then calculates the inverse frequency of each word ti  in tweets d1 and d2, relative to the word’s frequency in the corpus D, for all words t1...n that appear in either tweet.
+Equation 2 then calculates the inverse frequency of each word ti  in tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all words t1...n that appear in either tweet.
 
@@
 still preserving a sampling rate that respects the native timescale of the
-system [cf. Nyquist frequency in signal processing; @grenander1959probability].
+system [cf.
+Nyquist frequency in signal processing; @grenander1959probability].
+In other words, a system that changes every day must be sampled more often than a system that changes every year and less often than a system that changes every hour.
+However, to compare two time series with CRQA, the two time series must be sampled at the same frequency as one another.
 Because the social cohesion and event data have different scales and values, we
@@
 
-Using the real deciles of social cohesion, count of all events, count of
+Using the real deciled time series of social cohesion, count of all events, count of
 positive events, and count of negative events, we conducted a series of
@@
 structure and thus a more meaningful interpretation of DET.
+A window size smaller than 14 would limit the possibilities for shared trajectories and make determinism uninterpretable, and window sizes larger than 14 would increasingly overshadow the fine-grain dynamics that we want to investigate.
 
@@
 By adding Syria as a source in the data filtering, the event dataset increased in size
-by 1,690 samples. These additional observations are times where Syria initiated
+by N [fix number here] samples. These additional observations are times where Syria initiated
 an event with another country. Events initiated by Syria but directed internally
@@
 ### Syria as Target
-The time period of differing dynamics noted in the cross-recurrence plots---from
-observation 32 through 47---appears to be captured by the above-chance RR values
-in WCRQA of social cohesion and count of all events (Figure
-\@ref(fig:plot-wcrqa-targ-all)). However, DET for these periods only
-intermittently rises above chance; it more consistently reaches statistical
-significance only at the end of the window through the end of the observation
-period, following a spike in the RR between negative event count and social
-cohesion. During this period, the modal ICEWS event for each day (Figure
+For the RR values in WCRQA of social cohesion and count of all events (Figure
+\@ref(fig:plot-wcrqa-targ-all)), we see both an early and late above-chance peak.
+However, DET for these periods only rises above chance for the later peak.
+During this later period, the modal ICEWS event for each day (Figure
 \@ref(fig:plot-mode-event)) was almost consistently -10, the most violent event
-category. This supports our first hypothesis.
+category. This supports our first hypothesis, that overall online cohesion may reflect the frequency of events occurring on the ground, particularly those that are violent in nature.
 
@@
 
-Surprisingly---and contrary to our second hypothesis---we saw consistent
-coupling between positive event count and social cohesion. Although both had a
-downward trajectory throughout the time period under consideration, RR was at or
-above chance in nearly all windows, and DET showed much more consistent shared
-trajectories than negative events. This may suggest that Syrian Twitter
-community was reacting more cohesively to the positive events aimed at Syria
-from the international community; this interpretation is supported by the
-attenuation of the effect in the analyses that include Syria as both a source
-and a target.
+///
 
 ### Syria as Source and Target
-WCRQA on the source-and-target-filtered data showed similar patterns of RR
-between the count of all events and social cohesion (as observed in the
-target-only data), though the values increased. This suggests that large numbers
-on a given day match increased levels of social cohesion online. However, the
-results for DET changed: While the majority of statistically significant DET
-windows occurred toward the end of the observation period for target-only data
-(creating a positive trendline), the source-and-target data showed a negative
-trendline for DET.
-
-The divergences in the all-event count data for these two datasets underscores
-the differences between RR and DET. As noted earlier, DET captures
-*trajectories*---in this case, similar to the impact of actions and social
-cohesion carrying across time. The same number of points (RR) can fall in
-different patterns (DET), providing important information about the structure of
-the system in question.
-
-WCRQA metrics for positive-only event counts with social cohesion showed similar
-patterns in RR and DET as the target-only data, but the precise values of DET
-and RR were diminished. This may support the ideas suggested in the CRQA
-section, but again, only future work including the *content* of those tweets can
-directly speak to that explanation.
-
-Finally, the coupling between negative-only event counts and social cohesion
-also remained relatively similar but demonstrated some important differences.
-First, we see a greater number of windows at above-chance levels for RR,
-including an interesting spike around window 32 that suggests a negative
-externally focused action taken by Syria prompted a sharp rise in social
-cohesion. (This would not have been captured by the target-only dataset.)
-Second---like with the all-event data---we see different structuring of the data
-through differences in the patterns of DET; above-chance DET only occurrs within
-the middle of the observation period, around a time of increased strife (as
-noted above).
+
+///
 
@@
 the #MeToo movement and for the relationship between social protest and repression
-during the Black Lives Matter protests. Fundamentally, this methodological
-approach can help us better understand the human social mechanisms underlying
+during the Black Lives Matter protests. This methodological
+approach can help us better understand the fundamental human social mechanisms underlying
 social media and its influence on human behavior in real life. Given that many

### 2020-12-26 manuscript.Rmd
Fix typo
Add error bars to daily cohesion plot

@@
 classoption       : "man"
-output            : papaja::apa6_word
-#output            : papaja::apa6_pdf
+#output            : papaja::apa6_word
+output            : papaja::apa6_pdf
 ---
@@
 Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
-[@fink2016complex]. The prevalence and rate of particular hashtags were
+[@fink2016complex]. The prevalence and rate of particular hashtags
 contributed to the overall sociolinguistic cohesion. The more that people
@@
 # read in social cohesion data
-cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
-
-# plot time series
-raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
+#cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
+raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")
+
+# converge date to single variable
+raw_cohesion_data$Start.Year <- "2012"
+raw_cohesion_data$date <- as.Date(with(raw_cohesion_data,
+                                       paste(Start.Year, Start.Month, Start.Day,
+                                            sep="-")), "%Y-%m-%d")
+
+# detach plyr so summarise works
+detach("package:plyr", unload=TRUE)
+
+# calculate mean cohesion
+raw_cohesion_data %>%
+  group_by(date) %>%
+  summarise(
+    MeanCohesion = mean(Cohesion_avg),
+    sd = sd(Cohesion_avg),
+    var = sd^2,
+    n = n(),
+    se = sd / n) %>%
+  ggplot(aes(x = date, y = MeanCohesion)) +
+  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
   geom_point() +
   geom_line() +
-  #geom_errorbar(aes(ymin=len-ci, ymax=len+ci), colour="black", width=.1, position=pd) +
   xlab("Date") +
   ylab("Mean Social Cohesion")
-ggsave("./results/primary/raw-cohesion-ts.png")
 

### 2020-12-26 manuscript.Rmd
Address reviewer comments

@@
 Stop words, punctuations, and duplicate words were not removed from the tweets.
+The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description.
 
@@
 
-```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'Mode ICEWS event per day.'}
+```{r plot-mode-event, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.cap = 'A  plot of the most frequently documented ICEWS event score per day.'}
 

### 2020-12-26 manuscript.Rmd
Address reviewer comments pt. 2

@@
 The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description.
+The presence of bots was not investigated.
+According to a 10-Q report for Twitter, Inc., for a quarterly period in 2014, the estimated number of third party applications automatically contacting the servers (i.e., bots), was less than 8.5% [@twitter2014].
+As the data in this study were collected two years prior, this number was likely even less.
+Thus we consider the number of bots negligible for the present investigation.
 

### 2020-12-26 scripts/primary-analyses/01_formatting_data.R
Fix number of unique surrogate time series

@@ -603,7 +603,7 @@ for (i in 1:1000){
 # check to see if we have 1000 distinct time series
 print(paste0("Total distinct shuffled negative-event time series (target only) for windowed CRQA: ",
              nrow(distinct(shuffled_neg_target))))
-if(nrow(distinct(shuffled_neg_target)) != 1001){
+if(nrow(distinct(shuffled_neg_target)) != 1000){
   print("WARNING: Duplicates in surrogate time series.")
 }
 

### 2020-12-26 scripts/00_tweet_stats.R
Identify retweets

@@ -1,0 +1,89 @@
+######## Tweet Stats ########
+#
+# This script explores statistics of the tweet corpus
+# for the Arab Spring project.
+#
+# Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
+# University of Connecticut
+# Last updated: 2020_09_02
+
+#### 1. Set up ####
+
+# set working directory
+#setwd("./Documents/_github/arab-spring/")
+
+# clear environment
+rm(list=ls())
+
+# load required packages
+library(tidyverse)
+library(stringi)
+library(lubridate)
+library(data.table)
+library(bit64)
+
+# read in the data 
+raw_tweets <- data.table::fread("./data/raw/syria_tweets_en.txt", 
+                         header = FALSE, 
+                         sep = "\r", # just read it as one variable for now
+                         stringsAsFactors = FALSE,
+                         encoding='UTF-8')
+
+#### 2. Parse data ####
+formatted_tweets <- raw_tweets %>%
+  
+  # separate into multiple variables
+  separate(V1, c("datestamp","tweet"), sep=",", extra="merge")
+  
+# fix encoding
+Encoding(formatted_tweets$tweet) <- "latin1"
+
+# filter for dates and times
+formatted_tweets <- formatted_tweets %>%
+
+  # remove whitespace from beginning of tweet
+  mutate(tweet = str_trim(tweet)) %>%
+  
+  # parse day level
+  mutate(date = (stri_extract_first_regex(datestamp, "[0-9]{8}+"))) %>%
+  
+  # convert to date format
+  mutate(date = anytime::anydate(date, "%Y%m%d")) %>%
+  
+  # truncate to date range used
+  dplyr::filter(date >= as.Date("2012-03-30") 
+                & date <= as.Date("2012-06-15")) %>%
+  
+  # number of days since new year
+  mutate(num_days = yday(date)) %>%
+  
+  # parse time
+  mutate(time = str_sub(datestamp,9,14)) %>%
+  
+  # subset hour
+  mutate(hour = as.integer(str_sub(time,1,2))) %>%
+  
+  # subset minutes
+  mutate(minute = as.integer(str_sub(time,3,4))) %>%
+  
+  # subset seconds
+  mutate(seconds = as.integer(str_sub(time,5,6))) %>%
+  
+  # calculate total seconds for later analyses
[…]

### 2020-12-26 manuscript.Rmd

@@
 Syria, revealing the details of the conflict suppressed by the government.
-A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in Brownlee (2013) [fix bib] and Lynch (2016) [fix bib].
+A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016ne].
 
@@
 accessibility and proficiency as an information exchange tool, Twitter has
-provided social and political activists an opportunity to complement (Greijdanus et al., 2020) [fix bib] and not hinder participation in (Harlow & Harp, 2012; Milošević-Đorđević & Žeželj, 2017) [fix bib] real-world social mobilization.
+provided social and political activists an opportunity to complement [@greijdanus2020psychology] and not hinder participation in [@harlow2012collective; @milovsevic2017civic] real-world social mobilization.
 During the 2012 Italian protests for global economic change, tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms [@vicari2013public].
@@
 @koehler2017political], but to our knowledge, the direct *coupling* between
-Syrian Twitter cohesion and international action has not been investigated  (though hashtag usage has been linked to next-day protests; Steinert-Threlkeld et al., 2015) [fix bib].
+Syrian Twitter cohesion and international action has not been investigated  (though hashtag usage has been linked to next-day protests; @steinert2015online).
 In fact, some have been skeptical about the effect of social media on collective action at all [@seay2014slacktivism].
@@
 of cohesion between speakers and the alignment between that cohesion and their
-collective political behavior, just as the degree of cohesion among real-world protestors in past movements has been captured in their shared sign messaging (Windsor, 2020) [fix bib].
+collective political behavior, just as the degree of cohesion among real-world protestors in past movements has been captured in their shared sign messaging [@Windsor2020].
 

### 2020-12-26 scripts/primary-analyses/00_tweet_stats.R
Update RT detection

@@ -109,9 +109,9 @@ stats$min_daily_tweets <- min(daily_stats$daily_tweets)
 stats$total_tweets <- nrow(formatted_tweets)
 hist(daily_stats$daily_tweets)
 
-# tweets where RT appears in the beginning of the text
+# tweets where RT appears not in the middle of a word
 retweets_beginning <- formatted_tweets %>% 
-  filter(str_detect(text, "^RT"))
+  dplyr::filter(str_detect(tweet,"^@"))
   
 # tweets where RT appears anywhere in the text
 retweets_all <- formatted_tweets %>% 

### 2020-12-26 scripts/primary-analyses/00_tweet_stats.R
Silence setwd by default

@@ -9,7 +9,7 @@
 
 #### 1. Set up ####
 
-setwd("./Documents/_github/arab-spring/")
+#setwd("./Documents/_github/arab-spring/")
 
 library(data.table)
 library(readxl)

### 2020-12-26 scripts/primary-analyses/00_tweet_stats.R
Add new RT filter

@@ -109,12 +109,16 @@ stats$min_daily_tweets <- min(daily_stats$daily_tweets)
 stats$total_tweets <- nrow(formatted_tweets)
 hist(daily_stats$daily_tweets)
 
-# tweets where RT appears not in the middle of a word
-retweets_beginning <- formatted_tweets %>% 
-  dplyr::filter(str_detect(tweet,"^@"))
-  
+# filter for retweets
+retweets = formatted_tweets %>%
+  dplyr::filter(str_detect(text, "\\WRT\\W"))
+
+# # tweets where RT appears not in the middle of a word
+retweets_beginning <- formatted_tweets %>%
+  dplyr::filter(str_detect(text,"^RT"))
+
 # tweets where RT appears anywhere in the text
-retweets_all <- formatted_tweets %>% 
+retweets_all <- formatted_tweets %>%
   filter(str_detect(text, "RT"))
 
 # create corpus of replies and mentions
@@ -124,11 +128,14 @@ replies_mentions <- formatted_tweets %>%
 # create corpus of original tweets
 original_tweets <- formatted_tweets %>% 
   
+  # remove RTs
+  filter(!str_detect(text, "\\WRT\\W"))
+
   # tweets where RT appears in the beginning of the text
-  filter(!str_detect(text, "^RT")) %>%
+  # filter(!str_detect(text, "^RT")) %>%
 
   # tweets where RT appears anywhere in the text
-  #filter(!str_detect(text, "RT")) %>%
+  # filter(!str_detect(text, "RT")) %>%
 
   # create corpus of replies and mentions
   filter(!str_detect(text, "@[[:alnum:]]"))

### 2020-12-26 scripts/primary-analyses/00_tweet_stats.R
Try more efficient ways of counting retweets and replies

@@ -109,17 +109,25 @@ stats$min_daily_tweets <- min(daily_stats$daily_tweets)
 stats$total_tweets <- nrow(formatted_tweets)
 hist(daily_stats$daily_tweets)
 
-# tweets where RT appears not in the middle of a word
-retweets_beginning <- formatted_tweets %>% 
-  dplyr::filter(str_detect(tweet,"^@"))
-  
-# tweets where RT appears anywhere in the text
-retweets_all <- formatted_tweets %>% 
-  filter(str_detect(text, "RT"))
+# identify retweets
+retweets_alt = formatted_tweets %>%
+  dplyr::filter(!is.na(retweet_id))
 
-# create corpus of replies and mentions
-replies_mentions <- formatted_tweets %>% 
-  filter(str_detect(text, "@[[:alnum:]]"))
+# identify mentions
+replies_alt = formatted_tweets %>%
+  dplyr::filter(!is.na(in_reply_to_screen_name))
+
+# # tweets where RT appears not in the middle of a word
+# retweets_beginning <- formatted_tweets %>% 
+#   dplyr::filter(str_detect(tweet,"^@"))
+#   
+# # tweets where RT appears anywhere in the text
+# retweets_all <- formatted_tweets %>% 
+#   filter(str_detect(text, "RT"))
+
+# # create corpus of replies and mentions
+# replies_mentions <- formatted_tweets %>% 
+#   filter(str_detect(text, "@[[:alnum:]]"))
 
 # create corpus of original tweets
 original_tweets <- formatted_tweets %>% 

### 2020-12-26 scripts/primary-analyses/00_tweet_stats.R
Add cleaner way of removing retweets and replies

@@ -113,9 +113,15 @@ hist(daily_stats$daily_tweets)
 retweets_alt = formatted_tweets %>%
   dplyr::filter(!is.na(retweet_id))
 
-# identify mentions
+# identify replies
 replies_alt = formatted_tweets %>%
   dplyr::filter(!is.na(in_reply_to_screen_name))
+
+# identify original tweets by stripping out retweets and replies
+original_tweets_alt = anti_join(formatted_tweets,
+                                replies_alt) %>%
+  anti_join(., 
+            retweets_alt)
 
 # # tweets where RT appears not in the middle of a word
 # retweets_beginning <- formatted_tweets %>% 
@@ -129,21 +135,21 @@ replies_alt = formatted_tweets %>%
 # replies_mentions <- formatted_tweets %>% 
 #   filter(str_detect(text, "@[[:alnum:]]"))
 
-# create corpus of original tweets
-original_tweets <- formatted_tweets %>% 
-  
-  # remove RTs
-  filter(!str_detect(text, "\\WRT\\W"))
+# # create corpus of original tweets
+# original_tweets <- formatted_tweets %>% 
+#   
+#   # remove RTs
+#   filter(!str_detect(text, "\\WRT\\W"))
+# 
+#   # tweets where RT appears in the beginning of the text
+#   # filter(!str_detect(text, "^RT")) %>%
+# 
+#   # tweets where RT appears anywhere in the text
+#   # filter(!str_detect(text, "RT")) %>%
+# 
+#   # create corpus of replies and mentions
+#   filter(!str_detect(text, "@[[:alnum:]]"))
 
-  # tweets where RT appears in the beginning of the text
-  # filter(!str_detect(text, "^RT")) %>%
-
-  # tweets where RT appears anywhere in the text
-  # filter(!str_detect(text, "RT")) %>%
-
-  # create corpus of replies and mentions
-  filter(!str_detect(text, "@[[:alnum:]]"))
-  
 # count retweets
 stats$total_retweets_beginning <- nrow(retweets_beginning)
 stats$total_retweets_all <- nrow(retweets_all)

### 2020-12-27 manuscript.Rmd
Fix references and update replies call

@@
 Syria, revealing the details of the conflict suppressed by the government.
-A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016ne].
+A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016new].
 
@@
 
-The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets and `r tweet_stats$percent_retweets_all`% retweets.
+The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets, `r tweet_stats$percent_retweets`% retweets, and `r tweet_stats$percent_replies`% replies.
 There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.
@@
 # detach plyr so summarise works
-detach("package:plyr", unload=TRUE)
+#detach("package:plyr", unload=TRUE)
 

### 2020-12-27 scripts/primary-analyses/00_tweet_stats.R
Fix tweet stats script with final method

@@ -66,7 +66,7 @@ formatted_tweets <- raw_tweets %>%
 hist(formatted_tweets$time_to_tweet, xlim=c(0, 55))
 
 # get empty data frame
-stats = data.frame(matrix(NA, ncol=15))
+stats = data.frame(matrix(NA, ncol=14))
 colnames(stats) <- c("avg_time_to_tweet",
                      "max_time_to_tweet",
                      "min_time_to_tweet",
@@ -74,12 +74,11 @@ colnames(stats) <- c("avg_time_to_tweet",
                      "avg_daily_tweets", 
                      "max_daily_tweets", 
                      "min_daily_tweets",
-                     "total_retweets_beginning",
-                     "total_retweets_all",
-                     "percent_retweets_beginning",
+                     "retweets",
+                     "percent_retweets",
                      "num_users",
-                     "total_replies_mentions",
-                     "percent_replies_mentions",
+                     "total_replies",
+                     "percent_replies",
                      "percent_original_tweets",
                      "total_original_tweets")
 
@@ -110,58 +109,33 @@ stats$total_tweets <- nrow(formatted_tweets)
 hist(daily_stats$daily_tweets)
 
 # identify retweets
-retweets_alt = formatted_tweets %>%
+retweets = formatted_tweets %>%
   dplyr::filter(!is.na(retweet_id))
 
 # identify replies
-replies_alt = formatted_tweets %>%
+replies = formatted_tweets %>%
   dplyr::filter(!is.na(in_reply_to_screen_name))
 
 # identify original tweets by stripping out retweets and replies
-original_tweets_alt = anti_join(formatted_tweets,
+original_tweets = anti_join(formatted_tweets,
                                 replies_alt) %>%
   anti_join(., 
             retweets_alt)
 
-# # tweets where RT appears not in the middle of a word
-# retweets_beginning <- formatted_tweets %>% 
-#   dplyr::filter(str_detect(tweet,"^@"))
-#   
-# # tweets where RT appears anywhere in the text
-# retweets_all <- formatted_tweets %>% 
-#   filter(str_detect(text, "RT"))
-
-# # create corpus of replies and mentions
-# replies_mentions <- formatted_tweets %>% 
-#   filter(str_detect(text, "@[[:alnum:]]"))
-
-# # create corpus of original tweets
[…]

### 2020-12-27 manuscript.Rmd
Add automatic calls for numbers of observations

@@
 source('./scripts/primary-analyses/01_formatting_data.R')
+
+num_target <- sum(ICEWS_formatted_target$all_events_target)
+num_source_target <- sum(ICEWS_formatted_source_target$all_events_source_target)
 
@@
 
-For both the target-only and the target and source data described above, time
+For both the target-only (n = `r num_target`) and the target and source data (n = `r num_source_target`) described above, time
 series of the count of all events were generated by summing the total number of
@@
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the event dataset increased in size
-by N [fix number here] samples. These additional observations are times where Syria initiated
+By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
 an event with another country. Events initiated by Syria but directed internally

### 2020-12-28 manuscript.Rmd
Add Alex's edits

@@
 social movements were reflected in their cohesive placards and posters. For
-example, the pervasive “I am a man” posters during the 1968 sanitation workers'
+example, the pervasive “I am a man” posters during the 1968 Memphis sanitation workers'
 strike reflected their internal cohesion and unified, goal-oriented movement
@@
 Amid the cacophony of messages during political upheaval---such
-as the Arab Spring---consistent themes emerge through hashtags, retweets, and
+as the Arab Spring of the early 2010s---consistent themes emerge through hashtags, retweets, and
 the repeated mentions of concepts such as regime, demonstration, and
-human rights. The cohesiveness of these themes (i.e., whether movement
-participants are metaphorically singing in one voice) reflects the real-world
-events happening contemporaneously with collective action in social movements or
-civil conflicts.
+human rights.
+The cohesiveness of these themes (i.e., the degree to which participants in the movement are metaphorically singing in one voice) reflects the real-world events happening contemporaneously with collective action in social movements or civil conflicts.
 
 In the present research, we investigate the relationship between linguistic
-cohesion and social cohesion in times of social conflict and unrest. We tackle a
-question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does
-social media reflect on-the-ground realities during times of social conflict? To
-do so, we examine patterns of linguistic cohesion on Twitter and their
-connection to real-world events during the Arab Spring uprising in Syria between
-March and June 2012.
+cohesion and social cohesion in times of social conflict and unrest.
+We tackle a question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does social media reflect on-the-ground realities during times of social conflict?
+To do so, we examine patterns of linguistic cohesion on Twitter and their connection to real-world events during the Arab Spring uprising in Syria between March and June 2012.
 
@@
 Political and social cohesion in the world can be modeled using event data which
-encodes who does what to whom on a given day. CAMEO (Conflict and Mediation
-Event Observations) encode a set of activities with numerical values, rescaled
+encodes who does what to whom on a given day. The CAMEO (Conflict and Mediation
+Event Observations) coding scheme encodes a set of activities with numerical values, rescaled
 to reflect a conflict-cooperation scale [@schrodt2006twenty;
-@goldstein1992conflict]. These event codes include a range of behaviors, from
-making public statements and appeals, to demanding, threatening, protesting, and
+@goldstein1992conflict]. These event codes include a range of behaviors of varying intensities and valences, from
+making public statements and appeals to demanding, threatening, protesting, and
 using unconventional mass violence.
@@
 driven by one another. From a dynamical systems perspective, online social
-cohesion and in-person action can be considered two complementary components of
-a single system, mutually constrained and constantly interacting and influencing
-one another [@mahner1997foundations]. Investigation of the coupling of
+cohesion and in-person action can be considered two complementary components of a single system--constantly constrained by, interacting with, and influencing one another [@mahner1997foundations].
+Investigation of the coupling of
 real-world mobilization and social cohesion could provide new insight into the
@@
 conceptualize the physical and virtual movements as a dynamical system, both
-constantly interacting and influencing the other. We aim to study this by
+constantly interacting with and influencing the other. We aim to study this by
 analyzing the real-world events and online social cohesion during nearly three
@@
 
-The corpus of tweets used included `r tweet_stats$total_tweets` Syrian tweets
+The corpus of tweets used included `r tweet_stats$total_tweets` English-language Syrian tweets
 occurring between March 31--June 15, 2012. Using the Twitter streaming API,
@@
 authentication (OAuth was optional, at the time) at
-https://stream.twitter.com/1.1/statuses/filter.json, and stored the data
+https://stream.twitter.com/1.1/statuses/filter.json and stored the data
 directly to the local hard disk. The tweets were then post-processed with a
@@
 The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets, `r tweet_stats$percent_retweets`% retweets, and `r tweet_stats$percent_replies`% replies.
-There were `r tweet_stats$num_users` users in the corpus, and an average of `r tweet_stats$avg_daily_tweets` tweets per day.
+There were `r tweet_stats$num_users` users in the corpus and an average of `r tweet_stats$avg_daily_tweets` tweets per day.
 
@@
 @robertson2004understanding].
-However, this method focuses more squarely on terms (i.e., agnostic to the number of documents in the corpus), aggregates at a higher semantic level (i.e., summing across words), and accounts for linguistic novelty relative to the pair and the corpus (i.e., ratio of Eq.
+However, the method focuses more squarely on terms (i.e., agnostic to the number of documents in the corpus), aggregates at a higher semantic level (i.e., summing across words), and accounts for linguistic novelty relative to the pair and the corpus (i.e., ratio of Eq.
 1 to Eq.
 2).
-The social cohesion calculation was performed on the tweet corpus containing both English and Arabic tweets.
+The social cohesion calculation was performed on the tweet corpus containing English tweets.
 All hashtags and URLs were included in the analysis.
@@
 ### Cross-Recurrence Quantification Analysis
-We first used cross-recurrence quantification analysis [CRQA;
+We first used categorical cross-recurrence quantification analysis [CRQA;
 @zbilut1998detecting] to investigate the temporal patterns of social cohesion
-and real-world events in Syria during Arab Spring. CRQA is an extension of RQA,
-which captures the patterns of revisited states of a single time series
+and real-world events in Syria during Arab Spring. CRQA is an extension of RQA, which captures the patterns of revisited states of a single time series
 [@zbilut1992embeddings; @webber1994dynamical]. CRQA allows for two time series
 to be projected onto one another to investigate shared states and trajectories.
-In CRQA, we track these shared states by identifying *recurrent points*, or
-intersections of time during which two signals shared or revisited the same
-state. These shared states can be at the same time or at later points in the
-time series. We can further chart shared trajectories by examining the
+In CRQA, we track these shared states by identifying *recurrent points*, or intersections of time during which two signals shared or revisited the same state.
+These shared states can be at the same time or at later points in the time series.
+We can further chart shared trajectories by examining the
 occurrences and patterns of multiple sequential recurrent points.
 
-To perform CRQA, the time series must be converted to the same scale, while
+To perform categorical CRQA, the time series must be converted to the same scale, while
 still preserving a sampling rate that respects the native timescale of the
@@
 a cross-recurrence plot, two time series are plotted against each other on the
-$x$ and $y$ axes. At every point where they share the same state, a point in
+$x$ and $y$ axes. At every point where they share the same state, a point is
 placed on the plot to indicate recurrence. (For categorical CRQA, this process
@@
 We can visually analyze these plots to reveal patterns of structure and
-recurrence. The line $y = x$ is known as the *line of identity*. This line falls
-where the time series match temporally. A filled line would indicate perfect
-in-phase synchrony between the two time series. See Figures
+recurrence.
+The main diagonal line on the plot is known as the *line of synchrony*.
+This line falls where the time series match temporally.
+A completely filled main diagonal line would indicate perfect in-phase synchrony between the two time series.
+See Figures
 \@ref(fig:plot-rp-targ)-\@ref(fig:plot-rp-source-targ) for examples of
@@
 The percentage of recurrent points to total possible points is a metric called
-the *recurrence rate* (*RR*). This metrics gives a general description of how
+the *recurrence rate* (*RR*). This metric gives a general description of how
 frequently the time series are sharing the same states. In the current study, a
@@
 points along the line of identity. For more details on the CRQA parameters and
-how they impact the analysis, see @R-crqa.
+how they impact analyses, see @R-crqa.
 
@@
 experimentally derived datasets, it can pose a barrier to researchers using
-small-$n$ data or conducting data-informed case studies.
+smaller datasets or conducting data-informed case studies.
 
@@
 chance was set at the 95th and 99th percentiles of the metrics from the permuted
-CRQ analyses. Given that a permutation test is similar to bootstrapping but does
-not include replacement, all points were included in each CRQA analysis, leaving
-RR constant across all permutations. Thus, RR is not included in the inferential
-tests.
+CRQ analyses.
+Given that a permutation test is similar to bootstrapping but does not include replacement, all real recurrent points were included in each CRQA analysis, leaving RR constant across all permutations.
+Thus, RR is not included in the inferential stests.
 
@@
 “window” of time points is used to calculate CRQA and capture more fine-grained
-dynamics of two time series. The window remains the same size and “slides”
-diagonally up the line of identity. The changes in the CRQA metrics across the
+dynamics of two time series. The window remains the same size and “slides” diagonally up the line of synchrony. The changes in the CRQA metrics across the
 windows can reveal changes in dynamics that can then be linked to external,
@@
 For social cohesion and negative events, RR was above chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows.
-DET showed a upward trend as the windows moved.
+DET showed an upward trend as the windows moved.
 It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows.
@@
 exogenous political events. This work stands alongside the model of
-Palestinian-Israeli social media and events developed by @zeitzoff2017social, and
+Palestinian-Israeli social media and events developed by @zeitzoff2017social and
 the role of peripheral participants in the Syrian Arab Spring movement by
-@steinert2017spontaneous. By introducing the CRQA and WCRQA methods, we
+@steinert2017spontaneous. By introducing CRQA and WCRQA to political science as time series analysis methods, we
 demonstrate how language and social mobilization interact with events along the
 conflict-cooperation continuum in Syria. We have introduced a novel theoretical
-framework of sociolinguistic cohesion which we operationalize using a weighted
-measure of lexical relationships. Using nonlinear dynamical time series
+framework of sociolinguistic cohesion, which we operationalize using a weighted
+measure of lexical relationships among social media posts. Using nonlinear dynamical time series
 analyses, we investigated the theory that virtual mobilization is increasingly
@@
 However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis.
-In addition to the significant DET and NRLINE metrics seen in the all events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
-This may be a reflection of citizens' reaction to events that are positively influential to their cause.
+In addition to the significant DET and NRLINE metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
+This may be a reflection of citizens' reaction to events that align with their cause.
 An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale.
 By contrast, negative event frequency showed weak coupling, counter to our third hypothesis.
-Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, but that negative events were less coupled for the other points in time.
-Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter in the following days to report post-hoc what had happened.
+Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, although negative events were less coupled for the other points in time.
+Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter to report and rally together.
 Further text analysis should be conducted to decipher the underlying tone of the tweets.
@@
 There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events.
-Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social cohesion online.
+Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online.
 In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events.
 These two time series showed greater stability in their coupling (reflected in L).
-But the significant ENTR metric suggests that there is more variability in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events.
-Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR).
+However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events.
+Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR).
 Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.

### 2020-12-28 manuscript.Rmd
Add Alex's edits pt. 2

@@
 Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR).
-Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.
+Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.
 
@@
 Nonlinear methods have been transformative for a variety of research areas
-[including psychology, @coco2014cross]. One of the goals of the present work was
+[including psychology; @coco2014cross]. One of the goals of the present work was
 to introduce variants of one kind of nonlinear method---specifically, recurrence
@@
 
-This methodology should be of great interest to social scientists investigating
+This methodology should be of great interest to interdisciplinary scientists investigating
 social mobilization. It has potential applications for gender studies and

### 2020-12-28 manuscript.Rmd
Fix image rendering and update event counts

@@
 classoption       : "man"
-#output            : papaja::apa6_word
-output            : papaja::apa6_pdf
+output            : papaja::apa6_word
+#output            : papaja::apa6_pdf
 ---
@@
 incomplete and incorrectly formatted data. They were then filtered to include
-only events that were directed at (i.e., `target`) Syria ($n = INSERT NUMBER HERE$). To
+only events that were directed at (i.e., `target`) Syria (n = `r num_target`). To
 explore the impact of outwardly directed Syrian events, the data were filtered
 again to include events that were both directed at (i.e., `target`) or directed
-by (i.e., `source`) Syria ($n = INSERT NUMBER HERE$).
+by (i.e., `source`) Syria (n = `r num_source_target`).
 
@@
 # read in social cohesion data
-#cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
 raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")
@@
 # calculate mean cohesion
-raw_cohesion_data %>%
+raw_cohesion_ts <- raw_cohesion_data %>%
   group_by(date) %>%
@@
   ylab("Mean Social Cohesion")
+
+# save the plot
+ggsave("./results/primary/raw-cohesion-ts.png")
 
@@
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
+By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target - num_target` samples. These additional observations are times where Syria initiated
 an event with another country. Events initiated by Syria but directed internally

### 2020-12-28 manuscript.Rmd
Remove other event counts

@@
 
-For both the target-only (n = `r num_target`) and the target and source data (n = `r num_source_target`) described above, time
+For both the target-only and the target and source data described above, time
 series of the count of all events were generated by summing the total number of

### 2020-12-28 manuscript.Rmd
Add page number for quote

@@
 mobilization, which facilitate the development of protest movements in some
-instances and constrain them in others” [@kitschelt1986political]. Emergent strategies and tactics in contentious politics are a function of
+instances and constrain them in others” [@kitschelt1986political, p. 58]. Emergent strategies and tactics in contentious politics are a function of
 what the system makes possible. This includes the number of people and their

### 2020-12-29 manuscript.Rmd
Add table legends and fix subscripts

@@
 
-Equation 1 identifies the inverse frequency weighting of each overlapping word ti between two tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all overlapping words t1...k between the two tweets.
+Equation 1 identifies the inverse frequency weighting of each overlapping word $t_i$ between two tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all overlapping words $t_{1...k}$ between the two tweets.
 
@@
 
-Equation 2 then calculates the inverse frequency of each word ti  in tweets d_1 and d_2, relative to the word’s frequency in the corpus D, for all words t1...n that appear in either tweet.
+Equation 2 then calculates the inverse frequency of each word $t_i$  in tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all words $t{1...n}$ that appear in either tweet.
 
@@
 Given that a permutation test is similar to bootstrapping but does not include replacement, all real recurrent points were included in each CRQA analysis, leaving RR constant across all permutations.
-Thus, RR is not included in the inferential stests.
+Thus, RR is not included in the inferential tests.
 
@@
 # build table
-pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.")
+pander(target_results, caption = "\\label{table-1}CRQA results for target-only data.\n. p < .10, * p < .05, ** p < .001")
 
@@
 # build table
-pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.")
+pander(source_target_results, caption = "\\label{table-2}CRQA results for source and target data.\n. p < .10, * p < .05, ** p < .001")
 
@@
 This may be a reflection of citizens' reaction to events that align with their cause.
-An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to an uproar on Twitter in an attempt to boost morale.
+An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to a groundswell of support on Twitter in an attempt to boost morale.
 By contrast, negative event frequency showed weak coupling, counter to our third hypothesis.

### 2020-12-29 scripts/primary-analyses/00_tweet_stats.R
Update file names

@@ -18,8 +18,10 @@ library(readxl)
 rm(list=ls())
 
 # read in the data 
-raw_tweets <- read_excel("./data/raw/syria_merge.xlsx")
-coh_data <- read.csv("./data/raw/syria_cohesion.csv",
+raw_tweets <- read.csv("./data/raw/syria_merge_sort.csv",
+                       header = TRUE,
+                       sep = ',')
+coh_data <- read.csv("./data/raw/syria_coherence_sort_5.csv",
                      header = TRUE,
                      sep = ',')
 

### 2020-12-29 scripts/primary-analyses/01_formatting_data.R
Update file name

@@ -15,14 +15,14 @@
 rm(list=ls())
 
 # read in the data 
-cohesion_df <- read.csv("./data/raw/syria_cohesion.csv")
+cohesion_df_original <- read.csv("./data/raw/syria_coherence_sort_5.csv")
 ICEWS_df <- read.delim("./data/raw/events.2012.20150313084811.tab", 
                        header = TRUE, sep = "\t", quote = "")
 
 #### 2. Filter and format the time series ####
 
 ### prep cohesion data ###
-cohesion_df <- cohesion_df %>%
+cohesion_df <- cohesion_df_original %>%
   
   mutate(Start.Year = 2012) %>%
   
@@ -38,7 +38,7 @@ cohesion_df <- cohesion_df %>%
   group_by(Date) %>%
   
   summarise(n = n(),
-            MeanCohesion = mean(Cohesion_avg, na.rm=T))
+            MeanCohesion = mean(Cohesion..avg., na.rm=T))
 
 ### filter for source and target ###
 

### 2020-12-29 manuscript.Rmd
Change filenames and add small revision

@@
 # read in social cohesion data
-raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")
+raw_cohesion_data <- read.csv("./data/raw/syria_coherence_sort_5.csv")
 
@@
   summarise(
-    MeanCohesion = mean(Cohesion_avg),
-    sd = sd(Cohesion_avg),
+    MeanCohesion = mean(Cohesion..avg.),
+    sd = sd(Cohesion..avg.),
     var = sd^2,
@@
 consecutive recurrent points. The Theiler window was set to $0$ to include
-points along the line of identity. For more details on the CRQA parameters and
+points along the line of synchrony. For more details on the CRQA parameters and
 how they impact analyses, see @R-crqa.
@@
 The second parameter to be chosen is a *window step size*. Window step size is
-how far the window moves up the line of identity before conducting CRQA again.
+how far the window moves up the line of synchrony before conducting CRQA again.
 We chose $1$ for the step size to understand how the metrics evolve from day to

### 2020-12-29 manuscript.Rmd
Update CRQA results

@@
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistically significant difference from chance for maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
+found a statistically significant difference from chance for DET, NRLINE, and maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for maxL and LAM. All other metrics
+a statistical difference from chance for DET, maxL, and LAM. All other metrics
 were non-significant (Figure \@ref(fig:plot-rp-source-targ);
@@
 A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for DET, NRLINE, maxL, L, ENTR, and LAM (Figure
+found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM (Figure
 \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
@@
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistical difference from chance for rENTR. All other
-metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
+found no statistical difference from chance for and metrics (Figure \@ref(fig:plot-rp-source-targ);
 \autoref{table-2}).

### 2020-12-29 manuscript.Rmd
Update WCRQA results

@@
 For social cohesion and count of all events, there was a consistent period of
-above-chance RR from the 2nd--12th and 44th--50th window. DET was largely above chance
-from the 47th to the 52nd window, with some exceptions (Figure
+at or above-chance RR from the 3rd--12th and 44th--50th window. DET was largely above chance
+from the 47th to the 54th window, with some exceptions (Figure
 \@ref(fig:plot-wcrqa-targ-all)).
@@
 as the window advances throughout the sample. Interestingly, we see largely
-above-chance RR until the 18th window, with an exception for window 17.
+above-chance RR until the 16th window, with an exception for window 1.
 A peak also appeared for the 40th--42nd windows.
@@
 For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 4th--7th and 46th--49th windows and was below chance for extended period from the 56th--62nd window.
-DET bottomed out at zero for the 15th--23rd and 34th--39th windows.
+above chance from the 5th--6th and 46th--49th windows and was below chance for an extended period from the 56th--62nd window.
+DET bottomed out at zero for the 15th--23rd windows.
 The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance DET from the 2nd--18th and 44th--52nd windows. DET
-also showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
+above- or nearly above-chance RR in the first 23 windows and the 44th--52nd windows.
+RR was consistently below chance for the 29th--39th windows.
+DET showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
 \@ref(fig:plot-wcrqa-source-targ-all)).
@@
 For social cohesion and count of positive events, there was a downward trend in
-RR as the window moved, with above-chance values in the first 23 windows
-and the 57th--62nd windows. DET stayed largely within chance, with the exception
-of windows 1 and 4 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-For social cohesion and negative events, RR was above chance for the 4th--6th and 46th--49th windows and below chance for the 56th--62nd windows.
-DET showed an upward trend as the windows moved.
-It bottomed out to zero for the 15th--23rd and 34th--39th windows, and was only above change for the 47th--54th and 62nd windows.
+RR as the window moved, with above- or nearly above-chance values in the first 23 windows
+and the 57th--62nd windows.
+RRR was largely below-chance for the 30th--38th windows.
+DET stayed largely within chance with intermittent bottoming-out to a value of 0 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and negative events, RR was above chance for the 7th window and below chance for the 15th--19th windows, intermittently below chance beetween the 25th--39th windows, and below chance for the 51st--62nd windows.
+DET showed a downward trend as the windows moved, with no abovee-chance values.
+It bottomed out to zero for the 15th--20th and 24th-27th windows, intermittently bottomed out for the 34th--45th windows, and consistently bottomed out for the 52nd--62nd windows.
 (Figure

### 2020-12-29 manuscript.Rmd
Update CRQA discussion

@@
 ### Syria as Target
-The significant result of DET and NRLINE for social cohesion with all events
-supports our first hypothesis that event activity is coupled with online social
-cohesion. The frequency of all events are thus associated with
-greater shared trajectories with social cohesion than would be expected by
-chance.
+The significant result of DET and NRLINE for social cohesion with all events supports our first hypothesis that event activity is coupled with online social cohesion.
+The frequency of all events are thus associated with a greater number and greater length of shared trajectories with social cohesion than would be expected by chance.
 This could be due to a conflation of the different kinds of events.
 However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis.
-In addition to the significant DET and NRLINE metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
-This may be a reflection of citizens' reaction to events that align with their cause.
+In addition to the significant DET,NRLINE, and LAM metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
+This may be a reflection of citizens’ reactions to events that align with their cause.
 An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to a groundswell of support on Twitter in an attempt to boost morale.
-By contrast, negative event frequency showed weak coupling, counter to our third hypothesis.
-Although the significant result for maxL suggests stability, the lack of significant results for other metrics indicate that the maxL metric may point toward a particular period where coupling was strong, although negative events were less coupled for the other points in time.
-Perhaps during times of intense strife, individuals in Syria focused on real-world action, turning to Twitter to report and rally together.
+
+Negative event frequency also showed coupling with social cohesion, as indicated by significant DET, NRLINE, and maxL metrics..
+The significant result for maxL again suggests greater stability of coupling with negative events than with all events.
+Perhaps during times of intense strife, individuals in Syria focused on communication and public awareness, turning to Twitter to report and rally together.
 Further text analysis should be conducted to decipher the underlying tone of the tweets.
@@
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target - num_target` samples. These additional observations are times where Syria initiated
-an event with another country. Events initiated by Syria but directed internally
-within the country were already captured by the target-only filtering.
-Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion.
-There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events.
-Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; considering additional source events then overshadowed the relationship between target events and social cohesion online.
-In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events.
-These two time series showed greater stability in their coupling (reflected in L).
-However, the significant ENTR metric suggests that there is more variability in the coupling, so rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, we interpret this as a breaking-up of the trajectories formed by the target events.
-Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and an increase in complexity of shared trajectories (reflected in rENTR).
+By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target - num_target` observations.
+These additional observations were times in which Syria initiated an event with another country.
+Events initiated by Syria but directed internally within the country were already captured by the target-only filtering.
+Taking outwardly directed events into account  changed the coupling for all-event filtering methods.
+There was no longer a significant number of shared trajectories or line lengths for social cohesion and count of all events.
+The recurrent points were still more likely to fall in diagonal trajectories (as seen in the significant DET metric), but there were fewer trajectories overall.
+This indicates that the cohesion on Twitter is not as strongly tied to the frequency of overall daily events when considering Syria as the target country, as they are less likely to share the same intensity values across extended periods of time.
+Since Syria-as-source events must be at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; integrating  additional source events then overshadowed the relationship between target events and social cohesion online.
+
+In contrast, there was a slight change in coupling between positive events and social cohesion that once again can only be due to the externally directed events.
+These two time series showed greater stability in their coupling (reflected in L) but lower attractor strength (reflected in maxL).
+This means that—although the longest trajectory in the target-only analysis was disrupted by the addition of source events—the additional observations resulted in an overall greater average length of trajectories.
+However, the significant ENTR and rENTR metrics suggest that there was more variability in the coupling.
+Rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, this may indicate that the trajectories formed by the target events were broken by the additional source events.
+This would also explain the overall decrease in the number of shared trajectories (reflected in NRLINE).
+
+The coupling between social cohesion with negative events changed dramatically.
+All previously significant metrics (DET, NRLINE, maxL) became non-significant.
 Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.
+The negative outward-directed source events may not have been of interest to Syrian Twitter users.
+Those external events may have then overshadowed the true coupled system between negative target events and virtual social cohesion.
 
 While interesting, the underlying meaning or drivers of these changes in CRQA results requires further investigation that incorporates the actual content of the tweets themselves.
-One possible reason (among many) may be that the findings were spurious.
-The source events may be covering up the relationship between different kinds of target events and Twitter social cohesion.
-However, we cannot test this hypothesis with the current time series data; future research should explore the semantic content of this tweet corpus to determine the nature of the socially cohered
-language.
+One possible reason (among many) may be that the processes of social cohesion of a population in the midst of an uprising are more tightly coupled to the state of the country itself, rather than the externally directed actions taken by the ruling class to manage international relations.
+For example, we observed coupling between negative events and social cohesion when considering only the target-filtered data, but that coupling disappeared when we added the source-filtered data to our dataset.
+In other words, the source events—that is, those taken by Syria toward parties outside of Syria (since Syrian-directed, Syrian-initiated actions were already included in the target-only dataset)—may have muddied the relationship between different kinds of target events and Twitter social cohesion—that is, the “singing with one voice” of the Syrian populace as they protested against their government.
+However, we cannot test this hypothesis with the current time series data; future research should explore the semantic content of this tweet corpus to determine the nature of the socially cohered language.
 

### 2020-12-30 manuscript.Rmd
Update discussion

@@
 the role of peripheral participants in the Syrian Arab Spring movement by
-@steinert2017spontaneous. By introducing CRQA and WCRQA to political science as time series analysis methods, we
-demonstrate how language and social mobilization interact with events along the
-conflict-cooperation continuum in Syria. We have introduced a novel theoretical
-framework of sociolinguistic cohesion, which we operationalize using a weighted
-measure of lexical relationships among social media posts. Using nonlinear dynamical time series
+@steinert2017spontaneous. By introducing CRQA and WCRQA to political science as
+time series analysis methods, we demonstrate how language and social
+mobilization interact with events along the conflict-cooperation continuum in
+Syria. We have introduced a novel theoretical framework of sociolinguistic
+cohesion, which we operationalize using a weighted measure of lexical
+relationships among social media posts. Using nonlinear dynamical time series
 analyses, we investigated the theory that virtual mobilization is increasingly
@@
 ### Syria as Target
-The significant result of DET and NRLINE for social cohesion with all events supports our first hypothesis that event activity is coupled with online social cohesion.
-The frequency of all events are thus associated with a greater number and greater length of shared trajectories with social cohesion than would be expected by chance.
-This could be due to a conflation of the different kinds of events.
-However, when we specifically target positive events, the coupling with social cohesion is strong, running counter to our second hypothesis.
-In addition to the significant DET,NRLINE, and LAM metrics seen in the all-events analysis, maxL and TT are significant for positive events, suggesting a more stable relationship.
-This may be a reflection of citizens’ reactions to events that align with their cause.
-An act of concession by the government or aid from another country may have led to an increase in morale or feelings of hope, in turn leading to a groundswell of support on Twitter in an attempt to boost morale.
-
-Negative event frequency also showed coupling with social cohesion, as indicated by significant DET, NRLINE, and maxL metrics..
-The significant result for maxL again suggests greater stability of coupling with negative events than with all events.
-Perhaps during times of intense strife, individuals in Syria focused on communication and public awareness, turning to Twitter to report and rally together.
-Further text analysis should be conducted to decipher the underlying tone of the tweets.
+The significant result of DET and NRLINE for social cohesion with all events
+supports our first hypothesis that event activity is coupled with online social
+cohesion. The frequency of all events are thus associated with a greater number
+and greater length of shared trajectories with social cohesion than would be
+expected by chance. This could be due to a conflation of the different kinds of
+events. However, when we specifically target positive events, the coupling with
+social cohesion is strong, running counter to our second hypothesis. In addition
+to the significant DET,NRLINE, and LAM metrics seen in the all-events analysis,
+maxL and TT are significant for positive events, suggesting a more stable
+relationship. This may be a reflection of citizens’ reactions to events that
+align with their cause. An act of concession by the government or aid from
+another country may have led to an increase in morale or feelings of hope, in
+turn leading to a groundswell of support on Twitter in an attempt to boost
+morale.
+
+Negative event frequency also showed coupling with social cohesion, as indicated
+by significant DET, NRLINE, and maxL metrics.. The significant result for maxL
+again suggests greater stability of coupling with negative events than with all
+events. Perhaps during times of intense strife, individuals in Syria focused on
+communication and public awareness, turning to Twitter to report and rally
+together. Further text analysis should be conducted to decipher the underlying
+tone of the tweets.
 
 ### Syria as Source and Target
-By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target - num_target` observations.
-These additional observations were times in which Syria initiated an event with another country.
-Events initiated by Syria but directed internally within the country were already captured by the target-only filtering.
-Taking outwardly directed events into account  changed the coupling for all-event filtering methods.
-There was no longer a significant number of shared trajectories or line lengths for social cohesion and count of all events.
-The recurrent points were still more likely to fall in diagonal trajectories (as seen in the significant DET metric), but there were fewer trajectories overall.
-This indicates that the cohesion on Twitter is not as strongly tied to the frequency of overall daily events when considering Syria as the target country, as they are less likely to share the same intensity values across extended periods of time.
-Since Syria-as-source events must be at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them; integrating  additional source events then overshadowed the relationship between target events and social cohesion online.
-
-In contrast, there was a slight change in coupling between positive events and social cohesion that once again can only be due to the externally directed events.
-These two time series showed greater stability in their coupling (reflected in L) but lower attractor strength (reflected in maxL).
-This means that—although the longest trajectory in the target-only analysis was disrupted by the addition of source events—the additional observations resulted in an overall greater average length of trajectories.
-However, the significant ENTR and rENTR metrics suggest that there was more variability in the coupling.
-Rather than interpreting these two changes as a fundamental change in coupling between source events and positive events, this may indicate that the trajectories formed by the target events were broken by the additional source events.
-This would also explain the overall decrease in the number of shared trajectories (reflected in NRLINE).
+By adding Syria as a source in the data filtering, the event dataset increased
+in size by `r num_source_target - num_target` observations. These additional
+observations were times in which Syria initiated an event with another country.
+Events initiated by Syria but directed internally within the country were
+already captured by the target-only filtering. Taking outwardly directed events
+into account  changed the coupling for all-event filtering methods. There was no
+longer a significant number of shared trajectories or line lengths for social
+cohesion and count of all events. The recurrent points were still more likely to
+fall in diagonal trajectories (as seen in the significant DET metric), but there
+were fewer trajectories overall. This indicates that the cohesion on Twitter is
+not as strongly tied to the frequency of overall daily events when considering
+Syria as the target country, as they are less likely to share the same intensity
+values across extended periods of time. Since Syria-as-source events must be at
+the root of this difference, it is plausible that Syrians were focused on the
+target events as they are immediately impacting them; integrating  additional
+source events then overshadowed the relationship between target events and
+social cohesion online.
+
+In contrast, there was a slight change in coupling between positive events and
+social cohesion that once again can only be due to the externally directed
+events. These two time series showed greater stability in their coupling
+(reflected in L) but lower attractor strength (reflected in maxL). This means
+that—although the longest trajectory in the target-only analysis was disrupted
+by the addition of source events—the additional observations resulted in an
+overall greater average length of trajectories. However, the significant ENTR
+and rENTR metrics suggest that there was more variability in the coupling.
+Rather than interpreting these two changes as a fundamental change in coupling
+between source events and positive events, this may indicate that the
+trajectories formed by the target events were broken by the additional source
+events. This would also explain the overall decrease in the number of shared
+trajectories (reflected in NRLINE).
 
@@
 All previously significant metrics (DET, NRLINE, maxL) became non-significant.
-Similarly to that of positive events, this change may not be reflective of source events themselves but rather a disruption of the relationship with target events.
-The negative outward-directed source events may not have been of interest to Syrian Twitter users.
-Those external events may have then overshadowed the true coupled system between negative target events and virtual social cohesion.
-
-While interesting, the underlying meaning or drivers of these changes in CRQA results requires further investigation that incorporates the actual content of the tweets themselves.
-One possible reason (among many) may be that the processes of social cohesion of a population in the midst of an uprising are more tightly coupled to the state of the country itself, rather than the externally directed actions taken by the ruling class to manage international relations.
-For example, we observed coupling between negative events and social cohesion when considering only the target-filtered data, but that coupling disappeared when we added the source-filtered data to our dataset.
-In other words, the source events—that is, those taken by Syria toward parties outside of Syria (since Syrian-directed, Syrian-initiated actions were already included in the target-only dataset)—may have muddied the relationship between different kinds of target events and Twitter social cohesion—that is, the “singing with one voice” of the Syrian populace as they protested against their government.
-However, we cannot test this hypothesis with the current time series data; future research should explore the semantic content of this tweet corpus to determine the nature of the socially cohered language.
+Similarly to that of positive events, this change may not be reflective of
+source events themselves but rather a disruption of the relationship with target
+events. The negative outward-directed source events may not have been of
+interest to Syrian Twitter users. Those external events may have then
+overshadowed the true coupled system between negative target events and virtual
+social cohesion.
+
+While interesting, the underlying meaning or drivers of these changes in CRQA
+results requires further investigation that incorporates the actual content of
+the tweets themselves. One possible reason (among many) may be that the
+processes of social cohesion of a population in the midst of an uprising are
+more tightly coupled to the state of the country itself, rather than the
+externally directed actions taken by the ruling class to manage international
+relations. For example, we observed coupling between negative events and social
+cohesion when considering only the target-filtered data, but that coupling
+disappeared when we added the source-filtered data to our dataset. In other
+words, the source events—that is, those taken by Syria toward parties outside of
+Syria (since Syrian-directed, Syrian-initiated actions were already included in
+the target-only dataset)—may have muddied the relationship between different
+kinds of target events and Twitter social cohesion—that is, the “singing with
+one voice” of the Syrian populace as they protested against their government.
+However, we cannot test this hypothesis with the current time series data;
+future research should explore the semantic content of this tweet corpus to
+determine the nature of the socially cohered language.
 
@@
 For the RR values in WCRQA of social cohesion and count of all events (Figure
-\@ref(fig:plot-wcrqa-targ-all)), we see both an early and late above-chance peak.
-However, DET for these periods only rises above chance for the later peak.
+\@ref(fig:plot-wcrqa-targ-all)), we see both an early and late above-chance
+peak. However, DET for these periods only rises above chance for the later peak.
 During this later period, the modal ICEWS event for each day (Figure
 \@ref(fig:plot-mode-event)) was almost consistently -10, the most violent event
-category. This supports our first hypothesis, that overall online cohesion may reflect the frequency of events occurring on the ground, particularly those that are violent in nature.
+category. This supports our first hypothesis, that overall online cohesion may
+reflect the frequency of events occurring on the ground, particularly those that
+are violent in nature.
 
@@
 
-///
+For positive events, we see a similar early peak in RR, but the later
+above-chance values did not match up temporally with that of the all-events time
+series (FIX Figure 10). This suggests that the early stretch of above-chance RR
+may have been captured in the RR of the all-events analysis, whereas the shorter
+stretches were overshadowed by the coupling with negative events. The early
+period of above-chance DET in the positive-event analysis aligned with the early
+period of above-chance RR, whereas the later stretch of significant DET values
+aligns temporally with that of the all-events analysis. It is possible that the
+later stretch reflected the decrease in the number of positive events happening
+(FIX see Fig. 4), while the relative sparsity of positive events led to an
+increase in coupling, with denizens rallying around dwindling bits of hope as
+time went on.
+
+For negative events, RR rarely reached above-chance values, but around the later
+windows, there were above-chance peaks in both RR and DET that were similar to
+that of the all-events analysis. As mentioned above, this time period was almost
+consistently dominated by events with a score of -10, indicating the most
+violent, dramatic events; during this time, Twitter users may come together to
+express grievances, bring about public awareness, ask for the help of other
+countries, or just document the events. However, further semantic analysis is
+needed to investigate these hypotheses.
+
+The above-chance values for negative-event coupling are followed by a consistent
+period of below-chance RR and a drastic drop in DET, co-occurring with the
+increase in positive-event coupling. This again may reflect the shift in
+attention to some positive events (e.g., aid, ceasefire agreements) or even a
+decrease in hostilities. However, the present analyses should be complemented
+with future analyses of semantic content to investigate these possible
+explanations.
 
 ### Syria as Source and Target
-
-///
+For count of all events and social cohesion, the WCRQA plot for RR looked
+largely the same as that of the target-only events, but DET showed a new early
+peak in above-chance values. This suggests that the overall number of events
+were more consistent from day to day when considering source events, as might be
+expected given that individuals can only participate in a limited number of
+events each day. Days that previously had a lower than average number of target
+events may now have had a more near-average number of source and target events
+because the reduced participation in target events allows for increased
+participation and initiation of source events.
+
+For positive events, we see a similar trend in RR as was observed in the
+target-only dataset, with a more pronounced late peak. However, the previously
+significant peaks in DET were no longer present. The addition of source events
+may have thus increased the amount of recurrence but overshadowed the
+trajectories of shared values found in the target-only events.
+
+For negative events, the early peak in RR for the target-only filtering was
+dramatically reduced compared to the target-only dataset, now spanning only two
+windows. Similar to that of positive events, the late peak in DET was no longer
+present. We hypothesize again that the addition of source events may have
+obscured the true coupled relationship between the negative events and social
+cohesion.
 
@@
 
-This methodology should be of great interest to interdisciplinary scientists investigating
-social mobilization. It has potential applications for gender studies and
-the #MeToo movement and for the relationship between social protest and repression
-during the Black Lives Matter protests. This methodological
-approach can help us better understand the fundamental human social mechanisms underlying
-social media and its influence on human behavior in real life. Given that many
-governments enact repressive measures when they determine that collective action
-by citizens is imminent, this methodology should help to improve the predictive
-power of using social media data in estimating repressive behavior. If social
-media messages are increasing in cohesion, this may represent a threat to civil
-and political liberties of citizens engaging in collective action.
+After identifying the dataset of interest, researchers should think carefully
+about how they will winnow down their data for analysis. The differences in our
+findings when considering target-only or source-and-target filtering highlight
+the importance of considering directionality when using event data. The parties
+involved and the specific actions they take can dramatically influence results,
+and it is critical to think carefully about which will be chosen and why.
+
+This methodology should be of great interest to interdisciplinary scientists
+investigating social mobilization. It has potential applications for gender
+studies and the #MeToo movement and for the relationship between social protest
+and repression during the Black Lives Matter protests. This methodological
+approach can help us better understand the fundamental human social mechanisms
+underlying social media and its influence on human behavior in real life. Given
+that many governments enact repressive measures when they determine that
+collective action by citizens is imminent, this methodology should help to
+improve the predictive power of using social media data in estimating repressive
+behavior. If social media messages are increasing in cohesion, this may
+represent a threat to civil and political liberties of denizens engaging in
+collective action, a unified reaction to sparse positive events, or an attempt
+to decry the government’s attempt to distract from what may be going on.
 
@@
 power and peace. Social media mobilization may thus help alert the world to
-citizens' actions and reactions that are suppressed by government regimes,
-providing insight into events that may not otherwise be broadcast and allowing
-for faster intervention.
+citizens' actions and reactions that are otherwise suppressed by government
+regimes, providing insight into events that may not otherwise be broadcast and
+allowing for faster intervention.
 

### 2020-12-30 manuscript.Rmd
Fix line breaks

@@
 social movements were reflected in their cohesive placards and posters. For
-example, the pervasive “I am a man” posters during the 1968 Memphis sanitation workers'
-strike reflected their internal cohesion and unified, goal-oriented movement
-[@Windsor2020].
+example, the pervasive “I am a man” posters during the 1968 Memphis sanitation
+workers' strike reflected their internal cohesion and unified, goal-oriented
+movement [@Windsor2020].
 
@@
 
-Amid the cacophony of messages during political upheaval---such
-as the Arab Spring of the early 2010s---consistent themes emerge through hashtags, retweets, and
-the repeated mentions of concepts such as regime, demonstration, and
-human rights.
-The cohesiveness of these themes (i.e., the degree to which participants in the movement are metaphorically singing in one voice) reflects the real-world events happening contemporaneously with collective action in social movements or civil conflicts.
+Amid the cacophony of messages during political upheaval---such as the Arab
+Spring of the early 2010s---consistent themes emerge through hashtags, retweets,
+and the repeated mentions of concepts such as regime, demonstration, and human
+rights. The cohesiveness of these themes (i.e., the degree to which participants
+in the movement are metaphorically singing in one voice) reflects the real-world
+events happening contemporaneously with collective action in social movements or
+civil conflicts.
 
 In the present research, we investigate the relationship between linguistic
-cohesion and social cohesion in times of social conflict and unrest.
-We tackle a question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does social media reflect on-the-ground realities during times of social conflict?
-To do so, we examine patterns of linguistic cohesion on Twitter and their connection to real-world events during the Arab Spring uprising in Syria between March and June 2012.
+cohesion and social cohesion in times of social conflict and unrest. We tackle a
+question related to the one posed by Zeitzoff [-@zeitzoff2017social]: How does
+social media reflect on-the-ground realities during times of social conflict? To
+do so, we examine patterns of linguistic cohesion on Twitter and their
+connection to real-world events during the Arab Spring uprising in Syria between
+March and June 2012.
 
@@
 
-In December 2010, a Tunisian man named Mohamed Bouazizi died after setting himself on fire to protest the authoritarian government’s unjustifiable confiscation of his vendor cart by municipal officials.
-His actions served as a catalyst for the Tunisian Revolution, which rapidly spread to surrounding countries also subject to unjust authoritarian rule, including Egypt, Libya, and Syria.
+In December 2010, a Tunisian man named Mohamed Bouazizi died after setting
+himself on fire to protest the authoritarian government’s unjustifiable
+confiscation of his vendor cart by municipal officials. His actions served as a
+catalyst for the Tunisian Revolution, which rapidly spread to surrounding
+countries also subject to unjust authoritarian rule, including Egypt, Libya, and
+Syria.
 
@@
 turned to social media to coordinate their activism and communicate to the
-world. Between March and June 2012, millions of tweets were sent within
-Syria, revealing the details of the conflict suppressed by the government.
-A full account of the history of the Arab Spring is outside of the scope of the current article; more information can be found in [@brownlee2013syria] and [@lynch2016new].
+world. Between March and June 2012, millions of tweets were sent within Syria,
+revealing the details of the conflict suppressed by the government. A full
+account of the history of the Arab Spring is outside of the scope of the current
+article; more information can be found in [@brownlee2013syria] and
+[@lynch2016new].
 
@@
 accessibility and proficiency as an information exchange tool, Twitter has
-provided social and political activists an opportunity to complement [@greijdanus2020psychology] and not hinder participation in [@harlow2012collective; @milovsevic2017civic] real-world social mobilization.
-During the 2012 Italian protests for global economic change, tweeting was determined to be more effective locally in discussing real-world, real-time events than traditional mainstream media platforms [@vicari2013public].
-As people increasingly rely on social media for local news and information, we must understand exactly how these micro-blogs connect to and reflect real-world action.
+provided social and political activists an opportunity to complement
+[@greijdanus2020psychology] and not hinder participation in
+[@harlow2012collective; @milovsevic2017civic] real-world social mobilization.
+During the 2012 Italian protests for global economic change, tweeting was
+determined to be more effective locally in discussing real-world, real-time
+events than traditional mainstream media platforms [@vicari2013public]. As
+people increasingly rely on social media for local news and information, we must
+understand exactly how these micro-blogs connect to and reflect real-world
+action.
 
@@
 @koehler2017political], but to our knowledge, the direct *coupling* between
-Syrian Twitter cohesion and international action has not been investigated  (though hashtag usage has been linked to next-day protests; @steinert2015online).
-In fact, some have been skeptical about the effect of social media on collective action at all [@seay2014slacktivism].
+Syrian Twitter cohesion and international action has not been investigated
+(though hashtag usage has been linked to next-day protests;
+@steinert2015online). In fact, some have been skeptical about the effect of
+social media on collective action at all [@seay2014slacktivism].
 
@@
 
-\noindent The important story about the 2011
-Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
-norms of civic engagement shaped the protesters' aspirations. Nor is it about
-how activists used technology to share ideas and tactics. Instead, the critical
-issue is how and why these ambitions and techniques resonated in their various
-local contexts. (p. 2)
+\noindent The important story about the 2011 Arab revolts in Tunisia, Egypt, and
+Libya is not how the globalization of the norms of civic engagement shaped the
+protesters' aspirations. Nor is it about how activists used technology to share
+ideas and tactics. Instead, the critical issue is how and why these ambitions
+and techniques resonated in their various local contexts. (p. 2)
 
@@
 
-Protestors and social activists communicate with each other with increased transparency due to the ubiquitous availability of social media like Twitter.
-Activists are able to access these tools via mobile
-phones and computers with Internet connectivity, providing a stream of real-time
-shared information. Citizens can share the location of events like protests and
-military incursions, the degree of state repression, and the number of
-casualties. In turn, the government---interested in remaining in
-power---monitors social media platforms to ascertain emerging threats
-[@comninos2011twitter], such as where new groups are forming, where existing
-groups are strengthening, where gatherings are held, and who the leaders are.
-
-With few exceptions, leader Bashar al-Assad chose to keep social media platforms up and running.
-Gohdes [-@gohdes2015pulling] notes that regimes can attempt to thwart the growth of social protest online and in the streets by shutting down the Internet.
-During these times, military repression increases, but government information about the citizens decreases.
-As a result, regimes may elect to maintain Internet connectivity to monitor and surveil their citizens.
+Protestors and social activists communicate with each other with increased
+transparency due to the ubiquitous availability of social media like Twitter.
+Activists are able to access these tools via mobile phones and computers with
+Internet connectivity, providing a stream of real-time shared information.
+Citizens can share the location of events like protests and military incursions,
+the degree of state repression, and the number of casualties. In turn, the
+government---interested in remaining in power---monitors social media platforms
+to ascertain emerging threats [@comninos2011twitter], such as where new groups
+are forming, where existing groups are strengthening, where gatherings are held,
+and who the leaders are.
+
+With few exceptions, leader Bashar al-Assad chose to keep social media platforms
+up and running. Gohdes [-@gohdes2015pulling] notes that regimes can attempt to
+thwart the growth of social protest online and in the streets by shutting down
+the Internet. During these times, military repression increases, but government
+information about the citizens decreases. As a result, regimes may elect to
+maintain Internet connectivity to monitor and surveil their citizens.
 
@@
 of cohesion between speakers and the alignment between that cohesion and their
-collective political behavior, just as the degree of cohesion among real-world protestors in past movements has been captured in their shared sign messaging [@Windsor2020].
+collective political behavior, just as the degree of cohesion among real-world
+protestors in past movements has been captured in their shared sign messaging
+[@Windsor2020].
 
@@
 strong aversion to an individual, event, or political injustice
-[@goldstone1980theories; @goldstone2011understanding]. Political resistance offers participants the
-opportunity to “lose themselves” and relinquish their individual identity in
-favor of identification with a larger group, contributing to a cohesive group
-ready and mobilized for action [@Hoffer2011true].
+[@goldstone1980theories; @goldstone2011understanding]. Political resistance
+offers participants the opportunity to “lose themselves” and relinquish their
+individual identity in favor of identification with a larger group, contributing
+to a cohesive group ready and mobilized for action [@Hoffer2011true].
 
@@
 mobilization, which facilitate the development of protest movements in some
-instances and constrain them in others” [@kitschelt1986political, p. 58]. Emergent strategies and tactics in contentious politics are a function of
-what the system makes possible. This includes the number of people and their
+instances and constrain them in others” [@kitschelt1986political, p. 58].
+Emergent strategies and tactics in contentious politics are a function of what
+the system makes possible. This includes the number of people and their
 disposition (i.e. nonviolent or violent), as well as their internal structure.
@@
 
-\noindent a religious or linguistic minority
-might suffer disproportionately in a given society, and this form of
-aggrievement can lead to unrest across the social lines that distinguish the
-minority group. Therefore, while collective cohesion is a function of targeted
-maldistributions, it is individual penury that allows for this collective
-mobilization. (p. 323)
+\noindent a religious or linguistic minority might suffer disproportionately in
+a given society, and this form of aggrievement can lead to unrest across the
+social lines that distinguish the minority group. Therefore, while collective
+cohesion is a function of targeted maldistributions, it is individual penury
+that allows for this collective mobilization. (p. 323)
 
@@
 the relative intensity of the conflict. Cohesion is a multi-layered concept
-referring to the connectedness of speakers, actions, and societies. It
-reflects the continuity of language and expression and shows the
-connectivity of participants in a social movement. To address the relationship
-between language and discourse and social movements, we adopt an
-interdisciplinary approach that incorporates linguistics, psychology, and
-political science using nonlinear dynamical systems methodology to disentangle the relationship between language and action.
+referring to the connectedness of speakers, actions, and societies. It reflects
+the continuity of language and expression and shows the connectivity of
+participants in a social movement. To address the relationship between language
+and discourse and social movements, we adopt an interdisciplinary approach that
+incorporates linguistics, psychology, and political science using nonlinear
+dynamical systems methodology to disentangle the relationship between language
+and action.
 
@@
 Just as real-world social cohesion can be quantified, so can online cohesion.
-One kind of cohesion is the similarity in language use on social
-media. This implicit or explicit similarity can indicate shared
-beliefs, thoughts, and feelings, as has been studied in research on language
-style in psycholinguistics and social psychology [@gonzales2010language;
+One kind of cohesion is the similarity in language use on social media. This
+implicit or explicit similarity can indicate shared beliefs, thoughts, and
+feelings, as has been studied in research on language style in psycholinguistics
+and social psychology [@gonzales2010language;
 @tausczik2010psychological;
@@
 media posts.  In Figure \@ref(fig:cohesion-in-tweets), we see four sequential
-tweets of four words each. Each sequential tweet contains some content
-included in the previous tweets. The linguistic construct of content word
-overlap measures the relationship across units of meaning---here, tweets---where
+tweets of four words each. Each sequential tweet contains some content included
+in the previous tweets. The linguistic construct of content word overlap
+measures the relationship across units of meaning---here, tweets---where
 identical and semantically similar words are repeated [@graesser2004coh]. These
@@
 
-In estimating cohesion in Twitter posts, tweets that share content words
-yield higher cohesion values, even among speakers with opposing
-views on the subject matter. Repetition of terms and concepts is captured by
-reiteration, which is a type of lexical cohesion in which a subsequent item
-repeats a previous item, or refers to it through synonymous language
-[@halliday1976cohesion].
-We include retweets (i.e., reposts or forwards of previous messages) because they are a form of reiteration that increases message cohesion.
-They indicate that individuals are “singing to the same tune” by amplifying the original message.
-Since retweets replicate verbatim another tweet (sometimes with the addition of commentary or supplementary messages), these tweets would also have higher cohesion.
+In estimating cohesion in Twitter posts, tweets that share content words yield
+higher cohesion values, even among speakers with opposing views on the subject
+matter. Repetition of terms and concepts is captured by reiteration, which is a
+type of lexical cohesion in which a subsequent item repeats a previous item, or
+refers to it through synonymous language [@halliday1976cohesion]. We include
+retweets (i.e., reposts or forwards of previous messages) because they are a
+form of reiteration that increases message cohesion. They indicate that
+individuals are “singing to the same tune” by amplifying the original message.
+Since retweets replicate verbatim another tweet (sometimes with the addition of
+commentary or supplementary messages), these tweets would also have higher
+cohesion.
 
@@
 
-We also include hashtags in our analyses.
-Hashtags are a way of identifying similar topics (e.g., people, events, places, themes) across users and across tweets by typing a string of characters preceded by a “#” symbol.
-Users may choose to include as many hashtags (up to the total character limit of the tweet) as they would like, and they may choose to create their own or adopt hashtags from other users or groups.
-The use of the same hashtags would increase cohesion; however, because hashtags are often included or embedded within longer messages, simply using the same hashtags would not be a guarantee of higher cohesion if the rest of the words in the tweets do not overlap.
+We also include hashtags in our analyses. Hashtags are a way of identifying
+similar topics (e.g., people, events, places, themes) across users and across
+tweets by typing a string of characters preceded by a “#” symbol. Users may
+choose to include as many hashtags (up to the total character limit of the
+tweet) as they would like, and they may choose to create their own or adopt
+hashtags from other users or groups. The use of the same hashtags would increase
+cohesion; however, because hashtags are often included or embedded within longer
+messages, simply using the same hashtags would not be a guarantee of higher
+cohesion if the rest of the words in the tweets do not overlap.
 
@@
 in-person social mobilization event, alerting a repressive government that
-collective mobilization is happening. It may also respond to
-exogenous events such as spontaneous, unprovoked militarized conflict.
+collective mobilization is happening. It may also respond to exogenous events
+such as spontaneous, unprovoked militarized conflict.
 
@@
 
-At the same time, behavioral similarity in certain contexts has been
-connected to important psychological and social effects. For example, shared
-language is associated with rapport [both in face-to-face and computer-mediated
-conversations; @niederhoffer2002linguistic; @riordan2011evidence] and
-can even be connected to better performance on shared tasks [as long as
-the language is relevant to the task at hand; @fusaroli2012coming]. Shared
-movement is associated with greater group bonding and greater willingness
-to contribute to the group [@wiltermuth2009synchrony], and shared identity
-leads to a greater willingness to adopt the group's goals and
-motivations [@walton2012mere].
+At the same time, behavioral similarity in certain contexts has been connected
+to important psychological and social effects. For example, shared language is
+associated with rapport [both in face-to-face and computer-mediated
+conversations; @niederhoffer2002linguistic; @riordan2011evidence] and can even
+be connected to better performance on shared tasks [as long as the language is
+relevant to the task at hand; @fusaroli2012coming]. Shared movement is
+associated with greater group bonding and greater willingness to contribute to
+the group [@wiltermuth2009synchrony], and shared identity leads to a greater
+willingness to adopt the group's goals and motivations [@walton2012mere].
 
 We expect to see increased linguistic cohesion among people participating in
-online discussions about an idea, event, individual, or movement.
-While the overall frequency of social media messages related to the event may increase as a result of the event, their linguistic cohesion helps us understand if denizens are using the platforms in a coordinated way that amplifies their messages or goals and creates a virtual protest space.
-Given that
-Syrian protesters coordinated their activity through Twitter by discussing their
-own events (e.g., planned protests, active demonstrations) and their reactions
-to events happening around them (e.g., government reactions, international
-action or inaction), the cohesion in social media should correlate with the
-social cohesion of the group [@zeitzoff2011using].
+online discussions about an idea, event, individual, or movement. While the
+overall frequency of social media messages related to the event may increase as
+a result of the event, their linguistic cohesion helps us understand if denizens
+are using the platforms in a coordinated way that amplifies their messages or
+goals and creates a virtual protest space. Given that Syrian protesters
+coordinated their activity through Twitter by discussing their own events (e.g.,
+planned protests, active demonstrations) and their reactions to events happening
+around them (e.g., government reactions, international action or inaction), the
+cohesion in social media should correlate with the social cohesion of the group
+[@zeitzoff2011using].
 
@@
 encodes who does what to whom on a given day. The CAMEO (Conflict and Mediation
-Event Observations) coding scheme encodes a set of activities with numerical values, rescaled
-to reflect a conflict-cooperation scale [@schrodt2006twenty;
-@goldstein1992conflict]. These event codes include a range of behaviors of varying intensities and valences, from
-making public statements and appeals to demanding, threatening, protesting, and
-using unconventional mass violence.
+Event Observations) coding scheme encodes a set of activities with numerical
+values, rescaled to reflect a conflict-cooperation scale [@schrodt2006twenty;
+@goldstein1992conflict]. These event codes include a range of behaviors of
+varying intensities and valences, from making public statements and appeals to
+demanding, threatening, protesting, and using unconventional mass violence.
 
@@
 @mcadam1986recruitment], building the movement by expanding and deepening
-heterogenous ties. Therefore, during social conflict, the linguistic cohesion
-of the online conversation should correspond to the degree of social cohesion on
+heterogenous ties. Therefore, during social conflict, the linguistic cohesion of
+the online conversation should correspond to the degree of social cohesion on
 the ground.
@@
 changes over time in response to external events and the internal dynamics of
-the social movement, even if the social interaction occurs entirely 
-online [@centola2007complex].
+the social movement, even if the social interaction occurs entirely online
+[@centola2007complex].
 
@@
 
-Related previous work has also explored diffusion of hashtags in viral contagion in
-Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
-[@fink2016complex]. The prevalence and rate of particular hashtags
-contributed to the overall sociolinguistic cohesion. The more that people
-reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
-this phenomenon occurs during socially significant times like protests
-[@state2015diffusion].
+Related previous work has also explored diffusion of hashtags in viral contagion
+in Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
+[@fink2016complex]. The prevalence and rate of particular hashtags contributed
+to the overall sociolinguistic cohesion. The more that people reuse hashtags or
+common phrases, the greater the sociolinguistic cohesion when this phenomenon
+occurs during socially significant times like protests [@state2015diffusion].
 
@@
 driven by one another. From a dynamical systems perspective, online social
-cohesion and in-person action can be considered two complementary components of a single system--constantly constrained by, interacting with, and influencing one another [@mahner1997foundations].
-Investigation of the coupling of
+cohesion and in-person action can be considered two complementary components of
+a single system--constantly constrained by, interacting with, and influencing
+one another [@mahner1997foundations]. Investigation of the coupling of
 real-world mobilization and social cohesion could provide new insight into the
@@
 
-At the same time, the foundational theoretical assumptions of a linear world have
-been increasingly replaced by ideas from dynamical systems theory. Rather than a
-chain of events, time series data can be thought of as nested occurrences, where
-mutually constrained parts (e.g., citizens, governments, real-world events,
-social media platforms) are constantly interacting, leading to more global
-behaviors that are larger than the sum of the parts [@turvey2018lectures]. When
-analyzed as dynamical systems, many phenomena exhibit new nonlinear patterns
-that were formerly overlooked. Nonlinear methods provide means for capturing the
-rich temporal dynamics and variability that unfold in time series data.
-
-Although a number of other nonlinear methods exist, the primary nonlinear methods
-used in the current work are cross-recurrence quantification analysis [CRQA;
+At the same time, the foundational theoretical assumptions of a linear world
+have been increasingly replaced by ideas from dynamical systems theory. Rather
+than a chain of events, time series data can be thought of as nested
+occurrences, where mutually constrained parts (e.g., citizens, governments,
+real-world events, social media platforms) are constantly interacting, leading
+to more global behaviors that are larger than the sum of the parts
+[@turvey2018lectures]. When analyzed as dynamical systems, many phenomena
+exhibit new nonlinear patterns that were formerly overlooked. Nonlinear methods
+provide means for capturing the rich temporal dynamics and variability that
+unfold in time series data.
+
+Although a number of other nonlinear methods exist, the primary nonlinear
+methods used in the current work are cross-recurrence quantification analysis
+[CRQA;
 @zbilut1998detecting] and its offshoot, windowed cross-recurrence quantification
@@
 This study aims to explore the dynamics of Twitter users in Syria, who used the
-social media platform to raise awareness about the Arab Spring and the relationship of those messages to mass mobilization in the real world.
+social media platform to raise awareness about the Arab Spring and the
+relationship of those messages to mass mobilization in the real world.
 
@@
 
-The corpus of tweets used included `r tweet_stats$total_tweets` English-language Syrian tweets
-occurring between March 31--June 15, 2012. Using the Twitter streaming API,
-servers at the University of Texas at Austin collected the tweets. The servers
-were run on a stable (LTS) version of Ubuntu Linus (v. 10.04) and were connected
-directly to the high-bandwidth UT network maintained by IT services.
+The corpus of tweets used included `r tweet_stats$total_tweets` English-language
+Syrian tweets occurring between March 31--June 15, 2012. Using the Twitter
+streaming API, servers at the University of Texas at Austin collected the
+tweets. The servers were run on a stable (LTS) version of Ubuntu Linus (v.
+10.04) and were connected directly to the high-bandwidth UT network maintained
+by IT services.
 
@@
 authentication (OAuth was optional, at the time) at
-https://stream.twitter.com/1.1/statuses/filter.json and stored the data
-directly to the local hard disk. The tweets were then post-processed with a
-Python script to convert the JSON-formatted tweets to tab-separated files, which
-were then compressed to maximize storage efficiency.
-
-The corpus consisted of `r tweet_stats$percent_original_tweets`% original tweets, `r tweet_stats$percent_retweets`% retweets, and `r tweet_stats$percent_replies`% replies.
-There were `r tweet_stats$num_users` users in the corpus and an average of `r tweet_stats$avg_daily_tweets` tweets per day.
+https://stream.twitter.com/1.1/statuses/filter.json and stored the data directly
+to the local hard disk. The tweets were then post-processed with a Python script
+to convert the JSON-formatted tweets to tab-separated files, which were then
+compressed to maximize storage efficiency.
+
+The corpus consisted of `r tweet_stats$percent_original_tweets`% original
+tweets, `r tweet_stats$percent_retweets`% retweets, and `r
+tweet_stats$percent_replies`% replies. There were `r tweet_stats$num_users`
+users in the corpus and an average of `r tweet_stats$avg_daily_tweets` tweets
+per day.
 
@@
 incomplete and incorrectly formatted data. They were then filtered to include
-only events that were directed at (i.e., `target`) Syria (n = `r num_target`). To
-explore the impact of outwardly directed Syrian events, the data were filtered
-again to include events that were both directed at (i.e., `target`) or directed
-by (i.e., `source`) Syria (n = `r num_source_target`).
+only events that were directed at (i.e., `target`) Syria (n = `r num_target`).
+To explore the impact of outwardly directed Syrian events, the data were
+filtered again to include events that were both directed at (i.e., `target`) or
+directed by (i.e., `source`) Syria (n = `r num_source_target`).
 
@@
 ### Social Cohesion Metric
-The social cohesion or linguistic similarity of daily tweets was calculated by quantifying the frequency of shared content words with respect to those words’ frequencies in the entire tweet corpus.
-Retweets were included in the corpus and used in the social cohesion calculation, as they indicate strong support for an individual’s message.
-Stop words, punctuations, and duplicate words were not removed from the tweets.
-The lengths of tweets were disregarded, as the aspect of interest is in shared linguistic content and not breadth of description.
-The presence of bots was not investigated.
-According to a 10-Q report for Twitter, Inc., for a quarterly period in 2014, the estimated number of third party applications automatically contacting the servers (i.e., bots), was less than 8.5% [@twitter2014].
-As the data in this study were collected two years prior, this number was likely even less.
-Thus we consider the number of bots negligible for the present investigation.
-
-The tweets were first sorted into ascending order by timestamp.
-They were then grouped into successive sets of five tweets.
-Groups of five were chosen to allow for manageability and efficiency of the analyses.
-Linguistic cohesion was quantified for all possible pairs of tweets in the group of five, resulting in 10 pairs per group of tweets; all 10 cohesion values for the group were averaged for a single group cohesion value.
-The cohesion value for each day was quantified as the average cohesion values for all groups in that day.
-Each pair’s cohesion value was calculated in three parts:
+The social cohesion or linguistic similarity of daily tweets was calculated by
+quantifying the frequency of shared content words with respect to those words’
+frequencies in the entire tweet corpus. Retweets were included in the corpus and
+used in the social cohesion calculation, as they indicate strong support for an
+individual’s message. Stop words, punctuations, and duplicate words were not
+removed from the tweets. The lengths of tweets were disregarded, as the aspect
+of interest is in shared linguistic content and not breadth of description. The
+presence of bots was not investigated. According to a 10-Q report for Twitter,
+Inc., for a quarterly period in 2014, the estimated number of third party
+applications automatically contacting the servers (i.e., bots), was less than
+8.5% [@twitter2014]. As the data in this study were collected two years prior,
+this number was likely even less. Thus we consider the number of bots negligible
+for the present investigation.
+
+The tweets were first sorted into ascending order by timestamp. They were then
+grouped into successive sets of five tweets. Groups of five were chosen to allow
+for manageability and efficiency of the analyses. Linguistic cohesion was
+quantified for all possible pairs of tweets in the group of five, resulting in
+10 pairs per group of tweets; all 10 cohesion values for the group were averaged
+for a single group cohesion value. The cohesion value for each day was
+quantified as the average cohesion values for all groups in that day. Each
+pair’s cohesion value was calculated in three parts:
 
@@
 
-Equation 1 identifies the inverse frequency weighting of each overlapping word $t_i$ between two tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all overlapping words $t_{1...k}$ between the two tweets.
-
-\begin{align}
-\text{Inverse frequency weighting of all words = }\sum_{i=1}^n \frac{log(f(t_i,
-d_1) + f(t_i, d_2) + 1)}{log(f(t_i) + 1)}
+Equation 1 identifies the inverse frequency weighting of each overlapping word
+$t_i$ between two tweets $d_1$ and $d_2$, relative to the word’s frequency in
+the corpus D, for all overlapping words $t_{1...k}$ between the two tweets.
+
+\begin{align} \text{Inverse frequency weighting of all words = }\sum_{i=1}^n
+\frac{log(f(t_i, d_1) + f(t_i, d_2) + 1)}{log(f(t_i) + 1)} \end{align}
+
+Equation 2 then calculates the inverse frequency of each word $t_i$  in tweets
+$d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all words
+$t{1...n}$ that appear in either tweet.
+
+\begin{align} \text{Two tweets' similarity =}\frac{\text{inverse frequency
+weighting of overlap words}}{\text{inverse frequency weighting of all words}}
 \end{align}
 
-Equation 2 then calculates the inverse frequency of each word $t_i$  in tweets $d_1$ and $d_2$, relative to the word’s frequency in the corpus D, for all words $t{1...n}$ that appear in either tweet.
-
-\begin{align}
-\text{Two tweets' similarity =}\frac{\text{inverse frequency weighting of overlap
-words}}{\text{inverse frequency weighting of all words}}
-\end{align}
-
-Finally, Equation 3 identifies their linguistic cohesion by taking the ratio of the results of Equations 1 and 2.
-Through this process, we are able to naturally account for the frequencies of natural language generally and of online language specifically: Words that occur many times in the corpus (which we can operationalize as function words; e.g., prepositions, pronouns) influence the similarity scores between two tweets much less than words that occur rarely in the corpus (which we can operationalize as content words; e.g., names, hashtags).
+Finally, Equation 3 identifies their linguistic cohesion by taking the ratio of
+the results of Equations 1 and 2. Through this process, we are able to naturally
+account for the frequencies of natural language generally and of online language
+specifically: Words that occur many times in the corpus (which we can
+operationalize as function words; e.g., prepositions, pronouns) influence the
+similarity scores between two tweets much less than words that occur rarely in
+the corpus (which we can operationalize as content words; e.g., names,
+hashtags).
 
@@
 frequency* [tf-idf; see also @jones1972statistical;
-@robertson2004understanding].
-However, the method focuses more squarely on terms (i.e., agnostic to the number of documents in the corpus), aggregates at a higher semantic level (i.e., summing across words), and accounts for linguistic novelty relative to the pair and the corpus (i.e., ratio of Eq.
-1 to Eq.
-2).
-The social cohesion calculation was performed on the tweet corpus containing English tweets.
-All hashtags and URLs were included in the analysis.
-The raw social cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
+@robertson2004understanding]. However, the method focuses more squarely on terms
+(i.e., agnostic to the number of documents in the corpus), aggregates at a
+higher semantic level (i.e., summing across words), and accounts for linguistic
+novelty relative to the pair and the corpus (i.e., ratio of Eq. 1 to Eq. 2). The
+social cohesion calculation was performed on the tweet corpus containing English
+tweets. All hashtags and URLs were included in the analysis. The raw social
+cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
 
@@
 
-[Figures \@ref(fig:raw-event-ts-target) and \@ref(fig:raw-event-ts-source-target) about here]
+[Figures \@ref(fig:raw-event-ts-target) and
+\@ref(fig:raw-event-ts-source-target) about here]
 
@@
 @zbilut1998detecting] to investigate the temporal patterns of social cohesion
-and real-world events in Syria during Arab Spring. CRQA is an extension of RQA, which captures the patterns of revisited states of a single time series
+and real-world events in Syria during Arab Spring. CRQA is an extension of RQA,
+which captures the patterns of revisited states of a single time series
 [@zbilut1992embeddings; @webber1994dynamical]. CRQA allows for two time series
 to be projected onto one another to investigate shared states and trajectories.
-In CRQA, we track these shared states by identifying *recurrent points*, or intersections of time during which two signals shared or revisited the same state.
-These shared states can be at the same time or at later points in the time series.
-We can further chart shared trajectories by examining the
+In CRQA, we track these shared states by identifying *recurrent points*, or
+intersections of time during which two signals shared or revisited the same
+state. These shared states can be at the same time or at later points in the
+time series. We can further chart shared trajectories by examining the
 occurrences and patterns of multiple sequential recurrent points.
 
-To perform categorical CRQA, the time series must be converted to the same scale, while
-still preserving a sampling rate that respects the native timescale of the
-system [cf.
-Nyquist frequency in signal processing; @grenander1959probability].
-In other words, a system that changes every day must be sampled more often than a system that changes every year and less often than a system that changes every hour.
-However, to compare two time series with CRQA, the two time series must be sampled at the same frequency as one another.
+To perform categorical CRQA, the time series must be converted to the same
+scale, while still preserving a sampling rate that respects the native timescale
+of the system [cf. Nyquist frequency in signal processing;
+@grenander1959probability]. In other words, a system that changes every day must
+be sampled more often than a system that changes every year and less often than
+a system that changes every hour. However, to compare two time series with CRQA,
+the two time series must be sampled at the same frequency as one another.
+
 Because the social cohesion and event data have different scales and values, we
@@
 We can visually analyze these plots to reveal patterns of structure and
-recurrence.
-The main diagonal line on the plot is known as the *line of synchrony*.
-This line falls where the time series match temporally.
-A completely filled main diagonal line would indicate perfect in-phase synchrony between the two time series.
-See Figures
-\@ref(fig:plot-rp-targ)-\@ref(fig:plot-rp-source-targ) for examples of
-RPs.
+recurrence. The main diagonal line on the plot is known as the *line of
+synchrony*. This line falls where the time series match temporally. A completely
+filled main diagonal line would indicate perfect in-phase synchrony between the
+two time series. See Figures
+\@ref(fig:plot-rp-targ)-\@ref(fig:plot-rp-source-targ) for examples of RPs.
 
@@
 
-Using the real deciled time series of social cohesion, count of all events, count of
-positive events, and count of negative events, we conducted a series of
+Using the real deciled time series of social cohesion, count of all events,
+count of positive events, and count of negative events, we conducted a series of
 permutation tests (one for the comparison between social cohesion and each type
@@
 chance was set at the 95th and 99th percentiles of the metrics from the permuted
-CRQ analyses.
-Given that a permutation test is similar to bootstrapping but does not include replacement, all real recurrent points were included in each CRQA analysis, leaving RR constant across all permutations.
-Thus, RR is not included in the inferential tests.
+CRQ analyses. Given that a permutation test is similar to bootstrapping but does
+not include replacement, all real recurrent points were included in each CRQA
+analysis, leaving RR constant across all permutations. Thus, RR is not included
+in the inferential tests.
 
@@
 “window” of time points is used to calculate CRQA and capture more fine-grained
-dynamics of two time series. The window remains the same size and “slides” diagonally up the line of synchrony. The changes in the CRQA metrics across the
+dynamics of two time series. The window remains the same size and “slides”
+diagonally up the line of synchrony. The changes in the CRQA metrics across the
 windows can reveal changes in dynamics that can then be linked to external,
@@
 investigate the dynamics over two weeks and allow for the capture of more
-structure and thus a more meaningful interpretation of DET.
-A window size smaller than 14 would limit the possibilities for shared trajectories and make determinism uninterpretable, and window sizes larger than 14 would increasingly overshadow the fine-grain dynamics that we want to investigate.
+structure and thus a more meaningful interpretation of DET. A window size
+smaller than 14 would limit the possibilities for shared trajectories and make
+determinism uninterpretable, and window sizes larger than 14 would increasingly
+overshadow the fine-grain dynamics that we want to investigate.
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for DET, NRLINE, and LAM. All other
-metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
+a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
+did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
+
+A permutation test for the CRQA of social cohesion and count of positive events
+found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT.
+All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
 \autoref{table-1}).
 
-A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT. All other
-metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
-
 A permutation test for the CRQA of social cohesion and count of negative events
-found a statistically significant difference from chance for DET, NRLINE, and maxL. All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
+found a statistically significant difference from chance for DET, NRLINE, and
+maxL. All other metrics did not reach significance (Figure
+\@ref(fig:plot-rp-targ); \autoref{table-1}).
 
@@
 a statistical difference from chance for DET, maxL, and LAM. All other metrics
-were non-significant (Figure \@ref(fig:plot-rp-source-targ);
-\autoref{table-2}).
+were non-significant (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
 
 A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM (Figure
+found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM
+(Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found no statistical difference from chance for and metrics (Figure
 \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of negative events
-found no statistical difference from chance for and metrics (Figure \@ref(fig:plot-rp-source-targ);
-\autoref{table-2}).
 
@@
 
-For social cohesion and count of all events, there was a consistent period of
-at or above-chance RR from the 3rd--12th and 44th--50th window. DET was largely above chance
-from the 47th to the 54th window, with some exceptions (Figure
+For social cohesion and count of all events, there was a consistent period of at
+or above-chance RR from the 3rd--12th and 44th--50th window. DET was largely
+above chance from the 47th to the 54th window, with some exceptions (Figure
 \@ref(fig:plot-wcrqa-targ-all)).
@@
 as the window advances throughout the sample. Interestingly, we see largely
-above-chance RR until the 16th window, with an exception for window 1.
-A peak also appeared for the 40th--42nd windows.
-DET was intermittently at or above chance for the 8th--14th and 54th--62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+above-chance RR until the 16th window, with an exception for window 1. A peak
+also appeared for the 40th--42nd windows. DET was intermittently at or above
+chance for the 8th--14th and 54th--62nd windows (Figure
+\@ref(fig:plot-wcrqa-targ-all)).
 
 For social cohesion and count of negative events, RR stayed above or almost
-above chance from the 5th--6th and 46th--49th windows and was below chance for an extended period from the 56th--62nd window.
-DET bottomed out at zero for the 15th--23rd windows.
-The metric was above or nearly above chance only toward the end of the time series, in the 47th--54th and 62nd windows (Figure \@ref(fig:plot-wcrqa-targ-all)).
+above chance from the 5th--6th and 46th--49th windows and was below chance for
+an extended period from the 56th--62nd window. DET bottomed out at zero for the
+15th--23rd windows. The metric was above or nearly above chance only toward the
+end of the time series, in the 47th--54th and 62nd windows (Figure
+\@ref(fig:plot-wcrqa-targ-all)).
 
@@
 For social cohesion and count of all events, there was a consistent period of
-above- or nearly above-chance RR in the first 23 windows and the 44th--52nd windows.
-RR was consistently below chance for the 29th--39th windows.
-DET showed above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
+above- or nearly above-chance RR in the first 23 windows and the 44th--52nd
+windows. RR was consistently below chance for the 29th--39th windows. DET showed
+above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
 \@ref(fig:plot-wcrqa-source-targ-all)).
@@
 For social cohesion and count of positive events, there was a downward trend in
-RR as the window moved, with above- or nearly above-chance values in the first 23 windows
-and the 57th--62nd windows.
-RRR was largely below-chance for the 30th--38th windows.
-DET stayed largely within chance with intermittent bottoming-out to a value of 0 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-For social cohesion and negative events, RR was above chance for the 7th window and below chance for the 15th--19th windows, intermittently below chance beetween the 25th--39th windows, and below chance for the 51st--62nd windows.
+RR as the window moved, with above- or nearly above-chance values in the first
+23 windows and the 57th--62nd windows. RRR was largely below-chance for the
+30th--38th windows. DET stayed largely within chance with intermittent
+bottoming-out to a value of 0 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+
+For social cohesion and negative events, RR was above chance for the 7th window
+and below chance for the 15th--19th windows, intermittently below chance
+beetween the 25th--39th windows, and below chance for the 51st--62nd windows.
 DET showed a downward trend as the windows moved, with no abovee-chance values.
-It bottomed out to zero for the 15th--20th and 24th-27th windows, intermittently bottomed out for the 34th--45th windows, and consistently bottomed out for the 52nd--62nd windows.
-(Figure
-\@ref(fig:plot-wcrqa-source-targ-all)).
+It bottomed out to zero for the 15th--20th and 24th-27th windows, intermittently
+bottomed out for the 34th--45th windows, and consistently bottomed out for the
+52nd--62nd windows. (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
 

### 2020-12-30 manuscript.Rmd
Add revisions

@@
 social cohesion calculation was performed on the tweet corpus containing English
-tweets. All hashtags and URLs were included in the analysis. The raw social
-cohesion time series can be seen in Figure \@ref(fig:raw-cohesion-ts).
+tweets. All hashtags were included in the analysis, while URLs were removed. The
+raw social cohesion time series can be seen in Figure
+\@ref(fig:raw-cohesion-ts).
 
@@
 the two time series must be sampled at the same frequency as one another.
-
 Because the social cohesion and event data have different scales and values, we
-converted each time series (e.g., Figure \@ref(fig:raw-ts)) into deciles (e.g.,
-Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of different
-levels of social cohesion and counts of all, positive, and negative events on
-each day. We implemented CRQA using the `crqa` package [@R-crqa] for R
+converted each time series of daily values (e.g., Figure \@ref(fig:raw-ts)) into
+deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of
+different levels of social cohesion and counts of all, positive, and negative
+events on each day. We implemented CRQA using the `crqa` package [@R-crqa] for R
 [@R-base].
@@
 recurrent point would indicate that the level of social cohesion and frequency
-of events were at the same intensity.
+of events were at the same intensity for across two particular points in time
+(in this case, one-day windows). Importantly, the nature of CRQA allows us to
+quantify how a system shares similar states across time: In other words, it
+identifies recurrence whether a window of shared intensity occurs on the same
+day for the two time series or after a one-week gap between when the two time
+series exhibit the same intensity.
 
@@
 permutation tests (one for the comparison between social cohesion and each type
-of event count) to determine statistical difference from chance for each CRQA
+of event count) to determine whether the observed measure is statistically different from chance for each CRQA
 metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for DET, NRLINE, and LAM. All other metrics
-did not reach significance (Figure \@ref(fig:plot-rp-targ); \autoref{table-1}).
+a statistically significant difference from chance for DET, NRLINE, and LAM. All
+other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
+\autoref{table-1}).
 
 A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for DET, NRLINE, maxL, LAM, and TT.
-All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
-\autoref{table-1}).
+found a statistically significant difference from chance for DET, NRLINE, maxL,
+LAM, and TT. All other metrics did not reach significance (Figure
+\@ref(fig:plot-rp-targ); \autoref{table-1}).
 
@@
 A permutation test for the CRQA of social cohesion and count of all events found
-a statistical difference from chance for DET, maxL, and LAM. All other metrics
-were non-significant (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
+a statistically significant difference from chance for DET, maxL, and LAM. All
+other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
+\autoref{table-2}).
 
 A permutation test for the CRQA of social cohesion and count of positive events
-found a statistical difference from chance for DET, L, ENTR, rENTR, and LAM
+found a statistically significant difference from chance for DET, L, ENTR,
+rENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
+
+A permutation test for the CRQA of social cohesion and count of negative events
+found no statistically significant difference from chance for and metrics
 (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
-
-A permutation test for the CRQA of social cohesion and count of negative events
-found no statistical difference from chance for and metrics (Figure
-\@ref(fig:plot-rp-source-targ); \autoref{table-2}).
 

### 2020-12-30 manuscript.Rmd
Add revisions to permutation sections

@@
   - name          : "Alistair Windsor"
-    affiliation   : "4"
+    affiliation   : "3,4"
   - name          : "Alexandra Paxton"
@@
 10 pairs per group of tweets; all 10 cohesion values for the group were averaged
-for a single group cohesion value. The cohesion value for each day was
-quantified as the average cohesion values for all groups in that day. Each
-pair’s cohesion value was calculated in three parts:
+for a single group cohesion value. The cohesion value for each day was computed
+as the average cohesion values for all groups whose first tweet was on that day.
+Each pair’s cohesion value was calculated in three parts:
 
@@
 
-#### Permutation Test
+#### Approximate Permutation Test
 Unlike some nonlinear analyses (e.g., fractal analyses), CRQA metrics do not
 have inherently meaningful values. As a result, CRQA is best used as a relative
-metric---that is, comparing the CRQA values across conditions or subsets of the
+metric—that is, comparing the CRQA values across conditions or subsets of the
 data. Typically, meaningful differences between values are determined with
@@
 
-For CRQA, this can be addressed using *permutation tests*. Similar to more
-established methods of statistical significance in CRQA research [which create
-surrogate time series; e.g., @paxton2017interpersonal], the permutation test
-approach to significance testing allows the researcher to use a time series as
-its own baseline by testing whether the *structure* of the unfolding events of
-the time series---rather than the *raw frequency* of the events within the time
-series---cohere together more than would be expected by chance. A permutation
-test is similar to bootstrapping, except that the sampling of observations is
-done without replacement. In this approach, we simply create a large number of
-permutations of the original time series (i.e., breaking up the dependency
-across time points but preserving the frequencies of the events), conduct CRQA
-for each of those permutations, and then examine whether the real time series'
-CRQA metrics exceed those that we would expect to see by chance. The proportion
-of times that the real time series' values exceeds the surrogate time series'
-values can be interpreted as the alpha criterion to determine significance. For
-more information on permutation tests, see @good2013permutation.
+For CRQA, this can be addressed using *approximate permutation tests*. Similar
+to more established methods of statistical significance in CRQA research (which
+create surrogate time series; e.g., @paxton2017interpersonal), the permutation
+test approach to significance testing allows the researcher to use a time series
+as its own baseline by testing whether the *structure* of the unfolding events
+of the time series—rather than the *raw frequency* of the events within the time
+series—cohere together more than would be expected by chance. Permutation tests
+are used to identify null distributions for test statistics when the null
+hypothesis is that the group assignment does not matter, and they can be used
+when traditional parametric tests may not be appropriate [e.g.,
+@collingridge2013primer;
+@boring2016student]. The test is similar to bootstrapping, except that the
+sampling of observations is done without replacement.
+
+To quantify the differences in the CRQA metrics from those that would be
+expected by chance, we conducted approximate permutation tests for significance
+with upper and lower bounds for the 95th and 99th percentiles (comparable to
+traditional alpha criteria of .05 and .01, respectively). In this approach, we
+simply create a large number of permutations of the original time series (i.e.,
+breaking up the dependency across time points but preserving the frequencies of
+the events), conduct CRQA for each of those permutations, and then examine
+whether the real time series’ CRQA metrics exceed those that we would expect to
+see by chance. The proportion of times that the real time series’ values exceeds
+the surrogate time series’ values can be interpreted as the alpha criterion to
+determine significance. For more information on permutation tests, see
+@good2013permutation.
 
@@
 permutation tests (one for the comparison between social cohesion and each type
-of event count) to determine whether the observed measure is statistically different from chance for each CRQA
-metric. Using the `sample` function in base R [@R-base], $1000$ permuted time
-series were created for each of the real time series. CRQA was then run $1000$
-times for social cohesion and count of all events, social cohesion and count of
-positive events, and social cohesion and count of negative events using the
-permuted time series. This resulted in $1000$ results for each of the CRQA
-metrics for each combination of time series. Statistical significance from
-chance was set at the 95th and 99th percentiles of the metrics from the permuted
-CRQ analyses. Given that a permutation test is similar to bootstrapping but does
-not include replacement, all real recurrent points were included in each CRQA
-analysis, leaving RR constant across all permutations. Thus, RR is not included
-in the inferential tests.
+of event count) to determine whether the observed measure is statistically
+different from chance for each CRQA metric. Using the `sample` function in base
+R [@R-base], $1000$ permuted time series were created for each of the real time
+series. CRQA was then run for each permuted time series combination for social
+cohesion and count of all events, social cohesion and count of positive events,
+and social cohesion and count of negative events using the permuted time series.
+This resulted in $1000$ results for each of the CRQA metrics for each
+combination of time series. Statistical significance from chance was set at the
+95th and 99th percentiles of the metrics from the permuted CRQ analyses. Given
+that a permutation test is similar to bootstrapping but does not include
+replacement, all real recurrent points were included in each CRQA analysis,
+leaving RR constant across all permutations. Thus, RR is not included in the
+inferential tests.
 
@@
 investigate the dynamics over two weeks and allow for the capture of more
-structure and thus a more meaningful interpretation of DET. A window size
-smaller than 14 would limit the possibilities for shared trajectories and make
-determinism uninterpretable, and window sizes larger than 14 would increasingly
-overshadow the fine-grain dynamics that we want to investigate.
+structure and thus a more meaningful interpretation of DET. We first attempted
+to use a window size of $7$ to investigate the dynamics at the week scale, but
+found that window sizes smaller than $14$ limited the possibilities for shared
+trajectories and made determinism uninterpretable. In addition, window sizes
+larger than $14$ increasingly overshadowed the fine-grain dynamics that we wanted
+to investigate. Thus we decided to use a window size of $14$ to investigate the
+dynamics at the two week scale.
 
@@
 
-#### Permutation Test
+#### Approximate Permutation Test
 To visualize the differences in the WCRQA metrics from those obtained by chance,
-a permutation test was done to set upper and lower bounds for the 95th and 99th
-percentiles. Using a sample size of 14, $1000$ permuted time series were
-generated without replacement for each real time series. The upper and lower
-95th and 99th percentiles were set based on the distribution of the permuted
-WCRQA metrics.
+a permutation test was done. $1000$ permuted time series were generated (without
+replacement) of length $14$, (in accordance with the 14-day windows of real data
+for our WCRQA analyses), for each real time series; WCRQA was conducted on each
+combination of cohesion and event permuted time series. The upper and lower 95th
+and 99th percentiles for significance were set based on the distribution of the
+permuted WCRQA metrics.
 
@@
 peak in above-chance values. This suggests that the overall number of events
-were more consistent from day to day when considering source events, as might be
-expected given that individuals can only participate in a limited number of
-events each day. Days that previously had a lower than average number of target
-events may now have had a more near-average number of source and target events
-because the reduced participation in target events allows for increased
-participation and initiation of source events.
+were more consistent from day to day when considering both source and target
+events, as compared to target-only events. In other words, days that previously
+had a more variable number of target events may now have had a more stable
+number of source and target events.
 
@@
 social media platforms could be monitored for fluctuations indicating shifts in
-power and peace. Social media mobilization may thus help alert the world to
-citizens' actions and reactions that are otherwise suppressed by government
-regimes, providing insight into events that may not otherwise be broadcast and
-allowing for faster intervention.
+power and peace.
 

### 2020-12-31 manuscript.Rmd
Fix typo
Fix figures

@@
 streaming API, servers at the University of Texas at Austin collected the
-tweets. The servers were run on a stable (LTS) version of Ubuntu Linus (v.
+tweets. The servers were run on a stable (LTS) version of Ubuntu Linux (v.
 10.04) and were connected directly to the high-bandwidth UT network maintained
@@
 above-chance values did not match up temporally with that of the all-events time
-series (FIX Figure 10). This suggests that the early stretch of above-chance RR
-may have been captured in the RR of the all-events analysis, whereas the shorter
-stretches were overshadowed by the coupling with negative events. The early
-period of above-chance DET in the positive-event analysis aligned with the early
-period of above-chance RR, whereas the later stretch of significant DET values
-aligns temporally with that of the all-events analysis. It is possible that the
-later stretch reflected the decrease in the number of positive events happening
-(FIX see Fig. 4), while the relative sparsity of positive events led to an
-increase in coupling, with denizens rallying around dwindling bits of hope as
-time went on.
+series (Figure \@ref(fig:plot-wcrqa-targ-all)). This suggests that the early
+stretch of above-chance RR may have been captured in the RR of the all-events
+analysis, whereas the shorter stretches were overshadowed by the coupling with
+negative events. The early period of above-chance DET in the positive-event
+analysis aligned with the early period of above-chance RR, whereas the later
+stretch of significant DET values aligns temporally with that of the all-events
+analysis. It is possible that the later stretch reflected the decrease in the
+number of positive events happening (see Figure \@ref(fig:raw-event-ts-target)),
+while the relative sparsity of positive events led to an increase in coupling,
+with denizens rallying around dwindling bits of hope as time went on.
 

### 2020-12-31 manuscript.Rmd
Fix formatting for the jounal

@@
 The first level of cohesion that we will consider are the words within social
-media posts.  In Figure \@ref(fig:cohesion-in-tweets), we see four sequential
+media posts.  In Fig \@ref(fig:cohesion-in-tweets), we see four sequential
 tweets of four words each. Each sequential tweet contains some content included
@@
 
-[Figure \@ref(fig:cohesion-in-tweets) about here]
+[Fig \@ref(fig:cohesion-in-tweets) about here]
 
@@
 We tie the constructs of lexical, interlocutor, and social cohesion together in
-a theoretical framework called *sociolinguistic cohesion*, as shown in Figure
+a theoretical framework called *sociolinguistic cohesion*, as shown in Fig
 \@ref(fig:theoretical-framework). Previous values of linguistic cohesion should
@@
 
-[Figure \@ref(fig:theoretical-framework) about here]
+[Fig \@ref(fig:theoretical-framework) about here]
 
@@
 tweets. All hashtags were included in the analysis, while URLs were removed. The
-raw social cohesion time series can be seen in Figure
+raw social cohesion time series can be seen in Fig
 \@ref(fig:raw-cohesion-ts).
 
-[Figure \@ref(fig:raw-cohesion-ts) about here]
+[Fig \@ref(fig:raw-cohesion-ts) about here]
 
@@
 
-The raw event time series for target filtered data can be seen in Figure
+The raw event time series for target filtered data can be seen in Fig
 \@ref(fig:raw-event-ts-target). The raw event time series for source and target
-filtered data can be seen in Figure \@ref(fig:raw-event-ts-source-target).
-
-[Figures \@ref(fig:raw-event-ts-target) and
+filtered data can be seen in Fig \@ref(fig:raw-event-ts-source-target).
+
+[Figs \@ref(fig:raw-event-ts-target) and
 \@ref(fig:raw-event-ts-source-target) about here]
@@
 Because the social cohesion and event data have different scales and values, we
-converted each time series of daily values (e.g., Figure \@ref(fig:raw-ts)) into
-deciles (e.g., Figure \@ref(fig:deciled-ts)) to analyze the relative dynamics of
+converted each time series of daily values (e.g., Fig \@ref(fig:raw-ts)) into
+deciles (e.g., Fig \@ref(fig:deciled-ts)) to analyze the relative dynamics of
 different levels of social cohesion and counts of all, positive, and negative
@@
 
-[Figures \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]
+[Figs \@ref(fig:raw-ts) and \@ref(fig:deciled-ts) about here]
 
@@
 filled main diagonal line would indicate perfect in-phase synchrony between the
-two time series. See Figures
+two time series. See Figs
 \@ref(fig:plot-rp-targ)-\@ref(fig:plot-rp-source-targ) for examples of RPs.
@@
 of the metrics across time. These dynamics can then be linked to other external
-events. See Figures \@ref(fig:plot-wcrqa-targ-all) and
+events. See Figs \@ref(fig:plot-wcrqa-targ-all) and
 \@ref(fig:plot-wcrqa-source-targ-all) for examples.
@@
 a statistically significant difference from chance for DET, NRLINE, and LAM. All
-other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ);
+other metrics did not reach significance (Fig \@ref(fig:plot-rp-targ);
 \autoref{table-1}).
@@
 found a statistically significant difference from chance for DET, NRLINE, maxL,
-LAM, and TT. All other metrics did not reach significance (Figure
+LAM, and TT. All other metrics did not reach significance (Fig
 \@ref(fig:plot-rp-targ); \autoref{table-1}).
@@
 found a statistically significant difference from chance for DET, NRLINE, and
-maxL. All other metrics did not reach significance (Figure
+maxL. All other metrics did not reach significance (Fig
 \@ref(fig:plot-rp-targ); \autoref{table-1}).
 
-[Figure \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]
+[Fig \@ref(fig:plot-rp-targ) and \autoref{table-1} about here]
 
@@
 a statistically significant difference from chance for DET, maxL, and LAM. All
-other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ);
+other metrics were non-significant (Fig \@ref(fig:plot-rp-source-targ);
 \autoref{table-2}).
@@
 found a statistically significant difference from chance for DET, L, ENTR,
-rENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
+rENTR, and LAM (Fig \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
 
@@
 found no statistically significant difference from chance for and metrics
-(Figure \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
-
-[Figure \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]
+(Fig \@ref(fig:plot-rp-source-targ); \autoref{table-2}).
+
+[Fig \@ref(fig:plot-rp-source-targ) and \autoref{table-2} about here]
 
@@
 
-In the WCRQA plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and
+In the WCRQA plots (see Figs \@ref(fig:plot-wcrqa-targ-all) and
 \@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented by
@@
 or above-chance RR from the 3rd--12th and 44th--50th window. DET was largely
-above chance from the 47th to the 54th window, with some exceptions (Figure
+above chance from the 47th to the 54th window, with some exceptions (Fig
 \@ref(fig:plot-wcrqa-targ-all)).
@@
 also appeared for the 40th--42nd windows. DET was intermittently at or above
-chance for the 8th--14th and 54th--62nd windows (Figure
+chance for the 8th--14th and 54th--62nd windows (Fig
 \@ref(fig:plot-wcrqa-targ-all)).
@@
 15th--23rd windows. The metric was above or nearly above chance only toward the
-end of the time series, in the 47th--54th and 62nd windows (Figure
+end of the time series, in the 47th--54th and 62nd windows (Fig
 \@ref(fig:plot-wcrqa-targ-all)).
 
-[Figure \@ref(fig:plot-wcrqa-targ-all) about here]
+[Fig \@ref(fig:plot-wcrqa-targ-all) about here]
 
@@
 windows. RR was consistently below chance for the 29th--39th windows. DET showed
-above- or nearly above-chance values in windows 7--11 and 59--62 (Figure
+above- or nearly above-chance values in windows 7--11 and 59--62 (Fig
 \@ref(fig:plot-wcrqa-source-targ-all)).
@@
 30th--38th windows. DET stayed largely within chance with intermittent
-bottoming-out to a value of 0 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
+bottoming-out to a value of 0 (Fig \@ref(fig:plot-wcrqa-source-targ-all)).
 
@@
 bottomed out for the 34th--45th windows, and consistently bottomed out for the
-52nd--62nd windows. (Figure \@ref(fig:plot-wcrqa-source-targ-all)).
-
-[Figure \@ref(fig:plot-wcrqa-source-targ-all) about here]
+52nd--62nd windows. (Fig \@ref(fig:plot-wcrqa-source-targ-all)).
+
+[Fig \@ref(fig:plot-wcrqa-source-targ-all) about here]
 
@@
 ### Syria as Target
-For the RR values in WCRQA of social cohesion and count of all events (Figure
+For the RR values in WCRQA of social cohesion and count of all events (Fig
 \@ref(fig:plot-wcrqa-targ-all)), we see both an early and late above-chance
 peak. However, DET for these periods only rises above chance for the later peak.
-During this later period, the modal ICEWS event for each day (Figure
+During this later period, the modal ICEWS event for each day (Fig
 \@ref(fig:plot-mode-event)) was almost consistently -10, the most violent event
@@
 
-[Figure \@ref(fig:plot-mode-event) about here]
+[Fig \@ref(fig:plot-mode-event) about here]
 
@@
 above-chance values did not match up temporally with that of the all-events time
-series (Figure \@ref(fig:plot-wcrqa-targ-all)). This suggests that the early
+series (Fig \@ref(fig:plot-wcrqa-targ-all)). This suggests that the early
 stretch of above-chance RR may have been captured in the RR of the all-events
@@
 analysis. It is possible that the later stretch reflected the decrease in the
-number of positive events happening (see Figure \@ref(fig:raw-event-ts-target)),
+number of positive events happening (see Fig \@ref(fig:raw-event-ts-target)),
 while the relative sparsity of positive events led to an increase in coupling,

### 2020-12-31 scripts/primary-analyses/00_tweet_stats.R
Fix tweet counts and duration counts

@@ -5,14 +5,9 @@
 #
 # Code by: M. Chiovaro (@mchiovaro) and A. Paxton (@a-paxton)
 # University of Connecticut
-# Last updated: 2020_12_22
+# Last updated: 2020_12_31
 
 #### 1. Set up ####
-
-#setwd("./Documents/_github/arab-spring/")
-
-library(data.table)
-library(readxl)
 
 # clear environment
 rm(list=ls())
@@ -68,7 +63,7 @@ formatted_tweets <- raw_tweets %>%
 hist(formatted_tweets$time_to_tweet, xlim=c(0, 55))
 
 # get empty data frame
-stats = data.frame(matrix(NA, ncol=14))
+stats = data.frame(matrix(NA, ncol=17))
 colnames(stats) <- c("avg_time_to_tweet",
                      "max_time_to_tweet",
                      "min_time_to_tweet",
@@ -82,7 +77,10 @@ colnames(stats) <- c("avg_time_to_tweet",
                      "total_replies",
                      "percent_replies",
                      "percent_original_tweets",
-                     "total_original_tweets")
+                     "total_original_tweets",
+                     "avg_duration",
+                     "max_duration",
+                     "min_duration")
 
 # get time between tweets
 stats$avg_time_to_tweet <- mean(formatted_tweets$time_to_tweet[2:length(formatted_tweets)])
@@ -116,13 +114,13 @@ retweets = formatted_tweets %>%
 
 # identify replies
 replies = formatted_tweets %>%
-  dplyr::filter(!is.na(in_reply_to_screen_name))
+  dplyr::filter(!is.na(in_reply_to_status_id))
 
 # identify original tweets by stripping out retweets and replies
 original_tweets = anti_join(formatted_tweets,
-                                replies_alt) %>%
+                                replies) %>%
   anti_join(., 
-            retweets_alt)
+            retweets)
 
 # count retweets
 stats$retweets <- nrow(retweets)
@@ -142,12 +140,15 @@ percent_sum <- stats$percent_retweets + stats$percent_replies + stats$percent_or
 #### 4. Tweet group stats ####
 
 # check max and mins
-max(coh_data$Duration..s.)
-min(coh_data$Duration..s.)
+stats$avg_duration = mean(coh_data$Duration..s.)
+stats$max_duration = max(coh_data$Duration..s.)
+stats$min_duration = min(coh_data$Duration..s.)
+
[…]

### 2020-12-31 scripts/primary-analyses/02_crqa.R
Increase image size

@@ -130,7 +130,7 @@ crp_2 <- readPNG('./results/primary/crqa/source_target-rp-pos_events.png')
 crp_3 <- readPNG('./results/primary/crqa/source_target-rp-neg_events.png')
 
 # join images and save
-png("./results/primary/crqa/source_target-rp-joined.png", width=720,height=325)
+png("./results/primary/crqa/source_target-rp-joined.png", width=1440,height=650)
 grid.arrange(rasterGrob(crp_1), rasterGrob(crp_2), rasterGrob(crp_3), nrow=1)
 dev.off()
 
@@ -231,7 +231,7 @@ crp_2 <- readPNG('./results/primary/crqa/target-rp-pos_events.png')
 crp_3 <- readPNG('./results/primary/crqa/target-rp-neg_events.png')
 
 # join and save
-png("./results/primary/crqa/target-rp-joined.png", width=720,height=325)
+png("./results/primary/crqa/target-rp-joined.png", width=1440,height=650)
 grid.arrange(rasterGrob(crp_1), rasterGrob(crp_2), rasterGrob(crp_3), nrow=1)
 dev.off()
 

### 2020-12-31 scripts/primary-analyses/03_windowed_crqa.R
Fix figure header

@@ -747,7 +747,7 @@ plot_source_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with source and target filtering (ICEWS)",
+                       "with source and target filtering",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_source_target_windowed_all_RR,
@@ -999,7 +999,7 @@ plot_target_windowed_all = gridExtra::grid.arrange(
   top = textGrob(paste("Windowed cross-recurrence",
                        "quantification analysis",
                        "\nwith event count data",
-                       "with target-only filtering (ICEWS)",
+                       "with target-only filtering",
                        sep = " "),
                  gp=gpar(fontsize=15)), 
   plot_target_windowed_all_RR,
